### 2019-09-13 Documentation/Replication_Instruction.tex
initialization

% Article Format: American Economic Review
% Xin Tang @ Stony Brook University
% Last Updated: August 2014
\documentclass[twoside,11pt,leqno]{article}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                    Text Layout                       %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Page Layout
\usepackage[hmargin={1.2in,1.2in},vmargin={1.5in,1.5in}]{geometry}
\topmargin -1cm        % read Lamport p.163
\oddsidemargin 0.04cm   % read Lamport p.163
\evensidemargin 0.04cm  % same as oddsidemargin but for left-hand pages
\textwidth 16.59cm
\textheight 21.94cm
\renewcommand\baselinestretch{1.15}
\parskip 0.25em
\parindent 1em
\linespread{1}

% Set header and footer
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhead{}
\fancyhead[LE,RO]{\thepage}
%\fancyhead[CE]{\textit{JI QI, XIN TANG AND XICAN XI}}
%\fancyhead[CO]{\textit{THE SIZE DISTRIBUTION OF FIRMS AND INDUSTRIAL POLLUTION}}
\cfoot{}
\renewcommand{\headrulewidth}{0pt}
%\renewcommand*\footnoterule{}
%\setcounter{page}{1}

% Font
\renewcommand{\rmdefault}{ptm}
\renewcommand{\sfdefault}{phv}
%\usepackage[lite]{mtpro2}
% use Palatinho-Roman as default font family
%\renewcommand{\rmdefault}{ppl}
\usepackage[scaled=0.88]{helvet}
\makeatletter   % Roman Numbers
\newcommand*{\rom}[1]{\expandafter\@slowromancap\romannumeral #1@}
\makeatother
\usepackage{CJK}

% Section Titles
\renewcommand\thesection{\textnormal{\textbf{\Roman{section}.}}}
\renewcommand\thesubsection{\textnormal{\Alph{subsection}.}}
\usepackage{titlesec}
\titleformat*{\section}{\bf \center}
\titleformat*{\subsection}{\it \center}
\renewcommand{\refname}{\textnormal{REFERENCES}}

% Appendix
\usepackage[title]{appendix}
\renewcommand{\appendixname}{APPENDIX}

% Citations
\usepackage[authoryear,comma]{natbib}
\renewcommand{\bibfont}{\small}
\setlength{\bibsep}{0em}
\usepackage[%dvipdfmx,%
            bookmarks=true,%
            pdfstartview=FitH,%
            breaklinks=true,%
            colorlinks=true,%
            %allcolors=black,%
            citecolor=blue,
            linkcolor=red,
            pagebackref=true]{hyperref}

% Functional Package
\usepackage{enumerate}
\usepackage{url}      % This package helps to typeset urls

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                    Mathematics                       %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{amsmath,amssymb,amsfonts,amsthm,mathrsfs,upgreek}
% Operators
\newcommand{\E}{\mathbb{E}}
\newcommand{\e}{\mathrm{e}}
\DeclareMathOperator*{\argmax}{argmax}
\DeclareMathOperator*{\argmin}{argmin}
\DeclareMathOperator*{\plim}{plim}
\renewcommand{\vec}[1]{\ensuremath{\mathbf{#1}}}
\newcommand{\gvec}[1]{{\boldsymbol{#1}}}

\newcommand{\code}{\texttt}
\newcommand{\bcode}[1]{\texttt{\blue{#1}}}
\newcommand{\rcode}[1]{\texttt{\red{#1}}}
\newcommand{\rtext}[1]{{\red{#1}}}
\newcommand{\btext}[1]{{\blue{#1}}}

% New Environments
\newtheorem{result}{Result}
\newtheorem{assumption}{Assumption}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newtheorem{definition}{Definition}
\setlength{\unitlength}{1mm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                 Tables and Figures                   %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{threeparttable,booktabs,multirow,array} % This allows notes in tables
\usepackage{floatrow} % For Figure Notes
\floatsetup[table]{capposition=top}
\usepackage[font={sc,footnotesize}]{caption}
\DeclareCaptionLabelSeparator{aer}{---}
\captionsetup[table]{labelsep=aer}
\captionsetup[figure]{labelsep=period}
\usepackage{graphicx,pstricks,epstopdf}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                 Insert Code Snippet                  %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{listings,textcomp,upquote}
\lstset{
     language=fortran,
     frame = single,
%     backgroundcolor=\color[RGB]{255,228,202}, % pink
     backgroundcolor=\color[RGB]{231,240,233}, % green
%     backgroundcolor=\color[RGB]{239,240,248},
     framerule=0pt,
     showstringspaces=false,
     basicstyle=\ttfamily\footnotesize,
     numbers=left,
     stepnumber=1,
     numberstyle=\tiny,
     keywordstyle=\color{blue}\ttfamily,
     stringstyle=\color{red}\ttfamily,
     commentstyle=\color[rgb]{.133,.545,.133}\ttfamily,
     morecomment=[l][\color{magenta}]{\#},
     fontadjust,
     captionpos=t,
     framextopmargin=2pt,framexbottommargin=2pt,
     abovecaptionskip=4ex,belowcaptionskip=3pt,
     belowskip=3pt,
     framexleftmargin=4pt,
     xleftmargin=4em,xrightmargin=4em,
     texcl=false,
     extendedchars=false,columns=flexible,mathescape=true,
     captionpos=b,
}
\renewcommand{\lstlistingname}{Source Code}

\title{\vspace{-1cm}\Large{\textsf{The Size Distribution of Firms and Industrial Water Pollution: A Quantitative Analysis of China} \\ \textsf{Replication Instruction}}}
\author{\normalsize\textsc{Xin Tang} \\ \normalsize\textsc{International Monetary Fund}}
\date{\normalsize\today}

\begin{document}
\maketitle

This note explains step-by-step how to replicate all the results in \textit{The Size Distribution of Firms and Industrial Water Pollution: A Quantitative Analysis of China}.

\end{document}

### 2019-09-16 Documentation/Replication_Instruction.tex
daily sync

@@
 This note explains step-by-step how to replicate all the results in \textit{The Size Distribution of Firms and Industrial Water Pollution: A Quantitative Analysis of China}.
+We begin with several house-keeping notes.
+We begin with some housekeeping stuff in Section \rom{1}.
+Section \rom{2} explains in detail how to replicate all the empirical results.
+
+\section{Housekeeping Stuff}
+
+To replicate all the results in the paper, three softwares are used.
+Specifically, \textsc{Stata} is used for initial data processing.
+All the empirical results are then produced using \code{R}.
+We use MATLAB to compute all the quantitative results.
+There is no particular scientific reason that we use one statistical software (\textsc{Stata}) for data cleaning and the other (\code{R}) for empirical analysis.
+It is easier to handle Chinese characters with \textsc{Stata} while \code{R} switches back and forth between different datasets swiftly.
+Veterans of \textsc{Stata} (or \code{R}) should be able to replicate all the empirical results with just one software using our source code as reference with ease.
+In addition, which in fact should go without saying, for readers without a licence to MATALB, GNU Octave could be used instead.
+
+We use three datasets in our analysis: The National General Survey of Pollution Sources (NGSPS, \begin{CJK}{GBK}{kai}第一次全国污染源普查\end{CJK}), The National Economic Census (CNEC, \begin{CJK}{GBK}{kai}第一次全国经济普查\end{CJK}) and the Statistics of U.S.
+Businesses (SUSB).
+\begin{itemize}
+    \item
+    The NGSPS is a confidential dataset housed at the Ministry of Ecology and Environment.
+The data can only be accessed within the Ministry of Ecology and Environment as well as institutions under its direct supervision.
+Individual researchers requesting access should submit the application through the official portal for Information Access (\begin{CJK}{GBK}{kai}政府信息公开\end{CJK}) by the Ministry of Ecology and Environment at the following url: \url{http://www.mee.gov.cn/weihu/201706/t20170625_416641.shtml}.
+The url is retrieved on September 15th, 2019 and may vary in the future.
+All applications are subject to official approval by the Ministry of Ecology and Environment.
+    \item
+    The CNEC is also a confidential dataset belonging to National Bureau of Statistics of China.
+Many universities and institutions have legal copy of the dataset.
+Our copy was obtained from Wuhan University.
+One portal to request access to the data for individual researchers is through the Micro-data Lab of the National Bureau of Statistics (\begin{CJK}{GBK}{kai}国家统计局微观数据实验室，国家统计局-清华大学数据开发中心\end{CJK}).
+The url, retrieved on September 15th, 2019, is \url{http://microdata.stats.gov.cn/}; and again it may vary in the future.
+All applications are subject to official approval by the National Bureau of Statistics.
+    \item
+    The SUSB is publicly available from the Census Bureau's dedicated website.
+The url, retrieved on September 15th, 2019, and subject to possible change in the future, is \url{https://www.census.gov/programs-surveys/susb.html}.
+\end{itemize}
+
+In the replication files, we cannot provide micro-level data of the NGSPS, due to the Non-Disclosure Agreement with the Ministry of Ecology and Environment.
+Therefore, we only post the source code that generates the results.
+The NGSPS is used to compute the following results:
+\begin{itemize}
+    \item
+    Tables: 1, 2, A.1, C.1, D.1 and F.1.
+    \item
+    Figures: 1, B.1 (upper panels), C.1, C.2, D.3.
+    \item
+    Regressions: 1 and the un-numbered one in Section \rom{1}.B, 2, 3, the 6 un-numbered regression in Appendix C.1 and the un-numbered regression in Appendix D.2.
+    \item
+    Some miscellaneous information scattered across the paper.
+\end{itemize}
+
+\section{Empirical Results}
+
+The instructions are organized by logic instead of the order of appearance in the paper.
+
+\section{Quantitative Results}
 

### 2019-09-16 Documentation/Replication_Instruction.tex
daily sync

@@
 This note explains step-by-step how to replicate all the results in \textit{The Size Distribution of Firms and Industrial Water Pollution: A Quantitative Analysis of China}.
-We begin with several house-keeping notes.
 We begin with some housekeeping stuff in Section \rom{1}.
 Section \rom{2} explains in detail how to replicate all the empirical results.
+Section \rom{3} shows how the quantitative results can be replicated.
 
 \section{Housekeeping Stuff}
+
+\subsection{Overview}
 
@@
 All the empirical results are then produced using \code{R}.
-We use MATLAB to compute all the quantitative results.
+MATLAB is used to compute all the quantitative results.
 There is no particular scientific reason that we use one statistical software (\textsc{Stata}) for data cleaning and the other (\code{R}) for empirical analysis.
-It is easier to handle Chinese characters with \textsc{Stata} while \code{R} switches back and forth between different datasets swiftly.
+We do this simply because it is easier to handle Chinese characters with \textsc{Stata} while \code{R} switches back and forth between different datasets swiftly.
 Veterans of \textsc{Stata} (or \code{R}) should be able to replicate all the empirical results with just one software using our source code as reference with ease.
@@
 \end{itemize}
+The rest of the results can all be replicated by following this guide.
+
+\subsection{File Structures}
+
+The readers will get a number of files for replicating the results.
+To ease digestion, we briefly introduce the structure of the folders and files.
+As typographical convention, we use \bcode{blue computer modern typewriter} to indicate \bcode{folders}, and \code{black computer modern typewriter} to label \code{files}.
+The current folder is referred to as \code{./}.
+\begin{itemize}
+    \item
+    \bcode{./Empirical/}:
+    \begin{itemize}
+        \item
+        \bcode{./Data/}
+        \item
+        \bcode{./Results/}
+        \item
+        \code{./cpsc\_raw.do}
+        \item
+        \code{./cec\_clean.do}
+        \item
+        \code{./cpsc\_convert.R}
+        \item
+        \code{./cec\_convert.R}        
+        \item
+        \code{./Empirical\_AEJ.R}        
+        \item
+        \code{./Empirical\_Appendix.R}                
+        \item
+        \code{./Accounting.R}
+    \end{itemize}
+    \item
+    \bcode{./Quantitative/}
+    \begin{itemize}
+        \item
+        \bcode{./Results/}
+        \item
+        \bcode{./Figures/}
+        \item
+        \code{./twosectors.m}
+        \item
+        \code{./fcn2.m}
+        \item
+        \code{./compute\_tables.m}
+        \item
+        \code{./plot\_figures.m}
+        \item
+        \code{./twosectors\_ces.m}        
+        \item
+        \code{./fcnces.m}        
+        \item
+        \code{./compute\_tables\_ces.m}   
+        \item
+        \code{./misc.m}     
+    \end{itemize}
+\end{itemize}
+
+\subsection{Data Cleaning}
 
@@
 
+\begin{enumerate}
+    \item
+    set \code{twosectors.m} to benchmark and run
+    \item
+    set \code{twosectors.m} to no tax and run
+    \item
+    set \code{twosectors.m} to regulation and run
+    \item
+    set \code{twosectors.m} to flat tax and run
+    \item
+    run \code{plot\_figures.m}
+    \item
+    set \code{compute\_tables.m} to benchmark and run
+    \item
+    set \code{compute\_tables.m} to no tax and run    
+    \item
+    set \code{compute\_tables.m} to regulation and run    
+    \item
+    set \code{compute\_tables.m} to flat tax and run    
+    \item
+    manually compute the numbers for the tables
+\end{enumerate}
+
 \end{document}

### 2019-09-16 Empirical/Accounting.R

@@ -1,0 +1,689 @@
+# Code File for computing the accouting exercises
+# Data from: China Economic Census and Statistics of US Businesses
+# Xin Tang @ Stony Brook University
+# Last Updated: July 2014
+
+# Clear memory
+rm(list = ls())
+
+# Load in packages
+library(foreign)
+library(data.table)
+library(AER)
+library(ggplot2)
+library(scales)
+library(grid)
+
+# Load SUSB Data
+USall <- read.csv("./Data/susb04.csv",header = TRUE)  # Statistics of US Businesses
+USall <- as.data.table(USall)
+USall <- USall[,list(NAICS, ENTRSIZE, FIRM, ESTB, EMPL, NAICSDSCR, ENTRSIZEDSCR)]
+USleft <- c(1,5,10,15,20,25,30,35,40,45,50,75,100,150,200,300,400,500,750,1000,1500,2500)
+USright <- c(4,9,14,19,24,29,34,39,44,49,74,99,149,199,299,399,499,749,999,1499,2499,10000)
+NUS <- length(USleft)
+
+# Load CNEC Data
+# load("DLARGE_R.RData")
+# DLARGE <- as.data.table(DLARGE)
+# load("DSMALL_R.RData")
+# DSMALL <- as.data.table(DSMALL)
+# # Combine the LARGE and SMALL from CEC
+# ljunk <- DLARGE[,list(industry,nbarworkers,industry_a,status,nbarworkers,product)]
+# sjunk <- DSMALL[,list(industry,nbarworkers,industry_a,status,nbarworkers,product)]
+# CHNprod <- rbind(ljunk,sjunk)
+# # Release memory usage
+# rm(DLARGE,DSMALL,ljunk,sjunk)
+# save(CHNprod, file = "CHprod_all.RData")
+load("./Data/CNEC_avgp.RData")
+CHNprod <- CNEC_avgp
+# Select only firms with positive employment, product and are operating normally
+sel <- which(CHNprod$status == 1 & CHNprod$nbarworkers > 0 & CHNprod$product > 0 )
+CHNprod <- CHNprod[sel]
+CHleft <- rep(0,NUS)
+CHright <- CHleft
+# Load NGSPS
+load("./Data/KEYFIRM_R.RData")
+CHNpol <- KEYFIRM[,list(industry,industry_a,opr_hours,product,cod_e)]
+sel <- which(CHNpol$opr_hours > 0 & CHNpol$product > 0 & CHNpol$cod_e > 0)
[…]

### 2019-09-16 Empirical/Empirical_AEJ.R

@@ -1,0 +1,575 @@
+# -------------------------------------------------------------------------
+#                       Program Description
+# -------------------------------------------------------------------------
+#    
+# Purpose:
+#     - Produce all the empirical results in the main text.
+#     - 1. log(COD)~log(Sales) and Figure 1
+#     - 2. Inv~log(Sales)
+#     - 3. log(COD)~log(Sales) for Dirty and Clean
+#     - 4. Figure 2
+#     - 5. Distortions
+#     - The Size Distribution of Firms and Industrial Water Pollution: A
+#       Quantitative Analysis of China
+#     - Prepared for AEJM Final Submission
+# 
+# Author:
+#     - Xin Tang @ International Monetary Fund
+# 
+# Record of Revisions:
+#          Date:                 Description of Changes
+#    ============        =================================
+#       04/06/2019                 Original Version
+#       09/16/2019                Improved Annotation
+# =========================================================================
+# Clear memory
+rm(list = ls())
+
+# Load in packages
+library(foreign)
+library(data.table)
+library(AER)
+library(scales)
+library(grid)
+
+# =========================================================================
+#                   0. Aggregating Categorical Variables
+# =========================================================================
+load("./Data/KEYFIRM_R.RData")
+# ------------ Aggregate ownership rights type ------------------
+# 0: missing, 1: State/collective, 3: private, 4: HMT, 5: foreign
+KEYFIRM$type_a <- 0
+# State and collective
+sel <- which(KEYFIRM$type == 110 | KEYFIRM$type == 141
+    | KEYFIRM$type == 151 | KEYFIRM$type == 120 | KEYFIRM$type == 130
+    | KEYFIRM$type == 140 | KEYFIRM$type == 150 | KEYFIRM$type == 142
[…]

### 2019-09-16 Empirical/Empirical_Appendix.R

@@ -1,0 +1,371 @@
+# -------------------------------------------------------------------------
+#                       Program Description
+# -------------------------------------------------------------------------
+#    
+# Purpose:
+#     - Produce all the empirical results in the online appendix.
+#     - 1. log(COD)~log(Sales) and Figure 1
+#     - 2. Inv~log(Sales)
+#     - 3. log(COD)~log(Sales) for Dirty and Clean
+#     - 4. Figure 2
+#     - 5. Distortions
+#     - The Size Distribution of Firms and Industrial Water Pollution: A
+#       Quantitative Analysis of China
+#     - Prepared for AEJM R&R
+# 
+# Author:
+#     - Xin Tang @ International Monetary Fund
+# 
+# Record of Revisions:
+#          Date:                 Description of Changes
+#    ============        =================================
+#       04/06/2019                 Original Version
+# =========================================================================
+# Clear memory
+rm(list = ls())
+
+# Load in packages
+library(foreign)
+library(data.table)
+library(AER)
+library(scales)
+library(grid)
+
+# Set working directory
+PathIn <- paste("C:/Users/zjuta/Dropbox/Daily Printing/PollutionPaper",
+      "AEJ_Submission/R&R/Empirical", sep="/")
+setwd(PathIn)
+
+# =====================================================================
+#                       Figures
+# =====================================================================
+# Distribution of output for NGSPS (Key/All), CNEC (All/Large)
+# Read the full sample of CNEC 
+load("./Data/CHprod_all.RData")
+# Drop missing values
+sel <- which(CHNprod$product > 0)
+CHNprod <- CHNprod[sel]
+# CNEC records output in 2004 CNY 1000, but NGSPS records output 
+#   in 2007 CNY 10,000.
+deflator <- 96.30/93.50
[…]

### 2019-09-16 Empirical/cec_convert.R

@@ -1,0 +1,183 @@
+# -------------------------------------------------------------------------
+#                       Program Description
+# -------------------------------------------------------------------------
+#    
+# Purpose:
+#     - Convert CNEC from Stata format to R binary format
+# 
+# Author:
+#     - Xin Tang @ Stony Brook, May 2014
+# 
+# Record of Revisions:
+#       Date:                 Description of Changes
+#    ============        =================================
+#     05/25/2014                 Original Version
+#     09/16/2019                Improved Annotation
+# =========================================================================
+
+# Clear memory
+rm(list = ls())
+
+# Load in packages
+library(foreign)
+library(data.table)
+
+# -------------------------------------------------------------------------
+#                           Small Firms
+# -------------------------------------------------------------------------
+# Read in Data
+tmpread <- read.dta("./Data/cec2004_small.dta")
+# For faster processing, save data as data.table
+DSMALL <- data.table(tmpread, key=c("firm_id"))
+rm(tmpread) # free the temp file
+
+# Commenting Variables
+comment(DSMALL$firm_id) <- "Firm's Identifier"
+comment(DSMALL$areacode) <- "Firm's Administrative Region"
+comment(DSMALL$industry) <- "4 Digits GB2002 Sector"
+comment(DSMALL$type) <- "Firm's Ownership Rights Type"
+comment(DSMALL$statectl) <- "State Control of Firm"
+comment(DSMALL$admintier) <- 
+    "Level of government firm registers under"
+comment(DSMALL$founding_y) <- "Founding Year"
+comment(DSMALL$founding_m) <- "Founding Month"
+comment(DSMALL$status) <- "Operating Status of Firm"
+comment(DSMALL$nworkers) <- "# of Workers END of year"
+comment(DSMALL$product) <- "Total Industrial Output Value"
+comment(DSMALL$sales) <- "Total Sales Value"
+comment(DSMALL$export) <- "Total Value of sales to abroad"
+comment(DSMALL$capital) <- "Book Value of Fixed Capital"
+comment(DSMALL$cur_depre) <- "Current Year Depreciation"
+comment(DSMALL$sales_cost) <- 
[…]

### 2019-09-16 Empirical/cpsc_convert.R

@@ -1,0 +1,214 @@
+# -------------------------------------------------------------------------
+#                       Program Description
+# -------------------------------------------------------------------------
+#    
+# Purpose:
+#     - Convert NGSPS from Stata format to R binary format
+# 
+# Author:
+#     - Xin Tang @ Stony Brook, May 2014
+# 
+# Record of Revisions:
+#       Date:                 Description of Changes
+#    ============        =================================
+#     05/25/2014                 Original Version
+#     09/16/2019                Improved Annotation
+# =========================================================================
+
+# Clear memory
+rm(list = ls())
+
+# Load in packages
+library(foreign)
+library(data.table)
+
+# Set working directory
+setwd("D:/Computation/pollution_rep/Empirical")
+
+# -------------------------------------------------------------------------
+#                           Key Firms
+# -------------------------------------------------------------------------
+PathIn <- "./Data"
+File <- paste(PathIn, "keynum.dta", sep = "/")
+
+KEYFIRM <- read.dta(File)
+# For faster processing, save data as data.table
+KEYFIRM <- data.table(KEYFIRM, key=c("firm_id"))
+
+comment(KEYFIRM$firm_id) <- "Firm ID"
+comment(KEYFIRM$areacode) <- "Area Code up to the Level of Subdistrict"
+comment(KEYFIRM$industry) <- "4-digits Industrial Sector Code (GB2002)"
+comment(KEYFIRM$type) <- "Ownership Rights of the Firm"
+comment(KEYFIRM$opr_hours) <- "Total Annual Operating Hours"
+comment(KEYFIRM$product) <- "Total VALUE of Output (in RMB10000)"
+comment(KEYFIRM$quantity1) <- "Total QUANTITY of Output 1"
+comment(KEYFIRM$quantity2) <- "Total QUANTITY of Output 2"
+comment(KEYFIRM$quantity3) <- "Total QUANTITY of Output 3"
[…]

### 2019-09-16 Quantitative/compute_tables.m

@@ -1,0 +1,226 @@
+% -------------------------------------------------------------------------
+%                      Program Description
+% -------------------------------------------------------------------------
+%   
+% Purpose:
+%     - Compute Entries in the Tables
+%     - Two Sectors Model
+%     - The Size Distribution of Firms and Industrial Water Pollution: A
+%       Quantitative Analysis of China.
+%  
+% Author:
+%     - Xin Tang @ International Monetary Fund
+% 
+% File Dependence:
+%     - fcn.m: evaluates all the allocations at a given wage and returns 
+%       the excess demand in the labor market.
+%  
+% Record of Revisions:
+%         Date:                 Description of Changes
+%     ============        =================================
+%      04/19/2019                 Original Version
+% =========================================================================
+clc;
+clear all;
+
+% ================ Load Data ======================
+% load('./Results/benchmark_new.mat');
+% disp('Print Results for the Benchmark')
+% load('./Results/notax_new.mat');
+% disp('Print Results for the No-tax case')
+% load('./Results/regulation_new.mat');
+% disp('Print Results for the Regulation case')
+load('./Results/flattax_new.mat');
+disp('Print Results for the Flat Tax')
+
+% =========================================================================
+%                               Table 5
+%                          Aggregate Impacts
+% =========================================================================
+% ================ Compute the Results ======================
+% --------------- Panel A -------------------
+% Aggregate Output
+aggyd = sum(yd(indzhatd:end).*zprob(indzhatd:end));
+aggyc = sum(yc(indzhatc:end).*zprob(indzhatc:end));
+aggy  = mud*aggyd + (1-mud)*aggyc;
+% Aggregate Capital
+aggkd = sum(kdd(indzhatd:end).*zprob(indzhatd:end));
+aggkd = aggkd + ke*sum(zprob(indztilded:end));
+aggkc = sum(kdc(indzhatc:end).*zprob(indzhatc:end));
[…]

### 2019-09-16 Quantitative/compute_tables_ces.m

@@ -1,0 +1,112 @@
+% -------------------------------------------------------------------------
+%                      Program Description
+% -------------------------------------------------------------------------
+%   
+% Purpose:
+%     - Compute Entries in the Tables for the Online Appendix.
+%     - Two Sectors Model with CES aggregation.
+%     - The Size Distribution of Firms and Industrial Water Pollution: A
+%       Quantitative Analysis of China.
+%  
+% Author:
+%     - Xin Tang @ International Monetary Fund
+% 
+% File Dependence:
+%     - fcn.m: evaluates all the allocations at a given wage and returns 
+%       the excess demand in the labor market.
+%  
+% Record of Revisions:
+%         Date:                 Description of Changes
+%     ============        =================================
+%      04/19/2019                 Original Version
+% =========================================================================
+clc;
+clear all;
+
+% ================ Load Data ======================
+% load('./Results/benchmark_ces.mat');
+% disp('Print Results for the CES Benchmark')
+% load('./Results/nodirty_ces.mat');
+% disp('Print Results for the CES No Dirty Tax')
+% load('./Results/notax_ces.mat');
+% disp('Print Results for the CES No Tax')
+% load('./Results/benchmark_ces3.mat');
+% disp('Print Results for the CES 3 Benchmark')
+% load('./Results/notax_ces3.mat');
+% disp('Print Results for the CES 3 No Tax')
+load('./Results/nodirty_ces3.mat');
+disp('Print Results for the CES 3 No Dirty Tax')
+
+% =========================================================================
+%                               Table 5
+%                          Aggregate Impacts
+% =========================================================================
+% ================ Compute the Results ======================
+% --------------- Panel A -------------------
+% Aggregate Output
+aggyd = sum(yd(indzhatd:end).*zprob(indzhatd:end));
+aggyc = sum(yc(indzhatc:end).*zprob(indzhatc:end));
+aggypd = priced*aggyd;
+aggypc = pricec*aggyc;
+aggyp = aggypd+aggypc;
+aggy = (varces*aggyd^((sigmaces-1)/sigmaces)+...
+    (1-varces)*aggyc^((sigmaces-1)/sigmaces))^(sigmaces/(sigmaces-1));
+
+% --------------- Panel B -------------------
[…]

### 2019-09-16 Quantitative/fcn2.m

@@ -1,0 +1,71 @@
+% -------------------------------------------------------------------------
+%                      Program Description
+% -------------------------------------------------------------------------
+%   
+% Purpose:
+%     - Evaluates the allocations and returns the excess demand in the 
+%       labor market.
+%     - Two sectors model
+%     - The Size Distribution of Firms and Industrial Water Pollution: A
+%       Quantitative Analysis of China.
+%  
+% Author:
+%     Xin Tang @ International Monetary Fund
+%  
+% Record of Revisions:
+%         Date:                 Description of Changes
+%     ============        =================================
+%      04/10/2019                  Original Version
+% =========================================================================
+
+function out = fcn2(wage)
+
+% ================== Declare global variables =====================
+% Shared with pollution_main.m
+% ------ Model parameters -------
+% Technology and Preference
+global gamma alpha ke rss
+% Size Distribution
+global zgrid zprob mud
+% Regulation
+global xi tauzd tauzc
+% ------ Allocations -------
+global zhatc zhatd ztilded indzhatc indzhatd indztilded 
+global ldd kdd yd ldc kdc yc pi0d pi1d pid pic
+
+% ================== Factor Demand =====================
+kappa = (alpha/(1-alpha))*(wage/rss) ;      % capital-labor ratio
+% Polluting Firms
+ldd = (wage./((1-alpha)*gamma*(1-tauzd)*kappa^(alpha*gamma)))...
+    .^(1/(gamma-1)).*zgrid ;                % labor demand
+kdd = kappa*ldd ;                             % capital demand
+yd  = zgrid.^(1-gamma)*(kappa^(alpha*gamma)).*(ldd.^gamma) ;   % Output
+pi0d = (1-xi)*((1-tauzd).*yd - wage*ldd - rss*kdd);      % dirty profits
+pi1d = ((1-tauzd).*yd - rss*kdd - wage*ldd) - rss*ke;    % clean profits
+pid  = max(pi0d,pi1d);
+% Non-polluting Firms
+ldc = (wage./((1-alpha)*gamma*(1-tauzc)*kappa^(alpha*gamma)))...
+    .^(1/(gamma-1)).*zgrid ;                % labor demand
[…]

### 2019-09-16 Quantitative/fcnces.m

@@ -1,0 +1,84 @@
+% -------------------------------------------------------------------------
+%                      Program Description
+% -------------------------------------------------------------------------
+%   
+% Purpose:
+%     - Evaluates the allocations and returns the excess demand in the 
+%       labor market.
+%     - Two sectors model: ces
+%     - The Size Distribution of Firms and Industrial Water Pollution: A
+%       Quantitative Analysis of China.
+%  
+% Author:
+%     Xin Tang @ International Monetary Fund
+%  
+% Record of Revisions:
+%         Date:                 Description of Changes
+%     ============        =================================
+%      04/10/2019                  Original Version
+% =========================================================================
+
+function out = fcnces(input)
+
+% ================== Declare global variables =====================
+% Shared with pollution_main.m
+% ------ Model parameters -------
+% Technology and Preference
+global gamma alpha ke rss sigmaces varces
+% Size Distribution
+global zgrid zprob mud
+% Regulation
+global xi tauzd tauzc
+% ------ Allocations -------
+global zhatc zhatd ztilded indzhatc indzhatd indztilded 
+global ldd kdd yd ldc kdc yc pi0d pi1d pid pic
+% debug
+global aggld aggls aggyd aggyc outrhs
+
+wage = input(1);
+pd   = input(2);
+pc   = ( (1-varces^sigmaces*pd^(1-sigmaces))...
+    /(1-varces)^sigmaces )^(1/(1-sigmaces));
+
+% ================== Factor Demand =====================
+kappa = (alpha/(1-alpha))*(wage/rss) ;      % capital-labor ratio
+% Polluting Firms
+ldd = (wage./((1-alpha)*pd*gamma*(1-tauzd)*kappa^(alpha*gamma)))...
+    .^(1/(gamma-1)).*zgrid ;                % labor demand
+kdd = kappa*ldd ;                             % capital demand
+yd  = zgrid.^(1-gamma)*(kappa^(alpha*gamma)).*(ldd.^gamma) ;   % Output
[…]

### 2019-09-16 Quantitative/misc.m

@@ -1,0 +1,51 @@
+% =========================================================================
+% The role of size distribution
+% A hypothetical world where the two equipments are the same.
+clear all;
+load('./Results/benchmark_new.mat');
+aggyd = sum(yd(indzhatd:end).*zprob(indzhatd:end));
+aggyc = sum(yc(indzhatc:end).*zprob(indzhatc:end));
+aggy  = mud*aggyd + (1-mud)*aggyc;
+ksid_0 = -3.4114;
+ksid_1 = -0.3636;
+ez_nt = exp(ksid_0)*yd(indzhatd:end).^(1+ksid_1);
+agge_nt_bench = sum(ez_nt.*zprob(indzhatd:end));
+aggi_nt_bench = agge_nt_bench/aggyd;
+clearvars -except ez_nt agge_nt_bench aggi_nt_bench 
+
+% load('./Results/notax_new.mat');
+load('./Results/regulation_new.mat');
+aggyd = sum(yd(indzhatd:end).*zprob(indzhatd:end));
+aggyc = sum(yc(indzhatc:end).*zprob(indzhatc:end));
+aggy  = mud*aggyd + (1-mud)*aggyc;
+ksid_0 = -3.4114;
+ksid_1 = -0.3636;
+ez_nt = exp(ksid_0)*yd(indzhatd:end).^(1+ksid_1);
+agge_nt_notax = sum(ez_nt.*zprob(indzhatd:end));
+aggi_nt_notax = agge_nt_notax/aggyd;
+
+ez_dirty = exp(ksid_0)*yd(indzhatd:indztilded-1).^(1+ksid_1);
+ez_clean = exp(ksic_0)*yd(indztilded:end).^(1+ksic_1);
+agge_d = sum(ez_dirty.*zprob(indzhatd:indztilded-1));
+agge_c = sum(ez_clean.*zprob(indztilded:end));
+agge = agge_d + agge_c;
+aggi = agge/aggyd;
+
+totrede = agge/agge_nt_bench;
+prodrede = agge_nt_notax/agge_nt_bench;
+
+totredi = aggi/aggi_nt_bench;
+prodredi = aggi_nt_notax/aggi_nt_bench;
+disp('The Role of Technology')
+1-(1-prodredi)/(1-totredi)
+
+% Plot the tax function
+clear all;
+load('./Results/benchmark_new.mat');
+figure(1)
+plot(log(zgrid(indzhatc:end)),tauzc(indzhatc:end),...
[…]

### 2019-09-16 Quantitative/plot_figures.m

@@ -1,0 +1,179 @@
+% -------------------------------------------------------------------------
+%                      Program Description
+% -------------------------------------------------------------------------
+%   
+% Purpose:
+%     - Plot Figures 4 and 5.
+%     - Two Sectors Model
+%     - The Size Distribution of Firms and Industrial Water Pollution: A
+%       Quantitative Analysis of China.
+%  
+% Author:
+%     - Xin Tang @ International Monetary Fund
+% 
+% File Dependence:
+%     - benchmark_new.mat
+%     - notax_new.mat
+%     - regulation_new.mat
+%  
+% Record of Revisions:
+%         Date:                 Description of Changes
+%     ============        =================================
+%      04/19/2019                 Original Version
+% =========================================================================
+clc;
+clear all;
+
+% Benchmark Distributions
+load('./Results/benchmark_new.mat');
+% ================== Plot Figure 5 ======================
+% Bench vs No-tax: firm
+figure(1)
+bar([firmmodel,fsdata'],1,'group');
+colormap summer ;
+legend('Model','China','Location','NorthEast');
+set(gca,'XTick',1:5);
+set(gca,'XTickLabel',{'1-19','20-49','50-99','100-399','400+'});
+ylim([0 1]);
+xlabel('Firm Size Groups');
+ylabel('Fraction of Firms');
+title('Firm Size Distribution: Benchmark','FontWeight','Normal');
+saveas(gcf,'./Results/Figure5_Left.eps','epsc');
+
+% Bench vs No-tax: employment
+figure(2)
+bar([esmodel,esdata'],1,'group');
+colormap summer ;
+legend('Model','China','Location','NorthEast');
+set(gca,'XTick',1:5);
+set(gca,'XTickLabel',{'1-19','20-49','50-99','100-399','400+'});
+ylim([0 1]);
+xlabel('Firm Size Groups');
+ylabel('Fraction of Workers');
+title('Employment Distribution: Benchmark','FontWeight','Normal');
+saveas(gcf,'./Results/Figure5_Right.eps','epsc');
+
[…]

### 2019-09-16 Quantitative/twosectors.m

@@ -1,0 +1,215 @@
+% -------------------------------------------------------------------------
+%                      Program Description
+% -------------------------------------------------------------------------
+%   
+% Purpose:
+%     - Main program to solve the stationary equilibrium. 
+%     - Two Sectors Model
+%     - The Size Distribution of Firms and Industrial Water Pollution: A
+%       Quantitative Analysis of China.
+%  
+% Author:
+%     - Xin Tang @ International Monetary Fund
+% 
+% File Dependence:
+%     - fcn.m: evaluates all the allocations at a given wage and returns 
+%       the excess demand in the labor market.
+%  
+% Record of Revisions:
+%         Date:                 Description of Changes
+%     ============        =================================
+%      04/10/2019                 Original Version
+% =========================================================================
+clc;
+clear all;
+
+tic;
+% ================== Declare global variables =====================
+% Shared with fcn.m
+% ------ Model parameters -------
+% Technology and Preference
+global gamma alpha ke rss
+% Size Distribution
+global zgrid zprob mud
+% Regulation
+global xi tauzc tauzd
+
+% ------ Allocations -------
+global zhatc zhatd ztilded indzhatc indzhatd indztilded 
+global ldd kdd yd ldc kdc yc pi0d pi1d pid pic
+
+% =========================================================================
+%                      Data Dictionary
+% =========================================================================
+% Utility variables
+tol = 1e-6 ;
+% Technology and Preference
+beta   = 0.8750 ;           % Discount Factor
+gamma  = 0.93 ;             % Span-of-control
+alpha  = 0.50/gamma ;       % Capital share
+delta  = 0.10 ;             % Depreciation rate
+% Pollution intensity
+ksid_0 = -3.4144 ;          % Dirty technology: intercept
+ksid_1 = -0.3636 ;          % Dirty technology: slope
[…]

### 2019-09-16 Quantitative/twosectors_ces.m

@@ -1,0 +1,256 @@
+% -------------------------------------------------------------------------
+%                      Program Description
+% -------------------------------------------------------------------------
+%   
+% Purpose:
+%     - Main program to solve the stationary equilibrium. 
+%     - Two Sectors Model: CES aggregation
+%     - The Size Distribution of Firms and Industrial Water Pollution: A
+%       Quantitative Analysis of China.
+%  
+% Author:
+%     - Xin Tang @ International Monetary Fund
+% 
+% File Dependence:
+%     - fcn.m: evaluates all the allocations at a given wage and returns 
+%       the excess demand in the labor market.
+%  
+% Record of Revisions:
+%         Date:                 Description of Changes
+%     ============        =================================
+%      04/10/2019                 Original Version
+% =========================================================================
+clc;
+clear all;
+
+tic;
+% ================== Declare global variables =====================
+% Shared with fcn.m
+% ------ Model parameters -------
+% Technology and Preference
+global gamma alpha ke rss sigmaces varces
+% Size Distribution
+global zgrid zprob mud
+% Regulation
+global xi tauzc tauzd
+
+% ------ Allocations -------
+global zhatc zhatd ztilded indzhatc indzhatd indztilded 
+global ldd kdd yd ldc kdc yc pi0d pi1d pid pic
+% ---debug ---
+global aggld aggls aggyd aggyc outrhs
+
+% =========================================================================
+%                      Data Dictionary
+% =========================================================================
+% Utility variables
+tol = 1e-6 ;
+% Technology and Preference
+beta   = 0.8750 ;           % Discount Factor
+gamma  = 0.93 ;             % Span-of-control
+alpha  = 0.50/gamma ;       % Capital share
+delta  = 0.10 ;             % Depreciation rate
[…]

### 2019-09-17 Empirical/Empirical_AEJ.R
daily sync

@@ -140,11 +140,6 @@ lm_pool <- lm(log(cod_e) ~ log(product) + province
 summary(lm_pool)
 lm1 <- lm(log(intensity) ~ log(product) + province + industry_a + type_a, 
     data = POL5[(dm1_code_a == 4 | dm1_code_a == 5) & intensity > 0])
-# lm0 <- lm(log(cod_e) ~ log(product) + province 
-#           + industry_a + type_a, data = POL5[dm1_code_a == 1 & intensity > 0])
-# lm1 <- lm(log(cod_e) ~ log(product) + province + industry_a + type_a, 
-#           data = POL5[(dm1_code_a == 4 | dm1_code_a == 5) & intensity > 0])
-summary(lm_pool)
 summary(lm1)
 
 # Calculate ke to y ratio
@@ -328,7 +323,7 @@ distus <- distus/sum(distus)
 sel1 <- which(CH$nbarworkers > cutoff[n1])
 distchn[n1] <- sum(CH$nbarworkers[sel1])
 distchn <- distchn/sum(distchn)
-
+# Employment share used in quantitative part
 distchn
 
 # calculate firm size distribution of China
@@ -351,7 +346,7 @@ for (i in 2:n1){
 sel1 <- which(CH$nbarworkers > cutoff[n1])
 distchn[n1] <- length(sel1)
 distchn <- distchn/sum(distchn)
-
+# Firm size distribution used in quantitative part
 distchn
 
 # =========================================================================
@@ -436,6 +431,7 @@ phiupnew <- mean(CNEC$phil[sel])
 sel <- which(CNEC$phil < phidown)
 phidownnew <- mean(CNEC$phil[sel])
 phi_quant <- (log(phidownnew/phiupnew))/(log(zupnew/zdownnew))
+# phi1 in calibration
 phi_quant
 
 # Figure 3
@@ -516,12 +512,6 @@ for (i in 2:n1){
   phiplot[i-1] <- sum(CNEC_TRIM$logphiratio[sel]*CNEC_TRIM$product[sel])/sum(CNEC_TRIM$product[sel])
   phiplotraw[i-1] <- mean(CNEC_TRIM$logphiratio[sel])
 }
-
-# raw
-plot(zplotraw[1:n1],phiplotraw[1:n1],type = "l")
-
-# weighted
-plot(zplot[1:n1],phiplot[1:n1],type = "l")
 
[…]

### 2019-09-17 Empirical/cpsc_convert.R

@@ -22,9 +22,6 @@ rm(list = ls())
 library(foreign)
 library(data.table)
 
-# Set working directory
-setwd("D:/Computation/pollution_rep/Empirical")
-
 # -------------------------------------------------------------------------
 #                           Key Firms
 # -------------------------------------------------------------------------

### 2019-09-17 Quantitative/twosectors.m

@@ -177,8 +177,8 @@ firmmodel = (mud*firmmodeld+(1-mud)*firmmodelc)/totfirm;
 esmodel = (mud*esmodeld+(1-mud)*esmodelc)/tote;
 
 % newly computed
-fsdata = [0.4723 0.2812 0.1296 0.1025 0.0143];
-esdata = [0.0953 0.1776 0.1825 0.3861 0.1585];
+fsdata = [0.4698 0.2797 0.1290 0.1020 0.0195];
+esdata = [0.0864 0.1611 0.1655 0.3501 0.2369];
 
 string = ['gamma = ', num2str(gamma)];
 disp(string)

### 2019-09-17 Documentation/Replication_Instruction.tex
replication done

@@
 MATLAB is used to compute all the quantitative results.
-There is no particular scientific reason that we use one statistical software (\textsc{Stata}) for data cleaning and the other (\code{R}) for empirical analysis.
-We do this simply because it is easier to handle Chinese characters with \textsc{Stata} while \code{R} switches back and forth between different datasets swiftly.
+There is no particular scientific reason that we use one statistical software (\textsc{Stata}) for data cleaning and the other (\code{R}) for empirical analysis.\footnote{Due to limited backward compatibility of \textsc{Stata} and that the \code{foreign} package of \code{R} supports only \code{.dta} files saved by \textsc{Stata} up to Version 12, to run the code without any modification, the reader would need \textsc{Stata} 12.
+Readers with more recent version of the \textsc{Stata} would need to either modify in the \code{.do} file everywhere \code{.dta} files are read and written, or use alternative \code{R} package (for instance \code{readstata13}) to convert the data in \code{cpsc\_convert.R} and \code{cec\_convert.R}.
+Compatibility of our code is not tested under such environments though.
+None of our results would be affected though.} We do this simply because it is easier to handle Chinese characters with \textsc{Stata} while \code{R} switches back and forth between different datasets swiftly.
 Veterans of \textsc{Stata} (or \code{R}) should be able to replicate all the empirical results with just one software using our source code as reference with ease.
@@
 
+We try to group results according to their order of appearance in the paper.
+But this is not possible all the time.
+To ease the navigation, Table summarizes the results in the paper and in which file they are replicated.
+Acronym: \code{KEYFIRM\_R.RData (PK)}, \code{ALLFIRM\_R.RData (PA)}, \code{DLARGE\_R.RData (DL)} \code{CNEC\_avgp.RData (CA)}, \code{susb04.csv (US)}.
+\begin{table}[t]
+\footnotesize
+\centering
+\begin{threeparttable}
+\caption{Navigating the Main Text}
+\begin{tabular}{llll}
+    \hline \hline
+    Content                         & File Name                 & File Dependency   & Location in Code \\
+    \midrule
+    \textbf{Section \rom{1}.A} \\
+    \ \ \ Table 1                   & \code{Descriptive.R}      & \code{PK, PA} \\ 
+    \textbf{Section \rom{1}.B} \\
+    \ \ \ Figure 1                  & \code{Empirical\_AEJ.R}   & \code{PK}         & Section 1  \\
+    \ \ \ Table 2                   & \code{Empirical\_AEJ.R}   & \code{PK}         & Section 2  \\
+    \ \ \ Regression 1              & \code{Empirical\_AEJ.R}   & \code{PK}         & Section 1  \\
+    \ \ \ Regressions 2, 3          & \code{Empirical\_AEJ.R}   & \code{PK}         & Section 2 \\
+    \ \ \ Regression (!\#)          & \code{Empirical\_AEJ.R}   & \code{PK}         & Section 2 \\
+    \textbf{Section \rom{1}.C} \\
+    \ \ \ Figure 2                  & \code{Empirical\_AEJ.R}   & \code{CA, US}     & Section 3 \\
+    \ \ \ Accounting                & \code{Accounting.R}       & \code{PK, CA, US} \\
+    \textbf{Section \rom{2}.A} \\
+    \ \ \ Figure 3                  & \code{Empirical\_AEJ.R}   & \code{CA}         & Section 4 \\
+    \ \ \ Figure 4                  & Illustrative figure. \\
+    \textbf{Section \rom{3}} \\
+    \ \ \ Size Distribution         & \code{Empirical\_AEJ.R}   & \code{CA, US}     & Section 3 \\
+    \ \ \ $\varphi_1$               & \code{Empirical\_AEJ.R}   & \code{CA} & Section 4 \\
+    \ \ \ Clean share               & \code{Empirical\_AEJ.R}   & \code{PK} & Section 2 \\
+    \ \ \ $k_E/Y$ for clean firms   & \code{Empirical\_AEJ.R}   & \code{PK} & Section 2 \\
+    \ \ \ Figure 5                  & \code{twosectors.m}       & \multirow{2}{*}{\centering \code{*.mat}} \\ 
+                                    & \code{plot\_figures.m} \\
+    \textbf{Section \rom{4}.A} \\    
+    \ \ \ Table 4                   & \code{compute\_tables.m}  & \code{*.mat} \\ 
+    \ \ \ Table 5                   & \code{compute\_tables.m}  & \code{*.mat} \\ 
+    \ \ \ Figure 6                  & \code{plot\_figures.m}    & \code{*.mat} \\
+    \ \ \ Decomposition             & \code{misc.m}             & \code{*.mat} \\
+    \textbf{Section \rom{4}.B} \\
+    \ \ \ Table 6                   & \code{compute\_tables.m}  & \code{*.mat} \\ 
+    \ \ \ Decomposition             & \code{misc.m}             & \code{*.mat} \\    
+    \bottomrule
+\end{tabular}
+\label{tab:navi}
+\end{threeparttable}
+\end{table}
+
+\begin{table}[t]
+\footnotesize
+\centering
+\begin{threeparttable}
+\caption{Navigating the Appendix}
+\begin{tabular}{llll}
+    \hline \hline
+    Content                         & File Name                      & File Dependency   & Location in Code \\
+    \midrule
+    \textbf{Appendix A.1} \\
+    \ \ \ Table A.1                 & \code{Descriptive.R}           & \code{PK, PA} \\
+    \textbf{Appendix B} \\
+    \ \ \ Figure B.1                & \code{Empirical\_Appendix.R}   & \code{PK, PA, DL, CA}  & Section 1  \\
+    \textbf{Appendix C.1} \\    
+    \ \ \ Figure C.1                & \code{Empirical\_Appendix.R}   & \code{PK}  & Section 2  \\
+    \ \ \ Table C.1              & \code{Empirical\_Appendix.R}   & \code{PK}  & Section 2  \\
+    \ \ \ Figure C.2          & \code{Empirical\_Appendix.R}   & \code{PK}  & Section 2  \\
+    \ \ \ Regressions (!\#)          & \code{Empirical\_Appendix.R}   & \code{PK}  & Section 2  \\
+    \ \ \ 3-Regressions (!\#) & \code{Empirical\_AEJ.R}   & \code{PK}         & Section 2 \\
+    \textbf{Appendix D.1} \\
+    \ \ \ Figure D.1            & \code{Empirical\_Appendix.R}   & \code{CA}  & Section 4  \\
+    \ \ \ Figure D.2                & \code{misc.m}       \\
+    \textbf{Appendix D.2} \\
+    \ \ \ Table D.1                  & \code{Empirical\_Appendix.R}   & \code{PK}  & Section 3  \\
+    \ \ \ Regression (!\#)           & \code{Empirical\_Appendix.R}   & \code{PK}  & Section 3  \\
+    \ \ \ Fixed Cost Ratio & \code{Empirical\_Appendix.R}   & \code{PK}  & Section 3  \\
+    \textbf{Appendix E.1} \\
+    \ \ \ Figure E.1         & \code{Empirical\_Appendix.R}   & \code{CA, US}  & Section 5  \\
+    \textbf{Appendix F} \\    
+    \ \ \ Table F.1               & \code{Accounting.R}   & \code{PK, CA, US}  \\
+    \textbf{Appendix J} \\
+    \ \ \ Table J                  & \code{twosectors\_ces.m}       & \multirow{2}{*}{\centering \code{*.mat}} \\
+                                    & \code{compute\_tables\_ces.m} \\
+    \bottomrule
+\end{tabular}
+\label{tab:navi}
+\end{threeparttable}
+\end{table}
+
 \subsection{Data Cleaning}

### 2019-09-17 Empirical/Descriptive.R

@@ -1,0 +1,184 @@
+# Code File for calcluating descriptive statistics of CPSC
+# Xin Tang @ Stony Brook University
+# Last Updated: May 2014
+
+# Clear memory
+rm(list = ls())
+
+# Load in packages
+library(foreign)
+library(AER)
+library(data.table)
+
+########################### Key Firms ##################################
+load("./Data/KEYFIRM_R.RData")
+setkey(KEYFIRM,industry_a)
+KEYSUM_E <- KEYFIRM[, list(wastewater=sum(wastewater_e, na.rm = TRUE), cod=sum(cod_e, na.rm = TRUE), nh=sum(nh_e, na.rm = TRUE), pet=sum(pet_e, na.rm = TRUE), phe=sum(phe_e, na.rm = TRUE), bod=sum(bod_e, na.rm = TRUE), cyn=sum(cyn_e, na.rm = TRUE), as=sum(as_e, na.rm = TRUE), chr=sum(chr_e, na.rm = TRUE), chr6=sum(chr6_e, na.rm = TRUE)), by=list(industry_a)]
+
+# Calculate the percentage
+KEYPER_E <- KEYSUM_E[, list(wastewater = 100*wastewater/sum(wastewater), cod = 100*cod/sum(cod), nh = 100*nh/sum(nh), pet = 100*pet/sum(pet), phe = 100*phe/sum(phe), bod = 100*bod/sum(bod), cyn = 100*cyn/sum(cyn), as = 100*as/sum(as), chr = 100*chr/sum(chr), chr6 = 100*chr6/sum(chr6), industry_a = industry_a)]
+
+# Chemical Oxygen Demand
+# Table 1, Row 1
+s <- order(-KEYPER_E$cod)
+KEYPER_E <- KEYPER_E[s]
+head(KEYPER_E$cod,5)
+
+rm(list = ls())
+
+########################### All Firms ##################################
+
+load("./Data/ALLFIRM_R.RData")
+setkey(ALLFIRM,industry_a)
[…]

### 2019-09-17 Empirical/Empirical_AEJ.R

@@ -25,7 +25,7 @@
 # Clear memory
 rm(list = ls())
 
-# Load in packages
+# Load packages
 library(foreign)
 library(data.table)
 library(AER)
@@ -33,10 +33,11 @@ library(scales)
 library(grid)
 
 # =========================================================================
-#                   0. Aggregating Categorical Variables
+#                   1. Intensity and Firm Size
 # =========================================================================
 load("./Data/KEYFIRM_R.RData")
-# ------------ Aggregate ownership rights type ------------------
+# -------------------- Data Processing --------------------------
+# Aggregate ownership rights type
 # 0: missing, 1: State/collective, 3: private, 4: HMT, 5: foreign
 KEYFIRM$type_a <- 0
 # State and collective
@@ -60,8 +61,7 @@ sel <- which(KEYFIRM$type == 300 | KEYFIRM$type == 310
     | KEYFIRM$type == 320 | KEYFIRM$type == 330 | KEYFIRM$type == 340)
 KEYFIRM$type_a[sel] <- 5
 
-# ------------ Aggregate treatment technology type ------------------
-# For disposal equipment type
+# Aggregate treatment technology type
 KEYFIRM$dm1_code_a <- 0
 # Physical
 sel <- which(KEYFIRM$dm1_code >= 1000 & KEYFIRM$dm1_code < 2000)
@@ -78,31 +78,26 @@ KEYFIRM$dm1_code_a[sel] <- 4
 # Combination
 sel <- which(KEYFIRM$dm1_code >= 5000 & KEYFIRM$dm1_code < 6000)
 KEYFIRM$dm1_code_a[sel] <- 5
+# dm1_code_a == 0 means the equipment is unclassified
 
-# --------------- Declare dummies -----------------
 KEYFIRM$province <- factor(KEYFIRM$province)        # Province
 KEYFIRM$industry_a <- factor(KEYFIRM$industry_a)    # 2-digit industry
 KEYFIRM$Census_Type <- factor(KEYFIRM$Census_Type)  # key 1, regular 2
 KEYFIRM$dm1_code_a <- factor(KEYFIRM$dm1_code_a)    # treatment
 KEYFIRM$type_a <- factor(KEYFIRM$type_a)            # ownership rights
 
-# =========================================================================
[…]

### 2019-09-17 Empirical/Empirical_Appendix.R

@@ -31,17 +31,15 @@ library(AER)
 library(scales)
 library(grid)
 
-# Set working directory
-PathIn <- paste("C:/Users/zjuta/Dropbox/Daily Printing/PollutionPaper",
-      "AEJ_Submission/R&R/Empirical", sep="/")
-setwd(PathIn)
-
 # =====================================================================
-#                       Figures
+#         1. Firm Size Distribution in Different Datasets
 # =====================================================================
+# ====================== Figure B.1 ===============================
 # Distribution of output for NGSPS (Key/All), CNEC (All/Large)
 # Read the full sample of CNEC 
-load("./Data/CHprod_all.RData")
+load("./Data/CNEC_avgp.RData")
+CHNprod <- CNEC_avgp
+rm(CNEC_avgp)
 # Drop missing values
 sel <- which(CHNprod$product > 0)
 CHNprod <- CHNprod[sel]
@@ -51,7 +49,7 @@ deflator <- 96.30/93.50
 CHNprod$rproduct <- (CHNprod$product/10.0)*deflator
 tmpden <- density(log(CHNprod$rproduct),
       kernel = "gaussian", bw =0.50, na.rm = TRUE)
-pdf("./Figures/cnec_den_all_appen.pdf",height=5,width=5)
+pdf("./Figures/FigureB1_BotRight.pdf",height=5,width=5)
 plot(tmpden,xlab="Log Output",ylab="Density",main="CNEC All",
      xlim = c(0, 12), ylim=c(0,0.5), cex.lab = 1.25, 
      lwd = 2.0, col = 4)
@@ -68,7 +66,7 @@ deflator <- 96.30/93.50
 DLARGE$rproduct <- (DLARGE$product/10.0)*deflator
 tmpden <- density(log(DLARGE$rproduct),
       kernel = "gaussian", bw =0.50, na.rm = TRUE)
-pdf("./Figures/cnec_den_large_appen.pdf",height=5,width=5)
+pdf("./Figures/FigureB1_BotLeft.pdf",height=5,width=5)
 plot(tmpden,xlab="Log Output",ylab="Density",main="CNEC Large",
      xlim = c(0, 12), ylim=c(0,0.5), cex.lab = 1.25,
      lwd = 2.0, col = 4)
[…]

### 2019-09-17 Quantitative/compute_tables_ces.m

@@ -32,10 +32,10 @@ clear all;
 % disp('Print Results for the CES No Tax')
 % load('./Results/benchmark_ces3.mat');
 % disp('Print Results for the CES 3 Benchmark')
-% load('./Results/notax_ces3.mat');
-% disp('Print Results for the CES 3 No Tax')
-load('./Results/nodirty_ces3.mat');
-disp('Print Results for the CES 3 No Dirty Tax')
+% load('./Results/nodirty_ces3.mat');
+% disp('Print Results for the CES 3 No Dirty Tax')
+load('./Results/notax_ces3.mat');
+disp('Print Results for the CES 3 No Tax')
 
 % =========================================================================
 %                               Table 5

### 2019-09-17 Quantitative/twosectors_ces.m

@@ -54,15 +54,17 @@ ksid_0 = -3.4114 ;          % Dirty technology: intercept
 ksid_1 = -0.3636 ;          % Dirty technology: slope
 ksic_0 = -4.3747 ;          % Clean technology: intercept
 ksic_1 = -0.3288 ;          % Clean technology: slope
-% ke     = 1.50 ;             % Fixed cost of clean technology
-ke = 1.30 ; % ces = 3.0
 rss    = 1/beta-1+delta ;   % Equilibrium interest rate
-% sigmaces = 1.5;
-sigmaces = 3.0 ;
 
-% Benchmark case
-% varces = 0.31 ;   % ces = 1.5
-varces = 0.42 ;             % Share of polluting good in final production
+% CES = 1.5
+% sigmaces = 1.5;
+% ke     = 1.50 ;             % Fixed cost of clean technology
+% varces = 0.31 ;   % Share of polluting good in final production
+
+% CES = 3.0
+ke = 1.30 ;
+sigmaces = 3.0 ;
+varces = 0.42 ; % ces = 3.0 
 
 % Size Distribution
 mud   = 0.20 ;               % Share of entrepreneurs in polluting sector
@@ -108,9 +110,11 @@ zprob = [zprob*(1-zendw); zendw] ;
 % Now we transform z' to z
 zgrid = (zgrid/(phi0^(1/(1-gamma)))).^((1-gamma)/(1-gamma+phi1));
 
+% benchmark
 % tauzd = max(0,1-phi0*zgrid.^phi1);
 % tauzc = max(0,1-phi0*zgrid.^phi1);
 
+% no tax
 tauzd = zeros(zn,1);
 tauzc = zeros(zn,1);
 
@@ -211,8 +215,8 @@ end
 firmmodel = (mud*firmmodeld+(1-mud)*firmmodelc)/totfirm;
 esmodel = (mud*esmodeld+(1-mud)*esmodelc)/tote;
 
-fsdata = [0.4889 0.1948 0.1567 0.1365 0.0232];
-esdata = [0.0780 0.1021 0.1833 0.4218 0.2148];
+fsdata = [0.4698 0.2797 0.1290 0.1020 0.0195];
+esdata = [0.0864 0.1611 0.1655 0.3501 0.2369];
 
 string = ['gamma = ', num2str(gamma)];
 disp(string)

### 2019-09-18 Empirical/Accounting.R
daily sync

@@ -1,7 +1,21 @@
-# Code File for computing the accouting exercises
-# Data from: China Economic Census and Statistics of US Businesses
-# Xin Tang @ Stony Brook University
-# Last Updated: July 2014
+# --------------------------------------------------------------------------
+#                       Program Description
+# --------------------------------------------------------------------------
+#    
+# Purpose:
+#     - Compute the Accounting Exercise
+#     - Table F.1 of Appendix F
+#     - In-text number of Section I.C
+# 
+# Author:
+#     - Xin Tang @ Stony Brook, May 2014
+# 
+# Record of Revisions:
+#       Date:                 Description of Changes
+#    ============        =================================
+#     05/25/2014                 Original Version
+#     09/16/2019                Improved Annotation
+# ==========================================================================
 
 # Clear memory
 rm(list = ls())
@@ -15,56 +29,39 @@ library(scales)
 library(grid)
 
 # Load SUSB Data
-USall <- read.csv("./Data/susb04.csv",header = TRUE)  # Statistics of US Businesses
+USall <- read.csv("./Data/susb04.csv",header = TRUE)
 USall <- as.data.table(USall)
-USall <- USall[,list(NAICS, ENTRSIZE, FIRM, ESTB, EMPL, NAICSDSCR, ENTRSIZEDSCR)]
-USleft <- c(1,5,10,15,20,25,30,35,40,45,50,75,100,150,200,300,400,500,750,1000,1500,2500)
-USright <- c(4,9,14,19,24,29,34,39,44,49,74,99,149,199,299,399,499,749,999,1499,2499,10000)
+USall <- USall[,list(NAICS, ENTRSIZE, FIRM, 
+                     ESTB, EMPL, NAICSDSCR, ENTRSIZEDSCR)]
+USleft <- c(1,5,10,15,20,25,30,35,40,45,50,75,100,150,
+            200,300,400,500,750,1000,1500,2500)
+USright <- c(4,9,14,19,24,29,34,39,44,49,74,99,149,199,
+             299,399,499,749,999,1499,2499,10000)
 NUS <- length(USleft)
 
-# Load CNEC Data
-# load("DLARGE_R.RData")
-# DLARGE <- as.data.table(DLARGE)
-# load("DSMALL_R.RData")
-# DSMALL <- as.data.table(DSMALL)
[…]

### 2019-09-18 Empirical/Descriptive.R

@@ -1,6 +1,21 @@
-# Code File for calcluating descriptive statistics of CPSC
-# Xin Tang @ Stony Brook University
-# Last Updated: May 2014
+# --------------------------------------------------------------------------
+#                       Program Description
+# --------------------------------------------------------------------------
+#    
+# Purpose:
+#     - Compute summary statistics of the NGSPS
+#     - Table 1 of main text
+#     - Table A.1 of Appendix A.1
+# 
+# Author:
+#     - Xin Tang @ Stony Brook, May 2014
+# 
+# Record of Revisions:
+#       Date:                 Description of Changes
+#    ============        =================================
+#     05/25/2014                 Original Version
+#     09/16/2019                Improved Annotation
+# ==========================================================================
 
 # Clear memory
 rm(list = ls())
@@ -13,10 +28,20 @@ library(data.table)
 ########################### Key Firms ##################################
 load("./Data/KEYFIRM_R.RData")
 setkey(KEYFIRM,industry_a)
-KEYSUM_E <- KEYFIRM[, list(wastewater=sum(wastewater_e, na.rm = TRUE), cod=sum(cod_e, na.rm = TRUE), nh=sum(nh_e, na.rm = TRUE), pet=sum(pet_e, na.rm = TRUE), phe=sum(phe_e, na.rm = TRUE), bod=sum(bod_e, na.rm = TRUE), cyn=sum(cyn_e, na.rm = TRUE), as=sum(as_e, na.rm = TRUE), chr=sum(chr_e, na.rm = TRUE), chr6=sum(chr6_e, na.rm = TRUE)), by=list(industry_a)]
+KEYSUM_E <- KEYFIRM[, list(wastewater=sum(wastewater_e, na.rm = TRUE), 
+      cod=sum(cod_e, na.rm = TRUE), nh=sum(nh_e, na.rm = TRUE), 
[…]

### 2019-09-18 Empirical/Empirical_AEJ.R

@@ -1,17 +1,17 @@
-# -------------------------------------------------------------------------
+# --------------------------------------------------------------------------
 #                       Program Description
-# -------------------------------------------------------------------------
+# --------------------------------------------------------------------------
 #    
 # Purpose:
-#     - Produce all the empirical results in the main text.
-#     - 1. log(COD)~log(Sales) and Figure 1
-#     - 2. Inv~log(Sales)
-#     - 3. log(COD)~log(Sales) for Dirty and Clean
-#     - 4. Figure 2
-#     - 5. Distortions
+#     - Produce most of the empirical results in the main text.
+#     - 1. Table 2
+#     - 2. Figures: 1, 2, 3
+#     - 3. Regressions: 1, 2, 3, Section I.B
+#     - 4. Calibration Targets: Size distribution, phi1, clean share
+#             ke/Y
 #     - The Size Distribution of Firms and Industrial Water Pollution: A
 #       Quantitative Analysis of China
-#     - Prepared for AEJM Final Submission
+#     - Prepared for AEJ: Macro
 # 
 # Author:
 #     - Xin Tang @ International Monetary Fund
@@ -21,7 +21,7 @@
 #    ============        =================================
 #       04/06/2019                 Original Version
 #       09/16/2019                Improved Annotation
-# =========================================================================
+# ==========================================================================
 # Clear memory
 rm(list = ls())
 
@@ -32,9 +32,9 @@ library(AER)
 library(scales)
 library(grid)
 
-# =========================================================================
+# ==========================================================================
 #                   1. Intensity and Firm Size
-# =========================================================================
+# ==========================================================================
 load("./Data/KEYFIRM_R.RData")
 # -------------------- Data Processing --------------------------
 # Aggregate ownership rights type
@@ -80,23 +80,23 @@ sel <- which(KEYFIRM$dm1_code >= 5000 & KEYFIRM$dm1_code < 6000)
 KEYFIRM$dm1_code_a[sel] <- 5
 # dm1_code_a == 0 means the equipment is unclassified
 
-KEYFIRM$province <- factor(KEYFIRM$province)        # Province
-KEYFIRM$industry_a <- factor(KEYFIRM$industry_a)    # 2-digit industry
[…]

### 2019-09-18 Empirical/Empirical_Appendix.R

@@ -1,17 +1,16 @@
-# -------------------------------------------------------------------------
+# --------------------------------------------------------------------------
 #                       Program Description
-# -------------------------------------------------------------------------
+# --------------------------------------------------------------------------
 #    
 # Purpose:
-#     - Produce all the empirical results in the online appendix.
-#     - 1. log(COD)~log(Sales) and Figure 1
-#     - 2. Inv~log(Sales)
-#     - 3. log(COD)~log(Sales) for Dirty and Clean
-#     - 4. Figure 2
-#     - 5. Distortions
+#     - Produce most of the empirical results in the Online Appendices.
+#     - 1. Tables: C.1, D.1
+#     - 2. Figures: B.1, C.1, C.2, D.1, E.1
+#     - 3. Regressions: Appendix C.1, D.2
+#     - 4. Miscellaneous Info: Appendix D.2
 #     - The Size Distribution of Firms and Industrial Water Pollution: A
 #       Quantitative Analysis of China
-#     - Prepared for AEJM R&R
+#     - Prepared for AEJ: Macro
 # 
 # Author:
 #     - Xin Tang @ International Monetary Fund
@@ -20,7 +19,8 @@
 #          Date:                 Description of Changes
 #    ============        =================================
 #       04/06/2019                 Original Version
-# =========================================================================
+#       09/17/2019                Improved Annotation
+# ==========================================================================
 # Clear memory
 rm(list = ls())
 
@@ -31,10 +31,10 @@ library(AER)
 library(scales)
 library(grid)
 
-# =====================================================================
+# ==========================================================================
 #         1. Firm Size Distribution in Different Datasets
-# =====================================================================
-# ====================== Figure B.1 ===============================
+# ==========================================================================
+# ====================== Figure B.1 ========================================
 # Distribution of output for NGSPS (Key/All), CNEC (All/Large)
 # Read the full sample of CNEC 
 load("./Data/CNEC_avgp.RData")
[…]

### 2019-09-18 Empirical/cec_convert.R

@@ -1,6 +1,6 @@
-# -------------------------------------------------------------------------
+# --------------------------------------------------------------------------
 #                       Program Description
-# -------------------------------------------------------------------------
+# --------------------------------------------------------------------------
 #    
 # Purpose:
 #     - Convert CNEC from Stata format to R binary format
@@ -13,7 +13,7 @@
 #    ============        =================================
 #     05/25/2014                 Original Version
 #     09/16/2019                Improved Annotation
-# =========================================================================
+# ==========================================================================
 
 # Clear memory
 rm(list = ls())
@@ -166,7 +166,8 @@ DSMALL <- as.data.table(DSMALL)
 
 # Merge the two samples
 # Variables Needed:
-# industry, status, industry_a, type_a, founding_y, nbarworkers, product, totcapital, wage, nonwage, province
+# industry, status, industry_a, type_a, 
+#   founding_y, nbarworkers, product, totcapital, wage, nonwage, province
 ljunk <- DLARGE[,list(status,industry, industry_a, type_a, founding_y, 
       province, product, totcapital, nbarworkers, wage, nonwage)]
 sjunk <- DSMALL[,list(status,industry, industry_a, type_a, founding_y, 

### 2019-09-18 Empirical/cpsc_convert.R

@@ -1,6 +1,6 @@
-# -------------------------------------------------------------------------
+# --------------------------------------------------------------------------
 #                       Program Description
-# -------------------------------------------------------------------------
+# --------------------------------------------------------------------------
 #    
 # Purpose:
 #     - Convert NGSPS from Stata format to R binary format
@@ -13,7 +13,7 @@
 #    ============        =================================
 #     05/25/2014                 Original Version
 #     09/16/2019                Improved Annotation
-# =========================================================================
+# ==========================================================================
 
 # Clear memory
 rm(list = ls())
@@ -22,13 +22,10 @@ rm(list = ls())
 library(foreign)
 library(data.table)
 
-# -------------------------------------------------------------------------
+# --------------------------------------------------------------------------
 #                           Key Firms
-# -------------------------------------------------------------------------
-PathIn <- "./Data"
-File <- paste(PathIn, "keynum.dta", sep = "/")
-
-KEYFIRM <- read.dta(File)
+# --------------------------------------------------------------------------
+KEYFIRM <- read.dta("./Data/keynum.dta")
 # For faster processing, save data as data.table
 KEYFIRM <- data.table(KEYFIRM, key=c("firm_id"))
 
@@ -43,47 +40,71 @@ comment(KEYFIRM$quantity2) <- "Total QUANTITY of Output 2"
 comment(KEYFIRM$quantity3) <- "Total QUANTITY of Output 3"
 comment(KEYFIRM$quantity4) <- "Total QUANTITY of Output 4"
 comment(KEYFIRM$quantity5) <- "Total QUANTITY of Output 5"
[…]

### 2019-09-18 Quantitative/twosectors_ces.m

@@ -5,6 +5,7 @@
 % Purpose:
 %     - Main program to solve the stationary equilibrium. 
 %     - Two Sectors Model: CES aggregation
+%     - Table J in Appendix J
 %     - The Size Distribution of Firms and Industrial Water Pollution: A
 %       Quantitative Analysis of China.
 %  
@@ -12,7 +13,7 @@
 %     - Xin Tang @ International Monetary Fund
 % 
 % File Dependence:
-%     - fcn.m: evaluates all the allocations at a given wage and returns 
+%     - fcnces.m: evaluates all the allocations at a given wage and returns 
 %       the excess demand in the labor market.
 %  
 % Record of Revisions:

### 2019-09-18 Documentation/Replication_Instruction.tex
replication done

--- 2019-09-16 Documentation/Replication_Instruction.tex
@@
 % Functional Package
-\usepackage{enumerate}
+\usepackage{enumerate, enumitem}
 \usepackage{url}      % This package helps to typeset urls
@@
 This note explains step-by-step how to replicate all the results in \textit{The Size Distribution of Firms and Industrial Water Pollution: A Quantitative Analysis of China}.
-We begin with several house-keeping notes.
 We begin with some housekeeping stuff in Section \rom{1}.
-Section \rom{2} explains in detail how to replicate all the empirical results.
+Section \rom{2} explains in detail how to replicate all the results in the main text.
+Section \rom{3} shows how the results in the appendices can be replicated.
 
-\section{Housekeeping Stuff}
+\section{Housekeeping Information}
+
+\subsection{Overview}
 
@@
 All the empirical results are then produced using \code{R}.
-We use MATLAB to compute all the quantitative results.
-There is no particular scientific reason that we use one statistical software (\textsc{Stata}) for data cleaning and the other (\code{R}) for empirical analysis.
-It is easier to handle Chinese characters with \textsc{Stata} while \code{R} switches back and forth between different datasets swiftly.
+MATLAB is used to compute all the quantitative results.
+There is no particular scientific reason that we use one statistical software (\textsc{Stata}) for data cleaning and the other (\code{R}) for empirical analysis.\footnote{Due to limited backward compatibility of \textsc{Stata} and that the \code{foreign} package of \code{R} supports only \code{.dta} files saved by \textsc{Stata} up to Version 12, to run the code without any modification, the reader would need \textsc{Stata} 12.
+Readers with more recent version of the \textsc{Stata} would need to either modify in the \code{.do} file everywhere \code{.dta} files are read and written, or use alternative \code{R} package (for instance \code{readstata13}) to convert the data in \bcode{cpsc\_convert.R} and \bcode{cec\_convert.R}.
+Compatibility of our code is not tested under such environments.
+However, none of our results should be affected though.} We do this simply because it is easier to handle Chinese characters with \textsc{Stata} while \code{R} switches back and forth between different datasets swiftly.
 Veterans of \textsc{Stata} (or \code{R}) should be able to replicate all the empirical results with just one software using our source code as reference with ease.
@@
     \item
-    The NGSPS is a confidential dataset housed at the Ministry of Ecology and Environment.
-The data can only be accessed within the Ministry of Ecology and Environment as well as institutions under its direct supervision.
-Individual researchers requesting access should submit the application through the official portal for Information Access (\begin{CJK}{GBK}{kai}政府信息公开\end{CJK}) by the Ministry of Ecology and Environment at the following url: \url{http://www.mee.gov.cn/weihu/201706/t20170625_416641.shtml}.
+    The NGSPS is a confidential dataset housed at the Ministry of Ecology and Environment (MEE henceforth).
+The dataset is subject to regulation by \textit{The Law of the People's Republic of China on Guarding State Secrets} \begin{CJK}{GBK}{kai}（中华人民共和国保守国家秘密法）\end{CJK} because it contains sensitive information.
+Please refer to \textit{Regulation on Archiving the National General Survey of Pollution Sources Data (State Environmental Protection Administration [2007] No.187)} {\begin{CJK}{GBK}{kai}（污染源普查档案管理办法[环发[2007]187号]）\end{CJK}}.
+The data can only be accessed within the MEE as well as institutions under its direct supervision \begin{CJK}{GBK}{kai}（中华人民共和国生态环境部及其直属单位）\end{CJK}.
+Researchers affiliated with these institutions should submit application for access following the internal procedure of the MEE.
+This is how we access the data.
+
+    Individual researchers not affiliated with the MEE and institutions under its direct supervision needs to submit the application through the official portal for Information Access (\begin{CJK}{GBK}{kai} 政府信息公开\end{CJK}) by the MEE at the following url: \url{http://www.mee.gov.cn/weihu/201706/t20170625_416641.shtml}.
 The url is retrieved on September 15th, 2019 and may vary in the future.
-All applications are subject to official approval by the Ministry of Ecology and Environment.
+All applications are subject to official approval by the General Office of Ministry of Ecology and Environment \begin{CJK}{GBK}{kai}（中华人民共和国生态环境部办公厅）\end{CJK}.
+
+    For an official introduction to the NGSPS and declassified information at the aggregated level, interested readers could refer to the book \textit{Data Collection of the National General Survey of Pollution Sources} \begin{CJK}{GBK}{kai}（《污染源普查数据集》，中国环境科学出版社，2011）\end{CJK}, which is publicly available.
     \item
     The CNEC is also a confidential dataset belonging to National Bureau of Statistics of China.
-Many universities and institutions have legal copy of the dataset.
-Our copy was obtained from Wuhan University.
-One portal to request access to the data for individual researchers is through the Micro-data Lab of the National Bureau of Statistics (\begin{CJK}{GBK}{kai}国家统计局微观数据实验室，国家统计局-清华大学数据开发中心\end{CJK}).
-The url, retrieved on September 15th, 2019, is \url{http://microdata.stats.gov.cn/}; and again it may vary in the future.
-All applications are subject to official approval by the National Bureau of Statistics.
+Many universities and institutions have legal copy of the dataset though.
+Our copy was obtained from Fudan University.
     \item
@@
 
-In the replication files, we cannot provide micro-level data of the NGSPS, due to the Non-Disclosure Agreement with the Ministry of Ecology and Environment.
+In the replication files, we cannot provide micro-level data of the NGSPS and CNEC, due to non-disclosure agreements with the MEE and Fudan University.
 Therefore, we only post the source code that generates the results.
-The NGSPS is used to compute the following results:
+However, to facilitate replication by the readers who have access to the datasets, we post the log files when running the analysis on our computer.
+
+\subsection{File Structures}
+
+The readers will get a number of files for replicating the results.
+To ease digestion, we briefly introduce the structure of the folders and files.
+As typographical convention, we use \bcode{blue computer modern typewriter} to indicate \bcode{folders} and \bcode{files}.
+The current folder is referred to as \bcode{./}.
 \begin{itemize}
     \item
-    Tables: 1, 2, A.1, C.1, D.1 and F.1.
+    \bcode{./Empirical/}:
+    \begin{itemize}
         \item
-    Figures: 1, B.1 (upper panels), C.1, C.2, D.3.
+        \bcode{./Data/}: contains the raw and cleaned data.
         \item
-    Regressions: 1 and the un-numbered one in Section \rom{1}.B, 2, 3, the 6 un-numbered regression in Appendix C.1 and the un-numbered regression in Appendix D.2.
+        \bcode{./Results/}: contains all the figures and log-files.
         \item
-    Some miscellaneous information scattered across the paper.
+        \bcode{./cpsc\_raw.do}: does initial processing of the NGSPS.
+        \item
+        \bcode{./cec\_clean.do}: does initial processing of the CNEC.
+        \item
+        \bcode{./cpsc\_convert.R}: converts the NGSPS to binary format of \code{R}.
+        \item
+        \bcode{./cec\_convert.R}: converts the CNEC to binary format of \code{R}.
+        \item
+        \bcode{./Empirical\_AEJ.R}: produces most empirical results in the main text.
+        \item
+        \bcode{./Empirical\_Appendix.R} produces most empirical results in the appendices.
+        \item
+        \bcode{./Accounting.R}: executes the accounting exercise.
+        \item
+        \bcode{./Descriptive.R}: computes some summary statistics of the NGSPS.
+    \end{itemize}
+    \item
+    \bcode{./Quantitative/}
+    \begin{itemize}
+        \item
+        \bcode{./Results/}: contains all the results and figures.
+        \item
+        \bcode{./twosectors.m}: computes the equilibrium of the two-sector model with perfect substitution used in the main text and saves the results in \bcode{.mat} format.
+        \item
+        \bcode{./fcn2.m}: computes the excess demand at a given vector of price; called by \bcode{twosectors.m}.
+        \item
+        \bcode{./compute\_tables.m}: computes the raw data used to calculate Tables 4, 5 and 6 in the main text.
+        \item
+        \bcode{./plot\_figures.m}: plots Figures 4 and 5 in the main text.
+        \item
+        \bcode{./twosectors\_ces.m}: computes the equilibrium of the two-sector model with constant elasticity of substitution used in Appendix J and saves the results in \bcode{.mat} format.
+        \item
+        \bcode{./fcnces.m}: computes the excess demand at a given vector of price; called by \\
+        \bcode{twosectors\_ces.m}.
+        \item
+        \bcode{./compute\_tables\_ces.m}: computes the raw data used to calculate Tables J.1 in Appendix J.
+        \item
+        \bcode{./misc.m}: draws Figure D.2 and computes the decomposition in Sections \rom{4}.A and \rom{4}.B of the main text.
+    \end{itemize}
 \end{itemize}
 
-\section{Empirical Results}
+All the file reference in the source code is specified by relative position.
+Please set the working director of your software to the current folder that hosts the file.
+For example, if the package is saved locally at \bcode{C:/Users/AEJ/pollution\_rep/}, then to replicate the empirical results, the working directory of \textsc{Stata} and \code{R} should all be set to \bcode{C:/Users/AEJ/pollution\_rep/Empirical}, while the MATLAB working directory should be set to \bcode{C:/Users/AEJ/pollution\_rep/Quantitative} when replicating the quantitative results.
 
-The instructions are organized by logic instead of the order of appearance in the paper.
+\subsection{Data Cleaning}
 
-\section{Quantitative Results}
+The NGSPS comes by 5 \textsc{Stata} \code{.dta} files.
+\bcode{keynum.dta} contains information of the key sources, while \bcode{reg1.dta} to \bcode{reg4.dta} host information of the regular sources.
+There are 4 files for the regular sources because of the technical limitation back when we initially applied for the data.
+It is likely that the reader will get one file for the regular source at this moment.
+These files should be placed under \bcode{./Empirical/Data/}.
+Executing \bcode{cpsc\_raw.do} will combine the four \bcode{regx.dta} to \bcode{regall.dta} and label all the variables in \bcode{keynum.dta} and \bcode{regall.dta}.
+It also generates another file \bcode{allfirms.dta} where the two files are combined.
+All three files are saved under \bcode{./Empirical/Data/}.
+
+Our copy of the CNEC has two \textsc{Stata} \code{.dta} files.
+\bcode{cec2004\_large\_full.dta} holds those samples that overlap with the commonly used 2004 Annual Surveys of Industrial Firms, while \bcode{cec2004\_small.dta} contains small firms not surveyed in the annual ASIF.
+Again, they should be placed under \bcode{./Empirical/Data/}.
+The file \bcode{cec\_clean.do} labels all the variables.
+Upon completion, the original un-labeled files will be replaced by files of the same name.
+
+With these two steps completed, the reader needs to convert the data from \textsc{Stata} \code{.dta} to the internal binary \code{R} format \code{.RData}.
+File \bcode{cpsc\_convert.R} converts \bcode{keynum.dta} to \bcode{KEYFIRM\_R.RData}, \bcode{regall.dta} to \bcode{REGFIRM\_R.RData} and \bcode{allfirms.dta} to \bcode{ALLFIRM\_R.RData}.
+Similarly, \bcode{cec\_convert.R} converts \\ \bcode{cec2004\_small.dta} to \bcode{DSMALL\_R.RData}, \bcode{cec2004\_large\_full.dta} to \bcode{DLARGE\_R.RData}.
+It then extracts only the variables used in the paper and combines the two \code{.RData} files to one file \bcode{CNEC\_avgp.RData}.
+All the files are saved under \bcode{./Empirical/Data/} as before.
+
+The SUSB data are directly downloaded from the Census website as \bcode{susb04.csv}. We use the dataset in its original form.
+
+In what follows, we will only be using the files converted by \code{R}.
+A list of the essential files is provided below.
+All the files should be placed under \bcode{./Empirical/Data/}.
+For ease of reference, we use the two-letter acronyms in parenthesis when referring to the data files later.
+\begin{itemize}
+    \item
+    \bcode{KEYFIRM\_R.RData (PK)}: Key sources of the NGSPS.
+    \item
+    \bcode{ALLFIRM\_R.RData (PA)}: All sources of the NGSPS.
+    \item
+    \bcode{CNEC\_avgp.RData (CA)}: All samples in the CNEC.
+    \item
+    \bcode{DLARGE\_R.RData (DL)}: A subset of \code{CA} which overlaps with the 2004 Annual Surveys of Industrial Firm.    
+    \item
+    \bcode{susb04.csv (US)}: SUSB 2004.
+\end{itemize}
+
+\section{Replicate Results in the Main Text}
+
+We try to organize our source code by sections in the paper as much as we can.
+This is not always possible though (or creates unnecessary confusion).
+We do, however, break the code by sections within the file, where tasks that are reasonably connected logically are grouped together.
+The code is written such that each section is self-contained, so the readers do not have to run from the very beginning if she/he only wants to replicate a certain result.
+Table \ref{tab:navi_main} summarizes the correspondence between the results in the paper (tables, figures, regression results, in-text numbers, etc.) and the section of code files that computes them, as well as data dependency.
+To further assist the readers to visually navigate through the code, important sections are always indicated by a 76-character line of \code{=}.
+This is the longest line in all the source code, and should be those most visually noticeable amongst all.
+
+We now explain how to replicate the results in the main text step-by-step. The results are presented in the order of appearance in the main text.
+
+\begin{table}[t]
+\footnotesize
+\centering
+\begin{threeparttable}
+\caption{Navigating the Main Text}
+\begin{tabular}{llll}
+    \hline \hline
+    Content                         & File Name                  & File Dependency   & Location in Code \\
+    \midrule
+    \textbf{Section \rom{1}.A} \\
+    \ \ \ Table 1                   & \bcode{Descriptive.R}      & \code{PK, PA} \\
+    \textbf{Section \rom{1}.B} \\
+    \ \ \ Figure 1                  & \bcode{Empirical\_AEJ.R}   & \code{PK}         & Section 1  \\
+    \ \ \ Table 2                   & \bcode{Empirical\_AEJ.R}   & \code{PK}         & Section 2  \\
+    \ \ \ Regression 1              & \bcode{Empirical\_AEJ.R}   & \code{PK}         & Section 1  \\
+    \ \ \ Regressions 2, 3          & \bcode{Empirical\_AEJ.R}   & \code{PK}         & Section 2 \\
+    \ \ \ Regression (!\#)          & \bcode{Empirical\_AEJ.R}   & \code{PK}         & Section 2 \\
+    \textbf{Section \rom{1}.C} \\
+    \ \ \ Figure 2                  & \bcode{Empirical\_AEJ.R}   & \code{CA, US}     & Section 3 \\
+    \ \ \ Accounting                & \bcode{Accounting.R}       & \code{PK, CA, US} \\
+    \textbf{Section \rom{2}.A} \\
+    \ \ \ Figure 3                  & \bcode{Empirical\_AEJ.R}   & \code{CA}         & Section 4 \\
+    \textbf{Section \rom{3}} \\
+    \ \ \ Size Distribution         & \bcode{Empirical\_AEJ.R}   & \code{CA, US}     & Section 3 \\
+    \ \ \ $\varphi_1$               & \bcode{Empirical\_AEJ.R}   & \code{CA} & Section 4 \\
+    \ \ \ Clean share               & \bcode{Empirical\_AEJ.R}   & \code{PK} & Section 2 \\
+    \ \ \ $k_E/Y$ for clean firms   & \bcode{Empirical\_AEJ.R}   & \code{PK} & Section 2 \\
+    \ \ \ Figure 5                  & \bcode{twosectors.m}       & \multirow{2}{*}{\centering \code{*.mat}} \\
+                                    & \bcode{plot\_figures.m} \\
+    \textbf{Section \rom{4}.A} \\
+    \ \ \ Table 4                   & \bcode{compute\_tables.m}  & \code{*.mat} \\
+    \ \ \ Table 5                   & \bcode{compute\_tables.m}  & \code{*.mat} \\
+    \ \ \ Figure 6                  & \bcode{plot\_figures.m}    & \code{*.mat} \\
+    \ \ \ Decomposition             & \bcode{misc.m}             & \code{*.mat} \\
+    \textbf{Section \rom{4}.B} \\
+    \ \ \ Table 6                   & \bcode{compute\_tables.m}  & \code{*.mat} \\
+    \ \ \ Decomposition             & \bcode{misc.m}             & \code{*.mat} \\
+    \bottomrule
+\end{tabular}
+\label{tab:navi_main}
+\begin{tablenotes}
+     \footnotesize{
+     \item[$\dagger$]
+     Acronyms for datasets:
+     \begin{itemize}[leftmargin=*]
+        \item
+        \bcode{KEYFIRM\_R.RData (PK)}: Key sources of the NGSPS.
+        \item
+        \bcode{ALLFIRM\_R.RData (PA)}: All sources of the NGSPS.
+        \item
+        \bcode{CNEC\_avgp.RData (CA)}: All samples in the CNEC.
+        \item
+        \bcode{susb04.csv (US)}: SUSB 2004.
+     \end{itemize}
+     }
+     \item[$\ddag$]
+     All the \code{*.mat} files will be produced by \bcode{twosectors.m}.
+     \item[$\diamondsuit$]
+     Notation (!\#) stands for ``un-numbered.''
+\end{tablenotes}
+\end{threeparttable}
+\end{table}
+
+\begin{enumerate}
+    \item
+    Table 1 is produced by the first part of \bcode{Descriptive.R}. All the numbers are printed to the terminal. Row 1 comes first, with Rows 2 and 3 follow.
+    \item
+    Regression (1) and Figure 1 are generated by Section 1 of \bcode{Empirical\_AEJ.R}.
+The regression results are printed to the terminal.
+Figure 1 is saved at \bcode{./Empirical/Results/Figure1.pdf}.
+    \item
+    Regressions (2), (3), and the un-numbered one in Section \rom{1}.B part \textit{The Role of End-of-pipe Treatment Technologies}, as well as Table 2 are produced by Section 2 of \bcode{Empirical\_AEJ.R}.
+As one exception, Section 2 relies on Section 1 of \bcode{Empirical\_AEJ.R}.
+The information in Table 2 is printed to the terminal in the order of Columns 2, 1, 3 and 4.
+The numbers in Columns 1 and 2 are directly taken from the output.
+Columns 3 and 4 are calculated by normalizing the physical equipment level to 100.
+Regression results are then printed to the terminal.
+First is the unnumbered regression, with those of Regressions (2) and (3) follow in order.
+    \item
+    Figure 2 is produced by Section 3 of \bcode{Empirical\_AEJ.R}. The two panels are exported as \\ \bcode{./Empirical/Results/Figure2\_Left.pdf} and \bcode{Figure2\_Right.pdf}.
+    \item
+    The in-text number of the accounting exercise can be calculated from the results following executing \bcode{Accounting.R}.
+The 33\% reduction in the last paragraph of Section \rom{1}.C part \textit{An Accounting Exercise} can then be calculated as the weighted average of the variable \bcode{ppar} with Row 1 of Table 1 as the weight.
+Notice that the variable \bcode{ppar} is exactly Row 3 of Table F.1.
+Because according to Row 1 of Table 1, the five industries combined contribute to 77\% of total COD emission, assuming that industries emitting the other 23\% COD remain intact, the 25\% reduction in average intensity is simply calculated as $1 - (67\% \times 77\% + 100\% \times 23\%) \triangleq 25\%$.
+    \item
+    Figure 3 is produced by the second part of Section 4 of \bcode{Empirical\_AEJ.R}. The two panels are exported as \bcode{./Empirical/Results/Figure3\_Left.pdf} and \bcode{Figure3\_Right.pdf}.
+    \item
+    To compute the quantitative results, the reader would need to execute \bcode{twosectors.m} several times.
+There are four cases to be computed: the benchmark case, the no distortion case, the regulation case and the flat tax case.
+The reader need to manually set the parameters in \bcode{twosectors.m} for each cases, namely the distortions \code{tauzd, tauzc}, the regulation intensity \code{xi} and the file name at the very end.
+The code is set to compute and save the benchmark results initially.
+The code contains all the relevant statements.
+The readers only need to comment and un-comment the relevant sections, which should be very easy to locate by searching for the variable name.
+    \begin{enumerate}
+        \item
+        Execute \bcode{twosectors.m}.
+Some information would be printed to the terminal.
+Please refer to the log file \bcode{twosectors\_log.pdf} for details.
+The results are saved in \\ \bcode{./Quantitative/Results/benchmark\_new.mat}.
+        \item
+        Set \code{tauzd} and \code{tauzc} to zero, and the export destination to \bcode{./Results/notax\_new.mat}.
+The results will be saved in this file after execution.
+This case is labeled as Case (i) in the paper.
+        \item
+        Set \code{tauzd} and \code{tauzc} to the benchmark level, change \code{xi} to 0.355, and the export destination to \bcode{./Results/regulation\_new.mat}.
+The results will be saved in this file after execution.
+This case is labeled as Case (ii) in the paper.
+        \item
+        Set \code{tauzd} and \code{tauzc} to the flat tax level, reverse \code{xi} back to 0.23, and the export destination to \bcode{./Results/flattax\_new.mat}.
+The results will be saved in this file after execution.
+This case is labeled as Case (i') in the paper.
+    \end{enumerate}
+    \item
+    With all the \code{*.mat} files computed, execute \bcode{plot\_figures.m} will produce Figures 5 and 6.
+The corresponding files will be saved under \bcode{./Quantitative/Results/}.
+The list of files include \\ \bcode{Figure5\_Left.pdf}, \bcode{Figure5\_Right.pdf}, \bcode{Figure6\_TopLeft.pdf}, \bcode{Figure6\_TopRight.pdf}, \\ \bcode{Figure6\_BotLeft.pdf} and \bcode{Figure6\_BotRight.pdf}.
+    \item
+    Tables 4, 5 and 6 are calculated using the output of \bcode{compute\_tables.m}.
+Notice that Tables 4 and 6 are presented in relative changes and share a similar structure.
+By changing the input files at the beginning of \bcode{compute\_tables.m} (in particular the 4 \code{.mat} just computed), \bcode{compute\_tables.m} prints the raw data of the corresponding entries in the same structure as the tables in the paper.
+Table 5 can be directly taken from the output \code{Table 5} of executing \bcode{compute\_tables.m} with the input being the corresponding cases.
+Entries in Table 4 can be calculated from the \code{Table 4} of the benchmark case and Cases (i) and (ii), while that of Table 6 can be calculated from \code{Table 4} of the benchmark case and Case (i').
+The calculations of the relative changes are not automated, and the readers do have to do the calculations manually as we did.
+We apologize for the inconvenience.
+The in-text decomposition of the total reduction to the contribution of size distribution and technology adoption can be performed using \bcode{misc.m}.
+The readers need to change the second input file to either \bcode{notax\_new.mat} or \bcode{regulation\_new.mat}, depending on the cases to compute.
+The role of technology adoption is printed to the terminal, with the residual being that from the size distribution.
+    \item
+    Several calibration targets are computed from the data as well. This last bulletin explains where they are computed.
+    \begin{itemize}
+        \item
+        The share of firms using clean technology 57\% is calculated in Section 2 of \bcode{Empirical\_AEJ.R}. The variable \code{clean\_share} hosts the number.
+        \item
+        The average adoption cost of clean technology as a ratio of output for clean firms 2.5\% is calculated at the end of Section 2 of \bcode{Empirical\_AEJ.R}.
+The number is printed to the terminal directly.
+        \item
+        The value of $\phi_1$ is computed in the first part of Section 4 of \bcode{Empirical\_AEJ.R}. The variable \code{phi\_quant} carries the information.
+        \item
+        The firm size and employment distributions [the light (yellow) bars in Figure 5] are computed at the end of Section 3 of \bcode{Empirical\_AEJ.R}.
+The variable \code{distchn} is first used to save the employment distribution and then the firm size distribution.
+    \end{itemize}
+\end{enumerate}
+
+That concludes our instructions of replicating all the results in the main text.
+
+\section{Replicate Results in the Appendices}
+
+We now proceed with replicating the results in the appendices step-by-step.
+The results are presented in the order of appearance in the appendices.
+The correspondence between the results in the appendices and the section of code files is summarized in Table \ref{tab:navi_appendix}.
+
+\begin{table}[t]
+\footnotesize
+\centering
+\begin{threeparttable}
+\caption{Navigating the Appendix}
+\begin{tabular}{llll}
+    \hline \hline
+    Content                         & File Name                       & File Dependency          & Location in Code \\
+    \midrule
+    \textbf{Appendix A.1} \\
+    \ \ \ Table A.1                 & \bcode{Descriptive.R}           & \code{PK, PA} \\
+    \textbf{Appendix B} \\
+    \ \ \ Figure B.1                & \bcode{Empirical\_Appendix.R}   & \code{PK, PA, DL, CA}    & Section 1  \\
+    \textbf{Appendix C.1} \\
+    \ \ \ Figure C.1                & \bcode{Empirical\_Appendix.R}   & \code{PK}                & Section 2  \\
+    \ \ \ Table C.1                 & \bcode{Empirical\_Appendix.R}   & \code{PK}                & Section 2  \\
+    \ \ \ Figure C.2                & \bcode{Empirical\_Appendix.R}   & \code{PK}                & Section 2  \\
+    \ \ \ Regressions (!\#)         & \bcode{Empirical\_Appendix.R}   & \code{PK}                & Section 2  \\
+    \ \ \ 3-Regressions (!\#)       & \bcode{Empirical\_AEJ.R}        & \code{PK}                & Section 2 \\
+    \textbf{Appendix D.1} \\
+    \ \ \ Figure D.1                & \bcode{Empirical\_Appendix.R}   & \code{CA}                & Section 4  \\
+    \ \ \ Figure D.2                & \bcode{misc.m}       \\
+    \textbf{Appendix D.2} \\
+    \ \ \ Table D.1                 & \bcode{Empirical\_Appendix.R}   & \code{PK}                & Section 3  \\
+    \ \ \ Regression (!\#)          & \bcode{Empirical\_Appendix.R}   & \code{PK}                & Section 3  \\
+    \ \ \ Fixed Cost Ratio          & \bcode{Empirical\_Appendix.R}   & \code{PK}                & Section 3  \\
+    \textbf{Appendix E.1} \\
+    \ \ \ Figure E.1                & \bcode{Empirical\_Appendix.R}   & \code{CA, US}            & Section 5  \\
+    \textbf{Appendix F} \\
+    \ \ \ Table F.1                 & \bcode{Accounting.R}            & \code{PK, CA, US}  \\
+    \textbf{Appendix J} \\
+    \ \ \ Table J                   & \bcode{twosectors\_ces.m}       & \multirow{2}{*}{\centering \code{*.mat}} \\
+                                    & \bcode{compute\_tables\_ces.m} \\
+    \bottomrule
+\end{tabular}
+\label{tab:navi_appendix}
+\begin{tablenotes}
+     \footnotesize{
+     \item[$\dagger$]
+     Acronyms for datasets:
+     \begin{itemize}[leftmargin=*]
+        \item
+        \bcode{KEYFIRM\_R.RData (PK)}: Key sources of the NGSPS.
+        \item
+        \bcode{ALLFIRM\_R.RData (PA)}: All sources of the NGSPS.
+        \item
+        \bcode{CNEC\_avgp.RData (CA)}: All samples in the CNEC.
+        \item
+        \bcode{DLARGE\_R.RData (DL)}: A subset of \code{CA} which overlaps with the 2004 Annual Surveys of Industrial Firm.
+        \item
+        \bcode{susb04.csv (US)}: SUSB 2004.
+     \end{itemize}
+     }
+     \item[$\ddag$]
+     All the \code{*.mat} files will be produced by \bcode{twosectors\_ces.m}.
+     \item[$\diamondsuit$]
+     Notation (!\#) stands for ``un-numbered.''     
+\end{tablenotes}
+\end{threeparttable}
+\end{table}
+
+\begin{enumerate}
+    \item
+    Table A.1 is produced by the second part of \bcode{Descriptive.R}. All numbers are printed to the terminal.
+    \item
+    Figure B.1 is generated by Section 1 of \bcode{Empirical\_Appendix.R}.
+The four panels are saved respectively as \bcode{./Empirical/Results/FigureB1\_TopLeft.pdf}, \bcode{FigureB1\_TopRight.pdf}, \\ \bcode{FigureB1\_BotLeft.pdf} and \bcode{FigureB1\_BotRight.pdf}.
+    \item
+    Section 2 of \bcode{Empirical\_Appendix.R} produces the results in Appendix C.1.
+The beginning of that section first runs the regression of intensity to size by industry.
+The regression results are printed to the terminal, which are exactly the results reported in Table C.1.
+The five panels of Figure C.1 are then exported to \bcode{./Empirical/Results/} with the names \bcode{FigureC1\_TopLeft.pdf}, \\ \bcode{FigureC1\_TopRight.pdf}, \bcode{FigureC1\_MidLeft.pdf}, \bcode{FigureC1\_MidRight.pdf} and \\ \bcode{FigureC1\_BotLeft.pdf}.
+Notice that the bottom-right panel is simply Figure 1 in the main text.
+The code then repeats the exercise for the manufacturing sector as a whole.
+Results to the un-numbered regressions on Pages 7, 9 and 10 (the last one) are then printed to the terminal, with Figure C.2 exported to \bcode{./Empirical/Results/FigureC2.pdf}.
+
+    The three un-numbered regressions on the intensity-size relationship by the type of equipment are estimated in Section 2 of \bcode{Empirical\_AEJ.R}.
+    \item
+    The three panels of Figure D.1 are produced by Section 4 of \bcode{Empirical\_Appendix.R}.
+The figures are exported as \bcode{./Empirical/Results/FigureD1\_TopLeft.pdf}, \bcode{FigureD1\_TopRight} and \bcode{FigureD1\_Bot.pdf}.
+    \item
+    Figure D.2 is generated by the last part of \bcode{misc.m}.
+This requires the results from the benchmark case \bcode{./Quantitative/Results/benchmark\_new.mat}.
+The file hosts this figure would be \\ \bcode{./Quantitative/Results/FigureD2.eps}.
+    \item
+    Results in Appendix D.2 are computed by Section 3 of \bcode{Empirical\_Appendix.R}.
+Specifically, the 4 panels of Figures D.3 are first plotted and saved as \bcode{./Empirical/Results/FigureD3\_TopLeft.pdf}, \bcode{FigureD3\_TopRight.pdf}, \bcode{FigureD3\_BotLeft.pdf} and \bcode{FigureD3\_BotRight.pdf}.
+A series of results are then printed to the terminal: first are the in-text numbers of the mean of the ratio of adoption cost to output for firms with output in each quintile (22\%, 11\%, 6.7\%, 5.0\% and 2.7\%), second the coefficients of the un-numbered regression, with the results to Table D.3 come at last.
+    \item
+    Panels in Figure E.1 are produced by Section 5 of \bcode{Empirical\_Appendix.R}.
+The five panels are saved as \bcode{./Empirical/Results/FigureE1\_TopLeft.pdf}, \bcode{FigureE1\_TopRight.pdf}, \\ \bcode{FigureE1\_MidLeft.pdf}, \bcode{FigureE1\_MidRight.pdf} and \bcode{FigureE1\_BotLeft.pdf}.
+Similarly as for Figure C.1, the bottom-right panel is simply the left panel of Figure 2 in the main text.
+    \item
+    The accounting exercises in Appendix F are performed by \bcode{Accounting.R}. Variables \code{pmed}, \code{preg} and \code{ppar} are respectively for Rows 1, 2 and 3 in Table F.1.
+    \item
+    Finally, to reproduce Table J.1, one essentially follows the same logic as in the main text: namely execute \bcode{twosectors\_ces.m} many times with different parameter values, print the raw numbers for the corresponding variables and then manually compute the percentage changes in Table J.1.
+There are two cases in general, where CES $=$ 1.5 and CES $=$ 3.0.
+There are three parameters that are ``CES-specific:'' \code{sigmaces}, \code{ke} and \code{varces}.
+They are conveniently grouped together in the code, under the snippet \bcode{\% CES = 1.5} and  \bcode{\% CES = 3.0}.
+The readers would also need to modify \code{tauzd} and \code{tauzc} for different scenarios.
+As before, all the statements have been coded; and the readers only need to comment and un-comment the relevant snippets of the code.
+Likewise, the instruction to save the results at the end of the file also needs to be changed.
+One complication is that the readers need to set the initial guess for the market clearing prices.
+For each case, the initial guesses are conveniently stored in the code snippets at the beginning of Section \code{Solve the equilibrium wage}.
+The program is reasonable robust to different initial guesses.
+However, if the readers do not use the exact initial guess as we do, there may be very minor numerical difference for some of the variables.
+Similarly, if the reader uses other versions of MATLAB (we use 2016a) or Octave, such numerical errors would probably show up as well.
+    \begin{enumerate}
+        \item
+        By default, \bcode{twosectors\_ces.m} is tuned to produce the benchmark results with CES $=$ 1.5.
+Executing the file would print some information to the terminal, again please refer to the log file \bcode{twosectors\_ces\_log.pdf} for detail.
+The equilibrium results are then saved under \\ \bcode{./Quantitative/Results/benchmark\_ces.mat}.
+This case is called benchmark.
+        \item
+        Set both \code{tauzd} to zero and leave \code{tauzc} untouched, change the initial guesses and the export destination.
+The results for eliminating only the distortions in the polluting sector would be saved under \bcode{./Quantitative/Results/nodirty\_ces.mat}.
+This is case (ii) in Appendix J.
+        \item
+        Set both \code{tauzd} and \code{tauzc} to zero, change the initial guesses and the export destination.
+The results for the no distortion case would be saved under \\ \bcode{./Quantitative/Results/notax\_ces.mat}.
+This case is labeled as case (i) in Appendix J.
+    \end{enumerate}
+    \item
+    With all the \code{*.mat} files computed, as before, \bcode{compute\_tables\_ces.m} computes the raw data used in calculating entries in Table J.1.
+The results printed to the terminal can then be used to compute the percentage changes between equilibria in Table J.1.
+In particular, with the three cases at hand, the upper panel of Table J.1 can be reproduced.
+    \item
+    Repeat Steps 9 and 10 with the parameters set to CES $=$ 3.0 then produces the lower panel of Table J.1, which finally completes the replication of all the results in our paper.
+\end{enumerate}
+
+Right before our final submission, we did a final test run on all the programs.
+We saved all the log files of this particular run in \code{.pdf} format.
+The correspondence between the log files and the source code is as follows.
+The original log files are with the same name but postfix \code{.log}.
+For instance, executing the source code \bcode{cpsc\_raw.do} will generate a text log file \bcode{cpsc\_raw.log}, which we converted to \bcode{cpsc\_raw\_log.pdf} manually.
+\begin{itemize}
+    \item
+    \bcode{cpsc\_raw.do} $\longleftrightarrow$ \bcode{cpsc\_raw\_log.pdf}
+    \item
+    \bcode{cec\_clean.do} $\longleftrightarrow$ \bcode{cec\_clean\_log.pdf}
+    \item
+    \bcode{cpsc\_convert.R} $\longleftrightarrow$ \bcode{cpsc\_convert\_log.pdf}
+    \item
+    \bcode{cec\_convert.R} $\longleftrightarrow$ \bcode{cec\_convert\_log.pdf}    
+    \item
+    \bcode{Empirical\_AEJ.R} $\longleftrightarrow$ \bcode{empirical\_main\_log.pdf}        
+    \item
+    \bcode{Empirical\_Appendix.R} $\longleftrightarrow$ \bcode{empirical\_appendix\_log.pdf}            
+    \item
+    \bcode{Descriptive.R} $\longleftrightarrow$ \bcode{descriptive\_log.pdf}        
+    \item
+    \bcode{Accounting.R} $\longleftrightarrow$ \bcode{accounting\_log.pdf}            
+\end{itemize}
+The log files for the quantitative exercises are not automatically generated.
+We manually copied and pasted the intermediate results sent to the terminal to two text files: \bcode{quantitative\_main.log} for the perfect substitute case in the main text and \bcode{quantitative\_ces.log} for the constant elasticity of substitution case in the appendix.
+Then we convert the two files to \code{.pdf} format.
+\begin{itemize}
+    \item
+    \bcode{quantitative\_main\_log.pdf} $\longleftrightarrow$ \bcode{quantitative\_main.log}
+    \item
+    \bcode{quantitaitve\_ces\_log.pdf} $\longleftrightarrow$ \bcode{quantitative\_ces.log}
+\end{itemize}
 

### 2019-09-18 Empirical/Accounting.R

@@ -639,6 +639,10 @@ pch <- sum(par_int*distchn2)
 ppar_bever <- pus/pch
 
 # ======================= Table F.1 ========================================
-pmed <- cat(pmed_paper,pmed_agri,pmed_text,pmed_chem,pmed_bever)
-preg <- cat(preg_paper,preg_agri,preg_text,preg_chem,-1)
-ppar <- cat(ppar_paper,ppar_agri,ppar_text,ppar_chem,ppar_bever)
+pmed <- c(pmed_paper,pmed_agri,pmed_text,pmed_chem,pmed_bever)
+preg <- c(preg_paper,preg_agri,preg_text,preg_chem,-1)
+ppar <- c(ppar_paper,ppar_agri,ppar_text,ppar_chem,ppar_bever)
+
+pmed
+preg
+ppar

### 2019-09-18 Empirical/Descriptive.R

@@ -44,7 +44,7 @@ KEYPER_E <- KEYSUM_E[, list(wastewater = 100*wastewater/sum(wastewater),
       chr6 = 100*chr6/sum(chr6), industry_a = industry_a)]
 
 # Chemical Oxygen Demand
-# Table 1, Row 1
+# ==================== Table 1 Row 1 =======================================
 s <- order(-KEYPER_E$cod)
 KEYPER_E <- KEYPER_E[s]
 head(KEYPER_E$cod,5)
@@ -109,14 +109,14 @@ for (i in foo1){
   ALLCOMP_E$product[i+1] <- 100 - ALLCOMP_E$product[i]
 }
 
-# Table 1, Rows 2 and 3
+# ==================== Table 1 Rows 2 and 3 ================================
 ALLCOMP_E[which(ALLCOMP_E$industry_a == 22), list(cod, product)]
 ALLCOMP_E[which(ALLCOMP_E$industry_a == 13), list(cod, product)]
 ALLCOMP_E[which(ALLCOMP_E$industry_a == 17), list(cod, product)]
 ALLCOMP_E[which(ALLCOMP_E$industry_a == 26), list(cod, product)]
 ALLCOMP_E[which(ALLCOMP_E$industry_a == 15), list(cod, product)]
 
-# Table A.1, Row 1
+# ==================== Table A.1 Row 1 =====================================
 # number of firms
 sel <- which(ALLFIRM$Census_Type == 1)
 numkey <- length(sel)

### 2019-09-18 Empirical/Empirical_AEJ.R

@@ -129,6 +129,9 @@ dmtb <- table(PAPER$dm1_code_a)
 phyrate <- dmtb[2]/sum(dmtb[2:6])
 chemrate <- dmtb[3]/sum(dmtb[2:6])
 biorate <- sum(dmtb[5:6])/sum(dmtb[2:6])
+phyrate
+chemrate
+biorate
 
 # Table 2 Column 1
 PAPER <- within(PAPER,{
@@ -146,6 +149,9 @@ chemeffc <- 1 -
 bioeffc <- 1 - 
   mean(PAPER$cod_eg[(PAPER$dm1_code_a == 4 | PAPER$dm1_code_a == 5) 
                     & PAPER$cod_eg <= 1],na.rm=TRUE)
+phyeffc
+chemeffc
+bioeffc
 
 # Table 2 Column 3
 median(PAPER$dm1_inv[PAPER$dm1_code_a == 1 & PAPER$cod_eg <= 1],na.rm=TRUE)
@@ -467,6 +473,7 @@ phiupnew <- mean(philz_pol$phil[sel])
 sel <- which(philz_pol$phil < phidown)
 phidownnew <- mean(philz_pol$phil[sel])
 phi_quant <- (log(phidownnew/phiupnew))/(log(zupnew/zdownnew))
+# Five polluting industries only
 phi_quant
 
 # All Manufacturing Industries
@@ -487,6 +494,7 @@ phidownnew <- mean(CNEC$phil[sel])
 phi_quant <- (log(phidownnew/phiupnew))/(log(zupnew/zdownnew))
 
 # =================== phi1 in calibration ==================================
+# All manufacturing
 phi_quant
 
 # ----------------------------------------------------------------

### 2019-09-18 Empirical/Empirical_Appendix.R

@@ -49,7 +49,7 @@ deflator <- 96.30/93.50
 CHNprod$rproduct <- (CHNprod$product/10.0)*deflator
 tmpden <- density(log(CHNprod$rproduct),
       kernel = "gaussian", bw =0.50, na.rm = TRUE)
-pdf("./Figures/FigureB1_BotRight.pdf",height=5,width=5)
+pdf("./Results/FigureB1_BotRight.pdf",height=5,width=5)
 plot(tmpden,xlab="Log Output",ylab="Density",main="CNEC All",
      xlim = c(0, 12), ylim=c(0,0.5), cex.lab = 1.25, 
      lwd = 2.0, col = 4)
@@ -66,7 +66,7 @@ deflator <- 96.30/93.50
 DLARGE$rproduct <- (DLARGE$product/10.0)*deflator
 tmpden <- density(log(DLARGE$rproduct),
       kernel = "gaussian", bw =0.50, na.rm = TRUE)
-pdf("./Figures/FigureB1_BotLeft.pdf",height=5,width=5)
+pdf("./Results/FigureB1_BotLeft.pdf",height=5,width=5)
 plot(tmpden,xlab="Log Output",ylab="Density",main="CNEC Large",
      xlim = c(0, 12), ylim=c(0,0.5), cex.lab = 1.25,
      lwd = 2.0, col = 4)
@@ -79,7 +79,7 @@ sel <- which(KEYFIRM$product > 0)
 KEYFIRM <- KEYFIRM[sel]
 tmpden <- density(log(KEYFIRM$product),
       kernel = "gaussian", bw =0.50, na.rm = TRUE)
-pdf("./Figures/FigureB1_TopLeft.pdf",height=5,width=5)
+pdf("./Results/FigureB1_TopLeft.pdf",height=5,width=5)
 plot(tmpden,xlab="Log Output",ylab="Density",main="NGSPS Key",
      xlim = c(0, 12), ylim=c(0,0.5), cex.lab = 1.25, 
      lwd = 2.0, col = 4)
@@ -92,7 +92,7 @@ sel <- which(ALLFIRM$product > 0)
 ALLFIRM <- ALLFIRM[sel]
 tmpden <- density(log(ALLFIRM$product),
       kernel = "gaussian", bw =0.50, na.rm = TRUE)
-pdf("./Figures/FigureB1_TopRight.pdf",height=5,width=5)
[…]

### 2019-09-18 Empirical/cpsc_convert.R

@@ -116,9 +116,7 @@ rm(KEYFIRM)
 # -------------------------------------------------------------------------
 #                           Regular Firms
 # -------------------------------------------------------------------------
-File <- paste(PathIn, "regall.dta", sep = "/")
-
-REGFIRM <- read.dta(File)
+REGFIRM <- read.dta("./Data/regall.dta")
 # For faster processing, save data as data.table
 REGFIRM <- data.table(REGFIRM, key=c("firm_id"))
 
@@ -178,9 +176,7 @@ rm(REGFIRM)
 # -------------------------------------------------------------------------
 #                           All Firms
 # -------------------------------------------------------------------------
-File <- paste(PathIn, "allfirms.dta", sep = "/")
-
-ALLFIRM <- read.dta(File)
+ALLFIRM <- read.dta("./Data/allfirms.dta")
 # For faster processing, save data as data.table
 ALLFIRM <- data.table(ALLFIRM, key=c("firm_id"))
 

### 2019-09-18 Quantitative/plot_figures.m

@@ -148,7 +148,7 @@ xlabel('Firm Size Groups');
 ylabel('Fraction of Workers');
 title('Employment Distribution: Benchmark vs. No Tax',...
     'FontWeight','Normal');
-saveas(gcf,'./Results/Figure6_BottomLeft.eps','epsc');
+saveas(gcf,'./Results/Figure6_BotLeft.eps','epsc');
 
 % Bench vs Regulation: firm
 figure(5)

### 2019-09-18 Quantitative/twosectors.m

@@ -102,16 +102,16 @@ zprob = [zprob*(1-zendw); zendw] ;
 % Now we transform z' to z
 zgrid = (zgrid/(phi0^(1/(1-gamma)))).^((1-gamma)/(1-gamma+phi1));
 % benchmark tax
-% tauzd = max(0,1-phi0*zgrid.^phi1);
-% tauzc = max(0,1-phi0*zgrid.^phi1);
+tauzd = max(0,1-phi0*zgrid.^phi1);
+tauzc = max(0,1-phi0*zgrid.^phi1);
 
 % no tax
 % tauzd = zeros(zn,1);
 % tauzc = zeros(zn,1);
 
 % flat tax
-tauzd = 0.1755*ones(zn,1);
-tauzc = tauzd;
+% tauzd = 0.1755*ones(zn,1);
+% tauzc = tauzd;
 
 % =========================================================================
 %               Allocate memory to remaining variables
@@ -209,7 +209,7 @@ aggyc = sum(yc(indzhatc:end).*zprob(indzhatc:end));
 aggy  = mud*aggyd+(1-mud)*aggyc;
 disp(aggk/aggy)
 
-% save('./Results/benchmark_new.mat');
+save('./Results/benchmark_new.mat');
 % save('./Results/notax_new.mat');
 % save('./Results/regulation_new.mat');
-save('./Results/flattax_new.mat');
+% save('./Results/flattax_new.mat');

### 2019-09-18 Quantitative/twosectors_ces.m

@@ -58,14 +58,14 @@ ksic_1 = -0.3288 ;          % Clean technology: slope
 rss    = 1/beta-1+delta ;   % Equilibrium interest rate
 
 % CES = 1.5
-% sigmaces = 1.5;
-% ke     = 1.50 ;             % Fixed cost of clean technology
-% varces = 0.31 ;   % Share of polluting good in final production
+sigmaces = 1.5;
+ke     = 1.50 ;             % Fixed cost of clean technology
+varces = 0.31 ;   % Share of polluting good in final production
 
 % CES = 3.0
-ke = 1.30 ;
-sigmaces = 3.0 ;
-varces = 0.42 ; % ces = 3.0 
+% ke = 1.30 ;
+% sigmaces = 3.0 ;
+% varces = 0.42 ; % ces = 3.0 
 
 % Size Distribution
 mud   = 0.20 ;               % Share of entrepreneurs in polluting sector
@@ -112,12 +112,12 @@ zprob = [zprob*(1-zendw); zendw] ;
 zgrid = (zgrid/(phi0^(1/(1-gamma)))).^((1-gamma)/(1-gamma+phi1));
 
 % benchmark
-% tauzd = max(0,1-phi0*zgrid.^phi1);
-% tauzc = max(0,1-phi0*zgrid.^phi1);
+tauzd = max(0,1-phi0*zgrid.^phi1);
+tauzc = max(0,1-phi0*zgrid.^phi1);
 
 % no tax
-tauzd = zeros(zn,1);
-tauzc = zeros(zn,1);
+% tauzd = zeros(zn,1);
+% tauzc = zeros(zn,1);
 
 % =========================================================================
 %               Allocate memory to remaining variables
@@ -139,8 +139,8 @@ yc   = zeros(zn,1) ;     % output
 % =========================================================================
 % CES = 1.5
 % Benchmark
-% wage = 0.4847;
-% priced = 0.5617;
+wage = 0.4847;
+priced = 0.5617;
 
 % No polluting tax
 % wage = 0.5429 ;
@@ -160,8 +160,8 @@ yc   = zeros(zn,1) ;     % output
 % priced = 0.4618 ;
 
 % No tax
-wage = 0.6739;
-priced = 0.5286 ;
+% wage = 0.6739;
+% priced = 0.5286 ;
 
 pguess = [wage priced];
 
[…]

### 2019-09-19 Documentation/DataAppendix_AEJ_Final.tex
tex added

% Article Format: American Economic Review
% Xin Tang @ Stony Brook University
% Last Updated: August 2014
\documentclass[twoside,11pt,leqno]{article}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                    Text Layout                       %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Page Layout
\usepackage[hmargin={1.2in,1.2in},vmargin={1.5in,1.5in}]{geometry}
\topmargin -1cm        % read Lamport p.163
\oddsidemargin 0.04cm   % read Lamport p.163
\evensidemargin 0.04cm  % same as oddsidemargin but for left-hand pages
\textwidth 16.59cm
\textheight 21.94cm
\renewcommand\baselinestretch{1.15}
\parskip 0.25em
\parindent 1em
\linespread{1}

% Set header and footer
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhead{}
\fancyhead[LE,RO]{\thepage}
%\fancyhead[CE]{\textit{X. TANG}}
%\fancyhead[CO]{\textit{DATA APPENDIX: FIRM-SIZE AND POLLUTION}}
\cfoot{}
\renewcommand{\headrulewidth}{0pt}

% Font
\renewcommand{\rmdefault}{ptm}
\renewcommand{\sfdefault}{phv}
%\usepackage[lite]{mtpro2}
% use Palatinho-Roman as default font family
%\renewcommand{\rmdefault}{ppl}
\usepackage[scaled=0.88]{helvet}
\makeatletter   % Roman Numbers
\newcommand*{\rom}[1]{\expandafter\@slowromancap\romannumeral #1@}
\makeatother
\usepackage{CJK}

% Section Titles
\renewcommand\thesection{\textnormal{{\Alph{section}}}}
\renewcommand\thesubsection{\thesection.\textnormal{\arabic{subsection}}}
\usepackage{titlesec}
\titleformat*{\section}{ \center}
\titleformat*{\subsection}{\it \center}
\renewcommand{\refname}{\textnormal{REFERENCES}}

% Appendix
\usepackage[title]{appendix}
\renewcommand{\appendixname}{APPENDIX}

% Citations
\usepackage[authoryear,comma]{natbib}
\renewcommand{\bibfont}{\small}
\setlength{\bibsep}{0em}
\usepackage[%dvipdfmx,%
            bookmarks=true,%
            pdfstartview=FitH,%
            breaklinks=true,%
            colorlinks=true,%
            %allcolors=black,%
            citecolor=blue,
            linkcolor=red,
            pagebackref=true]{hyperref}

% Functional Package
\usepackage{enumerate}
\usepackage{url}      % This package helps to typeset urls

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                    Mathematics                       %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{amsmath,amssymb,amsfonts,amsthm,mathrsfs,upgreek}
% Operators
\newcommand{\E}{\mathbb{E}}
\newcommand{\e}{\mathrm{e}}
\DeclareMathOperator*{\argmax}{argmax}
\DeclareMathOperator*{\argmin}{argmin}
\DeclareMathOperator*{\plim}{plim}
\renewcommand{\vec}[1]{\ensuremath{\mathbf{#1}}}
\newcommand{\gvec}[1]{{\boldsymbol{#1}}}

% New Environments
\newtheorem{result}{Result}
\newtheorem{assumption}{Assumption}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newtheorem{definition}{Definition}[section]
\setlength{\unitlength}{1mm}

% Equations
\renewcommand{\theequation}{\arabic{equation}}
%\renewcommand{\thefigure}{\thesection\arabic{figure}}
%\renewcommand{\thefigure}{\arabic{figure}}
%\renewcommand{\thefigure}{A\arabic{figure}}
\renewcommand{\thetable}{\thesection\arabic{table}}
\numberwithin{equation}{section}
\numberwithin{figure}{section}
\numberwithin{table}{section}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                 Tables and Figures                   %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{threeparttable,booktabs,multirow,array} % This allows notes in tables
\usepackage{floatrow} % For Figure Notes
\floatsetup[table]{capposition=top}
\usepackage[font={sc,footnotesize}]{caption}
\DeclareCaptionLabelSeparator{aer}{---}
\captionsetup[table]{labelsep=aer}
\captionsetup[figure]{labelsep=period}
\usepackage{graphicx,pstricks,epstopdf}

\usepackage{tocloft}
\renewcommand{\contentsname}{\large\sc Contents}
\renewcommand{\cfttoctitlefont}{\hfill \normalfont}
\renewcommand{\cftaftertoctitle}{\hfill}
\renewcommand\cftsecfont{\normalfont}
\renewcommand\cftsecpagefont{\normalfont}
\renewcommand{\cftsecleader}{\normalfont\cftdotfill{\cftsecdotsep}}
\renewcommand\cftsecdotsep{5}%{\cftdot}
%\renewcommand\cftsubsecdotsep{\cftdot}

\title{For Online Publication \\ Appendix for ``The Size Distribution of Firms and Industrial Water Pollution: A Quantitative Analysis of China''}
\author{
  \normalsize{{Ji Qi}} \\
  \normalsize{{Chinese Academy of Environmental Science}}
  \and
  \normalsize{{Xin Tang}}\footnote{Corresponding Author: zjutangxin@gmail.com} \\
  \normalsize{{Wuhan University}} \\
  \normalsize{{International Monetary Fund}}
  \and
  \normalsize{{Xican Xi}} \\
  \normalsize{{Fudan University}}
}
\date{{\today}}

\begin{document}
\maketitle

{\hypersetup{linkcolor=black}
\setcounter{tocdepth}{1}
\tableofcontents}

\newpage
\section{National General Survey of Pollution Sources}

The most important data source that we draw upon in Section \rom{1}.B of the main text is the 2007 \textit{National General Survey of Pollution Sources} (henceforth NGSPS). In this section, we provide a detailed description of the dataset, which is based on the following documents:

%The most important data source that we draw upon in Section \rom{1}.B of the main text is the 2007 \textit{National General Survey of Pollution Sources} (henceforth, NGSPS). Since to the best of our knowledge, the data were not used before in economic studies, we provide a detailed description of the dataset in this section. The content in this section is combined from:
\begin{itemize}
    \item
    \textit{Census Program of the National General Survey of Pollution Sources} {\begin{CJK}{GBK}{kai}(第一次全国污染源普查方案)\end{CJK}};
    \item
    \textit{Regulation on National General Survey of Pollution Sources [Decree of the State Council of the People's Republic of China (No.508)]} {\begin{CJK}{GBK}{kai}(全国污染源普查条例[中华人民共和国国务院令第508号])\end{CJK}}.
    \item
    \textit{Technical Specifications Requirements of the First National General Survey of Pollution Sources} {\begin{CJK}{GBK}{kai}(第一次全国污染源普查技术规定)\end{CJK}}.
\end{itemize}

For an official introduction to the NGSPS and declassified information at the aggregated level, interested readers could refer to the book \textit{Data Collection of the National General Survey of Pollution Sources} (\begin{CJK}{GBK}{kai}《污染源普查数据集》, 中国环境科学出版社, 2011\end{CJK}), which is publicly available.

\subsection{General Introduction}

The NGSPS was a joint effort of multiple national ministries in China. The survey was organized directly by the State Council with data collection and quality control done by specially trained field staffs. According to the Regulation on National General Survey of Pollution Sources [Decree of the State Council of the People's Republic of China (No. 508)], faking data would lead to financial penalties or even lawsuits. The purpose of the NGSPS is to understand the number of pollution sources and their distribution in different industries and regions; to understand the generation, discharge and treatment of major pollutants; to establish records for key pollution sources; to build a pollution source information database and an environmental statistics platform; and to provide basis for formulating policies and plans for economic and social development and environmental protection. The term ``pollution source'' here refers to premises, facilities and equipment which discharge pollutants to environment in the process of production, living or other activities or have adverse impact on environment, as well as other sources that result in pollution.

The survey covers all of the pollution units from agricultural, industrial, domestic sources, and facilities for the centralized treatment of pollution within the borders of the People's Republic of China. In this study, we focus on the {industrial pollution sources}, which consist of businesses from 39 manufacturing industries according to the \textit{Industrial Classification for National Economic Activities} (GB/T4547-2002).

%The purpose of the NGSPS is to understand the number of pollution sources and their distribution in different industries and regions; to understand the generation, discharge and treatment of major pollutants; to establish records for key pollution sources; to build a pollution source information database and an environmental statistics platform; and to provide basis for formulating policies and plans for economic and social development and environmental protection.

%The term ``pollution source'' here refers to premises, facilities and equipment which discharge pollutants to environment in the process of production, living or other activities or have adverse impact on environment, as well as other sources that result in pollution.

%The NGSPS surveys all entities and self-employed households which have pollution sources within the borders of the People's Republic of China. The scope of the survey includes industrial pollution sources, agricultural pollution sources, domestic pollution sources, facilities for centralized treatment of pollution, and other facilities generating or discharging pollutants. In this paper, we focus on the industrial sources. The industrial sources include all production entities that belong to any of the 39 manufacturing industries according to the \textit{Industrial Classification for National Economic Activities} (GB/T4547-2002).

\textit{Key and Regular Sources.---}The firms in the industrial sources are divided into two groups, \textit{key sources} and \textit{regular sources}. A key source firm is required to file questionnaires that are more detailed than those filed by the regular source firms. A firm is categorized as a key source, if one of the following condition is satisfied:
\begin{enumerate}
    \item
    All production entities that discharge pollutants that contain heavy metal, hazardous waste, and radioactive substance.
    \item
    All production entities that belong to the 11 heavily polluting industries, which include: Paper and Paper Products; Food Processing; Raw Chemical Materials and Chemical Products; Textile; Ferrous Metal Smelting and Rolling Processing; Food Manufacturing; Production and Supply of Electric and Heating Power; Manufacturing of Leather, Fur, and Feather; Processing of Petroleum, Coking, and Nuclear Fuel; Manufacturing of Non-metallic Mineral Goods; Ferrous Metal Smelting and Rolling Processing.
    \item
    Firms with more than CNY 5 million in revenue that belong to the 16 key industries, which include: Beverage Manufacturing; Medicine Manufacturing; Chemical Fibers Manufacturing; Transportation Equipment Manufacturing; Coal Mining and Washing; Non-ferrous Metal Mining; Processing of Timber, and Manufacture of Wood, Bamboo, Rattan, Palm and Straw Products; Petroleum and Natural Gas Exploitation; General Purpose Machinery Manufacturing; Ferrous Metal Mining; Non-metal Mining; Apparel, Footwear and Caps Manufacturing; Water Production and Supply; Metal Products Manufacturing; Special Purpose Machinery Manufacturing; Communication Equipment, Computers and Other Electronic Equipment.
\end{enumerate}
A firm is categorized as a regular source firm, if none of the above conditions holds.

\textit{Variables.---}The survey collects information on the following variables for the industrial sources.
\begin{enumerate}
    \item
    Firm's basic registration information, geographic latitude and longitude, the receiving water body of firm's discharged wastewater, etc.
    \item
    The consumption of raw and intermediate inputs, including: water consumption, energy consumption (coal, petroleum, gas, electricity, etc.), the sulfur content of fuel, the consumption of hazardous intermediate input, etc.
    \item
    The quantity of each of the products produced by the firm.
    \item
    The type, size and number of the pollutants treatment equipment that the firms own.
    \item
    The generation, abatement, discharge and comprehensive utilization of various types of pollutants; and the operation of various kinds of pollution prevention and control facilities.
    \item
    The monitoring of pollutants emissions, including: the date and frequency of the monitoring; the type, quantity, and concentration of the pollutant.
\end{enumerate}

\textit{Pollutants.---}The pollutants included for the industrial sources are those that have general implications on pollution control. In particular, these pollutants are as follows.
\begin{enumerate}
    \item
    Wastewater: Chemical Oxygen Demand (COD), Ammonian, Petrochemicals, Volatile Phenols, Mercury, Cadmium, Plumbum, Arsenium, Hexavalent Chromium, Cyanidium. For Paper and Paper Product, Food Processing, Food Manufacturing and Beverage Manufacturing Industries, Five-days Biochemical Oxygen Demand ($\text{BOD}_5$) is added. For Urban Sewage Treatment Plants, Total Phosphorus, Total Nitrogen, and $\text{BOD}_5$ are added.
    \item
    Exhaust: Soot, Industrial Dust, Sulfur Dioxide. For Electrolytic Aluminium, Cement, Ceramic, Frosted Glass industries, Fluoride is added. For Vehicle Exhaust Census, Carbon Monoxide and Hydrocarbon are added.
    \item
    Industrial Solid Waste: Hazardous Waste (according to the \textit{National Catalogue of Hazardous Wastes}), Smelting Waste, Flying-Ash, Slag, Coal Refuse, Gangue, Radioactive Slag.
    \item
    Plaster discharged by Desulfurization Facilities, Sludge generated by waste water treatment facilities, and the remaining from burning hazardous waste.
    \item
    Radioactive pollution sources from the utilization of Concomitant Radioactive Mineral and from Civil Nuclear Power Generation.
\end{enumerate}

\begin{table}[t]
\footnotesize
\centering
\begin{threeparttable}
\caption{Percentage of Firms with Positive Emissions by Pollutants}
\begin{tabular}{lccccccccccc}
    \hline \hline
%    & Waste & COD & Petrochemicals & Ammonian & BOD & Cyanidum & Hex-Chromium & Phenol & Arsenium & Chromium \\
                    & Waste & COD  & Petro & $\text{NH}_4^+$ & BOD  & CN   & $\text{Cr}^{6+}$ & Phenol & As   & Cr      \\   %& Total\\
    \midrule
    Key Sources     & 76.2  & 73.2 & 31.4 & 25.2             & 17.5 & 4.90 & 4.86             & 2.42   & 2.27 & 2.01    \\ %& 106,067 \\
    Regular Sources & 35.2  & 28.3 & 7.91 & 6.49             & 2.56 & 0.13 & N/A              & 0.04   & 0.07 & N/A     \\  %& 814,937 \\
    \bottomrule
\end{tabular}
\begin{tablenotes}
     \footnotesize{\item[$\dagger$]
     Source: The 2007 National General Survey of Pollution Sources (NGSPS). The acronyms are respectively referring to: Wastewater, Chemical Oxygen Demand, Petrochemicals, Ammonian, Biochemical Oxygen Demand, Cyanidium, Hexavalent Chromium, Volatile Phenols, Arsenium and Chromium.}
\end{tablenotes}
\label{tab:nfirmPollutant}
\end{threeparttable}
\end{table}

Table \ref{tab:nfirmPollutant} lists the percentage of key and regular firms that report positive emissions of different water pollutants, respectively.

\subsection{Methods of Measurement}

There are three different methods to measure the level of pollutant emissions, which are \textit{Monitoring Method, Method of Emission Coefficient}, and \textit{Material Balance Method}. In this section, we describe these three methods and explain which method is used to determine the level of pollutant emissions in practice.

%There are three different methods that the data of pollutants emissions are collected, which in the priority of adoption when data from multiple sources are available, are \textit{Monitoring, Method of Emission Coefficient}, and \textit{Material Balance Method}. In this section, we describe these three methods and the principles that the three methods are used in practice.

\textit{Monitoring Method.---}In this method, the actual quantity and concentration of pollutants are measured, which are used to infer the annual quantity of the generation and discharge of different pollutants. In practice, there are three sources from which the monitored data are obtained, ranked by the priority of adoption when data from multiple sources are available: \textit{NGSPS monitoring, historical monitoring}, and \textit{online monitoring}. The NGSPS monitoring data are collected by the field staff in the survey year (2007). The historical monitoring data are measured and recorded in the past three years, with the latest data having the highest priority.\footnote{There are four different sources of historical data, ranked again by the priority of adoption when data from multiple sources are available: the historical data monitored by the local environmental authorities, the data monitored upon the completion of a newly constructed project, the data monitored by a third-party agency, and those self-reported by the firms.} The online monitoring data are those automatically uploaded by computerized and Internet-connected pollutants treatment equipment. Before the historical and online monitoring data are adopted, the field staff of the survey would ensure that the production condition and pollutant treatment technology have not undergone substantial changes.

%\textit{Monitoring.---}Monitored data are collected by measuring the actual quantity and pollutants concentration of wastewater and exhaust to infer the annual quantity of generation and discharge of certain types of pollutants. In addition, three sources from which the monitored data are obtained, which in the priority of adoption when data from multiple sources are available are: \textit{NGSPS monitoring, historical monitoring}, and \textit{online monitoring}. The NGSPS monitoring data are measured by the field staff of the survey in the survey year. The historical monitoring data are those measured and recorded in past three years, with the latest data having the highest priority.\footnote{There are in addition four different sources of historical data, in the order of adoption when more than one source are available, these four sources are: the historical data monitored by the local environmental authorities, the data monitored upon the completion of a newly constructed project, the data monitored by a third-party agency, and those that are self-reported by the firms.} The online monitoring data are those that are automatically uploaded by computerized and Internet-connected pollutants treatment equipment. Before historical and online monitoring data are accepted, the field staff of the survey examine to ensure that the production and pollutants treatment technology have not undergone substantial changes.

A pollution source needs to report monitored data, if any of the following four criteria is met:
\begin{enumerate}
    \item
    Nationally Monitored Key Pollution Sources {\begin{CJK}{GBK}{kai}(国控重点污染源)\end{CJK}}: all firms listed in the \textit{List of National Intensively Monitored Firms} {\begin{CJK}{GBK}{kai}(国家重点监控企业名单,环办函[2007]93号)\end{CJK}}.
    \item
    Facilities for Centralized Treatment of Pollution.
    \item
    Provincially Monitored Key Pollution Sources {\begin{CJK}{GBK}{kai}(省控重点污染源)\end{CJK}} that in sum account for 65\% of total provincial emission as is recorded in the \textit{2005 Environmental Statistic Yearbook}. That is for each of the major pollutants, starting from the most polluting firm and adding up the quantity of emission, all firms until the summation reaches the 65\% of the total provincial emission are recorded. The collection of the list of firms for all major pollutants provides the firms in this category.
    \item
    Newly established projects since 2005 whose pollutants discharge is higher than the least polluting firms in the Provincial Monitored Key Pollution Sources.
\end{enumerate}
These firms are later referred to as the \textit{monitored firms} in this document.

Starting from 2007Q1, for all Nationally Monitored Key Pollution Sources, Centralized Treatment Facilities, and Provincially Monitored Key Pollution Sources, waste water sources have to be monitored at least once per quarter, and exhaust sources have to be monitored at least once per six months.

The actual monitoring practice is subject to the following guidelines:
\begin{enumerate}
    \item
    The monitoring of Mercury, Cadmium, Hexavalent Chromium, Plumbum, and Arsenium must be conducted at the discharging outlets of individual factory workshops, with each outlets monitored separately.
    \item
    Other water-based pollutants are monitored at the outlets of the factory.
    \item
    The flow rates of wastewater and exhaust are monitored at the same time with the monitoring of pollutants discharges.
    \item
    The monitoring of pollution sources are conducted at the representative production and polluting time periods.
    \item
    All monitoring technical standards of wastewater pollutants follow \textit{The Technical Specifications Requirements for the Monitoring of Surface Water and Wastewater} {\begin{CJK}{GBK}{kai}(地表水和污水监测技术规范, HJ/T91-2002)\end{CJK}} and \textit{The Technical Specifications Requirements for the Monitoring of Wastewater Pollutants Emission} {\begin{CJK}{GBK}{kai}(水污染物排放总量监测技术规范, HJ/T92-2002)\end{CJK}}.
    \item
    For unstable wastewater sources, the samples are collected using the \textit{Water Ratio Automatic Sampler}.
    \item
    All monitoring technical standards of exhaust pollutants follow \textit{The Determination of Particulates and Sampling Methods of Gaseous Pollutants from Exhaust Gas of Stationary Sources} {\begin{CJK}{GBK}{kai}(固定污染源排气中颗粒物测定和气态污染物采样方法, GB/T16157-1996)\end{CJK}}.
\end{enumerate}

\textit{Method of Emission Coefficient.---}In this method, the generation and discharge of pollutants are calculated according to the \textit{Handbook of Emission Coefficient}, edited by the \textit{Chinese Academy of Sciences}. The benchmark coefficients are estimated based on firm's production technology, production scale, etc. The actual coefficients used are modified from the benchmark coefficients according to firm's use of intermediate inputs, its managerial practice, and the pollution treatment equipment installed. The actual pollutants generation and discharge are then calculated according to the actual production scale of the firm in year 2007.

\textit{Material Balance Method.---}In this method, the quantities of the materials entering and leaving a system are measured, and therefore the material flows which might have been unknown or difficult to measure without this method are identified. The exact rule of conservation used in the analysis of the system depends on the specific context, but all rules revolve around mass conservation, i.e., that matter cannot disappear or be created spontaneously. In parctice, a firm's usage of intermediate inputs, energy consumption, water consumption, and production technology are used simultaneously, in order that the calculated pollutants generation and discharge can realistically reflect the actual production and emission of the firm in reality.
%\textit{Material Balance Method.---}The Material Balance Method is an application of conservation of mass to the analysis of physical systems. By accounting for material entering and leaving a system, mass flows can be identified which might have been unknown, or difficult to measure without this technique. The exact conservation law used in the analysis of the system depends on the context of the problem, but all revolve around mass conservation, i.e. that matter cannot disappear or be created spontaneously. When applied, a firm's usage of intermediate inputs, energy consumption, water consumption, and production technology are considered simultaneously, in order that the calculated pollutants generation and discharge can realistically reflect the actual production and emission of the firm in reality.

\textit{Which Method Will Be Used in Practice?---}To determine which measurement method will be used in practice, the survey follows the following guidelines.
\begin{enumerate}
    \item
    The data of the Key Pollution Sources are obtained mainly through monitoring and the method of emission coefficient, while the material balance method is only used when the other two methods are not feasible. More specifically, the data of all firms that are identified as the monitored firms are obtained by monitoring. The data of other firms in the key sources are obtained by the method of emission coefficient.
    \item
    The data of the Regular Pollution Sources are obtained mainly through the method of emission coefficient, while the material balance method is used only when the method of emission coefficient is not feasible.
    \item
    Before being accepted, the monitored data are compared with those calculated from the method of emission coefficient. If the discrepancy is less than 20\% of the monitored value, the monitored value is used. If the discrepancy is larger than 20\%, the production technology and operating status of the firm are examined. If the operating status is in compliance with that specified in the technical regulations of the monitoring practice (for example, the firm has to reach at least 75\% of its production capacity when the emission is monitored), the monitored data are accepted. Otherwise, the emissions are calculated using the method of emission coefficient.
\end{enumerate}

\section{A Comparison of Firm Size Distributions for Different Samples}
%\section{Firm Size Distribution in NGSPS and CNEC}
This section compares the firm size distributions for different samples of firms in China. In Figure \ref{fig:distcomp}, we present the kernel densities of firm size estimated using different samples in NGSPS and CNEC.
%This section shows the firm size distributions by output value from the NGSPS and CNEC. In Figure \ref{fig:distcomp}, we present kernel densities of firm sizes estimated using different samples in NGSPS and CNEC.
\begin{figure}[t]
    \begin{center}
    \includegraphics[width=0.4\textwidth]{./Figures/ngsps_den_key_appen.pdf}%
    \includegraphics[width=0.4\textwidth]{./Figures/ngsps_den_all_appen.pdf} \\
    \includegraphics[width=0.4\textwidth]{./Figures/cnec_den_large_appen.pdf}
    \includegraphics[width=0.4\textwidth]{./Figures/cnec_den_all_appen.pdf}
    \caption{Firm Size Distributions in Various Data Sources}
    \floatfoot{Sources: NGSPS and CNEC. In all panels, the horizontal axes are in log-scale.}
    \label{fig:distcomp}
    \end{center}
\end{figure}
On the upper panels, we plot the firm size distributions for the samples that consist of the key source firms (the left panel) and all firms (the right panel) in the NGSPS, respectively. On the lower panels, we plot the firm size distributions for the \textit{Annual Surveys of Industrial Firms (ASIF)} sample (the left panel), which consists of all state-owned firms and private firms with sales above CNY 5 million, and the sample of all firms (the right panel) in the CNEC. There are two findings that we would like to emphasize:
%On the upper panel, we plot the firm size distribution by using only the key firms (left) and all firms (right) in NGSPS. On the lower panel, we plot those estimated using only the Annual Survey samples (left) and all firms (right). There are two findings that we would like to emphasize.
\begin{enumerate}
    \item
    Although the key source firms are on average larger than the firms in the full sample, they include both small and large firms, and the empirical density of the log output of the key source firms resembles a bell shape. This suggests that the key source firms are reflecting the characteristics of the firms over the entire range of firm size. As a result, no systematic bias will be introduced when we use the key source firms to empirically analyze the relationship between pollution intensity/treatment technology adoption and firm size in Section \rom{1}.B.
    %The key firms in NGSPS cover broadly firms of all sizes. Though the key firms tend to be larger than an average firm from the full sample, a fair amount of small firms are included. Hence both densities from the key and all firms resemble those bell-shaped densities from the normal distribution family. This also suggests that the estimated elasticity in Regression (1) of the main text is likely to reflect the correlation between production and emissions over the entire range of firm size.
    \item
    There are marked differences in the firm size distributions between the ASIF sample and CNEC full sample, with the ASIF sample missing most of the small firms. As a result, while the ASIF data are widely used in the studies of Chinese economy, we use the CNEC full sample in our paper, because both the small and large firms play a critical role in our empirical and quantitative analysis.
   % The densities estimated from the CNEC full sample and the Annual Surveys of Industrial Production subsample show marked difference, with the Annual Survey samples missing all the small firms, of which a lot are covered by the NGSPS key firms.
\end{enumerate}

In sum, the two take away points from the four panels in Figure \ref{fig:distcomp} are that the key firms in NGSPS are representative of both large and small firms, and that we have to use the CNEC full sample in companion with the NSGPS for our purpose.

\section{Additional Results on Firm Size and Pollution Intensity}

In this section, we present additional results on the statistical relationship between firm size and pollution intensity. In Section C.1, we show the scatter-plots and regression results for individual polluting industries and and for the whole manufacturing sector as well. In addition, we show that the negative relationship between firm size and pollution intensity holds conditional on whether the firms are using physical, chemical or biological technologies. We also show that our results in Section \rom{1}.B remain robust if we cluster the standard errors by provinces. In Section C.2, we explain our estimates on coefficients of the dummy variables, and compare our findings with those from the existing literature.

%In this section, we present more results about the statistical relationship between firm size and pollution intensity. In Section 1, we show the scatterplots and regression results obtained using individual industries. We further show that the estimates pooling all polluting industries together remain significant if we cluster the standard errors by provinces. In Section 2, we explain the estimates of the dummy variables and compare our study with some of the existing literature.

\subsection{Additional Scatter-plots and Regression Results}

For each industry among the top five polluting industries, we regress the following equation:
\begin{equation*}
    \log (\text{COD}_i) = \beta_0 + \beta_1 \log (\text{Output}_i) + \vec{X_p} \gvec{\upgamma}_1 + \vec{X_o} \gvec{\upgamma}_2+ \varepsilon_i,
\end{equation*}
where $\vec{X_p}$ is the provincial dummy, and $\vec{X_o}$ is the ownership dummy. The estimation results are summarized in Table \ref{tab:olsresults}, with the corresponding scatterplots plotted in Figure \ref{fig:codscatters}. We also include the scatterplot with the top five industries pooled together in Figure \ref{fig:codscatters} for completeness.
\begin{figure}[htbp]
    \begin{center}
    \includegraphics[width=0.40\textwidth]{./Figures/paper_ez.pdf}%
    \includegraphics[width=0.40\textwidth]{./Figures/agri_ez.pdf} \\
    \includegraphics[width=0.40\textwidth]{./Figures/text_ez.pdf}
    \includegraphics[width=0.40\textwidth]{./Figures/chem_ez.pdf} \\
    \includegraphics[width=0.40\textwidth]{./Figures/bever_ez.pdf}
    \includegraphics[width=0.40\textwidth]{./Figures/pooled_intensity_size.pdf} \\
 % \includegraphics[width=0.40\textwidth]{./Figures/all_manufacturing_cod_size.png} \\
%    \vspace{-1em}
    \caption{Firm Size and Pollution Intensity}
    \floatfoot{Source: NGSPS. Line: Least square fit.}
    \label{fig:codscatters}
    \end{center}
\end{figure}
\begin{table}[t]
\footnotesize
\centering
\begin{threeparttable}
\caption{Firm Size and Pollution Intensity by Industry}
\begin{tabular}{cccccc}
    \hline \hline
    Parameters & Paper           & Food    & Textiles         & Chemical Materials  & Beverages   \\
    \midrule
    $\beta_0$  & $-$4.14         & $-$2.15              & $-$3.71          & $-$7.12             & $-$2.86     \\
               & (0.56)          & (0.26)               & (0.57)           & (0.33)              & (0.39)      \\
    $\beta_1$  & 0.74            & 0.39                 & 0.70             & 0.88                & 0.59        \\
               & (0.02)          & (0.01)               & (0.01)           & (0.01)              & (0.02)      \\
    $R^2$      & 0.38            & 0.31                 & 0.38             & 0.40                & 0.34        \\
    \midrule
    $N$        & 5,632           & 6,893                & 6,284            & 8,686               & 1,558       \\
    \bottomrule
\end{tabular}
\begin{tablenotes}
     \footnotesize{
     \item[$\dagger$]
     Data Source: NGSPS.}
\end{tablenotes}
\label{tab:olsresults}
\end{threeparttable}
\end{table}
All the estimates are significant both statistically and economically with reasonable levels of $R^2$. %perhaps with Chemistry Materials being the one possible abnormal exception. Further investigation into the data reveals that the reason that we do not observe a negative correlation in the Chemistry Materials industry as evident as in the other industries is because there are many sub-industry level heterogeneities pooled at the two-digit level. To show that this is indeed the case, we repeat the exercise for the top polluting four-digit industry within the Chemistry Material industry, {Nitrogen Fertilizer} (C2621) which ranks the sixth among all four-digit industries by pollution. The results are shown in the bottom right panel of Figure \ref{fig:codscatters} where the negative correlation is clear, and the last column of Table \ref{tab:olsresults}. Put differently, the ``circle'' we see in the Chemistry case is in fact a combination of several ``ellipses,'' each with a downward sloping transverse diameter. This is confirmed by including four-digit industry dummy in the regression for Chemistry industry specified below. After introducing four-digit industry dummies, the magnitude estimates for $\beta_1$ decreases to 0.79 and the $R^2$ increases to 0.26. Both numbers are now of comparable magnitudes with the other industries.

If we apply Regression (1) in Section \rom{1}.B of the main text to the whole manufacturing sector, we get the following results
\begin{equation*}
    \log (\text{COD}_i) = \underset{(0.84)}{-11.05} + \underset{(0.00)}{0.63} \times \log (\text{Output}_i) + \vec{X} \gvec{\upgamma} + \varepsilon_i,
\end{equation*}
which implies a negative correlation between firm size and pollution intensity. However, as we mentioned in Section \rom{1}.A of the main text, because industrial water pollutants are typically concentrated in a handful of industries, when we apply the above analysis to the whole manufacturing sector, we lose about two thirds of the manufacturing firms, as firms in many industries did not report positive COD emissions. Figure \ref{fig:codscatter} visualizes the above regression by plotting residuals after controlling for all the covariates. Likewise, if we apply the linear regression of technology adoption in Section \rom{1}.B of the main text to the whole manufacturing sector, we get the following results:
\begin{equation*}
    y_i = \underset{(0.11)}{-0.16} + \underset{(0.000)}{0.04} \times \log (\text{Output}_i) + \vec{X} \gvec{\upgamma} + \varepsilon_i,
        %\label{eq:poolols}
\end{equation*}
implying again a similar positive correlation between firm size and the adoption of clean technology.
\begin{figure}[t]
    \begin{center}
    \includegraphics[width=0.40\textwidth]{./Figures/all_manufacturing_cod_size.png}%
    \caption{Firm Size and Pollution Intensity: All Manufacturing Industries}
    \floatfoot{Source: NGSPS. Line: Least square fit. Residuals after controlling for the covariates are plotted.}
    \label{fig:codscatter}
    \end{center}
\end{figure}

For the size-intensity relationship conditional on treatment equipment, in Section \rom{1}.B of the main text, we group physical and chemical equipments together with an extra dummy variable for chemical equipment. Here, we show that the relationship holds as well when we estimate the relation for each type of equipment separately:
\begin{align*}
%\label{eq:poolols_physical}
    \text{Physical:}   \quad \log (\text{COD}_i) &= \underset{(0.40)}{-3.50} + \underset{(0.01)}{0.58} \times \log (\text{Output}_i) + \vec{X_s} \gvec{\upgamma}_1 + \vec{X_p} \gvec{\upgamma}_2 + \vec{X_o} \gvec{\upgamma}_3 + \varepsilon_i, \\
%\label{eq:poolols_chemical}
    \text{Chemical:}   \quad \log (\text{COD}_i) &= \underset{(0.49)}{-4.59} + \underset{(0.01)}{0.77} \times \log (\text{Output}_i) + \vec{X_s} \gvec{\upgamma}_1 + \vec{X_p} \gvec{\upgamma}_2 + \vec{X_o} \gvec{\upgamma}_3 + \varepsilon_i, \\
%\label{eq:poolols_biological}
    \text{Biological:} \quad \log (\text{COD}_i) &= \underset{(0.20)}{-4.37} + \underset{(0.01)}{0.67} \times \log (\text{Output}_i) + \vec{X_s} \gvec{\upgamma}_1 + \vec{X_p} \gvec{\upgamma}_2 + \vec{X_o} \gvec{\upgamma}_3 +\varepsilon_i.
\end{align*}

For Regression (1) in the main text, we have also clustered standard errors at the provincial level. We confirm that the statistical significance does not change:
\begin{equation*}
    \log (\text{COD}_i) = \underset{(0.30)}{-3.75} + \underset{(0.03)}{0.63} \times \log (\text{Output}_i) + \vec{X_s} \gvec{\upgamma}_1 + \vec{X_p} \gvec{\upgamma}_2 + \vec{X_o} \gvec{\upgamma}_3 + \varepsilon_i.
\end{equation*}

\subsection{Locations and Ownership Rights}

The pollution intensity also exhibits rich provincial level variations. We take the regression results on the paper industry for example. Using Beijing as the benchmark, of all the remaining 29 provinces and municipalities, only the coefficient of Shanghai is negative and statistically insignificant. For the remainders, all estimates are positive and highly significant.\footnote{One province, Hebei is significant at 10\% level. Four others are significant at 1\% level while all others are significant at 0.1\% level. We notice here that Hebei, a province that is commonly considered as heavily affected by industrial pollution, is in fact an outlier, since the paper manufacturing is not its pillar industry.} The five most polluting provinces are Ningxia, Inner Mongolia, Gansu, Shaanxi and Xinjiang, for which the rankings of their provincial GDP in 2007 are respectively 29, 16, 27, 19 and 25 out of 31 provincial administrative regions (not including Hong Kong and Macau). Geographically, these are also inland provinces. In fact, despite that the majority of the paper manufacturers are located in Zhejiang and Guangdong (ranked 1st and 4th by GDP), the pollution level is lower comparing to those inland less developed regions. These patterns are highly robust across various specifications of our regressions. The general message we get from these dummy coefficients are the following. First, Beijing and Shanghai, arguably the political and economic center of China, exert pollution control standard far more stringent than the rest provinces. Second, inland and less developed provinces in general have worse control over and are more prone to the industrial pollution problem. These two patterns are broadly consistent with the environmental Kuznetz curve and the results from previous literature. However, unlike \citet{Jiangetal:2014}, ownership rights do not seem to have significant effects. If anything, the Foreign and Hong Kong, Macau and Taiwan based firms have only weakly better pollution controls. However, the statistical significance of the estimates never exceed 10\% across all our regressions. We conjecture that this could be because \citet{Jiangetal:2014}'s estimates are derived using a different sample of firms (in total 1,931 firms), while our data cover more firms.

\section{Evidence Supporting the Modeling Assumptions}

In this section, we provide some evidence in support of our modeling assumptions. In Section \ref{sec:distortions}, we present the evidence that motivates us to model the distortions as progressive taxes on output. In Section \ref{sec:appen_techspec}, we justify our choice of modeling the adoption of advanced treatment technology as fixed costs. We also describe additional distributional features of the treatment technology, including the {processing efficiency, designed processing capacity}, and {installation costs}, using the Paper and Paper Product industry as an example. Section \ref{sec:china_regulation} contains a brief summary of the environmental regulations in China.

%In this section, we provide the evidence in support of some of our modeling assumptions. In Section \ref{sec:distortions}, we show the evidence that motivates us to model the distortions as a generic tax on output. In Section \ref{sec:appen_techspec}, we justify our choice of modeling the adoption of advanced treatment technology as a one-time fixed costs. We also describe some additional distributional feature of the treatment technology, including the {processing efficiency, designed processing capacity}, and {installation costs}, for the Paper and Paper Product industry. Section \ref{sec:china_regulation} contains a brief summary of the environmental regulations in China.

\subsection{Firm-level Distortions}
\label{sec:distortions}

Recent studies of the Chinese economy have described large distortions at both the sector and the firm levels, which negatively affect aggregate productivity and output considerably.\footnote{See \citet{HsiehKlenow:2009}, \citet{Songetal:2011}, \citet{Brandtetal:2013}, and \citet{TombeZhu:2015}, among others.} Following the seminal approach developed by \citet{HsiehKlenow:2009,HsiehKlenow:2014}, we model and estimate firm-level distortions by using variations in the average products of capital and labor across firms.\footnote{Though average factor product dispersion could arise due to dynamic capital adjustment [\citet{Askeretal:2014}], for the case of China, \citet{DavidVenkateswaran:2017} show that dynamic adjustment costs only accounts for about 10\% of the variation in average factor product in the data. Naturally, we also cannot separate out variations in average factor product caused by firm-specific characteristics, for instance firm-specific markup or capital share. However, we argue that it would require empirical implausible variations of such parameters to generate the patterns of the data we observe.} %An important feature of Cobb-Douglas production function is that the ratio of average factor products to marginal factor products is constant. Therefore, the average factor products also provide information on marginal factor products.\footnote{In particular, using the notations later in this section, we can verify that $\partial y/\partial k = \alpha \gamma z^{1-\gamma} k^{\alpha \gamma - 1} l^{(1-\alpha)\gamma} = \alpha \gamma (y/k)$. Similarly, we can show that $\partial y/\partial k = (1-\alpha) \gamma (y/l)$.}
More specifically, if we let $\tau_{z_i}, \tau_{k_i}$, and $\tau_{l_i}$ be the wedges that firm $i$ faces in the product, capital, and labor markets, respectively, the profit maximization problem of firm $i$ is:
\begin{equation*}
    \pi_i = \max_{k_i,l_i} \left\{ (1-\tau_{z_i}) z_i^{1-\gamma} (k_i^{\alpha} l_i^{1-\alpha})^{\gamma} - (1+\tau_{k_i})Rk_i - (1+\tau_{l_i})W l_i \right\}.
\end{equation*}
By using the first-order conditions, the firm level average product of capital $\phi_{k_i}$, labor $\phi_{l_i}$, and the capital/labor ratio $\kappa_i$ can be expressed as
\begin{align}
    \label{eq:phik}
    \phi_{k_i} &= \frac{y_i}{k_i} = \frac{(1+\tau_{k_i})R}{\alpha \gamma (1-\tau_{z_i})}, \\
    \label{eq:phil}
    \phi_{l_i} &= \frac{y_i}{l_i} = \frac{(1+\tau_{l_i})W}{(1-\alpha) \gamma (1-\tau_{z_i})}, \\
    \label{eq:kappa}
    \kappa_i &= \frac{k_i}{l_i} = \frac{\alpha}{1-\alpha} \cdot \frac{(1+\tau_{l_i})W}{(1+\tau_{k_i})R}.
\end{align}
The above equations show that in the absence of any distortions ($\tau_{z_i} = \tau_{k_i} = \tau_{l_i} = $ 0), $\phi_{k_i}, \phi_{l_i}$, and $\kappa_i$ should be equalized across firms. Equations (\ref{eq:phik}) and (\ref{eq:phil}) state that firms that face higher distortions in the capital (labor) and/or product markets demonstrate a higher average product of capital (labor). In addition, according to Equation (\ref{eq:kappa}), the capital/labor ratio increases with the {relative} size of labor to the capital market wedge. By using firm-level data on total production value, the book value of capital stock, and labor compensation from the CNEC, we calculate $z_i, \phi_{k_i}, \phi_{l_i}$, and $\kappa_i$ for each firm in our sample. Here we set $\gamma = $ 0.93, which is the calibrated value of returns to scale in the main text. Figure \ref{fig:phiklkappa} shows on log scales the scatterplots of $\phi_{k_i}, \phi_{l_i}$, and $\kappa_i$ against firm-level productivity $z_i$ for the Paper and Paper Products industry. We plot the Paper industry for demonstration purpose, qualitatively the results for all five polluting industries as well as all manufacturing industries combined are the same.
\begin{figure}[t]
    \begin{center}
%    \includegraphics[width=0.4\textwidth]{./Figures/arpk.pdf}%
%    \includegraphics[width=0.4\textwidth]{./Figures/arpl.pdf} \\
%    \includegraphics[width=0.4\textwidth]{./Figures/klratio.pdf}
    \includegraphics[width=0.4\textwidth]{./Figures/FigureD1_TopLeft.pdf}%
    \includegraphics[width=0.4\textwidth]{./Figures/FigureD1_TopRight.pdf} \\
    \includegraphics[width=0.4\textwidth]{./Figures/FigureD1_Bot.pdf}
    \caption{Average Factor Products and Capital-Labor Ratio across Firm TFP Levels}
    \floatfoot{Source: CNEC. All panels are plot in log scale. Lines are least square fit. Data of the Paper and Paper Product Industry are plotted.}
    \label{fig:phiklkappa}
    \end{center}
\end{figure}

Two patterns emerge from Figure \ref{fig:phiklkappa}. First, from the two upper panels, we see that both $\phi_{k_i}$ and $\phi_{l_i}$ are positively correlated with $z_i$, which suggests that more productive firms have higher average products of both capital and labor. Expressed in wedges, this means that both $(1+\tau_{k_i})/(1-\tau_{z_i})$ and $(1+\tau_{l_i})/(1-\tau_{z_i})$ are higher for more productive firms.
%If we assume $\gamma = 0.85$ following \citet{AtkesonKehoe:2005}, then the elasticities of $\phi_k$ and $\phi_l$ to $z$ are both about 0.25, meaning that doubling firm productivity is associated with a 25\% increase in the average revenue product of factor inputs.\footnote{Generally speaking, the estimated elasticity depends on the value of $\gamma$, since $z$ is calculated for a given $\gamma$. However, because we are using a \citet{Lucas:1978b} model, while \citet{HsiehKlenow:2014} and \citet{BentoRestuccia:2016} both use the \citet{Melitz:2003} model, our results are not directly comparable with theirs. Yet broadly speaking, our estimates are quantitatively consistent with theirs. By using comprehensive micro data, \citet{HsiehKlenow:2014} find that the elasticity is 0.1 for the United States and between 0.5 and 0.6 for India and Mexico. By using data from the World Bank's Enterprise Surveys, \citet{BentoRestuccia:2016} find that the elasticities range from 0.22 to 0.74, averaging 0.52.}
This could be because more productive firms are subject to higher factor or product market distortions or both. %Statistically, if we regress the average factor products to $\log z$, then for the five polluting industries, we get
%\begin{align*}
%    \text{Labor:}   \quad \log \phi_{l,i} &= \underset{(0.01)}{1.10} + \underset{(0.00)}{0.04} \times \log z_i + \vec{X_s} \gvec{\upgamma}_1 + \vec{X_p} \gvec{\upgamma}_2 + \vec{X_o} \gvec{\upgamma}_3 + \varepsilon_i, \quad R^2 = 0.49, \\
%    \text{Capital:} \quad \log \phi_{k,i} &= \underset{(0.01)}{-1.03} + \underset{(0.00)}{0.06} \times \log z_i + \vec{X_s} \gvec{\upgamma}_1 + \vec{X_p} \gvec{\upgamma}_2 + \vec{X_o} \gvec{\upgamma}_3 + \varepsilon_i, \quad R^2 = 0.62.
%\end{align*}
Second, from the lower panel, we see that the capital/labor ratio is at best weakly negatively correlated with $z$. %Statistically, a similar regression specification as above yields
%\begin{equation*}
%    \log \kappa_i = \underset{(0.02)}{1.66} - \underset{(0.00)}{0.009} \times \log z_i + \vec{X_s} \gvec{\upgamma}_1 + \vec{X_p} \gvec{\upgamma}_2 + \vec{X_o} \gvec{\upgamma}_3 + \varepsilon_i, \quad R^2 = 0.065.
%\end{equation*}
%Notice that the $R^2$s differ sharply between the two groups of regressions.\footnote{Generally speaking, the estimated elasticities of $\phi_k$ and $\phi_l$ to $z$ depend on the value of $\gamma$, since $z$ is calculated for a given $\gamma$. For $\gamma = 0.93$ used here, if taken at its face value, the elasticities of $\phi_k$ and $\phi_l$ to $z$ seem well below the estimates in the literature. For instance, by using comprehensive micro data, \citet{HsiehKlenow:2014} find that the elasticity is 0.1 for the United States and between 0.5 and 0.6 for India and Mexico. By using data from the World Bank's Enterprise Surveys, \citet{BentoRestuccia:2016} find that the elasticities range from 0.22 to 0.74, averaging 0.52. However, we argue that this is because in the calibration of our general equilibrium model, as is explained in details in Section \rom{3}, in order that our model generates a wide range of firm size, a value of $\gamma$ that is higher than commonly used in the literature is needed. If we assume $\gamma = 0.85$ following \citet{AtkesonKehoe:2005}, then the elasticities of $\phi_k$ and $\phi_l$ to $z$ are both about 0.25, which are quantitatively consistent with those in the literature. The value of $\gamma$ used, however, will not affect the qualitative conclusion that large firms are subject to more distortions, which is the purpose here. In addition, because when calculating $z$, a $\gamma$ closer to one will greatly amplify measurement errors. As a result, we use only the samples between the first and last deciles in the estimation. Qualitatively, our results are not affected as well.}\textsuperscript{, }\footnote{For all three regressions, using the manufacturing sector as a whole lead to the same estimates (0.04, 0.06, and $-$0.01) and $R^2$s (0.50, 0.63, and 0.09).}

Qualitatively, these findings indicate that the {relative} wedge firms face in the capital and labor markets does not depend strongly on the idiosyncratic productivity of firms, which in the context of our model implies $1+\tau_{k_i} \approx 1+\tau_{l_i}$.\footnote{This also explains the reason why $\phi_{k_i} \approx \phi_{l_i}, \forall i$.} Since we cannot separately identify the three wedges, for simplicity, we assume $\tau_{k_i} = \tau_{l_i} = $ 0 and attribute all the variations in the average product of factors to the wedges in the product market $\tau_{z_i}$. Whether we assume $\tau_{k_i} = \tau_{l_i} = $ 0 or alternatively $\tau_{z_i} = $ 0 does not affect our results, but the interpretations need to be changed accordingly.\footnote{For example, we cannot distinguish between the data-generating process we use here and another process where $\tau_{k_i}$ and $\tau_{l_i}$ increase simultaneously, while $\tau_{z_i}$ is equal to zero.}

\begin{figure}[t]
    \begin{center}
    \includegraphics[width=0.50\textwidth]{./Figures/tax.eps}
    \caption{The Output Tax Fuction $\tau_z$}
     \floatfoot{The actual output tax function used in the quantitative exercises, given the calibrated values for $\phi_0$ and $\phi_1$}
    \label{fig:tauz}
    \end{center}
\end{figure}
%In the spirit of \citet{BentoRestuccia:2016}, we implement these idiosyncratic wedges in the model by positing a generic ``tax'' function that specifies the wedges as a function of a firm's productivity $z$:\footnote{This tax function has a long history in macro-public finance literature, for instance \citet{Benabou:2002}. We thank a referee for pointing this out. Recent studies that adopt the same tax functions include \citet{AdamopoulosRestuccia:2014}, \citet{HsiehKlenow:2014}, and \citet{Guneretal:2017}.}

As a result, following \citet{HsiehKlenow:2014} and \citet{BentoRestuccia:2016}, we model these distortions as implicit progressive output taxes, and the tax rate function takes the form used in the main text:%\footnote{This tax function has a long history in macro-public finance literature, which dates back to at least \citet{Benabou:2002}. We thank a referee for pointing this out. Recent studies that use this function include \citet{BentoRestuccia:2016} and \citet{Guneretal:2017}.}
\begin{equation}
    \tau_z = \max \left\{ 0, 1 - \phi_0 z^{\phi_1} \right\}.
\label{eq:tax}
\end{equation}
where the parameter $\phi_0$ determines the mean level of the taxes, and the parameter $\phi_1$ determines the progressiveness of the taxes. When $\phi_1<0$, the tax rates are increasing in firm TFP $z$, and the progressiveness of the taxes is decreasing in the value of $\phi_1$.\footnote{Notice that since $\phi_1 < $0, decreasing $\phi_1$ increases its absolute value.} %\footnote{There is one difference between Equation (\ref{eq:tax}) and the tax function used by \citet{AdamopoulosRestuccia:2014}. To model the progressiveness, in their specification, the authors use an exponential function as opposed to the power function here. We choose the power function because it is consistent with the log-linearity of $\phi_k$ ($\phi_l$) and $z$, while the exponential function implies a tax scheme that is much steeper than what our data suggest.}
The actual tax function used in the quantitative exercises is plotted against log productivity in Figure \ref{fig:tauz}, which is increasing and concave in $z$ given our calibrated values for $\phi_0$ and $\phi_1$.
%From now on, we use $\tau_z$ instead of $\tau_y$ to denote the product market frictions.We assume that the taxes collected are returned to the household as lump-sum transfers.
%Anticipating the benchmark calibration in the next section, the wedge function specified in Equation (\ref{eq:tax}) is increasing and concave in $z$, with the lower and upper bounds being 0 and 1, respectively. The shape of the function captures the size dependency of the product market distortions where the wedges are higher for larger firms. The actual tax function used in the quantitative exercises is plotted against log productivity in Figure \ref{fig:tauz}. %\footnote{There is one difference between Equation (\ref{eq:tax}) and the tax function used by \citet{AdamopoulosRestuccia:2014}. To model the size dependency, in their specification, the authors use an exponential function as opposed to the power function here. We choose the power function because it is consistent with the log-linearity of $\phi_k$ ($\phi_l$) and $z$, while the exponential function implies a tax scheme that increases much sharper with respect to productivity than the empirical counterpart for our case.} %We rule out subsidies ($\tau_z < 0$) because $\lim_{z \downarrow 0} \tau_z = -\infty$ which leads to unrealistic solutions.}

As we explained in the main text, the firm-level distortions $\tau_z$ are meant to capture a variety of policies and institutions that reallocate production factors from large productive to small unproductive firms, following the \emph{indirect} approach in the misallocation literature [\citet{RestucciaRogerson:2013}]. Examples include size-dependent taxes and subsidies that favor small firms, imperfect tax enforcement that induces tax evasion among small firms, financial constraints and contractual frictions that impede the growth of productive firms [\citet{CooleyQuadrini:2001}, \citet{ClementiHopenhayn:2006} and \citet{Akcigitetal:2018}], and local protectionism and internal trade barriers that disproportionately affect large productive firms [\citet{Eberhardtetal:2016} and \citet{TombeZhu:2015}]. While it is of great policy interest to study specific policies and institutions underlying $\tau_z$, we leave this important task to future work.\footnote{\citet{AdamopoulosRestuccia:2014} and \citet{AGpaper} are two recent examples where observable policy distortions are investigated. \citet{AdamopoulosRestuccia:2014} study the observable farm-level price distortions while our own work \citet{AGpaper} focuses on distortions created by migration and land distribution policies in China.}

%The idiosyncratic $\tau_z$ is meant to capture implicitly a variety of policies and institutions that allocate factors away from large productive firms. For example, this is consistent with the fact that large productive firms face transportation costs, additional management costs, and/or local protectionism and trade barriers that impede the inter-regional flow of goods [\citet{Young:2000}, \citet{HsiehKlenow:2014}, \citet{TombeZhu:2015}, and \citet{Eberhardtetal:2016}]. It could also be that smaller firms are subject to preferential tax treatment.\footnote{For instance, value added taxes for firms with an annual industrial output value of less than CNY 1 million is 3\%, while firms with a production scale larger than CNY 1 million are subject to a 13\% tax rate.} Some of these examples, for instance transportation costs and management costs, are not exactly the ``distortions'' narrowly defined as inefficiencies from policy interventions. Hence a more accurate interpretation of the distortions captured by our model is any factors that prevent firms from reaching their full potentials in a frictionless world. We stick to the word \textit{distortion} mainly for convenience. From a policy perspective, it would be of great interest to follow the so-called direct approach in \citet{RestucciaRogerson:2013} and study the specific policies and regulations that we observe in the economy. We leave this important task to future work.\footnote{\citet{AdamopoulosRestuccia:2014} and \citet{AGpaper} are two recent examples where observable policy distortions are investigated. \citet{AdamopoulosRestuccia:2014} study the observable farm-level price distortions while our own work \citet{AGpaper} focus on distortions created by migration and land distribution policies in China.}

\subsection{Treatment Technologies}
\label{sec:appen_techspec}

In the main text, we model the cost of adopting the clean technology as a fixed cost $k_E$ independent of the production scale of firms. In this subsection, we provide additional empirical evidence in support of this assumption using the firm-level data from the NGSPS.

%In the paper, we model the costs of adopting abatement technology as a fixed costs $k_E$, regardless of the production scale of firms. The readers may concern that this could be a mis-specification. Two alternatives arise naturally: fixed costs plus operating costs and scale-related fixed costs. In this section, we show that each alternative contradicts some of the empirical evidence we document from the data.

%\textit{Operating Costs.}---Trimming the top 1\% observations for outliers, we calculate the ratio of operating costs of treatment equipments to total output. On average, operating costs of abatement equipment takes about 1.5\% of a firm's annual value of production. The ratios at the 25\%, 50\%, and 75\% percentile are 0.13\%, 0.49\%, and 1.43\% respectively. This suggests that operating costs are negligible for more than 50\% of the firms. For simplicity, we omit them from the model.

The assumption that the cost of technology adoption is independent of firm size has two implications. First, larger firms are more likely to adopt clean technology, and as a result, we should see positive correlations between production scale with both the possibility of adoption and total expenditure in treatment technology. The linear probability model in the main text shows the first. Here we calculate the correlation between the log value of production and treatment equipment investment as well. Not surprisingly, we find that it is positive (0.64) as well.

%\textit{Fixed Costs Proportional to Production Level.}---In our model, we have assumed that the treatment technology investment is a fixed cost independent of the production scale. This has two implications. First, larger firms are more likely to adopt clean technology, and as a result, we should see positive correlation between production scale with both the possibility and total expenditure in treatment technology. The linear probability model in the main text shows that output is positively correlated with clean technology adoption rate. Here we calculate the correlation between the log value of production and treatment equipment investment as well. Not surprisingly, we find that it is positive (0.64) as well.

The second and perhaps more important implication is that the ratio of treatment technology expenditure over output should decrease with the size of the firm. We find that it is also the case in the NGSPS data. For firms in the top-5 polluting industries, we calculate the average of the ratio of treatment equipment expenditure to output value within each quintile of output. The means of the ratio from the first (smallest) to the fifth (largest) quintile are 22\%, 11\%, 6.7\%, 5.0\%, and 2.7\%, respectively. A linear regression model that controls for the same set of covariates as in the main text delivers the same message:
%The second and perhaps more important implication is that treatment technology investment cost should decrease with the size of the firm. We find that it is also the case. By using the NGSPS, for firms in the top-5 polluting industries, we calculate the average of the ratio of treatment equipment expenditure to output value within each quintile of output. The means of the ratio from the first (smallest) to the fifth (largest) quintile are respectively 22\%, 11\%, 6.7\%, 5.0\%, and 2.7\%. A linear regression model controlling for the same set of covariates as in the main text delivers the same message
\begin{equation*}
    \log \left(\frac{\text{Investment}_i}{\text{Output}_i} \right) = \underset{(0.11)}{-0.73} - \underset{(0.004)}{0.40} \times \log (\text{Output}_i) + \vec{X} \gvec{\upgamma} + \varepsilon_i,
\end{equation*}
which shows a negative correlation as well. Together, the evidence supports our choice of modeling the adoption cost of clean technology as a fixed cost.

\textit{Prices of Physical versus Biological Equipment.}---We assume in the main text that only the installation of biological technologies requires a fixed cost. Here we provide evidence in support of this choice. The distributions of the prices for physical and biological equipments in absolute term (in CNY 10,000) are listed in Table \ref{tab:fixcosts_appen}.
\begin{table}[t]
    \footnotesize
    \centering
    \begin{threeparttable}
    \caption{Prices of Different Treatment Equipments}
    \begin{tabular}{lccccc}
    \hline \hline
    Technologies    & 25\%      & 50\%      & 75\%      & Maximum   & Mean \\
    \midrule
    Physical        & 2      & 6      & 25    & 800   & 36.14 \\
    Biological      & 30     & 85     & 260    & 4000   & 249.90 \\
    \bottomrule
    \end{tabular}
    \floatfoot{Source: 2007 NGSPS. All the numbers are measured in CNY 10,000.}
    \label{tab:fixcosts_appen}
    \end{threeparttable}
\end{table}
As is shown in the table, the prices of biological equipments are 7 to 15 times of those of physical equipments. In addition, the total installation costs of physical equipment for the top-5 polluting industries over those of biological equipment is only 0.087. %, implying that the installation costs of physical equipment when aggregated across the economy are only 9\% of those of the biological equipments. These evidence suggest that comparing to biological equipment, the costs of installing physical treatment equipments are small. Therefore in our model we assume that only the adoption of biological equipment is costly.%In addition, the total investment of physical equipment over biological equipment is 0.087, meaning that the installation costs of physical equipments when aggregated across the economy are only 9\% of those of the biological equipments. These evidence suggest that comparing to biological equipment, the costs of installing physical treatment equipments are small. Therefore in our model we assume that only the adoption of biological equipment is costly.
These facts again point to the importance of the fixed costs associated with the adoption of the clean technology. Therefore in our model we assume that only the adoption of biological equipment is costly.\footnote{In fact, what is crucial here is that the cost to install clean technology is higher than that of dirty technology.} %and support our somewhat extreme assumption that only the installation of biological technologies requires a fixed cost.

%In summary, the evidence suggests that firms' investment in abatement equipment is increasing with production scale but to a much lesser extent in absolute term. Again for simplicity and without loss of generality, we choose the fixed costs modeling strategy.

%\subsection{Treatment Technologies}

\textit{Additional Technical Features of the Treatment Technologies.---}We are interested in the following features of these technologies: {processing efficiency, designed processing capacity} and {installation costs}. We proxy the {processing efficiency} using one minus the ratio of {emitted COD} to {generated COD}. The {designed processing capacity} (in tons) and {actual installation costs} are recorded directly by the data. We then calculate the {unit capacity costs} by dividing the installation costs by the processing capacity. We use the unit capacity costs as an indicator of returns to scale of clean treatment equipment. In Figure \ref{fig:techdiff}, in clockwise order we plot the density functions of processing capacity, installation costs, total value of industrial output and unit capacity cost by technology types. For all panels, log-scale is used in the horizontal axes.
\begin{figure}[t]
    \begin{center}
    \includegraphics[width=0.4\textwidth]{./Figures/abate_cap.pdf}%
    \includegraphics[width=0.4\textwidth]{./Figures/abate_inv.pdf} \\
    \includegraphics[width=0.4\textwidth]{./Figures/abate_unit.pdf}
    \includegraphics[width=0.4\textwidth]{./Figures/abate_prod.pdf}
    \caption{Technical Features of Different Treatment Technologies}
    \floatfoot{Source: NGSPS. In all panels, the horizontal axes are in log-scale.}
    \label{fig:techdiff}
    \end{center}
\end{figure}

Broadly speaking, biological technologies have the {best} processing efficiency, the {largest} processing capacity, the {highest} installation costs but the {lowest} unit capacity cost. More specifically, the mean and median processing efficiency of biological technology are 17 and 10 percentage points higher than the physical technology. %The density functions of processing capacity, installation costs and production scale for physical, chemical and biological equipments order from left to right while those of the unit capacity costs order from right to left.
The evidence again points to a fixed costs type of mechanism behind the lower pollution intensity by large firms. That is, although biological technologies are more advanced in terms of processing capacity and efficiency, they are also more costly. Therefore, small firms lack the profit margins needed to take advantage of the returns to scale exhibited by biological technologies, and hence large firms are more likely to adopt these more advanced technologies. %This could also be seen by calculating the ratio of the \textit{summed} costs of treatment equipment to the \textit{summed} value of output for firms of different sizes. While this ratio is equal to 18\% when only firms with output level below the median are included, the ratio decreases dramatically to 4\% when up to 95\% firms are included, which point to the importance of fixed adoption costs.

\subsection{Environmental Regulations in China}
\label{sec:china_regulation}
In this section, we briefly summarize the environmental regulations in China. We follow the descriptions in \citet{Lin:2013} closely here.

Environmental regulations in China are specified in \textit{The Environmental Protection Law of the People's Republic of China (EPL)}. The EPL was launched on trial basis in 1979 and was officially enacted by the National People's Congress in 1989. It was later amended in 1993 and 2003. The Ministry of Environmental Protection (MEP, previously the State Environmental Protection Administration) is in charge of the monitoring and administration of China's environmental issues. Two major policy instruments that the MEP uses are a pollution levy system and command-and-control instruments.

\textit{The Pollution Levy System.---}The pollution levy system charges firms a pollution fee based on their quantity of effluent discharge of pollutants. Before 1993, firms were required to pay for the emissions that go beyond the national standard. If a firm discharges multiple pollutants and the levels of more than one of the pollutants are above the national standard, it only has to pay for the one that exceeds the standard by the greatest amount (calculated according to the \textit{Pollutants Equivalent Factor}). Starting from 1993, firms also have to pay for within-standard emissions. After 2003, pollution levies are calculated based on the top three above standard pollutants instead of only the top one. The 2015 revision of the EPL significantly increases the financial penalties by allowing the environmental authorities to multiply the original penalties by the number of days that firms are incompliant with the regulations specified in the law.

In practice, the MEP oversees the enforcement of the EPL and the implementation of environmental policies. Local Environmental Protection Bureaus (EPBs) are the main authorities that do the field work. In general, larger polluters are monitored by municipal EPBs while smaller ones are by district and county EPBs. All polluting firms are required to submit an annual predicted volume of emissions at the beginning of a year. Based on the actual production and abatement practice, firms are also required to revise the actual emissions during the year. The EPBs send field staff to verify the credibility of firms' reports. The inspections include consistence between emissions, output, material usage, and across historical data. Field inspectors also conduct random on-site inspections of the emissions by firms without prior warning.

Pollution levies are then calculated based on the verified reports. False reporting are subject to financial penalty with a ceiling. Serious fraudulent reports could lead to further non-financial penalties, including temporary shut down from production, administrative detention of directly responsible personnel, and even criminal charges.

\textit{The Command-and-Control Instruments.---}The command-and-control instruments usually involve temporary shut down of firms incompliant with environmental emission standards, which would cost these firms a fraction of their profits. Serious violation sometimes also leads administrative detention and criminal charges similar to the case of fraudulent report of emissions. Because the pollution levy system is widely acknowledged for being ineffective in providing firms with incentives to control pollution [\citet{Dasguptaetal:2001}, \citet{WangWheeler:2005} and \citet{Lin:2013}], command-and-control instruments are usually used as a deterrence for potential violation by polluting firms. The command-and-control instruments prove to be effective in many government-led campaigns against pollution. See for example, Te-Ping Chen, ``China Cracks Down on Water-Polluting Industries,'' the Wall Street Journal, April 17th, 2015; or Trevor Nace, ``China shuts down tens of thousands of factories in widespread pollution crackdown,'' Forbes, October 24th 2017.

%\section{The Firm Size Distribution of the United States}
\section{The Firm Size Distributions of Individual Industries}

In the main text, we present the firm size distributions for the pooled polluting industries and the manufacturing sector as a whole. In this section, we explain in details how the firm size distributions are constructed, especially those for the U.S., and present the firm size distributions for each of the five polluting industries in China and in the U.S.

%In this section, we explain in details how the firm size distributions of the United States are constructed from the SUSB. We also present the size distribution of firms based on the number of firms in each size category. We refer to this in the current section as the \textit{firm size distribution}, and we call the distributions defined in the main text as \textit{employment distribution}. In the main text, we present only the employment distribution for the pooled polluting industries and the manufacturing sector as a whole. At the end of this Section, we also plot the employment distributions for each of the five polluting industries.

We use the 2004 CNEC and 2004 Statistics of U.S. Businesses (SUSB) data to construct the firm size distributions in China and in the U.S., respectively. The SUSB organizes data around the so-called {enterprise} size groups instead of firm size groups. According to the definition in SUSB, a large enterprise could consist of firms that belong to different industries. For each size bin, the SUSB reports the total number of firms, establishments and employees along with other variables summed up across all {enterprises} that fall in that size bin. As a result, we approximate the firm size distribution using the average firm size of a particular size group, which is calculated by dividing the total employment by the number of firms. We then assign groups of firms to different size bins according to their average size. Such imputation introduces approximation errors. %, but it is less likely for enterprises with less than 100 employees to have multiple firms.
To further reduce the approximation noise, we group the size bins into four main groups: 1--19, 20--99, 100--399 and 400+. The firm size distributions for each of the top polluting industries and all industries pooled together are shown in Figure \ref{fig:es}. As we can see, while there is substantial heterogeneity across individual industries, large firms in China account for much smaller employment shares than those in the U.S. for each industry.

%The SUSB organizes data according to {enterprise} size group rather than firm or establishment size which relates closer to what we want. In particular, for each size bin, the SUSB reports the total number of firms, establishments and employees along with other variables summed up across all {enterprises} that fall in that size bin. We cannot use the size and share distribution of the enterprises because according to the definition in SUSB, a large enterprise could consist of firms and establishments in different locations, of different sizes and even in different sectors. However, the number of firms includes only those firms that are categorized as belonging to one particular industry. Therefore, we approximate the firm size distribution using the average firm size of a particular size group, which is calculated by dividing the total employment by the number of firms. We then assign groups of firms to different size bins according to their average size. Such imputation introduces approximation errors. However, we argue that most approximation errors lie in the upper tail of the distribution since it is less common for enterprises with less than 200 employees to have multiple firms or establishments. To further reduce the approximation noise, we group the size bins into four main groups: 1--19, 20--99, 100--399 and 400+. We drop firms with less than 19 employees when plotting the size distribution because we think many of them may not be engaged in the actual production process but will significantly change the shape of the {firm size distribution}. Including or dropping these firms does \emph{not} change the employment distribution because the calculation is essentially a weighted average with the number of employees as the weight. These small firms are thus weighted much less compared to the large ones. However, the firm size distributions are affected because the sheer amount of these firms.\footnote{We choose not to use establishment as the unit of our analysis because more noise is likely to be introduced by the approximation procedure that we adopt. However, results regarding the employment distributions, which are our ultimate interest here, is quite robust across variations. What is less robust is the firm size distribution, which by itself is less relevant to our conclusions. All results along with robustness checks with different size bin cut-offs are available upon request.} The firm size distributions for each of the top polluting industries and all industries pooled together are shown in Figure \ref{fig:dist}. The corresponding employment distributions are shown in Figure \ref{fig:es}.

%\begin{figure}[htbp]
%    \begin{center}
%    \includegraphics[width=0.45\textwidth]{./Figures/paperdist_R.pdf}%
%    \includegraphics[width=0.45\textwidth]{./Figures/agridist_R.pdf} \\
%    \includegraphics[width=0.45\textwidth]{./Figures/textiledist_R.pdf}
%    \includegraphics[width=0.45\textwidth]{./Figures/chemmatdist_R.pdf} \\
%    \includegraphics[width=0.45\textwidth]{./Figures/beverdist_R.pdf}
%    \includegraphics[width=0.45\textwidth]{./Figures/pooldist_R.pdf}
    %\vspace{-1em}
%    \caption{Firm Size Distribution}
%    \floatfoot{Source: CNEC and SUSB.}
%    \label{fig:dist}
%    \end{center}
%\end{figure}

\begin{figure}[htbp]
    \begin{center}
    \includegraphics[width=0.45\textwidth]{./Figures/paperES_R.pdf}%
    \includegraphics[width=0.45\textwidth]{./Figures/agriES_R.pdf} \\
    \includegraphics[width=0.45\textwidth]{./Figures/textileES_R.pdf}
    \includegraphics[width=0.45\textwidth]{./Figures/chemmatES_R.pdf} \\
    \includegraphics[width=0.45\textwidth]{./Figures/beverES_R.pdf}
    \includegraphics[width=0.45\textwidth]{./Figures/poolES_R_1.pdf}
    %\vspace{-1em}
    \caption{Employment Distribution}
    \floatfoot{Sources: CNEC and SUSB.}
    \label{fig:es}
    \end{center}
\end{figure}

\section{Accounting Exercises}

This section provides details on the accounting exercises.

\textit{Estimation Strategies.}---Ideally, we would like to have information on pollution intensity over firms' \emph{employment} size bins. Unfortunately, the NGSPS only reports total output value and total amount of pollution at the firm level. Therefore, we need to construct pollution intensity over the number of employees. To do this, we use the CNEC to estimate a relationship between employment and output.

\begin{table}[t]
\footnotesize
\centering
\begin{threeparttable}
\caption{Size Distribution on Pollution}
\begin{tabular}{lccccccc}
    \hline \hline
    Methods             & Paper  & Agricultural Food   & Textile    & Chemistry    & Beverage     & Average \\
    \midrule
    Non-parametric      & 39.8\% & 60.7\%              & 81.6\%     & 102.5\%      & 103.7\%      & 63.5\%  \\
    Piecewise-linear    & 34.8\% & 69.4\%              & 93.5\%     & 180.1\%      & N/A\tnote{a} & 75.4\%  \\
    Parametric          & 43.5\% & 61.1\%              & 97.5\%     & 101.2\%      & 89.0\%       & 67.0\%  \\
    \bottomrule
\end{tabular}
\begin{tablenotes}
     \footnotesize{
     \item[$\dagger$]
     Note: For individual industries, the numbers reported are the pollution intensity from using the U.S. firm size distribution as percentage of that using China's distribution. We use the 1st and 3rd quartile as the ends of the output range corresponding to each employment bin in the non-parametric calculation. Column 6 (Average) calculates the weighted average of these ratios using the percentage contribution in the first row of Table 1 in the main text as weights.}
     \item[a]
     Since the beverage industry has fewer firms than the others, there are employment size bins with no corresponding firms in China, which invalidates the method. We set the ratio to 100\% in the calculation of the last average.
\end{tablenotes}
\label{tab:accounting_appen}
\end{threeparttable}
\end{table}
\begin{enumerate}
  \item
  \textit{Non-parametric}:
    \begin{itemize}
    \item
    For each U.S. employment bin, we compute the 1st and 3rd quartile of output level for Chinese firms within that employment bin. The two quartiles are used as the lower and upper bounds for the output bins in NGSPS.
    \item
    We then use the median pollution intensity of firms within the newly defined output bins as the average pollution intensity for those bins.
    \item
    Lastly, we calculate the aggregate pollution by assigning to each bin the corresponding share of output. %The NGSPS production bins are used for China and the employment bins are used for U.S.
    \end{itemize}
  \item
  \textit{Piecewise Linear}:
  \begin{itemize}
    \item
    For each U.S. employment bin, we regress log-output on log-employment using the subset of Chinese firms within that employment bin. The lower and upper bounds for the output bins in this case are calculated as the predicted value of the above regression.
    \item
    We then run piecewise log-linear regression of pollution intensity on output within each new production bin. The average pollution intensity is chosen to be the predicted intensity at the midpoint of the new log-output bin.
    \item
    Lastly, the average intensity is applied to the output share distributions. %The U.S distribution does not change, however, a new distribution for China is calculated since the endpoints of the output bins are different.
    \end{itemize}
  \item
  \textit{Parametric}:
  \begin{itemize}
    \item
    Using the CNEC, we regress log-output on log-number of workers, which yields a {parametric} relationship between the number of workers and output.
    \item
    Using the NGSPS, we regress log-intensity on log-output, which yields a {parametric} relationship between intensity and output. From these two relationships, we can subsequently construct a new \emph{parametric} relationship between intensity and number of employees. The average intensity is chosen to be the midpoint of each U.S. employment bin. Notice that in this case we have a direct functional form for employment and intensity).
    \item
    Lastly, the average intensity is applied to the output share distributions. %The U.S. distribution does not change, but a new distribution for China is calculated since the endpoints of the production bins are different. Notice that this distribution for China is the one we use in Section \rom{1}.C.
\end{itemize}
\end{enumerate}

The estimation results are shown in Table \ref{tab:accounting_appen}. Each of the three methods has its own advantages and disadvantages. The two non-parametric methods capture more of the variation at the local level, which could be washed out in the parametric estimation across the whole state space. However, this local nature also introduces a lot of instability on the estimates. Further, there are situations when there are gaps not covered by adjacent output bins and situations when these output bins overlap with each other. Under these conditions, some information will be lost while others are used for multiple times. Nevertheless, the results are robust across different estimation strategies. In the Section \rom{1}.C of the main text, we use the results from the parametric method.

\section{Proofs and Additional Analytical Results}

In this section, we provide formal proofs to Propositions 1 and 2 in Section \rom{2}.D of the main text. The two propositions are proved respectively in Sections \ref{sec:appen_proof_tech} and \ref{sec:appen_proof_pollution}. We also include additional analytical results in this section. Specifically, in Section \ref{sec:appen_proof_tech}, Lemma \ref{lemma:nofrictionpi_appen} and Corollary \ref{lemma:frictionpi_appen} highlight the key trade-off that firms face in deciding which type of treatment technology to install, when firms are and are not subject to correlated distortions respectively. Lemma \ref{prop:threshold_appen} shows the standard results of the \citet{Lucas:1978b} model where household members choose their occupations according to their comparative advantage. In Section \ref{sec:appen_proof_pollution}, in a simple one-sector model with a fixed number of firms and \emph{exogenous} firm-level pollution intensity, we present the conditions under which removing the progressiveness of the distortions would reduce average pollution intensity. In Section \ref{sec:appen_proof_melitz}, we show the qualitative equivalence between the effects of distortions on aggregate output and pollution in the \citet{Lucas:1978b} model with those in the closed-economy version of the \citet{Melitz:2003} model. Many researchers working with heterogeneous firms models are more familiar with the \citet{Melitz:2003} setup as opposed to the \citet{Lucas:1978b} setting, especially in the trade and environment community. We demonstrate in this section that the differences between the two settings are immaterial to our main findings. Finally, in Section \ref{sec:uncorrelated}, we use a simple model to study how \emph{uncorrelated} distortions---defined as distortions that are not correlated with firm TFP---affect aggregate output and pollution.

%In this section we provide formal proofs to the Results \ref{prop:friction_appen} and \ref{prop:pollution_distortion_appen} in Section \rom{2}.D. The two results are proved respectively in Sections \ref{sec:appen_proof_tech} and \ref{sec:appen_proof_pollution}. We also include some of the intermediate results as well. Specifically, in Section \ref{sec:appen_proof_tech}, Lemma \ref{lemma:nofrictionpi_appen} and Corollary \ref{lemma:frictionpi_appen} highlight the key trade-off firms face when deciding which type of treatment technology to install in economies without and with distortions. Lemma \ref{prop:threshold_appen} shows the standard results of the \citet{Lucas:1978b} model where households choose their occupation according to their comparative advantage. In Section \ref{sec:appen_proof_pollution}, we include additionally the condition under which removing the size-dependency of the distortions reduces average pollution intensity. In Section \ref{sec:appen_proof_melitz}, we show the equivalence of our model setup to one that features monopolistic competition. Many researchers working with heterogeneous firms model is more familiar with the \citet{Melitz:2003} setup as opposed to the \citet{Lucas:1978b} setting, especially in the trade and environment community. We demonstrate in this section that the difference between the two settings are immaterial.

\subsection{Correlated Distortions and Technology Adoption}
\label{sec:appen_proof_tech}

In this section, we prove Proposition 1 of the main text. To simplify notation, we set $\phi_0 =$ 1 in this section.

\noindent PROOF OF LEMMA \ref{lemma:nofrictionpi_appen}:
\begin{lemma}
\label{lemma:nofrictionpi_appen}
In an economy with no correlated distortions, $\pi_0(z)$ and $\pi_1(z)$ are both increasing and linear with respect to $z$. In addition, the slope of $\pi_1(z)$ is steeper than that of $\pi_0(z)$:
\begin{equation}
    \frac{\partial \pi_0 (z)}{\partial z} = (1 - \xi)\frac{\partial \pi_1 (z)}{\partial z}, \qquad \forall z \in Z.
\label{eq:lemma1ap}
\end{equation}
\end{lemma}
\begin{proof}
Once the fixed cost $k_E$ is paid, it no longer affects a firm's decision. The factor demand decisions for the two types of firms are therefore the same. The first order conditions for capital and labor are respectively
\begin{align}
    \label{eq:fock}
    & \frac{\partial \pi_i(z)}{\partial k}: \qquad \alpha \gamma z^{1-\gamma} k^{\alpha \gamma -1} l^{(1-\alpha)\gamma} = R, \\
    \label{eq:focn}
    & \frac{\partial \pi_i(z)}{\partial l}: \qquad (1-\alpha) \gamma z^{1-\gamma} k^{\alpha \gamma} l^{(1-\alpha)\gamma-1} = W, \qquad i = 0,1.
\end{align}
Dividing (\ref{eq:fock}) with (\ref{eq:focn}) yields constant capital to labor ratio $h$
\begin{equation*}
    h = \frac{k}{l} = \frac{\alpha W}{(1-\alpha)R},
\end{equation*}
which says more capital is demanded when technology is capital intensive (higher $\alpha$) or when capital rental price $R$ low. Notice that the system of equations (\ref{eq:fock}) with (\ref{eq:focn}) is log-linear and thus has closed-form solution. With some algebra, the solutions are characterized by
\begin{align}
    \label{eq:n}
    & l(z) = \Phi_1 R^{\frac{\alpha \gamma}{\gamma -1}} W^{\frac{1-\alpha \gamma}{\gamma-1}} \cdot z, \\
    \label{eq:k}
    & k(z) = \Phi_2 R^{\frac{1+\gamma(\alpha -1)}{\gamma -1}} W^{\frac{\gamma(1-\alpha)}{\gamma-1}} \cdot z,
\end{align}
where
\begin{equation*}
    \qquad \Phi_1 = \left[ \frac{(1-\alpha)^{\alpha \gamma}}{(1-\alpha)\gamma \alpha^{\alpha \gamma}}\right]^{\frac{1}{\gamma -1}} \text{ and } \Phi_2 = \frac{\alpha}{1-\alpha}\Phi_1.
\end{equation*}
Substitute the optimal solutions (\ref{eq:n}) and (\ref{eq:k}) back to the definition of profits functions $\pi_1(z)$ and $\pi_0(z)$, we have
\begin{align*}
    & \pi_0(z) = (1-\xi)\left(\Omega - \frac{1}{1-\alpha}\Phi_1 \right) \kappa z, \\
    & \pi_1(z) = \left(\Omega - \frac{1}{1-\alpha}\Phi_1 \right) \kappa z - R k_E,
\end{align*}
where
\begin{equation*}
    \Omega = \left(\frac{\alpha}{1-\alpha}\right)^{\alpha \gamma} \Phi_1^{\gamma} \text{ and } \kappa = W^{\frac{\gamma(1-\alpha)}{\gamma-1}} R^{\frac{\alpha\gamma}{\gamma-1}}.
\end{equation*}
It can be seen that both functions are increasing and linear in $z$, and hence Equation (\ref{eq:lemma1ap}) holds.
\end{proof}

\noindent PROOF OF COROLLARY \ref{lemma:frictionpi_appen}:
\begin{corollary}
\label{lemma:frictionpi_appen}
Suppose that the correlated distortions are specified as $\max\left\{ 0, 1 - z^{\phi_1} \right\}$ with $1 - \gamma + \phi_1 > 0$, then $\pi_0(z)$ and $\pi_1(z)$ are both increasing and concave with respect to $z$. In addition, the slope of $\pi_1(z)$ is steeper than that of $\pi_0(z)$:
\begin{equation*}
    \frac{\partial \pi_0 (z)}{\partial z} = (1 - \xi)\frac{\partial \pi_1 (z)}{\partial z}, \qquad \forall z \in Z.
\end{equation*}
\end{corollary}
\begin{proof}
The proof is straightforward given Lemma \ref{lemma:nofrictionpi_appen}. Substituting in the tax function, $\pi_0(z)$ and $\pi_1(z)$ now becomes
\begin{align*}
    & \pi_0(z) = (1-\xi)\left(\Omega - \frac{1}{1-\alpha}\Phi_1 \right) \kappa z^{\frac{1-\gamma+\phi_1}{1-\gamma}}, \\
    & \pi_1(z) = \left(\Omega - \frac{1}{1-\alpha}\Phi_1 \right) \kappa z^{\frac{1-\gamma+\phi_1}{1-\gamma}} - R k_E,
\end{align*}
where $\Omega, \Phi_1$ and $\kappa$ are defined as in Lemma \ref{lemma:nofrictionpi_appen}.

The assumption $1-\gamma+\phi_1 > 0$ guarantees the monotonicity of the profits functions. In the terminology of \citet{Hopenhayn:2014}, the assumption means that there is no rank reversal. Concavity is easily verified by taking the second order derivatives.
\end{proof}

\noindent PROOF OF LEMMA \ref{prop:threshold_appen}:
\begin{lemma}
\label{prop:threshold_appen}
There exists a unique threshold $\hat{z}$ such that all household members with $z \leq \hat{z}$ choose to be workers and those with $z \geq \hat{z}$ become entrepreneurs. Further, $\hat{z}$ is pinned down by $W = \pi(\hat{z})$
\end{lemma}
\begin{proof}
Since the overall profit function $\pi(z)$ is the upper envelope of $\pi_0(z)$ and $\pi_1(z)$, from Lemma \ref{lemma:nofrictionpi_appen} (and Corollary \ref{lemma:frictionpi_appen}) we know that $\pi(z)$ is monotonic increasing. It is easy to verify that $\pi(0) = $ 0. Therefore, as long as $0<W<\pi(\overline{z})$, we can find a unique $\hat{z}$ such that $\pi(\hat{z})=W$, where uniqueness follows from the monotonicity. The condition $0<W<\pi(\overline{z})$ is guaranteed in the general equilibrium version of our model by Inada condition on the production function.
\end{proof}

\noindent PROOF OF PROPOSITION \ref{prop:friction}:
\begin{proposition}
\label{prop:friction}
When $1-\gamma+\phi_1>0$, a firm chooses to install clean technology only when its productivity is higher than a threshold. Moreover, the threshold when the firm faces distortions $\tilde{z}_f$ is higher than that when the firm is not subject to any distortions $\tilde{z}_n$.
\end{proposition}

%\begin{result}
%\label{prop:friction_appen}
%Given $k_E, W, \tau_z$ and $R$, there exist unique thresholds $\tilde{z}_n$ and $\tilde{z}_f$ such that:
%\begin{enumerate}[(i)]
%    \item
%    In the economy with no product market frictions, entrepreneurs with $z \leq \tilde{z}_n$ produce using dirty technology while those with $z > \tilde{z}_n$ produce using clean technology.
%    \item
%    In the economy with product market frictions, entrepreneurs with $z \leq \tilde{z}_f$ produce using dirty technology while those with $z > \tilde{z}_f$ produce using clean technology.
%    \item
%    $\tilde{z}_n < \tilde{z}_f$, that is, product market frictions impede the technology upgrade.
%\end{enumerate}
%\end{result}
\begin{proof}
Uniqueness follows from
\begin{equation*}
    \frac{\partial \pi_0 (z)}{\partial z} = (1 - \xi)\frac{\partial \pi_1 (z)}{\partial z}, \qquad \forall z \in Z,
\end{equation*}
and monotonicity under both the cases with and without frictions.

We can solve for the analytical expression for $\tilde{z}_n$:
\begin{equation*}
    \tilde{z}_n = \frac{R k_E}{\xi \left( \Omega \kappa^{\gamma} - \frac{1}{1-\alpha} \kappa \right)}.
%\label{eq:zn}
\end{equation*}
%where $z_n$ is simply the ``distance'' ($R k_E$) over ``speed'' ($\phi \left[ \Omega \kappa^{\gamma} - \frac{1}{1-\alpha} \kappa \right]$). The ``distance'' in both cases are the same, so eventually whether $z_f$ lies left or right to $z_n$ depends on the ``speed'' of convergence.

Using expressions of the profits functions with correlated distortions and recall that $\phi_1 < 0$, we can show that
\begin{equation*}
%\label{eq:zf}
    \tilde{z}_n = \frac{R k_E}{\xi \left( \Omega\kappa^{\gamma} - \frac{1}{1-\alpha}\kappa \right)} < \left[\frac{R k_E}{\xi \left( \Omega\kappa^{\gamma} - \frac{1}{1-\alpha}\kappa \right)}\right]^{\frac{1-\gamma}{1-\gamma+\phi_1}} = \tilde{z}_f,
\end{equation*}
which proves the proposition.

One caveat is that the second inequality holds only if the number in the parentheses is greater than 1. We verify this in our quantitative analysis but restrain ourselves from discussing extreme cases where the condition is not hold.
\end{proof}
%One caveat with Proposition \ref{prop:friction} is that correlated distortions also affect the equilibrium wage $W$, which may partially offset the direct impact of distortions on technology adoption. However, in our quantitative analysis, this general equilibrium response is not large enough to invalidate the conclusion of Proposition \ref{prop:friction}.

\subsection{Correlated Distortions and Aggregate Pollution}
\label{sec:appen_proof_pollution}

In this section,  we present a simple one-sector model with a fixed number of firms and \emph{exogenous} firm-level pollution intensity, which is based on \citet{Lucas:1978b}. We then derive the conditions under which removing the progressiveness of the distortions would reduce aggregate pollution, which are summarized in Proposition 2 of the main text. We further show that similar results hold for average pollution intensity in Corollary \ref{prop:intensity_distortion_appen}. We start with a formal description of the model setting.

%In this section, we provide details pertaining to how the simple model is solved and subsequently prove Result \ref{prop:pollution_distortion_appen}. We start with a formal description of the model setting.

\textit{The Model.---}The model contains only the polluting sector. There is a representative household with a continuum of members. A measure one of the members are managers, while a measure $N$ are workers. The occupation of household members are fixed once born. Each manager is endowed with $z$ units of managerial talent, which is drawn from a log-normal distribution $G(z)$ with logarithmic mean and standard deviation $(\mu, \sigma)$. Workers supply one unit of labor inelastically in exchange for wage income, and managers run a neoclassical firms and earn profits. In the simplified economy, labor is the only production factor. We set the final good as the numeraire, and use $W$ to represent wage rate.

The production function is given by
\begin{equation*}
    y = F(z,l) = z^{1-\gamma}l^{\gamma},
\end{equation*}
where as usual, $0<\gamma<1$ is the span-of-control parameter that supports a non-degenerate distribution of firms in the equilibrium.

The production process generates pollutants $e$ as by-products. Here we abstract from the treatment technology choice decision. Firm-level emissions now depend only on production scale $y$:
\begin{equation*}
    e(y) = \psi_0 y^{1+\psi_1},
\end{equation*}
where $-1<\psi_1<1$ captures the negative correlation between output level and emission intensity as documented in Section \rom{1}.B of the main text.

Firm-level distortions take the same form as in the main text:
\begin{equation*}
    \tau_z = 1- \phi_0 z^{\phi_1},
\end{equation*}
where $\phi_1 < 0$ reflects the progressiveness of the distortions.

\textit{Proofs.---}With the above setup, we prove the following results.

\noindent PROOF OF PROPOSITION 2:
\begin{proposition}
\label{prop:pollution_distortion_appen}
In the simple model, there exists a threshold
\begin{equation*}
    \hat{\phi}_1 = \frac{\psi_1(1-\gamma)}{1-\gamma(1+\psi_1)},
\end{equation*}
such that $E$ is increasing in $\phi_1$ when $\phi_1 < \hat{\phi}_1$, and decreasing in $\phi_1$ when $\phi_1 \geq \hat{\phi}_1$.
\end{proposition}

\begin{proof}
Our goal here is to find a relationship between $E$ and $\phi_1$. With no capital, the maximization problem of the firm is
\begin{equation*}
    \pi(z) = \max_{l} \left\{(1-\tau_z)z^{1-\gamma}l^{\gamma} - W l \right\}.
\end{equation*}
The first order condition is
\begin{equation}
\label{eq:lz_simple}
    l(z) = \left( \frac{\gamma \phi_0 z^{1-\gamma+\phi_1}}{W} \right)^{\frac{1}{1-\gamma}}.
\end{equation}
The optimal labor demand leads immediately to output
\begin{equation}
\label{eq:yz_simple}
    y(z) = \left(\frac{\gamma \phi_0}{W} \right)^{\frac{\gamma}{1-\gamma}} z^{\frac{1-\gamma+\gamma\phi_1}{1-\gamma}}.
\end{equation}
We have assumed that
\begin{equation*}
%\label{eq:ey_simple}
    e(y) = \psi_0 y^{1+\psi_1}.
\end{equation*}
Combining this equation with Equation (\ref{eq:yz_simple}), we get the pollution of firm-$z$
\begin{equation}
\label{eq:ez_simple}
    e(z) = \psi_0 \left(\frac{\gamma \phi_0}{W} \right)^{\frac{\gamma(1+\psi_1)}{1-\gamma}}z^{\left(1+\frac{\gamma\phi_1}{1-\gamma} \right)(1+\psi_1)}.
\end{equation}
With Equation (\ref{eq:ez_simple}), all that remains is to compute the integral
\begin{align}
\label{eq:agge_simple}
    E &= \int e(z)dG(z) \nonumber \\
      &= \psi_0 \left(\frac{\gamma \phi_0}{W} \right)^{\frac{\gamma(1+\psi_1)}{1-\gamma}}\int z^{\left(1+\frac{\gamma\phi_1}{1-\gamma} \right)(1+\psi_1)} dG(z).
\end{align}
In Equation (\ref{eq:agge_simple}), we need to solve for closed-form expression for $W$ and the integral.

Recall that if $z \sim \text{Lognormal}(\mu,\sigma^2)$, $z^a \sim \text{Lognormal}(a\mu,a^2\sigma^2)$ for $a\neq 0$. Hence
\begin{equation}
\label{eq:agge_inte}
    \int z^{\left(1+\frac{\gamma\phi_1}{1-\gamma} \right)(1+\psi_1)} dG(z) = \exp\left\{\left(1+\frac{\gamma\phi_1}{1-\gamma} \right)(1+\psi_1)\mu + \frac{1}{2}\left(1+\frac{\gamma\phi_1}{1-\gamma}\right)^2(1+\psi_1)^2\sigma^2) \right\}.
\end{equation}
We use the labor market clearing condition
\begin{equation*}
    \int l(z)dG(z) = N,
\end{equation*}
to solve for wage $W$. In particular, by substituting Equation (\ref{eq:lz_simple}) in the labor market clearing condition, and using the property of log-normal distribution, we get
\begin{equation}
\label{eq:labormarket_simple}
    N = \left(\frac{\gamma\phi_0}{W} \right)^{\frac{1}{1-\gamma}}\exp\left\{\left(1+\frac{\phi_1}{1-\gamma}\right)\mu + \frac{1}{2}\left(1+\frac{\phi_1}{1-\gamma} \right)^2\sigma^2  \right\}.
\end{equation}

Substitute Equations (\ref{eq:agge_inte}) and (\ref{eq:labormarket_simple}) back to Equation (\ref{eq:agge_simple}), after some quite involved algebra, aggregate pollution can be written as
\begin{equation}
\label{eq:agge_phi1}
    E = \Omega \exp\left\{\frac{(1+\psi_1)\gamma}{1-\gamma}\frac{\sigma^2}{2}\left[2\psi_1\phi_1 + \frac{(1+\psi_1)\gamma-1}{1-\gamma}\phi_1^2 \right] \right\},
\end{equation}
where
\begin{equation*}
    \Omega = \psi_0 N^{\gamma(1+\psi_1)}\exp\left\{(1+\psi_1)\left[(1-\gamma+\psi_1)\frac{1}{2}\sigma^2 + (1-\gamma)\mu \right] \right\},
\end{equation*}
is a constant independent of $\phi_1$. Notice that inside the bracket in Equation (\ref{eq:agge_phi1}) is a parabola opening to the bottom. Importantly, the axis of the parabola is
\begin{equation}
\label{eq:phi1hat}
    \phi_1 = \frac{\psi_1(1-\gamma)}{1-\gamma(1+\psi_1)} \triangleq \hat{\phi}_1.
\end{equation}
Proposition \ref{prop:pollution_distortion_appen} thus follows immediately.
\end{proof}

Notice that by Equation (\ref{eq:yz_simple}),
\begin{equation*}
    Y = \int y(z)dG(z) = \int \left(\frac{\gamma \phi_0}{W} \right)^{\frac{\gamma}{1-\gamma}} z^{\frac{1-\gamma+\gamma\phi_1}{1-\gamma}} dG(z).
\end{equation*}
Using again the labor market clearing condition (\ref{eq:labormarket_simple}) and the property of log-normal distribution, we have
\begin{equation}
\label{eq:aggy_simple}
    Y = N^{\gamma} \exp\left\{(1-\gamma)\left(\mu+\frac{\sigma^2}{2} \right) \right\}\exp\left\{-\frac{\gamma}{1-\gamma}\frac{\sigma^2}{2}\phi_1^2 \right\}.
\end{equation}
We see from Equation (\ref{eq:aggy_simple}) that $Y$ is always decreasing in $\phi_1$. This echoes the finding in the literature that correlated distortions lead to losses in output by misallocation.

\noindent PROOF OF COROLLARY \ref{prop:intensity_distortion_appen}:
\begin{corollary}
\label{prop:intensity_distortion_appen}
In the simple model, the relationship between the average pollution intensity $E/Y$ and the progressiveness of the distortions $\phi_1$ is such that
\begin{enumerate}[(i)]
    \item
    when $\psi_1 < (1-2\gamma)/\gamma$, the average pollution intensity is always increasing in $\phi_1$;
    \item
    when $\psi_1 \geq (1-2\gamma)/\gamma$, there exists a threshold
    \begin{equation*}
        \overline{\phi}_1 = \frac{(1+\psi_1)(1-\gamma)}{1-2\gamma+\gamma\psi_1},
    \end{equation*}
    such that when $\phi_1 < \overline{\phi}_1$, $E/Y$ is increasing in $\phi_1$; and when $\phi_1 \geq \overline{\phi}_1$, $E/Y$ is decreasing in $\phi_1$;
    \item
    $\overline{\phi}_1$ is increasing in both $\psi_1$ and $\gamma$;
    \item
    $\overline{\phi}_1 < \hat{\phi}_1$.
\end{enumerate}
\end{corollary}
\begin{proof}
The proof is almost the same as that of Proposition \ref{prop:pollution_distortion_appen}. By Equations (\ref{eq:agge_phi1}) and (\ref{eq:aggy_simple}), and again some pretty involved algebra, we can write the average pollution intensity as
\begin{equation}
\label{eq:aggi_phi1}
    \frac{E}{Y} = \Gamma\exp\left\{\frac{\gamma}{1-\gamma}\frac{\sigma^2}{2}\left[2\psi_1(1+\psi_1)\phi_1 + \frac{\psi_1(2\gamma-1+\psi_1\gamma)}{1-\gamma}\phi_1^2 \right] \right\},
\end{equation}
where like before, $\Gamma$ is a constant independent of $\phi_1$.

Notice that once again, inside the bracket in Equation (\ref{eq:aggi_phi1}) is a parabola. When $\psi_1 < (1-2\gamma)/\gamma$, its opening is to the top, and hence the intensity is always increasing in distortions $\phi_1$. On the other hand, when $\psi_1 \geq (1-2\gamma)/\gamma$, the parabola is opening to the bottom with the axis being
\begin{equation}
\label{eq:phi1bar}
    \phi_1 = \frac{(1+\psi_1)(1-\gamma)}{1-2\gamma+\gamma\psi_1} \triangleq \overline{\phi}_1,
\end{equation}
which gives us items (ii) and (iii) of Corollary \ref{prop:intensity_distortion_appen} immediately. Straight forward comparison of Equations (\ref{eq:phi1hat}) and (\ref{eq:phi1bar}) yield item (iv).
\end{proof}

\textit{Remark.---}Notice that, if we assume alternatively that firm-level pollution emission is a function of its productivity $z$:
\begin{equation*}
    \frac{e}{y} = \psi_0 z^{\psi_1},
\end{equation*}
instead of as that in Equation (\ref{eq:ez_simple}), then Equations (\ref{eq:agge_phi1}) and (\ref{eq:aggi_phi1}) become
\begin{equation*}
    E = \Omega \exp\left\{\frac{\gamma}{1-\gamma}\frac{\sigma^2}{2}\left(2\psi_1 \phi_1 - \phi_1^2 \right) \right\},
\end{equation*}
and
\begin{equation*}
    \frac{E}{Y} = \Gamma\exp\left\{\frac{\gamma \psi_1 \sigma^2}{1-\gamma}\phi_1 \right\},
\end{equation*}
respectively.

The two equations imply that first, the average pollution intensity is always increasing in distortions; and second, aggregate pollution is increasing in distortions, as long as the elasticity of distortions to productivity $|\phi_1|$ is larger than that of pollution $|\psi_1|$. Intuitively, this simply says that when output is more responsive to firm size, it dominates the effect of firm-level pollution intensity. Put differently, the scale effect dominates the technique effect.

\subsection{Monopolistic Competition}
\label{sec:appen_proof_melitz}

In this section, we show that our results carry through to the setting of monopolistic competition, or a closed-economy version of \citet{Melitz:2003}. The crucial elements of our analysis are the following. First, in the equilibrium, there needs to be a non-degenerated distribution of firms with different levels of productivity. Second, the model should feature resource allocation along the extensive margin and intensive margin, where we refer to the selection of firms into production as the extensive margin, and the distribution of factors among active firms as the intensive margin. Mathematically, what we really need is decreasing returns to scale in profits which prevents the most productive firm from taking over all the resources in the economy and profits be a function in productivity which creates selection. The curvature could come from decreasing returns to scale in production as in \citet{Lucas:1978b}, or from the demand and market structure as in \citet{Melitz:2003}. We need curvature from one source or the other, but \textit{not} necessarily from both.\footnote{In fact, \citet{Hopenhayn:1992} has directly assumed that the profit function is increasing in productivity [Assumption A.2.(b)] without specifying the underlying mechanism, and \citet{Bartelsmanetal:2013} have assumed diminishing returns in production and utility coexist (page 319).} To ease the exposition, we first show the equivalence using only the backbone elements with no distortions or emissions. We then show that a similar version of Proposition \ref{prop:pollution_distortion_appen} holds under the monopolistic competition structure as well.

%In this section, we show that our results carry through to the setting of monopolistic competition. For the purpose of our analysis, the crucial elements are the following. First, in the equilibrium, there needs to be a non-degenerated distribution of firms with different level of productivity. Second, the model should feature resource allocation along the extensive margin and intensive margin, where as in the main text, we refer to the selection of firms into production as the extensive margin, and the distribution of production among active firms as the intensive margin. From a mathematical point of view, what we really need are decreasing returns to scale in profits which prevents the most productive firms from taking up all the market, and profits be a function in productivity which creates selection. Whether they are caused by decreasing returns to scale in production as in the \citet{Lucas:1978b} case or decreasing marginal utility in preference as in the \citet{Melitz:2003} case is irrelevant, as long as the corresponding parameters are disciplined with the same data.\footnote{In fact, \citet{Hopenhayn:1992} has directly assumed that the profit function is increasing in productivity [Assumption A.2.(b)] without specifying the underlying mechanisms, and \citet{Bartelsmanetal:2013} have assumed diminishing returns in production and utility coexist (page 319).} To ease the exposition, we first the equivalence using only the backbone elements with no distortions and emissions. We then show that a similar version of Result \ref{prop:pollution_distortion_appen} holds under the monopolistic competition structure as well.

\textit{Diminishing Returns to Scale and to Utility.---}The model differs from the \citet{Lucas:1978b} span-of-control model in three aspects: the production function is linear, the utility function is a CES aggregation of a continuum of varieties, and the market structure is monopolistic competition. Specifically, there is still a representative household with a continuum of members. The representative household derives utility from consuming a continuum variety of goods $\omega$ aggregated according to a CES function:
\begin{equation*}
    U = \left[\int_{\omega \in \Omega} q(\omega)^{\frac{\rho-1}{\rho}}d\omega \right]^{\frac{\rho}{\rho-1}},
\end{equation*}
where $\Omega$ is the set of available varieties, $q(\omega)$ is the quantity consumed for each variety $\omega$, and $\rho > 1$ is the elasticity of substitution.

Each household member is once again endowed with $z$ units of managerial talent, where $z \sim G(z)$. Household members choose between running a firm or working as a worker. Labor is the only production factor, which the firm hires at wage $W$ to produce a unique variety. Each variety is produced by only one firm. The production function of the firm is given as
\begin{equation}
\label{eq:melitz_production}
    y = F(z,l) = zl.
\end{equation}
Because firms now have market power, they can set the price of good $p(\omega)$ as well. Since $z$ and $\omega$ can both uniquely identify a firm in our setting, from now on, we will use $z$ to refer to different varieties as well. Therefore, price is now written as $p(z)$, and $y = q(z) = zl$. Likewise, the set $\Omega$ is the same set of active firms, which anticipating the results later, is interval $[\hat{z}, \overline{z}]$ where as before $\hat{z}$ is the threshold of selection into production.

The profit maximization problem of the firm now becomes
\begin{equation}
\label{eq:melitz_firm}
    \max_{\{p(z), q(z)\}} \left\{p(z)q(z) - Wl \right\}.
\end{equation}
To solve (\ref{eq:melitz_firm}), we need to solve for the demand function for each variety $z$ by the household. Standard results from \citet{DixitStiglitz:1977} lead to
\begin{equation*}
%\label{eq:qwithI}
    q(z) =Q \left[\frac{p(z)}{P} \right]^{-\rho},
\end{equation*}
where
\begin{equation*}
   P = \left[\int_{\hat{z}}^{\overline{z}} p(z)^{1-\rho}dz \right]^{\frac{1}{1-\rho}},
\end{equation*}
and
\begin{equation*}
   Q = \left[\int_{\hat{z}}^{\overline{z}} q(z)^{\frac{\rho-1}{\rho}}dz \right]^{\frac{\rho}{\rho-1}},
\end{equation*}
are the price and quantity of the composite good, respectively.
%\begin{lemma}
%\label{lemma:dixit}
%The optimization problem of the household is equivalent to the optimal consumption bundle problem with total expenditure $P \cdot Q$, where
%\begin{equation*}
%    P = \left[\int_{\hat{z}}^{\overline{z}} p(z)^{1-\rho}dz \right]^{\frac{1}{1-\rho}},
%\end{equation*}
%and
%\begin{equation*}
%    Q = \left[\int_{\hat{z}}^{\overline{z}} q(z)^{\frac{\rho-1}{\rho}}dz \right]^{\frac{\rho}{\rho-1}},
%\end{equation*}
%are the price and quantity of the composite good.
%\end{lemma}
%\begin{proof}
%Our proof follows the same spirit as \citet{DixitStiglitz:1977}. In particular, if we write the household optimization problem as
%\begin{align*}
%    & \max_{q(z)}\left[\int_{\hat{z}}^{\overline{z}} q(z)^{\frac{\rho-1}{\rho}}dz \right]^{\frac{\rho}{\rho-1}} \\
%    & s.t. \\
%    & \qquad \int_{\hat{z}}^{\overline{z}} p(z)q(z)dz \leq I,
%\end{align*}
%then it suffices to show that at the optimum, $I = P\cdot Q$.

%The Lagrangian of the problem is
%\begin{equation*}
%    \mathcal{L} = \left[\int_{\hat{z}}^{\overline{z}} q(z)^{\frac{\rho-1}{\rho}}dz \right]^{\frac{\rho}{\rho-1}} + \lambda \left[I - \int_{\hat{z}}^{\overline{z}} p(z)q(z)dz \right],
%\end{equation*}
%where $\lambda$ the multiplier. Assuming that the dominated convergence theorem holds, the derivative of $\mathcal{L}$ with respect to $q(z)$ is
%\begin{equation}
%\label{eq:lagrangian_foc}
%    \frac{\partial \mathcal{L}}{\partial q(z)} = \frac{\rho}{\rho -1}\left[\int_{\hat{z}}^{\overline{z}} q(z)^{\frac{\rho-1}{\rho}} \right]^{\frac{1}{\rho-1}}\frac{\rho-1}{\rho}q(z)^{-\frac{1}{\rho}} - \lambda p(z) = 0.
%\end{equation}
%Integrating Equation (\ref{eq:lagrangian_foc}) with respect to $z$, and substituting in household's budget constraint with equality, we have
%\begin{equation*}
%    Q = \left[\int_{\hat{z}}^{\overline{z}} q(z)^{\frac{\rho-1}{\rho}}dz \right]^{\frac{\rho}{\rho-1}} = \lambda I,
%\end{equation*}
%meaning that $\lambda = Q/I$. Substitute $\lambda$ back to Equation (\ref{eq:lagrangian_foc}), we get
%\begin{equation}
%\label{eq:qwithI}
%    q(z) = \left[\frac{p(z)}{I} \right]^{-\rho} \left[\int_{\hat{z}}^{\overline{z}} q(z)^{\frac{\rho-1}{\rho}}dz \right]^{\-\rho},
%\end{equation}
%which together with the definition of $P$, leads to $I = P\cdot Q$.
%\end{proof}
If we set the composite good to be the numeraire, i.e., $P=1$, then
%\begin{equation*}
%    P = \left[\int_{\hat{z}}^{\overline{z}} p(z)^{1-\rho}dz \right]^{\frac{1}{1-\rho}} = 1.
%\end{equation*}
% Equation (\ref{eq:qwithI}) immediately leads to the demand function of the household
\begin{equation}
\label{eq:melitz_demand}
    q(z) = Q[p(z)]^{-\rho}.
\end{equation}

Notice that the production function (\ref{eq:melitz_production}) means that $l = q(z)/z$. With Equation (\ref{eq:melitz_demand}), firm's problem (\ref{eq:melitz_firm}) is equivalent to
\begin{equation*}
    \max_{p(z)} Q \left[p(z)^{1-\rho} - W\frac{p(z)^{-\rho}}{z} \right],
\end{equation*}
where the first order condition directly leads to optimal labor demand
\begin{equation}
\label{eq:melitz_labor}
    l(z) = Q\left(\frac{W\rho}{\rho-1} \right)^{-\rho}z^{\rho-1},
\end{equation}
and profit
\begin{equation}
\label{eq:melitz_profit}
    \pi(z) = \frac{Q}{\rho}\left(\frac{\rho-1}{\rho} \right)^{\rho-1}z^{\rho-1}.
\end{equation}
We see that both (\ref{eq:melitz_labor}) and (\ref{eq:melitz_profit}) are increasing in $z$. This means that with a non-degenerate distribution of $z$, $l$ and $\pi$ are also non-degenerate. Further, Equation (\ref{eq:melitz_labor}) implies that if $l$ is log-normally distributed, $z$ will also be log-normally distributed, leaving us with a similar calibration strategy for $G(z)$ as in the main text. In addition, because (\ref{eq:melitz_profit}) implies that $\pi(0) = 0$, the selection threshold $\hat{z}$ is also determined by
\begin{equation}
\label{eq:melitz_selection}
    \pi(\hat{z}) = W.
\end{equation}
Recall that in the \citet{Lucas:1978b} model, the counterparts of (\ref{eq:melitz_labor}) and (\ref{eq:melitz_profit}) are respectively
\begin{equation*}
    l(z) = \left(\frac{\gamma}{W} \right)^{\frac{1}{1-\gamma}}z,
\end{equation*}
and
\begin{equation*}
    \pi(z) = \left[\left(\frac{\gamma}{W}\right)^{\frac{\gamma}{1-\gamma}} - W\left(\frac{\gamma}{W} \right)^{\frac{1}{1-\gamma}} \right]z,
\end{equation*}
and Equation (\ref{eq:melitz_selection}) stays the same, it can be seen that the two models are equivalent, with the elasticity of substitution $\rho$ in the monopolistic setting plays the same role as the span-of-control parameter $\gamma$. In fact, in the \citet{Lucas:1978b} model, one can think of firms as earning rents over the managerial talent $z$.

\textit{Monopolistic Competition and Aggregate Pollution.---}With the above notation, we now bring back the distortions
\begin{equation*}
    \tau_z = 1-\phi_0 z^{\phi_1},
\end{equation*}
and further assume that firm level emissions are given by
\begin{equation*}
    e(z) = \psi_0 [p(z)q(z)]^{1+\psi_1}.
\end{equation*}
We shut down the selection margin $\hat{z}$ as in Section \ref{sec:appen_proof_pollution} by assuming that a measure one of the household members are born as managers and a measure $N$ of them are born as workers. Following the same steps in the proofs of Proposition \ref{prop:pollution_distortion_appen}, we can show that the aggregate pollution in the monopolistic competition case can be shown as
\begin{equation*}
    E = \Gamma_1 \exp\left\{ -\frac{\sigma^2}{2}[2\rho - \psi_1(\rho-1)^2]\phi_1^2 + \left[\mu - 2[\rho - \psi_1 (\rho-1)^2] \right] \right\},
\end{equation*}
where $\Gamma_1$ is a constant. The expression indicates that there again exists a threshold
\begin{equation*}
    \hat{\phi}_1 = -1 + \frac{\rho-\mu/\sigma^2}{2\rho - \psi_1(\rho-1)^2},
\end{equation*}
such that $E$ is decreasing in $\phi_1$ when $\phi_1 > \hat{\phi}_1$, and increasing in $\phi_1$ when $\phi_1 < \hat{\phi}_1$.

Similarly, the aggregate output in the monopolistic competition case is
\begin{equation*}
    Q = N \exp \left\{\mu+\frac{\sigma^2}{2}(\rho-1)-\frac{\sigma^2}{2}\rho\phi_1^2 \right\},
\end{equation*}
which is decreasing in the progressiveness of distortions $-\phi_1$. The impact of distortions on aggregate output in this case is equivalent to that in the Lucas span-of-control case of Section \ref{sec:appen_proof_pollution} [Equation (\ref{eq:aggy_simple})].%, as long as we create a one-to-one mapping between the elasticity of substitution among varieties $\rho$ in \citet{Melitz:2003} and the span-of-control parameter $\gamma$ in \citet{Lucas:1978b}.

\subsection{Uncorrelated Distortions}
\label{sec:uncorrelated}

In the main text, we focus on correlated distortions, which increase in firm TFP. However, as can be seen from Figure \ref{fig:phiklkappa},  there are also substantial variations in average products across firms with the same TFP level.\footnote{We thank a referee for pointing this out.} In the language of \citet{RestucciaRogerson:2008}, these variations suggest the existence of \emph{uncorrelated} distortions, which are uncorrelated with firm TFP. In this section, we use the same model in Section \ref{sec:appen_proof_pollution}, except that the firm-level distortions are uncorrelated with firms' productivity $z$, to study the impact of uncorrelated distortions on aggregate output and pollution. We find that unlike the case of correlated distortions, uncorrelated distortions lower both aggregate output and aggregate pollution.

The uncorrelated distortions are defined as an output tax whose rate $\tau$ is randomly drawn and independent of firm productivity $z$. Specifically, $z$ is drawn from a log-normal distribution $G(z)$ with log mean and standard deviation $(\mu_z, \sigma_z)$, and $1-\tau$ is independently drawn from another log-normal distribution $H(\tau)$ with log mean and standard deviation $(\mu_{\tau}, \sigma_{\tau})$.

The firm's profit maximization problem can be written as
\begin{equation*}
    \pi(z,\tau) = \max_{l} \left\{ (1-\tau) z^{1-\gamma} l^{\gamma} - Wl  \right\}.
\end{equation*}
First-order conditions yield
\begin{align}
    l(z,\tau) &= \left[\frac{\gamma(1-\tau)}{W}\right]^{\frac{1}{1-\gamma}}z, \nonumber \\
    \label{eq:output_un}
    y(z,\tau) &= \left[\frac{\gamma(1-\tau)}{W}\right]^{\frac{\gamma}{1-\gamma}}z, \\
    e(z,\tau) &= \psi_0 \left[\frac{\gamma(1-\tau)}{W}\right]^{\frac{\gamma(1+\psi_1)}{1-\gamma}}z^{1+\psi_1}. \nonumber
\end{align}
The labor market clearing condition
\begin{equation*}
    \iint l(z,\tau)dG(z)dH(\tau) = N,
\end{equation*}
leads to
\begin{equation}
\label{eq:labor_market_un}
    N = \left(\frac{\gamma}{W}\right)^{\frac{1}{1-\gamma}} \exp\left\{\frac{\mu_\tau}{1-\gamma}+\frac{\sigma_\tau^2}{2(1-\gamma)^2}\right\} \exp\left\{\mu_z+\frac{\sigma_z^2}{2}\right\}.
\end{equation}

Combining Equations (\ref{eq:output_un}) and (\ref{eq:labor_market_un}), we can compute the aggregate output for this economy
\begin{align*}
    Y   &= \iint y(z,\tau)dG(z)dH(\tau) \\
        &= N^{\gamma} \exp\left\{(1-\gamma)\left(\mu_z+\frac{\sigma_z^2}{2}\right)\right\} \exp\left\{-\frac{\gamma \sigma_\tau^2}{2(1-\gamma)}\right\}.
\end{align*}
Consistent with the results in \citet{HsiehKlenow:2009}, aggregate output $Y$ is decreasing in the dispersion of firm-level distortions $\sigma_\tau^2$.

Similarly, the aggregate emissions can be written as
\begin{equation*}
    E = \Omega(\psi_0, \psi_1, \mu_z, \sigma_z, \mu_{\tau}, N) \exp\left\{\frac{[\gamma (1+\psi_1)]^2-\gamma (1+\psi_1)}{2(1-\gamma)^2}\sigma_\tau^2\right\},
\end{equation*}
where $\Omega(\psi_0,\psi_1,\mu_z,\sigma_z,\mu_{\tau},N)$ is a constant independent of the dispersion of distortions. Since $\gamma<1$ and $\psi_1<0$, $E$ is also decreasing in the dispersion of firm-level distortions $\sigma_\tau^2$.

\section{Additional Discussions on the Environmental Economics Literature}
%\section{Additional Summary of the Environmental Economics Literature}

In this section, we explain in greater details the differences between our paper and the literature on how international trade affects the environment through the reallocation across heterogeneous firms. Specifically, our paper differs from this literature in following ways. First, we bring our general equilibrium model to firm-level data directly, and provide a quantitative assessment of counterfactual policies using an internally-consistent model disciplined by firm-level data. Second, using the firm-level data on treatment technologies, we provide an explanation for the negative correlation between firm size and pollution intensity. Our model also has different implications for the impact of environmental regulations, due to the different nature of the distortions in our paper and the trade costs emphasized by the literature.
%In this section, we further explain the difference between our paper and most empirical trade studies summarized in \citet{Cherniwchanetal:2017}. In the main text, we mentioned that our paper differs from this literature in three broad ways. First is that our model has different implications on resource allocation along the intensive margin under the policy-relevant scenario of changing environmental regulation while keeping distortions fixed. Second, the fact we can observe emissions and treatment equipment directly in the data allows us to identify how distortions and firm size affect pollution through a specific channel, that is the upgrade of treatment technology induced by increasing revenues. Third, the quantitative nature of our model allows us to study the aggregate impact of policies. In this section, we try to explain these difference in greater details.

\textit{Quantitative General Equilibrium.---}Most studies in this literature focus on reduced-form analysis, in which the model is used to motivate the empirical analysis indirectly. See for example, \citet{Martin:2013}, \citet{Cherniwchan:2017}, \citet{Forslidetal:2015}, and \citet{BarrowsOllivier:2016}, among others. Some studies, such as \citet{Andersen:2016}, \citet{Holladay:2016} and \citet{Forslidetal:2015} derive qualitative predictions under strong parametric assumptions, but do not bring their models to the data directly. Instead, we provide a quantitative assessment of counterfactual policies using an internally-consistent model disciplined by firm-level data. Our quantitative analysis explicitly takes into account the general equilibrium effects of alternative policies, and it provides novel policy implications that are absent from either reduced-form or partial equilibrium analysis.  The quantitative nature makes our analysis suitable for evaluating alternative policies. First, it allows us to quantify  the trade-off between the technique and scale effects, that is, whether a reduction in pollution intensity couples with an increase in output would lead to an increase in aggregate pollution. This is important for our paper because the removal of distortions necessarily leads to increase in output and decrease in pollution intensity. Second, while the reduced-form analysis is able to identify how individual firm responds to changes in economic environment [for instance \citet{Cherniwchan:2017}], the aggregation of these responses would result in general equilibrium feedback that is more appropriately studied using a quantitative general equilibrium framework.

\textit{Technology Adoption.---}A unique feature of our data is that we observe both the emissions and treatment technologies at the firm level. Using the data on treatment technologies, we provide an explanation for the negative correlation between firm size and pollution intensity. It allows us to not only investigate the overall effects of distortions, but also quantify an important channel through which the distortions affect emissions, namely, the adoption of clean technology. This differentiates our paper from empirical work such as \citet{Andersen:2016} and \citet{Holladay:2016}. Specifically, \citet{Andersen:2016} studies the effects of credit constraints on pollution using regional data, which provides only indirect evidence on the firm behavior. While \citet{Holladay:2016} shows that on average exporters tend to be cleaner, but does not provide an explanation for this fact. %It also differentiates our work from \citet{ShapiroWalker:2015}, where environmental regulation works as a residual (and hence can include a wide range of factors) to match the model with the data.
One exception is \citet{BarrowsOllivier:2016}, which uses product-level data to study how trade liberalization affects pollution through the shift in the product-mix of exporting firms. Our paper differs from theirs by our focus on a completely different channel.

\textit{Implications for Environmental Regulations.---}The implication of our model for environmental regulations distinguishes us from studies that emphasize the role of trade costs, most of which build their models on the \citet{Melitz:2003} model. A major difference between the distortions in our model and the trade costs in an open-economy Melitz model is that exporting is an endogenous choice of firms which brings extra revenues.\footnote{In Section \ref{sec:appen_proof_melitz}, we establish the qualitative equivalence between the effects of distortions on aggregate output and pollution in \citet{Lucas:1978b}, and those in the \emph{closed-economy} version of \citet{Melitz:2003}.}A productive firm can choose not to pay the trade costs if it decides to stay domestic, while the distortions in our model are imperative and are purely deadweight losses. In addition, they interact with environmental regulations in different ways. In our model, environmental regulations would worsen resource allocation along the intensive margin, but this is not necessarily the case with trade costs, because the productive exporting firms can use foreign markets as a cushion to buffer the burdens from environmental regulations after paying the trade costs. We believe that such differences are policy-relevant, because in many cases environmental authorities have to make policy decisions in the presence of distortions.

%\textit{Intensive Margin.---}Most studies in this literature build their models based on the \citet{Melitz:2003} model. As is shown by \citet{HsiehKlenow:2009}, whether technically a non-degenerate distribution of firms are generated using a \citet{Melitz:2003} or \citet{Lucas:1978b} framework is irrelevant. Hence, our choice of \citet{Lucas:1978b} model following the macro literature does not lead to the difference in model implications. Rather, it is because trade costs in the \citet{Melitz:2003} model is associated with additional revenues from selling in foreign markets, but the distortions in our model are pure deadweight loss. It is this difference in the nature of distortions that leads to different implications. Put differently, the key here is whether firms have a choice over taking these costs or not. We think such difference in policy-relevant, because in many cases, environmental authorities do not have policy instruments to reduce economic distortions, and it is important to be able to evaluate the potential impacts of regulatory policies in these scenarios.

%\textit{A Specific Channel.---}A unique feature of our data is that we observe both the emissions and treatment technology, this allows us to quantify the environmental consequences of reducing distortions through a specific channel, that is the upgrade of treatment technology induced by increasing revenues. This differentiates our work from empirical work like \citet{Holladay:2016} and \citet{Andersen:2016}. Specifically, \citet{Holladay:2016} shows that on average, exporters tend to be cleaner, but does not focus on quantifying a particular mechanism; while \citet{Andersen:2016} studies the effect of credit constraints using data at the regional level, which can only provide suggestive evidence on the behavior of firms indirectly. It also differentiates our work from \citet{ShapiroWalker:2015}, where environmental regulation works as a residual (and hence can include a wide range of factors) to match the model with the data.

%This feature of our paper shares a similar spirit with \citet{Bustos:2011} and \citet{BarrowsOllivier:2016}. In particular, \citet{Bustos:2011} has data on firms' investment on technology, allowing her to empirically identify how trade liberalization improves firm-level productivity through technology upgrading. \citet{BarrowsOllivier:2016} exploit information on product-level data to estimate how trade liberalization affects pollution through shifting of the product-mix of exporting firms. Our paper differs from \citet{BarrowsOllivier:2016} in that we are emphasizing on a completely different channel. In addition, carbon emissions in  \citet{BarrowsOllivier:2016} are imputed from intermediate inputs, while pollutants emissions in our data are measured by field staffs.

%\textit{General Equilibrium Implication.---}The general equilibrium, quantitative nature of our paper differs from the literature in two important dimensions. First, it allows us to investigate whether a reduction in pollution intensity couples with a greater increase in output would lead to an increase in aggregate pollution. It is important for us because one of our counterfactual experiment evaluates the impacts from the removal of distortions, which necessarily leads to increase in output. Previous studies usually rely on strong parametric assumptions to derive qualitative predictions, see for instance \citet{Forslidetal:2015}, \citet{Holladay:2016}, and \citet{Andersen:2016}. However, because these models are not taken directly to the data, whether their parametric assumptions actually hold is left unanswered. Instead, in our paper, we take the model to the data directly. Second, although the diff-in-diff type of empirical estimation is able to identify how individual firm responds to changes in economic environment [\citet{Cherniwchan:2017}], the aggregation of these estimated behavior of firms almost certainly would result in general equilibrium feedback that is more appropriately studied using a quantitative general equilibrium model as in our paper.

\section{Computational Algorithm for the Main Model}
\label{sec:compu_main}

This section contains the computational algorithm we use to solve the version of the model in the main text, namely the two-sector model where products from the polluting and non-polluting sectors are perfect substitutes. The model is fairly standard to solve. In the stationary equilibrium, the Euler equation of the household implies that the net interest rate is
\begin{equation}
\label{eq:ss_r}
    R = \frac{1}{\beta} - 1 + \delta.
\end{equation}
As a result, once we find the equilibrium wage $W$, it is straightforward to compute the other allocations in the equilibrium. Specifically, the pseudo-code goes as follows.
\begin{enumerate}
    \item
    Calculate the equilibrium interest rate by Equation (\ref{eq:ss_r}).
    \item
    Find the equilibrium wage $W$. This includes the following steps.
    \begin{enumerate}[(a)]
        \item
        Make an initial guess of $W$.

        \item
        Given $R$ and $W$, for each firm-$z$ in both the polluting and non-polluting sectors, we can solve for their profit functions $\pi^d(z)$ and $\pi^c(z)$. Specifically, the first order conditions of firms in the non-polluting sector are given by
        \begin{align*}
            & (k): \qquad \alpha \gamma (1-\tau_z)z^{1-\gamma} k^{\alpha \gamma-1} l^{(1-\alpha)\gamma} = R, \\
            & (l): \qquad (1-\alpha)\gamma(1-\tau_z)z^{1-\gamma}k^{\alpha \gamma} l^{(1-\alpha)\gamma-1} = W.
        \end{align*}
        With the optimal factor demand $k(z)$ and $l(z)$, the profit function of firms in the non-polluting sector is given by
        \begin{equation*}
            \pi^c(z) = (1-\tau_z) z^{1-\gamma}[k(z)^{\alpha}l(z)^{1-\alpha}]^{\gamma} - Wl(z) - Rk(z).
        \end{equation*}
        \item
        Notice that the first order conditions of firms in the polluting sector are similar, hence we can at the same time solve the potential profits of polluting firms using dirty and clean technologies $\pi^d_0(z)$ and $\pi^d_1(z)$:
        \begin{align*}
            \pi^d_0(z) &= (1-\xi)\{(1-\tau_z) z^{1-\gamma}[k(z)^{\alpha}l(z)^{1-\alpha}]^{\gamma} - Wl(z) - Rk(z)\}, \\
            \pi^d_1(z) &= (1-\tau_z) z^{1-\gamma}[k(z)^{\alpha}l(z)^{1-\alpha}]^{\gamma} - Wl(z) - R[k(z)+k_E].
        \end{align*}

        \item
        Now $\pi^d_0(z),\pi^d_1(z)$ and $\pi^c(z)$ can be used to pin down the thresholds for occupational choices $\{\hat{z}_c,\hat{z}_d\}$ and technology adoption $\tilde{z}_d$. In particular,
        \begin{equation*}
            \pi^d(z) = \max\{\pi^d_0(z),\pi^d_1(z)\},
        \end{equation*}
        and $\hat{z}^j$s are such that
        \begin{equation*}
            W = \pi^j(\hat{z}_j), \qquad j = c,d.
        \end{equation*}
        When $\pi^d_0(z)$ and $\pi^d_1(z)$ satisfy single-crossing condition,
        \begin{equation*}
            \tilde{z}_d = \min_z \{z \in [\hat{z}_d,\overline{z}] | \pi^d_0(z) < \pi^d_1(z) \}.
        \end{equation*}
        Notice that now for the polluting sector, $\hat{z}_d$ and $\tilde{z}_d$ define two groups of firms: those that use dirty technology $z \in [\hat{z}_d, \tilde{z}_d]$, and those that use clean technology $z \in [\tilde{z}_d,\overline{z}]$.

        \item
        If the labor market clearing condition
        \begin{equation*}
            \mu G(\hat{z}_d) + (1-\mu) G(\hat{z}_c) = \mu \int_{\hat{z}_d}^{\overline{z}} l^d(z)dG(z) + (1-\mu)\int_{\hat{z}_c}^{\overline{z}} l^c(z)dG(z),
        \end{equation*}
        does not hold, return to Step 2.(a) and update the guess for $W$.
    \end{enumerate}

    \item
    With the equilibrium prices $W$ and $R$, all the allocations of the economy can be computed following Definition 1 in the main text.
\end{enumerate}

By Walras' Law, if the household budget constraint, capital, and labor market clearing conditions all hold, resource constraint is automatically satisfied. We now verify that this is the case. To simplify notation, first let us define
\begin{equation*}
    \overline{\pi}(z) = (1-\tau_z)z^{1-\gamma}(k^{\alpha}l^{1-\gamma})^{\gamma} - Wl - Rk,
\end{equation*}
and
\begin{equation*}
    y(z) = z^{1-\gamma}(k^{\alpha}l^{1-\alpha})^{\gamma},
\end{equation*}
where the optimal factor demands are implicitly substituted in. Government tax revenue $T$ comes from two sources here: from taxing firms using dirty technology
%where we have assumed that the optimal factor demands are implicitly substituted in. Government tax revenue $T$ comes from two sources here: from taxing firms using dirty technology
\begin{equation*}
    \mu \xi \int_{\hat{z}_d}^{\tilde{z}_d} \overline{\pi}(z)dG(z),
\end{equation*}
and from output taxes $\tau_z$
\begin{equation*}
    \mu \int_{\hat{z}_d}^{\overline{z}} \tau_z y(z)dG(z) + (1-\mu)\int_{\hat{z}_c}^{\overline{z}}\tau_z y(z)dG(z).
\end{equation*}
Recall that we have assumed that all taxes are rebated to the household as lump-sum transfers. Hence with these notations, household income $I$ is given by
\begin{align}
\label{eq:hh_income}
    I &= R K + W [\mu G(\hat{z}_d)+(1-\mu)G(\hat{z}_c)] + T \nonumber \\
      & \qquad + \mu\left[\int_{\hat{z}_d}^{\tilde{z}_d} \pi^d_0(z) dG(z) + \int_{\tilde{z}_d}^{\overline{z}} \pi^d_1(z)dG(z)\right] + (1-\mu)\int_{\hat{z}_c}^{\overline{z}}\pi^c(z)dG(z) \nonumber \\
      &= R K + W [\mu G(\hat{z}_d)+(1-\mu)G(\hat{z}_c)] + T + (1-\mu)\int_{\hat{z}_c}^{\overline{z}}\overline{\pi}(z)dG(z) \nonumber \\
      & \qquad + \mu\left[(1-\xi)\int_{\hat{z}_d}^{\tilde{z}_d} \overline{\pi}(z) dG(z) + \int_{\tilde{z}_d}^{\overline{z}} \overline{\pi}(z)dG(z) - R k_E [G(\overline{z}) - G(\tilde{z})]\right] \nonumber \\
      &= R K + W [\mu G(\hat{z}_d)+(1-\mu)G(\hat{z}_c)] + (1-\mu)\int_{\hat{z}_c}^{\overline{z}}[\overline{\pi}(z)+\tau_z y(z)]dG(z) \\
      & \qquad + \mu\left[\int_{\hat{z}_d}^{\overline{z}} (\overline{\pi}(z)+\tau_z y(z)) dG(z) - R k_E [G(\overline{z}) - G(\tilde{z})]\right]. \nonumber
\end{align}
Because
\begin{equation*}
    K = \mu \left[\int_{\hat{z}_d}^{\overline{z}} k^d(z)dG(z) + k_E [G(\overline{z})-G(\tilde{z}_d)]\right] + (1-\mu)\int_{\hat{z}_c}^{\overline{z}} k^c(z)dG(z),
\end{equation*}
and
\begin{equation*}
    \overline{\pi}(z) = (1-\tau_z)y(z) - Wl(z) - R k(z),
\end{equation*}
substitute these two equations and the labor market clearing condition into Equation (\ref{eq:hh_income}), we get
\begin{equation*}
    I = \mu \int_{\hat{z}_d}^{\overline{z}}y(z)dG(z) + (1-\mu) \int_{\hat{z}_c}^{\overline{z}}y(z)dG(z).
\end{equation*}
Household budget constraint then leads directly to
\begin{equation}
\label{eq:consumption}
    C + \delta K = Y.
\end{equation}
Equation (\ref{eq:consumption}) is used to construct the aggregate consumption.

\section{A Two-Sector Model with CES Aggregation}

In the main text, we have assumed that the goods produced by polluting and non-polluting sectors are perfect substitutes. Admittedly an extreme assumption, it is not critical to our quantitative results in the main text, because the counterfactual experiments there cause little reallocation across sectors. However, if we want to evaluate the effects of removing distortions from one sector only, this assumption is problematic because it would imply a reallocation across sectors that is too large. To address this issue, we build a two-sector model in which the final goods are produced by a representative producer, who combines the intermediate goods from the polluting and non-polluting sectors using a constant elasticity of substitution (CES) production function. We use the model to evaluate the effects of removing distortions from both sectors, and those of removing distortions from the polluting sector {only}. In this section, we first describe the model, and then explain the computational algorithm. In the end, we calibrate the model and report the quantitative results from the counterfactual experiments.

%In the main text, we have assumed that the goods produced by polluting and non-polluting sectors are perfect substitutes. This is clearly an extreme case. While it does not affect any of our results if the distortions to the two sectors are the same. It does make the resource allocation across sectors overly responsive to the relative difference in the level of distortions. To address this issue, we make one change to the model in the main text by introducing a representative neoclassical final good producer. In this section, we first describe the model with the newly introduced final good producer. We then explain the computational algorithm. In the last section, we calibrate the model and report the quantitative results.

\subsection{The Model}

We assume that there is a single final good Y produced by a representative firm in a perfectly competitive final good market. The final good producer manufactures $Y$ by combining the intermediate goods from the polluting sector $Y_d$ and non-polluting sector $Y_c$ respectively. The production function features \textit{constant elasticity of substitution (CES)} between the two goods:
\begin{equation*}
    Y = \left[\varphi (Y_d)^{\frac{\rho-1}{\rho}} + (1-\varphi)(Y_c)^{\frac{\rho-1}{\rho}} \right]^{\frac{\rho}{\rho-1}},
\end{equation*}
where $\rho$ is the elasticity of substitution, $\varphi$ is the average share of polluting goods in production. We assume that the final good $Y$ is the numeraire, and the relative prices of polluting and non-polluting goods are $p_d$ and $p_c$, respectively.\footnote{Notice that this setup is mathematically equivalent to the monopolistic competition setup in Section \ref{sec:appen_proof_melitz}.} The optimization problem of the final good producer is thus
\begin{equation*}
    \max_{Y_d,Y_c} \left\{ \left[\varphi (Y_d)^{\frac{\rho-1}{\rho}} + (1-\varphi)(Y_c)^{\frac{\rho-1}{\rho}} \right]^{\frac{\rho}{\rho-1}} - p_d Y_d - p_c Y_c \right\}.
\end{equation*}
The first order conditions yield
\begin{equation*}
    \frac{Y_d}{Y_c} = \left(\frac{\varphi}{1-\varphi} \cdot \frac{p_c}{p_d} \right)^{\rho}.
\end{equation*}
Since we pick the final good $Y$ as the numeraire, the aggregate price index is
%Using Lemma \ref{lemma:dixit}, the aggregate price index is
\begin{equation}
\label{eq:cesprice}
    \left[ \varphi^{\rho}(p_d)^{1-\rho} + (1-\varphi)^{\rho}(p_c)^{1-\rho} \right]^{\frac{1}{1-\rho}} = 1,
\end{equation}
which implicitly defines a mapping between $p_d$ and $p_c$.

Because now there are relative prices, the optimization problems for firms in the two intermediate goods sectors need to be modified accordingly. In particular, the profit maximization problem for firms in the non-polluting sector is
\begin{equation*}
    \pi^c(z) = \max_{k,l} \left\{ (1-\tau_z)p_c z^{1-\gamma}(k^{\alpha}l^{1-\alpha})^{\gamma} - Wl - Rk \right\},
\end{equation*}
while those for firms in the polluting sector using clean and dirty technologies are given respectively as
\begin{equation*}
    \pi^d_1(z) = \max_{k,l} \left\{ (1-\tau_z) p_d z^{1-\gamma} (k^{\alpha} l^{1-\alpha})^{\gamma} - Wl - R (k+k_E) \right\},
\end{equation*}
and
\begin{equation*}
    \pi^d_0(z) = \max_{k,l} \left\{ \left( 1 - \xi \right)
        \left[ (1-\tau_z) p_d z^{1-\gamma} (k^{\alpha} l^{1-\alpha})^{\gamma} - Wl - Rk \right] \right\}.
\end{equation*}
As before, the profit function of firms in the polluting sector is the envelope of $\pi^d_0(z)$ and $\pi^d_1(z)$:
\begin{equation*}
    \pi^d(z) = \max\left\{\pi^d_0(z), \pi^d_1(z)\right\}.
\end{equation*}
The rest elements of the model are identical to those in the main text.
%The rest elements of the model are exactly the same as those in the main text.

The stationary equilibrium with CES aggregation is defined as follows.
\begin{definition}
\label{def:ces}
A stationary equilibrium of this economy consists of prices $\{W, R, p_d, p_c\}$, allocations $\{C, K, Y_d, Y_c, Y\}$, firm's policy functions $\{k^j(z),l^j(z),y^j(z),\pi^j(z)\}$, $j = c, d$, thresholds for household members' occupational choices $\{\hat{z}_c, \hat{z}_d\}$ and polluting firms' technology adoption $\tilde{z}_d$, as well as aggregate pollution $E$, such that:
\begin{enumerate}[(i)]
    \item
    Given prices $\{W, R, p_d, p_c\}$, $\{C, K, \hat{z}_c, \hat{z}_d\}$ solve the household's optimization problem;
    \item
    Given prices $\{p_d, p_c\}$, $\{Y_d, Y_c\}$ solve the final good producer's optimization problem;
    \item
    Given prices $\{W, R, p_d, p_c\}$, $\{k^j(z),l^j(z),y^j(z),\pi^j(z)\}$, $j = c, d,$ and $\tilde{z}_d$ solve the intermediate goods producers' optimization problems;
    \item
    Prices $\{W, R, p_d, p_c \}$ clear all markets:
    \begin{itemize}
        \item
        Labor Market:
        \begin{equation*}
            \mu G(\hat{z}_d) + (1-\mu) G(\hat{z}_c) = \mu \int_{\hat{z}_d}^{\overline{z}} l^d(z)dG(z) + (1-\mu)\int_{\hat{z}_c}^{\overline{z}} l^c(z)dG(z),
        \end{equation*}
        \item
        Capital Market:
        \begin{equation*}
            K = \mu \left[\int_{\hat{z}_d}^{\overline{z}} k^d(z)dG(z) + k_E [G(\overline{z})-G(\tilde{z}_d)]\right] + (1-\mu)\int_{\hat{z}_c}^{\overline{z}} k^c(z)dG(z),
        \end{equation*}
        \item
        Intermediate goods produced by polluting and non-polluting sectors:
        \begin{equation*}
            Y_d = \mu \int_{\hat{z}_d}^{\overline{z}} y^d(z)dG(z), \qquad Y_c = (1-\mu)\int_{\hat{z}_c}^{\overline{z}} y^c(z)dG(z),
        \end{equation*}
        \item
        Final Good:
        \begin{equation*}
            C + K - (1-\delta)K = Y,
        \end{equation*}
        where
        \begin{equation*}
            Y = \left[\varphi (Y_d)^{\frac{\rho-1}{\rho}} + (1-\varphi)(Y_c)^{\frac{\rho-1}{\rho}} \right]^{\frac{\rho}{\rho-1}},
        \end{equation*}
    \end{itemize}
    \item
    Aggregate Pollution:
    \begin{equation*}
        E = \mu\left[\int_{\hat{z}_d}^{\tilde{z}^d} e\left(0,y^d(z)\right)dG(z) + \int_{\tilde{z}_d}^{\overline{z}} e\left(1,y^d(z)\right) dG(z)\right].
    \end{equation*}
\end{enumerate}
\end{definition}

\subsection{Computational Algorithm}

The stationary equilibrium can be computed in a similar way as depicted in Appendix \ref{sec:compu_main}. The only difference here is that instead of solving for the equilibrium wage $W$ only, we need to also find the prices for the intermediate goods, $p_c$ and $p_d$. With the equilibrium prices, the allocations in Definition \ref{def:ces} can be calculated accordingly. Recall that Equation (\ref{eq:cesprice}) defines a 1-1 mapping between $p_c$ and $p_d$, hence in practice we need to solve for $W$ and $p_d$. The pseudo-code is as follows.

%The stationary equilibrium can be solved in more or less the same way as depicted in Appendix \ref{sec:compu_main}. The only difference here is that instead of solving for only one price $W$, we need to find in addition the intermediate goods prices $p_c$ and $p_d$. With the equilibrium prices, the allocations in Definition \ref{def:ces} can be calculated easily. Recall that Equation (\ref{eq:cesprice}) defines a 1-1 mapping between $p_c$ and $p_d$, hence in practice we choose to solve for $W$ and $p_d$. The pseudo-code is given as follows.
\begin{enumerate}
    \item
    Calculate the equilibrium interest rate again by Equation (\ref{eq:ss_r}).
    \item
    Solve for the wage $W$ and the price of the polluting sector intermediate good $p_d$ in the equilibrium. This includes the following steps.
    \begin{enumerate}[(a)]
        \item
        Make initial guesses for $W$ and $p_d$, using Equation (\ref{eq:cesprice}) to back out $p_c$:
        \begin{equation*}
            p_c = \left[ \frac{1-\varphi^{\rho}(p_d)^{1-\rho}}{(1-\varphi)^{\rho}} \right]^{\frac{1}{1-\rho}}.
        \end{equation*}
        \item
        Given $R, W, p_d$ and $p_c$, for each firm-$z$ in both the polluting and non-polluting sectors, we can solve for the profit functions $\pi^c(z)$ and $\pi^d(z)$. Specifically, the first order conditions of firms in the non-polluting sector are given by:
        \begin{align*}
            & (k): \qquad \alpha \gamma (1-\tau_z)p_c z^{1-\gamma} k^{\alpha \gamma-1} l^{(1-\alpha)\gamma} = R, \\
            & (l): \qquad (1-\alpha)\gamma(1-\tau_z) p_c z^{1-\gamma}k^{\alpha \gamma} l^{(1-\alpha)\gamma-1} = W.
        \end{align*}
        With the optimal factor demand $k(z)$ and $l(z)$, the profit function of firms in the non-polluting sector is given by
        \begin{equation*}
            \pi^c(z) = (1-\tau_z)p_c z^{1-\gamma}[k(z)^{\alpha}l(z)^{1-\alpha}]^{\gamma} - Wl(z) - Rk(z).
        \end{equation*}
        \item
        Notice that the first order conditions of firms in the polluting sector are similar, hence we can at the same time solve the potential profits of polluting firms using dirty and clean technologies $\pi^d_0(z)$ and $\pi^d_1(z)$:
        \begin{align*}
            \pi^d_0(z) &= (1-\xi)\{(1-\tau_z) p_d z^{1-\gamma}[k(z)^{\alpha}l(z)^{1-\alpha}]^{\gamma} - Wl(z) - Rk(z)\}, \\
            \pi^d_1(z) &= (1-\tau_z)p_d z^{1-\gamma}[k(z)^{\alpha}l(z)^{1-\alpha}]^{\gamma} - Wl(z) - R[k(z)+k_E].
        \end{align*}

        \item
        Now $\pi^d_0(z),\pi^d_1(z)$ and $\pi^c(z)$ can be used to pin down the thresholds for occupational choices $\{\hat{z}_c,\hat{z}_d\}$ and technology adoption $\tilde{z}_d$. In particular,
        \begin{equation*}
            \pi^d(z) = \max\{\pi^d_0(z),\pi^d_1(z)\},
        \end{equation*}
        and $\hat{z}^j$s are such that
        \begin{equation*}
            W = \pi^j(\hat{z}_j), \qquad j = c,d.
        \end{equation*}
        When $\pi^d_0(z)$ and $\pi^d_1(z)$ satisfy single-crossing condition,
        \begin{equation*}
            \tilde{z}_d = \min_z \{z \in [\hat{z}_d,\overline{z}] | \pi^d_0(z) < \pi^d_1(z) \}.
        \end{equation*}
        Notice that now for the polluting sector, $\hat{z}_d$ and $\tilde{z}_d$ define two groups of firms: those that use dirty technology $z \in [\hat{z}_d, \tilde{z}_d]$, and those that use clean technology $z \in [\tilde{z}_d,\overline{z}]$.

        \item
        If the labor market clearing condition
        \begin{equation*}
            \mu G(\hat{z}_d) + (1-\mu) G(\hat{z}_c) = \mu \int_{\hat{z}_d}^{\overline{z}} l^d(z)dG(z) + (1-\mu)\int_{\hat{z}_c}^{\overline{z}} l^c(z)dG(z),
        \end{equation*}
        and the first order condition of the final good producer
        \begin{equation*}
            \frac{\mu}{1-\mu}\cdot \frac{\int_{\hat{z}_d}^{\overline{z}} y^d(z)dG(z)}{\int_{\hat{z}_c}^{\overline{z}} y^c(z)dG(z)} = \left(\frac{\varphi}{1-\varphi} \cdot \frac{p_c}{p_d} \right)^{\rho},
        \end{equation*}
        do not hold, return to Step 2.(a) and update the guesses for $W$ and $p_d$.
    \end{enumerate}

    \item
    With the equilibrium prices $W, R, p_d, p_c$, all allocations of the economy can be computed following Definition \ref{def:ces}.
\end{enumerate}

The resource constraint can be verified in the same way as in Appendix \ref{sec:compu_main}, and hence is omitted here.

\subsection{Quantitative Results}

We use the model to evaluate the effects of removing distortions from one sector only, and study how cross-sector reallocation affects our results. Specifically, we compare the results from two experiments. In Experiment (i), we repeat Experiment (i) in the main text by setting $\tau_z = 0$ for both sectors. This experiment serves two purposes. First, by comparing the results with those from the main text, we show that the alternative assumption of finite and constant elasticity of substitution between the two sectors would not change our main results materially. Therefore, the assumption that the products from the two sectors are perfect substitutes is innocuous for the main results of this paper. Second, it provides a benchmark for us to compare the effects of symmetric versus asymmetric changes in distortions. In Experiment (ii), we remove the distortions from the polluting sector {only}, and evaluate the effects of cross-sector reallocation on our results.

%We use the model to evaluate the effects of asymmetric changes in sectoral distortions to see how cross-sector resource allocation affects our results. Specifically, we compare the results from two experiments. In experiment (i), we repeat the same exercise in the main text by setting $\tau_z = 0$ for both sectors. This experiment serves two purposes. First, by comparing the results with those in the main text, we verify that assuming alternatively that the two goods have constant elasticity of substitution would not affect our results quantitatively. As a result, the simplification of assuming the two goods are perfect substitutes are innocuous. Second, it provides a benchmark for us to compare the impacts from symmetric versus asymmetric removal of distortions.

The quantitative exercises in this section are for illustration purpose mainly. Therefore, we only carry out a simple calibration of the model. We keep most of the parameters intact as in Section \rom{3} of the main text. There are two new parameters that we need to pin down, namely the elasticity of substitution $\rho$ and the share of the products of the polluting sector in the production of the final good $\varphi$. Empirical estimates of $\rho$ range from 3 to 10 for narrowly defined industries [\citet{BrodaWeinstein:2006} and \citet{HendelNevo:2006}]. \citet{HsiehKlenow:2009} use $\rho=3$ for 4-digit industries. Because we divide the whole economy into two broad sectors in our model, we begin with a smaller value of $\rho = 1.5$ and later consider $\rho = 3$ to gauge how the change in $\rho$ affects our results.\footnote{Intuitively, the elasticity of substitution is larger across more narrowly defined industries, since it is easier to substitute apples with oranges than with smartphones.} Given $\rho$, we choose $\varphi$ such that the revenues from the polluting sector $p_d Y_d$ is 20\% of those from both sectors, $p_d Y_d + p_c Y_c$. In addition, due to the presence of relative price, we adjust the adoption cost of clean technology so that the share of firms using clean technology is again 57\%.

%The main objective of the quantitative exercises in this section is for illustration purpose only. Therefore we only do a simple calibration of the model. We keep most of the parameters intact as calibrated in the main text. There are two new parameters we need to calibrate, the elasticity of substitution $\rho$ and the average share of intermediate goods produced by the polluting sector in the production of the final good. Empirical estimates of $\rho$ typically ranges from three to ten [\citet{BrodaWeinstein:2006} and \citet{HendelNevo:2006}]. \citet{HsiehKlenow:2009} use an elasticity of three at the four digit level. Because our polluting/non-polluting division is much coarser, we begin with a smaller value of $\rho = 1.5$ and later consider $\rho = 3$ to gauge how $\rho$ affects our results.\footnote{The intuition is that it is much easier to substitute apples with oranges than with smartphones.} Given $\rho$, we calibrate $\varphi$ such that the value of output by the polluting sector $p_d \cdot Y_d$ is 20\% of the total value of intermediate goods $p_d Y_d + p_c Y_c$. Finally, due to the presence of relative price, we adjust the cost of clean technology such that the clean share in the benchmark equilibrium is again around 57\%.

\begin{table}[t]
\footnotesize
\centering
\begin{threeparttable}
\caption{The Effects of Removing Distortions from Polluting Sector Only v.s. From Both Sectors}
%\begin{tabular}{lccccccc}%{p{85pt}>{\centering\arraybackslash}p{50pt}>{\centering\arraybackslash}p{50pt}>{\centering\arraybackslash}p{40pt}}%>{\centering\arraybackslash}p{35pt}}%{lccc}
\begin{tabular}{p{90pt} >{\centering\arraybackslash}p{45pt} >{\centering\arraybackslash}p{45pt}>{\centering\arraybackslash}p{40pt} >{\centering\arraybackslash}p{5pt} >{\centering\arraybackslash}p{45pt} >{\centering\arraybackslash}p{45pt} >{\centering\arraybackslash}p{40pt}}
    \hline \hline
                         & \multicolumn{3}{c}{Polluting}    & & \multicolumn{3}{c}{Non-polluting} \\
    \cmidrule{2-4} \cmidrule{6-8}
    Statistics                 & Benchmark & (i)      & (ii)      & & Benchmark     & (i)    & (ii) \\
    \midrule
    \textbf{CES $=$ 1.5} \\
    \ \ \ Physical Output      & 100.00    & 129.64   & 134.63    & & 100.00        & 129.90 &  98.03 \\
    \ \ \ Price                & 100.00    & 99.97    & 85.00     & & 100.00        & 100.00 & 102.34 \\
    \ \ \ Revenue              & 100.00    & 129.60   & 114.42    & & 100.00        & 129.90 & 100.32 \\
    \midrule
    \ \ \ \# of Firms          & 100.00    & 42.63    & 46.44     & & 100.00        & 41.88  &  95.38 \\
    \ \ \ Mean Size            & 64.31     & 152.21   & 176.17    & & 51.16         & 123.50 &  49.38 \\
    \midrule
    \ \ \ Pollution            & 100       & 74.69    & 80.05     \\
    \ \ \ Intensity            & 100       & 57.81    & 59.47     \\
    \ \ \ Clean Share          & 56.18     & 83.80    & 73.10     \\
    \midrule
    \textbf{CES $=$ 3.0} \\
    \ \ \ Physical Output      & 100.00    & 129.83   & 160.51    & & 100.00        & 129.89 & 89.45  \\
    \ \ \ Price                & 100.00    & 100.02   & 87.38     & & 100.00        & 100.00 & 100.46 \\
    \ \ \ Revenue              & 100.00    & 129.85   & 140.25    & & 100.00        & 129.88 & 89.86  \\
    \midrule
    \ \ \ \# of Firms          & 100.00    & 41.50    & 48.19     & & 100.00        & 42.30  & 89.24  \\
    \ \ \ Mean Size            & 68.36     & 166.29   & 214.24    & & 50.16         & 119.84 & 46.09  \\
    \midrule
    \ \ \ Pollution            & 100       & 74.69    & 89.61     \\
    \ \ \ Intensity            & 100       & 57.53    & 55.81     \\
    \ \ \ Clean Share          & 56.48     & 84.04    & 74.37     \\
    \bottomrule
\end{tabular}
\begin{tablenotes}
     \footnotesize{
     \item[$\dagger$]
     Note: All of the values are percentages except for mean size, which is the numbers of workers.}
\end{tablenotes}
\label{tab:aggregates_appen}
\end{threeparttable}
\end{table}

Table \ref{tab:aggregates_appen} presents the results. In the upper panels, we report the results for $\rho =$ 1.5 and in the lower panels $\rho =$ 3. For experiment (i), it is reassuring to see that for both levels of elasticity of substitution, the results are quantitatively similar to the perfect substitutes case in the main text. Following the elimination of $\tau_z$ from both sectors, aggregate output in both sectors increases by about 30\%. Again, there is little reallocation across sectors, and the changes in the prices of the products in both sectors are negligible. The average pollution intensity decreases by about 42\%, so again the technique effect dominates, and the aggregate pollution decreases by about 25\%.

For Experiment (ii), we start with the case $\rho =$ 1.5. Following the elimination of $\tau_z$ in the polluting sector, there again are a large increase in output and a large decrease in average pollution in the polluting sector. However, there is also a sizable reallocation of production factors from the non-polluting sector to the polluting sector. Specifically, since the equilibrium wage increases due to the higher labor demand from the polluting sector, firms in the non-polluting sector have to use less labor and capital. This causes a 2\% decrease in the physical output of the non-polluting sector. The physical output of the polluting sector increases by 35\% in this case compared to 30\% in Experiment (i). This composition effect partially offsets the technique effect, and the aggregate pollution decreases by 20\% compared to 25\% in Experiment (i), although the decreases in average pollution intensity are similar in these two cases (41\% versus 42\%).

%Table \ref{tab:aggregates_appen} presents the results. In the upper panels, we report the results for $\rho = 1.5$ and in the lower panels $\rho = 3$. For experiment (i), it is reassuring to see that for both levels of elasticity of substitution, the results are quantitatively similar to the perfect substitutes case in the main text. In experiment (ii), following the elimination of $\tau_z$ in the polluting sector, the cost of producing of these firms decreases, allowing them to charge a lower price for larger sales. Quantitatively, the polluting sector cuts the price by 15\% and as a result, it is able to sell 35\% more output, consequently leading to 15\% increase in revenue. On the other hand, because wage increases by 12\% as a result of higher factor demand from the polluting sector, firms in the non-polluting sector have to charge higher price to survive. This causes a 2\% decrease in the quantity sold. The average firm size increases in both sectors, but for different reasons. In the polluting sector, it is because the elimination of size-dependent distortions benefit the large firms disproportionately. While in the non-polluting sector, it is because tougher selection caused by a rising wage. Furthermore, for the same reason that environmental regulation amplifies the negative impact of size-dependent distortions, the average level of distortions on the non-polluting sector increases as well as a consequence of the expansion of average firm size. Nevertheless, the technique effect still dominates the scale effect, even with cross-sector redistribution due to asymmetric reduction in sectoral distortions.

When $\rho =$ 3,  the cross-sector reallocation of factors would be much larger given a higher elasticity of substitution. The physical output of the polluting sector increases by 60\% instead of 35\% in this case, and while physical output of the non-polluting sector decreases by 11\% instead of 2\%. As a result, although the average pollution intensity decreases by 44\%, the aggregate pollution in this case decreases by only 10\% as opposed to 20\% when $\rho =$ 1.5. If we increase $\rho$ further, it is possible that at some point the the cross-sector reallocation would be so strong that removing the distortions from the polluting sector would increase the aggregate pollution. However, as we mentioned above,  $\rho =$ 3 is likely to be upper bound of the range for empirically plausible elasticity of substitution in our model, given that we divide the whole economy into two broad sectors. Hence, our results suggest that even if we remove the distortions from the polluting sector only, the technique effect would still dominate within the empirically plausible range of $\rho$.%the effects on aggregate pollution are smaller when the elasticity of substitution $\rho$ is larger, but the technique effect would still dominate within the empirically plausible range of $\rho$.

%The results for $\rho = 3$ are qualitatively the same. However, with a higher elasticity of substitution, the cross-sector redistribution is indeed stronger. Total revenue in the polluting sector now increases by 40\% instead of 15\%, and aggregate pollution decreases by only 6\% as opposed to 11\%, despite that the average intensity decreases more. Further increasing $\rho$ is likely to cause a reverse of the relative strength of the scale versus technique effects in favor of increasing aggregate pollution. However, as we argued before, we think that $\rho = 3$ is likely to be at the higher end of the range of empirically plausible elasticity for the two-sector division if not already above. Hence our results suggest that it is plausible to expect that even for asymmetric reduction of distortions, the technique effect still outweighs the scale effect.

Interestingly, if we compare Experiment (ii) with (i)---recall that the only difference between these two is that we also remove distortions from the non-polluting sector in Experiment (i)---we find that removing distortions from the non-polluting sector has positive spillovers to the polluting sector, which increases the adoption rate of clean technology by about 10 percentage points. This is due to the demand effect that pulls up the price of the polluting goods, allowing many medium sized firms to earn enough profits to install clean technology. This result suggests that even the reduction of distortions in the non-polluting sector alone could potentially have positive environmental implications.

%Interestingly, by comparing experiment (i) with (ii), we find that a reduction of distortions in the non-polluting sector has positive spillover to the polluting sector by increasing the clean technology adoption rate. This is due to the income effect that pulls up the price of the polluting goods, allowing many medium sized firms to earn enough profits to install clean technology. This result suggests that even the reduction of distortions in the non-polluting sector could potentially have positive environmental implications.

%\section{Additional Quantitative Exercises}
%
%\subsection{Environmental Regulations and Size Distribution}
%
%In our benchmark calibration, $k_E$ is about 2.5 times the equilibrium wage of a typical worker. This relatively small value limits the extent to which environmental policy can affect the real economy. In this section, we show that when $k_E$ is increased to 10 times the value used in the benchmark calibration, environmental policy influences the resource allocation markedly. We consider two scenarios. In the first case, we again solve the model with all the parameters remaining at the benchmark calibration level, but increase $k_E$ to 41.5. With no changes in regulation intensity, the adoption rate of the clean technology drops. In the second case, we increase $\xi$ such that the adoption rate in the benchmark case (57\%) is restored. We label these two experiments (iii) and (iv).
%\begin{table}[t]
%\footnotesize
%\centering
%\begin{threeparttable}
%\caption{The Effect of Regulations: Higher $k_E$}
%\begin{tabular}{p{125pt} >{\centering\arraybackslash}p{75pt} >{\centering\arraybackslash}p{75pt} >{\centering\arraybackslash}p{75pt}}
%    \hline \hline
%    Statistics                      & Benchmark             & (iii)                 & (iv)    \\
%    \midrule
%    Aggregate Output                & 100.00                & 100.00                & 100.41  \\
%    Capital                         & 100.00                & 100.28                & 101.45  \\
%    Consumption                     & 100.00                & 99.94                 & 100.21  \\
%    Output per Worker (Wage)        & 100.00                & 100.00                & 99.63   \\
%    Output per Firm                 & 100.00                & 100.00                & 187.70  \\
%    Average Talent                  & 100.00                & 100.00                & 184.14  \\
%%    TFP                             & 100.00                & 100.00                & 100.81  \\
%    \midrule
%    Number of Firms                 & 100.00                & 100.00                & 53.50   \\
%    Mean Size                       & 59.27                 & 59.27                 & 111.65  \\
%    Median Size                     & 22.95                 & 22.95                 & 63.24   \\
%    \midrule
%    Aggregate Pollution             & 100.00                & 125.64                & 87.56 \\
%    Average Intensity               & 100.00                & 125.64                & 87.20 \\
%    Clean Share                     & 57.40                 & 8.89                  & 57.06  \\
%    Monitoring                      & 20.50                 & 20.50                 & 73.50  \\
%    \bottomrule
%\end{tabular}
%\begin{tablenotes}
%     \footnotesize{
%     \item[$\dagger$]
%     Note: All values reported are in percentage points except mean and median size, which are the absolute numbers of workers.}
%\end{tablenotes}
%\label{tab:aggregates_ke}
%\end{threeparttable}
%\end{table}
%
%Table \ref{tab:aggregates_ke} presents the results of experiments (iii) and (iv). For case (iii), we first note that the size distributions and efficiency of the economy remain virtually the same as in the benchmark case. However, the clean technology adoption rate falls to 9\% since a large number of firms now find it unprofitable to use the clean technology and higher pollution thus follows. Because the benchmark case can be understood as a decrease in the price of the clean technology from case (iii), this result suggests that subsidizing clean technologies can serve as a substitute for stronger regulations.
%
%If we increase the regulations to the level such that the original technology adoption rate is restored, as opposed to the results of case (ii) where the size distributions and resource allocation are only mildly affected, the effects of the regulation in experiment (iv) are much larger. Figure \ref{fig:envpolicy} shows the size and employment distributions for case (iv).
%\begin{figure}[t]
%    \begin{center}
%    \includegraphics[width=0.45\textwidth]{D:/PaperDrafts/Pollution/PrelimResults/sizedist_bench_highcost.eps}
%    \includegraphics[width=0.45\textwidth]{D:/PaperDrafts/Pollution/PrelimResults/eshare_bench_highcost.eps}
%    \caption{Environmental Policy and Size Distribution}
%    \label{fig:envpolicy}
%    \end{center}
%\end{figure}
%In contrast to the size and employment distributions in the benchmark case, all the firms in the first group are driven out. This fact is also reflected in column (iv) of Table \ref{tab:aggregates_ke} as increases in average talent and in the mean/median size of the firms. Therefore, environmental policy {improves} the resource allocation on the {extensive} margin by forcing small unproductive firms to exit the market. However, the gains from these improvements are limited because the allocation of resources on the {intensive} margin worsens (see Table \ref{tab:talentdist_ke}).
%\begin{table}[t]
%\footnotesize
%\centering
%\begin{threeparttable}
%\caption{Resource Allocation on the Intensive Margin: High $k_E$}
%\begin{tabular}{p{65pt} >{\centering\arraybackslash}p{45pt} >{\centering\arraybackslash}p{45pt} >{\centering\arraybackslash}p{45pt} >{\centering\arraybackslash}p{45pt} >{\centering\arraybackslash}p{45pt}}
%    \hline \hline
%    Economy     & $\text{QU}_1$ & $\text{QU}_2$ & $\text{QU}_3$ & $\text{QU}_4$ & $\text{QU}_5$ \\
%    \midrule
%    Benchmark   & 2.69          & 4.19          & 7.29          & 16.55         & 69.28 \\
%    Case (iv)   & 4.44          & 6.63          & 10.98         & 21.86         & 56.10 \\
%    Case (i)    & 1.50          & 2.83          & 6.34          & 18.06         & 71.27 \\
%    Case (ii)   & 2.93          & 4.47          & 7.77          & 17.37         & 67.46 \\
%    \bottomrule
%\end{tabular}
%\begin{tablenotes}
%     \footnotesize{
%     \item[$\dagger$]
%     Note: $\text{QU}_1$ to $\text{QU}_5$ represent the first to fifth quintiles, respectively.}
%\end{tablenotes}
%\label{tab:talentdist_ke}
%\end{threeparttable}
%\end{table}
%An efficient allocation on the intensive margin is achieved in the no-size-dependent $\tau_z$ case [case (i)]. Instead of an allocation of production toward larger firms as in the efficient case, here the production of firms in the bottom four quantiles expands significantly at the expense of the production share of the most productive firms. As a result, much of the gains in economic efficiency are offset by the worsening of the resource allocations on the intensive margin. Qualitatively, this result is the same as in case (ii). However, by comparing cases (ii) and (iv), we see that the larger fixed cost $k_E$, the higher is the degree of resource misallocation on the intensive margin . Although the level of industrial pollution lowers, the reduction could be much larger if the allocation on the intensive margin also improves, as in the case of the elimination of $\tau_z$.

\phantomsection
\addcontentsline{toc}{section}{REFERENCES}
\bibliography{D:/Dissertation/Literature/Dissertation1}
\bibliographystyle{aea}

\end{document}

### 2019-09-19 Documentation/Pollution_AEJ_Final.tex
tex added

% Article Format: American Economic Review
% Xin Tang @ Stony Brook University
% Last Updated: August 2014
\documentclass[twoside,12pt,leqno]{article}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                    Text Layout                       %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Page Layout
\usepackage[hmargin={1.2in,1.2in},vmargin={1.5in,1.5in}]{geometry}
\topmargin -1cm        % read Lamport p.163
\oddsidemargin 0.04cm   % read Lamport p.163
\evensidemargin 0.04cm  % same as oddsidemargin but for left-hand pages
\textwidth 16.59cm
\textheight 21.94cm
\renewcommand\baselinestretch{1.15}
\parskip 0.25em
\parindent 1em
\linespread{1}

% Set header and footer
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhead{}
\fancyhead[LE,RO]{\thepage}
%\fancyhead[CE]{\textit{JI QI, XIN TANG AND XICAN XI}}
%\fancyhead[CO]{\textit{THE SIZE DISTRIBUTION OF FIRMS AND INDUSTRIAL POLLUTION}}
\cfoot{}
\renewcommand{\headrulewidth}{0pt}
%\renewcommand*\footnoterule{}
%\setcounter{page}{1}

% Font
\renewcommand{\rmdefault}{ptm}
\renewcommand{\sfdefault}{phv}
%\usepackage[lite]{mtpro2}
% use Palatinho-Roman as default font family
%\renewcommand{\rmdefault}{ppl}
\usepackage[scaled=0.88]{helvet}
\makeatletter   % Roman Numbers
\newcommand*{\rom}[1]{\expandafter\@slowromancap\romannumeral #1@}
\makeatother
\usepackage{CJK}

% Section Titles
\renewcommand\thesection{\textnormal{\textbf{\Roman{section}.}}}
\renewcommand\thesubsection{\textnormal{\Alph{subsection}.}}
\usepackage{titlesec}
\titleformat*{\section}{\bf \center}
\titleformat*{\subsection}{\it \center}
\renewcommand{\refname}{\textnormal{REFERENCES}}

% Appendix
\usepackage[title]{appendix}
\renewcommand{\appendixname}{APPENDIX}

% Citations
\usepackage[authoryear,comma]{natbib}
\renewcommand{\bibfont}{\small}
\setlength{\bibsep}{0em}
\usepackage[%dvipdfmx,%
            bookmarks=true,%
            pdfstartview=FitH,%
            breaklinks=true,%
            colorlinks=true,%
            %allcolors=black,%
            citecolor=blue,
            linkcolor=red,
            pagebackref=true]{hyperref}

% Functional Package
\usepackage{enumerate}
\usepackage{url}      % This package helps to typeset urls

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                    Mathematics                       %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{amsmath,amssymb,amsfonts,amsthm,mathrsfs,upgreek}
% Operators
\newcommand{\E}{\mathbb{E}}
\newcommand{\e}{\mathrm{e}}
\DeclareMathOperator*{\argmax}{argmax}
\DeclareMathOperator*{\argmin}{argmin}
\DeclareMathOperator*{\plim}{plim}
\renewcommand{\vec}[1]{\ensuremath{\mathbf{#1}}}
\newcommand{\gvec}[1]{{\boldsymbol{#1}}}

% New Environments
\newtheorem{result}{Result}
\newtheorem{assumption}{Assumption}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newtheorem{definition}{Definition}
\setlength{\unitlength}{1mm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                 Tables and Figures                   %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{threeparttable,booktabs,multirow,array} % This allows notes in tables
\usepackage{floatrow} % For Figure Notes
\floatsetup[table]{capposition=top}
\usepackage[font={sc,footnotesize}]{caption}
\DeclareCaptionLabelSeparator{aer}{---}
\captionsetup[table]{labelsep=aer}
\captionsetup[figure]{labelsep=period}
\usepackage{graphicx,pstricks,epstopdf}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Begin Document Content %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{\vspace{-1cm}\Large{{\textsf{The Size Distribution of Firms and Industrial Water Pollution\\A Quantitative Analysis of China}}}\thanks{Disclaimer: The results and conclusions in this paper are those of the authors, and do not necessarily reflect the views of the China Ministry of Environmental Protection, or those of the International Monetary Fund. An online appendix containing additional materials is available on the author's website: {\color{blue}https://sites.google.com/site/zjutangxin/}.}}
\author{\normalsize{\textit{By}\ \textsc{Ji Qi},\ \textsc{Xin Tang},\textsc{\ and\ }\textsc{Xican Xi}}\thanks{Qi: Chinese Academy for Environmental Planning, Room 709-B BeiKeChuangYe Tower, No.10 Dayangfang, Beiyuan Road, Beijing, China, 100012 (e-mail: qiji@caep.org.cn); Tang: Wuhan University and International Monetary Fund, 700 19th St NW, Washington D.C., United States, 20431 (e-mail:zjutangxin@gmail.com); Xi: School of Economics, Fudan University, 600 Guoquan Road, Shanghai, China, 200433 (e-mail:xicanxi@fudan.edu.cn). We are grateful for the comments from Alexis Anagnostoupolos, Marina Azzimonti, Juan Carlos Conesa, Berthold Herrendorf, Nicolai Kuminoff, Pietro Peretto, Edward Prescott, Diego Restuccia, Todd Schoellman, Kerry Smith, Daniel Yi Xu, Gustavo Ventura, the editor and three anonymous referees. We also benefited from the comments received at Arizona State University, the Chinese Academy of Environmental Planning, Duke University, the IMF, U.S International Trade Commission, Peking University, Shanghai University of Finance and Economics, Singapore Management University, Stony Brook University, Washington State University, Wuhan University, and Zhejiang University. We sincerely thank the China Ministry of Ecology and Environment for granting us access to the National General Survey of Pollution Sources data. This paper has been screened to ensure that no confidential data are revealed.}} %The authors declare that they have no relevant or material financial interests that relate to the research described in this paper.}}
\date{\textnormal{\today}}

\begin{document}
\maketitle
%\renewcommand{\abstractname}{}
\vspace{-1.5em}
%\begin{abstract}
\begin{center}
\begin{minipage}[c]{0.8\textwidth}
{%\normalsize
%\noindent \textit{We study the role of firm-size distribution in industrial pollution using a quantitative model featuring a distribution of firms. Micro-level data support a negative correlation between firm size and polluting intensity. Fixed costs associated with advanced treatment technologies are shown to be important in explaining the negative size-intensity correlation. Evidence suggests that product market frictions limit the expansion of productive firms in China, which leads to survivals of unprofitable small polluting firms. Quantitative analysis using a model consistent with these empirical regularities shows that while having moderate effect on output, size distribution exerts considerable effect over industrial pollution. (\textit{JEL} E01, E23, O44, Q52, Q53, Q56)}
\noindent \textit{We argue that misallocation across firms amplifies industrial water pollution by distorting the firm size distribution in China. Firm-level data indicate that larger firms are more likely to use clean technology but face higher distortions. In a heterogeneous firms model with an endogenous choice of pollution treatment technologies, we show that distortions that increase with firm-level TFP lower the adoption of clean technology, amplify aggregate pollution intensity, and lower aggregate output. Quantitatively, eliminating these correlated distortions would increase output by 30\% and decrease pollution by 20\%. Meanwhile, environmental regulations have sizable impact on pollution but only limited effect on output. (JEL E23, L11, O44, Q52, Q53, Q56)}}
\end{minipage}
\end{center}

\textnormal{Severe} pollution has accompanied China's remarkable economic growth in the past few decades, causing environmental degradation, public health damage, and millions of premature deaths.\footnote{\citet{WorldBank_Cost_2007} estimates that the cost of air and water pollution in China is about 6\% of GDP. The health cost of pollution is estimated to be 4\% of GDP, the majority of which is associated with premature deaths caused by pollution. %\citet{Ebenstein:2012} finds that industrial water pollution has a large effect on deaths from digestive cancers in China, while \citet{Ebensteinetal:2015} show that air pollution is negatively associated with life expectancy.
See \citet{Vennemoetal:2009} and \citet{ZhengKahn:2013} for review of empirical studies on environmental pollution in China.} %Therefore it has become a major concern for both the public and policymakers. %\footnote{The Chinese government has initiated a campaign against pollution. According to the \textit{Report on the Work of the Government 2014}, the State Council has allocated \$600 billion of special funds to reduce air and water pollution during the Thirteenth Five-Year Plan (2016-2020).}
Understanding the driving forces behind this severe pollution is crucial for designing and evaluating anti-pollution policies. An outstanding question is whether the severe pollution is an inevitable consequence of rapid economic growth, or largely exacerbated by policy distortions and/or market inefficiencies.

In this paper, we argue that misallocation across firms amplifies industrial water pollution by distorting the firm size distribution in China. Using nationally representative data on firm production, pollution emissions and pollution treatment technologies, we document two facts on firm size and pollution intensity (pollutants per output) in China.\footnote{We use the \textit{National General Survey of Pollution Sources} (NGSPS) and \textit{National Economic Census} (CNEC) in China. Section \rom{1} provides more details.} First, large firms have lower pollution intensity than small firms, with an elasticity of $-$0.37 between firm size and pollution intensity for the top five polluting industries in China.\footnote{The industries are ranked by their emissions of \textit{Chemical Oxygen Demand} (COD). The five industries are (with two-digit GB/T4547-2002 code in parentheses): Paper and Paper Products (C22), Processing of Food from Agricultural Products (C13), Textiles (C17), Raw Chemical Materials and Chemical Products (C26), and Beverages (C15).} % We find 7- to 32-fold differences in pollution intensity between firms in the largest and smallest quartiles of the firm size distribution for the top five polluting industries in China.
Furthermore, we find that this is not only due to fewer pollutants per output are generated by large firms during production, but also that large firms are also more likely to use advanced end-of-pipe treatment technologies that require sizable fixed installation costs. %\footnote{The negative correlation between firm size/productivity and pollution intensity has also been found in other countries. For example, for developing countries \citet{Dasguptaetal:1998} find that small firms have higher air pollution intensity in Brazil and Mexico, and \citet{Martin:2013} and \citet{BarrowsOllivier:2016} find that smaller firms have higher energy intensity in India. For developed countries, \citet{Bloometal:2010} find that better managed firms have lower energy intensity in the United Kingdom, and \citet{ShapiroWalker:2015} find that more productive firms have lower pollution intensity in the United States. However, the richness of our data allows us to establish empirically a unique link between firm size and the adoption of clean technology, and thus to provide a mechanism for this negative correlation that is observable.}\textsuperscript{, }
%\footnote{Our data reveal that large firms are more likely to not only use advanced \textit{end-of-pipe} treatment technologies to remove a larger proportion of pollutants, but also generate less pollutants in production. This could be because that the production technologies used by large firms are also more environmentally friendly, or also because they are using less inputs. While we cannot directly observe firms' production technologies, we do have data on firms' end-of-pipe pollution treatment technologies.}
Second, large firms account for a smaller proportion of the total employment in China than in the United States. For the top five polluting industries in China, firms with more than 400 employees account for 20\% of the total employment compared with close to 70\% for the U.S. counterparts. %\footnote{See \citet{Axtell:2001}, \citet{Luttmer:2007}, and \citet{RossihansbergWright:2007} for theories and evidence regarding the heavy right tail of the U.S. firm and establishment distributions.}
If we take the U.S. economy as a less distorted benchmark, these facts suggest that distortions to firm size distribution could have important environmental consequences in China. %This fact is suggestive of the size-dependent distortions that reallocate factors away from large productive firms in China if we take the U.S. economy as a relatively distortion-free benchmark. Indeed, we find that in China, the average product of labor and capital increase strongly with firm size and productivity [\citet{HsiehKlenow:2009, HsiehKlenow:2014}].\footnote{This measure of distortion captures the effects of many of the factors that distort factor allocation across firms, including taxes and subsidies, regulations, local protectionism, transportation costs, and financial frictions. A prominent example of such size-dependent distortions is internal trade barriers that impede the flow of goods across regions, which presumably affect large firms more since these are more likely to sell goods across regions [\citet{Young:2000}, \citet{TombeZhu:2015}, and \citet{Eberhardtetal:2016}]. In addition, as is the case in many other developing countries, small firms are more likely to evade taxes because of imperfect tax enforcement.}
%Formally, we follow the approach developed by \citet{HsiehKlenow:2009, HsiehKlenow:2014}, and estimate distortions that affect factor allocation across firms using firm-level variations in average products of capital and labor. We find that firm-level distortions increase with firm size and productivity, consistent with the fact that large firms account for a smaller fraction of total employment in China.\footnote{It is well understood in the literature that this measure of distortions captures the effects of many factors that distort factor allocation across firms, including taxes and subsidies, regulations, transportation costs and financial frictions, among others. A prominent example of such size-dependent distortions is internal trade barriers that impede the flow of goods across regions, which presumably affect large firms more, since they are more likely to sell goods across regions. \citet{TombeZhu:2015} find that the internal trade barriers have a large impact on China's aggregate productivity. In addition, as is the case in many other developing countries, small firms are more likely to evade taxes due to imperfect tax enforcement.}

Motivated by these facts, we build a two-sector (polluting and non-polluting) model of heterogeneous firms based on \citet{Lucas:1978b} to evaluate how firm-level distortions affect aggregate output and pollution. The model has the following key features. First, firms in each sector differ in their productivity levels. There is a stand-in household with a continuum of members, and each member draws a sector specific managerial ability from a given distribution. When members choose to be manager, they enter the sector their managerial ability belongs to and the ability determines the TFP of the firm they run. Second, firms differ in pollution intensity as well. As in \citet{CopelandTaylor:1994}, pollution emissions are a by-product of production for firms in the polluting sector. Following Fact 1 above, we assume that generated emissions per output during production is decreasing in firm output.\footnote{While our data reveal that large firms generate fewer pollutants per output, we do not know precisely the reasons behind that. %It may be because large firms use fewer or cleaner inputs to produce the same amount of output. For example, \citet{Bloometal:2010} find that better managed firms use less energy to produce the same amount of output in the U.K.. As another example, the paper pulp industry in China uses two different types of inputs: bagasse and wood. While bagasse, which generates 140--180 kg COD per ton, is mostly used by firms with an annual production of {\color{black}less} than 100 k-tons, wood, which generates 30--55 kg COD per ton, is mostly used by firms with an annual production of {\color{black}more} than 100 k-tons.
Without further data, we model the emissions generated during production in a reduced-form way, which is then calibrated to the data. Section \rom{1}.B discusses this point in more details.} Third, firms have the option to adopt an advanced end-of-pipe treatment technology, which we refer to as \textit{clean} technology later, after paying a fixed adoption cost. Firms in the polluting sector are subject to environmental regulations such that firms that do not use the clean technology face a penalty that takes away a fraction of their profits. %\footnote{In reality, a powerful tool used by the Chinese government to enforce environmental regulations, is to randomly audit and then shut down firms that do not comply with environmental regulations for a certain period of time, which would cost these firms a fraction of their profits. See for example, Trevor Nace, ``China shuts down tens of thousands of factories in widespread pollution crackdown,'' Forbes, October 2017.} % (\url{https://www.forbes.com/sites/trevornace/2017/10/24/china-shuts-down-tens-of-thousands-of-factories-in-widespread-pollution-crackdown})
As a result, our model predicts that only firms above a certain size threshold would choose the clean technology, which is qualitatively consistent with the fact that large firms are more likely to use clean technology.

Finally, we assume that firms face distortions that increase with their TFP, or \emph{correlated} distortions following the terminology of \citet{RestucciaRogerson:2008}, which are modeled as progressive output taxes.\footnote{\citet{Guneretal:2008} study a closely related type of distortions, namely \emph{size-dependent} distortions, which increase with firm or establishment size (the amount of capital, labor or output). An example is the many labor regulations in Italy, Spain and France that start to bind on firms with more than a certain number of employees. Both correlated and size-dependent distortions lead to a reallocation of resources from high TFP to low TFP firms, and they are essentially equivalent when distortions do not lead to rank reversal defined as more productive firms being smaller [\citet{Hopenhayn:2014}].} We find in our data that firms with higher TFP exhibit substantially higher average products of capital and labor in both the polluting and non-polluting sectors, indicating that more productive firms do face higher distortions [\citet{HsiehKlenow:2009, HsiehKlenow:2014}]. %\footnote{Pioneered by \citet{HsiehKlenow:2009, HsiehKlenow:2014}, this approach to measure distortions captures the effects of a number of factors that distort factor allocation across firms, including taxes and subsidies, regulations, local protectionism, transportation costs, and financial frictions. A prominent example of correlated distortions is internal trade barriers that impede the flow of goods across regions, which presumably affect large productive firms more since these are more likely to sell goods across regions [\citet{Young:2000}, \citet{TombeZhu:2015}, and \citet{Eberhardtetal:2016}]. In addition, as is the case in many other developing countries, small firms are more likely to evade taxes because of imperfect tax enforcement.}
As emphasized by previous studies, such as \citet{RestucciaRogerson:2008} and \citet{HsiehKlenow:2014}, correlated distortions lower both mean firm size and aggregate output, since they limit the operations of productive firms and allow too many unproductive firms to survive and expand. %\footnote{See \citet{RestucciaRogerson:2008}, \citet{Bartelsmanetal:2013}, \citet{HsiehKlenow:2014}, \citet{AdamopoulosRestuccia:2014}, \citet{BentoRestuccia:2016} among many others.}
A new insight from our model is that correlated distortions also increase aggregate pollution intensity for two reasons. First, they lower the profits of productive firms which reduces their incentives to adopt the clean technology. Therefore fewer firms adopt clean technology in the equilibrium with correlated distortions. Second, they take production factors away from large productive firms that also have lower pollution intensity, which drives up the average pollution intensity further.

%When connecting our model with firm-level data, we are able to quantify the aggregate effects of correlated distortions in a comprehensive way, taking into account the general equilibrium responses. Specifically, we can assess structurally the three channels through which distortions affect aggregate pollution, following the convention in environmental economics: scale (change in aggregate output), composition (reallocation across sectors), and technique (change in sectoral pollution intensity).\footnote{See, for example, \citet{GrossmanKrueger:1993}, \citet{CopelandTaylor:2004}, and \citet{Levinson:2009}, among others.} Moreover, our model and data allow us to further decompose the technique effect into: within sector reallocation across firms, and the change in the adoption of clean technology.

Conventionally, environmental economics decomposes changes in aggregate pollution into three effects: scale (change in aggregate output), composition (reallocation across sectors), and technique (change in sectoral pollution intensity) effects.\footnote{See for example, \citet{GrossmanKrueger:1993}, \citet{CopelandTaylor:2004} and \citet{Levinson:2009} among others.} Our model allows us to assess structurally how distortions affect aggregate pollution through the three channels. Moreover, our model and data allow us to further decompose the technique effect into within sector reallocation across firms and the change in the adoption of clean technology.

To discipline our quantitative analysis, we calibrate our model to match the observed pollution intensity, the adoption of clean technology, the correlation between distortions and firm TFP, and the firm size distribution in the Chinese data. We map the polluting sector to the top five polluting industries mentioned above, which account for 80\% of the total emissions in the data, and map the non-polluting sector to the rest of the manufacturing sector. We then use the calibrated model to evaluate the effects of two policies: removing correlated distortions from both sectors and strengthening environmental regulations.\footnote{Here we follow the so-called \emph{indirect} approach in the study of misallocation [\citet{RestucciaRogerson:2013}] by quantifying the overall effects of a variety of policies and institutions that relocate production factors from high to low TFP firms. Several examples of such policies include size-dependent taxes and subsidies, selective enforcement of regulations, financial constraints, poor enforcement of contracts, and internal trade costs, among others. This approach has been widely used in the misallocation literature, for instance, by \citet{HsiehKlenow:2009, HsiehKlenow:2014}, \citet{Bartelsmanetal:2013}, \citet{AdamopoulosRestuccia:2014}, and \citet{BentoRestuccia:2016}, among others.}%\footnote{Here we take the so-called \emph{indirect} approach in the study of misallocation (\citet{RestucciaRogerson:2013}), and quantify the overall effects of misallocation without identifying the specific underlying sources of the misallocation, such as size-dependent taxes and subsidies, selective enforcement of regulations, financial constraints, internal trade costs, and poor enforcement of contracts, among others. This approach has been widely used in the misallocation literature, for example, by \citet{HsiehKlenow:2009, HsiehKlenow:2014}, \citet{Bartelsmanetal:2013}, and \citet{AdamopoulosRestuccia:2014}, \citet{BentoRestuccia:2016} among others.}

%Moreover, we find that in China, the average product of labor and capital increase strongly with firm size and productivity [\citet{HsiehKlenow:2009, HsiehKlenow:2014}], suggesting the existence of size-dependent distortions.
% Specifically, if we take the U.S. economy as a relatively distortion-free benchmark, Fact 2 suggests that there could exist size-dependent distortions that reallocate factors away from large productive firms China, which we indeed find from the positive correlation between average factor product and firm level productivity [\citet{HsiehKlenow:2009, HsiehKlenow:2014}].\footnote{This measure of distortion captures the effects of many of the factors that distort factor allocation across firms, including taxes and subsidies, regulations, local protectionism, transportation costs, and financial frictions. A prominent example of such size-dependent distortions is internal trade barriers that impede the flow of goods across regions, which presumably affect large firms more since these are more likely to sell goods across regions [\citet{Young:2000}, \citet{TombeZhu:2015}, and \citet{Eberhardtetal:2016}]. In addition, as is the case in many other developing countries, small firms are more likely to evade taxes because of imperfect tax enforcement.} The literature has found that size-dependent distortions limit the operations of large productive firms and allow too many small unproductive firms to survive, which lowers both mean firm size and aggregate output.\footnote{See for instance \citet{Guneretal:2008}, \citet{Bartelsmanetal:2013}, \citet{HsiehKlenow:2014}, and \citet{BentoRestuccia:2016} among others.}
% An additional insight that we provide in this study is that size-dependent distortions also increase aggregate pollution intensity for two reasons. First, they lower the profits of firms which makes clean technology investment unaffordable to many firms. Second, they reduce the factors allocated to large productive firms which are more likely to use advanced pollution treatment technologies, and therefore reduce the share of total output that is produced using clean technologies. However, since size-dependent distortions both increase aggregate pollution intensity and reduce aggregate output, it is a quantitative question whether they also amplify aggregate pollution.

% To guide our analysis, we use a quantitative model to organize our empirical findings as well as quantifying the effects of size-dependent distortions on aggregate output and pollution. In particular, we extend the classic \citet{Lucas:1978b} span-of-control model to include a distinction between polluting and non-polluting sector, size-dependent distortions, an endogenous choice of pollution treatment technologies, and imperfect environmental regulations. In our model, there is a stand-in household with a continuum of members. Household members are endowed with different sectoral specific managerial talents and make occupational choices based on their talents. If a member chooses to be an entrepreneur, s/he uses her managerial talent (which becomes the firm-level productivity), capital, and labor to produce the output in the sector where the managerial talent belongs. S/he also has to pay implicit taxes that depend on her talent, which aims to capture size-dependent distortions in an intuitive way. Firm size is therefore determined by the managerial talent and distortions jointly.

% A novel feature of our model is that firms in the polluting sector also make decisions on pollutants treatment technologies. The installation of clean technology incurs a fixed cost and we assume that firms without clean technology will lose a fraction of their profits, capturing various regulatory costs that firms using dirty technology face parsimoniously. The fixed costs associated with the installation of clean technology lead to increasing returns to scale, which implies that only firms above a certain size threshold choose to install the clean technology in our model. For a given distribution of managerial talents and distortions, the model generates endogenously a distribution of firm sizes and a negative association between firm size and pollution intensity. To discipline our quantitative analysis, we require our benchmark model to match the observed pollution intensity, clean technology adoption rate, size-dependent distortions, and firm size distribution in China. %Distortions in the model is measured using variations in average products of capital and labor across firms following \citet{HsiehKlenow:2009, HsiehKlenow:2014}.

Our quantitative results show that removing correlated distortions from both sectors would increase mean firm size by 130\% and aggregate output by 30\%, while lowering the pollution intensity of the polluting sector by 42\%. Since both sectors share similar distributions of firm TFP and distortions in the data, eliminating correlated distortions induces little reallocation across sectors. Therefore, aggregate pollution drops by 23\% because the technique effect dominates the scale effect. About half of the technique effect comes from the reallocation of factors across firms, while the rest is from a 27 percentage points increase in the adoption rate of clean technology. %Meanwhile, the proportion of firms using clean technology would increase by 27\%.% The drop in pollution comes from both the reduction in pollutants generated during the production stage and the increase in the adoption rate of clean technologies in the treatment stage. Each stage contributes to about 50\% of the total reduction.%\footnote{As noted earlier in this section, firms can take actions to cut their emissions levels in two stages. In the model, we focus on firms' choice of end-of-pipe treatment technologies, which we can directly observe and measure in the data. We capture the decrease in pollution intensity during the production stage in a reduced-form way, which is calibrated to the data.}
%The expansion of productive firms is crucial to both channels.
To isolate the importance of the \textit{progressiveness} of distortions, we solve a version of the model in which the progressive taxes are replaced with flat taxes while holding the total tax revenue constant. Our results show that while the progressiveness of distortions does not imply large output losses (7\%), it plays a central role in amplifying aggregate pollution (30\%).
% where all firms in the economy face the same level of distortions. In our model, the size dependency of the distortions does not imply large output loss.  However, it plays a central role in determining the pollution level. Removing the distortions altogether provide a useful upper bound to gauge the maximum gains that can be obtained by moving the economy to its first best.

In the second experiment, we increase the regulations to the extent that the fraction of firms adopting clean technology is the same as in the first experiment. We find that the policy reduces aggregate pollution by 14\%, but has very limited effect on aggregate output in the long run. %\footnote{A complete welfare analysis of tightening environmental regulations is beyond the scope of this paper, since we do not have enough data to estimate the increase in government expenditures when environmental regulations are tightened. We leave this important question to future research.} %
Comparing this with the first experiment, we find that tightening environmental regulations {improves} the resource allocation on the \textit{extensive} margin of resource allocation by driving small unproductive firms out of the economy. However, the allocation {worsens} on the \textit{intensive} margin in the sense that among the remaining active firms, the production of medium-sized firms expands more at the expense of that of large firms. %In addition, environmental regulation also amplifies the effects of size-dependent distortions by increasing the average size of active firms and consequently the average level of distortions in the economy.
In contrast, the removal of correlated distortions improves the allocation on both margins.

Overall, the key message from our findings is that policy distortions and market inefficiencies force developing countries such as China to operate within the production possibility frontier between economic output and environmental quality. Therefore, contrary to a popular belief among some policymakers in developing countries, there is not necessarily a trade-off between economic growth and pollution. Both an increase in output and a reduction in pollution can be attained by reducing policy distortions and market inefficiencies.

%Our findings have novel implications for the relationship between economic growth and pollution, both for the case of China and for developing countries in general. The environmental Kuznets curve (EKC henceforth) predicts an inverse U-shaped relationship between pollution and income per person, which implies a trade-off between economic growth and pollution when the income per person is low. There is a popular belief that China and other developing countries on the increasing part of the EKC and any policies that promote economic growth would necessarily cause more pollution. Our results suggest that a double-dividend where increase in the output and reduction in pollution are achieved simultaneously [\citet{Goulder:1994}] can be attained with policies that target at reducing the size-dependent economic frictions. Therefore, our paper sheds light on how environmental pollution can be controlled without damaging economic growth in developing countries.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                       STARTING LITERATURE REVIEW
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\textit{Related Literature.}---This paper is closely related to studies on the aggregate consequences of misallocation across heterogeneous firms. Pioneers in this field such as \citet{Guneretal:2008}, \citet{RestucciaRogerson:2008}, and \citet{HsiehKlenow:2009} establish that firm-level distortions can potentially cause large losses to aggregate output, especially those that correlate with firm size or productivity.\footnote{For more recent works, see \citet{Bartelsmanetal:2013}, \citet{Bhattacharyaetal:2013}, \citet{HsiehKlenow:2014}, \citet{BentoRestuccia:2016}, and \citet{Guneretal:2017}, among others. \citet{RestucciaRogerson:2013}, \citet{Hopenhayn:2014b}, and \citet{RestucciaRogerson:2017} summarize important contributions to the literature.} Our study shows that the impact of firm-level distortions goes beyond aggregate economic output: they cause not only a large decrease in aggregate output, but also a large increase in aggregate pollution. By considering both aggregate output and pollution, our study thus provides a more complete understanding of the consequences of policy distortions given the large costs of pollution in developing countries such as China.%\footnote{\citet{GreenstoneJack:2015} summarize recent studies on the pollution problems of developing countries, and document poor environmental quality and high health and productivity costs of pollution in these countries.}
%We view our approach as complementary to that work. In this paper, we build a macroeconomic model with rich quantitative implications which facilitates the investigation of policy related questions. Our focus on the firm size distribution and treatment technology adoption also distinguishes our paper from that literature, which studies the roles of product mix, consumer preference, etc. In connection with literature focusing on the cross-country comparison of firm size distributions [for example \citet{Poschke:2014}], our paper is also a candidate of structural interpretations of the EKC.

% We contribute to a large strand of the literature on the relationship between economic growth and environment. At the heart of the literature is the environmental Kuznets curve. \citet{GrossmanKrueger:1993, GrossmanKrueger:1995}, followed by many others, establish empirically a hump-shaped relationship between a country's per-capita income and its environmental quality.\footnote{\citet{CopelandTaylor:2004} provides a review on this literature.} %\footnote{\citet{CopelandTaylor:2004} identify three channels through which economic growth can affect environmental outcomes: scale (total production), technology, and industry composition. However, our study contributes to the literature by emphasizing the importance of a new channel, namely factor allocation across firms, and its interaction with the scale and technology channels. Further, in contrast to most studies of this topic, pollution treatment technology is endogenous in our study and we use the model and data to quantify the role of the adoption of such endogenous technology.} Many scholars have interpreted this fact as evidence of an unavoidable trade-off between economic growth and environmental improvement when per-capita income is low, and there is a popular belief that growth-promoting policies necessarily lower environmental quality in China and other developing countries. We challenge this view by showing that removing distortions leads to both higher aggregate output and lower aggregate pollution in China. %\footnote{Several recent studies also examine the extent to which factor allocation across firms affects aggregate pollution. By using Indian manufacturing data, \citet{BarrowsOllivier:2016} find that the reallocation of resources across firms explains more than 50\% of the decline in aggregate $\text{CO}_2$ emissions intensity in India between 1990 and 2010. Similarly, by using U.S. manufacturing data, \citet{ShapiroWalker:2015} find that emissions reductions in the United States are primarily driven by the decline in within-product emissions intensity. They further use a quantitative model to show that the increasing stringency of environmental regulations explains most of the emissions reduction. \citet{Martin:2013} estimates empirically the relative contribution of changes in different policies for India. Our work complements these studies in that we emphasize the importance of size-dependent distortions, and our data allow us to speak directly of quantifying the importance of adopting endogenous treatment technology.} The broad message from our findings is that policy distortions and market inefficiencies typically force developing economies to operate within the production possibility frontier between economic output and environmental quality. Therefore, both an increase in output and a reduction in pollution can be attained by reducing policy distortions and market inefficiencies.%\footnote{There is a large literature in environmental economics that discusses the possibility of a double dividend from environmental taxes, namely a simultaneous improvement in the environment and in economic efficiency by replacing other distortive taxes with environmental taxes. Our finding that environmental regulations improve resource allocation along the extensive margin is consistent with this literature. \citet{Goulder:1994} and \citet{FullertonMetcalf:1997} review the early work on this question.}

%The present study also provides a novel mechanism that could explain the declining part of the environmental Kuznets curve. One of its key findings is that large firms have lower pollution intensity. Recent empirical studies such as \citet{Poschke:2014} and \citet{BentoRestuccia:2016} find that mean firm size in the manufacturing sector increases with a country's per-capita income, with \citet{HsiehKlenow:2014} and \citet{BentoRestuccia:2016} attributing the cross-country differences in firm size largely to the cross-country differences in distortions. These two facts together imply that the decrease in distortions would contribute to the decline in aggregate pollution as per capita income increases.

This paper also contributes to a growing literature in environmental economics that emphasizes the importance of firm-level heterogeneity. One line of research uses the heterogeneous firms framework to evaluate specific environmental policies. \citet{LiSun:2015} and \citet{LiShi:2017} compare the welfare effects of emission taxes and standards. Their theoretical findings imply that emission taxes will generally be favored when the dispersion of productivity across firms is large. Relatedly, \citet{TombeWinter:2015} use a heterogeneous firms model calibrated to the U.S. to evaluate the productivity losses from output-based intensity standards. They find that these losses can be large. We differ from this line of research by our focus on how correlated distortions affect aggregate pollution and how they interact with environmental policies.
%our emphasis on the tight connection between our theory and firm-level data.

Another line of research focuses on how international trade affects the environment through resource reallocation across heterogeneous firms. \citet{Cherniwchanetal:2017} provide a comprehensive survey of recent contributions.\footnote{Notable examples include \citet{Martin:2013}, \citet{Cherniwchan:2017}, \citet{BarrowsOllivier:2016}, \citet{Forslidetal:2015}, and \citet{ShapiroWalker:2015}. A more detailed comparison between our paper and this line of research can be found in Online Appendix H.} Our paper differs from this literature in two aspects. First, most studies in this literature, with the exception of \citet{ShapiroWalker:2015}, are empirical where models are used primarily to motivate the empirical specification indirectly. Instead, we discipline our general equilibrium model using firm-level data directly in an internally consistent way, and quantitatively assess counterfactual policies using the model. Our quantitative analysis explicitly takes into account the general equilibrium effects of alternative policies, allowing us to investigate novel policy implications that are absent from reduced-form or partial equilibrium analyses. Second, using the firm-level data on treatment technologies, we provide an explanation for the negative correlation between firm size and pollution intensity. It allows us to not only investigate the overall effects of distortions, but also quantify an important channel through which the distortions affect emissions, namely, the adoption of clean technology.
%Recently, a growing literature studies how international trade affects industrial pollution through the reallocation of resources across heterogeneous firms; see \citet{Cherniwchanetal:2017} for a comprehensive survey. Our paper differs from this closely related literature in several ways.\footnote{A more detailed review of the difference between our paper and this literature is deferred to Online Appendix H.} First, while most studies in this literature use either reduced-form or purely theoretical analysis, with the exception of \citet{ShapiroWalker:2015}, we complement these studies by providing a quantitative assessment of the general equilibrium effects of alternative policies on output and emissions, using an internally-consistent model disciplined by firm-level data.\footnote{Some studies in the literature, for example, \citet{Forslidetal:2015}, prove some qualitative results in general equilibrium under certain assumptions on model parameters, while they do not take the model to data directly.} The quantitative nature makes our analysis suitable for evaluating alternative policies. Second, the information on treatment equipment used by firms allows us to provide an explanation for the negative correlation between firm size and pollution intensity, and to investigate not only the overall effects of distortions, but also an important channel through which the distortions affect emissions, namely the adoption of clean technology.\footnote{In this regard, our work shares similar spirits with empirical studies like \citet{BarrowsOllivier:2016} that study how trade liberalization affect carbon emissions through changes in the product-mix of firms, and \citet{Bustos:2011} that study how trade liberalization improves firm productivity by inducing more investment in technology.} Third, while the literature focuses on trade costs, we focus on domestic distortions, and these two types of frictions interact with environmental regulations in different ways. In our model, environmental regulations would worsen resource allocation along the intensive margin, but this may not be the case with trade costs, because the (more productive) exporting firms can use foreign markets as a cushion to buffer the burdens from environmental regulations after paying the trade costs.

%Our paper differ from a recent literature in international trade surveyed in \citet{Cherniwchanetal:2017} that also investigate how resource allocation across heterogenous firms affects industrial pollution in several important ways.\footnote{In the interests of space, we leave a more extensive review of the difference between our paper and this literature to the Online Appendix I.} First, the theoretical implications of our model on resource allocation along the intensive margin under the policy-relevant scenario where environmental policies are changed while keeping trade costs (a form of distortion) fixed are different from those of the models used in these studies. While our model implies that in these situations resource allocation along the intensive margin worsens, in those studies it is improved because exporting firms can use foreign markets as a cushion to buffer the increase in costs.\footnote{Loosely speaking, the counterpart of an increase in environmental regulation could be interpreted as an increase of the fixed entry cost $f$ in the original \citet{Melitz:2003} model. An increase in $f$ perturbs the optimal decisions of all firms by affecting the aggregate price index $P$ through general equilibrium effect. Since the revenues of exporting firms come from both domestic sources that are affected, and foreign sources that are not, they are less affected by the increase in $f$.} Such difference of our model offers a novel policy message compared to these papers and shows the conceptual difference of domestic distortion and trade costs.\footnote{The difference is not caused by our use of a \citet{Lucas:1978b} model instead of a \citet{Melitz:2003} model. Rather, it is because distortions in our model is a pure cost, while in the \citet{Melitz:2003} model, firms pay trade costs to access to foreign markets, which bring additional revenues. If instead we model in the \citet{Melitz:2003} model similar ``deadweight-loss'' distortions, we would get similar results.} Second, the quantitative nature of our study allows us to analyze in general equilibrium how output and emissions respond to distortions and environmental policies simultaneously, making it suitable to evaluate quantitatively scenarios such as whether a decrease in pollution intensity coupled with a larger increase in output would lead to an increase in aggregate pollution. The local nature of the empirical estimates in these studies are not designed to answer questions like this.\footnote{Some of these studies prove some qualitative results in general equilibrium under certain assumptions on model parameters, however they did not take the model to data directly on this respect [\citet{Forslidetal:2015}].} Our paper demonstrates the potential and the importance of studying environmental issues quantitatively. From a methodological perspective, our work is similar to that of \citet{ShapiroWalker:2015}. Third, the fact that we observe directly the emissions and treatment equipments of firms in the data allows us to investigate how distortions affect emission through a specific channel, that is the adoption of clean technology, instead of an overall effect of distortions (trade costs to be specific) to emissions [\citet{Martin:2013}, \citet{Forslidetal:2015}, and \citet{ShapiroWalker:2015}]. In this regard, our work shares similar spirits with empirical studies like \citet{BarrowsOllivier:2016} that study how trade liberalization affect carbon emissions through changes in the product-mix of firms, and \citet{Bustos:2011} that study how trade liberalization improves firm productivity by inducing more investment in technology.

Finally, our results highlight the role of firm size and misallocation for technology adoption in developing countries. As emphasized by \citet{ParentePrescott:1994, ParentePrescott:1999}, an important task in development economics is to understand the slow rate of technology adoption in developing countries. Recent contributions include \citet{Bustos:2011}, who study the role of tariff reductions, and \citet{Acemogluetal:2012}, who focus on taxes and subsidies. %and \citet{ColeGreenwoodSanchez:2016}, who emphasize the importance of contractual frictions and financial market inefficiencies.
Using direct observations on the adoption of pollution treatment technologies by firms, we establish empirically that firm size plays a key role in technology adoption. Our quantitative framework thus allows us to quantify how policy distortions and market inefficiencies that distort firm size would impede technology adoption. %If we view tariffs as a particular type of policy distortion, our results share a similar increasing returns to scale intuition with that of \citet{Bustos:2011}, who shows empirically that a bilateral reduction in tariffs induces more firms to adopt a new technology with a fixed cost. Our study also differs from hers in that the quantitative framework we adopt allows us to evaluate the effect of regulatory policies with the presence of distortions and analyze the economic mechanism. %This conclusion applies generally to cases in which technology adoption exhibits increasing returns to scale.\footnote{In a different setting, \citet{OlmsteadRhode:2001} study the adoption of tractors in the U.S agriculture between 1910--1960, and they also find that larger farm scale induced greater adoption of tractors.}

The remainder of the paper proceeds as follows. Section \rom{1} describes the data sources and empirical findings of this paper. Section \rom{2} introduces the model and analyzes its property. We calibrate the model in Section \rom{3}, and perform counterfactual experiments to study the effects of correlated distortions and environmental policies in Section \rom{4}. Section \rom{5} concludes the paper.

%The remainder of the paper proceeds as follows. Section \rom{1} discusses the two facts that motivate our study in details. We describe the model and use it to estimate the firm-level distortions in Section \rom{2}. We calibrate the model in Section \rom{3} and perform several policy experiments to study the interaction between size-dependent distortions and environmental policies in Section \rom{4}. Section \rom{5} concludes the paper.

\section{Empirical Analysis}

In this section, we describe our empirical findings on the firm-level pollution intensity and the firm size distribution in China. We start by introducing the data sources we use, and then document the key facts on pollution intensity, pollution treatment technologies and employment shares across firms of different sizes. In the end, using a simple accounting exercise, we show that firm size distribution plays a quantitatively important role in aggregate pollution intensity.

%In this section, we describe the key empirical findings that suggest firm size distribution as an important factor affecting aggregate pollution. We start by introducing the data and then explain the two motivating facts mentioned before in details. In the end, by using an accounting exercise, we show that firm size distribution has a sizable effect on aggregate pollution.

\subsection{Data Sources}
\label{sec:data_source}

This study draws upon three major data sources: the 2007 National General Survey of Pollution Sources (NGSPS) in China, the 2004 China National Economic Census (CNEC), and the Statistics of U.S. Businesses (SUSB).

%This study draws upon three major data sources to calculate the pollution intensity of Chinese manufacturing firms and the firm size distributions of manufacturing firms in China and the United States: China's National General Survey of Pollution Sources (NGSPS), China's National Economic Census (CNEC), and the Statistics of U.S. Businesses (SUSB).\footnote{In the interest of brevity, we defer a more detailed description of these data to Online Appendix A.}

\textit{NGSPS.}---The NGSPS was a joint effort of multiple national ministries in China.\footnote{A more detailed description of the dataset can be found in Online Appendix A.} It covers all of the pollution units from the agricultural, industrial, and domestic sources, as well as facilities for the centralized treatment of pollution. In this study, we focus on the {industrial pollution sources}, which consist of businesses generating pollutants from the 39 manufacturing industries. The survey is organized directly by the State Council with data collection and quality control done by specially trained field staffs. According to the \textit{Regulation on the National General Survey of Pollution Sources [Decree of the State Council of the People's Republic of China (No. 508)]}, faking data would lead to financial penalties or even lawsuits. Therefore, the dataset is administrative in nature and is subject to less concerns of systematic under-reporting.\footnote{In fact, uniform under-reporting of emissions by small and large firms will not change the basic conclusions of this paper. Our results will be contaminated only if under-reporting by large firms is more severe than that by small firms, which is less likely in most polluting industries since larger firms are usually inspected more carefully. For instance, many large firms in these industries are identified as \textit{Key Pollution Sources}, and therefore are inspected and monitored by the government routinely and carefully, making it harder for them to fake data during this one-time survey.} While we are not aware of other economic studies that use NGSPS, a number of studies in environmental sciences have used this dataset.\footnote{See \citet{Niuetal:2016} and \citet{Qietal:2017} and the references therein for recent examples.}

%\textit{NGSPS.}---The 2007 NGSPS was a joint effort of multiple national ministries in China. The survey records data for 2007. It is designed to cover {all} entities and self-employed households that emit pollutants in China. The complete survey consists of four components: industrial pollution sources, agricultural pollution sources, domestic pollution sources, and facilities for the centralized treatment of pollution. In this study, we focus on the {industrial pollution data}, which include all polluting production entities that belong to any of the 39 manufacturing industries. The survey is organized directly by the State Council with data collection and quality control done by specially trained field staffs. According to the \textit{Regulation on the National General Survey of Pollution Sources [Decree of the State Council of the People's Republic of China (No. 508)]}, faking data would lead to financial penalties or even lawsuits. Therefore, the dataset is administrative in its nature and is subject to less concerns of the systematic underreporting like those documented in \citet{Dufloetal:2013} and \citet{Currieetal:2015}.\footnote{In fact, universally systematic underreporting of emissions will not change the conclusion of our paper. Our results will be contaminated if underreporting among large firms are more severe than small firms, which is less likely since these firms are usually inspected more carefully. For instance, many large firms are categorized as \textit{Nationally and Provincially Monitored Key Pollution Sources} which have to report their emissions routinely, making it harder for them to fake data during the survey process.} While we are not aware of other studies in economics that use NGSPS so far besides our own, the data in fact have been used by a large number of studies in environmental sciences.\footnote{See \citet{Niuetal:2016} and \citet{Qietal:2017} and the references therein for recent examples.}

The NGSPS collects information on the emissions of multiple air, water, and solid waste pollutants. In this paper, we focus on water pollution mainly because the data are more accurately measured than air pollution.\footnote{After our interview with the field staff, we learned that the differences in data quality was mainly caused by the differences in the sampling environment. For water pollution, firms rarely discharge wastewater directly. Instead, the wastewater is first stored in a sedimentation tank to settle heavier solids to the bottom and let lighter materials to float. This process creates a quiescent environment for sampling. For air pollutants, the sampling tube has to be placed in the chimneys, where the environment is much more volatile. Moreover, if firms were to manipulate their instant emissions when the field staff is on-site sampling, the sedimentation process makes it more difficult, since firms would have to clean the tank prior to the on-site visit of the field staff.} Among all the water pollutants, we focus on \textit{chemical oxygen demand} (COD), a major water pollutant that is commonly used to measure water quality. It measures the overall quantity of contaminants that will eventually cause oxygen loss and thus the death of living creatures. We choose COD because a much larger share of firms report positive emissions of COD compared to other pollutants. If we focus on other pollutants, such as hexavalent chromium, we would limit ourselves to a much smaller share of firms that engage in special production processes like leather tanning or pigment manufacturing.\footnote{See Table A.1 in Online Appendix A for the share of firms that report positive emissions for different water pollutants. We would like to stress that many firms do not report emissions of specific pollutants such as cyanidium or chromium simply because they do not use related materials in production. It is \textit{not} because of under-reporting or other issues related to data quality. In fact, since these pollutants are more hazardous than others, firms that discharge these pollutants are usually monitored more closely.} Moreover, COD emissions are typically highly correlated with the emissions of other pollutants when both are positive.\footnote{In the Paper and Paper Products industry, for example, the correlation between the emissions of COD and $\text{NH}_4^+$ is $\text{corr}(\text{COD},\text{NH}_4^+) = \text{0.82}$ and that between COD and BOD is $\text{corr}(\text{COD},\text{BOD}) = \text{0.94}$.}
%The NGSPS contains information on the emissions of multiple air, water, and solid waste pollutants. Here, we focus on water pollution because the data are more accurately measured than air pollution.\footnote{We have interviewed the field staff responsible for data collection about this issue. The difference in data quality was mainly caused by the differences in the sampling environment. For water pollution, firms rarely discharge wastewater directly; instead, the wastewater is first stored in the sedimentation tank to settle heavier solids to the bottom and let lighter materials to float. This process creates a quiescent environment for sampling. For air pollutants, the sampling tube has to be placed in the chimneys, where the environment is much more volatile. Moreover, if firms were to manipulate their instant emissions when the field staff is on-site sampling, the sedimentation process involved with wastewater treatment makes it more difficult, since firms would have to clean the tank prior to the on-site visit of the field staff.} The variables we use are the amount of major pollutants generated and emitted, total production value, type, book value and annual operating costs of pollutant treatment equipment, firm's industry (four-digit GB/T4574-2002), ownership classification, and province. %However, we expect that the main results of this paper could be applied to other pollution sources as well. %The raw data contain 921,004 firms.

The data reveal that industrial water pollutants are typically concentrated in a handful of industries, including COD. In our empirical analysis, we focus on the top five polluting industries in terms of COD emissions, which account for nearly 80\% of all COD emissions from industrial sources. Within narrowly defined manufacturing industries, the NGSPS divides firms into two large groups---\textit{key sources} and \textit{regular sources}. Firms identified as ``key sources'' are deemed as more polluting, and therefore are inspected and monitored by the government more carefully.\footnote{See Online Appendix A.1 for more information on the definition of key sources.} During this census, the field staff also collected extra information on these firms, and the data from these firms were inspected with greater care. Importantly, the key sources include both small and large firms, and the empirical densities of the log output of the key sources resemble the bell shape of those of all firms.\footnote{Please see Figure B.1 in Online Appendix B.} As a result, when empirically analyzing the relationship of firm size with pollution intensity and treatment technology adoption, we focus on the key sources, which account for more than 90\% of total COD emissions and 80\% of total output from the top five polluting industries (Table \ref{tab:top5summary}). %\footnote{We have also run all the following regressions using a sample including both regular and key sources, and found similar negative correlations.}
The variables we use are the firm's output, the amount of major pollutants generated and emitted, installation costs of pollutant treatment technologies, industry (up to four-digit GB/T4574-2002), ownership classification, and province.

%Environmental sciences studies find that industrial waste is typically concentrated in a handful of sectors. Further, even within narrowly defined manufacturing sectors, pollutant emissions are usually concentrated among firms that engage in some particular manufacturing processes. Grouping firms by sector thus risks blurring important within sector variations. To address this issue, the NGSPS divides the sample into two large groups---\textit{key sources} and \textit{regular sources}---where loosely speaking, firms identified as ``key sources'' are the most polluting ones. We focus on key firms in the study because they produce the majority of the pollutants (Table \ref{tab:top5summary}, which is explained in details shortly after), while most regular firms emit very little pollutants. This means that key firms are more representative of polluting manufacturing firms in China.\footnote{Online Appendix A.1 defines these key sources formally.} Moreover, the key sources include large firms as well as small firms in that the empirical density function of the log output value of the key sources resembles the same hump-shape of that of all firms.\footnote{Please refer to Online Appendix B and the two upper panels of Figure B.1 therein for details.} As a result, we use the key sources to characterize the relationship between emissions and firm size more accurately.

%Among all the pollutants, we analyze \textit{Chemical Oxygen Demand} (COD), a major water pollutant commonly used to measure water quality. COD measures the amount of oxygen consumed when a chemical oxidant is added into a sample of water. It is an indirect measure of the overall quantity of contaminants that will eventually cause oxygen loss and thus the death of living creatures. We choose COD because it is widely emitted by firms across various sectors, which allows us to keep most observations from the data. Other pollutants are emitted by significantly fewer firms because they are usually associated with the production in particular industries, which raises sample selection concerns. See Table \ref{tab:nfirmPollutant}, which lists the percentage of key sources firms that have positive emissions of different pollutants. In other words, if we focus on other pollutants, for instance hexavalent chromium, we are limiting ourselves to a handful of firms that engage in particular production processes like leather tanning and pigment manufacturing.\footnote{We would like to stress that the fact many firms do not report emissions on specific pollutants like cyanidium or chromium is simply because their production process does not involve the use of related materials. It is \textit{not} because of under-reporting or other issues related to data quality. In fact, since these pollutants are more hazardous than others, firms that discharge these pollutants are monitored more closely.} Moreover, COD emissions are highly correlated with the emissions of other pollutants.\footnote{In the Paper and Paper Products industry, for example, the correlation between the emissions of COD and those of $\text{NH}_4^+$ is $\text{corr}(\text{COD},\text{NH}_4^+) = 0.82$ and that between COD and BOD is $\text{corr}(\text{COD},\text{BOD}) = 0.94$. This suggests that if a firm discharges a large amount of COD, it is likely that it also discharges a lot of other pollutants that are specific to its production process.} Finally, we focus on {measured} end-of-pipe emissions. Online Appendix A.2 explains in detail how these data are collected. In the interests of space, we note that the information contained is different from the mix of energy sources and intermediate goods in the production process. We present the results for the top five polluting industries (29,019 firms).
%\begin{figure}[t]
%    \begin{center}
%    \includegraphics[width=0.50\textwidth]{D:/PaperDrafts/Pollution/R_Implementation/pie_R.pdf}
%    %\floatfoot{Source: National General Survey of Pollution Sources}
%    \caption{COD Emissions by Sectors}
%    \label{fig:pie}
%    \end{center}
%\end{figure}
\begin{table}[t]
\footnotesize
\centering
\begin{threeparttable}
\caption{Statistics of the Top 5 Polluting Industries by COD}
\begin{tabular}{lcccccc}
    \hline \hline
%    & Waste & COD & Petrochemicals & Ammonian & BOD & Cyanidum & Hex-Chromium & Phenol & Arsenium & Chromium \\
                                                &  & Paper & Food Processing& Textiles  & Chemical Materials & Beverages  \\ %& Med  & Fer  & Petro & Food & Fib \\
    \midrule
    \% in Total COD Emission                    &  & 33.4  & 15.1 & 14.0 & 10.4 & 4.27  \\ %& 2.98 & 2.49 & 2.32  & 2.30 & 2.15 \\
    \% of Emissions by Key Sources              &  & 99.6  & 91.8 & 91.1 & 99.7 & 65.1  \\ %& 92.9 & 99.9 & 99.9  & 96.4 & 97.8 \\
    \% of Production by Key Sources             &  & 87.2  & 69.3 & 48.3 & 98.6 & 88.1  \\ %&& 95.7 & 99.3 & 99.7  & 98.5 & 91.9 \\
    \bottomrule
\end{tabular}
\begin{tablenotes}
     \footnotesize{
     \item[$\dagger$]
     Data Source: NGSPS. The acronyms respectively refer to (with the two-digit GB/T4547-2002 classification code in parentheses): Paper and Paper Products (C22), Processing of Food from Agricultural Products (C13), Textiles (C17), Raw Chemical Materials and Chemical Products (C26), and Beverages (C15).}
%     \item[a]
%     Relative contribution to total COD emissions by each sector.
%     \item[b]
%     Percentage of total COD emissions accounted for by key firms within each sector.
%     \item[c]
%     Percentage of total production accounted for by key firms within each sector.
\end{tablenotes}
\label{tab:top5summary}
\end{threeparttable}
\end{table}

%Table \ref{tab:top5summary} contains the basic statistics on these industries. The key firms in the top five polluting industries are representative of industrial pollution in China. These industries combined contribute 77\% of total industrial COD emissions, with key firms responsible on average for more than 90\% of the within-sector emissions and more than 80\% of the within-sector output.

\textit{CNEC.}---The CNEC was conducted by the National Bureau of Statistics in China. It was designed to cover {all} businesses that undertake economic activities in the secondary and tertiary industries in China. We use observations that belong to the manufacturing sector. The variables we use are the firm's output, labor compensation, book value of capital stock, number of employees, industry (up to four-digit GB/T4574-2002), ownership classification, and province.\footnote{A widely used firm-level dataset in China is the Annual Surveys of Industrial Firm (ASIF). We use CNEC instead of ASIF because that ASIF does not have information on non-state firms with sales below 5 million CNY, which are crucial for our analysis. If we used the 2004 ASIP, we would have missed 29\% of the employment and 80\% of the firms.}%\footnote{It is important to use the CNEC rather than the commonly used \textit{Annual Surveys of Industrial Production (ASIP)} for which the 2007 data are available (the same year that the NGSPS covers). The reason is that the CNEC surveys firms of {all} sizes as opposed to only firms with a revenue of more than CNY 5 million in the ASIP. In 2004, the number of firms and employees covered by the annual survey were 276,410 and 66,725,059, respectively, while those covered by the census were 1,375,148 and 93,541,923. Therefore, we would be missing 28.6\% of employment and 79.9\% of firms had we used only the annual survey. %The number of firms covered in the NGSPS and CNEC, 921,004 and 1,375,148, are broadly consistent given that the former further requires a production entity to have pollution sources in order to be included.Online Appendix B provides more details. However, the basic features such as the variable definitions are essentially the same in these two datasets. \citet{Brandtetal:2012} describe the annual surveys in detail.}

\textit{SUSB.}---The SUSB from the U.S. Census Bureau, is an annual series that provides national and subnational data on the distribution of economic activities by firm size and industry. We use the data on total employment by firm size and industry from 2004.

\subsection{Firm Size and Pollution Intensity}

\begin{figure}[t]
    \begin{center}
    \includegraphics[width=0.40\textwidth]{./Figures/pooled_intensity_size.pdf}%
%    \includegraphics[width=0.40\textwidth]{D:/PaperDrafts/Pollution/R_Implementation/agri_R.pdf} \\
%    \includegraphics[width=0.40\textwidth]{D:/PaperDrafts/Pollution/R_Implementation/textile_R.pdf}
%    \includegraphics[width=0.40\textwidth]{D:/PaperDrafts/Pollution/R_Implementation/chemmat_R.pdf} \\
%    \includegraphics[width=0.40\textwidth]{D:/PaperDrafts/Pollution/R_Implementation/bever_R.pdf}
%    \includegraphics[width=0.40\textwidth]{D:/PaperDrafts/Pollution/R_Implementation/nitro_R.pdf} \\
%    \vspace{-1em}
    \caption{Firm Size and Pollution Intensity}
    \floatfoot{Source: NGSPS. Line: Least square fit. Residuals after controlling for the covariates are plotted.}
    \label{fig:codscatter}
    \end{center}
\end{figure}

\textit{Firm Size and Pollution Intensity.---}To examine the statistical relationship between pollution intensity and firm size for the polluting sectors in China, we run the following regression using data on firms identified as ``key sources'' in the top five polluting industries:
\begin{equation}
%    \log (\text{COD}_i) = \underset{(0.17)}{-3.75} + \underset{(0.01)}{0.63} \times \log (\text{Output}_i) + \vec{X_s} \gvec{\upgamma}_1 + \vec{X_p} \gvec{\upgamma}_2 + \vec{X_o} \gvec{\upgamma}_3 + \varepsilon_i,
    \log (\text{COD}_i) = \underset{(0.17)}{-3.75} + \underset{(0.01)}{0.63} \times \log (\text{Output}_i) + \vec{X} \gvec{\upgamma} + \varepsilon_i,
\label{eq:poolols}
\end{equation}
where $\vec{X} = \{\vec{X_s}, \vec{X_p}, \vec{X_o}\}$ refers to the dummy variables for two-digit industry, province, and ownership respectively. The estimates are all statistically significant at the 0.1\% level, with the standard errors reported in the parentheses below the estimates.

These estimates imply that as a firm's output increases by 1\%, its COD emissions would on average increase by only 0.63\%. We define pollution intensity as COD emissions per unit of output. Then the above estimates imply an elasticity of $-$0.37 between firm-level pollution intensity and output. That is, other things equal, a 1\% increase in firm output is associated with a 0.37\% decrease in pollution intensity. %\footnote{Notice that regression (\ref{eq:poolols}) is mathematically equivalent to $\log(\text{COD}_i/\text{Sales}_i)= \beta_0 + \beta_1 \log(\text{Sales}_i) + \gvec{\upgamma}\vec{X} + \varepsilon_i$.}
Figure \ref{fig:codscatter} visualizes this negative relationship, where the residuals from regressing intensity and output on the dummies are plotted to remove the influences of other covariates.\footnote{Recall that here by the \textit{Regression Anatomy Formula}, the slope of the least square fit in Figure \ref{fig:codscatter} is precisely one minus the coefficient on $\log(\text{Output})$ in Equation (\ref{eq:poolols}).} The estimation has an $R^2$ of 0.47, suggesting that nearly half of the variations in COD emissions can be explained by the variations in firm output and in the three sets of dummies.\footnote{We also tried other econometric specifications, and found similar negative correlations between pollution intensity and firm size. For instance, we estimated versions of Equation (\ref{eq:poolols}) for each industry and with robust standard errors clustered in provinces. Please see Online Appendix C for more information.} We would also like to point out that the coefficient of the dummy on whether a firm is state-owned or not, is statistically \textit{insignificant}. %\footnote{This finding is different from that of \citet{Jiangetal:2014}. We think that this could be because we are using a different sample of firms. Specifically, while their data cover the Nationally Monitored Key Pollution Sources, ours have a much broader coverage.}
As a result, we do not distinguish between whether a firm is state-owned or not in our later analysis.

%the regression results indicate that pollution intensity decreases as firm sales rise. Specifically, by subtracting $\log (\text{Sales}_i)$ on both sides of Equation (\ref{eq:poolols}), the elasticity between pollution intensity and total sales is $-$0.37, which means that other things being equal, doubling total sales is associated with a 37\% decrease in pollution intensity.\footnote{Notice that regression (\ref{eq:poolols}) is mathematically equivalent to $\log(\text{COD}_i/\text{Sales}_i)= \beta_0 + \beta_1 \log(\text{Sales}_i) + \gvec{\upgamma}\vec{X} + \varepsilon_i$.} Figure \ref{fig:codscatter} shows this negative relationship, where the residuals from regressing intensity and sales on the dummies are plotted to remove the influences from other control variables.\footnote{Recall that here by the \textit{Regression Anatomy Formula}, the slope of the least square fit in Figure \ref{fig:codscatter} is precisely one minus the coefficient on $\log(\text{Sales})$ in Equation (\ref{eq:poolols}).} The estimation has an $R^2$ of 0.47, which suggests that a fair amount of variation can be explained by the variations in total sales and in the three sets of dummies.\footnote{We also estimated the relationship by using other econometric specifications. For instance, we estimated versions of Equation (\ref{eq:poolols}) for each industry and with robust standard errors clustered in different groups. All the regressions suggest the same negative qualitative relationship between intensity and size. The estimation results of the other specifications as well as the interpretations of the coefficients before the dummies are included in Online Appendix C.} It is important to emphasize that the coefficients of the ownership dummies ($\gvec{\upgamma}_3$)---that is whether a firm is state-owned, collectively owned, etc---are statistically \textit{insignificant}. %\footnote{This finding is different from that of \citet{Jiangetal:2014}. We think that this could be because we are using a different sample of firms. Specifically, while their data cover the Nationally Monitored Key Pollution Sources, ours have a much broader coverage.} As a result, in the remaining of the paper, we do not distinguish between whether a firm is state-owned or privately owned.

%We define pollution intensity as follows:
%\begin{equation*}
%    \text{Intensity} = \frac{\text{Total COD Emissions}}{\text{Total Production value}}.
%\end{equation*}
%We group firms into quartiles based on their total output value. For each industry, we calculate the output-weighted average of the pollution intensity of the firms in each quartile. Table [] reports the results. For the Paper and Paper Products industry, the pollution intensity of the firms in the bottom quartile is 6.7 times that of the firms in the top quartile. The difference can be as large as 31.4 times, as is the case for the Beverages industry. Moreover, pollution intensity decreases continuously as firm size rises. This trend can also be seen from the scatterplot of the logarithm of intensity against that of total production value. We plot the Paper and Paper Products industry in Figure \ref{fig:codscatter} as an example. It shows a significant negative correlation between log-intensity and log-production in the data. The scatterplots for the other four industries are deferred to Online Appendix C.%for the top-5 polluting industries are presented  (except the bottom-right one).

%\begin{table}[t]
%\footnotesize
%\centering
%\begin{threeparttable}
%\caption{Firm Size and Pollution Intensity}
%\begin{tabular}{p{120pt}>{\centering\arraybackslash}p{45pt} >{\centering\arraybackslash}p{45pt} >{\centering\arraybackslash}p{45pt} >{\centering\arraybackslash}p{45pt}}
%    \hline \hline
%        & \multicolumn{4}{c}{Quartile of Firm Sales} \\
%    \cmidrule{2-5}
%    Industry & $\text{QU}_1$ & $\text{QU}_2$ & $\text{QU}_3$ & $\text{QU}_4$ \\
%    \midrule
%    Paper               & 6.7   & 3.2   & 2.0 & 1.0 \\
%    Agricultural Food   & 20.8  & 7.6   & 3.6 & 1.0 \\
%    Textiles            & 8.3   & 3.6   & 2.4 & 1.0 \\
%    Chemical Materials  & 6.7   & 3.8   & 2.7 & 1.0 \\
%    Beverages           & 31.4  & 18.7  & 4.7 & 1.0 \\
%    \bottomrule
%\end{tabular}
%\begin{tablenotes}
%     \footnotesize{
%     \item[$\dagger$]
%     Data Source: NGSPS. $\text{QU}_1$ to $\text{QU}_4$ represent the bottom to top quartiles, respectively. The pollution intensity of the top quartile of each industry is normalized to one.}
%\end{tablenotes}
%\label{tab:intensityquartile}
%\end{threeparttable}
%\end{table}
%\footnote{One exception is Chemistry Materials, the middle right panel. Further investigation into the data reveals that the reason that we do not observe a negative correlation in the Chemistry Material industry as clear as in the other industries is because there are many sub-industry level heterogeneities pooled at the two-digit level. To show that this is indeed the case, we repeat the exercise for the top polluting four-digit industry within the Chemistry Material industry, {Nitrogen Fertilizer} (C2621) which ranks the sixth among all four-digit industries. The result is shown in the lower right panel of Figure \ref{fig:codscatter}, where the negative correlation is clear. Put differently, the ``circle'' we see in the Chemistry case is in fact a combination of several ``ellipses'', each with a downward sloping transverse diameter. We have also plotted these figures using the residuals from regressions (\ref{eq:indols}) and (\ref{eq:poolols}). The results are almost the same and are thus shown Online Appendix. This is confirmed by including four-digit industry dummy in the regression for Chemistry industry specified below. After introducing four-digit industry dummies, the magnitude estimates for $\beta_1$ increases to $-$0.21 and the $R^2$ increases to 0.26. Both numbers are now of comparable magnitudes with the other industries.}

%\begin{equation}
%    y_i = \beta_0 + \beta_1 V_i + \vec{X_p}\beta_2 + \vec{X_o}\beta_3 + \varepsilon_i
%
%\end{equation}
%We then run a pooled regression with :
%\begin{equation}
%    y_i = \beta_0 + \beta_1 V_i + \vec{X_p}\beta_2 + \vec{X_s}\beta_3 + \vec{X_o}\beta_4 + \epsilon_i
%\label{eq:poolols}
%\end{equation}

%Regression results from (\ref{eq:indols}) and (\ref{eq:poolols}) are shown in Table \ref{tab:olsresults}.
%\begin{table}[t]
%\footnotesize
%\centering
%\begin{threeparttable}
%\caption{OLS Regression Results}
%\begin{tabular}{ccccccc}
%    \hline \hline
%    Parameters & Paper           & Agri            & Textile         & Chem            & Bever           & Pooled          \\
%    \midrule
%    $\beta_0$  & $-$4.25$^{***}$ & $-$2.23$^{***}$ & $-$3.73$^{***}$ & $-$7.17$^{***}$ & $-$2.82$^{***}$ & $-$2.50$^{***}$ \\
%               & (0.56)          & (0.26)          & (0.57)          & (0.33)          & (0.38)          & (0.17)          \\
%    $\beta_1$  & $-$0.30$^{***}$ & $-$0.61$^{***}$ & $-$0.31$^{***}$ & $-$0.13$^{***}$ & $-$0.45$^{***}$ & $-$0.37$^{***}$ \\
%               & (0.01)          & (0.01)          & (0.01)          & (0.01)          & (0.02)          & (0.01)          \\
%    $R^2$      & 0.22            & 0.46            & 0.14            & 0.08            & 0.29            & 0.37            \\
%    \midrule
%    $N$        & 5626            & 6883            & 6281            & 8672            & 1557            & 29019 \\
%    \bottomrule
%\end{tabular}
%\begin{tablenotes}
%     \footnotesize{
%     \item[$\dagger$]
%     Note: All regressions include complete sets of provincial and ownership rights dummies. The pooled regression includes in addition two-digit industry dummies. OLS standard errors are reported in parentheses. Regressions with robust standard errors clustered on provinces (industry level regression) and industries (pooled regression) yield very similar results are reported only in Online Appendix for brevity. Statistical significance code: $^{***}$ $p < 0.001$.}
%\end{tablenotes}
%\label{tab:olsresults}
%\end{threeparttable}
%\end{table}
%Estimation results in Table \ref{tab:olsresults} confirm observations in Figure \ref{fig:codscatter}. The intensity-production elasticities $\beta_1$ are all accurately estimated to be negative and they are also of economic significance. The $R^2$ shows that a fair amount of variation observed in the intensity is changing with production scale. As a crude calculation, the coefficient $-$0.37 on $\log V_i$ for the pooled case implies that by doubling the production scale, the COD discharged per unit production will decrease by 37\%.\footnote{The pollution intensity also exhibits rich provincial level variations. We leave the discussion to Online Appendix.}

%The pollution intensity also exhibits rich provincial level variations. We take the regression on the paper industry for example. Using Beijing as the benchmark, of all the remaining 29 provinces and municipalities, only the coefficient of Shanghai is negative and statistically insignificant. For the remainders, all estimates positive and highly significant.\footnote{One province, Hebei is significant at 10\% level. Four others are significant at 1\% level while all others are significant at 0.1\% level. We notice here Hebei, a province that is seriously disturbed by industrial pollution, is in fact an outlier as the paper manufacturing is not its pillar industry.} The bottom-five provinces (those with largest dummy estimates) are Ningxia, Inner Mongolia, Gansu, Shaanxi and Xinjiang, for which the rankings of their provincial GDP in 2007 are respectively 29, 16, 27, 19 and 25 out of 31 provincial administrative regions (not including Hong Kong and Macau). Geographically, these are also inland provinces. In fact, despite that the majority of the paper manufacturers belong to the Zhejiang and Guangdong (GDP ranking 1st and 4th), the pollution problem is of less severity as opposed to those inland less developed regions. These patterns are highly robust across various versions of our regressions. The general message we get from these dummy coefficients are the following. First, Beijing and Shanghai, arguably the political and economic center of China, exert pollution control standard far more stringent than the rest provinces. Second, inland and less developed provinces in general have worse control over and are more prone to the industrial pollution problem. These two patterns are broadly consistent with the EKC and results from previous literature. However, unlike \citet{Jiangetal:2014}, ownership rights do not seem to have significant effect. If anything, the Foreign and Hong Kong, Macau and Taiwan based firms seem to have weakly better pollution controls. But the statistical significance of the estimates never exceed 10\% across all our regressions. We think this could well because their estimates are derived using a limited sample of firms (1931) while our data cover the universe of firms.

%\subsection{Firm Size and Treatment Technologies}

\textit{The Role of End-of-Pipe Treatment Technologies.---}An important question is, why do larger firms have lower pollution intensity? To answer this question, we exploit the detailed information on the end-of-pipe wastewater treatment technologies that firms use in the NGSPS. The NGSPS groups wastewater treatment technologies into five categories: physical, chemical, physio-chemical, biological, and {combined} technologies. In the subsequent analysis, we drop {physio-chemical} technologies because fewer than 0.5\% of the firms adopt this type of technologies. In addition, because {combined} technologies look very similar to biological technologies for all the technical aspects we are interested in, we group them with {biological} technologies.\footnote{Examples of the technologies attributed to these three base categories include filtering, centrifuging, precipitation, and separation (physical); oxidation reduction and neutralization (chemical); and aerobic biological treatment and activated sludge processes (biological). Broadly speaking, physical technology corresponds to the \textit{Preliminary} and \textit{Primary} treatment in the U.S., while chemical and biological technologies correspond to the \textit{Secondary} and \textit{Tertiary} treatment.} In sum, we are left with three broad categories of technologies.%Among all the technical aspects, we are particularly interested in the abatement efficiency and fixed installation costs of these technologies.%\footnote{We do not include the annual {operating costs} in our analysis because we do not model how much a firm uses its abatement equipment. Adding the operating costs to the installation costs does not change the results in this section. Hence we exclude the operating costs here for consistency. See Online Appendix D.2 for more details.}

%\textit{The Role of Treatment Technologies.---}The negative firm size--intensity relationship does not explain why larger firms pollute with less intensity. To answer this question, we exploit the detailed information in the NGSPS on the end-of-pipe wastewater treatment equipment that firms use. The NGSPS groups wastewater treatment technologies into five categories: physical, chemical, physio-chemical, biological, and combined technologies. In the subsequent analysis, we drop {physio-chemical} technologies because fewer than 0.5\% firms adopt this type of equipment. Further, because {combined} technologies are different combinations of biological technologies with other technologies, and for all the technical aspects we are interested in they look very similar to biological technologies, we group them with {biological} technologies.\footnote{Examples of the technologies attributed to these three base categories include filtering, centrifuging, precipitation, and separation (physical); oxidation reduction and neutralization (chemical); and aerobic biological treatment and activated sludge processes (biological). Broadly speaking, physical treatment corresponds to the \textit{Preliminary} and \textit{Primary} treatment in the United States, while chemical and biological treatment relates to the \textit{Secondary} and \textit{Tertiary} treatment and those that are more advanced.} We are interested in the processing efficiency and installation costs of these technologies.\footnote{We do not include the annual {operating costs} in our analysis because we do not model how much a firm uses its abatement equipment. Adding the operating costs to the installation costs does not change the results in this section. Hence we exclude the operating costs here for consistency. See Online Appendix D.2 for more details.}

%We do not include the annual {operating costs} in our analysis because, on average, the ratio of operating costs of the treatment equipment to annual production value is about 1.5\%. Furthermore, the median of this ratio is less than 0.5\%, suggesting that operating costs are almost negligible for more than 50\% of firms. Therefore, operating costs alone are unlikely to affect a firm's decision to adopt treatment technology. Actually, adding the operating costs into the installation costs does not change the results in this section. In practice, operating costs could affect how much a firm uses the abatement equipment though. Since we do not model this intensive margin in our theory, we exclude the operating costs here for consistency. See Online Appendix D.1 for more details.}

To illustrate the difference in technology adoption by firms of different sizes, we use the Paper and Paper Products industry as an example.\footnote{We focus on one industry because of the potential heterogeneity in production processes across industries.} Table \ref{tab:techeffi} shows the mean abatement efficiency, median installation costs, and median output of firms that adopt these technologies, where the {abatement efficiency} is defined as one minus the ratio of {emitted COD} to {generated COD}.\footnote{Online Appendix D.2 provides more details.}
%To show the difference in the technologies adopted by firms of different size, we use the Paper and Paper Products industry as an example. Here we use one industry as an example because we would like to control for the potential heterogeneities in production processes across industries. Table \ref{tab:techeffi} shows the mean processing efficiency, median installation costs, and median sales of firms that adopt these technologies. We proximate for {processing efficiency} by using one minus the ratio of {emitted COD} to {generated COD}.\footnote{Online Appendix D.2 presents more details. Also we would like to stress again that our data contain both emitted and generated quantity of pollutants, see Online Appendix A.1 for details.} We normalize both the median installation costs of physical technologies and the median sales of firms using physical technologies to 100.
\begin{table}[t]
\footnotesize
\centering
\begin{threeparttable}
\caption{Firm Size and Treatment Technologies}
\begin{tabular}{p{50pt} >{\centering\arraybackslash}p{70pt} >{\centering\arraybackslash}p{60pt} >{\centering\arraybackslash}p{60pt} >{\centering\arraybackslash}p{70pt}} %>{\centering\arraybackslash}p{80pt}}%{lcccc}{p{45pt} >{\centering\arraybackslash}p{40pt} >{\centering\arraybackslash}p{40pt} >{\centering\arraybackslash}p{40pt} >{\centering\arraybackslash}p{40pt} >{\centering\arraybackslash}p{80pt}}
%{>{\centering\arraybackslash}p{45pt}>{\centering\arraybackslash}p{40pt}>{\centering\arraybackslash}p{40pt}>{\centering\arraybackslash}p{40pt}
%>{\centering\arraybackslash}p{40pt}>{\centering\arraybackslash}p{80pt}}
    \hline \hline
    Technology  & Mean Efficiency & Adoption Rate & Median Costs\tnote{a} & Median Output\tnote{b} \\
    \midrule
    Physical    & 63.37\%         & 25.89\%       & 100                   & 100                       \\
    Chemical    & 74.96\%         & 33.64\%       & 308                   & 219                       \\
    Biological  & 80.90\%         & 38.60\%       & 923                   & 500                       \\
    \bottomrule
\end{tabular}
\label{tab:techeffi}
\begin{tablenotes}
     \footnotesize{
     \item[$\dagger$]
     Data Source: NGSPS. The numbers reported are for the Paper and Paper Products (C22) industry. Abatement efficiency is defined as $1 - \text{COD Emitted}/\text{COD Generated}$.
     \item[a,b]
     The median installation costs of physical technologies and median output of firms that adopt them are normalized to 100.}
\end{tablenotes}
\end{threeparttable}
\end{table}
We find that for each 100 tons of COD generated, firms with biological technologies on average emit 19.1 tons of COD, compared to 36.6 tons for firms with physical technologies. Meanwhile, the median installation costs of biological technologies are 8 times higher than those of physical technologies. In addition, the median output of the firms using biological technologies are 4 times higher than those of firms with physical technologies. These point to increasing returns to scale in the adoption of cleaner technologies. As a result, small firms lack the profit margins needed to take advantage of these increasing returns to scale, while large firms are more likely to adopt cleaner technologies.
%We find that, on average, biological equipment is 17 percentage points more efficient than physical equipment, but its installation costs are also 11 times more expensive. Further, the sales of the firms using biological technologies are about 8 times those of firms with physical technologies. This evidence points to increasing returns to scale of clean technologies, indicating that small firms lack the profit margins needed to take advantage of the returns to scale imbedded in biological technologies, whereas large firms are more likely to adopt these more advanced technologies.

To see the statistical relationship between firm size and technology adoption, we pool all five polluting industries together and estimate a linear probability model of treatment technology adoption with the same set of covariates as in Equation (\ref{eq:poolols}):
\begin{equation*}
%     y_i = \underset{(0.04)}{0.23} + \underset{(0.001)}{0.05} \times \log (\text{Output}_i) + \vec{X_s} \gvec{\upgamma}_1 + \vec{X_p} \gvec{\upgamma}_2 + \vec{X_o} \gvec{\upgamma}_3 + \epsilon_i,
    y_i = \underset{(0.04)}{0.23} + \underset{(0.001)}{0.05} \times \log (\text{Output}_i) + \vec{X} \gvec{\upgamma} + \epsilon_i,
%\label{eq:poolols}
\end{equation*}
where $y_i$ is a dummy variable which equals to 1 when a firm uses biological technologies. The estimates show that doubling a firm's output leads to a 5 percentage points increase in the adoption rate of biological technologies. This confirms our previous finding with the paper industry that larger firms are more likely to use cleaner technologies.

%\begin{table}[t]
%\footnotesize
%\centering
%\begin{threeparttable}
%\caption{Treatment Efficiencies and Adoption Rates}
%\begin{tabular}{p{45pt} >{\centering\arraybackslash}p{40pt} >{\centering\arraybackslash}p{40pt} >{\centering\arraybackslash}p{40pt} >{\centering\arraybackslash}p{40pt} >{\centering\arraybackslash}p{80pt}}
%%{>{\centering\arraybackslash}p{45pt}>{\centering\arraybackslash}p{40pt}>{\centering\arraybackslash}p{40pt}>{\centering\arraybackslash}p{40pt}
%%>{\centering\arraybackslash}p{40pt}>{\centering\arraybackslash}p{80pt}}
%    \hline \hline
%    Technology  & 25\%      & Median    & 75\%      & Mean      & Adoption Rates \\
%    \midrule
%    Physical    & 39.54\%   & 77.81\%   & 87.83\%   & 63.37\%   & 25.79\%        \\
%    Chemical    & 74.96\%   & 81.29\%   & 86.78\%   & 69.77\%   & 34.50\%        \\
%    Biological  & 78.87\%   & 86.77\%   & 91.27\%   & 80.90\%   & 39.71\%        \\
%    \bottomrule
%\end{tabular}
%\label{tab:techeffi}
%\begin{tablenotes}
%     \footnotesize{
%     \item[$\dagger$]
%     Note: The numbers reported are for the Paper and Paper Product (C22) industry. Treatment Efficiencies is defined as $1 - \text{COD Emitted}/\text{COD Generated}$.}
%\end{tablenotes}
%\end{threeparttable}
%\end{table}
%The {designed processing capacity} (in tons) and {actual installation costs} (in 2007 CNY) can be retrieved directly from the data. We calculate the average processing cost by dividing the installation cost with capacity. In Figure \ref{fig:techdiff}, in clockwise order we plot the density functions of processing capacity, installation costs, total value of industrial output, and average processing cost by technology type. For all panels, log-scale is used in the horizontal axes.
%\begin{figure}[ht]
%    \begin{center}
%    \includegraphics[width=0.4\textwidth]{D:/PaperDrafts/Pollution/R_Implementation/abate_cap.pdf}%
%    \includegraphics[width=0.4\textwidth]{D:/PaperDrafts/Pollution/R_Implementation/abate_inv.pdf} \\
%    \includegraphics[width=0.4\textwidth]{D:/PaperDrafts/Pollution/R_Implementation/abate_unit.pdf}
%    \includegraphics[width=0.4\textwidth]{D:/PaperDrafts/Pollution/R_Implementation/abate_prod.pdf}
%    \caption{Technical Features of Different Treatment Technologies}
%    \floatfoot{Source: National General Survey of Pollution Sources. In all panels, the horizontal axes are in log-scale.}
%    \label{fig:techdiff}
%    \end{center}
%\end{figure}
%Broadly speaking, biological technologies have the {best} processing efficiency, the {largest} processing capacity, the {highest} installation costs, but the {lowest} average processing cost. Therefore, although biological technologies are more advanced in terms of processing capacity and efficiency, they are also more costly. Combined with the lower average processing cost that is displayed by the biological technologies, the evidence points to increasing returns to scale of the clean technologies. In fact, in the bottom-right panel, we find that the clean technologies are more likely to be installed by larger firms. %For example, the mean (median) processing efficiency of biological technologies is 17\% (10\%) higher than the physical technologies.
%The density functions of processing capacity, installation costs and production scale for physical, chemical and biological equipments order from left to right while those of the unit capacity costs order from right to left.
%It indicates that small firms lack the profit margins that are needed to take advantage of the increasing returns to scale exhibited by biological technologies, while at the same time, large firms are more likely to adopt these more advanced technologies. %This could also be seen by calculating the ratio of the \textit{summed} value of treatment equipments to the \textit{summed} value of production using firms of different scales. While this ratio is equal to 18\% when only firms with production level below the median are included, the number decreases dramatically to 4\% when up to 95\% firms are included which suggests strongly for the existence of fixed costs.

%\textit{Environmentally Friendly Production Technology.---}Note that the above results all relate to end-of-pipe treatment technologies; we have ignored those factors that could lead to less generation of COD. Indeed,
\textit{Emissions Generated During Production.---}Another reason behind the negative correlation between pollution intensity and firm size is that large firms also generate less COD per output during the production stage. In particular, if we divide our sample into two groups according to whether a firm is using biological technologies or not and repeat regression (\ref{eq:poolols}) again, we find significantly negative correlations between COD per output and firm size within each group:
\begin{align}
%\label{eq:poolols_physical}
%    \text{Physical:}   \quad \log (\text{COD}_i) &= \underset{(0.40)}{-3.50} + \underset{(0.01)}{0.58} \times \log (\text{Output}_i) + \vec{X_s} \gvec{\upgamma}_1 + \vec{X_p} \gvec{\upgamma}_2 + \vec{X_o} \gvec{\upgamma}_3 + %%\varepsilon_i \\
%\label{eq:poolols_chemical}
%    \text{Chemical:}   \quad \log (\text{COD}_i) &= \underset{(0.49)}{-4.59} + \underset{(0.01)}{0.77} \times \log (\text{Output}_i) + \vec{X_s} \gvec{\upgamma}_1 + \vec{X_p} \gvec{\upgamma}_2 + \vec{X_o} \gvec{\upgamma}_3 + %\varepsilon_i \\
%\label{eq:poolols_biological}
%    \text{Biological:} \quad \log (\text{COD}_i) &= \underset{(0.20)}{-4.37} + \underset{(0.01)}{0.67} \times \log (\text{Output}_i) + \vec{X_s} \gvec{\upgamma}_1 + \vec{X_p} \gvec{\upgamma}_2 + \vec{X_o} \gvec{\upgamma}_3 +\varepsilon_i, \\
%\label{eq:poolols_others}
%    \text{Others:} \quad \log (\text{COD}_i) &= \underset{(0.31)}{-3.41} + \underset{(0.01)}{0.64} \times \log (\text{Output}_i) + \vec{X_s} \gvec{\upgamma}_1 + \vec{X_p} \gvec{\upgamma}_2 + \vec{X_o} \gvec{\upgamma}_3 +\varepsilon_i,
\label{eq:poolols_biological}
    \text{Biological:} \quad \log (\text{COD}_i) &= \underset{(0.20)}{-4.37} + \underset{(0.01)}{0.67} \times \log (\text{Output}_i) + \vec{X} \gvec{\upgamma} + \varepsilon_i, \\
\label{eq:poolols_others}
    \text{Others:} \quad \log (\text{COD}_i) &= \underset{(0.31)}{-3.41} + \underset{(0.01)}{0.64} \times \log (\text{Output}_i) + \vec{X} \gvec{\upgamma} + X_e \gamma_e + \varepsilon_i,
\end{align}
where $X_e$ is the dummy for chemical equipment.\footnote{In our model and quantitative analysis below, we assume two types of treatment technologies. This is why we divide firms into two groups here. Running regression (\ref{eq:poolols}) separately for firms using physical and chemical equipments yield similarly significantly negative correlations between COD per output and firm size for each technology. Online Appendix C.3 reports the results in details.}

Such within group negative correlations could be because that larger firms use \emph{cleaner} or \emph{fewer} inputs to produce the same amount of ouput. For one example, the paper pulp industry uses two different types of inputs: bagasse and wood. While bagasse, which generates 140--180 kg COD per ton, is mostly used by firms with an annual production of {\color{black}less} than 100 kilotons, wood, which generates 30--55 kg COD per ton, is mostly used by firms with an annual production of {\color{black}more} than 100 kilotons.\footnote{See the \textit{Handbook of Emission Coefficients} published by the \textit{Chinese Academy of Sciences}.} As another example, \citet{Bloometal:2010} find that better managed firms use less energy to produce the same amount of output in the U.K. Unfortunately, we cannot test these hypotheses directly using our data. Instead, we focus on firms' decisions to adopt treatment technologies, and model the emissions reduction during the production stage in a reduced-form way based on Equations (\ref{eq:poolols_biological}) and (\ref{eq:poolols_others}).

%Such within group relationship could be because that larger firms use environmentally friendlier production technologies, sell products with a higher mark-up, or produce products that are technologically less polluting. An example from the \textit{Handbook of Emission Coefficients} published by the \textit{Chinese Academy of Sciences} is as follows. The paper pulp manufacturing use two different types of inputs: bagasse and wood. While bagasse, which generates 140--180 kg COD per ton, is mostly used by firms with an annual production of {\color{black}less} than 100 k-tons, wood, which generates 30--55 kg COD per ton, is mostly used by firms with an annual production of {\color{black}more} than 100 k-tons. Alternatively, it could also be that more productive firms simply use less resource to produce [\citet{Bloometal:2010} and \citet{ShapiroWalker:2015}]. Unfortunately, we cannot test these hypotheses directly with our data. Therefore, in this study, we focus on firms' decisions to adopt treatment equipment and model the intensity reduction during the production stage by using the reduced-form characterization of (\ref{eq:poolols_dirty}) and (\ref{eq:poolols_clean}).

\subsection{Firm Size Distribution and Aggregate Pollution Intensity}

The negative correlation between pollution intensity and firm size suggests that firm size distribution plays a potentially important role in aggregate pollution intensity. To illustrate the point, we document facts on the firm size distribution in China and in the U.S., and compute the change in the aggregate pollution intensity if the firm size distribution for the top five polluting industries in China were replaced with that in the U.S. We choose the U.S. as the benchmark because it is a relatively less distorted economy, and China and the U.S. are both large economies with a complete set of industries so that we can find comparable industries in both economies.\footnote{It is a commonly used strategy in the macro-development literature to take the U.S. economy as an undistorted benchmark. See \citet{Guneretal:2008}, \citet{HsiehKlenow:2009, HsiehKlenow:2014}, \citet{Bartelsmanetal:2013}, and \citet{AdamopoulosRestuccia:2014}, among others.}

%The negative correlation between pollution intensity and production scale implies that, {ceteris paribus}, the shares of total output by large and small firms could influence aggregate industrial pollution markedly. An important task then is to understand the firm size distribution in China. To gain some intuitions, we compare the firm size distribution in China with that in the United States. We choose the United States as the benchmark because the U.S. economy is relatively distortion-free compared with other economies, and China and the United States are both large economies with complete sets of industrial sectors. Naturally, firm size in the United States and China differs for many reasons. Yet we do not intend to answer why they are different in this paper. The primary purpose of this section is to motivate the investigation of size-dependent distortions that disproportionately affect large firms.

Since the SUSB does not report information on output, we focus on the shares of employment accounted for by firms of different sizes, since firm-level employment is strongly correlated with output. We use the \textit{International Standard Industrial Classification of All Economic Activities, Revision 3.1} (ISIC Rev. 3.1) published by the United Nations to bridge the different industrial classification systems adopted by China (GB/T4574-2002) and the United States (NAICS 2002). Specifically, we use the crosswalks of GB/2002 at the four-digit level and those of NAICS/2002 at the six-digit level to the ISIC Rev. 3.1 issued respectively by the National Bureau of Statistics of China and the U.S. Census Bureau, respectively. %The results presented in this section are from matching at the disaggregated level (four-digit GB with six-digit NAICS).\footnote{Matching at a more aggregated level (two-digit GB with three-digit NAICS) yields similar results.}

\begin{figure}[t]
    \begin{center}
%    \includegraphics[width=0.45\textwidth]{D:/PaperDrafts/Pollution/R_Implementation/paperES_R.pdf}%
%    \includegraphics[width=0.45\textwidth]{D:/PaperDrafts/Pollution/R_Implementation/agriES_R.pdf} \\
%    \includegraphics[width=0.45\textwidth]{D:/PaperDrafts/Pollution/R_Implementation/textileES_R.pdf}
%    \includegraphics[width=0.45\textwidth]{D:/PaperDrafts/Pollution/R_Implementation/chemmatES_R.pdf} \\
    \includegraphics[width=0.45\textwidth]{./Figures/poolES_R_1.pdf}
    \includegraphics[width=0.45\textwidth]{./Figures/allES_R_1.pdf}
    %\vspace{-1em}
    \caption{Employment Distributions}
    \floatfoot{Sources: CNEC and SUSB.}
    \label{fig:es}
    \end{center}
\end{figure}

%\begin{figure}[htbp]
%    \begin{center}
%    \includegraphics[width=0.45\textwidth]{D:/PaperDrafts/Pollution/R_Implementation/paperdist_R.pdf}%
%    \includegraphics[width=0.45\textwidth]{D:/PaperDrafts/Pollution/R_Implementation/agridist_R.pdf} \\
%    \includegraphics[width=0.45\textwidth]{D:/PaperDrafts/Pollution/R_Implementation/textiledist_R.pdf}
%    \includegraphics[width=0.45\textwidth]{D:/PaperDrafts/Pollution/R_Implementation/chemmatdist_R.pdf} \\
%    \includegraphics[width=0.45\textwidth]{D:/PaperDrafts/Pollution/R_Implementation/beverdist_R.pdf}
%    \includegraphics[width=0.45\textwidth]{D:/PaperDrafts/Pollution/R_Implementation/pooldist_R.pdf}
%    %\vspace{-1em}
%    \caption{Firm Size Distribution}
%    %\floatfoot{Source: China National Economic Census and the Statistics of U.S Businesses}
%    \label{fig:dist}
%    \end{center}
%\end{figure}

The left panel of Figure \ref{fig:es} depicts the firm size distribution for the top five polluting industries pooled together. %\footnote{Online Appendix E explains the calculation.}
We find that approximately 70\% of employment in the United States is accounted for by firms with 400+ employees, while in China the number is only 20\%.\footnote{In Online Appendix E, we compare the firm size distributions between China and the U.S. for each individual polluting industry. We find that while there is substantial heterogeneity across individual industries, large firms in China account for a much smaller employment shares than those in the U.S. for each industry.} %\footnote{Some readers may concern that the large difference of population size between the United States and China could drive the results. However, as shown in \citet{BentoRestuccia:2016}, there is no systematic relationship between average firm size and population size. In addition, because China has a much larger population size, the difference in population size between the two countries is more likely to make our case stronger.}
Compared with the U.S., a much larger share of production is carried out by small and medium-sized firms in China. %This implies that could be a candidate for explaining the high industrial pollution emissions in China. %\footnote{These results are consistent with those of \citet{WangWhalley:2014}, who compare the manufacturing concentration ratios (the share of market occupied by the largest firms) for China and the United States. According to Table 1 in their paper, the ratios of the concentration indicators of the United States over China for the top five polluting industries are higher than the {overall average}, which suggests that in polluting industries, large firms in the United States take a larger share of the markets.}
From the right panel of Figure \ref{fig:es}, we find a similar pattern for the whole manufacturing sector.

%\subsection{Size Distribution and Aggregate Pollution}

\textit{An Accounting Exercise.---}To see the potential importance of firm size distribution, we conduct the following accounting exercise. For the top five polluting industries in China, we fix the total output and  the estimated firm size--pollution intensity relationship, and replace the firm size distributions with those in the U.S. Then we compute the resulting average pollution intensity for these polluting industries pooled together.\footnote{Online Appendix F provides more details.} This simple exercise is complicated by the fact that the NGSPS reports firm-level output instead of number of employees. Therefore, we construct an employment--output relationship from a linear regression using the CNEC data.\footnote{There are different methods to construct the employment--output relationship using the CNEC data, and all of them provide similar results. See Online Appendix F for details.} %We use CNEC to overcome this problem. There are many ways to construct the employment-production relationship using CNEC, and each method has its own advantages and disadvantages. In this section, we report results where the employment-production relationship is constructed by linear regression. Calculation using alternative methods gives similar results. We leave the details of these alternative methods in Appendix A.

%\textit{An Accounting Exercise.---}To see how the firm size distribution affects aggregate pollution quantitatively, we conduct an accounting exercise in which, for the pooled polluting industries in China, we fix total output, but replace the employment distribution with that from the United States in order to calculate the implied level of average pollution intensity by using the firm size--intensity relationship estimated in Section \rom{1}.B.\footnote{We show the results for each of the five industries in Online Appendix F.} This simple exercise is complicated by the fact that the NGSPS only reports firm-level production values but not the number of employees. Therefore, we construct the employment--production relationship by using a linear regression with CNEC data.\footnote{There are many ways to construct the employment--production relationship by using CNEC data; however, these alternative methods all provide similar results. See Online Appendix F for details.} %We use CNEC to overcome this problem. There are many ways to construct the employment-production relationship using CNEC, and each method has its own advantages and disadvantages. In this section, we report results where the employment-production relationship is constructed by linear regression. Calculation using alternative methods gives similar results. We leave the details of these alternative methods in Appendix A.

We find that the average pollution intensity for the pooled top five polluting industries drops by 33\%, when the firm size distributions in these industries are changed to those in the U.S. This would cause a 25\% decrease in the average pollution intensity for the whole manufacturing sector if we leave other manufacturing industries untouched. Admittedly a crude approximation, this exercise nevertheless shows that distortions to firm size distribution could potentially have a large impact on aggregate pollution intensity.

%By doing so, we calculate that on average, for the top five polluting industries, the effect of changing the firm size distribution reduces emissions to 83\% of the original level. Changing the firm size distributions of these five industries while keeping those of all the other industries untouched leads to a reduction in total emissions of about 17\%. Although the exercise here is a crude approximation, it nevertheless shows that the firm size distribution can have a significant impact on aggregate industrial pollution.
%The numbers reported in Table \ref{tab:accounting} are the ratio of the aggregate pollution produced with the U.S. employment share distribution over that with the original Chinese distribution.
%\begin{table}[t]
%\footnotesize
%\centering
%\begin{threeparttable}
%\caption{Size Distribution on Pollution}
%\begin{tabular}{lccccccc}
%    \hline \hline
%                        & Paper  & Agricultural Food   & Textiles    & Chemical Materials    & Beverages        & Average  \\
%    \midrule
%    Average Intensity   & 43.5\% & 61.1\%              & 97.5\%      & 101.2\%               & 89.0\%           & 67.0\% \\
%    \bottomrule
%\end{tabular}
%\begin{tablenotes}
%     \footnotesize{
%     \item[$\dagger$]
%     Note: The numbers reported are aggregate pollution from the artificial U.S. production structure as a percentage of that of China. Column 6 (``Average'') calculates the weighted average of these ratios by using the percentage contributions in row one of Table \ref{tab:top5summary} as the weights.}
%\end{tablenotes}
%\label{tab:accounting}
%\end{threeparttable}
%\end{table}
%These results imply that by changing the employment share distribution to that of the United States, while keeping production at the same level, aggregate emissions in the Paper and Paper Products industry reduce to 43.5\% of the original level. On average, for the top five polluting industries, the effect of changing the firm size distribution reduces emissions to 67\% of the original level. The average is calculated by using the relative pollution levels of each industry as the weights, which is the first row of Table []. %Changing the firm size distributions of these five industries while keeping those of all the other industries untouched leads to a reduction in total emissions of about 25.5\%.

\section{The Model}

%The accounting exercise presented in the last section has several limitations. First, aggregate output is fixed. Indeed, when the size distribution changes, although pollution intensity decreases, aggregate pollution may increase as a result of the larger increase in aggregate output. In the language of scale, composition, and technique decomposition commonly used in the environmental literature [\citet{CopelandTaylor:2004} and \citet{Levinson:2009}], the accounting exercise evaluates only the technique effect, while instead we would like to consider the trade-off between scale and technique effects. Second, the firm size distribution is mechanically changed to that in the United States. From the accounting exercise alone, the factors that drive the difference between the firm size distribution of China and that of the United States remain unclear. We also do not know whether the implied employment distribution will in fact become that of the United States. Third, the relationship between firm size and emissions intensity is taken as exogenous and invariant. However, changes in the factors that affect the employment distribution may also influence the technology choices of firms, which makes the firm size--intensity relationship endogenous. Therefore, to better evaluate the environmental consequences of distortions to firm size, we need a model that (i) contains economic factors affecting both aggregate output and pollution, (ii) reveals which factors affect firm size and how, and (iii) explains the firm size--intensity relationship.

The above accounting exercise is illuminating but has several limitations. First, the firm size distribution is mechanically changed to that in the U.S. Although the U.S. economy is often taken as a benchmark in the development literature, it is unclear whether the differences in firm size distribution between China and the U.S. are mainly caused by distortions or by some other factors. Second, the accounting exercise captures the technique channel only, while distortions may operate through the scale and composition effects as well. Third, the relationship between firm size and emissions intensity is taken as exogenous in the accounting exercise. However, distortions to firm size may also influence firm's incentive to adopt different treatment technologies, which endogenizes the firm size-intensity relationship.

To address these issues, we build a two-sector (polluting and non-polluting) model of heterogeneous firms based on the classic \citet{Lucas:1978b} span-of-control model.\footnote{A widely used alternative  in the misallocation literature is the closed-economy version of \citet{Melitz:2003}. \citet{HsiehKlenow:2009} establish that these two frameworks are isomorphic for the effects of misallocation on aggregate output when the number of firms is fixed. In Appendix G.3, we show the qualitative equivalence between the two family of models.} The model features heterogeneity in firm productivities in both sectors, heterogeneity in pollution intensity and endogenous choice of pollution treatment technologies in the polluting sector. Motivated by the data, firms in both sectors are subject to correlated distortions [\citet{RestucciaRogerson:2008}] in the form of progressive output taxes. Throughout, we refer to the sectors as polluting and non-polluting, and technologies as dirty and clean. In the context of our model, the polluting sector is mapped to the top five polluting industries and the non-polluting sector to the rest of the manufacturing sector, while clean and dirty technologies are interpreted as biological and other (physical plus chemical) equipments as specified in Section \rom{1}.B.

%The model allows us to assess structurally the scale, composition and technique channels, through which counterfactual policies affect aggregate pollution. Moreover, the model allow us to further decompose the technique channel into: within sector reallocation across firms, and the change in clean technology adoption.
%For this purpose, we consider a two-sector neoclassical growth model with heterogeneous firms within each sector. We refer to the two sectors as polluting and non-polluting sector, which corresponds respectively to the five polluting industries and the rest of the manufacturing sector. Both sectors feature size-dependent distortions, while firms in the polluting sector face in addition imperfect environmental regulation and endogenous treatment technology choice. We assume two types of treatment technologies: dirty and clean. In the context of our model, these two technologies are interpreted as the {physical} and {biological} technology classifications discussed in Section \rom{2}.B.

\subsection{Setup}

We assume that the products of the two sectors in the model economy are perfect substitutes to each other.\footnote{In Online Appendix J, we consider the case in which the final good is a CES aggregation of the goods produced in two sectors, and conduct counterfactual experiments under different values of the elasticity of substitution in the CES function. For the counterfactual experiments we discuss in the main text, the quantitative results in the CES cases are similar to those in the perfect substitute case, largely because the experiments induce very limited reallocation between sectors.} The polluting sector generates emissions as a by-product of production as in \citet{CopelandTaylor:1994}, while the non-polluting sector does not. The top five polluting industries (hence the polluting sector) account for nearly 80\% of total industrial COD emissions and 20\% of total industrial output, with the rest accounted for by the non-polluting sector. Firms in both sectors behave competitively.

\textit{Household.}---%Assuming that there is perfect risk sharing within the household, the preference of the household could then be characterized by
%\begin{equation}
%    \sum_{t=0}^{\infty} \beta^t U(C_t)
%\end{equation}
%where $C_t$ is the consumption at time $t$ and $\beta$ is the discount factor.
There is a representative household with a continuum of members that maximizes the life-time utility $\sum_{t=0}^{\infty} \beta^t U(C_t)$,
%\begin{equation*}
%    \sum_{t=0}^{\infty} \beta^t U(C_t)
%\end{equation*}
where $C_t$ is the consumption at time $t$ and $\beta$ is the discount factor.

A fraction $\mu$ of the members are endowed with managerial talent that can be used in the polluting sector, drawn from a distribution with cumulative distribution function (CDF) $G^{d}(z)$. Meanwhile, a fraction $1-\mu$ of the members are endowed with managerial talent for the non-polluting sector with CDF $G^{c}(z)$. The support for both distributions are $Z \triangleq [0,\overline{z}]$. We assume that $z$ is fixed once drawn. Household members face an occupational choice between {worker} and {manager}. A worker supplies one unit of labor inelastically in exchange for wage income, and is perfectly mobile between sectors, while a manager in each sector runs a neoclassical firm and earns profits. As we see in Figure \ref{fig:es}, the firm size distributions in the polluting sector and the whole manufacturing sector are almost identical. Based on this observation, we assume that $G^{d}(z) = G^{c}(z) \triangleq G(z)$ from now on.

In addition, we assume that the household owns all the firms and capital in this economy. The goods produced in the non-polluting sector are taken as the numeraire. With perfect substitution between goods, the price of the goods produced in the polluting sector is also 1. $R$ and $W$ are the capital rental price and wage rate, respectively.

%There is a representative household with a continuum of members. Each household member is endowed with $z$ units of managerial talent, $z \sim G(z)$ with support $Z \triangleq [0,\overline{z}]$, where $G(z)$ is the cumulative distribution function and $g(z)$ is the probability density function. We assume that the support and distribution of $z$ are exogenous, and $z$ is fixed once drawn. Household members face an occupational choice between {worker} and {entrepreneur}. A worker supplies one unit of labor inelastically in exchange for wage income, whereas an entrepreneur rents capital and labor to run a neoclassical firm and earns profits. In the latter case, $z$ is also interpreted as firm-level TFP and with the understanding from the readers, we take the liberty to the term managerial talent and firm-level TFP interchangeably depending on whether we emphasize the household member or the firm.

%We assume that the managerial talent $z$ is sector specific in the sense that a share $\mu$ of the members can only choose to open firms in the polluting sector, while the rest $1-\mu$ have to enter the non-polluting sector. Workers are perfect mobile between sectors. Notice that by the law of large numbers, the ex ante distributions of $z$ in the two sectors are both $G(z)$. This is inspired by the fact that the firm size distributions in the polluting and non-polluting sectors are very similar (Figure \ref{fig:es}). We assume that the goods produced by the two sectors are perfect substitutes and are the numeraire.%\footnote{In Online Appendix J, we consider the case where there is a final good producer that aggregates the two intermediate goods following a CES production function. Because in the two quantitative experiments we study in the main text, there is very little cross-sector reallocation of production, the quantitative results from a CES setup are very similar. As a result, for simplicity, we choose the perfect substitute setup.} Let $R$ and $W$ be the capital and labor rental price respectively.

\textit{Firms.}---The production functions in the two sectors take the same form. Production requires managerial talent $z$, capital $k$, and labor $l$. For a firm run by a manager with managerial talent $z$, its output is
\begin{equation*}
    y = F(z,k,l) = z^{1-\gamma} (k^{\alpha}l^{1-\alpha})^{\gamma},
\end{equation*}
where $0<\gamma<1$ is the \emph{span-of-control} parameter, which governs the returns to scale at the firm level. Due to diminishing returns to scale at the firm level, a non-degenerate distribution of firm size can be supported, and firms earn positive profits as the payment to managerial talent $z$. %\footnote{We build our model based on \citet{Lucas:1978b}. However, all the qualitative properties of our model remain valid if instead we use a model with monopolistic competition [\citet{Melitz:2003}] since the two models are isomorphic. In the Melitz model, the decreasing returns to scale come from the concavity of the utility function. Similarly, firms in the Melitz model earn profits because of the monopolistic competition market structure, while the profits in our model are the factor payment to managerial talent $z$. We show the math details in Appendix G.3 [see also Appendix \rom{1} of \citet{HsiehKlenow:2009}].}
As is typically the case with studies that follow \citet{Lucas:1978b}, managerial talent $z$ is the only source of firm-level TFP in this model. In what follows, we also refer to $z$ as firm-level TFP.

In the non-polluting sector, firms do not discharge pollutants and are not subject to environmental regulations.  In the polluting sector, pollutants $e$ are generated as a by-product of production. Total emissions $e = \mathcal{E}(i,y)$ depend on the amount of output $y$, and the pollution treatment technology firms use, with $i = 1$ refers to the {clean} technology and $i = 0$ the dirty technology. Based on the empirical findings from Section \rom{1}, we assume that
\begin{equation}
\label{eq:intensity_size}
    \log\left(\frac{e}{y}\right) = \psi_0^i + \psi_1^i \log y, \quad i = 0,1,
\end{equation}
where $\psi_1^i<0$. This formulation indicates that larger firms emit fewer pollutants per unit of output, which is consistent with our empirical findings in Section \rom{1}.B.

Adopting the clean technology incurs fixed cost $R k_E$. %\footnote{Adding the variable costs of adopting the clean technology to our model will not change our quantitative results fundamentally. Specifically, the introduction of the variable costs would lead to an increase in calibrated value of $k_E$ but would not lead to materials changes in our quantitative results.See more related discussions in Online Appendix D.2.} %Furthermore, we assume that firms only invest in one treatment technology. We make this assumption because in the data only 7\% firms have more than one set of treatment equipment, and only 2\% have more than two sets.}
We assume that the environmental authority punishes firms for using the dirty technology. Similar in spirit to \citet{ShapiroWalker:2015}, we model the environmental regulations in a parsimonious way as a penalty which equals to a proportion $\xi$ of the firm's profits. The penalty is later redistributed to the household as lump-sum transfers.\footnote{In practice, China employs both economic incentives and command-and-control instruments in its current industrial pollution management and control system. A powerful tool used by the Chinese government is to randomly audit and then shut down firms that do not comply with environmental regulations for a certain period of time, which would cost these firms a fraction of their profits. See Trevor Nace, ``China shuts down tens of thousands of factories in widespread pollution crackdown,'' Forbes, October 24th 2017, for an anecdotal example.  We present a short summary of China's current environmental regulations based on \citet{Lin:2013} in Online Appendix D.3.} Therefore, the central trade-off in a firm's technology choice is weighing the adoption cost $R k_E$ against the profit losses from the environmental penalties. To the extent that firms' profits increase with firm size, we implicitly capture the size-dependency of the environmental regulations, in the sense that larger firms are usually monitored and inspected more closely. A key prediction from these assumptions is that, only firms above a certain size threshold would choose the clean technology, which is qualitatively consistent with our empirical findings on technology adoption in Section \rom{1}.B.\footnote{In Online Appendix D.2, we provide further evidence that the ratio of a firm's expenditures on treatment technology to firm output decreases with firm size, which supports the fixed cost assumption.}

%Installing the clean equipment incurs fixed cost $R k_E$, where we assume that the equipment is also rented from the market, just as the production capital $k$.\footnote{We choose to model the installation costs as one-time fixed costs as opposed to fixed costs plus operating costs or size-dependent fixed costs because the latter two are not supported by the empirical evidence. We also assume that the fixed cost is only associated with the clean technology. Qualitatively, assuming that the dirty technology also requires a fixed cost does not affect the property of the model. This is equivalent to a decrease in the cost of the clean technology, since what matters for the firm's decision is the difference between the two costs. See Online Appendix D.2 for further details.} %Furthermore, we assume that firms only invest in one treatment technology. We make this assumption because in the data only 7\% firms have more than one set of treatment equipment, and only 2\% have more than two sets.}
%We assume that the environmental authority penalizes firms for using dirty technology. We take a similar approach as \citet{ShapiroWalker:2015} to capture the regulations in a parsimonious way by modeling the penalty as a proportion of $\xi$ of the total profits of these firms.\footnote{In practice, China employs both economic incentives and command-and-control instruments in its current industrial pollution management and control system. A pollution levy system requires that firms pay levies according to how much pollutants they discharge. In addition, local authorities penalize firms for fraudulent report of pollutants emissions and temporarily suspend firms using obsolete treatment technology from production under some occasions. \citet{Lin:2013} provides a detailed description of China's current environmental regulations. We present a short summary in the Online Appendix D.3 based on his work. The $\xi$ is used to summarize all these regulations jointly.} The penalty is distributed back to the household as lump-sum transfers.

%As a result, the core trade-off of firm's technology adoption decision is between the installation cost $R k_E$ and the profit loss. Because firm's profits and size increase with its productivity $z$, by assuming a constant fraction $\xi$, we are implicitly capturing the fact that environmental regulation is also size-dependent, that is large firms are being watched more closely. Also since our model is deterministic and firms are risk neutral, $\xi$ captures the deterrence effects of the regulations as well.

%\textit{Regulators.}---We assume that the environmental authority monitors the adoption of the clean technology by firms with probability $p$. When a firm using the dirty technology is inspected, we assume that a proportion $\xi$ of its total profits is confiscated by the regulating agency. As a result, firms using the dirty technology lose a proportion of $p\xi$ of their total profits. The confiscated profits are distributed to the household as lump-sum transfers, meaning that they do not affect the decision problem of household members. This reduced-form way of modeling monitoring policy could, for instance, be rationalized by a mixed strategy Nash equilibrium of a behind-the-scenes ``monitoring game.''
%
%The current industrial pollution management and control system in China consists of {economic incentives} and {command-and-control instruments}.\footnote{See Chapter 5 of \citet{WorldBankChinaPollution:2001} for a detailed description.} The pollution levy system is the most widely used economic instrument in China. However, it places limited constraints on the emissions of firms because the penalty imposed is very low. Firms only have to pay for the emissions that go {beyond} the national standard. Moreover, these emissions are {self-reported} and the truthfulness of the reported emissions is imperfectly examined by the regulators.\footnote{This may be a common problem for developing countries. For example, \citet{Dufloetal:2013} conduct a field experiment in India and find that the emissions reporting system is largely corrupted, with auditors systematically reporting plant emissions just below the standard.} Further, for firms that discharge multiple pollutants and when the levels of more than one of the pollutants are above the national standards, firms only have to pay for the one that leads to the highest penalty. We calculate from the CNEC the pollution fees levied on firms as a proportion of total labor compensation. We find that for firms with strictly positive emissions fees, these fees only account for 0.06\% (median) and 0.3\% (mean) of the labor compensation.
%
%Therefore, in practice, environmental agencies rely mostly on command-and-control instruments. To implement the regulation, field inspections are conducted by the staff of local environmental agencies. %Using data from the Environmental Protection Bureau in Zhenjiang, \citet{Dasguptaetal:2001} showed that at the firm level, compared to variations in pollution levies, variations in the number of field inspections better explains the variations in pollution levels.
%Field staff typically check the type of treatment equipment that firms have installed and test the emissions intensity of major pollutants. Firms found to be at fault are usually suspended from production until the issues are resolved.\footnote{See \citet{Dasguptaetal:2001} for a case study of Zhenjiang.} In our model, the proportion $\xi$ of the profits confiscated is used to approximate these costs. Since, according to Table \ref{tab:techeffi}, the treatment technology used by firms is highly correlated with pollution intensity, we assume that the regulator in our model checks only treatment technologies. Although the local environmental agencies also monitor total emissions, these regulations are usually based on a {provincial-level} aggregation. They are thus less relevant to the firm-level decision that we study here.\footnote{Firm inspections in the United States also target the adopted treatment technologies. See \citet{BeckerHenderson:2000} and the references therein for more details.}
%%\footnote{Firm level inspections in the U.S are also targeted mainly on the adopted treatment technologies. For example, as is stated in the 1977 Amendment of the Clean Air Act, each July every county in the U.S will be classified as either an {attainment} or a {non-attainment} county according to their overall pollutants emissions level. Firms in {non-attainment} counties are subject to substantially stronger environmental regulations. For instance, newly established firms in these counties are required to meet the standard of Lowest Achievable Emission Rate (LAER) which demands the installation of the cleanest possible technology supposedly regardless of costs. While on the other hand, in {attainment} counties only Best Available Control Technology (BACT) which incorporates cost considerations is required. Similarly, existing firms are also subject to stricter regulations on production and end-of-pipe treatment technologies in non-attainment counties than in the attainment counties. See \citet{BeckerHenderson:2000} and the references therein for more details.}

%\subsection{Firm-level Distortions}
%
%Recent studies of the Chinese economy have described large distortions at both the sector and the firm levels, which negatively affect aggregate productivity and output considerably.\footnote{See \citet{HsiehKlenow:2009}, \citet{Songetal:2011}, \citet{Brandtetal:2013}, and \citet{TombeZhu:2015}, among others.} Following the seminal approach developed by \citet{HsiehKlenow:2009,HsiehKlenow:2014}, we model and estimate firm-level distortions by using variations in the average products of capital and labor across firms.\footnote{Though average factor product dispersion could arise due to dynamic capital adjustment [\citet{Askeretal:2014}], for the case of China, \citet{DavidVenkateswaran:2017} show that dynamic adjustment costs only accounts for about 10\% of the variation in average factor product in the data. Naturally, we also cannot separate out variations in average factor product caused by firm-specific characteristics, for instance firm-specific markup or capital share. However, we argue that it would require empirical implausible variations of such parameters to generate the patterns of the data we observe.} %An important feature of Cobb-Douglas production function is that the ratio of average factor products to marginal factor products is constant. Therefore, the average factor products also provide information on marginal factor products.\footnote{In particular, using the notations later in this section, we can verify that $\partial y/\partial k = \alpha \gamma z^{1-\gamma} k^{\alpha \gamma - 1} l^{(1-\alpha)\gamma} = \alpha \gamma (y/k)$. Similarly, we can show that $\partial y/\partial k = (1-\alpha) \gamma (y/l)$.}
%More specifically, if we let $\tau_{z_i}, \tau_{k_i}$, and $\tau_{l_i}$ be the wedges that firm $i$ faces in the product, capital, and labor markets, respectively, the profit maximization problem of firm $i$ is
%\begin{equation*}
%    \pi_i = \max_{k_i,l_i} \left\{ (1-\tau_{z_i}) z_i^{1-\gamma} (k_i^{\alpha} l_i^{1-\alpha})^{\gamma} - (1+\tau_{k_i})Rk_i - (1+\tau_{l_i})W l_i \right\}.
%\end{equation*}
%By using the first-order conditions, the firm level average product of capital $\phi_{k_i}$, labor $\phi_{l_i}$, and the capital/labor ratio $\kappa_i$ can be expressed as
%\begin{align}
%    \label{eq:phik}
%    \phi_{k_i} &= \frac{y_i}{k_i} = \frac{(1+\tau_{k_i})R}{\alpha \gamma (1-\tau_{z_i})}, \\
%    \label{eq:phil}
%    \phi_{l_i} &= \frac{y_i}{l_i} = \frac{(1+\tau_{l_i})W}{(1-\alpha) \gamma (1-\tau_{z_i})}, \\
%    \label{eq:kappa}
%    \kappa_i &= \frac{k_i}{l_i} = \frac{\alpha}{1-\alpha} \cdot \frac{(1+\tau_{l_i})W}{(1+\tau_{k_i})R}.
%\end{align}
%The above equations show that in the absence of any distortions ($\tau_{z_i} = \tau_{k_i} = \tau_{l_i} = 0$), $\phi_{k_i}, \phi_{l_i}$, and $\kappa_i$ should be equalized across firms. Equations (\ref{eq:phik}) and (\ref{eq:phil}) state that firms that face higher distortions in the capital (labor) and/or product markets demonstrate a higher average product of capital (labor). In addition, according to Equation (\ref{eq:kappa}), the capital/labor ratio increases with the {relative} size of labor to the capital market wedge. By using firm-level data on total production value, the book value of capital stock, and labor compensation from the CNEC, we calculate $z_i, \phi_{k_i}, \phi_{l_i}$, and $\kappa_i$ for each firm in our sample. Anticipating the calibration later, here we set $\gamma = 0.93$. Figure \ref{fig:phiklkappa} shows on log scales the scatterplots of $\phi_{k_i}, \phi_{l_i}$, and $\kappa_i$ against firm-level productivity $z_i$ for the Paper and Paper Products industry. We plot the Paper industry for demonstration purpose, qualitatively the results for all five polluting industries combined are the same.
%\begin{figure}[t]
%    \begin{center}
%    \includegraphics[width=0.4\textwidth]{D:/PaperDrafts/Pollution/R_Implementation/arpk.pdf}%
%    \includegraphics[width=0.4\textwidth]{D:/PaperDrafts/Pollution/R_Implementation/arpl.pdf} \\
%    \includegraphics[width=0.4\textwidth]{D:/PaperDrafts/Pollution/R_Implementation/klratio.pdf}
%    \caption{Factor and Product Market Distortions}
%    \floatfoot{Source: CNEC. All panels are plot in log scale. Lines are least square fit.}
%    \label{fig:phiklkappa}
%    \end{center}
%\end{figure}
%
%Two patterns emerge from Figure \ref{fig:phiklkappa}. First, from the two upper panels, we see that both $\phi_{k_i}$ and $\phi_{l_i}$ are positively correlated with $z_i$, which suggests that more productive firms have higher average products of both capital and labor. Expressed in wedges, this means that both $(1+\tau_{k_i})/(1-\tau_{z_i})$ and $(1+\tau_{l_i})/(1-\tau_{z_i})$ are higher for more productive firms.\footnote{Generally speaking, the estimated elasticities of $\phi_k$ and $\phi_l$ to $z$ depend on the value of $\gamma$, since $z$ is calculated for a given $\gamma$. For $\gamma = 0.93$ used here, the elasticities of $\phi_k$ and $\phi_l$ to $z$ equal 0.03, which taken at its face value seem well below the estimates in the literature. For instance, by using comprehensive micro data, \citet{HsiehKlenow:2014} find that the elasticity is 0.1 for the United States and between 0.5 and 0.6 for India and Mexico. By using data from the World Bank's Enterprise Surveys, \citet{BentoRestuccia:2016} find that the elasticities range from 0.22 to 0.74, averaging 0.52. However, we argue that this is because in the calibration of our general equilibrium model, as is explained in details in Section \rom{3}, in order that our model generates a wide range of firm size, a value of $\gamma$ that is higher than commonly used in the literature is needed. If we assume $\gamma = 0.85$ following \citet{AtkesonKehoe:2005}, then the elasticities of $\phi_k$ and $\phi_l$ to $z$ are both about 0.25, which are quantitatively consistent with those in the literature. The value of $\gamma$ used, however, will not affect the qualitative conclusion that large firms are subject to more distortions.}
%%If we assume $\gamma = 0.85$ following \citet{AtkesonKehoe:2005}, then the elasticities of $\phi_k$ and $\phi_l$ to $z$ are both about 0.25, meaning that doubling firm productivity is associated with a 25\% increase in the average revenue product of factor inputs.\footnote{Generally speaking, the estimated elasticity depends on the value of $\gamma$, since $z$ is calculated for a given $\gamma$. However, because we are using a \citet{Lucas:1978b} model, while \citet{HsiehKlenow:2014} and \citet{BentoRestuccia:2016} both use the \citet{Melitz:2003} model, our results are not directly comparable with theirs. Yet broadly speaking, our estimates are quantitatively consistent with theirs. By using comprehensive micro data, \citet{HsiehKlenow:2014} find that the elasticity is 0.1 for the United States and between 0.5 and 0.6 for India and Mexico. By using data from the World Bank's Enterprise Surveys, \citet{BentoRestuccia:2016} find that the elasticities range from 0.22 to 0.74, averaging 0.52.}
%This could be because more productive firms are subject to higher factor or product market distortions or both. Second, from the lower panel, we see that the capital/labor ratio is at best weakly negatively correlated with $z$. The least squares estimate of the elasticity is $-$0.0057 and the $R^2$ is only 0.053. This finding indicates that the {relative} wedge firms face in the capital and labor markets does not depend strongly on the idiosyncratic productivity of firms, which in the context of our model implies $1+\tau_{k_i} \approx 1+\tau_{l_i}$.\footnote{This also explains the reason why $\phi_{k_i} \approx \phi_{l_i}, \forall i$.} Since we cannot separately identify the three wedges, for simplicity, we assume $\tau_{k_i} = \tau_{l_i} = 0$ and attribute all the variations in the average product of factors to the wedges in the product market $\tau_{z_i}$. Whether we assume $\tau_{k_i} = \tau_{l_i} = 0$ or alternatively $\tau_{z_i} = 0$ does not affect our results, but the interpretations need to be changed accordingly.\footnote{For example, we cannot distinguish between the data-generating process we use here and another process where $\tau_{k_i}$ and $\tau_{l_i}$ increase simultaneously, while $\tau_{z_i}$ is equal to zero. Moreover, when estimating the elasticity, since $y,k$ and $l$ enter the regression on both sides, when any of the variables are measured with measurement error, such error may drive spurious correlations. While we cannot rule out this possibility completely, we argue that this does not seem to be the case here. In particular, if $y$ is measured with extreme measurement error, the regression coefficient of $\phi_k$ over $z$ is $1-\gamma$. Similarly, if instead $k$ is measured with extreme measurement error, the regression coefficient is $(1-\gamma)/\gamma$. We calculate $\phi_{k_i}$ and $z_i$ by using different values of $\gamma$ and the regression coefficients do not vary as predicted by either case.}
%
%\begin{figure}[t]
%    \begin{center}
%    \includegraphics[width=0.50\textwidth]{D:/PaperDrafts/Pollution/PrelimResults/tauz.eps}
%    \caption{The Generic Tax Function of $\tau_z$}
%    \label{fig:tauz}
%    \end{center}
%\end{figure}
%In the spirit of \citet{BentoRestuccia:2016}, we implement these idiosyncratic wedges in the model by positing a generic ``tax'' function that specifies the wedges as a function of a firm's productivity $z$:\footnote{This tax function has a long history in macro-public finance literature, for instance \citet{Benabou:2002}. We thank a referee for pointing this out. Recent studies that adopt the same tax functions include \citet{AdamopoulosRestuccia:2014}, \citet{HsiehKlenow:2014}, and \citet{Guneretal:2017}.}
%\begin{equation}
%    \tau_z = \max \left\{ 0, 1 - \phi_0 z^{\phi_1} \right\}.
%\label{eq:tax}
%\end{equation}
%%From now on, we use $\tau_z$ instead of $\tau_y$ to denote the product market frictions.We assume that the taxes collected are returned to the household as lump-sum transfers.
%Anticipating the benchmark calibration in the next section, the wedge function specified in Equation (\ref{eq:tax}) is increasing and concave in $z$, with the lower and upper bounds being 0 and 1, respectively. The shape of the function captures the size dependency of the product market distortions where the wedges are higher for larger firms. The actual tax function used in the quantitative exercises is plotted against log productivity in Figure \ref{fig:tauz}. %\footnote{There is one difference between Equation (\ref{eq:tax}) and the tax function used by \citet{AdamopoulosRestuccia:2014}. To model the size dependency, in their specification, the authors use an exponential function as opposed to the power function here. We choose the power function because it is consistent with the log-linearity of $\phi_k$ ($\phi_l$) and $z$, while the exponential function implies a tax scheme that increases much sharper with respect to productivity than the empirical counterpart for our case.} %We rule out subsidies ($\tau_z < 0$) because $\lim_{z \downarrow 0} \tau_z = -\infty$ which leads to unrealistic solutions.}
%
%The idiosyncratic $\tau_z$ is meant to capture implicitly a variety of policies and institutions that allocate factors away from large productive firms. For example, this is consistent with the fact that large productive firms face transportation costs, additional management costs, and/or local protectionism and trade barriers that impede the inter-regional flow of goods [\citet{Young:2000}, \citet{HsiehKlenow:2014}, \citet{TombeZhu:2015}, and \citet{Eberhardtetal:2016}]. It could also be that smaller firms are subject to preferential tax treatment.\footnote{For instance, value added taxes for firms with an annual industrial output value of less than CNY 1 million is 3\%, while firms with a production scale larger than CNY 1 million are subject to a 13\% tax rate.} Some of these examples, for instance transportation costs and management costs, are not exactly the ``distortions'' narrowly defined as inefficiencies from policy interventions. Hence a more accurate interpretation of the distortions captured by our model is any factors that prevent firms from reaching their full potentials in a frictionless world. We stick to the word \textit{distortion} mainly for convenience. From a policy perspective, it would be of great interest to follow the so-called direct approach in \citet{RestucciaRogerson:2013} and study the specific policies and regulations that we observe in the economy. We leave this important task to future work.\footnote{\citet{AdamopoulosRestuccia:2014} and \citet{AGpaper} are two recent examples where observable policy distortions are investigated. \citet{AdamopoulosRestuccia:2014} study the observable farm-level price distortions while our own work \citet{AGpaper} focus on distortions created by migration and land distribution policies in China.}

\textit{Correlated Distortions.---}Finally, we introduce the correlated distortions at the firm level to both sectors as implicit progressive output taxes which increase with a firm's productivity levels. The functional form of the tax is:
\begin{equation}
    \tau^i_z = \max \left\{ 0, 1 - \phi_0^i z^{\phi_1^i} \right\}, i=c,d,
\label{eq:tax}
\end{equation}
where the parameter $\phi_0^i$ determines the mean level of the taxes, and the parameter $\phi_1^i$ determines the progressiveness of the taxes. When $\phi_1^i<0$, the tax rates are increasing in firm TFP $z$, and the progressiveness of the taxes is decreasing in the value of $\phi_1^i$.\footnote{This tax function has a long history in macro-public finance literature, which dates back to at least \citet{Benabou:2002}. We thank a referee for pointing this out. Recent studies that use this function include \citet{HsiehKlenow:2014}, \citet{BentoRestuccia:2016} and \citet{Guneretal:2017}. In Online Appendix D.1, we discuss distortions that take more general forms, and present empirical evidence in support of this specific form. See Figure D.2 in Online Appendix D for an illustration of this tax function.}

The tax function (\ref{eq:tax}) is consistent with the positive relationship between firm TFP and average product of factors we find in the CNEC data. This can be seen from Figure \ref{fig:apf}, which depicts the geometric average of the average product of labor and capital $(y/k)^\alpha(y/l)^{1-\alpha}$ against firm TFP $z$ for both the polluting and non-polluting sectors.\footnote{To estimate firm TFP and average product of factors, we need to assign the values to the parameter that determines the income share of capital, $\alpha$, and the span-of-control parameter, $\gamma$. We take these values from our calibration in Section \rom{3}, which implies that $\alpha = \text{0.54}$ and $\gamma = \text{0.93}$. The positive relationship between firm TFP and average product of factors, however, hold for a wide range of values for $\alpha$ and $\gamma$, in addition to the values used here. Moreover, similar patterns are also observed in other countries. For instance, \citet{HsiehKlenow:2014} find a strong and positive relationship between firm TFP and average product of factors in India and Mexico, while \citet{BentoRestuccia:2016} document similar patterns for dozens of developing countries.} It can also be seen that the relationships between the average product of factors and firm TFP in these two sectors share very similar slopes. Based on this observation, we assume $\tau^c_z = \tau^d_z \triangleq \tau_z$ from now on.

The firm-level distortions $\tau_z$ are meant to capture a variety of policies and institutions that reallocate production factors from large productive to small unproductive firms, following the \emph{indirect} approach in the misallocation literature [\citet{RestucciaRogerson:2013}]. These policies and institutions include size-dependent taxes and subsidies that favor small firms, imperfect tax enforcement that induces tax evasion among small firms, financial constraints and contractual frictions that impede the growth of productive firms [\citet{CooleyQuadrini:2001}, \citet{ClementiHopenhayn:2006} and \citet{Akcigitetal:2018}], and local protectionism and internal trade barriers that disproportionately affect large productive firms [\citet{Eberhardtetal:2016} and \citet{TombeZhu:2015}]. While it is of great policy interest to study specific policies and institutions underlying $\tau_z$, we leave this important task to future work.

\begin{figure}[t]
    \begin{center}
%    \includegraphics[width=0.45\textwidth]{D:/PaperDrafts/Pollution/R_Implementation/paperES_R.pdf}%
%    \includegraphics[width=0.45\textwidth]{D:/PaperDrafts/Pollution/R_Implementation/agriES_R.pdf} \\
%    \includegraphics[width=0.45\textwidth]{D:/PaperDrafts/Pollution/R_Implementation/textileES_R.pdf}
%    \includegraphics[width=0.45\textwidth]{D:/PaperDrafts/Pollution/R_Implementation/chemmatES_R.pdf} \\
    \includegraphics[width=0.45\textwidth]{./Figures/apf_pol_weight.pdf}
    \includegraphics[width=0.45\textwidth]{./Figures/apf_npol_weight.pdf}
    %\vspace{-1em}
    \caption{Average Product of Factors versus Firm Productivity in the Cross-Section}
    \floatfoot{Source: CNEC. Both variables have been normalized to reflect the relative values to the sectoral averages, which are similar across sectors.}
    \label{fig:apf}
    \end{center}
\end{figure}

\subsection{Firm's Profit Maximization Problem}

%Recent studies of the Chinese economy have described large distortions at both the sector and the firm levels, which negatively affect aggregate productivity and output considerably.\footnote{See \citet{HsiehKlenow:2009}, \citet{Songetal:2011}, \citet{Brandtetal:2013}, and \citet{TombeZhu:2015}, among others.}
%We assume that all firms face an idiosyncratic distortions $\tau_z$ depending on their productivity level. In the spirit of \citet{BentoRestuccia:2016}, we implement these idiosyncratic wedges in the model by positing a generic ``tax'' function:\footnote{This tax function has a long history in macro-public finance literature, for instance \citet{Benabou:2002}. We thank a referee for pointing this out. Recent studies that adopt the same tax functions include \citet{AdamopoulosRestuccia:2014}, \citet{HsiehKlenow:2014}, and \citet{Guneretal:2017}. Online Appendix D.1 presents detailed empirical evidence that motivates us using this specification.}\textsuperscript{, }\footnote{The idiosyncratic $\tau_z$ is meant to capture implicitly a variety of policies and institutions that allocate factors away from large productive firms. For example, this is consistent with the fact that large productive firms face transportation costs, additional management costs, and/or local protectionism and trade barriers that impede the inter-regional flow of goods [\citet{Young:2000}, \citet{HsiehKlenow:2014}, \citet{TombeZhu:2015}, and \citet{Eberhardtetal:2016}]. It could also be that smaller firms are subject to preferential tax treatment. Some of these examples, for instance transportation costs and management costs, are not exactly the ``distortions'' narrowly defined as inefficiencies from policy interventions. Hence a more accurate interpretation of the distortions captured by our model is any factors that prevent firms from reaching their full potentials in a frictionless world. We stick to the word \textit{distortion} mainly for convenience. From a policy perspective, it would be of great interest to follow the so-called direct approach in \citet{RestucciaRogerson:2013} and study the specific policies and regulations that we observe in the economy. We leave this important task to future work.}
%\begin{equation}
%    \tau_z = \max \left\{ 0, 1 - \phi_0 z^{\phi_1} \right\}.
%\label{eq:tax}
%\end{equation}
%Following the evidence in the Online Appendix D.1, we assume that the the tax function (\ref{eq:tax}) is the same for both sectors.

Firms in the non-polluting sector solve the standard profit maximization problem:
\begin{equation*}
    \pi^c(z) = \max_{k,l} \left\{ (1-\tau_z) z^{1-\gamma}(k^{\alpha}l^{1-\alpha})^{\gamma} - Wl - Rk \right\},
\end{equation*}
where the superscript $c$ stands for ``clean.''

Firms in the polluting sector choose first the optimal treatment technology and then the optimal production plan. The profit function $\pi^d(z)$ is the envelope of the profits when using the dirty technology $\pi_0^d(z)$ and clean technology, $\pi_1^d(z)$:
\begin{equation*}
    \pi^d(z) = \max \left\{ \pi_0^d(z), \pi_1^d(z) \right\},
%\label{eq:piz}
\end{equation*}
where the superscript $d$ stands for ``dirty,'' and the subscript denotes the treatment technologies. Firms using the clean technology are not subject to environmental penalties, hence the profit $\pi_1^d(z)$ is:
\begin{equation*}
    \pi_1^d(z) = \max_{k,l} \left\{ (1-\tau_z) z^{1-\gamma} (k^{\alpha} l^{1-\alpha})^{\gamma} - Wl - R (k+k_E) \right\}.
%\label{eq:pi1z}
\end{equation*}
However, when a firm chooses the dirty technology, it will be punished by the environmental authority, and lose a fraction $\xi$ of its gross profit. Its net profit $\pi_0^d(z)$ is thus:
\begin{equation*}
    \pi_0^d(z) = \max_{k,l} \left\{ \left( 1 - \xi \right)
        \left[ (1-\tau_z) z^{1-\gamma} (k^{\alpha} l^{1-\alpha})^{\gamma} - Wl - Rk \right] \right\}.
%\label{eq:pi0z}
\end{equation*}

The firm's problem implies that there exists a firm size threshold $\tilde{l}^d$ above which firm will choose the clean technology, which is consistent with our empirical finding that larger firms are more likely to use the clean technology. This can be seen by comparing the potential profits from using clean versus dirty technology:
\begin{equation*}
    \pi_1^d(z) - \pi_0^d(z)  = \frac{\xi(1-\gamma)}{(1-\alpha)\gamma}Wl^d(z) - Rk_E.
\end{equation*}
In addition, when $1-\gamma+\phi_1 > 0$, which is satisfied given our calibrated values for $\gamma$ and $\phi_1$, $\pi_i^d(z)$ and $l^d(z)$ are both increasing $z$. Then there exists a threshold $\tilde{z}_d$ such that only firms with TFP higher than $\tilde{z}_d$ would choose clean technology.\footnote{Please see Lemma 2 in Online Appendix G.1 for details.} There also exist two thresholds $\hat{z}_i, i=c,d,$ such that in sector $i$, only members with $z > \hat{z}_i$ choose to be managers.

%The first-order conditions from this problem imply that
%\begin{equation*}
%    \pi_1^d(z) = \frac{1-\gamma}{(1-\alpha)\gamma}Wl^d(z)-R k_E.
%%\label{eq:pi1z}
%\end{equation*}
%Note that here treatment equipment $k_E$ cannot be used to produce the final product. This assumption is based on the empirical finding of \citet{ShadbegianGray:2005}.
%\begin{equation*}
%    \pi_0^C(z) = (1-\xi) \left[ (1-\tau_z) z^{1-\gamma} (k^{\alpha} n^{1-\alpha})^{\gamma} - Wn - Rk \right],
%\end{equation*}
%where the superscript $C$ indicates ``caught.'' If the firm succeeds in evading inspection, the profit function is
%\begin{equation*}
%    \pi_0^{E}(z) = (1-\tau_z) z^{1-\gamma} (k^{\alpha} n^{1-\alpha})^{\gamma} - Wn - Rk,
%\end{equation*}
%where the superscript $E$ indicates ``evaded.'' Because we assume perfect risk sharing within the household, these entrepreneurs will {not} have precautionary motives and will simply maximize the expected profits over $\pi_0^C$ and $\pi_0^{E}$:
%\begin{equation*}
%    \pi_0(z) = \max_{k,n} \left\{ (1-p)\pi_0^{E}(z) + p\pi_0^{C}(z) \right\}.
%\end{equation*}
%Some algebra yields

%and the first-order conditions from this problem imply that
%\begin{equation*}
%    \pi_1^d(z) = \frac{(1-\gamma)(1 - \xi)}{(1-\alpha)\gamma}Wl^d(z).
%%\label{eq:pi1z}
%\end{equation*}

%The standard result from the Lucas model implies that there exist two thresholds $\hat{z}_d$ and $\hat{z}_c$ such that in each sector, all members with $z$ higher than the corresponding thresholds choose to become entrepreneurs. In addition, when $\pi_d^0(z)$ and $\pi_d^1(z)$ satisfy single-crossing condition, there also exists a third threshold $\tilde{z}_d$ such that all firms in the polluting sector with TFP higher than $\tilde{z}_d$ use clean technology. See Result \ref{prop:friction} in Section \rom{2}.D and Lemma 2 in Online Appendix G.1 for details.

\subsection{Stationary Equilibrium}

In this section, we close the model by specifying the household's optimization problem, and then define the stationary equilibrium.

The household solves the standard consumption-saving problem:
\begin{align}
\label{eq:household}
    & \max_{C_t, K_{t+1}} \sum_{t=0}^{\infty} \beta^t U(C_t) \\
    & s.t.  \nonumber \\
    & \qquad C_t + K_{t+1} - (1-\delta)K_t = I_t, \nonumber
\end{align}
where $K_t$ is aggregate capital, $\delta$ is the depreciation rate, and $I_t$ is household income, which we specify in detail shortly.%\footnote{We assume here that the household values only consumption and not environmental quality. This assumption is innocuous in the competitive equilibrium, since no individual household member has control over aggregate environmental quality. However, the assumption does affect the results if a planner's problem is studied or if we want to evaluate the welfare effect of different policies.}
\footnote{Here we do not explicitly model the household's preference over water quality. Adding water quality to the household's utility function will not change the firm's choices in a competitive equilibrium, as no individual household member has any control over the aggregate environmental quality. However, if we study the social planner's problem instead, the household's preference over water quality will become a major modeling choice.} The solution to (\ref{eq:household}) is the standard intertemporal Euler equation:
\begin{equation*}
    U'(C_t) = \beta U'(C_{t+1})(1+R_{t+1}-\delta),
%\label{eq:euler}
\end{equation*}
which pins down the equilibrium interest rate.%\footnote{There is no uncertainty at the household level since we assume perfect risk sharing and a continuum of household members which wash out all idiosyncratic uncertainty. As a result, on the right hand side of (\ref{eq:euler}) there is no expectation operator.}

Household income $I_t$ comes from three sources: wage and interest income, firms' profits, and lump-sum transfers from taxes $\tau_z$ and environmental penalties $\xi$. %To characterize $I_t$, we need some additional notation. We denote $Z_0 = \{z \in [\hat{z}_t, \overline{z}] | \pi_0(z) \geq \pi_1(z) \}$ as the set of firms operating with the dirty technology and $Z_1 = \{z \in [\hat{z}_t, \overline{z}] | \pi_0(z) < \pi_1(z) \}$ as the set of firms using the clean technology. Note that for the intermediate case, where $0 < \hat{z} < \tilde{z} < \overline{z}$, Result \ref{prop:friction} implies $Z_0 = [\hat{z}, \tilde{z})$, and $Z_1 = [\tilde{z}, \overline{z}]$. %Since the ``taxes'' are distributed to household as lump-sum transfers, in the budget constraint taxes and transfers cancel each other out.
If we let $T$ denote the transfers, then household income is\footnote{We have implicitly assumed that firms using clean and dirty technologies coexist in the equilibrium, meaning that $\hat{z}_d<\tilde{z}_d$. This is also the case in our quantitative exercises later.}
\begin{align*}
    I &= R K + W [\mu G(\hat{z}_d)+(1-\mu)G(\hat{z}_c)] + T \\
      & \qquad + \mu\left[\int_{\hat{z}_d}^{\tilde{z}_d} \pi^d_0(z) dG(z) + \int_{\tilde{z}_d}^{\overline{z}} \pi^d_1(z)dG(z)\right] + (1-\mu)\int_{\hat{z}_c}^{\overline{z}}\pi^c(z)dG(z),
\end{align*}
where the transfer $T$ is given by
\begin{equation*}
    T = \mu\xi\int_{\hat{z}_d}^{\tilde{z}_d}\pi^d(z)dG(z) + \tau_z\left[\mu \int_{\hat{z}_d}^{\overline{z}} \pi^d(z) dG(z) + (1-\mu)\int_{\hat{z}_c}^{\overline{z}} \pi^c(z) dG(z) \right].
\end{equation*}%the five terms are capital rental income, wage income, profits from dirty and clean firms, and government transfers, respectively. %The law of large numbers guarantees that the {ex ante} probability of being inspected equals the {ex post} proportion of firms that actually are inspected.

Let $Y$ be aggregate output and $E$ be aggregate pollution, then the stationary equilibrium of the model is defined as follows.
\begin{definition}
\label{def:ge}
A stationary equilibrium of the model consists of prices $\{W, R \}$, allocations $\{C, K, Y \}$, firms' policy functions $\{k^j(z),l^j(z),y^j(z),\pi^j(z)\}, j = c,d$, thresholds for household's occupational choices $\{\hat{z}_c, \hat{z}_d\}$ and polluting firms' technology adoption $\tilde{z}_d$, as well as aggregate pollution $E$, such that:
\begin{enumerate}[(i)]
    \item
    Given factor prices $\{W, R\}$, $\{C, K, \hat{z}_c, \hat{z}_d\}$ solve the household's optimization problem;
    \item
    Given factor prices $\{W, R\}$, $\{k^j(z),l^j(z),y^j(z),\pi^j(z)\}$, $j = c,d$, and $\tilde{z}_d$ solve the firms' optimization problems;
    \item
    Factor prices $\{W, R\}$ clear all markets:
    \begin{itemize}
        \item
        Labor Market:
        \begin{equation*}
            \mu G(\hat{z}_d) + (1-\mu) G(\hat{z}_c) = \mu \int_{\hat{z}_d}^{\overline{z}} l^d(z)dG(z) + (1-\mu)\int_{\hat{z}_c}^{\overline{z}} l^c(z)dG(z),
        \end{equation*}
        \item
        Capital Market:
        \begin{equation*}
            K = \mu \left[\int_{\hat{z}_d}^{\overline{z}} k^d(z)dG(z) + k_E [G(\overline{z})-G(\tilde{z}_d)]\right] + (1-\mu)\int_{\hat{z}_c}^{\overline{z}} k^c(z)dG(z),
        \end{equation*}
        \item
        Product Market (Walras' Law):
        \begin{equation*}
            C + K - (1-\delta)K = \mu \int_{\hat{z}_d}^{\overline{z}} y^d(z)dG(z) + (1-\mu)\int_{\hat{z}_c}^{\overline{z}} y^c(z)dG(z);
        \end{equation*}
    \end{itemize}
    \item
    Aggregate Pollution:
    \begin{equation*}
        E = \mu\left[\int_{\hat{z}_d}^{\tilde{z}_d} e\left(0,y^d(z)\right)dG(z) + \int_{\tilde{z}_d}^{\overline{z}} e\left(1,y^d(z)\right) dG(z)\right].
    \end{equation*}
\end{enumerate}
\end{definition}
\noindent The algorithm to compute the stationary equilibrium is sketched in Online Appendix I.

\subsection{Correlated Distortions, Technology Adoption, and Aggregate Pollution}
\label{sec:analytical}

In this section, we show qualitatively how correlated distortions modeled as Equation (\ref{eq:tax}) affect the adoption of clean technology across firms and the aggregate pollution. First, we show that correlated distortions have a negative impact on firms' incentives to adopt the clean technology. Second, using a simplified one-sector model with a fixed number of firms and \emph{exogenous} firm-level pollution intensity, we characterize the conditions under which correlated distortions lead to higher aggregate pollution. The core trade-off here is between the scale and technique effects, because the correlated distortions generally cause a decrease in average pollution intensity but an increase in aggregate output.\footnote{All the proofs and additional analytical results can be found in Appendices G.1 and G.2.}

%In this section, we illustrate the basic mechanisms of the model using a simplified version of the model. The core concept in our model is the trade-off between the scale and technique effects. Because the standard result from the misallocation literature where distortions reduce output is inherited by our model [\citet{Guneretal:2008}], the key here is hence to understand how distortions affect the technique effect, and how they shape the trade-off between the scale and technique effects. Specifically, we first show that size-dependent distortions discourage the technology adoption of medium size firms. We then characterize the condition under which reducing distortions lead to lower pollution, or equivalently, the technique effect dominates the scale effect. We leave all the proofs as well as additional analytical properties of the model to Appendices G.1 and G.2.

\textit{Technology Adoption.---}Proposition \ref{prop:friction} shows that correlated distortions discourage firms from adopting of clean technology, especially those with medium levels of TFP.
\begin{proposition}
\label{prop:friction}
When $1-\gamma+\phi_1>0$, a firm chooses to install clean technology only when its productivity is higher than a threshold. Moreover, the threshold when the firm faces distortions $\tilde{z}_f$ is higher than that when the firm is not subject to any distortions $\tilde{z}_n$.
\end{proposition}
%\begin{proposition}
%\label{prop:friction}
%Consider two economies, one (denoted as $f$) with correlated distortions as specified in Equation \ref{eq:tax}, and one (denoted as $n$) without distortions. When $1-\gamma+\phi_1^d>0$, there are two thresholds $\tilde{z}_f$ and $\tilde{z}_n$ such that:
%\begin{enumerate}[(i)]
%    \item
%    For each economy $j = f,n$, firms with $z \leq \tilde{z}_j$ choose the dirty technology, while those with $z > \tilde{z}_j$ choose the clean technology.
%%    \item
%%    In the economy with size-dependent distortions, entrepreneurs with $z \leq \tilde{z}_f$ produce by using the dirty technology, while those with $z > \tilde{z}_f$ produce by using the clean technology.
%    \item
%    When the equilibrium wages $W^f = W^n$, the threshold is higher for the distorted economy, that is, $\tilde{z}_f > \tilde{z}_n$.
%\end{enumerate}
%\end{proposition}

\begin{figure}[t]
\begin{center}
    \includegraphics[width=0.60\textwidth]{./Figures/prod_tax_effect.pdf}
    \caption{Correlated Distortions and Treatment Technologies}
    \label{fig:constantp}
    \floatfoot{Note: There are four profit functions in the figure, $\pi_0^n, \pi_0^f, \pi_1^n$, and $\pi_1^f$. The superscripts $n$ and $f$ denote whether firms face correlated distortions in the economy or not, and the subscripts $0$ and $1$ denote whether firms choose the dirty or clean technology, respectively.}
\end{center}
\end{figure}
\noindent Figure \ref{fig:constantp} illustrates the intuition behind Proposition \ref{prop:friction}. Recall that while the adoption cost $Rk_E$ is independent of $z$, the penalty for not using the clean technology $\xi \pi_0(z)$ is increasing in $z$. %Whether it is worthwhile for firms to pay the installation costs is determined by contrasting the costs with the expected profits loss from inspections by the regulator.
Therefore, the adoption of the clean technology pays off for firms with higher $z$. On the other hand, the elasticity of profits to productivity $z$ is $1-\gamma$ when there are no distortions, and is $1-\gamma+\phi_1$ when distortions exist. Since $\phi_1 < 0$, the slope of the profit functions are flatter, and the threshold where firms switch technologies is higher when they face distortions. As a result, while firms with TFP in the range $[\tilde{z}_n, \tilde{z}_f]$ would choose the clean technology when they are not subject to distortions and choose the dirty technology when they are.\footnote{Of course, when the correlated distortions apply to all firms in the economy, they would affect the equilibrium wage $W$ and hence $\tilde{z}_f$ in equilibrium. We find later in our quantitative exercises that $\tilde{z}_f > \tilde{z}_n$ even with general equilibrium effects considered.} %which may partially offset the direct impact of distortions on technology adoption. However, in our quantitative analysis, this general equilibrium response is not large enough to invalidate the conclusion of Proposition \ref{prop:friction}.

%\noindent Figure \ref{fig:constantp} illustrates Result \ref{prop:friction}. There are four profit functions in the figure, $\pi_0^n, \pi_0^f, \pi_1^n$, and $\pi_1^f$, where the superscripts $n$ and $f$ indicate whether there are size-dependent distortions, and the subscripts $0$ and $1$ represent firms using the dirty and clean technology, respectively. Note that although installation cost $Rk_E$ is fixed, expected loss $\xi \pi_0(z)$ is increasing in $z$. %Whether it is worthwhile for firms to pay the installation costs is determined by contrasting the costs with the expected profits loss from inspections by the regulator.
%Therefore, despite that the fixed installation costs of the clean technology are not justified for firms with lower $z$, they will eventually pay off for those with higher $z$. Because the elasticity of profits to productivity is $1-\gamma$ when there are no distortions, which is larger than that in a market with distortions $1-\gamma-\phi_1$, the distortions decrease the rate at which profits increase with $z$ by $\phi_1$. As a result, the threshold where firms switch technology is higher when there are distortions, causing a positive measure $\Delta z(\tau) = G(\tilde{z}_f) - G(\tilde{z}_n)$ of firms using the clean technology when there is no distortions to switch to dirty technology when facing the distortions.

\textit{Aggregate Pollution.---}To derive a closed-form expression for the relationship between correlated distortions and aggregate pollution, we build a simplified one-sector model that abstracts from the endogenous occupation choice and treatment technology choice.\footnote{Please see Online Appendix G.2 for a detailed description of the simplified model and additional analytical results.} This complements our analysis in Proposition \ref{prop:friction}, which focuses on how distortions affect firms' decision in that the general equilibrium effects are captured. Proposition \ref{prop:agge} summarizes our main findings.
%\textit{Aggregate Pollution.---}To derive a closed-form relationship between aggregate pollution and the size-dependency of the distortions $\phi_1$, we simplify the model along several key dimensions. In particular, we abstract from capital in the economy. We also shut down the two discrete choice decisions in the model by assuming first that household members are exogenously assigned to the roles of entrepreneurs and workers, and second that the firm-level pollution intensity mechanically decreases in production scale by elasticity $-1 < \psi_1 < 0$. Notice that here $\psi_1$ captures both the reduction in intensity from adopting clean technology and during the production stage. Formally, we have the following result.
\begin{proposition}
\label{prop:agge}
In the simplified model, there exists a threshold
\begin{equation*}
    \hat{\phi}_1 = \frac{\psi_1(1-\gamma)}{1-\gamma(1+\psi_1)},
\end{equation*}
such that $E$ is increasing in $\phi_1$ when $\phi_1 < \hat{\phi}_1$, and decreasing when $\phi_1 \geq \hat{\phi}_1$.
\end{proposition}

Proposition \ref{prop:agge} says that the relationship between $E$ and the progressiveness of the distortions $|\phi_1|$ is inverted-U shaped with the turning point $|\hat{\phi}_1|$ increasing in the elasticity of emission intensity to output $|\psi_1|$.\footnote{Here because $\phi_1$ and $\psi_1$ are both negative, the progressiveness and elasticity are stronger when $|\phi_1|$ and $|\psi_1|$ are larger, meaning that the raw values $\phi_1$ and $\psi_1$ are smaller.} Because correlated distortions generally decreases the total output while increasing the average pollution intensity, the intuition behind Proposition \ref{prop:agge} is a race between the scale and technique effects. In particular, the scale effect is larger when the progressiveness of the distortions is stronger (a smaller negative $\phi_1$), while the technique effect is larger when the elasticity of emission intensity to output is larger (a smaller negative $\psi_1<0$). As a result, when $|\phi_1|$ is not too large relative to $|\psi_1|$, the technique effect dominates. Hence an increase in $\phi_1$ (which means a decrease in the progressiveness) causes higher aggregate pollution $E$. Otherwise, the scale effect dominates, and an increase in $\phi_1$ reduces $E$. The average distortions $\phi_0$ (which is positive) always reduces $E$, however, since it does not affect the firm size distribution, and hence only has the scale effect. The overall effect of the correlated distortions is thus a combination of those from $\phi_0$ and $\phi_1$.

%Proposition \ref{prop:agge} basically says that  the aggregate pollution $E$ is decreasing in average distortion $\phi_0$, and the relationship between $E$ and the progressiveness of distortions $-\phi_1$  (notice that $\phi_1<0$) is inverted-U shaped, where the turning point $-\hat{\phi}_1$ is decreasing in $\psi_1$. The intuition goes as follows. Correlated distortions generally decreases the total output while increasing the average pollution intensity. Therefore, the change in aggregate pollution $E$ depends on the race between the scale and technique effects.  An increase in $\phi_0$ leads to a uniform increase in distortions facing all firms. This would increase aggregate output, but induce little reallocation of production factors across firms, and thus have little impact on the average pollution intensity. Therefore, an increase in $\phi_0$ would cause a decrease in $E$.
%
%What is more interesting and more relevant to our core mechanism-the reallocation across firms, is the relationship between $E$ and the progressiveness of distortions $-\phi_1$. Intuitively, the scale effects are larger when the progressiveness of the distortions $-\phi_1$ is larger, and the technique effects are larger when the elasticity of emission intensity to output $\psi_1$ is smaller (notice that $\psi_1<0$). When $-\phi_1$ is not too large relative to $-\psi_1$ (or $-\phi_1< -\hat{\phi}_1$), the technique effect dominates, and an increase in $-\psi_1$ leads to an increase in aggregate pollution $E$. Otherwise, the scale effect would dominate, and an increase in $-\psi_1$ leads to a decrease in $E$.
%
%To sum up, the key message from Proposition \ref{prop:agge} is, when both average distortion $\phi_0$ and progressiveness of distortions $-\phi_1$ are not too large relative to the absolute value of the elasticity of emission intensity to output $-\psi_1$, the technique effect of correlated distortions would dominate the scale effect, which lead to an increase in aggregate pollution.

%The intuition of the above result goes as follows. We have shown that reducing the distortions would increase the production scale and decrease the pollution intensity at the same time. Hence whether aggregate pollution $E$ increases or decreases depends on whether the scale or the technique effect dominates. For a given level of the technique effect $\psi_1$, if output is very responsive to a marginal decrease in distortions, total emissions are likely to increase as a consequence. Because more severe size-dependency of the distortions implies that more productive firms are subject to higher marginal tax, a marginal decrease of the size-dependency of the distortions at a higher level would increase output by more, and hence the increase in aggregate emissions. The reverse is true for lower level of the size-dependency. Since output is more responsive to the size-dependency of the distortions when returns to scale are high, and the technique effect is stronger when $\psi_1$ is lower (remember $\psi_1 < 0$, hence a larger $\psi_1$ implies weaker technology), the scale effect is more likely to dominate when returns to scale are high, and when the technique effect is weak.

%Proposition \ref{prop:agge} basically says that the relationship between the progressiveness of distortions $-\phi_1$ ($\phi_1<0$) and the aggregate pollution $E$ is inverted-U shaped. When $-\phi_1$ is below a threshold -$\hat{\phi}_1$, which itself is decreasing in $\psi_1$, the aggregate pollution $E$ is increasing in $-\phi_1$. Otherwise, the aggregate pollution $E$ is decreasing in $-\phi_1$. The intuition goes as follows. Correlated distortions would generally decrease the total output as well as increase the average pollution intensity, and the change in aggregate pollution $E$ depends on the race between the scale and technique effects.  The scale effects are larger when $-\phi_1$ is larger, and the technique effects are larger when $-\psi_1$ is larger ($\psi_1<0$). When $-\phi_1$ is not too large relative to $-\psi_1$, the technique effects dominate. Otherwise, the scale effects would dominate, and aggregate pollution $E$ is increasing in $-\phi_1$.  In addition,  when $\gamma$ is larger, the scale effects are also larger as the output is more responsive to distortions, and therefore the threshold -$\hat{\phi}_1$ would move to the left.

%Part (i) of Proposition \ref{prop:agge} basically says that when the progressiveness of distortions ($-\phi_1$) is below a threshold (-$\hat{\phi}_1$), the aggregate pollution $E$ is increasing in the progressiveness. Correlated distortions would generally decrease the total output as well as increase the average pollution intensity. As a result, the change in aggregate pollution $E$ depends on the race between the scale and technique effects. If average pollution intensity is very responsive to distortions while the aggregate output is not, total emissions would increase as a consequence. This is true if the progressiveness of distortions is not too high. Since output is more responsive to the distortions when returns to scale ($\gamma$) are high, and the average pollution intensity is less responsive when $\psi_1$ is higher ($-\psi_1$ is lower; in the extreme case of $\psi=0$, the average pollution intensity is not responsive to distortions at all), the threshold -$\hat{\phi}_1$ moves to the left when  $\psi_1$ or $\gamma$ are higher.

%Similar results hold for the average pollution intensity as well, which we summarize formally in the following corollary.
%\begin{corollary}
%\label{prop:aggi}
%In the simple model, the relationship between the average pollution intensity $E/Y$ and the size-dependency of the distortions $\phi_1$ is such that
%\begin{enumerate}[(i)]
%    \item
%    when $\psi_1 < (1-2\gamma)/\gamma$, the average pollution intensity is always increasing in $\phi_1$;
%    \item
%    when $\psi_1 \geq (1-2\gamma)/\gamma$, there exists a threshold
%    \begin{equation*}
%        \overline{\phi}_1 = \frac{(1+\psi_1)(1-\gamma)}{1-2\gamma+\gamma\psi_1},
%    \end{equation*}
%    such that when $\phi_1 < \overline{\phi}_1$, $E/Y$ is increasing in $\phi_1$; and when $\phi_1 \geq \overline{\phi}_1$, $E/Y$ is decreasing in $\phi_1$;
%    \item
%    $\overline{\phi}_1$ is increasing in both $\psi_1$ and $\gamma$;
%%    \item
%%    $\overline{\phi}_1 < \hat{\phi}_1$.
%\end{enumerate}
%\end{corollary}
%Notice that the threshold in Result \ref{prop:agge} %and Corollary \ref{prop:aggi}
%provides a quick way to predict that whether for a certain economy, reducing the size-dependency of the distortions would lead to decrease in aggregate pollution.% and average intensity.

%To clarify the basic mechanics of the model, in this section we analyze a firm's optimization problem when $R$ and $W$ are given exogenously. We prove two results. First, we show that there exists a threshold $\tilde{z}$ such that firms with $z>\tilde{z}$ adopt the clean technology, while firms with $z \leq \tilde{z}$ do not. Second, if we denote the previous threshold in environments with and without size-dependent distortions as $\tilde{z}_f$ and $\tilde{z}_n$ respectively, we show that $\tilde{z}_f > \tilde{z}_n$. The first result states that the returns to scale embedded with the clean technology are only exploited when firms are sufficiently large. The second result states that by introducing size-dependent distortions, some firms that adopt the clean technology when there are no distortions do not have the profit margin to benefit from the clean technology and hence choose to enter the market with the dirty technology. Throughout, we assume $0<\alpha<1$, $0<\gamma<1$, $\phi_0 = 1$, and $1 - \gamma - \phi_1 > 0$. We impose the last inequality because the tax specified in [reference to tax function] is imposed on firm-level TFP $z$. For the benefits of higher talent $z$ (the elasticity of profits to TFP is $1-\gamma$) to always outweigh the costs (the elasticity of tax to TFP is $\phi_1$), $1-\gamma-\phi_1 > 0$ must be satisfied. All proofs are deferred to Online Appendix G.
%
%Lemma \ref{lemma:nofrictionpi} characterizes firms' profit functions in the absence of size-dependent distortions.
%\begin{lemma}
%\label{lemma:nofrictionpi}
%In an economy with no size-dependent distortions, $\pi_0(z)$ and $\pi_1(z)$ are both increasing and linear with respect to $z$. In addition, the slope of $\pi_1(z)$ is steeper than that of $\pi_0(z)$:
%\begin{equation}
%    \frac{\partial \pi_0 (z)}{\partial z} = (1 - \xi)\frac{\partial \pi_1 (z)}{\partial z}, \qquad \forall z \in Z.
%\label{eq:lemma1}
%\end{equation}
%\end{lemma}
%\noindent Lemma \ref{lemma:nofrictionpi} highlights the core trade-off of adopting the clean technology in our model. Although the upfront fixed costs shift the overall profit function down by $R k_E$, the profits of firms using the clean technology will not be confiscated by the regulators. Owing to the constant elasticity between capital and labor, the optimal capital/labor ratio is constant in the absence of factor market distortions. Further, entrepreneurs reap economic rents from managerial talents $z$, and these economic rents increase linearly in $z$ because due to the constant returns to scale production function.
%
%Since the tax in [reference to tax function] is size-dependent in the sense that more talented entrepreneurs are subject to higher distortions, it can be shown that in an economy {with} size-dependent distortions, both $\pi_0(z)$ and $\pi_1(z)$ are concave.
%\begin{corollary}
%\label{lemma:frictionpi}
%Suppose size-dependent distortions are specified as $\max\left\{ 0, 1 - z^{\phi_1} \right\}$ with $1 - \gamma + \phi_1 > 0$; then, $\pi_0(z)$ and $\pi_1(z)$ are both increasing and concave with respect to $z$. In addition, the slope of $\pi_1(z)$ is steeper than that of $\pi_0(z)$:
%\begin{equation*}
%    \frac{\partial \pi_0 (z)}{\partial z} = (1 - \xi)\frac{\partial \pi_1 (z)}{\partial z}, \qquad \forall z \in Z.
%\end{equation*}
%\end{corollary}
%\noindent On the contrary, if the taxes are uniform---meaning that for all $i$, $\tau_{z_i}$s are the same---then $\pi_0(z)$ and $\pi_1(z)$ remain linear.
%
%Since the wage income associated with being a worker is fixed at $W$, the monotonicity of the profit functions implies a threshold $\hat{z}$ for which all household members with talents higher than $\hat{z}$ choose to become entrepreneurs. Put differently, household members choose their occupation according to their comparative advantages. This is the standard result from the Lucas model. We summarize this in Result \ref{prop:threshold}.
%\begin{result}
%\label{prop:threshold}
%There exists a unique threshold $\hat{z}$ such that all household members with $z < \hat{z}$ choose to be workers and those with $z \geq \hat{z}$ become entrepreneurs. Further, $\hat{z}$ is the solution of $W = \pi(\hat{z})$.
%\end{result}

%To explain the intuition, we solve a simplified version of the model here.

\section{Calibration}
\label{sec:calibration}

In this section, we calibrate our model to the Chinese data. We first describe our key calibration strategy, and then explain how our choice of the model parameters matches the key aspects of the Chinese economy at both the aggregate and firm levels.

%\textit{Calibration.}---We calibrate our model to the Chinese data. The model period is set to be one year. Motivated by the empirical evidence in Section \rom{1}, we assume that the pollution intensity function of firms with treatment technology $i$ and production level $y$ is log-linear:
%\begin{equation}
%    \log \left(\frac{e}{y}\right) = \psi_0^{(i)} + \psi_1^{(i)} \log y.
%\label{eq:emsn_cali}
%\end{equation}
%This specification implies that {conditional} on the treatment technology adopted, a ``within-group'' intensity reduction remains as production scale increases. Here, $\psi_1^{(i)}$ captures, for instance, the intensity reduction during the production stage mentioned in Section.\rom{1}.C. Equation (\ref{eq:emsn_cali}) implies that actual emissions are
%\begin{equation}
%    e = E(i,y) = \mathrm{e}^{\psi_0^{(i)}} y^{1+\psi_1^{(i)}}.
%\label{eq:emsn_firm}
%\end{equation}
%Our model features only two broad categories of treatment technologies as opposed to five in the data.
%Recall that we interpret the clean technology in our model as {biological} technology and dirty technology as the remaining types. We assume only the installation of biological technology incurs the fixed cost $R k_E$.\footnote{Qualitatively, assuming that dirty technology also requires a fixed cost will not affect the property of the model. It is equivalent to a decrease in the cost of clean technology, since what matters for firm's decision is the difference of the two costs.}
\subsection{Calibration Strategy}

The main task of our quantitative analysis is to study how correlated distortions affect aggregate pollution by changing the firm size distribution. Therefore, it is important that our model matches well the pollution intensity by firm size, the relative distortions faced by large versus small firms, and the firm size distribution in China. As we mentioned in the previous section, the polluting sector is mapped to the top five polluting industries and the non-polluting sector to the rest of the manufacturing sector, while clean and dirty technologies are interpreted as biological and other (physical plus chemical) technologies.

%\textit{Calibration Strategy.---}The purpose of our quantitative exercise is to study how firm size distribution affects aggregate pollution. Therefore, it is important that our model matches well the firm size distribution in China, the relative distortions faced by large versus small firms, and the pollution intensity of different sized firms. We calibrate our model to the whole manufacturing sector.

Following the evidence in Section \rom{1}.B, the relationship between pollution intensity and firm size is given by Equation (\ref{eq:intensity_size}), and the emissions by firms using different treatment technologies are
\begin{equation*}
    e = \mathcal{E}(i,y) = \mathrm{e}^{\psi_0^{(i)}} y^{1+\psi_1^{(i)}}, i=0,1,
\end{equation*}
where $\{\psi_0^{(i)}, \psi_1^{(i)}\}$ are based on the reduced-form estimates from Equations (\ref{eq:poolols_biological}) and (\ref{eq:poolols_others}).
%where $\{\psi_0^{(i)}, \psi_1^{(i)}\}$ are given by the regression coefficients from (\ref{eq:poolols_dirty}) and (\ref{eq:poolols_clean}).

The firm size distribution in the model is determined by {both} the talent distribution $G(\cdot)$ and the progressiveness of distortions $-\phi_1$. This can be seen from Equation (\ref{eq:zandl}), derived from firms' first order conditions:
\begin{equation}
\label{eq:zandl}
    (1-\tau_z)z^{1-\gamma} = \Phi l^{1-\gamma},
   % z^{1-\gamma+\phi_1} = \Phi l^{1-\gamma}
\end{equation}
where $\Phi$ is a constant. As a result, the progressiveness of the distortions $\phi_1$ has to be calibrated together with the talent distribution $G(\cdot)$. To do this, if we let $\theta_l = y/l$ be the average product of labor, the firm's first order conditions imply
\begin{equation*}
    \theta_l = \frac{y}{l} = \frac{W}{(1-\alpha)\gamma(1-\tau_z)}.
\end{equation*}
Substituting the tax function (\ref{eq:tax}) into the above equation, we have
\begin{equation}
\label{eq:avgl}
    \left(\frac{z_i}{z_j} \right)^{\phi_1} = \frac{\theta_{l,j}}{\theta_{l,i}}.
\end{equation}
Equation (\ref{eq:avgl}) can then be used to identify $\phi_1$ using the variations in average product of labor of firms with different TFP.

%Given a choice of the parameters $\alpha$ and $\gamma$, we can bring our model to the data, and back out the progressiveness of distortions $-\phi_1$. Then we choose $G(\cdot)$ to match the observed firm size distribution. Specifically, let $\theta_l = y/l$ be the average product of labor, the firm's first order conditions imply
%%Because the firm size distribution in the model is affected by {both} the talent distribution $G(\cdot)$ and distortions $\tau_z$, we cannot use only the distribution to calibrate these two elements. To find an additional moment to calibrate $\tau_z$, we follow a similar strategy as the one used by \citet{AdamopoulosRestuccia:2014} when they calibrate the elasticity of distortions to farm size. Specifically, if we let $\theta_l = y/l$ be the average product of labor, then the first order conditions of the firm give us

%Given a choice of the parameters $\alpha$ and $\gamma$, we can compute both $z$ and $\theta_l$ for each firm in the data. Then Equation (\ref{eq:avgl}) can be used to pin down $\phi_1$.
%Since $z$ and $\theta_l$ can all be measured from the data, Equation (\ref{eq:avgl}) can be used to back out $\phi_1$. Notice that because the value of $z$ changes with $\gamma$, and $\gamma$ naturally affects how $G(z)$ shapes the size distribution by altering the level of returns to scale, Equation (\ref{eq:avgl}) needs to be used together with the firm size distribution to calibrate jointly $\phi_1, \gamma$ and $G(z)$.\footnote{Another commonly used calibration strategy in the literature takes the United States as an undistorted economy (which means $\tau_z = 0$ in our model) and calibrates $G(z)$ by matching the size distribution from the tax-free economy to the U.S. data. Taxes are then introduced such that certain moments of the size distribution of the country in interest are matched. See, for example, \citet{Guneretal:2008}, \citet{Bartelsmanetal:2013}, \citet{AdamopoulosRestuccia:2014}, and \citet{BentoRestuccia:2016}, among others. If we calibrate our model in this way, the underlying assumption would be that the talent distribution of the entrepreneurs in China is the same as that in the United States and that all the difference between the size distributions of China and the United States is due to taxes. As is suggested by Figure 2 in \citet{BloomVanReenen:2010}, the evidence regarding this point is mixed. In our opinion, both strategies have their strengths and weaknesses, and face different data limitations. The quantitative results of our study are largely driven by the size and shape of $\tau_z$. Therefore, as long as the alternative calibrations imply similar tax schemes to that used in our benchmark, the quantitative aspects of our results would continue to hold.}

%Given a choice of $\alpha$, $\gamma$ and $\phi_1$, we then choose  $G(\cdot)$ to match the observed firm size distribution in China. Again, from the firm's first-order conditions, we get another useful equation that bridges our model and the data
%We ask the model to match two aspects of the firm size distribution---the total number and share of employment of firms of a certain size. Figure \ref{fig:es} suggests that the distribution of small and medium-sized firms follows approximately a log-normal distribution. However, a log-normal distribution cannot generate the concentration of employment among large firms. The heavy right tail is crucial to our evaluation because these are the firms that are producing with the clean technology. To capture both characteristics, we assume that the distribution consists a log-normal part with total mass $1-g_{max}$ that accounts for the lower end, and an atom with measure $g_{max}$ that accounts for those very large firms.\footnote{This strategy follows \citet{Guneretal:2008} and is popular among macroeconomic studies featuring distributions with fat tails. See, for example, \citet{Castanedaetal:2003}.} The first order conditions of the firms yield

%\begin{equation}
%\label{eq:zandl}
%    (1-\tau(z))z^{1-\gamma} = \Phi l^{1-\gamma}
%\end{equation}
%where $\Phi$ is a constant. Since by the property of log-normal distribution, if $l$ is log-normally distributed, $l^{1-\gamma}$ follows also a log-normal distribution, Equation (\ref{eq:zandl}) suggests that the ``after-tax'' productivity $(1-\tau_z)z^{1-\gamma} \triangleq z'$ follows the same distribution of $l^{1-\gamma}$, which we assume to be a combination of a log-normal part with mean $\mu_z$ and standard deviation $\sigma_z$, and an atom with value $z'_{max}$ and measure $g_{max}$. With $z'$ suitably calibrated, the ``before-tax'' productivity $z$ can then be calculated according to

To calibrate $G(\cdot)$, we cannot use Equation (\ref{eq:zandl}) and the firm-level data to back out the distribution semi-parametrically. The reason is that the endogenous occupation choice in our model makes the distribution of firm TFP in equilibrium also endogenous, making the semi-parametric way of calibration untractable in practice. This is unlike other studies that assume a fixed distribution of firm TFP in equilibrium, for instance \citet{BentoRestuccia:2016}. To keep the calibration process tractable, motivated by Equation (\ref{eq:zandl}), we assume that the distribution of the ``after-tax'' TFP $z' = (1-\tau_z)z^{1-\gamma}$ takes the following form: the majority on the bottom side characterized by a truncated log-normal distribution with log mean $\mu$ and standard deviation $\sigma$, and a top value $z'_{max}$ with a total mass $g_{max}$ representing the large firms. This mass of top managers allows our model to match the observed concentration of employment among large firms, which have lower emission intensities than other firms.\footnote{This strategy is popular among macroeconomic studies on distributions with fat tails. See for example, \citet{Castanedaetal:2003} and \citet{Guneretal:2008}.} We then choose the values of $(\mu, \sigma, z'_{max}, g_{max})$ together with $\gamma$ and $\phi_1$ to match the observed firm size distribution and Equation (\ref{eq:avgl}). The true firm-level TFP $z$ and its distribution $G(z)$ can be backed out by
\begin{equation*}
    z = \left[z'\phi_0^{1/(\gamma-1)}\right]^{\frac{1-\gamma}{1-\gamma+\phi_1}},
\end{equation*}
given a choice of $\phi_0$.
%\begin{equation*}
%    z = \left(z'\phi_0^{1/(\gamma-1)}\right)^{\frac{1-\gamma}{1-\gamma+\phi_1}}
%\end{equation*}

%Since $\tau_z$ is levied based on productivity $z$, we assume that the distribution of ``after-tax'' productivity $z' = (1-\tau_{z})z^{1-\gamma}$ is a combination of two components. The first is a log-normal distribution with mean $\mu$, standard deviation $\sigma$, and total probability mass $1-g_{max}$ that accounts for the majority of small and medium-sized firms. The second is an atom with value $z'_{max}$ and measure $g_{max}$, which accounts for those very large firms.\footnote{This strategy follows \citet{Guneretal:2008} and is popular among macroeconomic studies of wealth distribution. See, for example, \citet{Castanedaetal:2003}.} The ``before-tax'' productivity $z$ can then calculated by
%\begin{equation*}
%    z = \left(z'\phi_0^{1/(\gamma-1)}\right)^{\frac{1-\gamma}{1-\gamma+\phi_1}},
%\end{equation*}
%which gives us $G(z)$.

\subsection{The Choice of Parameter Values}

In total, we need to choose values for 17 parameters: the discount factor $\beta$, depreciation rate $\delta$, production technology parameters $\{\alpha, \gamma \}$, the relative size of the polluting sector $\mu$, treatment technology parameters $\{\psi_0^{(0)}, \psi_1^{(0)}, \psi_0^{(1)}, \psi_1^{(1)}, k_E, \xi \}$, correlated distortions $\{ \phi_0, \phi_1 \}$, and distributional parameters $\{\mu_z, \sigma_z, z'_{max}, g_{max}\}$.

Six of the seventeen parameters can be determined exogenously. We set the depreciation rate $\delta$ to 10\% [\citet{Songetal:2011}]. $\{\psi_0^{(0)}, \psi_1^{(0)}, \psi_0^{(1)}, \psi_1^{(1)} \}$ are taken from the reduced-form estimates from regressions (\ref{eq:poolols_biological}) and (\ref{eq:poolols_others}) in Section \rom{1}.B, giving us $\psi_0^{(0)} = -$3.41, $\psi_1^{(0)} = -$0.36, $\psi_0^{(1)} = -$4.37, and  $\psi_1^{(1)} = -$0.33. In the context of our model, these estimates suggest that, on average, for two firms with the same level of output but different treatment technologies, the firm using the clean technology emits 40\% to 60\% less pollutants than the one with the dirty technology. We set $\mu =$ 0.20, which is the share of manufacturing firms accounted for by the five polluting industries in the CNEC data.\footnote{The share of manufacturing output accounted for by these five industries is 18\%, which is very close as well.}

The remaining parameters have to be calibrated jointly due to general equilibrium feedback. Still, some parameters can be calibrated more or less independently from others, which substantially improves the tractability of the calibration process. In particular, we choose $\beta$ and $\alpha$ to match the capital to output ratio of 1.65, and capital share of 0.5 in China respectively [\citet{Baietal:2006}]. We set $\xi$ and $k_E$ such that the model reflects the average cost to install clean technology in the data. For the five polluting industries, we find in the NGSPS that 57\% of the firms use biological technology, and the average adoption cost of biological equipments is approximately 2.5\% of the average firm output \textit{for these firms}. These two targets help us pin down the values of $\xi$ and $k_E$.

We then calibrate $\{\gamma, \mu_z, \sigma_z, z'_{max}, g_{max}, \phi_1 \}$ such that the model generates a firm size distribution comparable to the data and Equation (\ref{eq:avgl}) holds. To link Equation (\ref{eq:avgl}) to the data, we set $\{z_i, z_j\}$ and $\{\theta_{l,i}, \theta_{l,j}\}$ to their average levels in the top and bottom quintiles respectively. Because the calculation of $z$ depends on $\gamma$, Equation (\ref{eq:avgl}) also defines a relationship between $\phi_1$ and $\gamma$. For the size distribution, we focus on the number of firms and the share of employment in each of the five size groups (Figure \ref{fig:fitness}). In practice, we adjust $\{\gamma, \mu_z, \sigma_z, z'_{max}, g_{max} \}$. For each $\gamma$, we compute the corresponding $\phi_1$ using Equation (\ref{eq:avgl}). We then compute the size distributions in the equilibrium and repeat the process for different combinations of the five parameters until the size distributions in the equilibrium are close to those in the data.

Finally, following \citet{BentoRestuccia:2016}, we calibrate $\phi_0$ such that the average tax burden in the economy matches the value added tax rate Chinese manufacturing firms face, which is 13\%. This gives us the value of $\phi_0 =$ 1.15.\footnote{In general, it is difficult to estimate the average distortions in an economy, because many factors that lead to resource misallocation are either poorly measured or not measured at all. Reassuringly, a change in $\phi_0$ causes a uniform change in firm-level distortions, and therefore has very limited impact on firm size distribution and aggregate pollution intensity. As a result, a different calibration target for $\phi_0$ will not affect the main insight of our paper.} Table \ref{tab:calibration} lists the model parameters, their targets, and the calibrated values.

%We then calibrate $\{\gamma, \mu_z, \sigma_z, z'_{max}, g_{max}, \phi_1 \}$ such that the model generates a firm size distribution comparable to the data and Equation (\ref{eq:avgl}) holds. To map Equation (\ref{eq:avgl}) to the data, we set $\{z_i, z_j\}$ and $\{\theta_{l,i}, \theta_{l,j}\}$ to their average levels in the top and bottom quintiles respectively. Because the calculation of $z$ depends on $\gamma$, Equation (\ref{eq:avgl}) also defines a relationship between $\phi_1$ and $\gamma$. For the size distribution, we focus on the number of firms and the share of employment in each of the five size groups (Figure \ref{fig:fitness}). In practice, we adjust $\{\gamma, \mu_z, \sigma_z, z'_{max}, g_{max} \}$. For each $\gamma$, we compute the corresponding $\phi_1$. Given the value of all other parameters, we then compute the size distributions in the equilibrium. We repeat the process for different combinations of the five parameters until the size distributions in the equilibrium are close to those in the data. Notice that Equation (\ref{eq:avgl}) holds by construction.

%Finally, we calibrate $\phi_0$ such that the average tax burden in the economy equals the 13\% value added tax imposed on Chinese manufacturing firms in the real life. This gives us the value of $\phi_0 =$ 1.15. In general, it is difficult to estimate the average distortions in an economy because many of the factors that lead to resource misallocation are unobservable [\citet{RestucciaRogerson:2013}] and they do not affect the firm size distribution [\citet{Guneretal:2008}]. Our choice of the average tax rate as the calibration target of $\phi_0$ follows \citet{BentoRestuccia:2016}.\footnote{As shown in Result \ref{prop:friction}, the gains in output (and capital and consumption as well) from eliminating size-dependent distortions are increasing in the average level of the distortions. Hence, targeting a higher average ``tax'' rate increases such gains monotonically, which does not affect the results qualitatively. However, quantitatively, the removal of extremely large distortions may lead to a larger increase in output than the decrease in pollution intensity, thereby raising aggregate pollution. Moreover, since Section \rom{4}.B examines the effect of a uniform tax, the results therein could be used to infer how qualitatively the results would change compare to the benchmark case.} Table \ref{tab:calibration} presents the model parameters, their targets, and the calibrated values.

%We use the information on the average products of capital to calibrate the tax function.\footnote{Using the average product of labor yields the same results, since $\phi_i \approx \phi_l$ as shown in Section \rom{2}.B.} Equation [reference to distortion] suggests that the elasticity of $\phi_k$ to $1-\tau_z$ is equal to unity. Therefore, $\phi_1$ is equal to the elasticity of $\phi_k$ to $z$. We thus calculate $\phi_k$ and $z$ according to Section \rom{2}.B, with $R = 0.1$ [\citet{HsiehKlenow:2009}] and the same $\gamma$ used later when we calibrate the model to match the firm size and employment distributions. We then run a regression
%\begin{equation*}
%    \log \phi_{k_i} = \phi_0 + \phi_1 \log z_i + \varepsilon_{z_i},
%\end{equation*}
%which gives us the value for $\phi_1 = -0.03$. %\footnote{The elasticity here is lower than that in Section \rom{2}.B because $z$ is calculated by using $\gamma = 0.93$, while previously we set $\gamma = 0.85$.}
%Given $\phi_1$, we then calibrate $\phi_0$ such that the average tax burden in the economy equals the value added tax imposed on Chinese manufacturing firms in the data, which is 13\%. This gives us the value of $\phi_0 = 1.15$. In general, it is difficult to estimate the average distortions in an economy because many of the factors that lead to resource misallocation are unobservable [\citet{RestucciaRogerson:2013}] and they do not affect the firm size distribution [\citet{Guneretal:2008}]. Our choice of the average tax rate as the calibration target of $\phi_0$ follows \citet{BentoRestuccia:2016}.\footnote{As shown in Result \ref{prop:friction}, the gains in output (and capital and consumption as well) from eliminating size-dependent distortions are increasing in the average level of the distortions. Hence, targeting a higher average ``tax'' rate increases such gains monotonically, which does not affect the results qualitatively. However, quantitatively, the removal of extremely large distortions may lead to a larger increase in output than the decrease in pollution intensity, thereby raising aggregate pollution. Moreover, since Section \rom{4}.B examines the effect of a uniform tax, the results therein could be used to infer how qualitatively the results would change compare to the benchmark case.}
%We choose to target only the value added tax rate and not include other frictions because as is shown in Proposition \ref{prop:friction}, the gains in output (and capital and consumption as well) from eliminating the product market friction are increasing in the average level of frictions. Targeting a higher average ``tax'' rate increases such gains monotonically, and will not affect the results qualitatively. We therefore choose a conservative target for the average level of frictions. We set $A=1$ as normalization.

%The remaining parameters are calibrated jointly by using two layers: an outer layer loops over the parameterization of $G(z)$ and an inner layer solves the model given $G(z)$. In the inner layer, we first approximate $G(z)$ with 5,000 grid points. We then choose $\beta$ and $\alpha$ to match the capital/output ratio of 1.65 and capital share of 0.5 in China, respectively [\citet{Baietal:2006}]. We set $\xi$ and $k_E$ such that the total investment in treatment equipment is equal to 1\% of total output and the proportion of firms adopting clean technologies equals the adoption rate of biological equipment 57\% for the five industries we focus on. The value of $\gamma$ is set such that the difference between the numbers of firms falls into each bin of the employment and firm size distributions generated by the model and those in the data are minimized. More specifically, if we let $s_q$ and $\hat{s}_q$ be the number of firms in each bin $q$ (10 in total) calculated from the data and from the model respectively, $\gamma^*$ solves
%\begin{equation}
%\label{eq:innergamma}
%    \gamma^* = \argmin_{\gamma} \sum_{q=1}^{10} \left( s_q - \hat{s}_q \right)^2.
%\end{equation}
%Note that for each combination of $\{ \mu, \sigma, z_{max}, g_{max} \}$, there is one corresponding $\gamma^*$. Therefore, in the outer layer, we choose the combination of $\{ \mu, \sigma, z_{max}, g_{max} \}$ that minimizes the minimum distances from the inner layer. Furthermore, we require that $\gamma^*$ is the same as that used to calculate $z$. %Put differently, the outer layer picks the minimum of the right hand side values of Equation (\ref{eq:innergamma}) when evaluated at $\gamma^*$.
\begin{table}[t]
\footnotesize
\centering
\begin{threeparttable}
\caption{Calibration}
\begin{tabular}{p{75pt}p{45pt}p{60pt}p{185pt}}
    \hline \hline
    Parameter     &                   & Value         & Target                                                      \\
    \midrule
    Production    & $\delta$          & 0.1000        & Depreciation Rate                                           \\
                  & $\alpha$          & 0.5376        & Capital Share (0.5)                                         \\
                  & $\gamma$          & 0.9300        & Size Distribution\tnote{$\dagger$}                          \\
    \midrule
    Treatment     & $\psi_0^{(0)}$    & $-$3.4144     & Estimates from Regression (\ref{eq:poolols_biological})     \\
                  & $\psi_1^{(0)}$    & $-$0.3636     &                                                             \\
                  & $\psi_0^{(1)}$    & $-$4.3748     & Estimates from Regression (\ref{eq:poolols_others})         \\
                  & $\psi_1^{(1)}$    & $-$0.3288     &                                                             \\
                  & $k_E$             & 4.6000        & Clean Firms: Fixed Cost/Output Ratio (2.5\%)                \\
                  & $\xi$             & 0.2300        & Clean Technology Adoption Rate                              \\
    \midrule
    Distortions   & $\phi_0$          & 1.15          & Average Value Added Tax Rate(13\%)                          \\
                  & $\phi_1$          & $-$0.03       & Elasticity of Average Product to TFP Eq. (\ref{eq:avgl})\tnote{$\dagger$}    \\%Relative Distortions Equation (\ref{eq:avgl})\tnote{$\dagger$}   \\
    Preference    & $\beta$           & 0.8750        & Capital/output Ratio (1.65)                                 \\
    \midrule
    Productivity  & $\mu_z$           & $-$2.4567     & Size Distribution\tnote{$\dagger$}                          \\
                  & $\sigma_z$        & 4.0020        &                                                             \\
                  & $z'_{max}$        & 24855         &                                                             \\
                  & $g_{max}$         & 0.00048       &                                                             \\
                  & $\mu$             & 0.20          & Fraction of Firms in the Polluting Sector                 \\
    \bottomrule
\end{tabular}
\begin{tablenotes}
     \footnotesize{
     \item[$\dagger$]
     Note: The parameters are jointly calibrated.}
\end{tablenotes}
\label{tab:calibration}
\end{threeparttable}
\end{table}

\textit{Discussions.---}Given the calibrated values of the parameters, our model matches well the key aspects of the Chinese economy at both the aggregate and firm levels. Figure \ref{fig:fitness} plots the distributions of the fractions (left panel) and employment shares (right panel) of firms with different sizes for the whole manufacturing sector in the model and in the data.\footnote{Since the distributions of managerial talent are the same in the polluting and non-polluting sectors, and the calibrated value of  $k_E$ is not too large, the firm size distributions for the two sectors in the model are close to each other, which is consistent with data patterns in Figure \ref{fig:es}.} Overall, the model matches the two distributions well. The mean and median of the firm size distribution 53.74 and 19.56, which are not directly targeted in the calibration, match their empirical counterparts of 52.19 and 20 respectively, suggesting that the top managers captures well the upper tail of the firm size distribution.

%\textit{Discussion.}---The calibrated model matches the capital share, capital/output ratio, ratio of average clean equipment cost to average output value for firms using clean technology, proportion of firms adopting the clean technology. %The implied discount rate $\beta$ is less than the values commonly used in the literature. The reason is that we calibrate our model to the steady state as opposed to the balanced growth path. If we assume that the household has log-utility function and the secular growth rate equals to 8\%, the counterpart of the discount rate in this situation is equal to 0.95. We choose to calibrate the model to the steady state because we do not have to make additional assumptions on the functional form of the utility function. Nevertheless, all of the qualitative and quantitative results in this paper hold in the balanced growth path calibration.
%The calibrated value of $\xi$ should be interpreted as the implied ``tax'' rate for using the dirty technology, which combines the effect of many disparate and overlapping policies and adds up to 20.5\% of a firm's annual output value.
%\footnote{While empirical counterpart of the value is difficult to find, the number lies within the range of percentage of plants inspected reported in \citet{BeckerHenderson:2000}. In particular, \citet{BeckerHenderson:2000} report the percentage of firms inspected in four industries in the U.S: Plastics, Wood Furniture, Industrial Organic Chemicals and Metal Containers. The numbers are respectively 2.4\%, 6.8\%, 20\% and 27\%.}

%Figure \ref{fig:fitness} plots the firm size (left panel) and employment share distributions (right panel) in the model and in the data. We plot the match for the whole manufacturing sector. However, since the ex ante distributions of productivity are the same in both the polluting and non-polluting sectors, and that the calibrated level of $k_E$ is small, the matches of the model for the polluting and non-polluting sectors look very similar to those in Figure \ref{fig:fitness}.

%Overall, the model matches the two distributions well given that there are five degrees of freedom. The mean (53.74) and median (19.56) of the firm size distribution, which are not directly targeted in the calibration, match their empirical counterparts of 52.19 and 20 respectively. This suggests that the atom $(z'_{max}, g_{max})$ captures well the upper tail of the firm size distribution.

\begin{figure}[t]
    \begin{center}
    \includegraphics[width=0.45\textwidth]{./Figures/benchfit_fs.eps}
    \includegraphics[width=0.45\textwidth]{./Figures/benchfit_es.eps}
    \caption{Firm Size Distribution: Model versus Data}
    \floatfoot{Note: The firm size and employment distributions of the whole manufacturing sector are reported.}
    \label{fig:fitness}
    \end{center}
\end{figure}

The calibrated value of the span-of-control parameter $\gamma$, which determines the firm-level returns to scale, lies close to the upper end of the range identified by the literature.\footnote{The values of firm-level returns to scale used in the macro literature range from 0.80 [\citet{Guneretal:2008}] to 0.95 [\citet{Bartelsmanetal:2013}]. Estimates from micro studies differ across industries. For example, \citet{OlleyPakes:1996} estimate the value to be between 0.8 and 0.9 for the U.S. telecommunications equipment industry, while the estimates from \citet{Bailyetal:1992} point towards close to constant returns to scale for many manufacturing industries in the U.S.. See also the discussions in \citet{AtkesonKehoe:2005}.} A relatively high value of $\gamma$ is needed to match the employment share of large firms (in particular those with 400+ employees) given the existence of correlated distortions, because we need high returns to scale so that the right amount of resources will be concentrated among firms with high TFP. However, if $\gamma$ is too large, the high demand for factors from the large firms would push up the factor prices, and therefore drive many small firms with low TFP out of the market through endogenous occupation choices. This would jeopardize our model's fit of the fraction of small firms to the data. Our choice of $\gamma =$ 0.93 is a compromise of the two countervailing forces.

%Specifically,  To match the observed employment shares among large firms in the presence of correlated distortions,  %\footnote{Models where these two forces are not antagonistic to each other usually have much better fit. For instance, \citet{Guneretal:2008} study the whole U.S. business sector, which has a narrower employment span and lighter employment concentration. In particular, the largest group they are targeting is firms with more than 100 employees. On the contrary, the largest group we are targeting is 400+ employees, which is significantly larger. In another study, \citet{AdamopoulosRestuccia:2014} assume away the selection mechanism in the model, which, put differently, mutes the general equilibrium feedback through wages. This relaxes the restriction on average talents considerably.}

%The calibrated value of returns to scale $\gamma$ warrants more explanation. The parameter value lies within the empirically estimated range, though close to the upper bound.\footnote{The values previously used in the macro literature range from 0.85 [\citet{AtkesonKehoe:2005}] at the lower end to 0.95 [\citet{Bartelsmanetal:2013}] at the upper end, although in $\gamma$ is not the only source of decreasing returns to scale in [\citet{Bartelsmanetal:2013}]. Please see also the discussion on page 319 of \citet{Bartelsmanetal:2013}. Estimations from micro-level data yield similar results. For example, \citet{OlleyPakes:1996} estimate the value to be between 0.8 and 0.9 for the U.S. telecommunications equipment industry, depending on the particular econometric specification.} The challenges of calibrating the model to simultaneously match the two aspects of the firm size distribution are as follows. To create the concentration of employment among large firms, we need entrepreneurs with very high productivity to face low wages and experience high returns to scale ($\gamma$). Due to the standard property of the \citet{Lucas:1978b} model, low prevailing wage implies that the profits of small firms are also low (Lemma 2 in Online Appendix G). However, higher $\gamma$ raises factor demand from large firms, which pushes up factor prices and drives out small firms with low profits. The latter jeopardizes the fit of the number of small firms in the model. The performance of our model is thus a compromise of these two forces.\footnote{Models where these two forces are not antagonistic to each other usually have much better fit. For instance, \citet{Guneretal:2008} study the whole U.S. business sector, which has a narrower employment span and lighter employment concentration. In particular, the largest group they are targeting is firms with more than 100 employees. On the contrary, the largest group we are targeting is 400+ employees, which is significantly larger. In another study, \citet{AdamopoulosRestuccia:2014} assume away the selection mechanism in the model, which, put differently, mutes the general equilibrium feedback through wages. This relaxes the restriction on average talents considerably.}

%The identification assumption of our benchmark calibration is that {given} taxes $\tau_z$, the talent distribution is identified by the size distribution in the data. Another commonly used calibration strategy in the literature takes the United States as an undistorted economy (which means $\tau_z = 0$ in our model) and calibrates $G(z)$ by matching the size distribution from the tax-free economy to the U.S. data. Taxes are then introduced such that certain moments of the size distribution of the country in interest are matched.\footnote{See, for example, \citet{Guneretal:2008}, \citet{Bartelsmanetal:2013}, \citet{AdamopoulosRestuccia:2014}, and \citet{BentoRestuccia:2016}, among others.} If we calibrate our model in this way, the underlying assumption would be that the talent distribution of the entrepreneurs in China is the same as that in the United States and that all the difference between the size distributions of China and the United States is due to taxes.\footnote{The evidence regarding this point is mixed. See Figure 2 in \citet{BloomVanReenen:2010}.} In our opinion, both strategies have their strengths and weaknesses, and face different data limitations. The quantitative results of our study are largely driven by the size and shape of $\tau_z$. Therefore, as long as the alternative calibrations imply similar tax schemes to that used in our benchmark, the quantitative aspects of our results would continue to hold.\footnote{In an earlier version of this study where endogenous treatment technology choice is not explicitly modeled, we find that this is indeed the case.} We choose to calibrate our model directly to the Chinese economy directly because better empirical evidence (Section \rom{2}.B) is available.

\section{Quantitative Exercises}

In the section, we use our calibrated model to evaluate the effects of alternative policies on aggregate output and pollution. We conduct two sets of counterfactual experiments.  In Experiment (i), we follow the \emph{indirect} approach in the misallocation literature and remove correlated distortions from both sectors by changing $\tau_z$ to $0$.\footnote{In Online Appendix I, we build and calibrate a similar model in which the final consumption is a CES aggregation of the products from two sectors, and use the model to evaluate the impact of removing the correlated distortions from \emph{the polluting sector only}. The main difference between this experiment and Experiment (i) in the main text is that this one induces large reallocation of factors from the non-polluting to the polluting sector. As a result, the reduction in aggregate pollution from removing distortions will be smaller. } This is meant to capture the overall effects of a variety of policies and institutions that reallocate resources from high to low TFP firms. To isolate the importance of the {progressiveness} of distortions, later we replace the progressive taxes with flat taxes by setting $\phi_1=0$, and change $\phi_0$ to keep the total implicit tax revenue constant. In Experiment (ii), we tighten the environmental regulations by increasing $\xi$ to the extent that the fraction of firms using the clean technology is the same as in Experiment (i). We then compare the results from these two experiments, and illustrate the key mechanisms that drive these different results.
%We use the calibrated model as a framework for understanding the effects of the firm size distribution on industrial pollution. We conduct two experiments. In experiment (i), we eliminate all distortions by setting $\tau_z = 0$. This experiment could be interpreted as reductions in inter-regional trade barriers, improvements in transportation infrastructure, decreases in tax burdens, and so on.\footnote{In the main text, we do not study asymmetric changes of $\tau_z$ across sectors, because we feel that it is unlikely that for instance an improvement in infrastructure benefits only the polluting sector. This also explains the reason we model the goods produced by the two sectors are perfect substitutes. However, for the case of asymmetric changes, the assumption of perfect substitutes would lead to overly elastic response in sectoral output. For such scenarios, a moderate elasticity of substitution is needed. We report the results from reducing only the distortions in the polluting sector in a model with CES aggregation (and hence price adjustment) in Online Appendix I. As expected, the main mechanism in our paper remains intact.} Since we are following the \textit{indirect} approach, we are not able to map the size of decrease in $\tau_z$ to observable policy changes. %empirical evidence of the size of the decrease in $\tau_z$ caused by a reduction in some observable distortions of a certain degree is lacking.
%However, as an approximation, the effects of the policy can be assessed by examining the changes in average firm size across steady states, as is done by for example \citet{Guneretal:2008} and \citet{BentoRestuccia:2016}. In experiment (ii), we increase regulation $\xi$ such that the proportion of firms using the clean technology reaches the same level as in experiment (i). In this experiment, we aim to approximate the current environmental policy that punishes firms for using the dirty technology. We then contrast the results of the two experiments to illustrate the different mechanisms and effects of these two types of policies.

%Since along most dimensions, the response from the two sectors are very similar, for each experiment, we will first focus on the polluting sector alone. We then turn to the non-polluting sector by analyzing where its response differs. The overall impact on the whole manufacturing sector is the weighted average of the changes in the two sectors.

\subsection{Counterfactual Experiments}

%\begin{table}[t]
%\footnotesize
%\centering
%\begin{threeparttable}
%\caption{The Effects of Distortions and Regulations}
%\begin{tabular}{p{125pt} >{\centering\arraybackslash}p{75pt} >{\centering\arraybackslash}p{75pt} >{\centering\arraybackslash}p{75pt}}
%    \hline \hline
%    Statistics                      & Benchmark             & (i)                   & (ii)    \\
%    \midrule
%    Aggregate Output                & 100.00                & 129.72                & 100.12  \\
%    Capital                         & 100.00                & 161.25                & 100.14  \\
%    Consumption                     & 100.00                & 123.45                & 100.11  \\
%    Output per Worker (Wage)        & 100.00                & 128.49                & 99.97   \\
%    Output per Firm                 & 100.00                & 298.78                & 109.76  \\
%    Average Talent                  & 100.00                & 224.67                & 109.49  \\
%%    TFP                             & 100.00                & 102.00                & 100.14  \\
%    \midrule
%    Number of Firms                 & 100.00                & 43.42                 & 91.22   \\
%    Mean Size                       & 59.27                 & 137.81                & 65.07   \\
%    Median Size                     & 22.95                 & 41.83                 & 26.72   \\
%    \midrule
%    Aggregate Pollution             & 100.00                & 78.95                 & 90.75 \\
%    Average Intensity               & 100.00                & 60.86                 & 90.65 \\
%    Clean Share                     & 57.40                 & 85.29                 & 85.15  \\
%    Monitoring                      & 20.50                 & 20.50                 & 32.50  \\
%    \bottomrule
%\end{tabular}
%\begin{tablenotes}
%     \footnotesize{
%     \item[$\dagger$]
%     Note: All values are in percentage points except mean and median size, which are the absolute numbers of workers.}
%\end{tablenotes}
%\label{tab:aggregates}
%\end{threeparttable}
%\end{table}

\textit{Removing the Correlated Distortions.}---In Experiment (i), we remove correlated distortions from both sectors by setting $\tau_z = 0$ for all $z$. Column (i) of Table \ref{tab:aggregates} summarizes the results. Overall, removing correlated distortions from both sectors increases aggregate output by about 30\% in both sectors (scale effect), while lowering the pollution intensity of the polluting sector by 42\% (technique effect). Since both sectors share the same distributions of firm-level productivity and distortions, removing correlated distortions induces little reallocation across sectors (composition effect). Therefore, the technique effect from eliminating correlated distortions dominates the scale and composition effects, and aggregate pollution drops by 23\%.\footnote{The decrease in aggregate pollution is consistent with the prediction from Proposition \ref{prop:agge}, given the calibrated values for $\phi_1$, $\gamma$ and the estimated relationship between pollution intensity and firm size.}

%\textit{Removing All Distortions.}---We begin with the effects on the resource allocation in the polluting sector. The core mechanism that generates the results of experiment (i) is the change in size distributions driven by the {general equilibrium wage effect}. Since the tax scheme $\tau_z$ is assumed to be size-dependent, which is larger for more productive firms, the market share of these firms is restrained in the benchmark economy. The elimination of $\tau_z$ removes these constraints. As a result, the previously suppressed factor demand increases considerably. In column (i) of Table \ref{tab:aggregates}, this shows up as a 61\% increase in aggregate capital and a 60\% increase in wages. The size dependency of $\tau_z$ also implies that the situation of small unproductive firms improves to a lesser extent than that of large productive ones. Many small unproductive firms that previously survived because of the low prevailing wage now lose their profit margins. The owners of these firms therefore find it more profitable to work for more productive firms. This {selection} mechanism explains the 121\% increase in the average productivity of firms and 132\% increase in the mean firm size. Furthermore, production is also more concentrated in firms with high productivity {among} the remaining firms. We define the \textit{extensive} margin as the selection of firms into production and the \textit{intensive} margin as the production distribution among the active firms. The first two rows of Table \ref{tab:talentdist}, which report the output share of firms with productivity in different quintiles, show the intensive margin.

\begin{table}[t]
\footnotesize
\centering
\begin{threeparttable}
\caption{The Effects of Correlated Distortions and Environmental Regulations}
%\begin{tabular}{lccccccc}%{p{85pt}>{\centering\arraybackslash}p{50pt}>{\centering\arraybackslash}p{50pt}>{\centering\arraybackslash}p{40pt}}%>{\centering\arraybackslash}p{35pt}}%{lccc}
\begin{tabular}{p{90pt} >{\centering\arraybackslash}p{45pt} >{\centering\arraybackslash}p{45pt}>{\centering\arraybackslash}p{40pt} >{\centering\arraybackslash}p{5pt} >{\centering\arraybackslash}p{45pt} >{\centering\arraybackslash}p{45pt} >{\centering\arraybackslash}p{40pt}}
    \hline \hline
                         & \multicolumn{3}{c}{Polluting}    & & \multicolumn{3}{c}{Non-polluting} \\
    \cmidrule{2-4} \cmidrule{6-8}
    Statistics           & Benchmark & (i)      & (ii)      & & Benchmark     & (i)    & (ii) \\
    \midrule
    Output               & 100.00    & 131.16   & 98.99     & & 100.00        & 129.62 & 100.28 \\
    Capital              & 100.00    & 163.06   & 99.00     & & 100.00        & 161.26 & 100.28 \\
    Consumption\tnote{a} & 100.00    & 123.63   & 100.02    & & 100.00        & 123.63 & 100.02 \\
    Wage\tnote{a}        & 100.00    & 160.00   & 99.96     & & 100.00        & 160.00 &  99.96 \\
    Output per Worker    & 100.00    & 128.25   & 100.15    & & 100.00        & 128.60 &  99.95 \\
    Output per Firm      & 100.00    & 297.62   & 110.17    & & 100.00        & 311.85 & 100.28 \\
    Average Productivity & 100.00    & 221.24   & 111.11    & & 100.00        & 235.39 & 100.00 \\
    \% in Output         & 19.73     & 19.91    & 19.52     & &  80.27        & 80.09  &  80.48 \\
    \midrule
    \# of Firms          & 100.00    & 44.07    & 89.86     & & 100.00        & 41.56  & 100.00 \\
    Mean Size            & 59.98     & 139.19   & 65.98     & & 52.18         & 126.53 &  52.35 \\
    Median Size          & 23.67     & 43.09    & 27.88     & & 18.61         & 34.31  & 18.67  \\
    \midrule
    Pollution            & 100       & 76.67    & 85.82     \\
    Intensity            & 100       & 58.46    & 86.73    \\
%    Pollution            & 100       & 81.66    & 90.60     \\
%    Intensity            & 100       & 62.27    & 91.56     \\
    Clean Share          & 57.77     & 85.61    & 85.10     \\
    Regulation           & 23.00     & 23.00    & 35.50     \\
    \bottomrule
\end{tabular}
\begin{tablenotes}
     \footnotesize{
     \item[$\dagger$]
     Note: All values are percentages except for mean size and median size, which are the numbers of workers.
     \item[a]
     Consumption and wage are not sector specific.}
\end{tablenotes}
\label{tab:aggregates}
\end{threeparttable}
\end{table}

\begin{table}[t]
\footnotesize
\centering
\begin{threeparttable}
\caption{Resource Allocation on the Intensive Margin}
\begin{tabular}{p{65pt} >{\centering\arraybackslash}p{45pt} >{\centering\arraybackslash}p{45pt} >{\centering\arraybackslash}p{45pt} >{\centering\arraybackslash}p{45pt} >{\centering\arraybackslash}p{45pt}}
    \hline \hline
    Economy           & $\text{QU}_1$ & $\text{QU}_2$ & $\text{QU}_3$ & $\text{QU}_4$ & $\text{QU}_5$ \\
    \midrule
    \multicolumn{3}{l}{\textbf{Polluting Sector:}} \\
    \ \ \ Benchmark   & 2.79          & 4.26          & 7.45          & 16.81         & 68.70          \\
    \ \ \ Case (i)    & 1.53          & 2.89          & 6.46          & 18.25         & 70.87          \\
    \ \ \ Case (ii)   & 3.02          & 4.63          & 8.01          & 17.79         & 66.55          \\
    \midrule
    \multicolumn{3}{l}{\textbf{Non-polluting Sector:}} \\
    \ \ \ Benchmark   & 2.42          & 3.78          & 6.65          & 15.39         & 71.75          \\
    \ \ \ Case (i)    & 1.30          & 2.49          & 5.68          & 16.97         & 73.57          \\
    \ \ \ Case (ii)   & 2.42          & 3.78          & 6.65          & 15.39         & 71.75          \\
    \bottomrule
\end{tabular}
\begin{tablenotes}
     \footnotesize{
     \item[$\dagger$]
     Note: $\text{QU}_1$ to $\text{QU}_5$ represent the first to fifth quintiles, respectively.}
\end{tablenotes}
\label{tab:talentdist}
\end{threeparttable}
\end{table}

Removing correlated distortions causes large reallocation of production factors across firms, and leads to improved allocation along both the extensive and intensive margins. The \textit{extensive} margin is defined as the selection of firms into production, and the \textit{intensive} margin as the production distribution among the active firms. Specifically, since the distortions $\tau_z$ are higher for high TFP firms in the benchmark economy, a large share of the production factors would flow to these firms after the removal of distortions (intensive margin). The increased labor demand from these firms would drive up the equilibrium wage by 60\%, which would in turn drive many unproductive firms out of the market through the endogenous occupation choices (extensive margin). Due to the changes along the extensive margin, the total number of firms is cut by more than half, and the mean firm size more than doubles. Along the intensive margin, as we see from Table \ref{tab:talentdist}, surviving firms with TFP in the top two quintiles expand at the expense of those with lower TFP. The two panels on the left of Figure \ref{fig:compare_size} show the changes in firm size distributions following the removal of the correlated distortions.
%Firms in the top two groups expand considerably at the expense of firms in the bottom three groups. Therefore, the elimination of $\tau_z$ improves the resource allocation on both the extensive and the intensive margins. For the polluting sector, the overall changes in the size and employment distributions can be seen in the two left-hand panels of Figure \ref{fig:compare_size}.
\begin{figure}[t]
    \begin{center}
    \includegraphics[width=0.45\textwidth]{./Figures/bench_notax_fs.eps}
    \includegraphics[width=0.45\textwidth]{./Figures/bench_reg_fs.eps} \\
    \includegraphics[width=0.45\textwidth]{./Figures/bench_notax_es.eps}
    \includegraphics[width=0.45\textwidth]{./Figures/bench_reg_es.eps}
    \caption{The Effects of Distortions and Regulations on Firm Size Distributions}
    \floatfoot{Note: The distributions of the polluting sector are reported. }
    \label{fig:compare_size}
    \end{center}
\end{figure}

%By defining aggregate $\text{TFP} = {Y}/{(K^{\alpha} N^{1-\alpha})^{1-\gamma}}$,
%%\begin{equation*}
%%    \text{TFP} = \frac{Y}{(K^{\alpha} N^{1-\alpha})^{1-\gamma}},
%%\end{equation*}
%which is the Solow residual following standard growth accounting studies [\citet{HallJones:1999}], we find that the size distributions in models {with} firm selection exert a limited influence over TFP. This finding is consistent with that in \citet{Guneretal:2008}.

The large increase in aggregate output is caused by both an improved allocation of production factors across firms, and a large increase in capital accumulation by about 60\% due to decreased average tax rate from 13\% to 0\%. The increase in capital accumulation plays a much larger role than improved allocation of factors in the increase in aggregate output. Our quantitative exercises in Section \rom{4}.B below illustrate this point further. The large decline in average pollution intensity is also caused by two factors: the improved allocation of production factors, and increased adoption of the clean technology. After the removal of correlated distortions, more production factors move to large productive firms which also have lower pollution intensity. This reallocation lowers the average pollution intensity. Meanwhile, as we discuss in Section \rom{3}.D, correlated distortions lower the elasticity of firm profits to firm TFP $z$, and therefore reduce their incentives to adopt the clean technology. Removing correlated distortions would do exactly the opposite and encourage the adoption of clean technology.

%Now, we examine the effects on pollution. Although aggregate output increases by 31\%, because average pollution intensity decreases by a larger extent of 38\%, aggregate pollution {decreases} by 19\%. In other words, quantitatively, the technique effect dominates the scale effect. The decline in average intensity comes both from the production stage and from the treatment stage. In both stages, changes in the size distribution play a key role. Since production in the no-distortions economy shows a higher degree of concentration in large firms, the fact that the two {within-group} elasticities $\psi_1^{(0)}$ and $\psi_1^{(1)}$ are negative implies a decrease in pollution intensity. %As discussed in Section \rom{1}.C, this could be because larger firms use more productive technologies which just happen to be environmentally friendly. Given that the focus of this paper is at the treatment stage, we capture this relationship in a reduced-form way and we leave a the full-fledged discussion for future research.
%The effect of the size distribution on a firm's choice of end-of-pipe treatment technology works exactly as described in Result \ref{prop:friction}. The elimination of $\tau_z$ increases firms' profits significantly, which strengthens the economic incentive to adopt the clean technology. %\footnote{If we treat international trade costs as one particular example of $\tau_z$, our findings are consistent with those in \citet{Bustos:2011}. More specifically, she found empirically that reduction in tariffs leads to more export revenues which induces upgrade of production technology.} %It is important to bear in mind that both the elimination of $\tau_z$ itself and the subsequent {decrease} of wages contribute to the strengthening of the economic incentive.
%Importantly, by setting the $\psi_1$ in Result \ref{prop:agge} to $\psi_1^{(1)}$, the upper bound of $\hat{\phi}_1$ under our current calibration is $-$0.06. With our calibrated $\phi_1 = -$0.03, which is higher than $\hat{\phi}_1$, the qualitative prediction from Result \ref{prop:agge} is consistent with the quantitative results.

To evaluate the relative contributions of the improved allocation of factors and improved adoption of clean technologies, we consider a hypothetical economy that is identical to our benchmark economy, except that the clean technology shows no improvement in abatement efficiency over the dirty technology, that is, $\psi_0^{(1)} = \psi_0^{(0)}$ and $\psi_1^{(1)} = \psi_1^{(0)}$. First, we remove correlated distortions from this hypothetical economy, which reveals the importance of the improved allocation of factors. We then re-introduce the differences between clean and dirty technologies to the hypothetical economy, so that the resulting equilibrium is exactly the same as that in Experiment (i). This further reveals the importance of the improved adoption of clean technologies. We find that the improved adoption of clean technologies account for 48\% of the decrease in average intensity.

%To evaluate the relative contribution of the reduction in the production and treatment stages, consider a hypothetical world where the clean and dirty technologies are the same, meaning that $\psi_0^{(0)} = \psi_0^{(1)}$ and $\psi_1^{(0)} = \psi_1^{(1)}$. Removing distortions in this economy reduces the aggregate pollution and average intensity by 20\% and 39\%. Restoring the technic specifications of the clean technology further reduces the pollution level and intensity by 17\% and 13\%. Hence on average, about 46\% and 25\% of the decrease in aggregate pollution and average intensity occur in the treatment stage.\footnote{One caveat here is that because we do not model explicitly the technology adoption decision of the firms during the \textit{production} stage due to data limitation, we have implicitly assumed that the relationship between emission and firm size conditional on treatment technology estimated from the data can be extrapolated to other scenarios. In the context of our experiments, this means that the relationships in the world with distortions provide reasonable approximations to those in a world without distortions. As long as this is the case, modeling the technology choice decisions in the production stage explicitly or not would not change the quantitative results.}

Finally, the polluting and non-polluting sectors respond in similar ways to the removal of correlated distortions, and little reallocation is induced across sectors. Recall that the distributions of managerial talent and distortions are the same across these two sectors, and the only material difference between these two sectors is the presence of the fixed adoption cost of clean technology $k_E$ and environmental regulations. Since the calibrated value of $k_E$ is not too large, the differences in the reaction of these two sectors to the removal of distortions are rather limited.

One notable difference is that the mean firm size is somewhat larger in the polluting sector, because the environmental regulations work as an additional selection mechanism. The interaction between the correlated distortions and environmental regulations leads to further efficiency losses in the polluting sector, because average firm size and hence the effective distortions increase. As a result, compared to the non-polluting sector, the removal of correlated distortions leads to a 1.5 percentage points larger increase in output in the polluting sector.

%The non-polluting sector responds to the removal of $\tau_z$ in more or less the same way as the polluting sector. Recall that the only material difference between the polluting and non-polluting sector is the presence of fixed cost $k_E$ and environmental regulations. Hence any difference observed between the two sectors has to stem from how the interaction of these two features affects the decisions of firms. There are two notable differences. First is that the efficiency loss caused by $\tau_z$ is smaller in the non-polluting sector. This can be seen from the fact that the output increase in the polluting sector is 1.5 percentage points smaller in the non-polluting sector. Notice that on average, firms are larger in the polluting sector, because very small firms cannot afford the cost of clean technology. This combines with the size-dependency of $\tau_z$ suggests that on average, the polluting sector is taxed heavier under the same tax scheme, leading to higher efficiency loss. This demonstrates an explicit channel of how environmental regulations amplifies existing distortions in the economy. Second is that although the polluting sector is more selective on the extensive margin, the output per firm is in fact lower. This is because that although the productivity of the very small firms are extremely low, by operating at very small scale, the marginal productivity of labor is in fact higher than other active firms. Leaving them off the market hence reduces the overall efficiency of how the economy uses production factor. Further, Table \ref{tab:talentdist} shows that the additional selection also worsens resource allocation along the intensive margin, which also lowers output per firm.

\textit{Tightening Environmental Regulations.}---In Experiment (ii), we increase environmental penalties $\xi$ to the extent that the fraction of firms using the clean technology increases to the same 56\% as in Experiment (i). The results are shown in Column (ii) of Table \ref{tab:aggregates}. Overall, in the polluting sector, the increase in $\xi$ leads to small decreases in aggregate output, capital stock and equilibrium wage, a sizable change in firm size distribution, and substantial decreases in aggregate pollution and pollution intenisty. On the other hand, the increase in $\xi$ has very limited spillover on both the aggregate outcomes and firm size distribution to the non-polluting sector.

%\textit{Tightening Environmental Regulations.}---The tightening of environmental regulations affects the decisions of firms {directly} through the requirement to adopt technology and {indirectly} through the general equilibrium wage feedback. Unlike in experiment (i), these two effects affect the size and employment distributions at the equilibrium by little, as shown in the two right-hand panels in Figure \ref{fig:compare_size}. There are two reasons behind this. First, large firms that have already adopted the clean technology in the benchmark case are not directly affected by changes in the policy. Second, the installation costs of the clean technology in our benchmark calibration are small. As a result, they do not divert a significant proportion of firms' resources from productive use and hence hardly affect the optimal operating scale of firms. Therefore, in column (ii) of the top panel of Table \ref{tab:aggregates}, the macro aggregates barely change compared with the benchmark case.

The increase in $\xi$ affects the resource allocation in the polluting sector along both the extensive and intensive margins. The most notable changes come along the extensive margin. In our model as well as in the data, it is the small unproductive firms that choose the dirty technology. Therefore, an increase in environmental penalties would mostly fall on small unproductive firms and lower their profits. This would drive a substantial fraction of small firms out of the market through the endogenous occupation choices, and lead to a sizable increase in average firm size. Meanwhile, labor supply increases as the managers of these exiting firms now choose to be workers, which suppresses the equilibrium wage. These changes along the extensive margin are efficiency-improving in the presence of correlated distortions, since the direction of the factor reallocation is opposite to that induced by the correlated distortions.

%However, despite the small {decrease} in wages (0.04\%), selection on the extensive margin {increases} the average size and productivity of active firms. The underlying mechanism here is that an increase in environmental regulations decreases the expected returns from being an entrepreneur, which drives out the least productive firms that cannot afford to install the clean technology. %\footnote{This prediction matches the policy practice in China. For example, during 2004 to 2008, the emissions of major air pollutants as well as industrial production declined significantly. The reductions in per-unit GDP emissions for these pollutants were 35\% for sulfur dioxide, 29\% for black carbon, and 31\% for carbon monoxide [\citet{Linetal:2014pnas}]. During that period, 34 million kW of coal-burning electricity-generating facilities were shut down, which amounts to 6.18\% of total electric production in 2013 (\textit{National Development and Reform Commission} [2009] Decree 4).}
%These household members then choose to become workers, which increases labor supply and suppresses equilibrium wage rates. The remaining large firms benefit from the reduction in wage rates and expand their operating scale, which explains the increases in size and productivity. In Figure \ref{fig:compare_size}, this is graphically reflected as contraction of the smallest group in the firm size distribution and expansion in the other four groups.

While small firms account for a large fraction of firms, they account for only a small fraction of production factors, which implies that the total amount of factors affected by the extensive changes is small. In addition, the polluting sector only account for 20\% of production factors in the benchmark economy. Therefore, the induced decline in equilibrium wage is very small (0.04\%). In addition, our calibrated value of the adoption cost of clean technology $k_E$ is not too large. Therefore, the impact on surviving firms in the polluting sector is also limited, which can be seen in Table \ref{tab:talentdist}. Despite this, the allocation of factors along the intensive margin worsens, in the sense that the share of factors used by the most productive group decreases, because more distorted productive firms benefit less from the wage decline. This offsets the improvement in efficiency from the reallocation along the extensive margin.

%The firms in the four expansion groups are not affected equally, however, as shown in row (ii) in Table \ref{tab:talentdist}. As experiment (i) shows, the most efficient way of allocating talents is to shift production to the most productive firms, increasing the share of output accounted for by firms with productivity in the top quintile. However, row (ii) shows the opposite. Compared with the benchmark case, the proportion of production accounted for by the lower quintiles {increases}, while that of the top quintile {decreases}. Therefore, although strengthening regulation improves the resource allocation on the {extensive} margin, the benefit is countered by exactly the same two channels documented above, namely the amplification of distortions and the loss in efficiency along the intensive margin. %because size-dependent $\tau_z$ limits the extent to which declining wages can benefit firms in the top quintile. %Nevertheless, both these effects are small here because in our benchmark calibration $k_E$ is small.

Since the total amount of factors involved in reallocation along the two margins is small, most of the decrease in average pollution intensity comes from the increased adoption of the clean technology. We repeat the same decomposition exercise as we did in Experiment (i), and find that 94\% and 96\% of the reductions in aggregate pollution and average intensity, respectively, stem from the increased adoption of the clean technology. Since the output of the polluting sector only decreases only slightly in this experiment, the decreases in aggregate pollution and intensity are quantitatively similar at around 14\%.

%Since aggregate output only decreases slightly in this experiment, the decreases in aggregate pollution and intensity are quantitatively similar (i.e., around 10\%). Moreover, because the size and employment distributions change little, most of the decrease comes from the treatment stage. If we repeat the decomposition exercise we just did for experiment (i), 88\% and 91\% of the reductions in aggregate pollution and average intensity stem from the adoption of the clean technology.

The non-polluting sector is indirectly affected in this experiment by the general equilibrium reponse in wage. Since the induced change in equilibrium wage is very small, the increase in $\xi$ has very small effects on both the aggregate outcomes and firm size distribution, even when the products of the two sectors are perfect substitutes.

%The non-polluting sector is barely affected in this experiment, because the only difference in environment it faces is a tiny drop in wage rate. In addition, the distributions of the polluting versus non-polluting sector in Table \ref{tab:talentdist} provide further evidence showing that environmental regulation reduces the efficiency along the intensive margin. The results suggest that when the size of the polluting sector is small, even with perfect substitutes between the goods and hence infinity elasticity of cross-sector substitution, the side effects are negligible.

\textit{Comparing the Two Experiments.}---Both of the above experiments cause the reallocation of factors across firms, but in different ways. Removing the correlated distortions from both sectors improve resource allocation along both the extensive and intensive margins, which push the economy closer to the production possibility frontiers. In contrast, while tightening environmental regulations leads to tougher selection of firms, which pushes the extensive margin closer to its first-best level, the resource allocation across firms along the intensive margin worsens.\footnote{In reality, tightening environmental regulations may cause other undesirable outcomes. For example, extra resources are needed to enforce tightening regulations, and more rent-seeking activities may possibly be induced by the regulations. Due to data limitations, we leave a complete welfare analysis of tightening environmental regulations to future research.} As a result, although the fraction of firms using clean technology is set to be the same in the two experiments, the reduction of aggregate pollution intensity is larger in Experiment (i), because  the larger (and cleaner) firms take a much larger market share compared to Experiment (ii).

%\textit{Comparing the Two Policies.}---These two experiments show that both removing distortions and intensifying regulations affect the resource allocation, but in different ways. Naturally, eliminating the distortions improve resource allocation along both the extensive and intensive margin, since it moves the economy to its first best. On the contrary, although environmental regulation intensifies the selection of firms, which pushes the threshold closer to its level in the first best equilibrium, the average distortions in the economy get amplified the resource allocation along the intensive margin worsens.\footnote{In reality, tightening environmental regulations may cause other undesirable outcomes. For example, extra resources are needed to enforce tightening regulations, and more rent-seeking activities may possibly be induced by the regulations. Due to data limitations, we leave a complete welfare analysis of tightening environmental regulations to future research. }As a result, although in both experiments the share of firms using clean technology is the same, the reduction of aggregate pollution during the treatment stage is larger in experiment (i) because firms adopting clean technology takes a larger market share.

%In particular, removing distortions increases labor {demand} from firms, while intensifying regulations increases labor \textit{supply} from household members. Because distortions are size-dependent, large firms benefit more from their removal. On the contrary, an increase in labor supply suppresses equilibrium wages, thereby potentially raising firms' profits. However, the actual extra profits firms earn need to take out the effect of distortions. As before, owing to the size dependency of the distortions, large firms benefit less from the decrease in wages. This explains the reason why the intensive margin improves when distortions are eliminated but worsens when stronger regulations are imposed. %Put differently, distortions shape the effect of environmental policies on different firms. %This finding complements the analysis by \citet{Bustos:2011}, who empirically studies the extent to which the elimination of tariffs---a particular form of size-dependent distortion---influences technology upgrading. The results of our first experiment are consistent with hers. Further, we examine how the economy is affected if the government implements policies that target technology adoption in the presence of size-dependent distortions.

%The lesson we learn from the quantitative exercises is that if resources are devoted to smoothing the frictions in the economy instead of being used to intensify regulations, reductions of pollution in both the production and treatment stage could arise naturally as equilibrium outcomes.
% Several recent studies argued that industrial pollution in China comes from the unanticipated responses of economic agents to different policies and institutional features.\footnote{For instance, \citet{Jia:2014} studies the role of the political incentives and career concerns of provincial governors, \citet{Jiangetal:2014} emphasize differential policy treatments to firms with different ownership rights structures, and \citet{Kahnetal:2015} and \citet{Caietal:2016} estimate the difference in the reduction efforts from provincial governments on upstream and downstream counties along the rivers in response to the pollution reduction mandates imposed by the central government.} In reality, the effects of regulatory policies such as government campaigns are often ineffective. These policies suffer from the challenge in monitoring small firms operating off the radar and the quick rebound of pollution level when those campaigns end. Indeed, our results suggest that policies and institutional features could work to amplify other existing distortions in the economy and removing such distortions may well provide a different path to growth that is more sustainable. At the same time, the elimination of those distortions could also reduce the unanticipated environmental consequences of these policies and institutional features. That said, it could be that reducing economic distortions costs more, meaning that strengthening regulations pays off to a larger degree in the short run.\footnote{Another concern is that if small firms have higher growth rates, the removal of size-dependent distortions could hamper economic growth in the long run. However, the recent study of India's manufacturing sector by \citet{Martinetal:2017} suggests that as in the United States, larger and younger factories grow more quickly and create more jobs than do smaller, older factories. If the pattern is the same with China, then it posits less of a concern to the long-run growth prospect of the Chinese economy.} However, the discussion of the implementation of specific policies is beyond the scope of the current study.

%\textit{Relationship to Trade Models.---}The implication of our model on resource allocation along the intensive margin distinguishes us from many studies in international trade that use the \citet{Melitz:2003} model to study the environmental consequences of trade liberalization. A major difference between the distortions in our model and the trade costs in a standard Melitz model is that exporting is an endogenous choice of firms which brings extra revenues. A productive firm can choose not to pay the trade costs if it decides to stay domestic. As a result, though trade costs are a specific type of distortion that only affect exporting (productive) firms, they are different from the distortions in our model which are imperative.\footnote{The difference is not caused by our use of a \citet{Lucas:1978b} model instead of a \citet{Melitz:2003} model. Rather, it is because distortions in our model are a pure cost, while in the \citet{Melitz:2003} model, firms pay trade costs to access to foreign markets, which bring additional revenues. If instead we model in the \citet{Melitz:2003} model similar ``deadweight-loss'' distortions, we would get similar results. In fact, trade costs that lead to higher average factor product are indeed captured as distortions by our model.}
%
%Removing the distortions in our model is the same as trade liberalization in these models. However, intensified regulations yield different implications on resource allocation in our model comparing to those that arise from the standard Melitz model. The reason is that stronger regulation works as an increase in the entry costs, which foreign markets serve as a shelter to exporting firms. Hence, less productive firms are affected more. This illustrates how domestic distortions are conceptually different from trade costs. We believe that such difference is important because the scenario where regulations are strengthened while keeping the distortions is closely related to environmental policies in practice. In this sense, our findings compliment those in the trade literature by pointing out a different way that domestic distortions could affect the economy.\footnote{As an example, we compare our results with those from \citet{Bustos:2011}. The results of our first experiment are consistent with both the theoretical and empirical results of trade liberalization on technology adoption in her paper. We are further able to examine how the economy is affected if the government implements policies that target technology adoption in the presence of size-dependent distortions.}

%\textit{Partial Equilibrium Interpretations.}--Some readers may be concerned that in reality, reduction of labor demand in one industry does not necessarily cause a decline of wages across the whole economy, thereby challenging the main mechanism of our model. We argue that the general logic carries well onto other model environments. First, what eventually matters in our model is not the wage {per se}, but the profits which are revenue less factor costs. In a partial equilibrium version or a \citet{Melitz:2003}-style version of our model where the wage and demand are both fixed, $\tau_z$ will push up the equilibrium price that the firms could charge. This is because with size-dependent $\tau_z$, the supply from the large productive firms is suppressed, where competition among consumers bids up the equilibrium price. Much of the quantitative results are still maintained in these situations. We choose to work with a general equilibrium Lucas model because it enables us to discuss the changes in output level. In fact, the results we present in the general equilibrium setting are stronger than those in the partial equilibrium counterparts. A decrease in the {average intensity} could well be accompanied by an increase in {aggregate pollution} if the output increases by too much. Second, if the labor markets in different industries are segmented, then a decrease in labor demand will in fact trigger a wage drop. Third, the nature of our comparison is to contrast economies {with} and {without} frictions as a whole, not any particular industry. Therefore, as long as the product market frictions exist at the aggregate level, wages will be {lower} in cases with frictions.

\subsection{Effects of the Progressiveness of the Distortions}
\label{sec:progressiveness}

In Experiment (i), by setting $\tau_z = 0$, we change both the progressiveness and and the average level of firm-level distortions. To isolate the importance of the progressiveness of $\tau_z$, we solve a version of the model where the progressive taxes are replaced with uniform taxes by setting $\phi_1 =$ 0, and change $\phi_0$ to keep the total implicit tax revenue constant.\footnote{This strategy has a long tradition in the public finance and development economics literature. See for example, \citet{Ventura:1999}, \citet{ConesaKrueger:2006}, \citet{Bhattacharyaetal:2013} and \citet{BentoRestuccia:2016}, among others.} %To this end, the experiments resemble those in the taxation literature, where progressive taxes are compared with flat taxes. If we interpret $\tau_z$ literally as a tax, it would be unwise to suggest eliminating the whole tax system on manufacturing sector. This exercise could be interpreted as a counterfactual on policies that remove the size-dependent feature of current taxation policies in China.
Not surprisingly, the implied uniform tax rate $\tau_z =$ 18\% is higher than the average tax rate of 13\% under the progressive tax system. Column (i') in Table \ref{tab:uniform} summarizes the results of this experiment and compares them to those from Experiment (i). A comparison of Column Benchmark and Column (i') reveals the effects of a change in progressiveness of $\tau_z$, while a comparison of Column (i') and (i) highlights the effects of a uniform change in tax rates across firms.

%To further isolate the effect of the firm size distribution, we solve a version of the model where uniform distortions are imposed on all firms in the economy. More specifically, in this exercise, we set values of $\tau_z$ such that the total amount of taxes collected is the same as in the benchmark case with size-dependent $\tau_z$. This experiment reveals the quantitative effect of the size dependency of $\tau_z$.\footnote{To this end, the experiment resembles those in the taxation literature, where progressive taxes are compared with flat taxes. See, for example, \citet{Ventura:1999} and \citet{ConesaKrueger:2006}.} %To this end, the experiments resemble those in the taxation literature, where progressive taxes are compared with flat taxes. If we interpret $\tau_z$ literally as a tax, it would be unwise to suggest eliminating the whole tax system on manufacturing sector. This exercise could be interpreted as a counterfactual on policies that remove the size-dependent feature of current taxation policies in China.
%The implied tax rate $\tau_z =$ 18\% is higher than the average tax rate in the size-dependent case, 13\%. Table \ref{tab:uniform} summarizes the results of the experiment. Columns benchmark and (i) present the results of the benchmark calibration and those from setting $\tau_z = 0$ from Table \ref{tab:aggregates}. We label the uniform tax case as (i'). Comparing the benchmark with (i') allows us to assess the effect of the size dependency of $\tau_z$. Similarly, a comparison of (i') with (i) reveals the effect of levying a flat tax. Note that because a uniform $\tau_z$ imposed on all firms does not change the extensive margin compared with the zero $\tau_z$ situation, the measures of average talents, number of firms, and mean/median firm size are unaffected. This means that the effects of the uniform tax all work through the intensive margin.
\begin{table}[t]
\footnotesize
\centering
\begin{threeparttable}
\caption{The Effects of the Progressiveness of Distortions}
\begin{tabular}{p{90pt} >{\centering\arraybackslash}p{45pt} >{\centering\arraybackslash}p{45pt}>{\centering\arraybackslash}p{40pt} >{\centering\arraybackslash}p{5pt} >{\centering\arraybackslash}p{45pt} >{\centering\arraybackslash}p{45pt} >{\centering\arraybackslash}p{40pt}}
    \hline \hline
                         & \multicolumn{3}{c}{Polluting}    & & \multicolumn{3}{c}{Non-polluting} \\
    \cmidrule{2-4} \cmidrule{6-8}
    Statistics           & Benchmark & (i')      & (i)      & & Benchmark     & (i')    & (i) \\
    \midrule
    Output               & 100.00    & 108.15   & 131.16    & & 100.00        & 106.87 & 129.62 \\
    Capital              & 100.00    & 110.91   & 163.06    & & 100.00        & 109.63 & 161.26 \\
    Consumption\tnote{a} & 100.00    & 106.57   & 123.63    & & 100.00        & 106.57 & 123.63 \\
    Wage\tnote{a}        & 100.00    & 108.76   & 160.00    & & 100.00        & 108.76 & 160.00 \\
    Output per Worker    & 100.00    & 105.74   & 128.25    & & 100.00        & 106.03 & 128.60 \\
%    Output per Firm      & 100.00    & 245.39   & 297.62    & & 100.00        & 257.12 & 311.85 \\
   \midrule
      \# of Firms          & 100.00    & 44.07    &44.07     & & 100.00        & 41.56  & 41.56 \\
    Mean Size            & 59.98     & 139.19   & 139.19     & & 52.18         & 126.53 &  126.53 \\
    \midrule
    Pollution            & 100       & 70.04    & 76.67     \\
    Intensity            & 100       & 64.78    & 58.46     \\
%    Pollution            & 100       & 73.27    & 81.66     \\
%    Intensity            & 100       & 67.78    & 62.27     \\
    Clean Share          & 57.77     & 73.33    & 85.61     \\
    \bottomrule
\end{tabular}
\begin{tablenotes}
     \footnotesize{
     \item[$\dagger$]
     Note: All of the values are percentages except for mean firm size, which are the numbers of workers.
     \item[a]
     Consumption and wage are not sector specific.}
\end{tablenotes}
\label{tab:uniform}
\end{threeparttable}
\end{table}

As we can see from Table \ref{tab:uniform}, removing the progressiveness of $\tau_z$ increases aggregate output, capital, consumption and output per worker. However, the 6\% to 11\% increases here are rather moderate compared to the 20\% to 60\% increases when all the distortions are eliminated. These differences are mainly caused by the relatively high level of the uniform tax rate of 18\% in Experiment (i'), which discourages capital accumulation and results in much lower capital stock compared to the case of $\tau_z =$ 0.\footnote{Our results on aggregate output also appear rather moderate compared to those in \citet{RestucciaRogerson:2008}, who control for the capital accumulation effects in their quantitative exercises. This is mainly because that the distortions in their paper cause large rank reversals between firm TFP and size, while the distortions in our paper preserve ranks. Please see the related discussions in \citet{Hopenhayn:2014}.}

However, removing the progressiveness of $\tau_z$ causes a large change in firm size distribution, and therefore large declines in aggregate pollution and pollution intensity. In fact, the resulting number of firms and mean firm size are the same between Experiment (i) and (i'), since the only difference between them is a uniform increase in tax rates across firms. The average pollution intensity decreases by 35\% when the progressiveness of $\tau_z$ is removed, compared to a 42\% decline when all the correlated distortions are eliminated. Again, the decline in average pollution intensity is caused by both an improved resource allocation and improved adoption of the clean technology among firms. However, the second channel is not as strong as in Experiment (i) (16 versus 28 percentage points), since the increase in the slope of the firm's profit functions is not as large as in Experiment (i). Moreover, since the output of the polluting sector only increases by 8\% in this experiment compared to 30\% in Experiment (i), the 30\% decline in aggregate pollution here is larger than the 23\% in Experiment (i).

In sum, our findings imply that it is the progressiveness of distortions, rather than the average level of firm-level distortions, that plays a dominate role in amplifying aggregate pollution and pollution intensity.

%The aggregate output, capital, consumption, output per worker, and output per firm in case (i') all increase compared with the benchmark case, which is consistent with the findings on size-dependent distortions in the literature. What is different here is that since the uniform tax rate needed to generate the same tax revenue is relatively high (the tax rate for the largest firm in the size-dependent case is 25\%), the tax itself still results in considerable output loss. The source of this output loss in our model works mainly through decrease in capital accumulation. However, for average pollution intensity, much of the reduction is achieved through the elimination of the size dependency of $\tau_z$. The adoption rate of the clean technology increases by 16 percentage points in case (i'), which is 56\% of the total increase resulting from the complete elimination of $\tau_z$. Moreover, 85\% of the total decline in average pollution intensity in the zero $\tau_z$ case is achieved by simply removing the size-dependent feature of $\tau_z$. Here, the non-polluting sector again behaves in a similar way, and hence the discussion is omitted.

%\textit{Discussion.}---The finding that the size dependency of $\tau_z$ affects economic efficiency moderately is consistent with the results of \citet{Hopenhayn:2014}. In particular, he shows that the size dependency of the policy does not necessarily imply large distortions. What matters for the size of the distortion is the total amount of resources that are affected, not to which firms these resources belong. Studies such as \citet{RestucciaRogerson:2008} and \citet{Guneretal:2008} find that size-dependent policies affect economic efficiency more than flat taxes because such policies happen to affect a large amount of resources. The fact that we impose fairly large $\tau_z$ in the flat tax case explains why removing the size dependency of $\tau_z$ hardly improves the efficiency of the economy.

%However, the size dependency of $\tau_z$ does matter for pollution, since it affects the {size distributions}. The reduction in pollution comes from two sources: the mechanical decrease in the production stage and the increase in the adoption rate of the clean technology since the intensity of regulation $\xi\pi^0(z)$ is increasing in $z$. More specifically, because the elimination of the size dependency of $\tau_z$ improves the resource allocation on the intensive margin, which increases the profits of large firms, the punishment from violating environmental regulations actually increases, thereby giving firms higher incentives to install clean technology.
%Since the size distribution of the firm is purely affected by the {size-dependency} of $\tau_z$ and {not} by the size of the distortions (in the definition of \citet{Hopenhayn:2014}), although size-dependency does {not} necessarily imply significant efficiency loss, it {necessarily} results in aggravation of pollution.

%\subsection{Environmental Regulations and Size Distribution}
%
%In our benchmark calibration, $k_E$ is about 2.5 times the equilibrium wage of a typical worker. This relatively small value limits the extent to which environmental policy can affect the real economy. In this section, we show that when $k_E$ is increased to 10 times the value used in the benchmark calibration, environmental policy influences the resource allocation markedly. We consider two scenarios. In the first case, we again solve the model with all the parameters remaining at the benchmark calibration level, but increase $k_E$ to 41.5. With no changes in regulation intensity, the adoption rate of the clean technology drops. In the second case, we increase $\xi$ such that the adoption rate in the benchmark case (57\%) is restored. We label these two experiments (iii) and (iv).
%\begin{table}[t]
%\footnotesize
%\centering
%\begin{threeparttable}
%\caption{The Effect of Regulations: Higher $k_E$}
%\begin{tabular}{p{125pt} >{\centering\arraybackslash}p{75pt} >{\centering\arraybackslash}p{75pt} >{\centering\arraybackslash}p{75pt}}
%    \hline \hline
%    Statistics                      & Benchmark             & (iii)                 & (iv)    \\
%    \midrule
%    Aggregate Output                & 100.00                & 100.00                & 100.41  \\
%    Capital                         & 100.00                & 100.28                & 101.45  \\
%    Consumption                     & 100.00                & 99.94                 & 100.21  \\
%    Output per Worker (Wage)        & 100.00                & 100.00                & 99.63   \\
%    Output per Firm                 & 100.00                & 100.00                & 187.70  \\
%    Average Talent                  & 100.00                & 100.00                & 184.14  \\
%%    TFP                             & 100.00                & 100.00                & 100.81  \\
%    \midrule
%    Number of Firms                 & 100.00                & 100.00                & 53.50   \\
%    Mean Size                       & 59.27                 & 59.27                 & 111.65  \\
%    Median Size                     & 22.95                 & 22.95                 & 63.24   \\
%    \midrule
%    Aggregate Pollution             & 100.00                & 125.64                & 87.56 \\
%    Average Intensity               & 100.00                & 125.64                & 87.20 \\
%    Clean Share                     & 57.40                 & 8.89                  & 57.06  \\
%    Monitoring                      & 20.50                 & 20.50                 & 73.50  \\
%    \bottomrule
%\end{tabular}
%\begin{tablenotes}
%     \footnotesize{
%     \item[$\dagger$]
%     Note: All values reported are in percentage points except mean and median size, which are the absolute numbers of workers.}
%\end{tablenotes}
%\label{tab:aggregates_ke}
%\end{threeparttable}
%\end{table}
%
%Table \ref{tab:aggregates_ke} presents the results of experiments (iii) and (iv). For case (iii), we first note that the size distributions and efficiency of the economy remain virtually the same as in the benchmark case. However, the clean technology adoption rate falls to 9\% since a large number of firms now find it unprofitable to use the clean technology and higher pollution thus follows. Because the benchmark case can be understood as a decrease in the price of the clean technology from case (iii), this result suggests that subsidizing clean technologies can serve as a substitute for stronger regulations.
%
%If we increase the regulations to the level such that the original technology adoption rate is restored, as opposed to the results of case (ii) where the size distributions and resource allocation are only mildly affected, the effects of the regulation in experiment (iv) are much larger. Figure \ref{fig:envpolicy} shows the size and employment distributions for case (iv).
%\begin{figure}[t]
%    \begin{center}
%    \includegraphics[width=0.45\textwidth]{D:/PaperDrafts/Pollution/PrelimResults/sizedist_bench_highcost.eps}
%    \includegraphics[width=0.45\textwidth]{D:/PaperDrafts/Pollution/PrelimResults/eshare_bench_highcost.eps}
%    \caption{Environmental Policy and Size Distribution}
%    \label{fig:envpolicy}
%    \end{center}
%\end{figure}
%In contrast to the size and employment distributions in the benchmark case, all the firms in the first group are driven out. This fact is also reflected in column (iv) of Table \ref{tab:aggregates_ke} as increases in average talent and in the mean/median size of the firms. Therefore, environmental policy {improves} the resource allocation on the {extensive} margin by forcing small unproductive firms to exit the market. However, the gains from these improvements are limited because the allocation of resources on the {intensive} margin worsens (see Table \ref{tab:talentdist_ke}).
%\begin{table}[t]
%\footnotesize
%\centering
%\begin{threeparttable}
%\caption{Resource Allocation on the Intensive Margin: High $k_E$}
%\begin{tabular}{p{65pt} >{\centering\arraybackslash}p{45pt} >{\centering\arraybackslash}p{45pt} >{\centering\arraybackslash}p{45pt} >{\centering\arraybackslash}p{45pt} >{\centering\arraybackslash}p{45pt}}
%    \hline \hline
%    Economy     & $\text{QU}_1$ & $\text{QU}_2$ & $\text{QU}_3$ & $\text{QU}_4$ & $\text{QU}_5$ \\
%    \midrule
%    Benchmark   & 2.69          & 4.19          & 7.29          & 16.55         & 69.28 \\
%    Case (iv)   & 4.44          & 6.63          & 10.98         & 21.86         & 56.10 \\
%    Case (i)    & 1.50          & 2.83          & 6.34          & 18.06         & 71.27 \\
%    Case (ii)   & 2.93          & 4.47          & 7.77          & 17.37         & 67.46 \\
%    \bottomrule
%\end{tabular}
%\begin{tablenotes}
%     \footnotesize{
%     \item[$\dagger$]
%     Note: $\text{QU}_1$ to $\text{QU}_5$ represent the first to fifth quintiles, respectively.}
%\end{tablenotes}
%\label{tab:talentdist_ke}
%\end{threeparttable}
%\end{table}
%An efficient allocation on the intensive margin is achieved in the no-size-dependent $\tau_z$ case [case (i)]. Instead of an allocation of production toward larger firms as in the efficient case, here the production of firms in the bottom four quantiles expands significantly at the expense of the production share of the most productive firms. As a result, much of the gains in economic efficiency are offset by the worsening of the resource allocations on the intensive margin. Qualitatively, this result is the same as in case (ii). However, by comparing cases (ii) and (iv), we see that the larger fixed cost $k_E$, the higher is the degree of resource misallocation on the intensive margin . Although the level of industrial pollution lowers, the reduction could be much larger if the allocation on the intensive margin also improves, as in the case of the elimination of $\tau_z$.

%\textit{Alternative Calibrations.}---Describe and analyze the results using the U.S calibration.
%
%\textit{Capital Market Frictions.}---Describe and analyze the results with capital market frictions.

\section{Conclusions}

This paper proposes a novel explanation for the industrial water pollution problem in China. In our theory, large productive firms are more likely to use clean technology and have lower pollution intensity, largely due to the fixed adoption cost of clean technology and imperfect environmental regulations. Distortions that increase with firm TFP reallocate production factors away from large productive firms, therefore reduce aggregate output while increasing aggregate pollution intensity. We support our theory by firm-level data on production, emissions, and pollution treatment technologies from China. Quantitatively, we find that distortions correlated with firm TFP reduce aggregate output by about 30\% and increase aggregate pollution by about 20\%.

Our findings have novel implications for both resource misallocation and environmental pollution. They imply that the welfare losses from misallocation include not only lower economic output, which is the focus of previous studies, and but also more pollution. This could have important welfare consequences given the severity of pollution in China and other developing countries. Our findings also challenge a popular view that economic growth necessarily comes at the cost of more pollution in developing countries. They suggest that a growth path with both higher output and lower pollution is attainable, if policy and institutional distortions can be removed in a cost effective way.

% Despite our novel findings, an important policy-related question remains: are there empirically observable size-dependent distortions that can generate quantitatively large effects on both firm size and pollution? Identifying observable policy distortions would also make it easier to collect more information on the costs of particular policy instruments, thereby allowing us to conduct a more complete cost-benefit analysis. Along this direction, our own work \citet{AGpaper} studies how migration and land policies affect the pollution from the overuse of agricultural chemicals in China.

The analytical framework in this paper can be extended to other pollutants, sectors, and countries. For other pollutants, China also has a severe air pollution problem, and casual observations reveal that small and medium-sized firms in high-polluting industries such as steel contribute dispropotionately to air pollution in China. For other sectors, \citet{AGpaper} find that misallocation caused by migration and land policies is an important cause of agricultural pollution in China. For other countries, \citet{HsiehKlenow:2014} and \citet{BentoRestuccia:2016} find evidence of distortions that are highly correlated with firm TFP in a number of developing countries, while \citet{Dasguptaetal:1998} find that small firms have higher air pollution intensity in Brazil and Mexico. It would be interesting to assess the impact of distortions on pollution in these countries.

%Another limitation of this study is that we restricted our attention to examining industrial water pollution in China. Researchers could consider extending our analysis to other pollutants, sectors, and countries. For instance, China also has a severe air pollution problem, and it has overtaken the United States as the world's largest emitter of greenhouse gases. Casual observations reveal that small and medium-sized firms in high-polluting industries such as steel are an important source of sulfur dioxide, hazardous haze, and greenhouse gas emissions in China. For other developing countries, \citet{HsiehKlenow:2014} and \citet{BentoRestuccia:2016} find that size-dependent distortions negatively affect average firm size, while \citet{Dasguptaetal:1998} find that small firms have higher air pollution intensity in Brazil and Mexico. It would thus be interesting for future research to assess whether size-dependent distortions amplify pollution in these countries as well.

%Finally, studies of urban economics and macroeconomics that adopt models that have rich macro and spatial implications are rising (\citet{Combesetal:2012}, \citet{DesmetRossihansberg:2013b}, \citet{DesmetRossihansberg:2014}). Industrial pollution naturally calls for interdisciplinary studies that analyze the environmental consequences of economic activities from a spatial perspective. Similar to the case presented herein, the agglomeration of pollution sources would be likely to change the costs and benefits structure of current studies where pollution is off the screen. We leave all these extensions to future studies.

%\newpage
%\begin{appendices}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%% Adjust the Layout of the Appendix %%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\setcounter{equation}{0}
%\setcounter{lemma}{0}
%\setcounter{corollary}{0}
%\setcounter{proposition}{0}
%\setcounter{figure}{0}
%\setcounter{table}{0}
%\renewcommand{\thesection}{\textnormal{\Alph{section}}}
%\renewcommand{\thesubsubsection}{\textnormal{\thesubsection\arabic{subsubsection}}}
%\titleformat*{\subsubsection}{\it \center}
%\renewcommand{\theequation}{\thesubsection\arabic{equation}}
%\renewcommand{\thefigure}{\thesubsection\arabic{figure}}
%\renewcommand{\thetable}{\thesubsection\arabic{table}}

%%%%%%%%%%%%%%%%%%%%%%%%%%% Beginning of the Appendix %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{center}
%\textsc{Appendix}
%\end{center}
%
%\subsection{Accounting Exercises}
%
%This appendix provides robustness calculations of the accounting exercises.
%
%\textit{Estimation Strategies.}---Ideally, we would like to have the pollution intensity over firm size. However, such data do not exist since the NGSPS only reports total value of production and total amount of pollution. Therefore, we would need to construct pollution intensity over the number of employees. We use the CNEC for this purpose. In particular, we estimate the corresponding bins for production for each employment bin from the U.S data.
%
%SUSB reports firm size in 22 bins. For the U.S size bins, we construct the corresponding production bins to be used in NGSPS. CNES is used to bridge the employment bins (SUSB) to the production bins (NGSPS).
%
%\begin{enumerate}
%  \item
%  \textit{Non-parametric}:
%    \begin{itemize}
%    \item
%    For each U.S employment bin, we compute the 1st quartile and 3rd quartile production levels for Chinese firms within that employment bin. The two quartiles are used as the lower and upper bounds for the production bins in NGSPS.
%    \item
%    We then use the median pollution intensity of firms within the newly defined production bins as the average pollution intensity for those bins.
%    \item
%    Lastly, we calculate the aggregate pollution by assigning to each bin the corresponding share of production. The NGSPS production bins are used for China and the employment bins are used for U.S.
%    \end{itemize}
%  \item
%  \textit{Piecewise Linear}:
%  \begin{itemize}
%    \item
%    For each U.S employment bin, we regress log-product on log-employment using the subset of Chinese firms within that employment bin. The lower and upper bounds for the production bins in this case are calculated as the predicted value of the above regression.
%    \item
%    We then run piecewise log-linear regression of pollution intensity on production within each new production bin. The average pollution intensity is chosen to be the predicted intensity at the midpoint of the new log-production bin.
%    \item
%    Lastly, the average intensity is applied to the production share distributions. The U.S distribution does not change, however, a new distribution for China is calculated since the endpoints of the production bins are different.
%    \end{itemize}
%  \item
%  \textit{Parametric}:
%  \begin{itemize}
%    \item
%    Using CNEC, we regress log-production on log-number of workers, which yields a {parametric} relationship between the number of workers and production.
%    \item
%    Using NGSPS, we regress log-intensity on log-production, which yields a {parametric} relationship between intensity and production. From these two relationships, we can subsequently construct a new \emph{parametric} relationship between intensity and number of employees. The average intensity is chosen to be the midpoint of each U.S employment bin. Notice that in this case we have a direct functional form for employment and intensity).
%    \item
%    Lastly, the average intensity is applied to the production share distributions. The U.S distribution does not change, but a new distribution for China is calculated since the endpoints of the production bins are different. Notice that this distribution for China is the one we use in Section \rom{1}.C.
%\end{itemize}
%\end{enumerate}
%
%The estimation results are shown in Table \ref{tab:accounting_appen}. Each of these three methods has its own advantages and disadvantages. The two non-parametric methods capture more of the variation at the local level, which could be washed out in a parametric estimation across the whole state space. However, this local nature also introduces a lot of instability on the estimations. Further, there are situations when there are gaps not covered by adjacent production bins and situations when these production bins overlap with each other. Under these conditions, some information will be lost while other is used for multiple times. Nevertheless, the results are robust across different estimation strategies.
%\begin{table}[t]
%\footnotesize
%\centering
%\begin{threeparttable}
%\caption{Size Distribution on Pollution}
%\begin{tabular}{lccccccc}
%    \hline \hline
%    Methods             & Paper  & Agricultural Food   & Textile    & Chemistry    & Beverage        & Average      \\
%    \midrule
%    Non-parametric      & 39.8\% & 60.7\% & 81.6\% & 102.5\% & 103.7\%      & 63.5\%  \\
%    Piecewise-linear    & 34.8\% & 69.4\% & 93.5\% & 180.1\% & N/A\tnote{a} & 75.4\%  \\
%    Parametric          & 43.5\% & 61.1\% & 97.5\% & 101.2\% & 89.0\%       & 67.0\%  \\
%    \bottomrule
%\end{tabular}
%\begin{tablenotes}
%     \footnotesize{
%     \item[$\dagger$]
%     Note: Please see notes of Table \ref{tab:top5summary} for acronyms of industries. For individual industries, the numbers reported are the aggregate pollution from the artificial U.S production structure as percentage from that of China. We use the 1st and 3rd quartile in the non-parametric calculation. Column 6 (Average) calculates the weighted average of these ratios using the percentage contribution in row one of Table \ref{tab:top5summary} as weights.}
%     \item[a]
%     Since the beverage industry has a lot fewer firms than the others, there are employment size bins with no corresponding firms in China, which invalidates the method. We set the ratio to 100\% in the calculation of the last two averages.
%\end{tablenotes}
%\label{tab:accounting_appen}
%\end{threeparttable}
%\end{table}
%
%\subsection{Proofs}
%
%In this section we provide formal proofs to the results in Section \rom{2}.C. For convenience, we state those results here again.
%
%\noindent PROOF OF LEMMA \ref{lemma:nofrictionpi_appen}:
%\begin{lemma}
%\label{lemma:nofrictionpi_appen}
%In an economy with no product market frictions, $\pi_0(z)$ and $\pi_1(z)$ are both increasing and linear with respect to $z$. In addition, the slope of $\pi_1(z)$ is steeper than that of $\pi_0(z)$:
%\begin{equation}
%    \frac{\partial \pi_0 (z)}{\partial z} = (1 - p\xi)\frac{\partial \pi_1 (z)}{\partial z}, \qquad \forall z \in Z
%\label{eq:lemma1ap}
%\end{equation}
%\end{lemma}
%\begin{proof}
%Since $k_E$ is sunk-cost, it does not affect firms' decision once is paid. The factor demand decisions for the two types of firms are therefore the same. The first order conditions for capital and labor are respectively
%\begin{align}
%    \label{eq:fock}
%    & \frac{\partial \pi_i(z)}{\partial k}: \qquad \alpha \gamma z^{1-\gamma} k^{\alpha \gamma -1} n^{(1-\alpha)\gamma} = R \\
%    \label{eq:focn}
%    & \frac{\partial \pi_i(z)}{\partial n}: \qquad (1-\alpha) \gamma z^{1-\gamma} k^{\alpha \gamma} n^{(1-\alpha)\gamma-1} = W, \qquad i = 0,1
%\end{align}
%Dividing (\ref{eq:fock}) with (\ref{eq:focn}) yields constant capital to labor ratio $h$
%\begin{equation}
%    h = \frac{k}{n} = \frac{\alpha W}{(1-\alpha)R}
%\end{equation}
%which says more capital is demanded when technology is capital intensive (higher $\alpha$) or when capital rental price $R$ low. Notice that the system of equations (\ref{eq:fock}) with (\ref{eq:focn}) is log-linear and thus has closed-form solution. With some algebra, the solutions are characterized by
%\begin{align}
%    \label{eq:n}
%    & n(z) = \Phi_1 R^{\frac{\alpha \gamma}{\gamma -1}} W^{\frac{1-\alpha \gamma}{\gamma-1}} \cdot z, \qquad \qquad \Phi_1 = \left[ \frac{(1-\alpha)^{\alpha \gamma}}{(1-\alpha)\gamma \alpha^{\alpha \gamma}}\right]^{\frac{1}{\gamma -1}} \\
%    \label{eq:k}
%    & k(z) = \Phi_2 R^{\frac{1+\gamma(\alpha -1)}{\gamma -1}} W^{\frac{\gamma(1-\alpha)}{\gamma-1}} \cdot z, \qquad \Phi_2 = \frac{\alpha}{1-\alpha}\Phi_1
%\end{align}
%Substitute the optimal solutions (\ref{eq:n}) and (\ref{eq:k}) back to the definition of profits functions (\ref{eq:pi1z}) and (\ref{eq:pi0z}), we have
%\begin{align*}
%    & \pi_0(z) = (1-p\xi)\left(\Omega - \frac{1}{1-\alpha}\Phi_1 \right) \kappa z, \qquad \Omega = \left(\frac{\alpha}{1-\alpha}\right)^{\alpha \gamma} \Phi_1^{\gamma} \text{ and } \kappa = W^{\frac{\gamma(1-\alpha)}{\gamma-1}} R^{\frac{\alpha\gamma}{\gamma-1}} \\
%    & \pi_1(z) = \left(\Omega - \frac{1}{1-\alpha}\Phi_1 \right) \kappa z - R k_E
%\end{align*}
%where it is clear that both functions are increasing and linear in $z$ and (\ref{eq:lemma1ap}) is true.
%\end{proof}
%
%\noindent PROOF OF COROLLARY \ref{lemma:frictionpi_appen}:
%\begin{corollary}
%\label{lemma:frictionpi_appen}
%Suppose the product market frictions are specified as $\max\left\{ 0, 1 - z^{\phi_1} \right\}$ with $1 - \gamma + \phi_1 > 0$, then $\pi_0(z)$ and $\pi_1(z)$ are both increasing and concave with respect to $z$. In addition, the slope of $\pi_1(z)$ is steeper than that of $\pi_0(z)$:
%\begin{equation*}
%    \frac{\partial \pi_0 (z)}{\partial z} = (1 - p\xi)\frac{\partial \pi_1 (z)}{\partial z}, \qquad \forall z \in Z
%\end{equation*}
%\end{corollary}
%\begin{proof}
%The proof is straightforward given Lemma \ref{lemma:nofrictionpi_appen}. Substituting in the tax function, $\pi_0(z)$ and $\pi_1(z)$ now becomes
%\begin{align*}
%    & \pi_0(z) = (1-p\xi)\left(\Omega - \frac{1}{1-\alpha}\Phi_1 \right) \kappa z^{\frac{1-\gamma+\phi_1}{1-\gamma}} \\
%    & \pi_1(z) = \left(\Omega - \frac{1}{1-\alpha}\Phi_1 \right) \kappa z^{\frac{1-\gamma+\phi_1}{1-\gamma}} - R k_E
%\end{align*}
%where $\Omega, \Phi_1$ and $\kappa$ are defined as in Lemma \ref{lemma:nofrictionpi_appen}.
%
%Assumption $1-\gamma+\phi_1 > 0$ guarantees the monotonicity of the profits functions. Concavity is easily verified by taking second order derivatives.
%\end{proof}
%
%\noindent PROOF OF PROPOSITION \ref{prop:threshold_appen}:
%\begin{proposition}
%\label{prop:threshold_appen}
%There exists a unique threshold $\hat{z}$ such that all household members with $z \leq \hat{z}$ choose to be workers and those with $z \geq \hat{z}$ become entrepreneurs. Further, $\hat{z}$ is the solution of $W = \pi(\hat{z})$
%\end{proposition}
%\begin{proof}
%Since the overall profit function $\pi(z)$ is the upper envelope of $\pi_0(z)$ and $\pi_1(z)$, from Lemma \ref{lemma:nofrictionpi_appen} and \ref{lemma:frictionpi_appen} we know $\pi(z)$ is monotonic increasing. It is easy to verify that $\pi(0)=0$. Therefore, as long as $0<W<\pi(\overline{z})$, we can find a unique $\hat{z}$ such that $\pi(\hat{z})=W$, where uniqueness follows from monotonicity. The condition $0<W<\pi(\overline{z})$ is guaranteed in the general equilibrium version of our model by Inada condition on the production function.
%\end{proof}
%
%\noindent PROOF OF PROPOSITION \ref{prop:friction_appen}:
%\begin{proposition}
%\label{prop:friction_appen}
%Given $k_E, W, \tau_z$ and $R$, there exist unique thresholds $\tilde{z}_n$ and $\tilde{z}_f$ such that:
%\begin{enumerate}[(i)]
%    \item
%    In the economy with no product market frictions, entrepreneurs with $z \leq \tilde{z}_n$ produce using dirty technology while those with $z > \tilde{z}_n$ produce using clean technology.
%    \item
%    In the economy with product market frictions, entrepreneurs with $z \leq \tilde{z}_f$ produce using dirty technology while those with $z > \tilde{z}_f$ produce using clean technology.
%    \item
%    $\tilde{z}_n < \tilde{z}_f$, that is, product market frictions impede the technology upgrade.
%\end{enumerate}
%\end{proposition}
%\begin{proof}
%Uniqueness follows from
%\begin{equation*}
%    \frac{\partial \pi_0 (z)}{\partial z} = (1 - p\xi)\frac{\partial \pi_1 (z)}{\partial z}, \qquad \forall z \in Z
%\end{equation*}
%and monotonicity under both the case with and without frictions.
%
%We can solve for analytical expression for $z_n$:
%\begin{equation}
%    z_n = \frac{R k_E}{p \xi \left[ \Omega \kappa^{\gamma} - \frac{1}{1-\alpha} \kappa \right]}
%\label{eq:zn}
%\end{equation}
%where $z_n$ is simply the ``distance'' ($R k_E$) over ``speed'' ($p \phi \left[ \Omega \kappa^{\gamma} - \frac{1}{1-\alpha} \kappa \right]$). The ``distance'' in both cases are the same, so eventually whether $z_f$ lies left or right to $z_n$ depends on the ``speed'' of convergence.
%
%Using expressions of the profits functions with frictions, we can show that
%\begin{equation}
%\label{eq:zf}
%    z_n = \frac{R k_E}{p \xi \left[ \Omega - \frac{1}{1-\alpha} \right] \kappa} < \left(\frac{R k_E}{p \xi \left[ \Omega - \frac{1}{1-\alpha} \right]\kappa}\right)^{\frac{1-\gamma}{1-\gamma+\phi_1}} = z_f^*
%\end{equation}
%which proves the proposition.
%
%One caveat is that the second inequality holds only if the number in the parentheses is greater than 1. We verify this in our quantitative analysis but restrain ourselves from discussing extreme cases where the condition is not hold.
%\end{proof}
%\end{appendices}
%
%\newpage
\bibliography{D:/Dissertation/Literature/Dissertation1}
%\bibliography{./Dissertation1}
\bibliographystyle{aea}
\bibliographystyle{apacite}
%\bibliographystyle{apalike}
%
%\newpage
%\begin{appendices}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%% Adjust the Layout of the Appendix %%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\setcounter{equation}{0}
%\setcounter{lemma}{0}
%\setcounter{proposition}{0}
%\setcounter{table}{0}
%\setcounter{page}{1}
%\renewcommand{\thesection}{\textnormal{\Alph{section}}}
%\renewcommand{\thesubsubsection}{\textnormal{\thesubsection\arabic{subsubsection}}}
%\titleformat*{\subsubsection}{\it \center}
%\renewcommand{\theequation}{\thesubsection\arabic{equation}}
%\renewcommand{\thetable}{\thesubsection\arabic{table}}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%% Beginning of the Appendix %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{center}
%\textsc{Online Appendix: Not for Publication}
%\end{center}
%[TO BE COMPLETED.]
%
%The section is a backup of the contents to be contained in Online Appendix only and will be removed from the paper upon the completion of the first draft.
%
%\subsection{Detailed Descriptions of Data Sources}
%
%The source of data that we draw upon in Sections \rom{1}.B and \rom{1}.C of the main text is the \textit{National General Survey of Pollution Sources} (henceforth, NGSPS). Since to the best of our knowledge, the data were not used before in economic studies, we provide a detailed description of the dataset in this section. The content in this section is combined from:
%\begin{itemize}
%    \item
%    \textit{Census Program of the National General Survey of Pollution Sources} {\begin{CJK}{GBK}{kai}(第一次全国污染源普查方案)\end{CJK}};
%    \item
%    \textit{Regulation on National General Survey of Pollution Sources [Decree of the State Council of the People's Republic of China (No.508)]} {\begin{CJK}{GBK}{kai}(全国污染源普查条例[中华人民共和国国务院令第508号])\end{CJK}}.\footnote{An official English translation is provided at the end of the current document.}
%    \item
%    \textit{Technical Specifications Requirements of the First National General Survey of Pollution Sources} {\begin{CJK}{GBK}{kai}(第一次全国污染源普查技术规定)\end{CJK}}.
%\end{itemize}
%
%\subsubsection{General Introduction}
%
%The purpose of the NGSPS is to understand the number of pollution sources and their distribution in different industries and regions; to understand the generation, discharge and treatment of major pollutants; to establish records for key pollution sources; to build a pollution source information database and an environmental statistics platform; and to provide basis for formulating policies and plans for economic and social development and environmental protection.
%
%The term ``pollution source'' here refers to premises, facilities and equipment which discharge pollutants to environment in the process of production, living or other activities or have adverse impact on environment, as well as other sources that result in pollution.
%
%The NGSPS surveys all entities and self-employed households which have pollution sources within the borders of the People's Republic of China. The scope of the survey includes industrial pollution sources, agricultural pollution sources, domestic pollution sources, facilities for centralized treatment of pollution, and other facilities generating or discharging pollutants. In this paper, we focus on the industrial sources. The industrial sources include all production entities that belong to any of the 39 manufacturing industries according to the \textit{Industrial Classification for National Economic Activities} (GB/T4547-2002). A complete list of the industries is provided in Table .
%
%\textit{Key Sources.---}The observations in the industrial sources are divided into two groups, \textit{key sources} and \textit{regular sources}. Key firms are required to file questionnaires that are more detailed than those filed by the regular firms. A firm is categorized as a key source, if one of the following condition is satisfied:
%\begin{enumerate}
%    \item
%    All production entities that discharge pollutants that contain heavy metal, hazardous waste, and radioactive substance.
%    \item
%    All production entities that belong to the 11 heavily polluting industries, which include: Paper and Paper Products; Food Processing; Raw Chemical Materials and Chemical Products; Textile; Ferrous Metal Smelting and Rolling Processing; Food Manufacturing; Production and Supply of Electric and Heating Power; Manufacturing of Leather, Fur, and Feather; Processing of Petroleum, Coking, and Nuclear Fuel; Manufacturing of Non-metallic Mineral Goods; Ferrous Metal Smelting and Rolling Processing.
%    \item
%    Firms with more than CNY 5 million in revenue that belong to the 16 key industries, which include: Beverage Manufacturing; Medicine Manufacturing; Chemical Fibers Manufacturing; Transportation Equipment Manufacturing; Coal Mining and Washing; Non-ferrous Metal Mining; Processing of Timber, and Manufacture of Wood, Bamboo, Rattan, Palm and Straw Products; Petroleum and Natural Gas Exploitation; General Purpose Machinery Manufacturing; Ferrous Metal Mining; Non-metal Mining; Apparel, Footwear and Caps Manufacturing; Water Production and Supply; Metal Products Manufacturing; Special Purpose Machinery Manufacturing; Communication Equipment, Computers and Other Electronic Equipment.
%\end{enumerate}
%A firm is categorized as a regular firm, if none of the above conditions holds.
%
%\textit{Variables.---}The industrial sources contain information of the following variables:
%\begin{enumerate}
%    \item
%    Firm's basic registration information, geographic latitude and longitude, receiving water of firm's discharged wastewater, etc;
%    \item
%    The consumption of raw and intermediate inputs, including: water consumption, energy consumption (coal, petroleum, gas, electricity, etc), sulfur content of fuel, the consumption of hazardous intermediate input, etc.
%    \item
%    The quantity of each of the products produced by the firm.
%    \item
%    The type, size and number of the pollutants treatment equipment that the firms own.
%    \item
%    The generation, control, discharge and comprehensive utilization of various kinds of pollutants, and the operation of various kinds of pollution prevention and control facilities.
%    \item
%    The monitoring of pollutants emission, including: the date and frequency of the monitoring; the type, quantity, and concentration of the pollutant.
%\end{enumerate}
%
%\textit{Pollutants Included.---}The pollutants included for the industrial sources are those that have general implications on pollution control. In particular, they are
%\begin{enumerate}
%    \item
%    Wastewater: Chemical Oxygen Demand (COD), Ammonian, Petrochemicals, Volatile Phenols, Mercury, Cadmium, Plumbum, Arsenium, Hexavalent Chromium, Cyanidium. For Paper and Paper Product, Food Processing, Food Manufacturing and Beverage Manufacturing Industries, Five-days Biochemical Oxygen Demand ($\text{BOD}_5$) is added. For Urban Sewage Treatment Plants, Total Phosphorus, Total Nitrogen, and $\text{BOD}_5$ are added.
%    \item
%    Exhaust: Soot, Industrial Dust, Sulfur Dioxide. For Electrolytic Aluminium, Cement, Ceramic, Frosted Glass industries, Fluoride. For Vehicle Exhaust Census, Carbon Monoxide and Hydrocarbon are added.
%    \item
%    Industrial Solid Waste: Hazardous Waste (according to the \textit{National Catalogue of Hazardous Wastes}), Smelting Waste, Fly Ash, Slag, Coal Refuse, Gangue, Radioactive Slag.
%    \item
%    Plaster discharged by Desulfurization Facilities, Sludge generated by waste water treatment facilities, and remaining from burning hazardous waste.
%    \item
%    Radioactive pollution sources from utilization of Concomitant Radioactive Mineral and from Civil Nuclear Power Generation.
%\end{enumerate}
%
%\subsubsection{Methods of Measurement}
%
%There are three methods that the data of pollutants discharge are collected, which in the priority of adoption when data from multiple sources are available, are \textit{Monitoring, Method of Emission Coefficient}, and \textit{Material Balance Method}. In this section, we go over these three methods and the principles that the three methods are used in practice.
%
%\textit{Monitoring.---}Monitored data are collected by measuring the actual quantity and pollutants concentration of wastewater and exhaust to infer the annual quantity of generation and discharge of certain types of pollutants. In addition, there are three sources that monitored data are obtained, which in the priority of adoption when data from multiple sources are available are: \textit{NGSPS monitoring, historical monitoring}, and \textit{online monitoring}. The NGSPS monitoring data are measured by the field staff of the survey in the survey year. The historical monitoring data are those measured and recorded in past three years, with the latest data having the highest priority.\footnote{There are in addition four different sources of historical data, in the order of adoption when more than one source are available, these four sources are: the historical data monitored by the local environmental authorities, the data monitored upon the completion of a newly constructed project, the data monitored by a third-party agency, and those that are self-reported by the firms.} The online monitoring data are those that are automatically uploaded by computerized and Internet-connected pollutants treatment equipment. Before historical and online monitoring data are accepted, the field staff of the survey examine to ensure that the production and pollutants treatment technology have not undergone substantial changes.
%
%A pollution source is subject to reporting monitored data, if any of the following four criteria is satisfied:
%\begin{enumerate}
%    \item
%    National Monitored Key Pollution Sources {\begin{CJK}{GBK}{kai}(国控重点污染源)\end{CJK}}: all firms listed in the \textit{List of National Intensively Monitored Firms} {\begin{CJK}{GBK}{kai}(国家重点监控企业名单,环办函[2007]93号)\end{CJK}}.
%    \item
%    Facilities for Centralized Treatment of Pollution.
%    \item
%    Provincial Monitored Key Pollution Sources {\begin{CJK}{GBK}{kai}(省控重点污染源)\end{CJK}} that in sum account for 65\% of total provincial emission as is recorded in the \textit{2005 Environmental Statistic Yearbook}. That is for each of the major pollutants, starting from the most polluting firm and adding up the quantity of emission, all firms until the summation reaches the 65\% of the total provincial emission are recorded. The union of the list of firms for all major pollutants are thus the firms that belong to this category.
%    \item
%    Newly established projects since 2005 whose pollutants discharge is more than the least polluting firms in the Provincial Monitored Key Pollution Sources.
%\end{enumerate}
%These firms are later referred to as the \textit{monitored firms} in this document.
%
%Starting from 2007Q1, for all National Monitored Key Pollution Sources, Centralized Treatment Facilities, and Provincial Monitored Key Pollution Sources, waste water sources have to be monitored at least once per quarter, and exhaust sources have to be monitored at least once per six months.
%
%The actual monitoring practice is subject to the following guidelines:
%\begin{enumerate}
%    \item
%    The monitoring of Mercury, Cadmium, Hexavalent Chromium, Plumbum, and Arsenium must be conducted at the discharge outlets of the individual factory workshops, with each outlets monitored separately.
%    \item
%    Other water-based pollutants are monitored at the outlets of the factory.
%    \item
%    The flow rates of wastewater and exhaust are monitored at the same time with the monitoring of pollutant discharge.
%    \item
%    The monitoring of pollution sources are conducted at the representative polluting time periods.
%    \item
%    All monitoring technical standards of wastewater pollutants follow \textit{Technical Specifications Requirements for the Monitoring of Surface Water and Wastewater} {\begin{CJK}{GBK}{kai}(地表水和污水监测技术规范, HJ/T91-2002)\end{CJK}} and \textit{Technical Specifications Requirements for the Monitoring of Wastewater Pollutants Emission} {\begin{CJK}{GBK}{kai}(水污染物排放总量监测技术规范, HJ/T92-2002)\end{CJK}}.
%    \item
%    For unstable wastewater sources, the samples are collected using \textit{Water Ratio Automatic Sampler}.
%    \item
%    All monitoring technical standards of exhaust pollutants follow \textit{The Determination of Particulates and Sampling Methods of Gaseous Pollutants from Exhaust Gas of Stationary Sources} {\begin{CJK}{GBK}{kai}(固定污染源排气中颗粒物测定和气态污染物采样方法, GB/T16157-1996)\end{CJK}}.
%\end{enumerate}
%
%\textit{Method of Emission Coefficient.---}The generation and discharge of pollutants are calculated according to the \textit{Handbook of Emission Coefficient}, edited by the \textit{Chinese Academy of Sciences}. The benchmark coefficients are estimated based on firm's production technology, production scale, etc. The actual coefficients used are modified from the benchmark coefficients according to firm's use of intermediate inputs, managerial practice, and pollution treatment equipment installed. The actual pollutants generation and discharge are then calculated according to the actual production scale of the firm in year 2007.
%
%\textit{Material Balance Method.---}The Material Balance Method is an application of conservation of mass to the analysis of physical systems. By accounting for material entering and leaving a system, mass flows can be identified which might have been unknown, or difficult to measure without this technique. The exact conservation law used in the analysis of the system depends on the context of the problem, but all revolve around mass conservation, i.e. that matter cannot disappear or be created spontaneously. When applied, a firm's usage of intermediate inputs, energy consumption, water consumption, and production technology are considered simultaneously, in order that the calculated pollutants generation and discharge can realistically reflect the actual production and emission of the firm in reality.
%
%\textit{Principles of Data Source Selection.---}The adoption of the methods of measurement follow the following guidelines:
%\begin{enumerate}
%    \item
%    The data of the Key Pollution Sources are obtained mainly through monitoring and the method of emission coefficient, while the material balance method is only used when the other two methods are not feasible. More specifically, the data of all firms that are identified as the monitored firms are obtained by monitoring. The data of other firms in the key sources are obtained by the method of emission coefficient.
%    \item
%    The data of the Regular Pollution Sources are obtained mainly through the method of emission coefficient, while the material balance method is only used when the method of emission coefficient is not feasible.
%    \item
%    Before accepted, the monitored data are compared with those calculated from the method of emission coefficient. If the discrepancy is less than 20\% of the monitored value, the monitored value is used. If the discrepancy is larger than 20\%, the production technology and operating status of the firm is examined. If the operating status is in compliance with that specified in the technical regulations of the monitoring practice (for example, the firm has to reach at least 75\% of its production capacity when the emission is monitored), the monitored data are accepted. Otherwise, the emission is calculated using the method of emission coefficient.
%\end{enumerate}
%
%\subsubsection{Comparisons of Statistical Features}
%
%In this section, we present detailed evidence to show that the samples covered in the CNEC and those in the NGSPS are broadly comparable.
%
%\subsection{Modeling Strategies}
%\label{sec:model_appen}
%In the paper, we model the costs of adopting abatement technology as a fixed costs $k_E$, regardless of the production scale of firms. The readers may concern that this could be a mis-specification. Two alternatives arise naturally: fixed costs plus operating costs and scale-related fixed costs. In this section, we show that each alternative contradicts some of the empirical evidence we document from the data.
%
%\textit{Operating Costs.}---We start with the case of operating costs. Trimming the top 1\% observations for outliers, the distribution of the ratio of operating costs over total value of production is shown in Table \ref{tab:oprcost_appen}.
%\begin{table}[h]
%    \footnotesize
%    \centering
%    \begin{threeparttable}
%    \caption{Operating Costs as a Fraction of Output}
%    \begin{tabular}{cccccc}
%    \hline \hline
%    Minimum & 25\%      & 50\%      & 75\%      & Maximum   & Mean \\
%    \midrule
%    0       & 0.0013    & 0.0049    & 0.0143    & 0.2084    & 0.0150 \\
%    \bottomrule
%    \end{tabular}
%    \label{tab:oprcost_appen}
%    \end{threeparttable}
%\end{table}
%On average, operating costs of abatement equipment takes about 1.5\% of a firm's annual value of production. In addition, the median of the ratio is less than 0.5\%, suggesting that operating costs are negligible for more than 50\% of the firms. For conciseness consideration, we choose to omit them from the model.
%
%\textit{Fixed Costs Proportional to Production Level.}---We do observe in the data that firms with larger production scale tend to make larger investment in abatement equipments. For instance, the correlation between the log value of production and abatement equipment investment is equal to 0.64. However, the relationship significantly weakens if we remove the percentage interpretation implied by taking logarithmic. In fact, if we calculate the ratio of abatement equipment investment over total production of firms below certain quantiles, the ratio decreases gradually as we include more large firms into the calculation. Table \ref{tab:key_appen} reports the ratio of \textit{aggregate} treatment equipments installation costs as a fraction of \textit{aggregate} value of output when firms with size below certain quantiles are included.
%\begin{table}[h]
%    \footnotesize
%    \centering
%    \begin{threeparttable}
%    \caption{Installation Costs as a Fraction of Output}
%    \begin{tabular}{cccccc}
%    \hline \hline
%    25\%      & 40\%      & 60\%      & 80\%      & 95\% \\
%    \midrule
%    0.6195    & 0.2475    & 0.1151    & 0.0668    & 0.0433 \\
%    \bottomrule
%    \end{tabular}
%    \label{tab:key_appen}
%    \end{threeparttable}
%\end{table}
%Recall that we have documented that the unit-cost per processing capacity is also decreasing with the equipment capacity, together these facts suggest the existence of returns to scale of treatment equipments.
%
%\textit{Relative Prices of Physical versus Biological Equipment.}---We assume in the main text that only the installation of biological equipments requires a fixed costs. In this paragraph, we provide evidence in support of this choice. The distributions of prices for physical and biological equipments in absolute term (CNY 10,000 in year 2007) are listed in Table \ref{tab:fixcosts_appen}.
%\begin{table}[t]
%    \footnotesize
%    \centering
%    \begin{threeparttable}
%    \caption{Relative Prices of Treatment Equipments}
%    \begin{tabular}{lcccccc}
%    \hline \hline
%    Technologies    & Minimum & 25\%      & 50\%      & 75\%      & Maximum   & Mean \\
%    \midrule
%    Physical        & 0.002   & 2.000     & 6.000     & 25.000    & 800.000   & 36.140 \\
%    Biological      & 0.04    & 30.00     & 85.00     & 260.00    & 4000.00   & 249.90 \\
%    \bottomrule
%    \end{tabular}
%    \label{tab:fixcosts_appen}
%    \end{threeparttable}
%\end{table}
%As is shown in Table \ref{tab:fixcosts_appen}, the costs of biological equipments is 7 to 15 times of those of the physical equipments. We further calculate the ratio of \textit{aggregate} treatment equipments installation costs as a fraction of \textit{aggregate} value of output for different technologies. We find that the ratio is 3.07\% for physical technology and 12.83\% for biological technology. In addition, the total investment of physical equipment over biological equipment is 0.087, meaning that the installation costs of physical equipments when aggregated across the economy are only 9\% of those of the biological equipments.
%
%These evidence suggest that comparing to biological equipment, the costs of installing physical treatment equipments are nearly negligible. Therefore in our later calculation we assume that only the adoption of biological equipment is costly.
%
%In summary, the evidence suggests that firms' investment in abatement equipment is increasing with production scale but to a much lesser extent in absolute term. Again for simplicity and without loss of generality, we choose the fixed costs modeling strategy.
%
%\subsection{Intensity-Size Correlation}
%
%\subsection{Size-Distribution}
%
%\subsection{Accounting Exercise}
%
%\subsection{Calibration}
%
%\subsection{The Partial Equilibrium Model}
%\label{sec:partial_appen}
%
%\end{appendices}

\end{document}

### 2019-09-19 Documentation/Replication_Instruction.tex
tex added

@@
 \title{\vspace{-1cm}\Large{\textsf{The Size Distribution of Firms and Industrial Water Pollution: A Quantitative Analysis of China} \\ \textsf{Replication Instruction}}}
-\author{\normalsize\textsc{Xin Tang} \\ \normalsize\textsc{International Monetary Fund}}
+\author{
+  \normalsize{{Ji Qi}} \\
+  \normalsize{{Chinese Academy of Environmental Science}}
+  \and
+  \normalsize{{Xin Tang}}\footnote{Corresponding Author: zjutangxin@gmail.com} \\
+  \normalsize{{Wuhan University}} \\
+  \normalsize{{International Monetary Fund}}
+  \and
+  \normalsize{{Xican Xi}} \\
+  \normalsize{{Fudan University}}
+}
 \date{\normalsize\today}
@@
     The NGSPS is a confidential dataset housed at the Ministry of Ecology and Environment (MEE henceforth).
-The dataset is subject to regulation by \textit{The Law of the People's Republic of China on Guarding State Secrets} \begin{CJK}{GBK}{kai}（中华人民共和国保守国家秘密法）\end{CJK} because it contains sensitive information.
-Please refer to \textit{Regulation on Archiving the National General Survey of Pollution Sources Data (State Environmental Protection Administration [2007] No.187)} {\begin{CJK}{GBK}{kai}（污染源普查档案管理办法[环发[2007]187号]）\end{CJK}}.
-The data can only be accessed within the MEE as well as institutions under its direct supervision \begin{CJK}{GBK}{kai}（中华人民共和国生态环境部及其直属单位）\end{CJK}.
+The dataset is subject to regulation by \textit{The Law of the People's Republic of China on Guarding State Secrets} (\begin{CJK}{GBK}{kai}中华人民共和国保守国家秘密法\end{CJK}) because it contains sensitive information.
+Please refer to \textit{Regulation on Archiving the National General Survey of Pollution Sources Data} (\textit{State Environmental Protection Administration [2007] No.187}, {\begin{CJK}{GBK}{kai}污染源普查档案管理办法[环发[2007]187号]\end{CJK}}).
+The data can only be accessed within the MEE as well as institutions under its direct supervision (\begin{CJK}{GBK}{kai}中华人民共和国生态环境部及其直属单位\end{CJK}).
 Researchers affiliated with these institutions should submit application for access following the internal procedure of the MEE.
@@
 The url is retrieved on September 15th, 2019 and may vary in the future.
-All applications are subject to official approval by the General Office of Ministry of Ecology and Environment \begin{CJK}{GBK}{kai}（中华人民共和国生态环境部办公厅）\end{CJK}.
+All applications are subject to official approval by the General Office of Ministry of Ecology and Environment (\begin{CJK}{GBK}{kai}中华人民共和国生态环境部办公厅\end{CJK}).
 
-    For an official introduction to the NGSPS and declassified information at the aggregated level, interested readers could refer to the book \textit{Data Collection of the National General Survey of Pollution Sources} \begin{CJK}{GBK}{kai}（《污染源普查数据集》，中国环境科学出版社，2011）\end{CJK}, which is publicly available.
+    For an official introduction to the NGSPS and declassified information at the aggregated level, interested readers could refer to the book \textit{Data Collection of the National General Survey of Pollution Sources} (\begin{CJK}{GBK}{kai}《污染源普查数据集》, 中国环境科学出版社, 2011\end{CJK}), which is publicly available.
     \item
@@
 We do, however, break the code by sections within the file, where tasks that are reasonably connected logically are grouped together.
-The code is written such that each section is self-contained, so the readers do not have to run from the very beginning if she/he only wants to replicate a certain result.
-Table \ref{tab:navi_main} summarizes the correspondence between the results in the paper (tables, figures, regression results, in-text numbers, etc.) and the section of code files that computes them, as well as data dependency.
+The code is written such that each section is self-contained, so the readers do not have to run from the very beginning if she/he only wants to replicate a certain result.\footnote{That said, the readers should always check to ensure that all the functional packages of \code{R} are loaded.} Table \ref{tab:navi_main} summarizes the correspondence between the results in the paper (tables, figures, regression results, in-text numbers, etc.) and the section of code files that computes them, as well as data dependency.
 To further assist the readers to visually navigate through the code, important sections are always indicated by a 76-character line of \code{=}.

### 2019-09-19 Empirical/Empirical_AEJ.R

@@ -177,7 +177,7 @@ summary(lm_clean)
 
 # ======================= Regressions 2 and 3 ==============================
 # Regression 2
-lm1 <- lm(log(intensity) ~ log(product) + province + industry_a + type_a, 
+lm1 <- lm(log(cod_e) ~ log(product) + province + industry_a + type_a, 
         data = POL5[(dm1_code_a == 4 | dm1_code_a == 5) & intensity > 0])
 summary(lm1)
 # Regression 3
@@ -305,6 +305,7 @@ sel1 <- which(CH$nbarworkers > cutoff[n1])
 distchn[n1] <- sum(CH$nbarworkers[sel1])
 distchn <- distchn/sum(distchn)
 # Employment distribution for polluting industries
+# NOT used in calibration
 distchn
 
 # --------------------------------------------------------------------------

### 2019-09-19 Quantitative/compute_tables.m

@@ -73,8 +73,6 @@ apf  = aggy/totfirm;
 %%%
 meanfd = zgrid(indzhatd:end)'*zprob(indzhatd:end)/totfirmd ;
 meanfc = zgrid(indzhatc:end)'*zprob(indzhatc:end)/totfirmc ;
-% meanfc = sum(zgrid(indzhatc:end).*zprob(indzhatc:end),1)/totfirmc ;
-% meanfd = sum(zgrid(indzhatd:end).*zprob(indzhatd:end))/totfirmd ;
 meanf  = mud*meanfd + (1-mud)*meanfc ;
 % --------------- Panel B -------------------
 % Mean Size

### 2019-09-19 Quantitative/misc.m

@@ -37,7 +37,7 @@ prodrede = agge_nt_notax/agge_nt_bench;
 totredi = aggi/aggi_nt_bench;
 prodredi = aggi_nt_notax/aggi_nt_bench;
 disp('The Role of Technology')
-1-(1-prodredi)/(1-totredi)
+disp(1-(1-prodredi)/(1-totredi))
 
 % Plot the tax function
 clear all;

### 2019-09-19 Quantitative/plot_figures.m

@@ -27,7 +27,7 @@ clear all;
 % Benchmark Distributions
 load('./Results/benchmark_new.mat');
 % ================== Plot Figure 5 ======================
-% Bench vs No-tax: firm
+% Bench vs Data: firm
 figure(1)
 bar([firmmodel,fsdata'],1,'group');
 colormap summer ;
@@ -40,7 +40,7 @@ ylabel('Fraction of Firms');
 title('Firm Size Distribution: Benchmark','FontWeight','Normal');
 saveas(gcf,'./Results/Figure5_Left.eps','epsc');
 
-% Bench vs No-tax: employment
+% Bench vs Data: employment
 figure(2)
 bar([esmodel,esdata'],1,'group');
 colormap summer ;

### 2019-09-19 Empirical/Empirical_Appendix.R
results cohesive

@@ -346,7 +346,7 @@ sel <- which(POLLUTEALL$product > 0 & POLLUTEALL$product < qup
              & POLLUTEALL$product > qdown)
 POLLUTEALL <- POLLUTEALL[sel]
 
-# ================== Regression (!#) Page 7 ================================
+# ================== Regression (!#) Page 9 Upper ==========================
 CODR <- POLLUTEALL[cod_e > 0]
 lm_all <- lm(log(cod_e)~log(product)+industry_a+province+type_a,
              data=CODR)
@@ -369,7 +369,7 @@ codr_residual <- lm(res_intensity ~ res_product, data = CODR)
 abline(codr_residual,col="red",lwd=4)
 dev.off()
 
-# ================== Regression (!#) Page 9 ================================
+# ================== Regression (!#) Page 9 Lower ==========================
 CODR$clean <- 0
 sel <- which(CODR$dm1_code_a == 4 | CODR$dm1_code_a == 5)
 CODR$clean[sel] <- 1

### 2019-09-19 Documentation/DataAppendix_AEJ_Final.tex
results cohesive
ready for submission

@@
 \fancyhead[LE,RO]{\thepage}
-%\fancyhead[CE]{\textit{X. TANG}}
-%\fancyhead[CO]{\textit{DATA APPENDIX: FIRM-SIZE AND POLLUTION}}
+\fancyhead[CE]{\textit{AMERICAN ECONOMIC JOURNAL: MACROECONOMICS}}
+\fancyhead[CO]{\textit{QI ET AL.: FIRM SIZE DISTRIBUTION AND POLLUTION APPENDIX}}
 \cfoot{}
@@
     \midrule
-    Key Sources     & 76.2  & 73.2 & 31.4 & 25.2             & 17.5 & 4.90 & 4.86             & 2.42   & 2.27 & 2.01    \\ %& 106,067 \\
+    Key Sources     & 76.2  & 73.2 & 31.4 & 25.2             & 17.4 & 4.90 & 4.86             & 2.42   & 2.28 & 2.01    \\ %& 106,067 \\
     Regular Sources & 35.2  & 28.3 & 7.91 & 6.49             & 2.56 & 0.13 & N/A              & 0.04   & 0.07 & N/A     \\  %& 814,937 \\
@@
 For firms in the top-5 polluting industries, we calculate the average of the ratio of treatment equipment expenditure to output value within each quintile of output.
-The means of the ratio from the first (smallest) to the fifth (largest) quintile are 22\%, 11\%, 6.7\%, 5.0\%, and 2.7\%, respectively.
+The means of the ratio from the first (smallest) to the fifth (largest) quintile are 23\%, 11\%, 6.7\%, 5.0\%, and 2.7\%, respectively.
 A linear regression model that controls for the same set of covariates as in the main text delivers the same message:
@@
     \midrule
-    Physical        & 2      & 6      & 25    & 800   & 36.14 \\
-    Biological      & 30     & 85     & 260    & 4000   & 249.90 \\
+    Physical        & 1.4       & 3.5       & 10        & 1000      & 12.4 \\
+    Biological      & 20        & 50        & 120       & 3056      & 109.6 \\
     \bottomrule
@@
     \midrule
-    Non-parametric      & 39.8\% & 60.7\%              & 81.6\%     & 102.5\%      & 103.7\%      & 63.5\%  \\
-    Piecewise-linear    & 34.8\% & 69.4\%              & 93.5\%     & 180.1\%      & N/A\tnote{a} & 75.4\%  \\
+    Non-parametric      & 39.8\% & 60.7\%              & 81.6\%     & 102.5\%      & 103.8\%      & 63.5\%  \\
+    Piecewise-linear    & 34.8\% & 69.4\%              & 93.5\%     & 180.2\%      & N/A\tnote{a} & 75.4\%  \\
     Parametric          & 43.5\% & 61.1\%              & 97.5\%     & 101.2\%      & 89.0\%       & 67.0\%  \\
@@
 \addcontentsline{toc}{section}{REFERENCES}
-\bibliography{D:/Dissertation/Literature/Dissertation1}
+\bibliography{./Dissertation1}
 \bibliographystyle{aea}

### 2019-09-19 Documentation/Pollution_Final_AEJ_Template.tex
ready for submission

--- 2019-09-19 Documentation/Pollution_AEJ_Final.tex
@@
-% Article Format: American Economic Review
-% Xin Tang @ Stony Brook University
-% Last Updated: August 2014
-\documentclass[twoside,12pt,leqno]{article}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%                    Text Layout                       %
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Page Layout
-\usepackage[hmargin={1.2in,1.2in},vmargin={1.5in,1.5in}]{geometry}
-\topmargin -1cm        % read Lamport p.163
-\oddsidemargin 0.04cm   % read Lamport p.163
-\evensidemargin 0.04cm  % same as oddsidemargin but for left-hand pages
-\textwidth 16.59cm
-\textheight 21.94cm
-\renewcommand\baselinestretch{1.15}
-\parskip 0.25em
-\parindent 1em
-\linespread{1}
-
-% Set header and footer
-\usepackage{fancyhdr}
-\pagestyle{fancy}
-\fancyhead{}
-\fancyhead[LE,RO]{\thepage}
-%\fancyhead[CE]{\textit{JI QI, XIN TANG AND XICAN XI}}
-%\fancyhead[CO]{\textit{THE SIZE DISTRIBUTION OF FIRMS AND INDUSTRIAL POLLUTION}}
-\cfoot{}
-\renewcommand{\headrulewidth}{0pt}
-%\renewcommand*\footnoterule{}
-%\setcounter{page}{1}
-
-% Font
-\renewcommand{\rmdefault}{ptm}
-\renewcommand{\sfdefault}{phv}
-%\usepackage[lite]{mtpro2}
-% use Palatinho-Roman as default font family
-%\renewcommand{\rmdefault}{ppl}
-\usepackage[scaled=0.88]{helvet}
-\makeatletter   % Roman Numbers
-\newcommand*{\rom}[1]{\expandafter\@slowromancap\romannumeral #1@}
-\makeatother
-\usepackage{CJK}
-
-% Section Titles
-\renewcommand\thesection{\textnormal{\textbf{\Roman{section}.}}}
-\renewcommand\thesubsection{\textnormal{\Alph{subsection}.}}
-\usepackage{titlesec}
-\titleformat*{\section}{\bf \center}
-\titleformat*{\subsection}{\it \center}
-\renewcommand{\refname}{\textnormal{REFERENCES}}
-
-% Appendix
-\usepackage[title]{appendix}
-\renewcommand{\appendixname}{APPENDIX}
-
-% Citations
-\usepackage[authoryear,comma]{natbib}
-\renewcommand{\bibfont}{\small}
-\setlength{\bibsep}{0em}
-\usepackage[%dvipdfmx,%
-            bookmarks=true,%
-            pdfstartview=FitH,%
-            breaklinks=true,%
-            colorlinks=true,%
-            %allcolors=black,%
-            citecolor=blue,
-            linkcolor=red,
-            pagebackref=true]{hyperref}
-
-% Functional Package
-\usepackage{enumerate}
-\usepackage{url}      % This package helps to typeset urls
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%                    Mathematics                       %
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\usepackage{amsmath,amssymb,amsfonts,amsthm,mathrsfs,upgreek}
-% Operators
+% AEJ-Article.tex for AEA last revised 22 June 2011
+\documentclass[AEJ]{AEA}
+
+% The mathtime package uses a Times font instead of Computer Modern.
+% Uncomment the line below if you wish to use the mathtime package:
+%\usepackage[cmbold]{mathtime}
+% Note that miktex, by default, configures the mathtime package to use commercial fonts
+% which you may not have. If you would like to use mathtime but you are seeing error
+% messages about missing fonts (mtex.pfb, mtsy.pfb, or rmtmi.pfb) then please see
+% the technical support document at http://www.aeaweb.org/templates/technical_support.pdf
+% for instructions on fixing this problem.
+
+% Note: you may use either harvard or natbib (but not both) to provide a wider
+% variety of citation commands than latex supports natively. See below.
+
+% Uncomment the next line to use the natbib package with bibtex
+\usepackage{natbib}
+
+% Uncomment the next line to use the harvard package with bibtex
+%\usepackage[abbr]{harvard}
+
+% This command determines the leading (vertical space between lines) in draft mode
+% with 1.5 corresponding to "double" spacing.
+\draftSpacing{1.5}
+\usepackage{natbib, graphicx, amssymb, epstopdf}
+% To the editor: booktabs is only used for \cmidrule in tables 4 and 6.
+\usepackage{enumerate, booktabs}
+
 \newcommand{\E}{\mathbb{E}}
@@
 \renewcommand{\vec}[1]{\ensuremath{\mathbf{#1}}}
-\newcommand{\gvec}[1]{{\boldsymbol{#1}}}
-
-% New Environments
-\newtheorem{result}{Result}
-\newtheorem{assumption}{Assumption}
 \newtheorem{proposition}{Proposition}
-\newtheorem{lemma}{Lemma}
-\newtheorem{corollary}{Corollary}
 \newtheorem{definition}{Definition}
-\setlength{\unitlength}{1mm}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%                 Tables and Figures                   %
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\usepackage{threeparttable,booktabs,multirow,array} % This allows notes in tables
-\usepackage{floatrow} % For Figure Notes
-\floatsetup[table]{capposition=top}
-\usepackage[font={sc,footnotesize}]{caption}
-\DeclareCaptionLabelSeparator{aer}{---}
-\captionsetup[table]{labelsep=aer}
-\captionsetup[figure]{labelsep=period}
-\usepackage{graphicx,pstricks,epstopdf}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Begin Document Content %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\title{\vspace{-1cm}\Large{{\textsf{The Size Distribution of Firms and Industrial Water Pollution\\A Quantitative Analysis of China}}}\thanks{Disclaimer: The results and conclusions in this paper are those of the authors, and do not necessarily reflect the views of the China Ministry of Environmental Protection, or those of the International Monetary Fund.
-An online appendix containing additional materials is available on the author's website: {\color{blue}https://sites.google.com/site/zjutangxin/}.}}
-\author{\normalsize{\textit{By}\ \textsc{Ji Qi},\ \textsc{Xin Tang},\textsc{\ and\ }\textsc{Xican Xi}}\thanks{Qi: Chinese Academy for Environmental Planning, Room 709-B BeiKeChuangYe Tower, No.10 Dayangfang, Beiyuan Road, Beijing, China, 100012 (e-mail: qiji@caep.org.cn); Tang: Wuhan University and International Monetary Fund, 700 19th St NW, Washington D.C., United States, 20431 (e-mail:zjutangxin@gmail.com); Xi: School of Economics, Fudan University, 600 Guoquan Road, Shanghai, China, 200433 (e-mail:xicanxi@fudan.edu.cn).
+
+\begin{document}
+
+\title{The Size Distribution of Firms and Industrial Water Pollution \\ A Quantitative Analysis of China}
+\shortTitle{FIRM SIZE DISTRIBUTION AND POLLUTION}
+\author{Ji Qi, Xin Tang, and Xican Xi\thanks{%
+Qi: Chinese Academy for Environmental Planning, Room 709-B BeiKeChuangYe Tower, No.10 Dayangfang, Beiyuan Road, Beijing, China, 100012 (e-mail: qiji@caep.org.cn); Tang: Wuhan University and International Monetary Fund, 700 19th St NW, Washington D.C., United States, 20431 (e-mail:zjutangxin@gmail.com); Xi: School of Economics, Fudan University, 600 Guoquan Road, Shanghai, China, 200433 (e-mail:xicanxi@fudan.edu.cn).
 We are grateful for the comments from Alexis Anagnostoupolos, Marina Azzimonti, Juan Carlos Conesa, Berthold Herrendorf, Nicolai Kuminoff, Pietro Peretto, Edward Prescott, Diego Restuccia, Todd Schoellman, Kerry Smith, Daniel Yi Xu, Gustavo Ventura, the editor and three anonymous referees.
@@
 We sincerely thank the China Ministry of Ecology and Environment for granting us access to the National General Survey of Pollution Sources data.
-This paper has been screened to ensure that no confidential data are revealed.}} %The authors declare that they have no relevant or material financial interests that relate to the research described in this paper.}}
-\date{\textnormal{\today}}
-
-\begin{document}
-\maketitle
-%\renewcommand{\abstractname}{}
-\vspace{-1.5em}
-%\begin{abstract}
-\begin{center}
-\begin{minipage}[c]{0.8\textwidth}
-{%\normalsize
-%\noindent \textit{We study the role of firm-size distribution in industrial pollution using a quantitative model featuring a distribution of firms.
-Micro-level data support a negative correlation between firm size and polluting intensity.
-Fixed costs associated with advanced treatment technologies are shown to be important in explaining the negative size-intensity correlation.
-Evidence suggests that product market frictions limit the expansion of productive firms in China, which leads to survivals of unprofitable small polluting firms.
-Quantitative analysis using a model consistent with these empirical regularities shows that while having moderate effect on output, size distribution exerts considerable effect over industrial pollution.
-(\textit{JEL} E01, E23, O44, Q52, Q53, Q56)}
-\noindent \textit{We argue that misallocation across firms amplifies industrial water pollution by distorting the firm size distribution in China.
+This paper has been screened to ensure that no confidential data are revealed.}}
+\date{\today}
+\pubMonth{Month}
+\pubYear{Year}
+\pubVolume{Vol}
+\pubIssue{Issue}
+\JEL{E23, L11, O44, Q52, Q53, Q56}
+\Keywords{Firm Size Distribution, Correlated Distortion, Industrial Water Pollution}
+
+\begin{abstract}
+    We argue that misallocation across firms amplifies industrial water pollution by distorting the firm size distribution in China.
 Firm-level data indicate that larger firms are more likely to use clean technology but face higher distortions.
@@
 Meanwhile, environmental regulations have sizable impact on pollution but only limited effect on output.
-(JEL E23, L11, O44, Q52, Q53, Q56)}}
-\end{minipage}
-\end{center}
-
-\textnormal{Severe} pollution has accompanied China's remarkable economic growth in the past few decades, causing environmental degradation, public health damage, and millions of premature deaths.\footnote{\citet{WorldBank_Cost_2007} estimates that the cost of air and water pollution in China is about 6\% of GDP.
+\end{abstract}
+
+\maketitle
+
+Severe pollution has accompanied China's remarkable economic growth in the past few decades, causing environmental degradation, public health damage, and millions of premature deaths.\footnote{\citet{WorldBank_Cost_2007} estimates that the cost of air and water pollution in China is about 6\% of GDP.
 The health cost of pollution is estimated to be 4\% of GDP, the majority of which is associated with premature deaths caused by pollution.
-%\citet{Ebenstein:2012} finds that industrial water pollution has a large effect on deaths from digestive cancers in China, while \citet{Ebensteinetal:2015} show that air pollution is negatively associated with life expectancy.
-See \citet{Vennemoetal:2009} and \citet{ZhengKahn:2013} for review of empirical studies on environmental pollution in China.} %Therefore it has become a major concern for both the public and policymakers.
-%\footnote{The Chinese government has initiated a campaign against pollution.
-According to the \textit{Report on the Work of the Government 2014}, the State Council has allocated \$600 billion of special funds to reduce air and water pollution during the Thirteenth Five-Year Plan (2016-2020).}
-Understanding the driving forces behind this severe pollution is crucial for designing and evaluating anti-pollution policies.
+See \citet{Vennemoetal:2009} and \citet{ZhengKahn:2013} for review of empirical studies on environmental pollution in China.} Understanding the driving forces behind this severe pollution is crucial for designing and evaluating anti-pollution policies.
 An outstanding question is whether the severe pollution is an inevitable consequence of rapid economic growth, or largely exacerbated by policy distortions and/or market inefficiencies.
@@
 Using nationally representative data on firm production, pollution emissions and pollution treatment technologies, we document two facts on firm size and pollution intensity (pollutants per output) in China.\footnote{We use the \textit{National General Survey of Pollution Sources} (NGSPS) and \textit{National Economic Census} (CNEC) in China.
-Section \rom{1} provides more details.} First, large firms have lower pollution intensity than small firms, with an elasticity of $-$0.37 between firm size and pollution intensity for the top five polluting industries in China.\footnote{The industries are ranked by their emissions of \textit{Chemical Oxygen Demand} (COD).
-The five industries are (with two-digit GB/T4547-2002 code in parentheses): Paper and Paper Products (C22), Processing of Food from Agricultural Products (C13), Textiles (C17), Raw Chemical Materials and Chemical Products (C26), and Beverages (C15).} % We find 7- to 32-fold differences in pollution intensity between firms in the largest and smallest quartiles of the firm size distribution for the top five polluting industries in China.
-Furthermore, we find that this is not only due to fewer pollutants per output are generated by large firms during production, but also that large firms are also more likely to use advanced end-of-pipe treatment technologies that require sizable fixed installation costs.
-%\footnote{The negative correlation between firm size/productivity and pollution intensity has also been found in other countries.
-For example, for developing countries \citet{Dasguptaetal:1998} find that small firms have higher air pollution intensity in Brazil and Mexico, and \citet{Martin:2013} and \citet{BarrowsOllivier:2016} find that smaller firms have higher energy intensity in India.
-For developed countries, \citet{Bloometal:2010} find that better managed firms have lower energy intensity in the United Kingdom, and \citet{ShapiroWalker:2015} find that more productive firms have lower pollution intensity in the United States.
-However, the richness of our data allows us to establish empirically a unique link between firm size and the adoption of clean technology, and thus to provide a mechanism for this negative correlation that is observable.}\textsuperscript{, }
-%\footnote{Our data reveal that large firms are more likely to not only use advanced \textit{end-of-pipe} treatment technologies to remove a larger proportion of pollutants, but also generate less pollutants in production.
-This could be because that the production technologies used by large firms are also more environmentally friendly, or also because they are using less inputs.
-While we cannot directly observe firms' production technologies, we do have data on firms' end-of-pipe pollution treatment technologies.}
+Section I provides more details.} First, large firms have lower pollution intensity than small firms, with an elasticity of $-$0.37 between firm size and pollution intensity for the top five polluting industries in China.\footnote{The industries are ranked by their emissions of \textit{Chemical Oxygen Demand} (COD).
+The five industries are (with two-digit GB/T4547-2002 code in parentheses): Paper and Paper Products (C22), Processing of Food from Agricultural Products (C13), Textiles (C17), Raw Chemical Materials and Chemical Products (C26), and Beverages (C15).} Furthermore, we find that this is not only due to fewer pollutants per output are generated by large firms during production, but also that large firms are also more likely to use advanced end-of-pipe treatment technologies that require sizable fixed installation costs.
 Second, large firms account for a smaller proportion of the total employment in China than in the United States.
@@
 counterparts.
-%\footnote{See \citet{Axtell:2001}, \citet{Luttmer:2007}, and \citet{RossihansbergWright:2007} for theories and evidence regarding the heavy right tail of the U.S.
-firm and establishment distributions.}
 If we take the U.S.
 economy as a less distorted benchmark, these facts suggest that distortions to firm size distribution could have important environmental consequences in China.
-%This fact is suggestive of the size-dependent distortions that reallocate factors away from large productive firms in China if we take the U.S.
-economy as a relatively distortion-free benchmark.
-Indeed, we find that in China, the average product of labor and capital increase strongly with firm size and productivity [\citet{HsiehKlenow:2009, HsiehKlenow:2014}].\footnote{This measure of distortion captures the effects of many of the factors that distort factor allocation across firms, including taxes and subsidies, regulations, local protectionism, transportation costs, and financial frictions.
-A prominent example of such size-dependent distortions is internal trade barriers that impede the flow of goods across regions, which presumably affect large firms more since these are more likely to sell goods across regions [\citet{Young:2000}, \citet{TombeZhu:2015}, and \citet{Eberhardtetal:2016}].
-In addition, as is the case in many other developing countries, small firms are more likely to evade taxes because of imperfect tax enforcement.}
-%Formally, we follow the approach developed by \citet{HsiehKlenow:2009, HsiehKlenow:2014}, and estimate distortions that affect factor allocation across firms using firm-level variations in average products of capital and labor.
-We find that firm-level distortions increase with firm size and productivity, consistent with the fact that large firms account for a smaller fraction of total employment in China.\footnote{It is well understood in the literature that this measure of distortions captures the effects of many factors that distort factor allocation across firms, including taxes and subsidies, regulations, transportation costs and financial frictions, among others.
-A prominent example of such size-dependent distortions is internal trade barriers that impede the flow of goods across regions, which presumably affect large firms more, since they are more likely to sell goods across regions.
-\citet{TombeZhu:2015} find that the internal trade barriers have a large impact on China's aggregate productivity.
-In addition, as is the case in many other developing countries, small firms are more likely to evade taxes due to imperfect tax enforcement.}
 
@@
 Following Fact 1 above, we assume that generated emissions per output during production is decreasing in firm output.\footnote{While our data reveal that large firms generate fewer pollutants per output, we do not know precisely the reasons behind that.
-%It may be because large firms use fewer or cleaner inputs to produce the same amount of output.
-For example, \citet{Bloometal:2010} find that better managed firms use less energy to produce the same amount of output in the U.K..
-As another example, the paper pulp industry in China uses two different types of inputs: bagasse and wood.
-While bagasse, which generates 140--180 kg COD per ton, is mostly used by firms with an annual production of {\color{black}less} than 100 k-tons, wood, which generates 30--55 kg COD per ton, is mostly used by firms with an annual production of {\color{black}more} than 100 k-tons.
 Without further data, we model the emissions generated during production in a reduced-form way, which is then calibrated to the data.
-Section \rom{1}.B discusses this point in more details.} Third, firms have the option to adopt an advanced end-of-pipe treatment technology, which we refer to as \textit{clean} technology later, after paying a fixed adoption cost.
+Section I.B discusses this point in more details.} Third, firms have the option to adopt an advanced end-of-pipe treatment technology, which we refer to as \textit{clean} technology later, after paying a fixed adoption cost.
 Firms in the polluting sector are subject to environmental regulations such that firms that do not use the clean technology face a penalty that takes away a fraction of their profits.
-%\footnote{In reality, a powerful tool used by the Chinese government to enforce environmental regulations, is to randomly audit and then shut down firms that do not comply with environmental regulations for a certain period of time, which would cost these firms a fraction of their profits.
-See for example, Trevor Nace, ``China shuts down tens of thousands of factories in widespread pollution crackdown,'' Forbes, October 2017.} % (\url{https://www.forbes.com/sites/trevornace/2017/10/24/china-shuts-down-tens-of-thousands-of-factories-in-widespread-pollution-crackdown})
 As a result, our model predicts that only firms above a certain size threshold would choose the clean technology, which is qualitatively consistent with the fact that large firms are more likely to use clean technology.
 
-Finally, we assume that firms face distortions that increase with their TFP, or \emph{correlated} distortions following the terminology of \citet{RestucciaRogerson:2008}, which are modeled as progressive output taxes.\footnote{\citet{Guneretal:2008} study a closely related type of distortions, namely \emph{size-dependent} distortions, which increase with firm or establishment size (the amount of capital, labor or output).
+Finally, we assume that firms face distortions that increase with their TFP, or \textit{correlated} distortions following the terminology of \citet{RestucciaRogerson:2008}, which are modeled as progressive output taxes.\footnote{\citet{Guneretal:2008} study a closely related type of distortions, namely \textit{size-dependent} distortions, which increase with firm or establishment size (the amount of capital, labor or output).
 An example is the many labor regulations in Italy, Spain and France that start to bind on firms with more than a certain number of employees.
 Both correlated and size-dependent distortions lead to a reallocation of resources from high TFP to low TFP firms, and they are essentially equivalent when distortions do not lead to rank reversal defined as more productive firms being smaller [\citet{Hopenhayn:2014}].} We find in our data that firms with higher TFP exhibit substantially higher average products of capital and labor in both the polluting and non-polluting sectors, indicating that more productive firms do face higher distortions [\citet{HsiehKlenow:2009, HsiehKlenow:2014}].
-%\footnote{Pioneered by \citet{HsiehKlenow:2009, HsiehKlenow:2014}, this approach to measure distortions captures the effects of a number of factors that distort factor allocation across firms, including taxes and subsidies, regulations, local protectionism, transportation costs, and financial frictions.
-A prominent example of correlated distortions is internal trade barriers that impede the flow of goods across regions, which presumably affect large productive firms more since these are more likely to sell goods across regions [\citet{Young:2000}, \citet{TombeZhu:2015}, and \citet{Eberhardtetal:2016}].
-In addition, as is the case in many other developing countries, small firms are more likely to evade taxes because of imperfect tax enforcement.}
 As emphasized by previous studies, such as \citet{RestucciaRogerson:2008} and \citet{HsiehKlenow:2014}, correlated distortions lower both mean firm size and aggregate output, since they limit the operations of productive firms and allow too many unproductive firms to survive and expand.
-%\footnote{See \citet{RestucciaRogerson:2008}, \citet{Bartelsmanetal:2013}, \citet{HsiehKlenow:2014}, \citet{AdamopoulosRestuccia:2014}, \citet{BentoRestuccia:2016} among many others.}
 A new insight from our model is that correlated distortions also increase aggregate pollution intensity for two reasons.
@@
 
-%When connecting our model with firm-level data, we are able to quantify the aggregate effects of correlated distortions in a comprehensive way, taking into account the general equilibrium responses.
-Specifically, we can assess structurally the three channels through which distortions affect aggregate pollution, following the convention in environmental economics: scale (change in aggregate output), composition (reallocation across sectors), and technique (change in sectoral pollution intensity).\footnote{See, for example, \citet{GrossmanKrueger:1993}, \citet{CopelandTaylor:2004}, and \citet{Levinson:2009}, among others.} Moreover, our model and data allow us to further decompose the technique effect into: within sector reallocation across firms, and the change in the adoption of clean technology.
-
 Conventionally, environmental economics decomposes changes in aggregate pollution into three effects: scale (change in aggregate output), composition (reallocation across sectors), and technique (change in sectoral pollution intensity) effects.\footnote{See for example, \citet{GrossmanKrueger:1993}, \citet{CopelandTaylor:2004} and \citet{Levinson:2009} among others.} Our model allows us to assess structurally how distortions affect aggregate pollution through the three channels.
@@
 We map the polluting sector to the top five polluting industries mentioned above, which account for 80\% of the total emissions in the data, and map the non-polluting sector to the rest of the manufacturing sector.
-We then use the calibrated model to evaluate the effects of two policies: removing correlated distortions from both sectors and strengthening environmental regulations.\footnote{Here we follow the so-called \emph{indirect} approach in the study of misallocation [\citet{RestucciaRogerson:2013}] by quantifying the overall effects of a variety of policies and institutions that relocate production factors from high to low TFP firms.
+We then use the calibrated model to evaluate the effects of two policies: removing correlated distortions from both sectors and strengthening environmental regulations.\footnote{Here we follow the so-called \textit{indirect} approach in the study of misallocation [\citet{RestucciaRogerson:2013}] by quantifying the overall effects of a variety of policies and institutions that relocate production factors from high to low TFP firms.
 Several examples of such policies include size-dependent taxes and subsidies, selective enforcement of regulations, financial constraints, poor enforcement of contracts, and internal trade costs, among others.
-This approach has been widely used in the misallocation literature, for instance, by \citet{HsiehKlenow:2009, HsiehKlenow:2014}, \citet{Bartelsmanetal:2013}, \citet{AdamopoulosRestuccia:2014}, and \citet{BentoRestuccia:2016}, among others.}%\footnote{Here we take the so-called \emph{indirect} approach in the study of misallocation (\citet{RestucciaRogerson:2013}), and quantify the overall effects of misallocation without identifying the specific underlying sources of the misallocation, such as size-dependent taxes and subsidies, selective enforcement of regulations, financial constraints, internal trade costs, and poor enforcement of contracts, among others.
-This approach has been widely used in the misallocation literature, for example, by \citet{HsiehKlenow:2009, HsiehKlenow:2014}, \citet{Bartelsmanetal:2013}, and \citet{AdamopoulosRestuccia:2014}, \citet{BentoRestuccia:2016} among others.}
-
-%Moreover, we find that in China, the average product of labor and capital increase strongly with firm size and productivity [\citet{HsiehKlenow:2009, HsiehKlenow:2014}], suggesting the existence of size-dependent distortions.
-% Specifically, if we take the U.S.
-economy as a relatively distortion-free benchmark, Fact 2 suggests that there could exist size-dependent distortions that reallocate factors away from large productive firms China, which we indeed find from the positive correlation between average factor product and firm level productivity [\citet{HsiehKlenow:2009, HsiehKlenow:2014}].\footnote{This measure of distortion captures the effects of many of the factors that distort factor allocation across firms, including taxes and subsidies, regulations, local protectionism, transportation costs, and financial frictions.
-A prominent example of such size-dependent distortions is internal trade barriers that impede the flow of goods across regions, which presumably affect large firms more since these are more likely to sell goods across regions [\citet{Young:2000}, \citet{TombeZhu:2015}, and \citet{Eberhardtetal:2016}].
-In addition, as is the case in many other developing countries, small firms are more likely to evade taxes because of imperfect tax enforcement.} The literature has found that size-dependent distortions limit the operations of large productive firms and allow too many small unproductive firms to survive, which lowers both mean firm size and aggregate output.\footnote{See for instance \citet{Guneretal:2008}, \citet{Bartelsmanetal:2013}, \citet{HsiehKlenow:2014}, and \citet{BentoRestuccia:2016} among others.}
-% An additional insight that we provide in this study is that size-dependent distortions also increase aggregate pollution intensity for two reasons.
-First, they lower the profits of firms which makes clean technology investment unaffordable to many firms.
-Second, they reduce the factors allocated to large productive firms which are more likely to use advanced pollution treatment technologies, and therefore reduce the share of total output that is produced using clean technologies.
-However, since size-dependent distortions both increase aggregate pollution intensity and reduce aggregate output, it is a quantitative question whether they also amplify aggregate pollution.
-
-% To guide our analysis, we use a quantitative model to organize our empirical findings as well as quantifying the effects of size-dependent distortions on aggregate output and pollution.
-In particular, we extend the classic \citet{Lucas:1978b} span-of-control model to include a distinction between polluting and non-polluting sector, size-dependent distortions, an endogenous choice of pollution treatment technologies, and imperfect environmental regulations.
-In our model, there is a stand-in household with a continuum of members.
-Household members are endowed with different sectoral specific managerial talents and make occupational choices based on their talents.
-If a member chooses to be an entrepreneur, s/he uses her managerial talent (which becomes the firm-level productivity), capital, and labor to produce the output in the sector where the managerial talent belongs.
-S/he also has to pay implicit taxes that depend on her talent, which aims to capture size-dependent distortions in an intuitive way.
-Firm size is therefore determined by the managerial talent and distortions jointly.
-
-% A novel feature of our model is that firms in the polluting sector also make decisions on pollutants treatment technologies.
-The installation of clean technology incurs a fixed cost and we assume that firms without clean technology will lose a fraction of their profits, capturing various regulatory costs that firms using dirty technology face parsimoniously.
-The fixed costs associated with the installation of clean technology lead to increasing returns to scale, which implies that only firms above a certain size threshold choose to install the clean technology in our model.
-For a given distribution of managerial talents and distortions, the model generates endogenously a distribution of firm sizes and a negative association between firm size and pollution intensity.
-To discipline our quantitative analysis, we require our benchmark model to match the observed pollution intensity, clean technology adoption rate, size-dependent distortions, and firm size distribution in China.
-%Distortions in the model is measured using variations in average products of capital and labor across firms following \citet{HsiehKlenow:2009, HsiehKlenow:2014}.
+This approach has been widely used in the misallocation literature, for instance, by \citet{HsiehKlenow:2009, HsiehKlenow:2014}, \citet{Bartelsmanetal:2013}, \citet{AdamopoulosRestuccia:2014}, and \citet{BentoRestuccia:2016}, among others.}
 
@@
 About half of the technique effect comes from the reallocation of factors across firms, while the rest is from a 27 percentage points increase in the adoption rate of clean technology.
-%Meanwhile, the proportion of firms using clean technology would increase by 27\%.% The drop in pollution comes from both the reduction in pollutants generated during the production stage and the increase in the adoption rate of clean technologies in the treatment stage.
-Each stage contributes to about 50\% of the total reduction.%\footnote{As noted earlier in this section, firms can take actions to cut their emissions levels in two stages.
-In the model, we focus on firms' choice of end-of-pipe treatment technologies, which we can directly observe and measure in the data.
-We capture the decrease in pollution intensity during the production stage in a reduced-form way, which is calibrated to the data.}
-%The expansion of productive firms is crucial to both channels.
-To isolate the importance of the \textit{progressiveness} of distortions, we solve a version of the model in which the progressive taxes are replaced with flat taxes while holding the total tax revenue constant.
-Our results show that while the progressiveness of distortions does not imply large output losses (7\%), it plays a central role in amplifying aggregate pollution (30\%).
-% where all firms in the economy face the same level of distortions.
-In our model, the size dependency of the distortions does not imply large output loss.
-However, it plays a central role in determining the pollution level.
-Removing the distortions altogether provide a useful upper bound to gauge the maximum gains that can be obtained by moving the economy to its first best.
+To isolate the importance of the \textit{progressivity} of distortions, we solve a version of the model in which the progressive taxes are replaced with flat taxes while holding the total tax revenue constant.
+Our results show that while the progressivity of distortions does not imply large output losses (7\%), it plays a central role in amplifying aggregate pollution (30\%).
 
@@
 We find that the policy reduces aggregate pollution by 14\%, but has very limited effect on aggregate output in the long run.
-%\footnote{A complete welfare analysis of tightening environmental regulations is beyond the scope of this paper, since we do not have enough data to estimate the increase in government expenditures when environmental regulations are tightened.
-We leave this important question to future research.} %
 Comparing this with the first experiment, we find that tightening environmental regulations {improves} the resource allocation on the \textit{extensive} margin of resource allocation by driving small unproductive firms out of the economy.
 However, the allocation {worsens} on the \textit{intensive} margin in the sense that among the remaining active firms, the production of medium-sized firms expands more at the expense of that of large firms.
-%In addition, environmental regulation also amplifies the effects of size-dependent distortions by increasing the average size of active firms and consequently the average level of distortions in the economy.
 In contrast, the removal of correlated distortions improves the allocation on both margins.
@@
 
-%Our findings have novel implications for the relationship between economic growth and pollution, both for the case of China and for developing countries in general.
-The environmental Kuznets curve (EKC henceforth) predicts an inverse U-shaped relationship between pollution and income per person, which implies a trade-off between economic growth and pollution when the income per person is low.
-There is a popular belief that China and other developing countries on the increasing part of the EKC and any policies that promote economic growth would necessarily cause more pollution.
-Our results suggest that a double-dividend where increase in the output and reduction in pollution are achieved simultaneously [\citet{Goulder:1994}] can be attained with policies that target at reducing the size-dependent economic frictions.
-Therefore, our paper sheds light on how environmental pollution can be controlled without damaging economic growth in developing countries.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \citet{RestucciaRogerson:2013}, \citet{Hopenhayn:2014b}, and \citet{RestucciaRogerson:2017} summarize important contributions to the literature.} Our study shows that the impact of firm-level distortions goes beyond aggregate economic output: they cause not only a large decrease in aggregate output, but also a large increase in aggregate pollution.
-By considering both aggregate output and pollution, our study thus provides a more complete understanding of the consequences of policy distortions given the large costs of pollution in developing countries such as China.%\footnote{\citet{GreenstoneJack:2015} summarize recent studies on the pollution problems of developing countries, and document poor environmental quality and high health and productivity costs of pollution in these countries.}
-%We view our approach as complementary to that work.
-In this paper, we build a macroeconomic model with rich quantitative implications which facilitates the investigation of policy related questions.
-Our focus on the firm size distribution and treatment technology adoption also distinguishes our paper from that literature, which studies the roles of product mix, consumer preference, etc.
-In connection with literature focusing on the cross-country comparison of firm size distributions [for example \citet{Poschke:2014}], our paper is also a candidate of structural interpretations of the EKC.
-
-% We contribute to a large strand of the literature on the relationship between economic growth and environment.
-At the heart of the literature is the environmental Kuznets curve.
-\citet{GrossmanKrueger:1993, GrossmanKrueger:1995}, followed by many others, establish empirically a hump-shaped relationship between a country's per-capita income and its environmental quality.\footnote{\citet{CopelandTaylor:2004} provides a review on this literature.} %\footnote{\citet{CopelandTaylor:2004} identify three channels through which economic growth can affect environmental outcomes: scale (total production), technology, and industry composition.
-However, our study contributes to the literature by emphasizing the importance of a new channel, namely factor allocation across firms, and its interaction with the scale and technology channels.
-Further, in contrast to most studies of this topic, pollution treatment technology is endogenous in our study and we use the model and data to quantify the role of the adoption of such endogenous technology.} Many scholars have interpreted this fact as evidence of an unavoidable trade-off between economic growth and environmental improvement when per-capita income is low, and there is a popular belief that growth-promoting policies necessarily lower environmental quality in China and other developing countries.
-We challenge this view by showing that removing distortions leads to both higher aggregate output and lower aggregate pollution in China.
-%\footnote{Several recent studies also examine the extent to which factor allocation across firms affects aggregate pollution.
-By using Indian manufacturing data, \citet{BarrowsOllivier:2016} find that the reallocation of resources across firms explains more than 50\% of the decline in aggregate $\text{CO}_2$ emissions intensity in India between 1990 and 2010.
-Similarly, by using U.S.
-manufacturing data, \citet{ShapiroWalker:2015} find that emissions reductions in the United States are primarily driven by the decline in within-product emissions intensity.
-They further use a quantitative model to show that the increasing stringency of environmental regulations explains most of the emissions reduction.
-\citet{Martin:2013} estimates empirically the relative contribution of changes in different policies for India.
-Our work complements these studies in that we emphasize the importance of size-dependent distortions, and our data allow us to speak directly of quantifying the importance of adopting endogenous treatment technology.} The broad message from our findings is that policy distortions and market inefficiencies typically force developing economies to operate within the production possibility frontier between economic output and environmental quality.
-Therefore, both an increase in output and a reduction in pollution can be attained by reducing policy distortions and market inefficiencies.%\footnote{There is a large literature in environmental economics that discusses the possibility of a double dividend from environmental taxes, namely a simultaneous improvement in the environment and in economic efficiency by replacing other distortive taxes with environmental taxes.
-Our finding that environmental regulations improve resource allocation along the extensive margin is consistent with this literature.
-\citet{Goulder:1994} and \citet{FullertonMetcalf:1997} review the early work on this question.}
-
-%The present study also provides a novel mechanism that could explain the declining part of the environmental Kuznets curve.
-One of its key findings is that large firms have lower pollution intensity.
-Recent empirical studies such as \citet{Poschke:2014} and \citet{BentoRestuccia:2016} find that mean firm size in the manufacturing sector increases with a country's per-capita income, with \citet{HsiehKlenow:2014} and \citet{BentoRestuccia:2016} attributing the cross-country differences in firm size largely to the cross-country differences in distortions.
-These two facts together imply that the decrease in distortions would contribute to the decline in aggregate pollution as per capita income increases.
+By considering both aggregate output and pollution, our study thus provides a more complete understanding of the consequences of policy distortions given the large costs of pollution in developing countries such as China.
 
@@
 We differ from this line of research by our focus on how correlated distortions affect aggregate pollution and how they interact with environmental policies.
-%our emphasis on the tight connection between our theory and firm-level data.
 
@@
 It allows us to not only investigate the overall effects of distortions, but also quantify an important channel through which the distortions affect emissions, namely, the adoption of clean technology.
-%Recently, a growing literature studies how international trade affects industrial pollution through the reallocation of resources across heterogeneous firms; see \citet{Cherniwchanetal:2017} for a comprehensive survey.
-Our paper differs from this closely related literature in several ways.\footnote{A more detailed review of the difference between our paper and this literature is deferred to Online Appendix H.} First, while most studies in this literature use either reduced-form or purely theoretical analysis, with the exception of \citet{ShapiroWalker:2015}, we complement these studies by providing a quantitative assessment of the general equilibrium effects of alternative policies on output and emissions, using an internally-consistent model disciplined by firm-level data.\footnote{Some studies in the literature, for example, \citet{Forslidetal:2015}, prove some qualitative results in general equilibrium under certain assumptions on model parameters, while they do not take the model to data directly.} The quantitative nature makes our analysis suitable for evaluating alternative policies.
-Second, the information on treatment equipment used by firms allows us to provide an explanation for the negative correlation between firm size and pollution intensity, and to investigate not only the overall effects of distortions, but also an important channel through which the distortions affect emissions, namely the adoption of clean technology.\footnote{In this regard, our work shares similar spirits with empirical studies like \citet{BarrowsOllivier:2016} that study how trade liberalization affect carbon emissions through changes in the product-mix of firms, and \citet{Bustos:2011} that study how trade liberalization improves firm productivity by inducing more investment in technology.} Third, while the literature focuses on trade costs, we focus on domestic distortions, and these two types of frictions interact with environmental regulations in different ways.
-In our model, environmental regulations would worsen resource allocation along the intensive margin, but this may not be the case with trade costs, because the (more productive) exporting firms can use foreign markets as a cushion to buffer the burdens from environmental regulations after paying the trade costs.
-
-%Our paper differ from a recent literature in international trade surveyed in \citet{Cherniwchanetal:2017} that also investigate how resource allocation across heterogenous firms affects industrial pollution in several important ways.\footnote{In the interests of space, we leave a more extensive review of the difference between our paper and this literature to the Online Appendix I.} First, the theoretical implications of our model on resource allocation along the intensive margin under the policy-relevant scenario where environmental policies are changed while keeping trade costs (a form of distortion) fixed are different from those of the models used in these studies.
-While our model implies that in these situations resource allocation along the intensive margin worsens, in those studies it is improved because exporting firms can use foreign markets as a cushion to buffer the increase in costs.\footnote{Loosely speaking, the counterpart of an increase in environmental regulation could be interpreted as an increase of the fixed entry cost $f$ in the original \citet{Melitz:2003} model.
-An increase in $f$ perturbs the optimal decisions of all firms by affecting the aggregate price index $P$ through general equilibrium effect.
-Since the revenues of exporting firms come from both domestic sources that are affected, and foreign sources that are not, they are less affected by the increase in $f$.} Such difference of our model offers a novel policy message compared to these papers and shows the conceptual difference of domestic distortion and trade costs.\footnote{The difference is not caused by our use of a \citet{Lucas:1978b} model instead of a \citet{Melitz:2003} model.
-Rather, it is because distortions in our model is a pure cost, while in the \citet{Melitz:2003} model, firms pay trade costs to access to foreign markets, which bring additional revenues.
-If instead we model in the \citet{Melitz:2003} model similar ``deadweight-loss'' distortions, we would get similar results.} Second, the quantitative nature of our study allows us to analyze in general equilibrium how output and emissions respond to distortions and environmental policies simultaneously, making it suitable to evaluate quantitatively scenarios such as whether a decrease in pollution intensity coupled with a larger increase in output would lead to an increase in aggregate pollution.
-The local nature of the empirical estimates in these studies are not designed to answer questions like this.\footnote{Some of these studies prove some qualitative results in general equilibrium under certain assumptions on model parameters, however they did not take the model to data directly on this respect [\citet{Forslidetal:2015}].} Our paper demonstrates the potential and the importance of studying environmental issues quantitatively.
-From a methodological perspective, our work is similar to that of \citet{ShapiroWalker:2015}.
-Third, the fact that we observe directly the emissions and treatment equipments of firms in the data allows us to investigate how distortions affect emission through a specific channel, that is the adoption of clean technology, instead of an overall effect of distortions (trade costs to be specific) to emissions [\citet{Martin:2013}, \citet{Forslidetal:2015}, and \citet{ShapiroWalker:2015}].
-In this regard, our work shares similar spirits with empirical studies like \citet{BarrowsOllivier:2016} that study how trade liberalization affect carbon emissions through changes in the product-mix of firms, and \citet{Bustos:2011} that study how trade liberalization improves firm productivity by inducing more investment in technology.
 
@@
 Recent contributions include \citet{Bustos:2011}, who study the role of tariff reductions, and \citet{Acemogluetal:2012}, who focus on taxes and subsidies.
-%and \citet{ColeGreenwoodSanchez:2016}, who emphasize the importance of contractual frictions and financial market inefficiencies.
 Using direct observations on the adoption of pollution treatment technologies by firms, we establish empirically that firm size plays a key role in technology adoption.
 Our quantitative framework thus allows us to quantify how policy distortions and market inefficiencies that distort firm size would impede technology adoption.
-%If we view tariffs as a particular type of policy distortion, our results share a similar increasing returns to scale intuition with that of \citet{Bustos:2011}, who shows empirically that a bilateral reduction in tariffs induces more firms to adopt a new technology with a fixed cost.
-Our study also differs from hers in that the quantitative framework we adopt allows us to evaluate the effect of regulatory policies with the presence of distortions and analyze the economic mechanism.
-%This conclusion applies generally to cases in which technology adoption exhibits increasing returns to scale.\footnote{In a different setting, \citet{OlmsteadRhode:2001} study the adoption of tractors in the U.S agriculture between 1910--1960, and they also find that larger farm scale induced greater adoption of tractors.}
 
 The remainder of the paper proceeds as follows.
-Section \rom{1} describes the data sources and empirical findings of this paper.
-Section \rom{2} introduces the model and analyzes its property.
-We calibrate the model in Section \rom{3}, and perform counterfactual experiments to study the effects of correlated distortions and environmental policies in Section \rom{4}.
-Section \rom{5} concludes the paper.
-
-%The remainder of the paper proceeds as follows.
-Section \rom{1} discusses the two facts that motivate our study in details.
-We describe the model and use it to estimate the firm-level distortions in Section \rom{2}.
-We calibrate the model in Section \rom{3} and perform several policy experiments to study the interaction between size-dependent distortions and environmental policies in Section \rom{4}.
-Section \rom{5} concludes the paper.
+Section I describes the data sources and empirical findings of this paper.
+Section II introduces the model and analyzes its property.
+We calibrate the model in Section III, and perform counterfactual experiments to study the effects of correlated distortions and environmental policies in Section IV.
+Section V concludes the paper.
 
@@
 
-%In this section, we describe the key empirical findings that suggest firm size distribution as an important factor affecting aggregate pollution.
-We start by introducing the data and then explain the two motivating facts mentioned before in details.
-In the end, by using an accounting exercise, we show that firm size distribution has a sizable effect on aggregate pollution.
-
 \subsection{Data Sources}
@@
 Businesses (SUSB).
-
-%This study draws upon three major data sources to calculate the pollution intensity of Chinese manufacturing firms and the firm size distributions of manufacturing firms in China and the United States: China's National General Survey of Pollution Sources (NGSPS), China's National Economic Census (CNEC), and the Statistics of U.S.
-Businesses (SUSB).\footnote{In the interest of brevity, we defer a more detailed description of these data to Online Appendix A.}
 
@@
 For instance, many large firms in these industries are identified as \textit{Key Pollution Sources}, and therefore are inspected and monitored by the government routinely and carefully, making it harder for them to fake data during this one-time survey.} While we are not aware of other economic studies that use NGSPS, a number of studies in environmental sciences have used this dataset.\footnote{See \citet{Niuetal:2016} and \citet{Qietal:2017} and the references therein for recent examples.}
-
-%\textit{NGSPS.}---The 2007 NGSPS was a joint effort of multiple national ministries in China.
-The survey records data for 2007.
-It is designed to cover {all} entities and self-employed households that emit pollutants in China.
-The complete survey consists of four components: industrial pollution sources, agricultural pollution sources, domestic pollution sources, and facilities for the centralized treatment of pollution.
-In this study, we focus on the {industrial pollution data}, which include all polluting production entities that belong to any of the 39 manufacturing industries.
-The survey is organized directly by the State Council with data collection and quality control done by specially trained field staffs.
-According to the \textit{Regulation on the National General Survey of Pollution Sources [Decree of the State Council of the People's Republic of China (No.
-508)]}, faking data would lead to financial penalties or even lawsuits.
-Therefore, the dataset is administrative in its nature and is subject to less concerns of the systematic underreporting like those documented in \citet{Dufloetal:2013} and \citet{Currieetal:2015}.\footnote{In fact, universally systematic underreporting of emissions will not change the conclusion of our paper.
-Our results will be contaminated if underreporting among large firms are more severe than small firms, which is less likely since these firms are usually inspected more carefully.
-For instance, many large firms are categorized as \textit{Nationally and Provincially Monitored Key Pollution Sources} which have to report their emissions routinely, making it harder for them to fake data during the survey process.} While we are not aware of other studies in economics that use NGSPS so far besides our own, the data in fact have been used by a large number of studies in environmental sciences.\footnote{See \citet{Niuetal:2016} and \citet{Qietal:2017} and the references therein for recent examples.}
 
@@
 In fact, since these pollutants are more hazardous than others, firms that discharge these pollutants are usually monitored more closely.} Moreover, COD emissions are typically highly correlated with the emissions of other pollutants when both are positive.\footnote{In the Paper and Paper Products industry, for example, the correlation between the emissions of COD and $\text{NH}_4^+$ is $\text{corr}(\text{COD},\text{NH}_4^+) = \text{0.82}$ and that between COD and BOD is $\text{corr}(\text{COD},\text{BOD}) = \text{0.94}$.}
-%The NGSPS contains information on the emissions of multiple air, water, and solid waste pollutants.
-Here, we focus on water pollution because the data are more accurately measured than air pollution.\footnote{We have interviewed the field staff responsible for data collection about this issue.
-The difference in data quality was mainly caused by the differences in the sampling environment.
-For water pollution, firms rarely discharge wastewater directly; instead, the wastewater is first stored in the sedimentation tank to settle heavier solids to the bottom and let lighter materials to float.
-This process creates a quiescent environment for sampling.
-For air pollutants, the sampling tube has to be placed in the chimneys, where the environment is much more volatile.
-Moreover, if firms were to manipulate their instant emissions when the field staff is on-site sampling, the sedimentation process involved with wastewater treatment makes it more difficult, since firms would have to clean the tank prior to the on-site visit of the field staff.} The variables we use are the amount of major pollutants generated and emitted, total production value, type, book value and annual operating costs of pollutant treatment equipment, firm's industry (four-digit GB/T4574-2002), ownership classification, and province.
-%However, we expect that the main results of this paper could be applied to other pollution sources as well.
-%The raw data contain 921,004 firms.
 
@@
 Importantly, the key sources include both small and large firms, and the empirical densities of the log output of the key sources resemble the bell shape of those of all firms.\footnote{Please see Figure B.1 in Online Appendix B.} As a result, when empirically analyzing the relationship of firm size with pollution intensity and treatment technology adoption, we focus on the key sources, which account for more than 90\% of total COD emissions and 80\% of total output from the top five polluting industries (Table \ref{tab:top5summary}).
-%\footnote{We have also run all the following regressions using a sample including both regular and key sources, and found similar negative correlations.}
 The variables we use are the firm's output, the amount of major pollutants generated and emitted, installation costs of pollutant treatment technologies, industry (up to four-digit GB/T4574-2002), ownership classification, and province.
 
-%Environmental sciences studies find that industrial waste is typically concentrated in a handful of sectors.
-Further, even within narrowly defined manufacturing sectors, pollutant emissions are usually concentrated among firms that engage in some particular manufacturing processes.
-Grouping firms by sector thus risks blurring important within sector variations.
-To address this issue, the NGSPS divides the sample into two large groups---\textit{key sources} and \textit{regular sources}---where loosely speaking, firms identified as ``key sources'' are the most polluting ones.
-We focus on key firms in the study because they produce the majority of the pollutants (Table \ref{tab:top5summary}, which is explained in details shortly after), while most regular firms emit very little pollutants.
-This means that key firms are more representative of polluting manufacturing firms in China.\footnote{Online Appendix A.1 defines these key sources formally.} Moreover, the key sources include large firms as well as small firms in that the empirical density function of the log output value of the key sources resembles the same hump-shape of that of all firms.\footnote{Please refer to Online Appendix B and the two upper panels of Figure B.1 therein for details.} As a result, we use the key sources to characterize the relationship between emissions and firm size more accurately.
-
-%Among all the pollutants, we analyze \textit{Chemical Oxygen Demand} (COD), a major water pollutant commonly used to measure water quality.
-COD measures the amount of oxygen consumed when a chemical oxidant is added into a sample of water.
-It is an indirect measure of the overall quantity of contaminants that will eventually cause oxygen loss and thus the death of living creatures.
-We choose COD because it is widely emitted by firms across various sectors, which allows us to keep most observations from the data.
-Other pollutants are emitted by significantly fewer firms because they are usually associated with the production in particular industries, which raises sample selection concerns.
-See Table \ref{tab:nfirmPollutant}, which lists the percentage of key sources firms that have positive emissions of different pollutants.
-In other words, if we focus on other pollutants, for instance hexavalent chromium, we are limiting ourselves to a handful of firms that engage in particular production processes like leather tanning and pigment manufacturing.\footnote{We would like to stress that the fact many firms do not report emissions on specific pollutants like cyanidium or chromium is simply because their production process does not involve the use of related materials.
-It is \textit{not} because of under-reporting or other issues related to data quality.
-In fact, since these pollutants are more hazardous than others, firms that discharge these pollutants are monitored more closely.} Moreover, COD emissions are highly correlated with the emissions of other pollutants.\footnote{In the Paper and Paper Products industry, for example, the correlation between the emissions of COD and those of $\text{NH}_4^+$ is $\text{corr}(\text{COD},\text{NH}_4^+) = 0.82$ and that between COD and BOD is $\text{corr}(\text{COD},\text{BOD}) = 0.94$.
-This suggests that if a firm discharges a large amount of COD, it is likely that it also discharges a lot of other pollutants that are specific to its production process.} Finally, we focus on {measured} end-of-pipe emissions.
-Online Appendix A.2 explains in detail how these data are collected.
-In the interests of space, we note that the information contained is different from the mix of energy sources and intermediate goods in the production process.
-We present the results for the top five polluting industries (29,019 firms).
-%\begin{figure}[t]
-%    \begin{center}
-%    \includegraphics[width=0.50\textwidth]{D:/PaperDrafts/Pollution/R_Implementation/pie_R.pdf}
-%    %\floatfoot{Source: National General Survey of Pollution Sources}
-%    \caption{COD Emissions by Sectors}
-%    \label{fig:pie}
-%    \end{center}
-%\end{figure}
 \begin{table}[t]
@@
 \centering
-\begin{threeparttable}
 \caption{Statistics of the Top 5 Polluting Industries by COD}
-\begin{tabular}{lcccccc}
+\begin{tabular}{lccccc}
     \hline \hline
-%    & Waste & COD & Petrochemicals & Ammonian & BOD & Cyanidum & Hex-Chromium & Phenol & Arsenium & Chromium \\
-                                                &  & Paper & Food Processing& Textiles  & Chemical Materials & Beverages  \\ %& Med  & Fer  & Petro & Food & Fib \\
-    \midrule
-    \% in Total COD Emission                    &  & 33.4  & 15.1 & 14.0 & 10.4 & 4.27  \\ %& 2.98 & 2.49 & 2.32  & 2.30 & 2.15 \\
-    \% of Emissions by Key Sources              &  & 99.6  & 91.8 & 91.1 & 99.7 & 65.1  \\ %& 92.9 & 99.9 & 99.9  & 96.4 & 97.8 \\
-    \% of Production by Key Sources             &  & 87.2  & 69.3 & 48.3 & 98.6 & 88.1  \\ %&& 95.7 & 99.3 & 99.7  & 98.5 & 91.9 \\
-    \bottomrule
+                                       & Paper & Food Processing& Textiles  & Chemical Materials & Beverages  \\
+    \hline
+    \% in Total COD Emission           & 33.4  & 15.1 & 14.0 & 10.4 & 4.27  \\
+    \% of Emissions by Key Sources     & 99.6  & 91.8 & 91.1 & 99.7 & 65.1  \\
+    \% of Production by Key Sources    & 87.2  & 69.3 & 48.3 & 98.6 & 88.1  \\
+    \hline
 \end{tabular}
-\begin{tablenotes}
-     \footnotesize{
-     \item[$\dagger$]
-     Data Source: NGSPS.
-The acronyms respectively refer to (with the two-digit GB/T4547-2002 classification code in parentheses): Paper and Paper Products (C22), Processing of Food from Agricultural Products (C13), Textiles (C17), Raw Chemical Materials and Chemical Products (C26), and Beverages (C15).}
-%     \item[a]
-%     Relative contribution to total COD emissions by each sector.
-%     \item[b]
-%     Percentage of total COD emissions accounted for by key firms within each sector.
-%     \item[c]
-%     Percentage of total production accounted for by key firms within each sector.
+\begin{tablenotes}[Sources]
+     NGSPS.
+The acronyms respectively refer to (with the two-digit GB/T4547-2002 classification code in parentheses): Paper and Paper Products (C22), Processing of Food from Agricultural Products (C13), Textiles (C17), Raw Chemical Materials and Chemical Products (C26), and Beverages (C15).
 \end{tablenotes}
 \label{tab:top5summary}
-\end{threeparttable}
 \end{table}
-
-%Table \ref{tab:top5summary} contains the basic statistics on these industries.
-The key firms in the top five polluting industries are representative of industrial pollution in China.
-These industries combined contribute 77\% of total industrial COD emissions, with key firms responsible on average for more than 90\% of the within-sector emissions and more than 80\% of the within-sector output.
 
@@
 We use CNEC instead of ASIF because that ASIF does not have information on non-state firms with sales below 5 million CNY, which are crucial for our analysis.
-If we used the 2004 ASIP, we would have missed 29\% of the employment and 80\% of the firms.}%\footnote{It is important to use the CNEC rather than the commonly used \textit{Annual Surveys of Industrial Production (ASIP)} for which the 2007 data are available (the same year that the NGSPS covers).
-The reason is that the CNEC surveys firms of {all} sizes as opposed to only firms with a revenue of more than CNY 5 million in the ASIP.
-In 2004, the number of firms and employees covered by the annual survey were 276,410 and 66,725,059, respectively, while those covered by the census were 1,375,148 and 93,541,923.
-Therefore, we would be missing 28.6\% of employment and 79.9\% of firms had we used only the annual survey.
-%The number of firms covered in the NGSPS and CNEC, 921,004 and 1,375,148, are broadly consistent given that the former further requires a production entity to have pollution sources in order to be included.Online Appendix B provides more details.
-However, the basic features such as the variable definitions are essentially the same in these two datasets.
-\citet{Brandtetal:2012} describe the annual surveys in detail.}
+If we used the 2004 ASIP, we would have missed 29\% of the employment and 80\% of the firms.}
 
@@
 \begin{figure}[t]
+\caption{Firm Size and Pollution Intensity}
+\label{fig:codscatter}
     \begin{center}
-    \includegraphics[width=0.40\textwidth]{./Figures/pooled_intensity_size.pdf}%
-%    \includegraphics[width=0.40\textwidth]{D:/PaperDrafts/Pollution/R_Implementation/agri_R.pdf} \\
-%    \includegraphics[width=0.40\textwidth]{D:/PaperDrafts/Pollution/R_Implementation/textile_R.pdf}
-%    \includegraphics[width=0.40\textwidth]{D:/PaperDrafts/Pollution/R_Implementation/chemmat_R.pdf} \\
-%    \includegraphics[width=0.40\textwidth]{D:/PaperDrafts/Pollution/R_Implementation/bever_R.pdf}
-%    \includegraphics[width=0.40\textwidth]{D:/PaperDrafts/Pollution/R_Implementation/nitro_R.pdf} \\
-%    \vspace{-1em}
-    \caption{Firm Size and Pollution Intensity}
-    \floatfoot{Source: NGSPS. Line: Least square fit. Residuals after controlling for the covariates are plotted.}
-    \label{fig:codscatter}
+    \includegraphics[width=0.40\textwidth]{./Figures/pooled_intensity_size.pdf}
     \end{center}
+    \begin{figurenotes}[Source]
+        NGSPS.
+    \end{figurenotes}
+    \begin{figurenotes}
+        The line is the least square fit. Residuals after controlling for the covariates are plotted.
+    \end{figurenotes}
 \end{figure}
@@
 \begin{equation}
-%    \log (\text{COD}_i) = \underset{(0.17)}{-3.75} + \underset{(0.01)}{0.63} \times \log (\text{Output}_i) + \vec{X_s} \gvec{\upgamma}_1 + \vec{X_p} \gvec{\upgamma}_2 + \vec{X_o} \gvec{\upgamma}_3 + \varepsilon_i,
-    \log (\text{COD}_i) = \underset{(0.17)}{-3.75} + \underset{(0.01)}{0.63} \times \log (\text{Output}_i) + \vec{X} \gvec{\upgamma} + \varepsilon_i,
+    \log (\text{COD}_i) = \underset{(0.17)}{-3.75} + \underset{(0.01)}{0.63} \times \log (\text{Output}_i) + \vec{X} \vec{\gamma} + \varepsilon_i,
 \label{eq:poolols}
@@
 That is, other things equal, a 1\% increase in firm output is associated with a 0.37\% decrease in pollution intensity.
-%\footnote{Notice that regression (\ref{eq:poolols}) is mathematically equivalent to $\log(\text{COD}_i/\text{Sales}_i)= \beta_0 + \beta_1 \log(\text{Sales}_i) + \gvec{\upgamma}\vec{X} + \varepsilon_i$.}
-Figure \ref{fig:codscatter} visualizes this negative relationship, where the residuals from regressing intensity and output on the dummies are plotted to remove the influences of other covariates.\footnote{Recall that here by the \textit{Regression Anatomy Formula}, the slope of the least square fit in Figure \ref{fig:codscatter} is precisely one minus the coefficient on $\log(\text{Output})$ in Equation (\ref{eq:poolols}).} The estimation has an $R^2$ of 0.47, suggesting that nearly half of the variations in COD emissions can be explained by the variations in firm output and in the three sets of dummies.\footnote{We also tried other econometric specifications, and found similar negative correlations between pollution intensity and firm size.
+Figure \ref{fig:codscatter} visualizes this negative relationship, where the residuals from regressing intensity and output on the dummies are plotted to remove the influences of other covariates.\footnote{Recall that here by the \textit{Regression Anatomy Formula}, the slope of the least square fit in Figure \ref{fig:codscatter} is precisely one minus the coefficient on $\log(\text{Output})$ in Equation (\ref{eq:poolols}).} The estimation has an $R^2$ of 0.41, suggesting that nearly half of the variations in COD emissions can be explained by the variations in firm output and in the three sets of dummies.\footnote{We also tried other econometric specifications, and found similar negative correlations between pollution intensity and firm size.
 For instance, we estimated versions of Equation (\ref{eq:poolols}) for each industry and with robust standard errors clustered in provinces.
 Please see Online Appendix C for more information.} We would also like to point out that the coefficient of the dummy on whether a firm is state-owned or not, is statistically \textit{insignificant}.
-%\footnote{This finding is different from that of \citet{Jiangetal:2014}.
-We think that this could be because we are using a different sample of firms.
-Specifically, while their data cover the Nationally Monitored Key Pollution Sources, ours have a much broader coverage.}
 As a result, we do not distinguish between whether a firm is state-owned or not in our later analysis.
-
-%the regression results indicate that pollution intensity decreases as firm sales rise.
-Specifically, by subtracting $\log (\text{Sales}_i)$ on both sides of Equation (\ref{eq:poolols}), the elasticity between pollution intensity and total sales is $-$0.37, which means that other things being equal, doubling total sales is associated with a 37\% decrease in pollution intensity.\footnote{Notice that regression (\ref{eq:poolols}) is mathematically equivalent to $\log(\text{COD}_i/\text{Sales}_i)= \beta_0 + \beta_1 \log(\text{Sales}_i) + \gvec{\upgamma}\vec{X} + \varepsilon_i$.} Figure \ref{fig:codscatter} shows this negative relationship, where the residuals from regressing intensity and sales on the dummies are plotted to remove the influences from other control variables.\footnote{Recall that here by the \textit{Regression Anatomy Formula}, the slope of the least square fit in Figure \ref{fig:codscatter} is precisely one minus the coefficient on $\log(\text{Sales})$ in Equation (\ref{eq:poolols}).} The estimation has an $R^2$ of 0.47, which suggests that a fair amount of variation can be explained by the variations in total sales and in the three sets of dummies.\footnote{We also estimated the relationship by using other econometric specifications.
-For instance, we estimated versions of Equation (\ref{eq:poolols}) for each industry and with robust standard errors clustered in different groups.
-All the regressions suggest the same negative qualitative relationship between intensity and size.
-The estimation results of the other specifications as well as the interpretations of the coefficients before the dummies are included in Online Appendix C.} It is important to emphasize that the coefficients of the ownership dummies ($\gvec{\upgamma}_3$)---that is whether a firm is state-owned, collectively owned, etc---are statistically \textit{insignificant}.
-%\footnote{This finding is different from that of \citet{Jiangetal:2014}.
-We think that this could be because we are using a different sample of firms.
-Specifically, while their data cover the Nationally Monitored Key Pollution Sources, ours have a much broader coverage.} As a result, in the remaining of the paper, we do not distinguish between whether a firm is state-owned or privately owned.
-
-%We define pollution intensity as follows:
-%\begin{equation*}
-%    \text{Intensity} = \frac{\text{Total COD Emissions}}{\text{Total Production value}}.
-%\end{equation*}
-%We group firms into quartiles based on their total output value.
-For each industry, we calculate the output-weighted average of the pollution intensity of the firms in each quartile.
-Table [] reports the results.
-For the Paper and Paper Products industry, the pollution intensity of the firms in the bottom quartile is 6.7 times that of the firms in the top quartile.
-The difference can be as large as 31.4 times, as is the case for the Beverages industry.
-Moreover, pollution intensity decreases continuously as firm size rises.
-This trend can also be seen from the scatterplot of the logarithm of intensity against that of total production value.
-We plot the Paper and Paper Products industry in Figure \ref{fig:codscatter} as an example.
-It shows a significant negative correlation between log-intensity and log-production in the data.
-The scatterplots for the other four industries are deferred to Online Appendix C.%for the top-5 polluting industries are presented  (except the bottom-right one).
-
-%\begin{table}[t]
-%\footnotesize
-%\centering
-%\begin{threeparttable}
-%\caption{Firm Size and Pollution Intensity}
-%\begin{tabular}{p{120pt}>{\centering\arraybackslash}p{45pt} >{\centering\arraybackslash}p{45pt} >{\centering\arraybackslash}p{45pt} >{\centering\arraybackslash}p{45pt}}
-%    \hline \hline
-%        & \multicolumn{4}{c}{Quartile of Firm Sales} \\
-%    \cmidrule{2-5}
-%    Industry & $\text{QU}_1$ & $\text{QU}_2$ & $\text{QU}_3$ & $\text{QU}_4$ \\
-%    \midrule
-%    Paper               & 6.7   & 3.2   & 2.0 & 1.0 \\
-%    Agricultural Food   & 20.8  & 7.6   & 3.6 & 1.0 \\
-%    Textiles            & 8.3   & 3.6   & 2.4 & 1.0 \\
-%    Chemical Materials  & 6.7   & 3.8   & 2.7 & 1.0 \\
-%    Beverages           & 31.4  & 18.7  & 4.7 & 1.0 \\
-%    \bottomrule
-%\end{tabular}
-%\begin{tablenotes}
-%     \footnotesize{
-%     \item[$\dagger$]
-%     Data Source: NGSPS. $\text{QU}_1$ to $\text{QU}_4$ represent the bottom to top quartiles, respectively. The pollution intensity of the top quartile of each industry is normalized to one.}
-%\end{tablenotes}
-%\label{tab:intensityquartile}
-%\end{threeparttable}
-%\end{table}
-%\footnote{One exception is Chemistry Materials, the middle right panel.
-Further investigation into the data reveals that the reason that we do not observe a negative correlation in the Chemistry Material industry as clear as in the other industries is because there are many sub-industry level heterogeneities pooled at the two-digit level.
-To show that this is indeed the case, we repeat the exercise for the top polluting four-digit industry within the Chemistry Material industry, {Nitrogen Fertilizer} (C2621) which ranks the sixth among all four-digit industries.
-The result is shown in the lower right panel of Figure \ref{fig:codscatter}, where the negative correlation is clear.
-Put differently, the ``circle'' we see in the Chemistry case is in fact a combination of several ``ellipses'', each with a downward sloping transverse diameter.
-We have also plotted these figures using the residuals from regressions (\ref{eq:indols}) and (\ref{eq:poolols}).
-The results are almost the same and are thus shown Online Appendix.
-This is confirmed by including four-digit industry dummy in the regression for Chemistry industry specified below.
-After introducing four-digit industry dummies, the magnitude estimates for $\beta_1$ increases to $-$0.21 and the $R^2$ increases to 0.26.
-Both numbers are now of comparable magnitudes with the other industries.}
-
-%\begin{equation}
-%    y_i = \beta_0 + \beta_1 V_i + \vec{X_p}\beta_2 + \vec{X_o}\beta_3 + \varepsilon_i
-%
-%\end{equation}
-%We then run a pooled regression with :
-%\begin{equation}
-%    y_i = \beta_0 + \beta_1 V_i + \vec{X_p}\beta_2 + \vec{X_s}\beta_3 + \vec{X_o}\beta_4 + \epsilon_i
-%\label{eq:poolols}
-%\end{equation}
-
-%Regression results from (\ref{eq:indols}) and (\ref{eq:poolols}) are shown in Table \ref{tab:olsresults}.
-%\begin{table}[t]
-%\footnotesize
-%\centering
-%\begin{threeparttable}
-%\caption{OLS Regression Results}
-%\begin{tabular}{ccccccc}
-%    \hline \hline
-%    Parameters & Paper           & Agri            & Textile         & Chem            & Bever           & Pooled          \\
-%    \midrule
-%    $\beta_0$  & $-$4.25$^{***}$ & $-$2.23$^{***}$ & $-$3.73$^{***}$ & $-$7.17$^{***}$ & $-$2.82$^{***}$ & $-$2.50$^{***}$ \\
-%               & (0.56)          & (0.26)          & (0.57)          & (0.33)          & (0.38)          & (0.17)          \\
-%    $\beta_1$  & $-$0.30$^{***}$ & $-$0.61$^{***}$ & $-$0.31$^{***}$ & $-$0.13$^{***}$ & $-$0.45$^{***}$ & $-$0.37$^{***}$ \\
-%               & (0.01)          & (0.01)          & (0.01)          & (0.01)          & (0.02)          & (0.01)          \\
-%    $R^2$      & 0.22            & 0.46            & 0.14            & 0.08            & 0.29            & 0.37            \\
-%    \midrule
-%    $N$        & 5626            & 6883            & 6281            & 8672            & 1557            & 29019 \\
-%    \bottomrule
-%\end{tabular}
-%\begin{tablenotes}
-%     \footnotesize{
-%     \item[$\dagger$]
-%     Note: All regressions include complete sets of provincial and ownership rights dummies.
-The pooled regression includes in addition two-digit industry dummies.
-OLS standard errors are reported in parentheses.
-Regressions with robust standard errors clustered on provinces (industry level regression) and industries (pooled regression) yield very similar results are reported only in Online Appendix for brevity.
-Statistical significance code: $^{***}$ $p < 0.001$.}
-%\end{tablenotes}
-%\label{tab:olsresults}
-%\end{threeparttable}
-%\end{table}
-%Estimation results in Table \ref{tab:olsresults} confirm observations in Figure \ref{fig:codscatter}.
-The intensity-production elasticities $\beta_1$ are all accurately estimated to be negative and they are also of economic significance.
-The $R^2$ shows that a fair amount of variation observed in the intensity is changing with production scale.
-As a crude calculation, the coefficient $-$0.37 on $\log V_i$ for the pooled case implies that by doubling the production scale, the COD discharged per unit production will decrease by 37\%.\footnote{The pollution intensity also exhibits rich provincial level variations.
-We leave the discussion to Online Appendix.}
-
-%The pollution intensity also exhibits rich provincial level variations.
-We take the regression on the paper industry for example.
-Using Beijing as the benchmark, of all the remaining 29 provinces and municipalities, only the coefficient of Shanghai is negative and statistically insignificant.
-For the remainders, all estimates positive and highly significant.\footnote{One province, Hebei is significant at 10\% level.
-Four others are significant at 1\% level while all others are significant at 0.1\% level.
-We notice here Hebei, a province that is seriously disturbed by industrial pollution, is in fact an outlier as the paper manufacturing is not its pillar industry.} The bottom-five provinces (those with largest dummy estimates) are Ningxia, Inner Mongolia, Gansu, Shaanxi and Xinjiang, for which the rankings of their provincial GDP in 2007 are respectively 29, 16, 27, 19 and 25 out of 31 provincial administrative regions (not including Hong Kong and Macau).
-Geographically, these are also inland provinces.
-In fact, despite that the majority of the paper manufacturers belong to the Zhejiang and Guangdong (GDP ranking 1st and 4th), the pollution problem is of less severity as opposed to those inland less developed regions.
-These patterns are highly robust across various versions of our regressions.
-The general message we get from these dummy coefficients are the following.
-First, Beijing and Shanghai, arguably the political and economic center of China, exert pollution control standard far more stringent than the rest provinces.
-Second, inland and less developed provinces in general have worse control over and are more prone to the industrial pollution problem.
-These two patterns are broadly consistent with the EKC and results from previous literature.
-However, unlike \citet{Jiangetal:2014}, ownership rights do not seem to have significant effect.
-If anything, the Foreign and Hong Kong, Macau and Taiwan based firms seem to have weakly better pollution controls.
-But the statistical significance of the estimates never exceed 10\% across all our regressions.
-We think this could well because their estimates are derived using a limited sample of firms (1931) while our data cover the universe of firms.
-
-%\subsection{Firm Size and Treatment Technologies}
 
@@
 In addition, because {combined} technologies look very similar to biological technologies for all the technical aspects we are interested in, we group them with {biological} technologies.\footnote{Examples of the technologies attributed to these three base categories include filtering, centrifuging, precipitation, and separation (physical); oxidation reduction and neutralization (chemical); and aerobic biological treatment and activated sludge processes (biological).
-Broadly speaking, physical technology corresponds to the \textit{Preliminary} and \textit{Primary} treatment in the U.S., while chemical and biological technologies correspond to the \textit{Secondary} and \textit{Tertiary} treatment.} In sum, we are left with three broad categories of technologies.%Among all the technical aspects, we are particularly interested in the abatement efficiency and fixed installation costs of these technologies.%\footnote{We do not include the annual {operating costs} in our analysis because we do not model how much a firm uses its abatement equipment.
-Adding the operating costs to the installation costs does not change the results in this section.
-Hence we exclude the operating costs here for consistency.
-See Online Appendix D.2 for more details.}
-
-%\textit{The Role of Treatment Technologies.---}The negative firm size--intensity relationship does not explain why larger firms pollute with less intensity.
-To answer this question, we exploit the detailed information in the NGSPS on the end-of-pipe wastewater treatment equipment that firms use.
-The NGSPS groups wastewater treatment technologies into five categories: physical, chemical, physio-chemical, biological, and combined technologies.
-In the subsequent analysis, we drop {physio-chemical} technologies because fewer than 0.5\% firms adopt this type of equipment.
-Further, because {combined} technologies are different combinations of biological technologies with other technologies, and for all the technical aspects we are interested in they look very similar to biological technologies, we group them with {biological} technologies.\footnote{Examples of the technologies attributed to these three base categories include filtering, centrifuging, precipitation, and separation (physical); oxidation reduction and neutralization (chemical); and aerobic biological treatment and activated sludge processes (biological).
-Broadly speaking, physical treatment corresponds to the \textit{Preliminary} and \textit{Primary} treatment in the United States, while chemical and biological treatment relates to the \textit{Secondary} and \textit{Tertiary} treatment and those that are more advanced.} We are interested in the processing efficiency and installation costs of these technologies.\footnote{We do not include the annual {operating costs} in our analysis because we do not model how much a firm uses its abatement equipment.
-Adding the operating costs to the installation costs does not change the results in this section.
-Hence we exclude the operating costs here for consistency.
-See Online Appendix D.2 for more details.}
-
-%We do not include the annual {operating costs} in our analysis because, on average, the ratio of operating costs of the treatment equipment to annual production value is about 1.5\%.
-Furthermore, the median of this ratio is less than 0.5\%, suggesting that operating costs are almost negligible for more than 50\% of firms.
-Therefore, operating costs alone are unlikely to affect a firm's decision to adopt treatment technology.
-Actually, adding the operating costs into the installation costs does not change the results in this section.
-In practice, operating costs could affect how much a firm uses the abatement equipment though.
-Since we do not model this intensive margin in our theory, we exclude the operating costs here for consistency.
-See Online Appendix D.1 for more details.}
+Broadly speaking, physical technology corresponds to the \textit{Preliminary} and \textit{Primary} treatment in the U.S., while chemical and biological technologies correspond to the \textit{Secondary} and \textit{Tertiary} treatment.} In sum, we are left with three broad categories of technologies.
 
 To illustrate the difference in technology adoption by firms of different sizes, we use the Paper and Paper Products industry as an example.\footnote{We focus on one industry because of the potential heterogeneity in production processes across industries.} Table \ref{tab:techeffi} shows the mean abatement efficiency, median installation costs, and median output of firms that adopt these technologies, where the {abatement efficiency} is defined as one minus the ratio of {emitted COD} to {generated COD}.\footnote{Online Appendix D.2 provides more details.}
-%To show the difference in the technologies adopted by firms of different size, we use the Paper and Paper Products industry as an example.
-Here we use one industry as an example because we would like to control for the potential heterogeneities in production processes across industries.
-Table \ref{tab:techeffi} shows the mean processing efficiency, median installation costs, and median sales of firms that adopt these technologies.
-We proximate for {processing efficiency} by using one minus the ratio of {emitted COD} to {generated COD}.\footnote{Online Appendix D.2 presents more details.
-Also we would like to stress again that our data contain both emitted and generated quantity of pollutants, see Online Appendix A.1 for details.} We normalize both the median installation costs of physical technologies and the median sales of firms using physical technologies to 100.
 \begin{table}[t]
@@
 \centering
-\begin{threeparttable}
 \caption{Firm Size and Treatment Technologies}
-\begin{tabular}{p{50pt} >{\centering\arraybackslash}p{70pt} >{\centering\arraybackslash}p{60pt} >{\centering\arraybackslash}p{60pt} >{\centering\arraybackslash}p{70pt}} %>{\centering\arraybackslash}p{80pt}}%{lcccc}{p{45pt} >{\centering\arraybackslash}p{40pt} >{\centering\arraybackslash}p{40pt} >{\centering\arraybackslash}p{40pt} >{\centering\arraybackslash}p{40pt} >{\centering\arraybackslash}p{80pt}}
-%{>{\centering\arraybackslash}p{45pt}>{\centering\arraybackslash}p{40pt}>{\centering\arraybackslash}p{40pt}>{\centering\arraybackslash}p{40pt}
-%>{\centering\arraybackslash}p{40pt}>{\centering\arraybackslash}p{80pt}}
+\begin{tabular}{lcccc}
     \hline \hline
-    Technology  & Mean Efficiency & Adoption Rate & Median Costs\tnote{a} & Median Output\tnote{b} \\
-    \midrule
+    Technology  & Mean Efficiency & Adoption Rate & Median Costs & Median Output \\
+    \hline
     Physical    & 63.37\%         & 25.89\%       & 100                   & 100                       \\
@@
     Biological  & 80.90\%         & 38.60\%       & 923                   & 500                       \\
-    \bottomrule
+    \hline
 \end{tabular}
 \label{tab:techeffi}
+\begin{tablenotes}[Source]
+     NGSPS. 
+\end{tablenotes}
 \begin{tablenotes}
-     \footnotesize{
-     \item[$\dagger$]
-     Data Source: NGSPS. The numbers reported are for the Paper and Paper Products (C22) industry. Abatement efficiency is defined as $1 - \text{COD Emitted}/\text{COD Generated}$.
-     \item[a,b]
-     The median installation costs of physical technologies and median output of firms that adopt them are normalized to 100.}
+     The numbers reported are for the Paper and Paper Products (C22) industry.
+Abatement efficiency is defined as $1 - \text{COD Emitted}/\text{COD Generated}$.
+The median installation costs of physical technologies and median output of firms that adopt them are normalized to 100.
 \end{tablenotes}
-\end{threeparttable}
 \end{table}
@@
 As a result, small firms lack the profit margins needed to take advantage of these increasing returns to scale, while large firms are more likely to adopt cleaner technologies.
-%We find that, on average, biological equipment is 17 percentage points more efficient than physical equipment, but its installation costs are also 11 times more expensive.
-Further, the sales of the firms using biological technologies are about 8 times those of firms with physical technologies.
-This evidence points to increasing returns to scale of clean technologies, indicating that small firms lack the profit margins needed to take advantage of the returns to scale imbedded in biological technologies, whereas large firms are more likely to adopt these more advanced technologies.
 
@@
 \begin{equation*}
-%     y_i = \underset{(0.04)}{0.23} + \underset{(0.001)}{0.05} \times \log (\text{Output}_i) + \vec{X_s} \gvec{\upgamma}_1 + \vec{X_p} \gvec{\upgamma}_2 + \vec{X_o} \gvec{\upgamma}_3 + \epsilon_i,
-    y_i = \underset{(0.04)}{0.23} + \underset{(0.001)}{0.05} \times \log (\text{Output}_i) + \vec{X} \gvec{\upgamma} + \epsilon_i,
-%\label{eq:poolols}
+    y_i = \underset{(0.04)}{0.23} + \underset{(0.001)}{0.05} \times \log (\text{Output}_i) + \vec{X} \vec{\gamma} + \epsilon_i,
 \end{equation*}
@@
 
-%\begin{table}[t]
-%\footnotesize
-%\centering
-%\begin{threeparttable}
-%\caption{Treatment Efficiencies and Adoption Rates}
-%\begin{tabular}{p{45pt} >{\centering\arraybackslash}p{40pt} >{\centering\arraybackslash}p{40pt} >{\centering\arraybackslash}p{40pt} >{\centering\arraybackslash}p{40pt} >{\centering\arraybackslash}p{80pt}}
-%%{>{\centering\arraybackslash}p{45pt}>{\centering\arraybackslash}p{40pt}>{\centering\arraybackslash}p{40pt}>{\centering\arraybackslash}p{40pt}
-%%>{\centering\arraybackslash}p{40pt}>{\centering\arraybackslash}p{80pt}}
-%    \hline \hline
-%    Technology  & 25\%      & Median    & 75\%      & Mean      & Adoption Rates \\
-%    \midrule
-%    Physical    & 39.54\%   & 77.81\%   & 87.83\%   & 63.37\%   & 25.79\%        \\
-%    Chemical    & 74.96\%   & 81.29\%   & 86.78\%   & 69.77\%   & 34.50\%        \\
-%    Biological  & 78.87\%   & 86.77\%   & 91.27\%   & 80.90\%   & 39.71\%        \\
-%    \bottomrule
-%\end{tabular}
-%\label{tab:techeffi}
-%\begin{tablenotes}
-%     \footnotesize{
-%     \item[$\dagger$]
-%     Note: The numbers reported are for the Paper and Paper Product (C22) industry. Treatment Efficiencies is defined as $1 - \text{COD Emitted}/\text{COD Generated}$.}
-%\end{tablenotes}
-%\end{threeparttable}
-%\end{table}
-%The {designed processing capacity} (in tons) and {actual installation costs} (in 2007 CNY) can be retrieved directly from the data.
-We calculate the average processing cost by dividing the installation cost with capacity.
-In Figure \ref{fig:techdiff}, in clockwise order we plot the density functions of processing capacity, installation costs, total value of industrial output, and average processing cost by technology type.
-For all panels, log-scale is used in the horizontal axes.
-%\begin{figure}[ht]
-%    \begin{center}
-%    \includegraphics[width=0.4\textwidth]{D:/PaperDrafts/Pollution/R_Implementation/abate_cap.pdf}%
-%    \includegraphics[width=0.4\textwidth]{D:/PaperDrafts/Pollution/R_Implementation/abate_inv.pdf} \\
-%    \includegraphics[width=0.4\textwidth]{D:/PaperDrafts/Pollution/R_Implementation/abate_unit.pdf}
-%    \includegraphics[width=0.4\textwidth]{D:/PaperDrafts/Pollution/R_Implementation/abate_prod.pdf}
-%    \caption{Technical Features of Different Treatment Technologies}
-%    \floatfoot{Source: National General Survey of Pollution Sources. In all panels, the horizontal axes are in log-scale.}
-%    \label{fig:techdiff}
-%    \end{center}
-%\end{figure}
-%Broadly speaking, biological technologies have the {best} processing efficiency, the {largest} processing capacity, the {highest} installation costs, but the {lowest} average processing cost.
-Therefore, although biological technologies are more advanced in terms of processing capacity and efficiency, they are also more costly.
-Combined with the lower average processing cost that is displayed by the biological technologies, the evidence points to increasing returns to scale of the clean technologies.
-In fact, in the bottom-right panel, we find that the clean technologies are more likely to be installed by larger firms.
-%For example, the mean (median) processing efficiency of biological technologies is 17\% (10\%) higher than the physical technologies.
-%The density functions of processing capacity, installation costs and production scale for physical, chemical and biological equipments order from left to right while those of the unit capacity costs order from right to left.
-%It indicates that small firms lack the profit margins that are needed to take advantage of the increasing returns to scale exhibited by biological technologies, while at the same time, large firms are more likely to adopt these more advanced technologies.
-%This could also be seen by calculating the ratio of the \textit{summed} value of treatment equipments to the \textit{summed} value of production using firms of different scales.
-While this ratio is equal to 18\% when only firms with production level below the median are included, the number decreases dramatically to 4\% when up to 95\% firms are included which suggests strongly for the existence of fixed costs.
-
-%\textit{Environmentally Friendly Production Technology.---}Note that the above results all relate to end-of-pipe treatment technologies; we have ignored those factors that could lead to less generation of COD.
-Indeed,
 \textit{Emissions Generated During Production.---}Another reason behind the negative correlation between pollution intensity and firm size is that large firms also generate less COD per output during the production stage.
@@
 \begin{align}
-%\label{eq:poolols_physical}
-%    \text{Physical:}   \quad \log (\text{COD}_i) &= \underset{(0.40)}{-3.50} + \underset{(0.01)}{0.58} \times \log (\text{Output}_i) + \vec{X_s} \gvec{\upgamma}_1 + \vec{X_p} \gvec{\upgamma}_2 + \vec{X_o} \gvec{\upgamma}_3 + %%\varepsilon_i \\
-%\label{eq:poolols_chemical}
-%    \text{Chemical:}   \quad \log (\text{COD}_i) &= \underset{(0.49)}{-4.59} + \underset{(0.01)}{0.77} \times \log (\text{Output}_i) + \vec{X_s} \gvec{\upgamma}_1 + \vec{X_p} \gvec{\upgamma}_2 + \vec{X_o} \gvec{\upgamma}_3 + %\varepsilon_i \\
-%\label{eq:poolols_biological}
-%    \text{Biological:} \quad \log (\text{COD}_i) &= \underset{(0.20)}{-4.37} + \underset{(0.01)}{0.67} \times \log (\text{Output}_i) + \vec{X_s} \gvec{\upgamma}_1 + \vec{X_p} \gvec{\upgamma}_2 + \vec{X_o} \gvec{\upgamma}_3 +\varepsilon_i, \\
-%\label{eq:poolols_others}
-%    \text{Others:} \quad \log (\text{COD}_i) &= \underset{(0.31)}{-3.41} + \underset{(0.01)}{0.64} \times \log (\text{Output}_i) + \vec{X_s} \gvec{\upgamma}_1 + \vec{X_p} \gvec{\upgamma}_2 + \vec{X_o} \gvec{\upgamma}_3 +\varepsilon_i,
 \label{eq:poolols_biological}
-    \text{Biological:} \quad \log (\text{COD}_i) &= \underset{(0.20)}{-4.37} + \underset{(0.01)}{0.67} \times \log (\text{Output}_i) + \vec{X} \gvec{\upgamma} + \varepsilon_i, \\
+    \text{Biological:} \quad \log (\text{COD}_i) &= \underset{(0.20)}{-4.37} + \underset{(0.01)}{0.67} \times \log (\text{Output}_i) + \vec{X} \vec{\gamma} + \varepsilon_i, \\
 \label{eq:poolols_others}
-    \text{Others:} \quad \log (\text{COD}_i) &= \underset{(0.31)}{-3.41} + \underset{(0.01)}{0.64} \times \log (\text{Output}_i) + \vec{X} \gvec{\upgamma} + X_e \gamma_e + \varepsilon_i,
+    \text{Others:} \quad \log (\text{COD}_i) &= \underset{(0.31)}{-3.41} + \underset{(0.01)}{0.64} \times \log (\text{Output}_i) + \vec{X} \vec{\gamma} + X_e \gamma_e + \varepsilon_i,
 \end{align}
@@
 
-Such within group negative correlations could be because that larger firms use \emph{cleaner} or \emph{fewer} inputs to produce the same amount of ouput.
+Such within group negative correlations could be because that larger firms use \textit{cleaner} or \textit{fewer} inputs to produce the same amount of output.
 For one example, the paper pulp industry uses two different types of inputs: bagasse and wood.
-While bagasse, which generates 140--180 kg COD per ton, is mostly used by firms with an annual production of {\color{black}less} than 100 kilotons, wood, which generates 30--55 kg COD per ton, is mostly used by firms with an annual production of {\color{black}more} than 100 kilotons.\footnote{See the \textit{Handbook of Emission Coefficients} published by the \textit{Chinese Academy of Sciences}.} As another example, \citet{Bloometal:2010} find that better managed firms use less energy to produce the same amount of output in the U.K.
+While bagasse, which generates 140--180 kg COD per ton, is mostly used by firms with an annual production of less than 100 kilotons, wood, which generates 30--55 kg COD per ton, is mostly used by firms with an annual production of more than 100 kilotons.\footnote{See the \textit{Handbook of Emission Coefficients} published by the \textit{Chinese Academy of Sciences}.} As another example, \citet{Bloometal:2010} find that better managed firms use less energy to produce the same amount of output in the U.K.
 Unfortunately, we cannot test these hypotheses directly using our data.
 Instead, we focus on firms' decisions to adopt treatment technologies, and model the emissions reduction during the production stage in a reduced-form way based on Equations (\ref{eq:poolols_biological}) and (\ref{eq:poolols_others}).
-
-%Such within group relationship could be because that larger firms use environmentally friendlier production technologies, sell products with a higher mark-up, or produce products that are technologically less polluting.
-An example from the \textit{Handbook of Emission Coefficients} published by the \textit{Chinese Academy of Sciences} is as follows.
-The paper pulp manufacturing use two different types of inputs: bagasse and wood.
-While bagasse, which generates 140--180 kg COD per ton, is mostly used by firms with an annual production of {\color{black}less} than 100 k-tons, wood, which generates 30--55 kg COD per ton, is mostly used by firms with an annual production of {\color{black}more} than 100 k-tons.
-Alternatively, it could also be that more productive firms simply use less resource to produce [\citet{Bloometal:2010} and \citet{ShapiroWalker:2015}].
-Unfortunately, we cannot test these hypotheses directly with our data.
-Therefore, in this study, we focus on firms' decisions to adopt treatment equipment and model the intensity reduction during the production stage by using the reduced-form characterization of (\ref{eq:poolols_dirty}) and (\ref{eq:poolols_clean}).
 
@@
 
-%The negative correlation between pollution intensity and production scale implies that, {ceteris paribus}, the shares of total output by large and small firms could influence aggregate industrial pollution markedly.
-An important task then is to understand the firm size distribution in China.
-To gain some intuitions, we compare the firm size distribution in China with that in the United States.
-We choose the United States as the benchmark because the U.S.
-economy is relatively distortion-free compared with other economies, and China and the United States are both large economies with complete sets of industrial sectors.
-Naturally, firm size in the United States and China differs for many reasons.
-Yet we do not intend to answer why they are different in this paper.
-The primary purpose of this section is to motivate the investigation of size-dependent distortions that disproportionately affect large firms.
-
 Since the SUSB does not report information on output, we focus on the shares of employment accounted for by firms of different sizes, since firm-level employment is strongly correlated with output.
@@
 Census Bureau, respectively.
-%The results presented in this section are from matching at the disaggregated level (four-digit GB with six-digit NAICS).\footnote{Matching at a more aggregated level (two-digit GB with three-digit NAICS) yields similar results.}
-
 \begin{figure}[t]
     \begin{center}
-%    \includegraphics[width=0.45\textwidth]{D:/PaperDrafts/Pollution/R_Implementation/paperES_R.pdf}%
-%    \includegraphics[width=0.45\textwidth]{D:/PaperDrafts/Pollution/R_Implementation/agriES_R.pdf} \\
-%    \includegraphics[width=0.45\textwidth]{D:/PaperDrafts/Pollution/R_Implementation/textileES_R.pdf}
-%    \includegraphics[width=0.45\textwidth]{D:/PaperDrafts/Pollution/R_Implementation/chemmatES_R.pdf} \\
     \includegraphics[width=0.45\textwidth]{./Figures/poolES_R_1.pdf}
     \includegraphics[width=0.45\textwidth]{./Figures/allES_R_1.pdf}
-    %\vspace{-1em}
     \caption{Employment Distributions}
-    \floatfoot{Sources: CNEC and SUSB.}
+    \begin{figurenotes}[Sources]
+        CNEC and SUSB.
+    \end{figurenotes}
     \label{fig:es}
@@
 
-%\begin{figure}[htbp]
-%    \begin{center}
-%    \includegraphics[width=0.45\textwidth]{D:/PaperDrafts/Pollution/R_Implementation/paperdist_R.pdf}%
-%    \includegraphics[width=0.45\textwidth]{D:/PaperDrafts/Pollution/R_Implementation/agridist_R.pdf} \\
-%    \includegraphics[width=0.45\textwidth]{D:/PaperDrafts/Pollution/R_Implementation/textiledist_R.pdf}
-%    \includegraphics[width=0.45\textwidth]{D:/PaperDrafts/Pollution/R_Implementation/chemmatdist_R.pdf} \\
-%    \includegraphics[width=0.45\textwidth]{D:/PaperDrafts/Pollution/R_Implementation/beverdist_R.pdf}
-%    \includegraphics[width=0.45\textwidth]{D:/PaperDrafts/Pollution/R_Implementation/pooldist_R.pdf}
-%    %\vspace{-1em}
-%    \caption{Firm Size Distribution}
-%    %\floatfoot{Source: China National Economic Census and the Statistics of U.S Businesses}
-%    \label{fig:dist}
-%    \end{center}
-%\end{figure}
-
-The left panel of Figure \ref{fig:es} depicts the firm size distribution for the top five polluting industries pooled together. %\footnote{Online Appendix E explains the calculation.}
+The left panel of Figure \ref{fig:es} depicts the firm size distribution for the top five polluting industries pooled together.
 We find that approximately 70\% of employment in the United States is accounted for by firms with 400+ employees, while in China the number is only 20\%.\footnote{In Online Appendix E, we compare the firm size distributions between China and the U.S.
@@
 We find that while there is substantial heterogeneity across individual industries, large firms in China account for a much smaller employment shares than those in the U.S.
-for each industry.} %\footnote{Some readers may concern that the large difference of population size between the United States and China could drive the results.
-However, as shown in \citet{BentoRestuccia:2016}, there is no systematic relationship between average firm size and population size.
-In addition, because China has a much larger population size, the difference in population size between the two countries is more likely to make our case stronger.}
+for each industry.}
 Compared with the U.S., a much larger share of production is carried out by small and medium-sized firms in China.
-%This implies that could be a candidate for explaining the high industrial pollution emissions in China.
-%\footnote{These results are consistent with those of \citet{WangWhalley:2014}, who compare the manufacturing concentration ratios (the share of market occupied by the largest firms) for China and the United States.
-According to Table 1 in their paper, the ratios of the concentration indicators of the United States over China for the top five polluting industries are higher than the {overall average}, which suggests that in polluting industries, large firms in the United States take a larger share of the markets.}
 From the right panel of Figure \ref{fig:es}, we find a similar pattern for the whole manufacturing sector.
-
-%\subsection{Size Distribution and Aggregate Pollution}
 
@@
 Therefore, we construct an employment--output relationship from a linear regression using the CNEC data.\footnote{There are different methods to construct the employment--output relationship using the CNEC data, and all of them provide similar results.
-See Online Appendix F for details.} %We use CNEC to overcome this problem.
-There are many ways to construct the employment-production relationship using CNEC, and each method has its own advantages and disadvantages.
-In this section, we report results where the employment-production relationship is constructed by linear regression.
-Calculation using alternative methods gives similar results.
-We leave the details of these alternative methods in Appendix A.
-
-%\textit{An Accounting Exercise.---}To see how the firm size distribution affects aggregate pollution quantitatively, we conduct an accounting exercise in which, for the pooled polluting industries in China, we fix total output, but replace the employment distribution with that from the United States in order to calculate the implied level of average pollution intensity by using the firm size--intensity relationship estimated in Section \rom{1}.B.\footnote{We show the results for each of the five industries in Online Appendix F.} This simple exercise is complicated by the fact that the NGSPS only reports firm-level production values but not the number of employees.
-Therefore, we construct the employment--production relationship by using a linear regression with CNEC data.\footnote{There are many ways to construct the employment--production relationship by using CNEC data; however, these alternative methods all provide similar results.
-See Online Appendix F for details.} %We use CNEC to overcome this problem.
-There are many ways to construct the employment-production relationship using CNEC, and each method has its own advantages and disadvantages.
-In this section, we report results where the employment-production relationship is constructed by linear regression.
-Calculation using alternative methods gives similar results.
-We leave the details of these alternative methods in Appendix A.
+See Online Appendix F for details.}
 
@@
 
-%By doing so, we calculate that on average, for the top five polluting industries, the effect of changing the firm size distribution reduces emissions to 83\% of the original level.
-Changing the firm size distributions of these five industries while keeping those of all the other industries untouched leads to a reduction in total emissions of about 17\%.
-Although the exercise here is a crude approximation, it nevertheless shows that the firm size distribution can have a significant impact on aggregate industrial pollution.
-%The numbers reported in Table \ref{tab:accounting} are the ratio of the aggregate pollution produced with the U.S. employment share distribution over that with the original Chinese distribution.
-%\begin{table}[t]
-%\footnotesize
-%\centering
-%\begin{threeparttable}
-%\caption{Size Distribution on Pollution}
-%\begin{tabular}{lccccccc}
-%    \hline \hline
-%                        & Paper  & Agricultural Food   & Textiles    & Chemical Materials    & Beverages        & Average  \\
-%    \midrule
-%    Average Intensity   & 43.5\% & 61.1\%              & 97.5\%      & 101.2\%               & 89.0\%           & 67.0\% \\
-%    \bottomrule
-%\end{tabular}
-%\begin{tablenotes}
-%     \footnotesize{
-%     \item[$\dagger$]
-%     Note: The numbers reported are aggregate pollution from the artificial U.S.
-production structure as a percentage of that of China.
-Column 6 (``Average'') calculates the weighted average of these ratios by using the percentage contributions in row one of Table \ref{tab:top5summary} as the weights.}
-%\end{tablenotes}
-%\label{tab:accounting}
-%\end{threeparttable}
-%\end{table}
-%These results imply that by changing the employment share distribution to that of the United States, while keeping production at the same level, aggregate emissions in the Paper and Paper Products industry reduce to 43.5\% of the original level.
-On average, for the top five polluting industries, the effect of changing the firm size distribution reduces emissions to 67\% of the original level.
-The average is calculated by using the relative pollution levels of each industry as the weights, which is the first row of Table [].
-%Changing the firm size distributions of these five industries while keeping those of all the other industries untouched leads to a reduction in total emissions of about 25.5\%.
-
 \section{The Model}
-
-%The accounting exercise presented in the last section has several limitations.
-First, aggregate output is fixed.
-Indeed, when the size distribution changes, although pollution intensity decreases, aggregate pollution may increase as a result of the larger increase in aggregate output.
-In the language of scale, composition, and technique decomposition commonly used in the environmental literature [\citet{CopelandTaylor:2004} and \citet{Levinson:2009}], the accounting exercise evaluates only the technique effect, while instead we would like to consider the trade-off between scale and technique effects.
-Second, the firm size distribution is mechanically changed to that in the United States.
-From the accounting exercise alone, the factors that drive the difference between the firm size distribution of China and that of the United States remain unclear.
-We also do not know whether the implied employment distribution will in fact become that of the United States.
-Third, the relationship between firm size and emissions intensity is taken as exogenous and invariant.
-However, changes in the factors that affect the employment distribution may also influence the technology choices of firms, which makes the firm size--intensity relationship endogenous.
-Therefore, to better evaluate the environmental consequences of distortions to firm size, we need a model that (i) contains economic factors affecting both aggregate output and pollution, (ii) reveals which factors affect firm size and how, and (iii) explains the firm size--intensity relationship.
 
@@
 Throughout, we refer to the sectors as polluting and non-polluting, and technologies as dirty and clean.
-In the context of our model, the polluting sector is mapped to the top five polluting industries and the non-polluting sector to the rest of the manufacturing sector, while clean and dirty technologies are interpreted as biological and other (physical plus chemical) equipments as specified in Section \rom{1}.B.
-
-%The model allows us to assess structurally the scale, composition and technique channels, through which counterfactual policies affect aggregate pollution.
-Moreover, the model allow us to further decompose the technique channel into: within sector reallocation across firms, and the change in clean technology adoption.
-%For this purpose, we consider a two-sector neoclassical growth model with heterogeneous firms within each sector.
-We refer to the two sectors as polluting and non-polluting sector, which corresponds respectively to the five polluting industries and the rest of the manufacturing sector.
-Both sectors feature size-dependent distortions, while firms in the polluting sector face in addition imperfect environmental regulation and endogenous treatment technology choice.
-We assume two types of treatment technologies: dirty and clean.
-In the context of our model, these two technologies are interpreted as the {physical} and {biological} technology classifications discussed in Section \rom{2}.B.
+In the context of our model, the polluting sector is mapped to the top five polluting industries and the non-polluting sector to the rest of the manufacturing sector, while clean and dirty technologies are interpreted as biological and other (physical plus chemical) equipments as specified in Section I.B.
 
@@
 
-\textit{Household.}---%Assuming that there is perfect risk sharing within the household, the preference of the household could then be characterized by
-%\begin{equation}
-%    \sum_{t=0}^{\infty} \beta^t U(C_t)
-%\end{equation}
-%where $C_t$ is the consumption at time $t$ and $\beta$ is the discount factor.
-There is a representative household with a continuum of members that maximizes the life-time utility $\sum_{t=0}^{\infty} \beta^t U(C_t)$,
-%\begin{equation*}
-%    \sum_{t=0}^{\infty} \beta^t U(C_t)
-%\end{equation*}
-where $C_t$ is the consumption at time $t$ and $\beta$ is the discount factor.
+\textit{Household.}---There is a representative household with a continuum of members that maximizes the life-time utility $\sum_{t=0}^{\infty} \beta^t U(C_t)$, where $C_t$ is the consumption at time $t$ and $\beta$ is the discount factor.
 
@@
 
-%There is a representative household with a continuum of members.
-Each household member is endowed with $z$ units of managerial talent, $z \sim G(z)$ with support $Z \triangleq [0,\overline{z}]$, where $G(z)$ is the cumulative distribution function and $g(z)$ is the probability density function.
-We assume that the support and distribution of $z$ are exogenous, and $z$ is fixed once drawn.
-Household members face an occupational choice between {worker} and {entrepreneur}.
-A worker supplies one unit of labor inelastically in exchange for wage income, whereas an entrepreneur rents capital and labor to run a neoclassical firm and earns profits.
-In the latter case, $z$ is also interpreted as firm-level TFP and with the understanding from the readers, we take the liberty to the term managerial talent and firm-level TFP interchangeably depending on whether we emphasize the household member or the firm.
-
-%We assume that the managerial talent $z$ is sector specific in the sense that a share $\mu$ of the members can only choose to open firms in the polluting sector, while the rest $1-\mu$ have to enter the non-polluting sector.
-Workers are perfect mobile between sectors.
-Notice that by the law of large numbers, the ex ante distributions of $z$ in the two sectors are both $G(z)$.
-This is inspired by the fact that the firm size distributions in the polluting and non-polluting sectors are very similar (Figure \ref{fig:es}).
-We assume that the goods produced by the two sectors are perfect substitutes and are the numeraire.%\footnote{In Online Appendix J, we consider the case where there is a final good producer that aggregates the two intermediate goods following a CES production function.
-Because in the two quantitative experiments we study in the main text, there is very little cross-sector reallocation of production, the quantitative results from a CES setup are very similar.
-As a result, for simplicity, we choose the perfect substitute setup.} Let $R$ and $W$ be the capital and labor rental price respectively.
-
 \textit{Firms.}---The production functions in the two sectors take the same form.
@@
 Due to diminishing returns to scale at the firm level, a non-degenerate distribution of firm size can be supported, and firms earn positive profits as the payment to managerial talent $z$.
-%\footnote{We build our model based on \citet{Lucas:1978b}.
-However, all the qualitative properties of our model remain valid if instead we use a model with monopolistic competition [\citet{Melitz:2003}] since the two models are isomorphic.
-In the Melitz model, the decreasing returns to scale come from the concavity of the utility function.
-Similarly, firms in the Melitz model earn profits because of the monopolistic competition market structure, while the profits in our model are the factor payment to managerial talent $z$.
-We show the math details in Appendix G.3 [see also Appendix \rom{1} of \citet{HsiehKlenow:2009}].}
 As is typically the case with studies that follow \citet{Lucas:1978b}, managerial talent $z$ is the only source of firm-level TFP in this model.
@@
 Total emissions $e = \mathcal{E}(i,y)$ depend on the amount of output $y$, and the pollution treatment technology firms use, with $i = 1$ refers to the {clean} technology and $i = 0$ the dirty technology.
-Based on the empirical findings from Section \rom{1}, we assume that
+Based on the empirical findings from Section I, we assume that
 \begin{equation}
@@
 \end{equation}
-where $\psi_1^i<0$. This formulation indicates that larger firms emit fewer pollutants per unit of output, which is consistent with our empirical findings in Section \rom{1}.B.
+where $\psi_1^i<0$. This formulation indicates that larger firms emit fewer pollutants per unit of output, which is consistent with our empirical findings in Section I.B.
 
 Adopting the clean technology incurs fixed cost $R k_E$.
-%\footnote{Adding the variable costs of adopting the clean technology to our model will not change our quantitative results fundamentally.
-Specifically, the introduction of the variable costs would lead to an increase in calibrated value of $k_E$ but would not lead to materials changes in our quantitative results.See more related discussions in Online Appendix D.2.} %Furthermore, we assume that firms only invest in one treatment technology.
-We make this assumption because in the data only 7\% firms have more than one set of treatment equipment, and only 2\% have more than two sets.}
 We assume that the environmental authority punishes firms for using the dirty technology.
@@
 To the extent that firms' profits increase with firm size, we implicitly capture the size-dependency of the environmental regulations, in the sense that larger firms are usually monitored and inspected more closely.
-A key prediction from these assumptions is that, only firms above a certain size threshold would choose the clean technology, which is qualitatively consistent with our empirical findings on technology adoption in Section \rom{1}.B.\footnote{In Online Appendix D.2, we provide further evidence that the ratio of a firm's expenditures on treatment technology to firm output decreases with firm size, which supports the fixed cost assumption.}
-
-%Installing the clean equipment incurs fixed cost $R k_E$, where we assume that the equipment is also rented from the market, just as the production capital $k$.\footnote{We choose to model the installation costs as one-time fixed costs as opposed to fixed costs plus operating costs or size-dependent fixed costs because the latter two are not supported by the empirical evidence.
-We also assume that the fixed cost is only associated with the clean technology.
-Qualitatively, assuming that the dirty technology also requires a fixed cost does not affect the property of the model.
-This is equivalent to a decrease in the cost of the clean technology, since what matters for the firm's decision is the difference between the two costs.
-See Online Appendix D.2 for further details.} %Furthermore, we assume that firms only invest in one treatment technology.
-We make this assumption because in the data only 7\% firms have more than one set of treatment equipment, and only 2\% have more than two sets.}
-%We assume that the environmental authority penalizes firms for using dirty technology.
-We take a similar approach as \citet{ShapiroWalker:2015} to capture the regulations in a parsimonious way by modeling the penalty as a proportion of $\xi$ of the total profits of these firms.\footnote{In practice, China employs both economic incentives and command-and-control instruments in its current industrial pollution management and control system.
-A pollution levy system requires that firms pay levies according to how much pollutants they discharge.
-In addition, local authorities penalize firms for fraudulent report of pollutants emissions and temporarily suspend firms using obsolete treatment technology from production under some occasions.
-\citet{Lin:2013} provides a detailed description of China's current environmental regulations.
-We present a short summary in the Online Appendix D.3 based on his work.
-The $\xi$ is used to summarize all these regulations jointly.} The penalty is distributed back to the household as lump-sum transfers.
-
-%As a result, the core trade-off of firm's technology adoption decision is between the installation cost $R k_E$ and the profit loss.
-Because firm's profits and size increase with its productivity $z$, by assuming a constant fraction $\xi$, we are implicitly capturing the fact that environmental regulation is also size-dependent, that is large firms are being watched more closely.
-Also since our model is deterministic and firms are risk neutral, $\xi$ captures the deterrence effects of the regulations as well.
-
-%\textit{Regulators.}---We assume that the environmental authority monitors the adoption of the clean technology by firms with probability $p$.
-When a firm using the dirty technology is inspected, we assume that a proportion $\xi$ of its total profits is confiscated by the regulating agency.
-As a result, firms using the dirty technology lose a proportion of $p\xi$ of their total profits.
-The confiscated profits are distributed to the household as lump-sum transfers, meaning that they do not affect the decision problem of household members.
-This reduced-form way of modeling monitoring policy could, for instance, be rationalized by a mixed strategy Nash equilibrium of a behind-the-scenes ``monitoring game.''
-%
-%The current industrial pollution management and control system in China consists of {economic incentives} and {command-and-control instruments}.\footnote{See Chapter 5 of \citet{WorldBankChinaPollution:2001} for a detailed description.} The pollution levy system is the most widely used economic instrument in China.
-However, it places limited constraints on the emissions of firms because the penalty imposed is very low.
-Firms only have to pay for the emissions that go {beyond} the national standard.
-Moreover, these emissions are {self-reported} and the truthfulness of the reported emissions is imperfectly examined by the regulators.\footnote{This may be a common problem for developing countries.
-For example, \citet{Dufloetal:2013} conduct a field experiment in India and find that the emissions reporting system is largely corrupted, with auditors systematically reporting plant emissions just below the standard.} Further, for firms that discharge multiple pollutants and when the levels of more than one of the pollutants are above the national standards, firms only have to pay for the one that leads to the highest penalty.
-We calculate from the CNEC the pollution fees levied on firms as a proportion of total labor compensation.
-We find that for firms with strictly positive emissions fees, these fees only account for 0.06\% (median) and 0.3\% (mean) of the labor compensation.
-%
-%Therefore, in practice, environmental agencies rely mostly on command-and-control instruments.
-To implement the regulation, field inspections are conducted by the staff of local environmental agencies.
-%Using data from the Environmental Protection Bureau in Zhenjiang, \citet{Dasguptaetal:2001} showed that at the firm level, compared to variations in pollution levies, variations in the number of field inspections better explains the variations in pollution levels.
-%Field staff typically check the type of treatment equipment that firms have installed and test the emissions intensity of major pollutants.
-Firms found to be at fault are usually suspended from production until the issues are resolved.\footnote{See \citet{Dasguptaetal:2001} for a case study of Zhenjiang.} In our model, the proportion $\xi$ of the profits confiscated is used to approximate these costs.
-Since, according to Table \ref{tab:techeffi}, the treatment technology used by firms is highly correlated with pollution intensity, we assume that the regulator in our model checks only treatment technologies.
-Although the local environmental agencies also monitor total emissions, these regulations are usually based on a {provincial-level} aggregation.
-They are thus less relevant to the firm-level decision that we study here.\footnote{Firm inspections in the United States also target the adopted treatment technologies.
-See \citet{BeckerHenderson:2000} and the references therein for more details.}
-%%\footnote{Firm level inspections in the U.S are also targeted mainly on the adopted treatment technologies.
-For example, as is stated in the 1977 Amendment of the Clean Air Act, each July every county in the U.S will be classified as either an {attainment} or a {non-attainment} county according to their overall pollutants emissions level.
-Firms in {non-attainment} counties are subject to substantially stronger environmental regulations.
-For instance, newly established firms in these counties are required to meet the standard of Lowest Achievable Emission Rate (LAER) which demands the installation of the cleanest possible technology supposedly regardless of costs.
-While on the other hand, in {attainment} counties only Best Available Control Technology (BACT) which incorporates cost considerations is required.
-Similarly, existing firms are also subject to stricter regulations on production and end-of-pipe treatment technologies in non-attainment counties than in the attainment counties.
-See \citet{BeckerHenderson:2000} and the references therein for more details.}
-
-%\subsection{Firm-level Distortions}
-%
-%Recent studies of the Chinese economy have described large distortions at both the sector and the firm levels, which negatively affect aggregate productivity and output considerably.\footnote{See \citet{HsiehKlenow:2009}, \citet{Songetal:2011}, \citet{Brandtetal:2013}, and \citet{TombeZhu:2015}, among others.} Following the seminal approach developed by \citet{HsiehKlenow:2009,HsiehKlenow:2014}, we model and estimate firm-level distortions by using variations in the average products of capital and labor across firms.\footnote{Though average factor product dispersion could arise due to dynamic capital adjustment [\citet{Askeretal:2014}], for the case of China, \citet{DavidVenkateswaran:2017} show that dynamic adjustment costs only accounts for about 10\% of the variation in average factor product in the data.
-Naturally, we also cannot separate out variations in average factor product caused by firm-specific characteristics, for instance firm-specific markup or capital share.
-However, we argue that it would require empirical implausible variations of such parameters to generate the patterns of the data we observe.} %An important feature of Cobb-Douglas production function is that the ratio of average factor products to marginal factor products is constant.
-Therefore, the average factor products also provide information on marginal factor products.\footnote{In particular, using the notations later in this section, we can verify that $\partial y/\partial k = \alpha \gamma z^{1-\gamma} k^{\alpha \gamma - 1} l^{(1-\alpha)\gamma} = \alpha \gamma (y/k)$.
-Similarly, we can show that $\partial y/\partial k = (1-\alpha) \gamma (y/l)$.}
-%More specifically, if we let $\tau_{z_i}, \tau_{k_i}$, and $\tau_{l_i}$ be the wedges that firm $i$ faces in the product, capital, and labor markets, respectively, the profit maximization problem of firm $i$ is
-%\begin{equation*}
-%    \pi_i = \max_{k_i,l_i} \left\{ (1-\tau_{z_i}) z_i^{1-\gamma} (k_i^{\alpha} l_i^{1-\alpha})^{\gamma} - (1+\tau_{k_i})Rk_i - (1+\tau_{l_i})W l_i \right\}.
-%\end{equation*}
-%By using the first-order conditions, the firm level average product of capital $\phi_{k_i}$, labor $\phi_{l_i}$, and the capital/labor ratio $\kappa_i$ can be expressed as
-%\begin{align}
-%    \label{eq:phik}
-%    \phi_{k_i} &= \frac{y_i}{k_i} = \frac{(1+\tau_{k_i})R}{\alpha \gamma (1-\tau_{z_i})}, \\
-%    \label{eq:phil}
-%    \phi_{l_i} &= \frac{y_i}{l_i} = \frac{(1+\tau_{l_i})W}{(1-\alpha) \gamma (1-\tau_{z_i})}, \\
-%    \label{eq:kappa}
-%    \kappa_i &= \frac{k_i}{l_i} = \frac{\alpha}{1-\alpha} \cdot \frac{(1+\tau_{l_i})W}{(1+\tau_{k_i})R}.
-%\end{align}
-%The above equations show that in the absence of any distortions ($\tau_{z_i} = \tau_{k_i} = \tau_{l_i} = 0$), $\phi_{k_i}, \phi_{l_i}$, and $\kappa_i$ should be equalized across firms.
-Equations (\ref{eq:phik}) and (\ref{eq:phil}) state that firms that face higher distortions in the capital (labor) and/or product markets demonstrate a higher average product of capital (labor).
-In addition, according to Equation (\ref{eq:kappa}), the capital/labor ratio increases with the {relative} size of labor to the capital market wedge.
-By using firm-level data on total production value, the book value of capital stock, and labor compensation from the CNEC, we calculate $z_i, \phi_{k_i}, \phi_{l_i}$, and $\kappa_i$ for each firm in our sample.
-Anticipating the calibration later, here we set $\gamma = 0.93$.
-Figure \ref{fig:phiklkappa} shows on log scales the scatterplots of $\phi_{k_i}, \phi_{l_i}$, and $\kappa_i$ against firm-level productivity $z_i$ for the Paper and Paper Products industry.
-We plot the Paper industry for demonstration purpose, qualitatively the results for all five polluting industries combined are the same.
-%\begin{figure}[t]
-%    \begin{center}
-%    \includegraphics[width=0.4\textwidth]{D:/PaperDrafts/Pollution/R_Implementation/arpk.pdf}%
-%    \includegraphics[width=0.4\textwidth]{D:/PaperDrafts/Pollution/R_Implementation/arpl.pdf} \\
-%    \includegraphics[width=0.4\textwidth]{D:/PaperDrafts/Pollution/R_Implementation/klratio.pdf}
-%    \caption{Factor and Product Market Distortions}
-%    \floatfoot{Source: CNEC. All panels are plot in log scale. Lines are least square fit.}
-%    \label{fig:phiklkappa}
-%    \end{center}
-%\end{figure}
-%
-%Two patterns emerge from Figure \ref{fig:phiklkappa}.
-First, from the two upper panels, we see that both $\phi_{k_i}$ and $\phi_{l_i}$ are positively correlated with $z_i$, which suggests that more productive firms have higher average products of both capital and labor.
-Expressed in wedges, this means that both $(1+\tau_{k_i})/(1-\tau_{z_i})$ and $(1+\tau_{l_i})/(1-\tau_{z_i})$ are higher for more productive firms.\footnote{Generally speaking, the estimated elasticities of $\phi_k$ and $\phi_l$ to $z$ depend on the value of $\gamma$, since $z$ is calculated for a given $\gamma$.
-For $\gamma = 0.93$ used here, the elasticities of $\phi_k$ and $\phi_l$ to $z$ equal 0.03, which taken at its face value seem well below the estimates in the literature.
-For instance, by using comprehensive micro data, \citet{HsiehKlenow:2014} find that the elasticity is 0.1 for the United States and between 0.5 and 0.6 for India and Mexico.
-By using data from the World Bank's Enterprise Surveys, \citet{BentoRestuccia:2016} find that the elasticities range from 0.22 to 0.74, averaging 0.52.
-However, we argue that this is because in the calibration of our general equilibrium model, as is explained in details in Section \rom{3}, in order that our model generates a wide range of firm size, a value of $\gamma$ that is higher than commonly used in the literature is needed.
-If we assume $\gamma = 0.85$ following \citet{AtkesonKehoe:2005}, then the elasticities of $\phi_k$ and $\phi_l$ to $z$ are both about 0.25, which are quantitatively consistent with those in the literature.
-The value of $\gamma$ used, however, will not affect the qualitative conclusion that large firms are subject to more distortions.}
-%%If we assume $\gamma = 0.85$ following \citet{AtkesonKehoe:2005}, then the elasticities of $\phi_k$ and $\phi_l$ to $z$ are both about 0.25, meaning that doubling firm productivity is associated with a 25\% increase in the average revenue product of factor inputs.\footnote{Generally speaking, the estimated elasticity depends on the value of $\gamma$, since $z$ is calculated for a given $\gamma$.
-However, because we are using a \citet{Lucas:1978b} model, while \citet{HsiehKlenow:2014} and \citet{BentoRestuccia:2016} both use the \citet{Melitz:2003} model, our results are not directly comparable with theirs.
-Yet broadly speaking, our estimates are quantitatively consistent with theirs.
-By using comprehensive micro data, \citet{HsiehKlenow:2014} find that the elasticity is 0.1 for the United States and between 0.5 and 0.6 for India and Mexico.
-By using data from the World Bank's Enterprise Surveys, \citet{BentoRestuccia:2016} find that the elasticities range from 0.22 to 0.74, averaging 0.52.}
-%This could be because more productive firms are subject to higher factor or product market distortions or both.
-Second, from the lower panel, we see that the capital/labor ratio is at best weakly negatively correlated with $z$.
-The least squares estimate of the elasticity is $-$0.0057 and the $R^2$ is only 0.053.
-This finding indicates that the {relative} wedge firms face in the capital and labor markets does not depend strongly on the idiosyncratic productivity of firms, which in the context of our model implies $1+\tau_{k_i} \approx 1+\tau_{l_i}$.\footnote{This also explains the reason why $\phi_{k_i} \approx \phi_{l_i}, \forall i$.} Since we cannot separately identify the three wedges, for simplicity, we assume $\tau_{k_i} = \tau_{l_i} = 0$ and attribute all the variations in the average product of factors to the wedges in the product market $\tau_{z_i}$.
-Whether we assume $\tau_{k_i} = \tau_{l_i} = 0$ or alternatively $\tau_{z_i} = 0$ does not affect our results, but the interpretations need to be changed accordingly.\footnote{For example, we cannot distinguish between the data-generating process we use here and another process where $\tau_{k_i}$ and $\tau_{l_i}$ increase simultaneously, while $\tau_{z_i}$ is equal to zero.
-Moreover, when estimating the elasticity, since $y,k$ and $l$ enter the regression on both sides, when any of the variables are measured with measurement error, such error may drive spurious correlations.
-While we cannot rule out this possibility completely, we argue that this does not seem to be the case here.
-In particular, if $y$ is measured with extreme measurement error, the regression coefficient of $\phi_k$ over $z$ is $1-\gamma$.
-Similarly, if instead $k$ is measured with extreme measurement error, the regression coefficient is $(1-\gamma)/\gamma$.
-We calculate $\phi_{k_i}$ and $z_i$ by using different values of $\gamma$ and the regression coefficients do not vary as predicted by either case.}
-%
-%\begin{figure}[t]
-%    \begin{center}
-%    \includegraphics[width=0.50\textwidth]{D:/PaperDrafts/Pollution/PrelimResults/tauz.eps}
-%    \caption{The Generic Tax Function of $\tau_z$}
-%    \label{fig:tauz}
-%    \end{center}
-%\end{figure}
-%In the spirit of \citet{BentoRestuccia:2016}, we implement these idiosyncratic wedges in the model by positing a generic ``tax'' function that specifies the wedges as a function of a firm's productivity $z$:\footnote{This tax function has a long history in macro-public finance literature, for instance \citet{Benabou:2002}.
-We thank a referee for pointing this out.
-Recent studies that adopt the same tax functions include \citet{AdamopoulosRestuccia:2014}, \citet{HsiehKlenow:2014}, and \citet{Guneretal:2017}.}
-%\begin{equation}
-%    \tau_z = \max \left\{ 0, 1 - \phi_0 z^{\phi_1} \right\}.
-%\label{eq:tax}
-%\end{equation}
-%%From now on, we use $\tau_z$ instead of $\tau_y$ to denote the product market frictions.We assume that the taxes collected are returned to the household as lump-sum transfers.
-%Anticipating the benchmark calibration in the next section, the wedge function specified in Equation (\ref{eq:tax}) is increasing and concave in $z$, with the lower and upper bounds being 0 and 1, respectively.
-The shape of the function captures the size dependency of the product market distortions where the wedges are higher for larger firms.
-The actual tax function used in the quantitative exercises is plotted against log productivity in Figure \ref{fig:tauz}.
-%\footnote{There is one difference between Equation (\ref{eq:tax}) and the tax function used by \citet{AdamopoulosRestuccia:2014}.
-To model the size dependency, in their specification, the authors use an exponential function as opposed to the power function here.
-We choose the power function because it is consistent with the log-linearity of $\phi_k$ ($\phi_l$) and $z$, while the exponential function implies a tax scheme that increases much sharper with respect to productivity than the empirical counterpart for our case.} %We rule out subsidies ($\tau_z < 0$) because $\lim_{z \downarrow 0} \tau_z = -\infty$ which leads to unrealistic solutions.}
-%
-%The idiosyncratic $\tau_z$ is meant to capture implicitly a variety of policies and institutions that allocate factors away from large productive firms.
-For example, this is consistent with the fact that large productive firms face transportation costs, additional management costs, and/or local protectionism and trade barriers that impede the inter-regional flow of goods [\citet{Young:2000}, \citet{HsiehKlenow:2014}, \citet{TombeZhu:2015}, and \citet{Eberhardtetal:2016}].
-It could also be that smaller firms are subject to preferential tax treatment.\footnote{For instance, value added taxes for firms with an annual industrial output value of less than CNY 1 million is 3\%, while firms with a production scale larger than CNY 1 million are subject to a 13\% tax rate.} Some of these examples, for instance transportation costs and management costs, are not exactly the ``distortions'' narrowly defined as inefficiencies from policy interventions.
-Hence a more accurate interpretation of the distortions captured by our model is any factors that prevent firms from reaching their full potentials in a frictionless world.
-We stick to the word \textit{distortion} mainly for convenience.
-From a policy perspective, it would be of great interest to follow the so-called direct approach in \citet{RestucciaRogerson:2013} and study the specific policies and regulations that we observe in the economy.
-We leave this important task to future work.\footnote{\citet{AdamopoulosRestuccia:2014} and \citet{AGpaper} are two recent examples where observable policy distortions are investigated.
-\citet{AdamopoulosRestuccia:2014} study the observable farm-level price distortions while our own work \citet{AGpaper} focus on distortions created by migration and land distribution policies in China.}
+A key prediction from these assumptions is that, only firms above a certain size threshold would choose the clean technology, which is qualitatively consistent with our empirical findings on technology adoption in Section I.B.\footnote{In Online Appendix D.2, we provide further evidence that the ratio of a firm's expenditures on treatment technology to firm output decreases with firm size, which supports the fixed cost assumption.}
 
@@
 \end{equation}
-where the parameter $\phi_0^i$ determines the mean level of the taxes, and the parameter $\phi_1^i$ determines the progressiveness of the taxes.
-When $\phi_1^i<0$, the tax rates are increasing in firm TFP $z$, and the progressiveness of the taxes is decreasing in the value of $\phi_1^i$.\footnote{This tax function has a long history in macro-public finance literature, which dates back to at least \citet{Benabou:2002}.
+where the parameter $\phi_0^i$ determines the mean level of the taxes, and the parameter $\phi_1^i$ determines the progressivity of the taxes.
+When $\phi_1^i<0$, the tax rates are increasing in firm TFP $z$, and the progressivity of the taxes is decreasing in the value of $\phi_1^i$.\footnote{This tax function has a long history in macro-public finance literature, which dates back to at least \citet{Benabou:2002}.
 We thank a referee for pointing this out.
@@
 This can be seen from Figure \ref{fig:apf}, which depicts the geometric average of the average product of labor and capital $(y/k)^\alpha(y/l)^{1-\alpha}$ against firm TFP $z$ for both the polluting and non-polluting sectors.\footnote{To estimate firm TFP and average product of factors, we need to assign the values to the parameter that determines the income share of capital, $\alpha$, and the span-of-control parameter, $\gamma$.
-We take these values from our calibration in Section \rom{3}, which implies that $\alpha = \text{0.54}$ and $\gamma = \text{0.93}$.
+We take these values from our calibration in Section III, which implies that $\alpha = \text{0.54}$ and $\gamma = \text{0.93}$.
 The positive relationship between firm TFP and average product of factors, however, hold for a wide range of values for $\alpha$ and $\gamma$, in addition to the values used here.
@@
     \begin{center}
-%    \includegraphics[width=0.45\textwidth]{D:/PaperDrafts/Pollution/R_Implementation/paperES_R.pdf}%
-%    \includegraphics[width=0.45\textwidth]{D:/PaperDrafts/Pollution/R_Implementation/agriES_R.pdf} \\
-%    \includegraphics[width=0.45\textwidth]{D:/PaperDrafts/Pollution/R_Implementation/textileES_R.pdf}
-%    \includegraphics[width=0.45\textwidth]{D:/PaperDrafts/Pollution/R_Implementation/chemmatES_R.pdf} \\
     \includegraphics[width=0.45\textwidth]{./Figures/apf_pol_weight.pdf}
     \includegraphics[width=0.45\textwidth]{./Figures/apf_npol_weight.pdf}
-    %\vspace{-1em}
     \caption{Average Product of Factors versus Firm Productivity in the Cross-Section}
-    \floatfoot{Source: CNEC. Both variables have been normalized to reflect the relative values to the sectoral averages, which are similar across sectors.}
+    \begin{figurenotes}[Source]
+        CNEC.
+    \end{figurenotes}
+    \begin{figurenotes}
+        Both variables have been normalized to reflect the relative values to the sectoral averages, which are similar across sectors.
+    \end{figurenotes}
     \label{fig:apf}
@@
 
-%Recent studies of the Chinese economy have described large distortions at both the sector and the firm levels, which negatively affect aggregate productivity and output considerably.\footnote{See \citet{HsiehKlenow:2009}, \citet{Songetal:2011}, \citet{Brandtetal:2013}, and \citet{TombeZhu:2015}, among others.}
-%We assume that all firms face an idiosyncratic distortions $\tau_z$ depending on their productivity level.
-In the spirit of \citet{BentoRestuccia:2016}, we implement these idiosyncratic wedges in the model by positing a generic ``tax'' function:\footnote{This tax function has a long history in macro-public finance literature, for instance \citet{Benabou:2002}.
-We thank a referee for pointing this out.
-Recent studies that adopt the same tax functions include \citet{AdamopoulosRestuccia:2014}, \citet{HsiehKlenow:2014}, and \citet{Guneretal:2017}.
-Online Appendix D.1 presents detailed empirical evidence that motivates us using this specification.}\textsuperscript{, }\footnote{The idiosyncratic $\tau_z$ is meant to capture implicitly a variety of policies and institutions that allocate factors away from large productive firms.
-For example, this is consistent with the fact that large productive firms face transportation costs, additional management costs, and/or local protectionism and trade barriers that impede the inter-regional flow of goods [\citet{Young:2000}, \citet{HsiehKlenow:2014}, \citet{TombeZhu:2015}, and \citet{Eberhardtetal:2016}].
-It could also be that smaller firms are subject to preferential tax treatment.
-Some of these examples, for instance transportation costs and management costs, are not exactly the ``distortions'' narrowly defined as inefficiencies from policy interventions.
-Hence a more accurate interpretation of the distortions captured by our model is any factors that prevent firms from reaching their full potentials in a frictionless world.
-We stick to the word \textit{distortion} mainly for convenience.
-From a policy perspective, it would be of great interest to follow the so-called direct approach in \citet{RestucciaRogerson:2013} and study the specific policies and regulations that we observe in the economy.
-We leave this important task to future work.}
-%\begin{equation}
-%    \tau_z = \max \left\{ 0, 1 - \phi_0 z^{\phi_1} \right\}.
-%\label{eq:tax}
-%\end{equation}
-%Following the evidence in the Online Appendix D.1, we assume that the the tax function (\ref{eq:tax}) is the same for both sectors.
-
 Firms in the non-polluting sector solve the standard profit maximization problem:
@@
 Then there exists a threshold $\tilde{z}_d$ such that only firms with TFP higher than $\tilde{z}_d$ would choose clean technology.\footnote{Please see Lemma 2 in Online Appendix G.1 for details.} There also exist two thresholds $\hat{z}_i, i=c,d,$ such that in sector $i$, only members with $z > \hat{z}_i$ choose to be managers.
-
-%The first-order conditions from this problem imply that
-%\begin{equation*}
-%    \pi_1^d(z) = \frac{1-\gamma}{(1-\alpha)\gamma}Wl^d(z)-R k_E.
-%%\label{eq:pi1z}
-%\end{equation*}
-%Note that here treatment equipment $k_E$ cannot be used to produce the final product. This assumption is based on the empirical finding of \citet{ShadbegianGray:2005}.
-%\begin{equation*}
-%    \pi_0^C(z) = (1-\xi) \left[ (1-\tau_z) z^{1-\gamma} (k^{\alpha} n^{1-\alpha})^{\gamma} - Wn - Rk \right],
-%\end{equation*}
-%where the superscript $C$ indicates ``caught.'' If the firm succeeds in evading inspection, the profit function is
-%\begin{equation*}
-%    \pi_0^{E}(z) = (1-\tau_z) z^{1-\gamma} (k^{\alpha} n^{1-\alpha})^{\gamma} - Wn - Rk,
-%\end{equation*}
-%where the superscript $E$ indicates ``evaded.'' Because we assume perfect risk sharing within the household, these entrepreneurs will {not} have precautionary motives and will simply maximize the expected profits over $\pi_0^C$ and $\pi_0^{E}$:
-%\begin{equation*}
-%    \pi_0(z) = \max_{k,n} \left\{ (1-p)\pi_0^{E}(z) + p\pi_0^{C}(z) \right\}.
-%\end{equation*}
-%Some algebra yields
-
-%and the first-order conditions from this problem imply that
-%\begin{equation*}
-%    \pi_1^d(z) = \frac{(1-\gamma)(1 - \xi)}{(1-\alpha)\gamma}Wl^d(z).
-%%\label{eq:pi1z}
-%\end{equation*}
-
-%The standard result from the Lucas model implies that there exist two thresholds $\hat{z}_d$ and $\hat{z}_c$ such that in each sector, all members with $z$ higher than the corresponding thresholds choose to become entrepreneurs.
-In addition, when $\pi_d^0(z)$ and $\pi_d^1(z)$ satisfy single-crossing condition, there also exists a third threshold $\tilde{z}_d$ such that all firms in the polluting sector with TFP higher than $\tilde{z}_d$ use clean technology.
-See Result \ref{prop:friction} in Section \rom{2}.D and Lemma 2 in Online Appendix G.1 for details.
 
@@
 \end{align}
-where $K_t$ is aggregate capital, $\delta$ is the depreciation rate, and $I_t$ is household income, which we specify in detail shortly.%\footnote{We assume here that the household values only consumption and not environmental quality.
-This assumption is innocuous in the competitive equilibrium, since no individual household member has control over aggregate environmental quality.
-However, the assumption does affect the results if a planner's problem is studied or if we want to evaluate the welfare effect of different policies.}
-\footnote{Here we do not explicitly model the household's preference over water quality.
+where $K_t$ is aggregate capital, $\delta$ is the depreciation rate, and $I_t$ is household income, which we specify in detail shortly.\footnote{Here we do not explicitly model the household's preference over water quality.
 Adding water quality to the household's utility function will not change the firm's choices in a competitive equilibrium, as no individual household member has any control over the aggregate environmental quality.
@@
     U'(C_t) = \beta U'(C_{t+1})(1+R_{t+1}-\delta),
-%\label{eq:euler}
-\end{equation*}
-which pins down the equilibrium interest rate.%\footnote{There is no uncertainty at the household level since we assume perfect risk sharing and a continuum of household members which wash out all idiosyncratic uncertainty.
-As a result, on the right hand side of (\ref{eq:euler}) there is no expectation operator.}
+\end{equation*}
+which pins down the equilibrium interest rate.
 
 Household income $I_t$ comes from three sources: wage and interest income, firms' profits, and lump-sum transfers from taxes $\tau_z$ and environmental penalties $\xi$.
-%To characterize $I_t$, we need some additional notation.
-We denote $Z_0 = \{z \in [\hat{z}_t, \overline{z}] | \pi_0(z) \geq \pi_1(z) \}$ as the set of firms operating with the dirty technology and $Z_1 = \{z \in [\hat{z}_t, \overline{z}] | \pi_0(z) < \pi_1(z) \}$ as the set of firms using the clean technology.
-Note that for the intermediate case, where $0 < \hat{z} < \tilde{z} < \overline{z}$, Result \ref{prop:friction} implies $Z_0 = [\hat{z}, \tilde{z})$, and $Z_1 = [\tilde{z}, \overline{z}]$.
-%Since the ``taxes'' are distributed to household as lump-sum transfers, in the budget constraint taxes and transfers cancel each other out.
 If we let $T$ denote the transfers, then household income is\footnote{We have implicitly assumed that firms using clean and dirty technologies coexist in the equilibrium, meaning that $\hat{z}_d<\tilde{z}_d$.
@@
     T = \mu\xi\int_{\hat{z}_d}^{\tilde{z}_d}\pi^d(z)dG(z) + \tau_z\left[\mu \int_{\hat{z}_d}^{\overline{z}} \pi^d(z) dG(z) + (1-\mu)\int_{\hat{z}_c}^{\overline{z}} \pi^c(z) dG(z) \right].
-\end{equation*}%the five terms are capital rental income, wage income, profits from dirty and clean firms, and government transfers, respectively.
-%The law of large numbers guarantees that the {ex ante} probability of being inspected equals the {ex post} proportion of firms that actually are inspected.
+\end{equation*}
 
@@
 
-%In this section, we illustrate the basic mechanisms of the model using a simplified version of the model.
-The core concept in our model is the trade-off between the scale and technique effects.
-Because the standard result from the misallocation literature where distortions reduce output is inherited by our model [\citet{Guneretal:2008}], the key here is hence to understand how distortions affect the technique effect, and how they shape the trade-off between the scale and technique effects.
-Specifically, we first show that size-dependent distortions discourage the technology adoption of medium size firms.
-We then characterize the condition under which reducing distortions lead to lower pollution, or equivalently, the technique effect dominates the scale effect.
-We leave all the proofs as well as additional analytical properties of the model to Appendices G.1 and G.2.
-
 \textit{Technology Adoption.---}Proposition \ref{prop:friction} shows that correlated distortions discourage firms from adopting of clean technology, especially those with medium levels of TFP.
@@
 \end{proposition}
-%\begin{proposition}
-%\label{prop:friction}
-%Consider two economies, one (denoted as $f$) with correlated distortions as specified in Equation \ref{eq:tax}, and one (denoted as $n$) without distortions.
-When $1-\gamma+\phi_1^d>0$, there are two thresholds $\tilde{z}_f$ and $\tilde{z}_n$ such that:
-%\begin{enumerate}[(i)]
-%    \item
-%    For each economy $j = f,n$, firms with $z \leq \tilde{z}_j$ choose the dirty technology, while those with $z > \tilde{z}_j$ choose the clean technology.
-%%    \item
-%%    In the economy with size-dependent distortions, entrepreneurs with $z \leq \tilde{z}_f$ produce by using the dirty technology, while those with $z > \tilde{z}_f$ produce by using the clean technology.
-%    \item
-%    When the equilibrium wages $W^f = W^n$, the threshold is higher for the distorted economy, that is, $\tilde{z}_f > \tilde{z}_n$.
-%\end{enumerate}
-%\end{proposition}
 
@@
     \label{fig:constantp}
-    \floatfoot{Note: There are four profit functions in the figure, $\pi_0^n, \pi_0^f, \pi_1^n$, and $\pi_1^f$.
-The superscripts $n$ and $f$ denote whether firms face correlated distortions in the economy or not, and the subscripts $0$ and $1$ denote whether firms choose the dirty or clean technology, respectively.}
+    \begin{figurenotes}
+        There are four profit functions in the figure, $\pi_0^n, \pi_0^f, \pi_1^n$, and $\pi_1^f$.
+The superscripts $n$ and $f$ denote whether firms face correlated distortions in the economy or not, and the subscripts $0$ and $1$ denote whether firms choose the dirty or clean technology, respectively.
+    \end{figurenotes}
 \end{center}
@@
 Recall that while the adoption cost $Rk_E$ is independent of $z$, the penalty for not using the clean technology $\xi \pi_0(z)$ is increasing in $z$.
-%Whether it is worthwhile for firms to pay the installation costs is determined by contrasting the costs with the expected profits loss from inspections by the regulator.
 Therefore, the adoption of the clean technology pays off for firms with higher $z$.
@@
 As a result, while firms with TFP in the range $[\tilde{z}_n, \tilde{z}_f]$ would choose the clean technology when they are not subject to distortions and choose the dirty technology when they are.\footnote{Of course, when the correlated distortions apply to all firms in the economy, they would affect the equilibrium wage $W$ and hence $\tilde{z}_f$ in equilibrium.
-We find later in our quantitative exercises that $\tilde{z}_f > \tilde{z}_n$ even with general equilibrium effects considered.} %which may partially offset the direct impact of distortions on technology adoption.
-However, in our quantitative analysis, this general equilibrium response is not large enough to invalidate the conclusion of Proposition \ref{prop:friction}.
-
-%\noindent Figure \ref{fig:constantp} illustrates Result \ref{prop:friction}.
-There are four profit functions in the figure, $\pi_0^n, \pi_0^f, \pi_1^n$, and $\pi_1^f$, where the superscripts $n$ and $f$ indicate whether there are size-dependent distortions, and the subscripts $0$ and $1$ represent firms using the dirty and clean technology, respectively.
-Note that although installation cost $Rk_E$ is fixed, expected loss $\xi \pi_0(z)$ is increasing in $z$.
-%Whether it is worthwhile for firms to pay the installation costs is determined by contrasting the costs with the expected profits loss from inspections by the regulator.
-%Therefore, despite that the fixed installation costs of the clean technology are not justified for firms with lower $z$, they will eventually pay off for those with higher $z$.
-Because the elasticity of profits to productivity is $1-\gamma$ when there are no distortions, which is larger than that in a market with distortions $1-\gamma-\phi_1$, the distortions decrease the rate at which profits increase with $z$ by $\phi_1$.
-As a result, the threshold where firms switch technology is higher when there are distortions, causing a positive measure $\Delta z(\tau) = G(\tilde{z}_f) - G(\tilde{z}_n)$ of firms using the clean technology when there is no distortions to switch to dirty technology when facing the distortions.
+We find later in our quantitative exercises that $\tilde{z}_f > \tilde{z}_n$ even with general equilibrium effects considered.}
 
@@
 Proposition \ref{prop:agge} summarizes our main findings.
-%\textit{Aggregate Pollution.---}To derive a closed-form relationship between aggregate pollution and the size-dependency of the distortions $\phi_1$, we simplify the model along several key dimensions.
-In particular, we abstract from capital in the economy.
-We also shut down the two discrete choice decisions in the model by assuming first that household members are exogenously assigned to the roles of entrepreneurs and workers, and second that the firm-level pollution intensity mechanically decreases in production scale by elasticity $-1 < \psi_1 < 0$.
-Notice that here $\psi_1$ captures both the reduction in intensity from adopting clean technology and during the production stage.
-Formally, we have the following result.
 \begin{proposition}
@@
 
-Proposition \ref{prop:agge} says that the relationship between $E$ and the progressiveness of the distortions $|\phi_1|$ is inverted-U shaped with the turning point $|\hat{\phi}_1|$ increasing in the elasticity of emission intensity to output $|\psi_1|$.\footnote{Here because $\phi_1$ and $\psi_1$ are both negative, the progressiveness and elasticity are stronger when $|\phi_1|$ and $|\psi_1|$ are larger, meaning that the raw values $\phi_1$ and $\psi_1$ are smaller.} Because correlated distortions generally decreases the total output while increasing the average pollution intensity, the intuition behind Proposition \ref{prop:agge} is a race between the scale and technique effects.
-In particular, the scale effect is larger when the progressiveness of the distortions is stronger (a smaller negative $\phi_1$), while the technique effect is larger when the elasticity of emission intensity to output is larger (a smaller negative $\psi_1<0$).
+Proposition \ref{prop:agge} says that the relationship between $E$ and the progressivity of the distortions $|\phi_1|$ is inverted-U shaped with the turning point $|\hat{\phi}_1|$ increasing in the elasticity of emission intensity to output $|\psi_1|$.\footnote{Here because $\phi_1$ and $\psi_1$ are both negative, the progressivity and elasticity are stronger when $|\phi_1|$ and $|\psi_1|$ are larger, meaning that the raw values $\phi_1$ and $\psi_1$ are smaller.} Because correlated distortions generally decreases the total output while increasing the average pollution intensity, the intuition behind Proposition \ref{prop:agge} is a race between the scale and technique effects.
+In particular, the scale effect is larger when the progressivity of the distortions is stronger (a smaller negative $\phi_1$), while the technique effect is larger when the elasticity of emission intensity to output is larger (a smaller negative $\psi_1<0$).
 As a result, when $|\phi_1|$ is not too large relative to $|\psi_1|$, the technique effect dominates.
-Hence an increase in $\phi_1$ (which means a decrease in the progressiveness) causes higher aggregate pollution $E$.
+Hence an increase in $\phi_1$ (which means a decrease in the progressivity) causes higher aggregate pollution $E$.
 Otherwise, the scale effect dominates, and an increase in $\phi_1$ reduces $E$.
@@
 
-%Proposition \ref{prop:agge} basically says that  the aggregate pollution $E$ is decreasing in average distortion $\phi_0$, and the relationship between $E$ and the progressiveness of distortions $-\phi_1$  (notice that $\phi_1<0$) is inverted-U shaped, where the turning point $-\hat{\phi}_1$ is decreasing in $\psi_1$.
-The intuition goes as follows.
-Correlated distortions generally decreases the total output while increasing the average pollution intensity.
-Therefore, the change in aggregate pollution $E$ depends on the race between the scale and technique effects.
-An increase in $\phi_0$ leads to a uniform increase in distortions facing all firms.
-This would increase aggregate output, but induce little reallocation of production factors across firms, and thus have little impact on the average pollution intensity.
-Therefore, an increase in $\phi_0$ would cause a decrease in $E$.
-%
-%What is more interesting and more relevant to our core mechanism-the reallocation across firms, is the relationship between $E$ and the progressiveness of distortions $-\phi_1$.
-Intuitively, the scale effects are larger when the progressiveness of the distortions $-\phi_1$ is larger, and the technique effects are larger when the elasticity of emission intensity to output $\psi_1$ is smaller (notice that $\psi_1<0$).
-When $-\phi_1$ is not too large relative to $-\psi_1$ (or $-\phi_1< -\hat{\phi}_1$), the technique effect dominates, and an increase in $-\psi_1$ leads to an increase in aggregate pollution $E$.
-Otherwise, the scale effect would dominate, and an increase in $-\psi_1$ leads to a decrease in $E$.
-%
-%To sum up, the key message from Proposition \ref{prop:agge} is, when both average distortion $\phi_0$ and progressiveness of distortions $-\phi_1$ are not too large relative to the absolute value of the elasticity of emission intensity to output $-\psi_1$, the technique effect of correlated distortions would dominate the scale effect, which lead to an increase in aggregate pollution.
-
-%The intuition of the above result goes as follows.
-We have shown that reducing the distortions would increase the production scale and decrease the pollution intensity at the same time.
-Hence whether aggregate pollution $E$ increases or decreases depends on whether the scale or the technique effect dominates.
-For a given level of the technique effect $\psi_1$, if output is very responsive to a marginal decrease in distortions, total emissions are likely to increase as a consequence.
-Because more severe size-dependency of the distortions implies that more productive firms are subject to higher marginal tax, a marginal decrease of the size-dependency of the distortions at a higher level would increase output by more, and hence the increase in aggregate emissions.
-The reverse is true for lower level of the size-dependency.
-Since output is more responsive to the size-dependency of the distortions when returns to scale are high, and the technique effect is stronger when $\psi_1$ is lower (remember $\psi_1 < 0$, hence a larger $\psi_1$ implies weaker technology), the scale effect is more likely to dominate when returns to scale are high, and when the technique effect is weak.
-
-%Proposition \ref{prop:agge} basically says that the relationship between the progressiveness of distortions $-\phi_1$ ($\phi_1<0$) and the aggregate pollution $E$ is inverted-U shaped.
-When $-\phi_1$ is below a threshold -$\hat{\phi}_1$, which itself is decreasing in $\psi_1$, the aggregate pollution $E$ is increasing in $-\phi_1$.
-Otherwise, the aggregate pollution $E$ is decreasing in $-\phi_1$.
-The intuition goes as follows.
-Correlated distortions would generally decrease the total output as well as increase the average pollution intensity, and the change in aggregate pollution $E$ depends on the race between the scale and technique effects.
-The scale effects are larger when $-\phi_1$ is larger, and the technique effects are larger when $-\psi_1$ is larger ($\psi_1<0$).
-When $-\phi_1$ is not too large relative to $-\psi_1$, the technique effects dominate.
-Otherwise, the scale effects would dominate, and aggregate pollution $E$ is increasing in $-\phi_1$.
-In addition,  when $\gamma$ is larger, the scale effects are also larger as the output is more responsive to distortions, and therefore the threshold -$\hat{\phi}_1$ would move to the left.
-
-%Part (i) of Proposition \ref{prop:agge} basically says that when the progressiveness of distortions ($-\phi_1$) is below a threshold (-$\hat{\phi}_1$), the aggregate pollution $E$ is increasing in the progressiveness.
-Correlated distortions would generally decrease the total output as well as increase the average pollution intensity.
-As a result, the change in aggregate pollution $E$ depends on the race between the scale and technique effects.
-If average pollution intensity is very responsive to distortions while the aggregate output is not, total emissions would increase as a consequence.
-This is true if the progressiveness of distortions is not too high.
-Since output is more responsive to the distortions when returns to scale ($\gamma$) are high, and the average pollution intensity is less responsive when $\psi_1$ is higher ($-\psi_1$ is lower; in the extreme case of $\psi=0$, the average pollution intensity is not responsive to distortions at all), the threshold -$\hat{\phi}_1$ moves to the left when  $\psi_1$ or $\gamma$ are higher.
-
-%Similar results hold for the average pollution intensity as well, which we summarize formally in the following corollary.
-%\begin{corollary}
-%\label{prop:aggi}
-%In the simple model, the relationship between the average pollution intensity $E/Y$ and the size-dependency of the distortions $\phi_1$ is such that
-%\begin{enumerate}[(i)]
-%    \item
-%    when $\psi_1 < (1-2\gamma)/\gamma$, the average pollution intensity is always increasing in $\phi_1$;
-%    \item
-%    when $\psi_1 \geq (1-2\gamma)/\gamma$, there exists a threshold
-%    \begin{equation*}
-%        \overline{\phi}_1 = \frac{(1+\psi_1)(1-\gamma)}{1-2\gamma+\gamma\psi_1},
-%    \end{equation*}
-%    such that when $\phi_1 < \overline{\phi}_1$, $E/Y$ is increasing in $\phi_1$; and when $\phi_1 \geq \overline{\phi}_1$, $E/Y$ is decreasing in $\phi_1$;
-%    \item
-%    $\overline{\phi}_1$ is increasing in both $\psi_1$ and $\gamma$;
-%%    \item
-%%    $\overline{\phi}_1 < \hat{\phi}_1$.
-%\end{enumerate}
-%\end{corollary}
-%Notice that the threshold in Result \ref{prop:agge} %and Corollary \ref{prop:aggi}
-%provides a quick way to predict that whether for a certain economy, reducing the size-dependency of the distortions would lead to decrease in aggregate pollution.% and average intensity.
-
-%To clarify the basic mechanics of the model, in this section we analyze a firm's optimization problem when $R$ and $W$ are given exogenously.
-We prove two results.
-First, we show that there exists a threshold $\tilde{z}$ such that firms with $z>\tilde{z}$ adopt the clean technology, while firms with $z \leq \tilde{z}$ do not.
-Second, if we denote the previous threshold in environments with and without size-dependent distortions as $\tilde{z}_f$ and $\tilde{z}_n$ respectively, we show that $\tilde{z}_f > \tilde{z}_n$.
-The first result states that the returns to scale embedded with the clean technology are only exploited when firms are sufficiently large.
-The second result states that by introducing size-dependent distortions, some firms that adopt the clean technology when there are no distortions do not have the profit margin to benefit from the clean technology and hence choose to enter the market with the dirty technology.
-Throughout, we assume $0<\alpha<1$, $0<\gamma<1$, $\phi_0 = 1$, and $1 - \gamma - \phi_1 > 0$.
-We impose the last inequality because the tax specified in [reference to tax function] is imposed on firm-level TFP $z$.
-For the benefits of higher talent $z$ (the elasticity of profits to TFP is $1-\gamma$) to always outweigh the costs (the elasticity of tax to TFP is $\phi_1$), $1-\gamma-\phi_1 > 0$ must be satisfied.
-All proofs are deferred to Online Appendix G.
-%
-%Lemma \ref{lemma:nofrictionpi} characterizes firms' profit functions in the absence of size-dependent distortions.
-%\begin{lemma}
-%\label{lemma:nofrictionpi}
-%In an economy with no size-dependent distortions, $\pi_0(z)$ and $\pi_1(z)$ are both increasing and linear with respect to $z$.
-In addition, the slope of $\pi_1(z)$ is steeper than that of $\pi_0(z)$:
-%\begin{equation}
-%    \frac{\partial \pi_0 (z)}{\partial z} = (1 - \xi)\frac{\partial \pi_1 (z)}{\partial z}, \qquad \forall z \in Z.
-%\label{eq:lemma1}
-%\end{equation}
-%\end{lemma}
-%\noindent Lemma \ref{lemma:nofrictionpi} highlights the core trade-off of adopting the clean technology in our model.
-Although the upfront fixed costs shift the overall profit function down by $R k_E$, the profits of firms using the clean technology will not be confiscated by the regulators.
-Owing to the constant elasticity between capital and labor, the optimal capital/labor ratio is constant in the absence of factor market distortions.
-Further, entrepreneurs reap economic rents from managerial talents $z$, and these economic rents increase linearly in $z$ because due to the constant returns to scale production function.
-%
-%Since the tax in [reference to tax function] is size-dependent in the sense that more talented entrepreneurs are subject to higher distortions, it can be shown that in an economy {with} size-dependent distortions, both $\pi_0(z)$ and $\pi_1(z)$ are concave.
-%\begin{corollary}
-%\label{lemma:frictionpi}
-%Suppose size-dependent distortions are specified as $\max\left\{ 0, 1 - z^{\phi_1} \right\}$ with $1 - \gamma + \phi_1 > 0$; then, $\pi_0(z)$ and $\pi_1(z)$ are both increasing and concave with respect to $z$.
-In addition, the slope of $\pi_1(z)$ is steeper than that of $\pi_0(z)$:
-%\begin{equation*}
-%    \frac{\partial \pi_0 (z)}{\partial z} = (1 - \xi)\frac{\partial \pi_1 (z)}{\partial z}, \qquad \forall z \in Z.
-%\end{equation*}
-%\end{corollary}
-%\noindent On the contrary, if the taxes are uniform---meaning that for all $i$, $\tau_{z_i}$s are the same---then $\pi_0(z)$ and $\pi_1(z)$ remain linear.
-%
-%Since the wage income associated with being a worker is fixed at $W$, the monotonicity of the profit functions implies a threshold $\hat{z}$ for which all household members with talents higher than $\hat{z}$ choose to become entrepreneurs.
-Put differently, household members choose their occupation according to their comparative advantages.
-This is the standard result from the Lucas model.
-We summarize this in Result \ref{prop:threshold}.
-%\begin{result}
-%\label{prop:threshold}
-%There exists a unique threshold $\hat{z}$ such that all household members with $z < \hat{z}$ choose to be workers and those with $z \geq \hat{z}$ become entrepreneurs.
-Further, $\hat{z}$ is the solution of $W = \pi(\hat{z})$.
-%\end{result}
-
-%To explain the intuition, we solve a simplified version of the model here.
-
 \section{Calibration}
@@
 
-%\textit{Calibration.}---We calibrate our model to the Chinese data.
-The model period is set to be one year.
-Motivated by the empirical evidence in Section \rom{1}, we assume that the pollution intensity function of firms with treatment technology $i$ and production level $y$ is log-linear:
-%\begin{equation}
-%    \log \left(\frac{e}{y}\right) = \psi_0^{(i)} + \psi_1^{(i)} \log y.
-%\label{eq:emsn_cali}
-%\end{equation}
-%This specification implies that {conditional} on the treatment technology adopted, a ``within-group'' intensity reduction remains as production scale increases.
-Here, $\psi_1^{(i)}$ captures, for instance, the intensity reduction during the production stage mentioned in Section.\rom{1}.C.
-Equation (\ref{eq:emsn_cali}) implies that actual emissions are
-%\begin{equation}
-%    e = E(i,y) = \mathrm{e}^{\psi_0^{(i)}} y^{1+\psi_1^{(i)}}.
-%\label{eq:emsn_firm}
-%\end{equation}
-%Our model features only two broad categories of treatment technologies as opposed to five in the data.
-%Recall that we interpret the clean technology in our model as {biological} technology and dirty technology as the remaining types.
-We assume only the installation of biological technology incurs the fixed cost $R k_E$.\footnote{Qualitatively, assuming that dirty technology also requires a fixed cost will not affect the property of the model.
-It is equivalent to a decrease in the cost of clean technology, since what matters for firm's decision is the difference of the two costs.}
 \subsection{Calibration Strategy}
@@
 
-%\textit{Calibration Strategy.---}The purpose of our quantitative exercise is to study how firm size distribution affects aggregate pollution.
-Therefore, it is important that our model matches well the firm size distribution in China, the relative distortions faced by large versus small firms, and the pollution intensity of different sized firms.
-We calibrate our model to the whole manufacturing sector.
-
-Following the evidence in Section \rom{1}.B, the relationship between pollution intensity and firm size is given by Equation (\ref{eq:intensity_size}), and the emissions by firms using different treatment technologies are
+Following the evidence in Section I.B, the relationship between pollution intensity and firm size is given by Equation (\ref{eq:intensity_size}), and the emissions by firms using different treatment technologies are
 \begin{equation*}
@@
 where $\{\psi_0^{(i)}, \psi_1^{(i)}\}$ are based on the reduced-form estimates from Equations (\ref{eq:poolols_biological}) and (\ref{eq:poolols_others}).
-%where $\{\psi_0^{(i)}, \psi_1^{(i)}\}$ are given by the regression coefficients from (\ref{eq:poolols_dirty}) and (\ref{eq:poolols_clean}).
-
-The firm size distribution in the model is determined by {both} the talent distribution $G(\cdot)$ and the progressiveness of distortions $-\phi_1$.
+
+The firm size distribution in the model is determined by {both} the talent distribution $G(\cdot)$ and the progressivity of distortions $-\phi_1$.
 This can be seen from Equation (\ref{eq:zandl}), derived from firms' first order conditions:
@@
     (1-\tau_z)z^{1-\gamma} = \Phi l^{1-\gamma},
-   % z^{1-\gamma+\phi_1} = \Phi l^{1-\gamma}
 \end{equation}
 where $\Phi$ is a constant.
-As a result, the progressiveness of the distortions $\phi_1$ has to be calibrated together with the talent distribution $G(\cdot)$.
+As a result, the progressivity of the distortions $\phi_1$ has to be calibrated together with the talent distribution $G(\cdot)$.
 To do this, if we let $\theta_l = y/l$ be the average product of labor, the firm's first order conditions imply
@@
 Equation (\ref{eq:avgl}) can then be used to identify $\phi_1$ using the variations in average product of labor of firms with different TFP.
-
-%Given a choice of the parameters $\alpha$ and $\gamma$, we can bring our model to the data, and back out the progressiveness of distortions $-\phi_1$.
-Then we choose $G(\cdot)$ to match the observed firm size distribution.
-Specifically, let $\theta_l = y/l$ be the average product of labor, the firm's first order conditions imply
-%%Because the firm size distribution in the model is affected by {both} the talent distribution $G(\cdot)$ and distortions $\tau_z$, we cannot use only the distribution to calibrate these two elements.
-To find an additional moment to calibrate $\tau_z$, we follow a similar strategy as the one used by \citet{AdamopoulosRestuccia:2014} when they calibrate the elasticity of distortions to farm size.
-Specifically, if we let $\theta_l = y/l$ be the average product of labor, then the first order conditions of the firm give us
-
-%Given a choice of the parameters $\alpha$ and $\gamma$, we can compute both $z$ and $\theta_l$ for each firm in the data. Then Equation (\ref{eq:avgl}) can be used to pin down $\phi_1$.
-%Since $z$ and $\theta_l$ can all be measured from the data, Equation (\ref{eq:avgl}) can be used to back out $\phi_1$.
-Notice that because the value of $z$ changes with $\gamma$, and $\gamma$ naturally affects how $G(z)$ shapes the size distribution by altering the level of returns to scale, Equation (\ref{eq:avgl}) needs to be used together with the firm size distribution to calibrate jointly $\phi_1, \gamma$ and $G(z)$.\footnote{Another commonly used calibration strategy in the literature takes the United States as an undistorted economy (which means $\tau_z = 0$ in our model) and calibrates $G(z)$ by matching the size distribution from the tax-free economy to the U.S.
-data.
-Taxes are then introduced such that certain moments of the size distribution of the country in interest are matched.
-See, for example, \citet{Guneretal:2008}, \citet{Bartelsmanetal:2013}, \citet{AdamopoulosRestuccia:2014}, and \citet{BentoRestuccia:2016}, among others.
-If we calibrate our model in this way, the underlying assumption would be that the talent distribution of the entrepreneurs in China is the same as that in the United States and that all the difference between the size distributions of China and the United States is due to taxes.
-As is suggested by Figure 2 in \citet{BloomVanReenen:2010}, the evidence regarding this point is mixed.
-In our opinion, both strategies have their strengths and weaknesses, and face different data limitations.
-The quantitative results of our study are largely driven by the size and shape of $\tau_z$.
-Therefore, as long as the alternative calibrations imply similar tax schemes to that used in our benchmark, the quantitative aspects of our results would continue to hold.}
-
-%Given a choice of $\alpha$, $\gamma$ and $\phi_1$, we then choose  $G(\cdot)$ to match the observed firm size distribution in China.
-Again, from the firm's first-order conditions, we get another useful equation that bridges our model and the data
-%We ask the model to match two aspects of the firm size distribution---the total number and share of employment of firms of a certain size.
-Figure \ref{fig:es} suggests that the distribution of small and medium-sized firms follows approximately a log-normal distribution.
-However, a log-normal distribution cannot generate the concentration of employment among large firms.
-The heavy right tail is crucial to our evaluation because these are the firms that are producing with the clean technology.
-To capture both characteristics, we assume that the distribution consists a log-normal part with total mass $1-g_{max}$ that accounts for the lower end, and an atom with measure $g_{max}$ that accounts for those very large firms.\footnote{This strategy follows \citet{Guneretal:2008} and is popular among macroeconomic studies featuring distributions with fat tails.
-See, for example, \citet{Castanedaetal:2003}.} The first order conditions of the firms yield
-
-%\begin{equation}
-%\label{eq:zandl}
-%    (1-\tau(z))z^{1-\gamma} = \Phi l^{1-\gamma}
-%\end{equation}
-%where $\Phi$ is a constant.
-Since by the property of log-normal distribution, if $l$ is log-normally distributed, $l^{1-\gamma}$ follows also a log-normal distribution, Equation (\ref{eq:zandl}) suggests that the ``after-tax'' productivity $(1-\tau_z)z^{1-\gamma} \triangleq z'$ follows the same distribution of $l^{1-\gamma}$, which we assume to be a combination of a log-normal part with mean $\mu_z$ and standard deviation $\sigma_z$, and an atom with value $z'_{max}$ and measure $g_{max}$.
-With $z'$ suitably calibrated, the ``before-tax'' productivity $z$ can then be calculated according to
 
@@
 given a choice of $\phi_0$.
-%\begin{equation*}
-%    z = \left(z'\phi_0^{1/(\gamma-1)}\right)^{\frac{1-\gamma}{1-\gamma+\phi_1}}
-%\end{equation*}
-
-%Since $\tau_z$ is levied based on productivity $z$, we assume that the distribution of ``after-tax'' productivity $z' = (1-\tau_{z})z^{1-\gamma}$ is a combination of two components.
-The first is a log-normal distribution with mean $\mu$, standard deviation $\sigma$, and total probability mass $1-g_{max}$ that accounts for the majority of small and medium-sized firms.
-The second is an atom with value $z'_{max}$ and measure $g_{max}$, which accounts for those very large firms.\footnote{This strategy follows \citet{Guneretal:2008} and is popular among macroeconomic studies of wealth distribution.
-See, for example, \citet{Castanedaetal:2003}.} The ``before-tax'' productivity $z$ can then calculated by
-%\begin{equation*}
-%    z = \left(z'\phi_0^{1/(\gamma-1)}\right)^{\frac{1-\gamma}{1-\gamma+\phi_1}},
-%\end{equation*}
-%which gives us $G(z)$.
 
@@
 We set the depreciation rate $\delta$ to 10\% [\citet{Songetal:2011}].
-$\{\psi_0^{(0)}, \psi_1^{(0)}, \psi_0^{(1)}, \psi_1^{(1)} \}$ are taken from the reduced-form estimates from regressions (\ref{eq:poolols_biological}) and (\ref{eq:poolols_others}) in Section \rom{1}.B, giving us $\psi_0^{(0)} = -$3.41, $\psi_1^{(0)} = -$0.36, $\psi_0^{(1)} = -$4.37, and  $\psi_1^{(1)} = -$0.33.
+\\ $\{\psi_0^{(0)}, \psi_1^{(0)}, \psi_0^{(1)}, \psi_1^{(1)} \}$ are taken from the reduced-form estimates from regressions (\ref{eq:poolols_biological}) and (\ref{eq:poolols_others}) in Section I.B, giving us $\psi_0^{(0)} = -$3.41, $\psi_1^{(0)} = -$0.36, $\psi_0^{(1)} = -$4.37, and  $\psi_1^{(1)} = -$0.33.
 In the context of our model, these estimates suggest that, on average, for two firms with the same level of output but different treatment technologies, the firm using the clean technology emits 40\% to 60\% less pollutants than the one with the dirty technology.
@@
 
-%We then calibrate $\{\gamma, \mu_z, \sigma_z, z'_{max}, g_{max}, \phi_1 \}$ such that the model generates a firm size distribution comparable to the data and Equation (\ref{eq:avgl}) holds.
-To map Equation (\ref{eq:avgl}) to the data, we set $\{z_i, z_j\}$ and $\{\theta_{l,i}, \theta_{l,j}\}$ to their average levels in the top and bottom quintiles respectively.
-Because the calculation of $z$ depends on $\gamma$, Equation (\ref{eq:avgl}) also defines a relationship between $\phi_1$ and $\gamma$.
-For the size distribution, we focus on the number of firms and the share of employment in each of the five size groups (Figure \ref{fig:fitness}).
-In practice, we adjust $\{\gamma, \mu_z, \sigma_z, z'_{max}, g_{max} \}$.
-For each $\gamma$, we compute the corresponding $\phi_1$.
-Given the value of all other parameters, we then compute the size distributions in the equilibrium.
-We repeat the process for different combinations of the five parameters until the size distributions in the equilibrium are close to those in the data.
-Notice that Equation (\ref{eq:avgl}) holds by construction.
-
-%Finally, we calibrate $\phi_0$ such that the average tax burden in the economy equals the 13\% value added tax imposed on Chinese manufacturing firms in the real life.
-This gives us the value of $\phi_0 =$ 1.15.
-In general, it is difficult to estimate the average distortions in an economy because many of the factors that lead to resource misallocation are unobservable [\citet{RestucciaRogerson:2013}] and they do not affect the firm size distribution [\citet{Guneretal:2008}].
-Our choice of the average tax rate as the calibration target of $\phi_0$ follows \citet{BentoRestuccia:2016}.\footnote{As shown in Result \ref{prop:friction}, the gains in output (and capital and consumption as well) from eliminating size-dependent distortions are increasing in the average level of the distortions.
-Hence, targeting a higher average ``tax'' rate increases such gains monotonically, which does not affect the results qualitatively.
-However, quantitatively, the removal of extremely large distortions may lead to a larger increase in output than the decrease in pollution intensity, thereby raising aggregate pollution.
-Moreover, since Section \rom{4}.B examines the effect of a uniform tax, the results therein could be used to infer how qualitatively the results would change compare to the benchmark case.} Table \ref{tab:calibration} presents the model parameters, their targets, and the calibrated values.
-
-%We use the information on the average products of capital to calibrate the tax function.\footnote{Using the average product of labor yields the same results, since $\phi_i \approx \phi_l$ as shown in Section \rom{2}.B.} Equation [reference to distortion] suggests that the elasticity of $\phi_k$ to $1-\tau_z$ is equal to unity.
-Therefore, $\phi_1$ is equal to the elasticity of $\phi_k$ to $z$.
-We thus calculate $\phi_k$ and $z$ according to Section \rom{2}.B, with $R = 0.1$ [\citet{HsiehKlenow:2009}] and the same $\gamma$ used later when we calibrate the model to match the firm size and employment distributions.
-We then run a regression
-%\begin{equation*}
-%    \log \phi_{k_i} = \phi_0 + \phi_1 \log z_i + \varepsilon_{z_i},
-%\end{equation*}
-%which gives us the value for $\phi_1 = -0.03$.
-%\footnote{The elasticity here is lower than that in Section \rom{2}.B because $z$ is calculated by using $\gamma = 0.93$, while previously we set $\gamma = 0.85$.}
-%Given $\phi_1$, we then calibrate $\phi_0$ such that the average tax burden in the economy equals the value added tax imposed on Chinese manufacturing firms in the data, which is 13\%.
-This gives us the value of $\phi_0 = 1.15$.
-In general, it is difficult to estimate the average distortions in an economy because many of the factors that lead to resource misallocation are unobservable [\citet{RestucciaRogerson:2013}] and they do not affect the firm size distribution [\citet{Guneretal:2008}].
-Our choice of the average tax rate as the calibration target of $\phi_0$ follows \citet{BentoRestuccia:2016}.\footnote{As shown in Result \ref{prop:friction}, the gains in output (and capital and consumption as well) from eliminating size-dependent distortions are increasing in the average level of the distortions.
-Hence, targeting a higher average ``tax'' rate increases such gains monotonically, which does not affect the results qualitatively.
-However, quantitatively, the removal of extremely large distortions may lead to a larger increase in output than the decrease in pollution intensity, thereby raising aggregate pollution.
-Moreover, since Section \rom{4}.B examines the effect of a uniform tax, the results therein could be used to infer how qualitatively the results would change compare to the benchmark case.}
-%We choose to target only the value added tax rate and not include other frictions because as is shown in Proposition \ref{prop:friction}, the gains in output (and capital and consumption as well) from eliminating the product market friction are increasing in the average level of frictions.
-Targeting a higher average ``tax'' rate increases such gains monotonically, and will not affect the results qualitatively.
-We therefore choose a conservative target for the average level of frictions.
-We set $A=1$ as normalization.
-
-%The remaining parameters are calibrated jointly by using two layers: an outer layer loops over the parameterization of $G(z)$ and an inner layer solves the model given $G(z)$.
-In the inner layer, we first approximate $G(z)$ with 5,000 grid points.
-We then choose $\beta$ and $\alpha$ to match the capital/output ratio of 1.65 and capital share of 0.5 in China, respectively [\citet{Baietal:2006}].
-We set $\xi$ and $k_E$ such that the total investment in treatment equipment is equal to 1\% of total output and the proportion of firms adopting clean technologies equals the adoption rate of biological equipment 57\% for the five industries we focus on.
-The value of $\gamma$ is set such that the difference between the numbers of firms falls into each bin of the employment and firm size distributions generated by the model and those in the data are minimized.
-More specifically, if we let $s_q$ and $\hat{s}_q$ be the number of firms in each bin $q$ (10 in total) calculated from the data and from the model respectively, $\gamma^*$ solves
-%\begin{equation}
-%\label{eq:innergamma}
-%    \gamma^* = \argmin_{\gamma} \sum_{q=1}^{10} \left( s_q - \hat{s}_q \right)^2.
-%\end{equation}
-%Note that for each combination of $\{ \mu, \sigma, z_{max}, g_{max} \}$, there is one corresponding $\gamma^*$.
-Therefore, in the outer layer, we choose the combination of $\{ \mu, \sigma, z_{max}, g_{max} \}$ that minimizes the minimum distances from the inner layer.
-Furthermore, we require that $\gamma^*$ is the same as that used to calculate $z$.
-%Put differently, the outer layer picks the minimum of the right hand side values of Equation (\ref{eq:innergamma}) when evaluated at $\gamma^*$.
 \begin{table}[t]
@@
 \centering
-\begin{threeparttable}
 \caption{Calibration}
-\begin{tabular}{p{75pt}p{45pt}p{60pt}p{185pt}}
+\begin{tabular}{lccl}
     \hline \hline
     Parameter     &                   & Value         & Target                                                      \\
-    \midrule
+    \hline
     Production    & $\delta$          & 0.1000        & Depreciation Rate                                           \\
                   & $\alpha$          & 0.5376        & Capital Share (0.5)                                         \\
-                  & $\gamma$          & 0.9300        & Size Distribution\tnote{$\dagger$}                          \\
-    \midrule
+                  & $\gamma$          & 0.9300        & Size Distribution\textsuperscript{$\dagger$}                \\
+    \hline
     Treatment     & $\psi_0^{(0)}$    & $-$3.4144     & Estimates from Regression (\ref{eq:poolols_biological})     \\
@@
                   & $\xi$             & 0.2300        & Clean Technology Adoption Rate                              \\
-    \midrule
+    \hline
     Distortions   & $\phi_0$          & 1.15          & Average Value Added Tax Rate(13\%)                          \\
-                  & $\phi_1$          & $-$0.03       & Elasticity of Average Product to TFP Eq.
-(\ref{eq:avgl})\tnote{$\dagger$}    \\%Relative Distortions Equation (\ref{eq:avgl})\tnote{$\dagger$}   \\
+                  & $\phi_1$          & $-$0.03       & Elasticity of Average Product to TFP Eq. (\ref{eq:avgl})\textsuperscript{$\dagger$}    \\
     Preference    & $\beta$           & 0.8750        & Capital/output Ratio (1.65)                                 \\
-    \midrule
-    Productivity  & $\mu_z$           & $-$2.4567     & Size Distribution\tnote{$\dagger$}                          \\
+    \hline
+    Productivity  & $\mu_z$           & $-$2.4567     & Size Distribution\textsuperscript{$\dagger$}                \\
                   & $\sigma_z$        & 4.0020        &                                                             \\
@@
                   & $\mu$             & 0.20          & Fraction of Firms in the Polluting Sector                   \\
-    \bottomrule
+    \hline
 \end{tabular}
 \begin{tablenotes}
-     \footnotesize{
-     \item[$\dagger$]
-     Note: The parameters are jointly calibrated.}
+     \textsuperscript{$\dagger$}The parameters are jointly calibrated.
 \end{tablenotes}
 \label{tab:calibration}
-\end{threeparttable}
 \end{table}
@@
 The mean and median of the firm size distribution 53.74 and 19.56, which are not directly targeted in the calibration, match their empirical counterparts of 52.19 and 20 respectively, suggesting that the top managers captures well the upper tail of the firm size distribution.
-
-%\textit{Discussion.}---The calibrated model matches the capital share, capital/output ratio, ratio of average clean equipment cost to average output value for firms using clean technology, proportion of firms adopting the clean technology.
-%The implied discount rate $\beta$ is less than the values commonly used in the literature.
-The reason is that we calibrate our model to the steady state as opposed to the balanced growth path.
-If we assume that the household has log-utility function and the secular growth rate equals to 8\%, the counterpart of the discount rate in this situation is equal to 0.95.
-We choose to calibrate the model to the steady state because we do not have to make additional assumptions on the functional form of the utility function.
-Nevertheless, all of the qualitative and quantitative results in this paper hold in the balanced growth path calibration.
-%The calibrated value of $\xi$ should be interpreted as the implied ``tax'' rate for using the dirty technology, which combines the effect of many disparate and overlapping policies and adds up to 20.5\% of a firm's annual output value.
-%\footnote{While empirical counterpart of the value is difficult to find, the number lies within the range of percentage of plants inspected reported in \citet{BeckerHenderson:2000}.
-In particular, \citet{BeckerHenderson:2000} report the percentage of firms inspected in four industries in the U.S: Plastics, Wood Furniture, Industrial Organic Chemicals and Metal Containers.
-The numbers are respectively 2.4\%, 6.8\%, 20\% and 27\%.}
-
-%Figure \ref{fig:fitness} plots the firm size (left panel) and employment share distributions (right panel) in the model and in the data.
-We plot the match for the whole manufacturing sector.
-However, since the ex ante distributions of productivity are the same in both the polluting and non-polluting sectors, and that the calibrated level of $k_E$ is small, the matches of the model for the polluting and non-polluting sectors look very similar to those in Figure \ref{fig:fitness}.
-
-%Overall, the model matches the two distributions well given that there are five degrees of freedom.
-The mean (53.74) and median (19.56) of the firm size distribution, which are not directly targeted in the calibration, match their empirical counterparts of 52.19 and 20 respectively.
-This suggests that the atom $(z'_{max}, g_{max})$ captures well the upper tail of the firm size distribution.
-
 \begin{figure}[t]
@@
     \caption{Firm Size Distribution: Model versus Data}
-    \floatfoot{Note: The firm size and employment distributions of the whole manufacturing sector are reported.}
+    \begin{figurenotes}
+        The firm size and employment distributions of the whole manufacturing sector are reported.
+    \end{figurenotes}
     \label{fig:fitness}
@@
 
-%Specifically,  To match the observed employment shares among large firms in the presence of correlated distortions,  %\footnote{Models where these two forces are not antagonistic to each other usually have much better fit.
-For instance, \citet{Guneretal:2008} study the whole U.S.
-business sector, which has a narrower employment span and lighter employment concentration.
-In particular, the largest group they are targeting is firms with more than 100 employees.
-On the contrary, the largest group we are targeting is 400+ employees, which is significantly larger.
-In another study, \citet{AdamopoulosRestuccia:2014} assume away the selection mechanism in the model, which, put differently, mutes the general equilibrium feedback through wages.
-This relaxes the restriction on average talents considerably.}
-
-%The calibrated value of returns to scale $\gamma$ warrants more explanation.
-The parameter value lies within the empirically estimated range, though close to the upper bound.\footnote{The values previously used in the macro literature range from 0.85 [\citet{AtkesonKehoe:2005}] at the lower end to 0.95 [\citet{Bartelsmanetal:2013}] at the upper end, although in $\gamma$ is not the only source of decreasing returns to scale in [\citet{Bartelsmanetal:2013}].
-Please see also the discussion on page 319 of \citet{Bartelsmanetal:2013}.
-Estimations from micro-level data yield similar results.
-For example, \citet{OlleyPakes:1996} estimate the value to be between 0.8 and 0.9 for the U.S.
-telecommunications equipment industry, depending on the particular econometric specification.} The challenges of calibrating the model to simultaneously match the two aspects of the firm size distribution are as follows.
-To create the concentration of employment among large firms, we need entrepreneurs with very high productivity to face low wages and experience high returns to scale ($\gamma$).
-Due to the standard property of the \citet{Lucas:1978b} model, low prevailing wage implies that the profits of small firms are also low (Lemma 2 in Online Appendix G).
-However, higher $\gamma$ raises factor demand from large firms, which pushes up factor prices and drives out small firms with low profits.
-The latter jeopardizes the fit of the number of small firms in the model.
-The performance of our model is thus a compromise of these two forces.\footnote{Models where these two forces are not antagonistic to each other usually have much better fit.
-For instance, \citet{Guneretal:2008} study the whole U.S.
-business sector, which has a narrower employment span and lighter employment concentration.
-In particular, the largest group they are targeting is firms with more than 100 employees.
-On the contrary, the largest group we are targeting is 400+ employees, which is significantly larger.
-In another study, \citet{AdamopoulosRestuccia:2014} assume away the selection mechanism in the model, which, put differently, mutes the general equilibrium feedback through wages.
-This relaxes the restriction on average talents considerably.}
-
-%The identification assumption of our benchmark calibration is that {given} taxes $\tau_z$, the talent distribution is identified by the size distribution in the data.
-Another commonly used calibration strategy in the literature takes the United States as an undistorted economy (which means $\tau_z = 0$ in our model) and calibrates $G(z)$ by matching the size distribution from the tax-free economy to the U.S.
-data.
-Taxes are then introduced such that certain moments of the size distribution of the country in interest are matched.\footnote{See, for example, \citet{Guneretal:2008}, \citet{Bartelsmanetal:2013}, \citet{AdamopoulosRestuccia:2014}, and \citet{BentoRestuccia:2016}, among others.} If we calibrate our model in this way, the underlying assumption would be that the talent distribution of the entrepreneurs in China is the same as that in the United States and that all the difference between the size distributions of China and the United States is due to taxes.\footnote{The evidence regarding this point is mixed.
-See Figure 2 in \citet{BloomVanReenen:2010}.} In our opinion, both strategies have their strengths and weaknesses, and face different data limitations.
-The quantitative results of our study are largely driven by the size and shape of $\tau_z$.
-Therefore, as long as the alternative calibrations imply similar tax schemes to that used in our benchmark, the quantitative aspects of our results would continue to hold.\footnote{In an earlier version of this study where endogenous treatment technology choice is not explicitly modeled, we find that this is indeed the case.} We choose to calibrate our model directly to the Chinese economy directly because better empirical evidence (Section \rom{2}.B) is available.
-
 \section{Quantitative Exercises}
@@
 } This is meant to capture the overall effects of a variety of policies and institutions that reallocate resources from high to low TFP firms.
-To isolate the importance of the {progressiveness} of distortions, later we replace the progressive taxes with flat taxes by setting $\phi_1=0$, and change $\phi_0$ to keep the total implicit tax revenue constant.
+To isolate the importance of the {progressivity} of distortions, later we replace the progressive taxes with flat taxes by setting $\phi_1=0$, and change $\phi_0$ to keep the total implicit tax revenue constant.
 In Experiment (ii), we tighten the environmental regulations by increasing $\xi$ to the extent that the fraction of firms using the clean technology is the same as in Experiment (i).
 We then compare the results from these two experiments, and illustrate the key mechanisms that drive these different results.
-%We use the calibrated model as a framework for understanding the effects of the firm size distribution on industrial pollution.
-We conduct two experiments.
-In experiment (i), we eliminate all distortions by setting $\tau_z = 0$.
-This experiment could be interpreted as reductions in inter-regional trade barriers, improvements in transportation infrastructure, decreases in tax burdens, and so on.\footnote{In the main text, we do not study asymmetric changes of $\tau_z$ across sectors, because we feel that it is unlikely that for instance an improvement in infrastructure benefits only the polluting sector.
-This also explains the reason we model the goods produced by the two sectors are perfect substitutes.
-However, for the case of asymmetric changes, the assumption of perfect substitutes would lead to overly elastic response in sectoral output.
-For such scenarios, a moderate elasticity of substitution is needed.
-We report the results from reducing only the distortions in the polluting sector in a model with CES aggregation (and hence price adjustment) in Online Appendix I.
-As expected, the main mechanism in our paper remains intact.} Since we are following the \textit{indirect} approach, we are not able to map the size of decrease in $\tau_z$ to observable policy changes.
-%empirical evidence of the size of the decrease in $\tau_z$ caused by a reduction in some observable distortions of a certain degree is lacking.
-%However, as an approximation, the effects of the policy can be assessed by examining the changes in average firm size across steady states, as is done by for example \citet{Guneretal:2008} and \citet{BentoRestuccia:2016}.
-In experiment (ii), we increase regulation $\xi$ such that the proportion of firms using the clean technology reaches the same level as in experiment (i).
-In this experiment, we aim to approximate the current environmental policy that punishes firms for using the dirty technology.
-We then contrast the results of the two experiments to illustrate the different mechanisms and effects of these two types of policies.
-
-%Since along most dimensions, the response from the two sectors are very similar, for each experiment, we will first focus on the polluting sector alone.
-We then turn to the non-polluting sector by analyzing where its response differs.
-The overall impact on the whole manufacturing sector is the weighted average of the changes in the two sectors.
 
 \subsection{Counterfactual Experiments}
-
-%\begin{table}[t]
-%\footnotesize
-%\centering
-%\begin{threeparttable}
-%\caption{The Effects of Distortions and Regulations}
-%\begin{tabular}{p{125pt} >{\centering\arraybackslash}p{75pt} >{\centering\arraybackslash}p{75pt} >{\centering\arraybackslash}p{75pt}}
-%    \hline \hline
-%    Statistics                      & Benchmark             & (i)                   & (ii)    \\
-%    \midrule
-%    Aggregate Output                & 100.00                & 129.72                & 100.12  \\
-%    Capital                         & 100.00                & 161.25                & 100.14  \\
-%    Consumption                     & 100.00                & 123.45                & 100.11  \\
-%    Output per Worker (Wage)        & 100.00                & 128.49                & 99.97   \\
-%    Output per Firm                 & 100.00                & 298.78                & 109.76  \\
-%    Average Talent                  & 100.00                & 224.67                & 109.49  \\
-%%    TFP                             & 100.00                & 102.00                & 100.14  \\
-%    \midrule
-%    Number of Firms                 & 100.00                & 43.42                 & 91.22   \\
-%    Mean Size                       & 59.27                 & 137.81                & 65.07   \\
-%    Median Size                     & 22.95                 & 41.83                 & 26.72   \\
-%    \midrule
-%    Aggregate Pollution             & 100.00                & 78.95                 & 90.75 \\
-%    Average Intensity               & 100.00                & 60.86                 & 90.65 \\
-%    Clean Share                     & 57.40                 & 85.29                 & 85.15  \\
-%    Monitoring                      & 20.50                 & 20.50                 & 32.50  \\
-%    \bottomrule
-%\end{tabular}
-%\begin{tablenotes}
-%     \footnotesize{
-%     \item[$\dagger$]
-%     Note: All values are in percentage points except mean and median size, which are the absolute numbers of workers.}
-%\end{tablenotes}
-%\label{tab:aggregates}
-%\end{threeparttable}
-%\end{table}
 
@@
 
-%\textit{Removing All Distortions.}---We begin with the effects on the resource allocation in the polluting sector.
-The core mechanism that generates the results of experiment (i) is the change in size distributions driven by the {general equilibrium wage effect}.
-Since the tax scheme $\tau_z$ is assumed to be size-dependent, which is larger for more productive firms, the market share of these firms is restrained in the benchmark economy.
-The elimination of $\tau_z$ removes these constraints.
-As a result, the previously suppressed factor demand increases considerably.
-In column (i) of Table \ref{tab:aggregates}, this shows up as a 61\% increase in aggregate capital and a 60\% increase in wages.
-The size dependency of $\tau_z$ also implies that the situation of small unproductive firms improves to a lesser extent than that of large productive ones.
-Many small unproductive firms that previously survived because of the low prevailing wage now lose their profit margins.
-The owners of these firms therefore find it more profitable to work for more productive firms.
-This {selection} mechanism explains the 121\% increase in the average productivity of firms and 132\% increase in the mean firm size.
-Furthermore, production is also more concentrated in firms with high productivity {among} the remaining firms.
-We define the \textit{extensive} margin as the selection of firms into production and the \textit{intensive} margin as the production distribution among the active firms.
-The first two rows of Table \ref{tab:talentdist}, which report the output share of firms with productivity in different quintiles, show the intensive margin.
-
 \begin{table}[t]
@@
 \centering
-\begin{threeparttable}
 \caption{The Effects of Correlated Distortions and Environmental Regulations}
-%\begin{tabular}{lccccccc}%{p{85pt}>{\centering\arraybackslash}p{50pt}>{\centering\arraybackslash}p{50pt}>{\centering\arraybackslash}p{40pt}}%>{\centering\arraybackslash}p{35pt}}%{lccc}
-\begin{tabular}{p{90pt} >{\centering\arraybackslash}p{45pt} >{\centering\arraybackslash}p{45pt}>{\centering\arraybackslash}p{40pt} >{\centering\arraybackslash}p{5pt} >{\centering\arraybackslash}p{45pt} >{\centering\arraybackslash}p{45pt} >{\centering\arraybackslash}p{40pt}}
+\begin{tabular}{lccccccc}
     \hline \hline
@@
     Statistics           & Benchmark & (i)      & (ii)      & & Benchmark     & (i)    & (ii) \\
-    \midrule
+    \hline
     Output               & 100.00    & 131.16   & 98.99     & & 100.00        & 129.62 & 100.28 \\
     Capital              & 100.00    & 163.06   & 99.00     & & 100.00        & 161.26 & 100.28 \\
-    Consumption\tnote{a} & 100.00    & 123.63   & 100.02    & & 100.00        & 123.63 & 100.02 \\
-    Wage\tnote{a}        & 100.00    & 160.00   & 99.96     & & 100.00        & 160.00 &  99.96 \\
+    Consumption          & 100.00    & 123.63   & 100.02    & & 100.00        & 123.63 & 100.02 \\
+    Wage                 & 100.00    & 160.00   & 99.96     & & 100.00        & 160.00 &  99.96 \\
     Output per Worker    & 100.00    & 128.25   & 100.15    & & 100.00        & 128.60 &  99.95 \\
@@
     \% in Output         & 19.73     & 19.91    & 19.52     & &  80.27        & 80.09  &  80.48 \\
-    \midrule
+    \hline
     \# of Firms          & 100.00    & 44.07    & 89.86     & & 100.00        & 41.56  & 100.00 \\
@@
     Median Size          & 23.67     & 43.09    & 27.88     & & 18.61         & 34.31  & 18.67  \\
-    \midrule
+    \hline
     Pollution            & 100       & 76.67    & 85.82     \\
     Intensity            & 100       & 58.46    & 86.73    \\
-%    Pollution            & 100       & 81.66    & 90.60     \\
-%    Intensity            & 100       & 62.27    & 91.56     \\
     Clean Share          & 57.77     & 85.61    & 85.10     \\
     Regulation           & 23.00     & 23.00    & 35.50     \\
-    \bottomrule
+    \hline
 \end{tabular}
 \begin{tablenotes}
-     \footnotesize{
-     \item[$\dagger$]
-     Note: All values are percentages except for mean size and median size, which are the numbers of workers.
-     \item[a]
-     Consumption and wage are not sector specific.}
+     All values are percentages except for mean size and median size, which are the numbers of workers. Consumption and wage are not sector specific.
 \end{tablenotes}
 \label{tab:aggregates}
-\end{threeparttable}
 \end{table}
@@
 \centering
-\begin{threeparttable}
 \caption{Resource Allocation on the Intensive Margin}
-\begin{tabular}{p{65pt} >{\centering\arraybackslash}p{45pt} >{\centering\arraybackslash}p{45pt} >{\centering\arraybackslash}p{45pt} >{\centering\arraybackslash}p{45pt} >{\centering\arraybackslash}p{45pt}}
+\begin{tabular}{lccccc}%{p{65pt} >{\centering\arraybackslash}p{45pt} >{\centering\arraybackslash}p{45pt} >{\centering\arraybackslash}p{45pt} >{\centering\arraybackslash}p{45pt} >{\centering\arraybackslash}p{45pt}}
     \hline \hline
     Economy           & $\text{QU}_1$ & $\text{QU}_2$ & $\text{QU}_3$ & $\text{QU}_4$ & $\text{QU}_5$ \\
-    \midrule
+    \hline
     \multicolumn{3}{l}{\textbf{Polluting Sector:}} \\
@@
     \ \ \ Case (ii)   & 3.02          & 4.63          & 8.01          & 17.79         & 66.55          \\
-    \midrule
+    \hline
     \multicolumn{3}{l}{\textbf{Non-polluting Sector:}} \\
@@
     \ \ \ Case (ii)   & 2.42          & 3.78          & 6.65          & 15.39         & 71.75          \\
-    \bottomrule
+    \hline
 \end{tabular}
 \begin{tablenotes}
-     \footnotesize{
-     \item[$\dagger$]
-     Note: $\text{QU}_1$ to $\text{QU}_5$ represent the first to fifth quintiles, respectively.}
+     $\text{QU}_1$ to $\text{QU}_5$ represent the first to fifth quintiles, respectively.
 \end{tablenotes}
 \label{tab:talentdist}
-\end{threeparttable}
 \end{table}
@@
 The two panels on the left of Figure \ref{fig:compare_size} show the changes in firm size distributions following the removal of the correlated distortions.
-%Firms in the top two groups expand considerably at the expense of firms in the bottom three groups.
-Therefore, the elimination of $\tau_z$ improves the resource allocation on both the extensive and the intensive margins.
-For the polluting sector, the overall changes in the size and employment distributions can be seen in the two left-hand panels of Figure \ref{fig:compare_size}.
+
 \begin{figure}[t]
@@
     \caption{The Effects of Distortions and Regulations on Firm Size Distributions}
-    \floatfoot{Note: The distributions of the polluting sector are reported. }
+    \begin{figurenotes}
+        The distributions of the polluting sector are reported.
+    \end{figurenotes}
     \label{fig:compare_size}
@@
 
-%By defining aggregate $\text{TFP} = {Y}/{(K^{\alpha} N^{1-\alpha})^{1-\gamma}}$,
-%%\begin{equation*}
-%%    \text{TFP} = \frac{Y}{(K^{\alpha} N^{1-\alpha})^{1-\gamma}},
-%%\end{equation*}
-%which is the Solow residual following standard growth accounting studies [\citet{HallJones:1999}], we find that the size distributions in models {with} firm selection exert a limited influence over TFP.
-This finding is consistent with that in \citet{Guneretal:2008}.
-
 The large increase in aggregate output is caused by both an improved allocation of production factors across firms, and a large increase in capital accumulation by about 60\% due to decreased average tax rate from 13\% to 0\%.
 The increase in capital accumulation plays a much larger role than improved allocation of factors in the increase in aggregate output.
-Our quantitative exercises in Section \rom{4}.B below illustrate this point further.
+Our quantitative exercises in Section IV.B below illustrate this point further.
 The large decline in average pollution intensity is also caused by two factors: the improved allocation of production factors, and increased adoption of the clean technology.
@@
 This reallocation lowers the average pollution intensity.
-Meanwhile, as we discuss in Section \rom{3}.D, correlated distortions lower the elasticity of firm profits to firm TFP $z$, and therefore reduce their incentives to adopt the clean technology.
+Meanwhile, as we discuss in Section III.D, correlated distortions lower the elasticity of firm profits to firm TFP $z$, and therefore reduce their incentives to adopt the clean technology.
 Removing correlated distortions would do exactly the opposite and encourage the adoption of clean technology.
-
-%Now, we examine the effects on pollution.
-Although aggregate output increases by 31\%, because average pollution intensity decreases by a larger extent of 38\%, aggregate pollution {decreases} by 19\%.
-In other words, quantitatively, the technique effect dominates the scale effect.
-The decline in average intensity comes both from the production stage and from the treatment stage.
-In both stages, changes in the size distribution play a key role.
-Since production in the no-distortions economy shows a higher degree of concentration in large firms, the fact that the two {within-group} elasticities $\psi_1^{(0)}$ and $\psi_1^{(1)}$ are negative implies a decrease in pollution intensity.
-%As discussed in Section \rom{1}.C, this could be because larger firms use more productive technologies which just happen to be environmentally friendly.
-Given that the focus of this paper is at the treatment stage, we capture this relationship in a reduced-form way and we leave a the full-fledged discussion for future research.
-%The effect of the size distribution on a firm's choice of end-of-pipe treatment technology works exactly as described in Result \ref{prop:friction}.
-The elimination of $\tau_z$ increases firms' profits significantly, which strengthens the economic incentive to adopt the clean technology.
-%\footnote{If we treat international trade costs as one particular example of $\tau_z$, our findings are consistent with those in \citet{Bustos:2011}.
-More specifically, she found empirically that reduction in tariffs leads to more export revenues which induces upgrade of production technology.} %It is important to bear in mind that both the elimination of $\tau_z$ itself and the subsequent {decrease} of wages contribute to the strengthening of the economic incentive.
-%Importantly, by setting the $\psi_1$ in Result \ref{prop:agge} to $\psi_1^{(1)}$, the upper bound of $\hat{\phi}_1$ under our current calibration is $-$0.06.
-With our calibrated $\phi_1 = -$0.03, which is higher than $\hat{\phi}_1$, the qualitative prediction from Result \ref{prop:agge} is consistent with the quantitative results.
 
@@
 
-%To evaluate the relative contribution of the reduction in the production and treatment stages, consider a hypothetical world where the clean and dirty technologies are the same, meaning that $\psi_0^{(0)} = \psi_0^{(1)}$ and $\psi_1^{(0)} = \psi_1^{(1)}$.
-Removing distortions in this economy reduces the aggregate pollution and average intensity by 20\% and 39\%.
-Restoring the technic specifications of the clean technology further reduces the pollution level and intensity by 17\% and 13\%.
-Hence on average, about 46\% and 25\% of the decrease in aggregate pollution and average intensity occur in the treatment stage.\footnote{One caveat here is that because we do not model explicitly the technology adoption decision of the firms during the \textit{production} stage due to data limitation, we have implicitly assumed that the relationship between emission and firm size conditional on treatment technology estimated from the data can be extrapolated to other scenarios.
-In the context of our experiments, this means that the relationships in the world with distortions provide reasonable approximations to those in a world without distortions.
-As long as this is the case, modeling the technology choice decisions in the production stage explicitly or not would not change the quantitative results.}
-
 Finally, the polluting and non-polluting sectors respond in similar ways to the removal of correlated distortions, and little reallocation is induced across sectors.
@@
 As a result, compared to the non-polluting sector, the removal of correlated distortions leads to a 1.5 percentage points larger increase in output in the polluting sector.
-
-%The non-polluting sector responds to the removal of $\tau_z$ in more or less the same way as the polluting sector.
-Recall that the only material difference between the polluting and non-polluting sector is the presence of fixed cost $k_E$ and environmental regulations.
-Hence any difference observed between the two sectors has to stem from how the interaction of these two features affects the decisions of firms.
-There are two notable differences.
-First is that the efficiency loss caused by $\tau_z$ is smaller in the non-polluting sector.
-This can be seen from the fact that the output increase in the polluting sector is 1.5 percentage points smaller in the non-polluting sector.
-Notice that on average, firms are larger in the polluting sector, because very small firms cannot afford the cost of clean technology.
-This combines with the size-dependency of $\tau_z$ suggests that on average, the polluting sector is taxed heavier under the same tax scheme, leading to higher efficiency loss.
-This demonstrates an explicit channel of how environmental regulations amplifies existing distortions in the economy.
-Second is that although the polluting sector is more selective on the extensive margin, the output per firm is in fact lower.
-This is because that although the productivity of the very small firms are extremely low, by operating at very small scale, the marginal productivity of labor is in fact higher than other active firms.
-Leaving them off the market hence reduces the overall efficiency of how the economy uses production factor.
-Further, Table \ref{tab:talentdist} shows that the additional selection also worsens resource allocation along the intensive margin, which also lowers output per firm.
 
@@
 On the other hand, the increase in $\xi$ has very limited spillover on both the aggregate outcomes and firm size distribution to the non-polluting sector.
-
-%\textit{Tightening Environmental Regulations.}---The tightening of environmental regulations affects the decisions of firms {directly} through the requirement to adopt technology and {indirectly} through the general equilibrium wage feedback.
-Unlike in experiment (i), these two effects affect the size and employment distributions at the equilibrium by little, as shown in the two right-hand panels in Figure \ref{fig:compare_size}.
-There are two reasons behind this.
-First, large firms that have already adopted the clean technology in the benchmark case are not directly affected by changes in the policy.
-Second, the installation costs of the clean technology in our benchmark calibration are small.
-As a result, they do not divert a significant proportion of firms' resources from productive use and hence hardly affect the optimal operating scale of firms.
-Therefore, in column (ii) of the top panel of Table \ref{tab:aggregates}, the macro aggregates barely change compared with the benchmark case.
 
@@
 
-%However, despite the small {decrease} in wages (0.04\%), selection on the extensive margin {increases} the average size and productivity of active firms.
-The underlying mechanism here is that an increase in environmental regulations decreases the expected returns from being an entrepreneur, which drives out the least productive firms that cannot afford to install the clean technology.
-%\footnote{This prediction matches the policy practice in China.
-For example, during 2004 to 2008, the emissions of major air pollutants as well as industrial production declined significantly.
-The reductions in per-unit GDP emissions for these pollutants were 35\% for sulfur dioxide, 29\% for black carbon, and 31\% for carbon monoxide [\citet{Linetal:2014pnas}].
-During that period, 34 million kW of coal-burning electricity-generating facilities were shut down, which amounts to 6.18\% of total electric production in 2013 (\textit{National Development and Reform Commission} [2009] Decree 4).}
-%These household members then choose to become workers, which increases labor supply and suppresses equilibrium wage rates.
-The remaining large firms benefit from the reduction in wage rates and expand their operating scale, which explains the increases in size and productivity.
-In Figure \ref{fig:compare_size}, this is graphically reflected as contraction of the smallest group in the firm size distribution and expansion in the other four groups.
-
 While small firms account for a large fraction of firms, they account for only a small fraction of production factors, which implies that the total amount of factors affected by the extensive changes is small.
@@
 
-%The firms in the four expansion groups are not affected equally, however, as shown in row (ii) in Table \ref{tab:talentdist}.
-As experiment (i) shows, the most efficient way of allocating talents is to shift production to the most productive firms, increasing the share of output accounted for by firms with productivity in the top quintile.
-However, row (ii) shows the opposite.
-Compared with the benchmark case, the proportion of production accounted for by the lower quintiles {increases}, while that of the top quintile {decreases}.
-Therefore, although strengthening regulation improves the resource allocation on the {extensive} margin, the benefit is countered by exactly the same two channels documented above, namely the amplification of distortions and the loss in efficiency along the intensive margin.
-%because size-dependent $\tau_z$ limits the extent to which declining wages can benefit firms in the top quintile.
-%Nevertheless, both these effects are small here because in our benchmark calibration $k_E$ is small.
-
 Since the total amount of factors involved in reallocation along the two margins is small, most of the decrease in average pollution intensity comes from the increased adoption of the clean technology.
@@
 
-%Since aggregate output only decreases slightly in this experiment, the decreases in aggregate pollution and intensity are quantitatively similar (i.e., around 10\%).
-Moreover, because the size and employment distributions change little, most of the decrease comes from the treatment stage.
-If we repeat the decomposition exercise we just did for experiment (i), 88\% and 91\% of the reductions in aggregate pollution and average intensity stem from the adoption of the clean technology.
-
-The non-polluting sector is indirectly affected in this experiment by the general equilibrium reponse in wage.
+The non-polluting sector is indirectly affected in this experiment by the general equilibrium response in wage.
 Since the induced change in equilibrium wage is very small, the increase in $\xi$ has very small effects on both the aggregate outcomes and firm size distribution, even when the products of the two sectors are perfect substitutes.
-
-%The non-polluting sector is barely affected in this experiment, because the only difference in environment it faces is a tiny drop in wage rate.
-In addition, the distributions of the polluting versus non-polluting sector in Table \ref{tab:talentdist} provide further evidence showing that environmental regulation reduces the efficiency along the intensive margin.
-The results suggest that when the size of the polluting sector is small, even with perfect substitutes between the goods and hence infinity elasticity of cross-sector substitution, the side effects are negligible.
 
@@
 
-%\textit{Comparing the Two Policies.}---These two experiments show that both removing distortions and intensifying regulations affect the resource allocation, but in different ways.
-Naturally, eliminating the distortions improve resource allocation along both the extensive and intensive margin, since it moves the economy to its first best.
-On the contrary, although environmental regulation intensifies the selection of firms, which pushes the threshold closer to its level in the first best equilibrium, the average distortions in the economy get amplified the resource allocation along the intensive margin worsens.\footnote{In reality, tightening environmental regulations may cause other undesirable outcomes.
-For example, extra resources are needed to enforce tightening regulations, and more rent-seeking activities may possibly be induced by the regulations.
-Due to data limitations, we leave a complete welfare analysis of tightening environmental regulations to future research.
-}As a result, although in both experiments the share of firms using clean technology is the same, the reduction of aggregate pollution during the treatment stage is larger in experiment (i) because firms adopting clean technology takes a larger market share.
-
-%In particular, removing distortions increases labor {demand} from firms, while intensifying regulations increases labor \textit{supply} from household members.
-Because distortions are size-dependent, large firms benefit more from their removal.
-On the contrary, an increase in labor supply suppresses equilibrium wages, thereby potentially raising firms' profits.
-However, the actual extra profits firms earn need to take out the effect of distortions.
-As before, owing to the size dependency of the distortions, large firms benefit less from the decrease in wages.
-This explains the reason why the intensive margin improves when distortions are eliminated but worsens when stronger regulations are imposed.
-%Put differently, distortions shape the effect of environmental policies on different firms.
-%This finding complements the analysis by \citet{Bustos:2011}, who empirically studies the extent to which the elimination of tariffs---a particular form of size-dependent distortion---influences technology upgrading.
-The results of our first experiment are consistent with hers.
-Further, we examine how the economy is affected if the government implements policies that target technology adoption in the presence of size-dependent distortions.
-
-%The lesson we learn from the quantitative exercises is that if resources are devoted to smoothing the frictions in the economy instead of being used to intensify regulations, reductions of pollution in both the production and treatment stage could arise naturally as equilibrium outcomes.
-% Several recent studies argued that industrial pollution in China comes from the unanticipated responses of economic agents to different policies and institutional features.\footnote{For instance, \citet{Jia:2014} studies the role of the political incentives and career concerns of provincial governors, \citet{Jiangetal:2014} emphasize differential policy treatments to firms with different ownership rights structures, and \citet{Kahnetal:2015} and \citet{Caietal:2016} estimate the difference in the reduction efforts from provincial governments on upstream and downstream counties along the rivers in response to the pollution reduction mandates imposed by the central government.} In reality, the effects of regulatory policies such as government campaigns are often ineffective.
-These policies suffer from the challenge in monitoring small firms operating off the radar and the quick rebound of pollution level when those campaigns end.
-Indeed, our results suggest that policies and institutional features could work to amplify other existing distortions in the economy and removing such distortions may well provide a different path to growth that is more sustainable.
-At the same time, the elimination of those distortions could also reduce the unanticipated environmental consequences of these policies and institutional features.
-That said, it could be that reducing economic distortions costs more, meaning that strengthening regulations pays off to a larger degree in the short run.\footnote{Another concern is that if small firms have higher growth rates, the removal of size-dependent distortions could hamper economic growth in the long run.
-However, the recent study of India's manufacturing sector by \citet{Martinetal:2017} suggests that as in the United States, larger and younger factories grow more quickly and create more jobs than do smaller, older factories.
-If the pattern is the same with China, then it posits less of a concern to the long-run growth prospect of the Chinese economy.} However, the discussion of the implementation of specific policies is beyond the scope of the current study.
-
-%\textit{Relationship to Trade Models.---}The implication of our model on resource allocation along the intensive margin distinguishes us from many studies in international trade that use the \citet{Melitz:2003} model to study the environmental consequences of trade liberalization.
-A major difference between the distortions in our model and the trade costs in a standard Melitz model is that exporting is an endogenous choice of firms which brings extra revenues.
-A productive firm can choose not to pay the trade costs if it decides to stay domestic.
-As a result, though trade costs are a specific type of distortion that only affect exporting (productive) firms, they are different from the distortions in our model which are imperative.\footnote{The difference is not caused by our use of a \citet{Lucas:1978b} model instead of a \citet{Melitz:2003} model.
-Rather, it is because distortions in our model are a pure cost, while in the \citet{Melitz:2003} model, firms pay trade costs to access to foreign markets, which bring additional revenues.
-If instead we model in the \citet{Melitz:2003} model similar ``deadweight-loss'' distortions, we would get similar results.
-In fact, trade costs that lead to higher average factor product are indeed captured as distortions by our model.}
-%
-%Removing the distortions in our model is the same as trade liberalization in these models.
-However, intensified regulations yield different implications on resource allocation in our model comparing to those that arise from the standard Melitz model.
-The reason is that stronger regulation works as an increase in the entry costs, which foreign markets serve as a shelter to exporting firms.
-Hence, less productive firms are affected more.
-This illustrates how domestic distortions are conceptually different from trade costs.
-We believe that such difference is important because the scenario where regulations are strengthened while keeping the distortions is closely related to environmental policies in practice.
-In this sense, our findings compliment those in the trade literature by pointing out a different way that domestic distortions could affect the economy.\footnote{As an example, we compare our results with those from \citet{Bustos:2011}.
-The results of our first experiment are consistent with both the theoretical and empirical results of trade liberalization on technology adoption in her paper.
-We are further able to examine how the economy is affected if the government implements policies that target technology adoption in the presence of size-dependent distortions.}
-
-%\textit{Partial Equilibrium Interpretations.}--Some readers may be concerned that in reality, reduction of labor demand in one industry does not necessarily cause a decline of wages across the whole economy, thereby challenging the main mechanism of our model.
-We argue that the general logic carries well onto other model environments.
-First, what eventually matters in our model is not the wage {per se}, but the profits which are revenue less factor costs.
-In a partial equilibrium version or a \citet{Melitz:2003}-style version of our model where the wage and demand are both fixed, $\tau_z$ will push up the equilibrium price that the firms could charge.
-This is because with size-dependent $\tau_z$, the supply from the large productive firms is suppressed, where competition among consumers bids up the equilibrium price.
-Much of the quantitative results are still maintained in these situations.
-We choose to work with a general equilibrium Lucas model because it enables us to discuss the changes in output level.
-In fact, the results we present in the general equilibrium setting are stronger than those in the partial equilibrium counterparts.
-A decrease in the {average intensity} could well be accompanied by an increase in {aggregate pollution} if the output increases by too much.
-Second, if the labor markets in different industries are segmented, then a decrease in labor demand will in fact trigger a wage drop.
-Third, the nature of our comparison is to contrast economies {with} and {without} frictions as a whole, not any particular industry.
-Therefore, as long as the product market frictions exist at the aggregate level, wages will be {lower} in cases with frictions.
-
-\subsection{Effects of the Progressiveness of the Distortions}
-\label{sec:progressiveness}
-
-In Experiment (i), by setting $\tau_z = 0$, we change both the progressiveness and and the average level of firm-level distortions.
-To isolate the importance of the progressiveness of $\tau_z$, we solve a version of the model where the progressive taxes are replaced with uniform taxes by setting $\phi_1 =$ 0, and change $\phi_0$ to keep the total implicit tax revenue constant.\footnote{This strategy has a long tradition in the public finance and development economics literature.
-See for example, \citet{Ventura:1999}, \citet{ConesaKrueger:2006}, \citet{Bhattacharyaetal:2013} and \citet{BentoRestuccia:2016}, among others.} %To this end, the experiments resemble those in the taxation literature, where progressive taxes are compared with flat taxes.
-If we interpret $\tau_z$ literally as a tax, it would be unwise to suggest eliminating the whole tax system on manufacturing sector.
-This exercise could be interpreted as a counterfactual on policies that remove the size-dependent feature of current taxation policies in China.
-Not surprisingly, the implied uniform tax rate $\tau_z =$ 18\% is higher than the average tax rate of 13\% under the progressive tax system.
+\subsection{Effects of the Progressivity of the Distortions}
+\label{sec:progressivity}
+
+In Experiment (i), by setting $\tau_z = 0$, we change both the progressivity and and the average level of firm-level distortions.
+To isolate the importance of the progressivity of $\tau_z$, we solve a version of the model where the progressive taxes are replaced with uniform taxes by setting $\phi_1 =$ 0, and change $\phi_0$ to keep the total implicit tax revenue constant.\footnote{This strategy has a long tradition in the public finance and development economics literature.
+See for example, \citet{Ventura:1999}, \citet{ConesaKrueger:2006}, \citet{Bhattacharyaetal:2013} and \citet{BentoRestuccia:2016}, among others.} Not surprisingly, the implied uniform tax rate $\tau_z =$ 18\% is higher than the average tax rate of 13\% under the progressive tax system.
 Column (i') in Table \ref{tab:uniform} summarizes the results of this experiment and compares them to those from Experiment (i).
-A comparison of Column Benchmark and Column (i') reveals the effects of a change in progressiveness of $\tau_z$, while a comparison of Column (i') and (i) highlights the effects of a uniform change in tax rates across firms.
-
-%To further isolate the effect of the firm size distribution, we solve a version of the model where uniform distortions are imposed on all firms in the economy.
-More specifically, in this exercise, we set values of $\tau_z$ such that the total amount of taxes collected is the same as in the benchmark case with size-dependent $\tau_z$.
-This experiment reveals the quantitative effect of the size dependency of $\tau_z$.\footnote{To this end, the experiment resembles those in the taxation literature, where progressive taxes are compared with flat taxes.
-See, for example, \citet{Ventura:1999} and \citet{ConesaKrueger:2006}.} %To this end, the experiments resemble those in the taxation literature, where progressive taxes are compared with flat taxes.
-If we interpret $\tau_z$ literally as a tax, it would be unwise to suggest eliminating the whole tax system on manufacturing sector.
-This exercise could be interpreted as a counterfactual on policies that remove the size-dependent feature of current taxation policies in China.
-%The implied tax rate $\tau_z =$ 18\% is higher than the average tax rate in the size-dependent case, 13\%.
-Table \ref{tab:uniform} summarizes the results of the experiment.
-Columns benchmark and (i) present the results of the benchmark calibration and those from setting $\tau_z = 0$ from Table \ref{tab:aggregates}.
-We label the uniform tax case as (i').
-Comparing the benchmark with (i') allows us to assess the effect of the size dependency of $\tau_z$.
-Similarly, a comparison of (i') with (i) reveals the effect of levying a flat tax.
-Note that because a uniform $\tau_z$ imposed on all firms does not change the extensive margin compared with the zero $\tau_z$ situation, the measures of average talents, number of firms, and mean/median firm size are unaffected.
-This means that the effects of the uniform tax all work through the intensive margin.
+A comparison of Column Benchmark and Column (i') reveals the effects of a change in progressivity of $\tau_z$, while a comparison of Column (i') and (i) highlights the effects of a uniform change in tax rates across firms.
+
 \begin{table}[t]
@@
 \centering
-\begin{threeparttable}
-\caption{The Effects of the Progressiveness of Distortions}
-\begin{tabular}{p{90pt} >{\centering\arraybackslash}p{45pt} >{\centering\arraybackslash}p{45pt}>{\centering\arraybackslash}p{40pt} >{\centering\arraybackslash}p{5pt} >{\centering\arraybackslash}p{45pt} >{\centering\arraybackslash}p{45pt} >{\centering\arraybackslash}p{40pt}}
+\caption{The Effects of the Progressivity of Distortions}
+\begin{tabular}{lccccccc}
     \hline \hline
@@
     Statistics           & Benchmark & (i')      & (i)      & & Benchmark     & (i')    & (i) \\
-    \midrule
+    \hline
     Output               & 100.00    & 108.15   & 131.16    & & 100.00        & 106.87 & 129.62 \\
     Capital              & 100.00    & 110.91   & 163.06    & & 100.00        & 109.63 & 161.26 \\
-    Consumption\tnote{a} & 100.00    & 106.57   & 123.63    & & 100.00        & 106.57 & 123.63 \\
-    Wage\tnote{a}        & 100.00    & 108.76   & 160.00    & & 100.00        & 108.76 & 160.00 \\
+    Consumption          & 100.00    & 106.57   & 123.63    & & 100.00        & 106.57 & 123.63 \\
+    Wage                 & 100.00    & 108.76   & 160.00    & & 100.00        & 108.76 & 160.00 \\
     Output per Worker    & 100.00    & 105.74   & 128.25    & & 100.00        & 106.03 & 128.60 \\
-%    Output per Firm      & 100.00    & 245.39   & 297.62    & & 100.00        & 257.12 & 311.85 \\
-   \midrule
+    \hline
     \# of Firms          & 100.00    & 44.07    &44.07      & & 100.00        & 41.56  & 41.56 \\
     Mean Size            & 59.98     & 139.19   & 139.19    & & 52.18         & 126.53 & 126.53 \\
-    \midrule
+    \hline
     Pollution            & 100       & 70.04    & 76.67     \\
     Intensity            & 100       & 64.78    & 58.46     \\
-%    Pollution            & 100       & 73.27    & 81.66     \\
-%    Intensity            & 100       & 67.78    & 62.27     \\
     Clean Share          & 57.77     & 73.33    & 85.61     \\
-    \bottomrule
+    \hline
 \end{tabular}
 \begin{tablenotes}
-     \footnotesize{
-     \item[$\dagger$]
-     Note: All of the values are percentages except for mean firm size, which are the numbers of workers.
-     \item[a]
-     Consumption and wage are not sector specific.}
+     All of the values are percentages except for mean firm size, which are the numbers of workers. Consumption and wage are not sector specific.
 \end{tablenotes}
 \label{tab:uniform}
-\end{threeparttable}
 \end{table}
 
-As we can see from Table \ref{tab:uniform}, removing the progressiveness of $\tau_z$ increases aggregate output, capital, consumption and output per worker.
+As we can see from Table \ref{tab:uniform}, removing the progressivity of $\tau_z$ increases aggregate output, capital, consumption and output per worker.
 However, the 6\% to 11\% increases here are rather moderate compared to the 20\% to 60\% increases when all the distortions are eliminated.
@@
 
-However, removing the progressiveness of $\tau_z$ causes a large change in firm size distribution, and therefore large declines in aggregate pollution and pollution intensity.
+However, removing the progressivity of $\tau_z$ causes a large change in firm size distribution, and therefore large declines in aggregate pollution and pollution intensity.
 In fact, the resulting number of firms and mean firm size are the same between Experiment (i) and (i'), since the only difference between them is a uniform increase in tax rates across firms.
-The average pollution intensity decreases by 35\% when the progressiveness of $\tau_z$ is removed, compared to a 42\% decline when all the correlated distortions are eliminated.
+The average pollution intensity decreases by 35\% when the progressivity of $\tau_z$ is removed, compared to a 42\% decline when all the correlated distortions are eliminated.
 Again, the decline in average pollution intensity is caused by both an improved resource allocation and improved adoption of the clean technology among firms.
@@
 
-In sum, our findings imply that it is the progressiveness of distortions, rather than the average level of firm-level distortions, that plays a dominate role in amplifying aggregate pollution and pollution intensity.
-
-%The aggregate output, capital, consumption, output per worker, and output per firm in case (i') all increase compared with the benchmark case, which is consistent with the findings on size-dependent distortions in the literature.
-What is different here is that since the uniform tax rate needed to generate the same tax revenue is relatively high (the tax rate for the largest firm in the size-dependent case is 25\%), the tax itself still results in considerable output loss.
-The source of this output loss in our model works mainly through decrease in capital accumulation.
-However, for average pollution intensity, much of the reduction is achieved through the elimination of the size dependency of $\tau_z$.
-The adoption rate of the clean technology increases by 16 percentage points in case (i'), which is 56\% of the total increase resulting from the complete elimination of $\tau_z$.
-Moreover, 85\% of the total decline in average pollution intensity in the zero $\tau_z$ case is achieved by simply removing the size-dependent feature of $\tau_z$.
-Here, the non-polluting sector again behaves in a similar way, and hence the discussion is omitted.
-
-%\textit{Discussion.}---The finding that the size dependency of $\tau_z$ affects economic efficiency moderately is consistent with the results of \citet{Hopenhayn:2014}.
-In particular, he shows that the size dependency of the policy does not necessarily imply large distortions.
-What matters for the size of the distortion is the total amount of resources that are affected, not to which firms these resources belong.
-Studies such as \citet{RestucciaRogerson:2008} and \citet{Guneretal:2008} find that size-dependent policies affect economic efficiency more than flat taxes because such policies happen to affect a large amount of resources.
-The fact that we impose fairly large $\tau_z$ in the flat tax case explains why removing the size dependency of $\tau_z$ hardly improves the efficiency of the economy.
-
-%However, the size dependency of $\tau_z$ does matter for pollution, since it affects the {size distributions}.
-The reduction in pollution comes from two sources: the mechanical decrease in the production stage and the increase in the adoption rate of the clean technology since the intensity of regulation $\xi\pi^0(z)$ is increasing in $z$.
-More specifically, because the elimination of the size dependency of $\tau_z$ improves the resource allocation on the intensive margin, which increases the profits of large firms, the punishment from violating environmental regulations actually increases, thereby giving firms higher incentives to install clean technology.
-%Since the size distribution of the firm is purely affected by the {size-dependency} of $\tau_z$ and {not} by the size of the distortions (in the definition of \citet{Hopenhayn:2014}), although size-dependency does {not} necessarily imply significant efficiency loss, it {necessarily} results in aggravation of pollution.
-
-%\subsection{Environmental Regulations and Size Distribution}
-%
-%In our benchmark calibration, $k_E$ is about 2.5 times the equilibrium wage of a typical worker.
-This relatively small value limits the extent to which environmental policy can affect the real economy.
-In this section, we show that when $k_E$ is increased to 10 times the value used in the benchmark calibration, environmental policy influences the resource allocation markedly.
-We consider two scenarios.
-In the first case, we again solve the model with all the parameters remaining at the benchmark calibration level, but increase $k_E$ to 41.5.
-With no changes in regulation intensity, the adoption rate of the clean technology drops.
-In the second case, we increase $\xi$ such that the adoption rate in the benchmark case (57\%) is restored.
-We label these two experiments (iii) and (iv).
-%\begin{table}[t]
-%\footnotesize
-%\centering
-%\begin{threeparttable}
-%\caption{The Effect of Regulations: Higher $k_E$}
-%\begin{tabular}{p{125pt} >{\centering\arraybackslash}p{75pt} >{\centering\arraybackslash}p{75pt} >{\centering\arraybackslash}p{75pt}}
-%    \hline \hline
-%    Statistics                      & Benchmark             & (iii)                 & (iv)    \\
-%    \midrule
-%    Aggregate Output                & 100.00                & 100.00                & 100.41  \\
-%    Capital                         & 100.00                & 100.28                & 101.45  \\
-%    Consumption                     & 100.00                & 99.94                 & 100.21  \\
-%    Output per Worker (Wage)        & 100.00                & 100.00                & 99.63   \\
-%    Output per Firm                 & 100.00                & 100.00                & 187.70  \\
-%    Average Talent                  & 100.00                & 100.00                & 184.14  \\
-%%    TFP                             & 100.00                & 100.00                & 100.81  \\
-%    \midrule
-%    Number of Firms                 & 100.00                & 100.00                & 53.50   \\
-%    Mean Size                       & 59.27                 & 59.27                 & 111.65  \\
-%    Median Size                     & 22.95                 & 22.95                 & 63.24   \\
-%    \midrule
-%    Aggregate Pollution             & 100.00                & 125.64                & 87.56 \\
-%    Average Intensity               & 100.00                & 125.64                & 87.20 \\
-%    Clean Share                     & 57.40                 & 8.89                  & 57.06  \\
-%    Monitoring                      & 20.50                 & 20.50                 & 73.50  \\
-%    \bottomrule
-%\end{tabular}
-%\begin{tablenotes}
-%     \footnotesize{
-%     \item[$\dagger$]
-%     Note: All values reported are in percentage points except mean and median size, which are the absolute numbers of workers.}
-%\end{tablenotes}
-%\label{tab:aggregates_ke}
-%\end{threeparttable}
-%\end{table}
-%
-%Table \ref{tab:aggregates_ke} presents the results of experiments (iii) and (iv).
-For case (iii), we first note that the size distributions and efficiency of the economy remain virtually the same as in the benchmark case.
-However, the clean technology adoption rate falls to 9\% since a large number of firms now find it unprofitable to use the clean technology and higher pollution thus follows.
-Because the benchmark case can be understood as a decrease in the price of the clean technology from case (iii), this result suggests that subsidizing clean technologies can serve as a substitute for stronger regulations.
-%
-%If we increase the regulations to the level such that the original technology adoption rate is restored, as opposed to the results of case (ii) where the size distributions and resource allocation are only mildly affected, the effects of the regulation in experiment (iv) are much larger.
-Figure \ref{fig:envpolicy} shows the size and employment distributions for case (iv).
-%\begin{figure}[t]
-%    \begin{center}
-%    \includegraphics[width=0.45\textwidth]{D:/PaperDrafts/Pollution/PrelimResults/sizedist_bench_highcost.eps}
-%    \includegraphics[width=0.45\textwidth]{D:/PaperDrafts/Pollution/PrelimResults/eshare_bench_highcost.eps}
-%    \caption{Environmental Policy and Size Distribution}
-%    \label{fig:envpolicy}
-%    \end{center}
-%\end{figure}
-%In contrast to the size and employment distributions in the benchmark case, all the firms in the first group are driven out.
-This fact is also reflected in column (iv) of Table \ref{tab:aggregates_ke} as increases in average talent and in the mean/median size of the firms.
-Therefore, environmental policy {improves} the resource allocation on the {extensive} margin by forcing small unproductive firms to exit the market.
-However, the gains from these improvements are limited because the allocation of resources on the {intensive} margin worsens (see Table \ref{tab:talentdist_ke}).
-%\begin{table}[t]
-%\footnotesize
-%\centering
-%\begin{threeparttable}
-%\caption{Resource Allocation on the Intensive Margin: High $k_E$}
-%\begin{tabular}{p{65pt} >{\centering\arraybackslash}p{45pt} >{\centering\arraybackslash}p{45pt} >{\centering\arraybackslash}p{45pt} >{\centering\arraybackslash}p{45pt} >{\centering\arraybackslash}p{45pt}}
-%    \hline \hline
-%    Economy     & $\text{QU}_1$ & $\text{QU}_2$ & $\text{QU}_3$ & $\text{QU}_4$ & $\text{QU}_5$ \\
-%    \midrule
-%    Benchmark   & 2.69          & 4.19          & 7.29          & 16.55         & 69.28 \\
-%    Case (iv)   & 4.44          & 6.63          & 10.98         & 21.86         & 56.10 \\
-%    Case (i)    & 1.50          & 2.83          & 6.34          & 18.06         & 71.27 \\
-%    Case (ii)   & 2.93          & 4.47          & 7.77          & 17.37         & 67.46 \\
-%    \bottomrule
-%\end{tabular}
-%\begin{tablenotes}
-%     \footnotesize{
-%     \item[$\dagger$]
-%     Note: $\text{QU}_1$ to $\text{QU}_5$ represent the first to fifth quintiles, respectively.}
-%\end{tablenotes}
-%\label{tab:talentdist_ke}
-%\end{threeparttable}
-%\end{table}
-%An efficient allocation on the intensive margin is achieved in the no-size-dependent $\tau_z$ case [case (i)].
-Instead of an allocation of production toward larger firms as in the efficient case, here the production of firms in the bottom four quantiles expands significantly at the expense of the production share of the most productive firms.
-As a result, much of the gains in economic efficiency are offset by the worsening of the resource allocations on the intensive margin.
-Qualitatively, this result is the same as in case (ii).
-However, by comparing cases (ii) and (iv), we see that the larger fixed cost $k_E$, the higher is the degree of resource misallocation on the intensive margin .
-Although the level of industrial pollution lowers, the reduction could be much larger if the allocation on the intensive margin also improves, as in the case of the elimination of $\tau_z$.
-
-%\textit{Alternative Calibrations.}---Describe and analyze the results using the U.S calibration.
-%
-%\textit{Capital Market Frictions.}---Describe and analyze the results with capital market frictions.
+In sum, our findings imply that it is the progressivity of distortions, rather than the average level of firm-level distortions, that plays a dominate role in amplifying aggregate pollution and pollution intensity.
 
@@
 
-% Despite our novel findings, an important policy-related question remains: are there empirically observable size-dependent distortions that can generate quantitatively large effects on both firm size and pollution?
-Identifying observable policy distortions would also make it easier to collect more information on the costs of particular policy instruments, thereby allowing us to conduct a more complete cost-benefit analysis.
-Along this direction, our own work \citet{AGpaper} studies how migration and land policies affect the pollution from the overuse of agricultural chemicals in China.
-
 The analytical framework in this paper can be extended to other pollutants, sectors, and countries.
-For other pollutants, China also has a severe air pollution problem, and casual observations reveal that small and medium-sized firms in high-polluting industries such as steel contribute dispropotionately to air pollution in China.
+For other pollutants, China also has a severe air pollution problem, and casual observations reveal that small and medium-sized firms in high-polluting industries such as steel contribute disproportionately to air pollution in China.
 For other sectors, \citet{AGpaper} find that misallocation caused by migration and land policies is an important cause of agricultural pollution in China.
@@
 
-%Another limitation of this study is that we restricted our attention to examining industrial water pollution in China.
-Researchers could consider extending our analysis to other pollutants, sectors, and countries.
-For instance, China also has a severe air pollution problem, and it has overtaken the United States as the world's largest emitter of greenhouse gases.
-Casual observations reveal that small and medium-sized firms in high-polluting industries such as steel are an important source of sulfur dioxide, hazardous haze, and greenhouse gas emissions in China.
-For other developing countries, \citet{HsiehKlenow:2014} and \citet{BentoRestuccia:2016} find that size-dependent distortions negatively affect average firm size, while \citet{Dasguptaetal:1998} find that small firms have higher air pollution intensity in Brazil and Mexico.
-It would thus be interesting for future research to assess whether size-dependent distortions amplify pollution in these countries as well.
-
-%Finally, studies of urban economics and macroeconomics that adopt models that have rich macro and spatial implications are rising (\citet{Combesetal:2012}, \citet{DesmetRossihansberg:2013b}, \citet{DesmetRossihansberg:2014}).
-Industrial pollution naturally calls for interdisciplinary studies that analyze the environmental consequences of economic activities from a spatial perspective.
-Similar to the case presented herein, the agglomeration of pollution sources would be likely to change the costs and benefits structure of current studies where pollution is off the screen.
-We leave all these extensions to future studies.
-
-%\newpage
-%\begin{appendices}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%% Adjust the Layout of the Appendix %%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\setcounter{equation}{0}
-%\setcounter{lemma}{0}
-%\setcounter{corollary}{0}
-%\setcounter{proposition}{0}
-%\setcounter{figure}{0}
-%\setcounter{table}{0}
-%\renewcommand{\thesection}{\textnormal{\Alph{section}}}
-%\renewcommand{\thesubsubsection}{\textnormal{\thesubsection\arabic{subsubsection}}}
-%\titleformat*{\subsubsection}{\it \center}
-%\renewcommand{\theequation}{\thesubsection\arabic{equation}}
-%\renewcommand{\thefigure}{\thesubsection\arabic{figure}}
-%\renewcommand{\thetable}{\thesubsection\arabic{table}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%% Beginning of the Appendix %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{center}
-%\textsc{Appendix}
-%\end{center}
-%
-%\subsection{Accounting Exercises}
-%
-%This appendix provides robustness calculations of the accounting exercises.
-%
-%\textit{Estimation Strategies.}---Ideally, we would like to have the pollution intensity over firm size.
-However, such data do not exist since the NGSPS only reports total value of production and total amount of pollution.
-Therefore, we would need to construct pollution intensity over the number of employees.
-We use the CNEC for this purpose.
-In particular, we estimate the corresponding bins for production for each employment bin from the U.S data.
-%
-%SUSB reports firm size in 22 bins.
-For the U.S size bins, we construct the corresponding production bins to be used in NGSPS.
-CNES is used to bridge the employment bins (SUSB) to the production bins (NGSPS).
-%
-%\begin{enumerate}
-%  \item
-%  \textit{Non-parametric}:
-%    \begin{itemize}
-%    \item
-%    For each U.S employment bin, we compute the 1st quartile and 3rd quartile production levels for Chinese firms within that employment bin.
-The two quartiles are used as the lower and upper bounds for the production bins in NGSPS.
-%    \item
-%    We then use the median pollution intensity of firms within the newly defined production bins as the average pollution intensity for those bins.
-%    \item
-%    Lastly, we calculate the aggregate pollution by assigning to each bin the corresponding share of production. The NGSPS production bins are used for China and the employment bins are used for U.S.
-%    \end{itemize}
-%  \item
-%  \textit{Piecewise Linear}:
-%  \begin{itemize}
-%    \item
-%    For each U.S employment bin, we regress log-product on log-employment using the subset of Chinese firms within that employment bin.
-The lower and upper bounds for the production bins in this case are calculated as the predicted value of the above regression.
-%    \item
-%    We then run piecewise log-linear regression of pollution intensity on production within each new production bin.
-The average pollution intensity is chosen to be the predicted intensity at the midpoint of the new log-production bin.
-%    \item
-%    Lastly, the average intensity is applied to the production share distributions.
-The U.S distribution does not change, however, a new distribution for China is calculated since the endpoints of the production bins are different.
-%    \end{itemize}
-%  \item
-%  \textit{Parametric}:
-%  \begin{itemize}
-%    \item
-%    Using CNEC, we regress log-production on log-number of workers, which yields a {parametric} relationship between the number of workers and production.
-%    \item
-%    Using NGSPS, we regress log-intensity on log-production, which yields a {parametric} relationship between intensity and production.
-From these two relationships, we can subsequently construct a new \emph{parametric} relationship between intensity and number of employees.
-The average intensity is chosen to be the midpoint of each U.S employment bin.
-Notice that in this case we have a direct functional form for employment and intensity).
-%    \item
-%    Lastly, the average intensity is applied to the production share distributions.
-The U.S distribution does not change, but a new distribution for China is calculated since the endpoints of the production bins are different.
-Notice that this distribution for China is the one we use in Section \rom{1}.C.
-%\end{itemize}
-%\end{enumerate}
-%
-%The estimation results are shown in Table \ref{tab:accounting_appen}.
-Each of these three methods has its own advantages and disadvantages.
-The two non-parametric methods capture more of the variation at the local level, which could be washed out in a parametric estimation across the whole state space.
-However, this local nature also introduces a lot of instability on the estimations.
-Further, there are situations when there are gaps not covered by adjacent production bins and situations when these production bins overlap with each other.
-Under these conditions, some information will be lost while other is used for multiple times.
-Nevertheless, the results are robust across different estimation strategies.
-%\begin{table}[t]
-%\footnotesize
-%\centering
-%\begin{threeparttable}
-%\caption{Size Distribution on Pollution}
-%\begin{tabular}{lccccccc}
-%    \hline \hline
-%    Methods             & Paper  & Agricultural Food   & Textile    & Chemistry    & Beverage        & Average      \\
-%    \midrule
-%    Non-parametric      & 39.8\% & 60.7\% & 81.6\% & 102.5\% & 103.7\%      & 63.5\%  \\
-%    Piecewise-linear    & 34.8\% & 69.4\% & 93.5\% & 180.1\% & N/A\tnote{a} & 75.4\%  \\
-%    Parametric          & 43.5\% & 61.1\% & 97.5\% & 101.2\% & 89.0\%       & 67.0\%  \\
-%    \bottomrule
-%\end{tabular}
-%\begin{tablenotes}
-%     \footnotesize{
-%     \item[$\dagger$]
-%     Note: Please see notes of Table \ref{tab:top5summary} for acronyms of industries.
-For individual industries, the numbers reported are the aggregate pollution from the artificial U.S production structure as percentage from that of China.
-We use the 1st and 3rd quartile in the non-parametric calculation.
-Column 6 (Average) calculates the weighted average of these ratios using the percentage contribution in row one of Table \ref{tab:top5summary} as weights.}
-%     \item[a]
-%     Since the beverage industry has a lot fewer firms than the others, there are employment size bins with no corresponding firms in China, which invalidates the method.
-We set the ratio to 100\% in the calculation of the last two averages.
-%\end{tablenotes}
-%\label{tab:accounting_appen}
-%\end{threeparttable}
-%\end{table}
-%
-%\subsection{Proofs}
-%
-%In this section we provide formal proofs to the results in Section \rom{2}.C. For convenience, we state those results here again.
-%
-%\noindent PROOF OF LEMMA \ref{lemma:nofrictionpi_appen}:
-%\begin{lemma}
-%\label{lemma:nofrictionpi_appen}
-%In an economy with no product market frictions, $\pi_0(z)$ and $\pi_1(z)$ are both increasing and linear with respect to $z$. In addition, the slope of $\pi_1(z)$ is steeper than that of $\pi_0(z)$:
-%\begin{equation}
-%    \frac{\partial \pi_0 (z)}{\partial z} = (1 - p\xi)\frac{\partial \pi_1 (z)}{\partial z}, \qquad \forall z \in Z
-%\label{eq:lemma1ap}
-%\end{equation}
-%\end{lemma}
-%\begin{proof}
-%Since $k_E$ is sunk-cost, it does not affect firms' decision once is paid.
-The factor demand decisions for the two types of firms are therefore the same.
-The first order conditions for capital and labor are respectively
-%\begin{align}
-%    \label{eq:fock}
-%    & \frac{\partial \pi_i(z)}{\partial k}: \qquad \alpha \gamma z^{1-\gamma} k^{\alpha \gamma -1} n^{(1-\alpha)\gamma} = R \\
-%    \label{eq:focn}
-%    & \frac{\partial \pi_i(z)}{\partial n}: \qquad (1-\alpha) \gamma z^{1-\gamma} k^{\alpha \gamma} n^{(1-\alpha)\gamma-1} = W, \qquad i = 0,1
-%\end{align}
-%Dividing (\ref{eq:fock}) with (\ref{eq:focn}) yields constant capital to labor ratio $h$
-%\begin{equation}
-%    h = \frac{k}{n} = \frac{\alpha W}{(1-\alpha)R}
-%\end{equation}
-%which says more capital is demanded when technology is capital intensive (higher $\alpha$) or when capital rental price $R$ low.
-Notice that the system of equations (\ref{eq:fock}) with (\ref{eq:focn}) is log-linear and thus has closed-form solution.
-With some algebra, the solutions are characterized by
-%\begin{align}
-%    \label{eq:n}
-%    & n(z) = \Phi_1 R^{\frac{\alpha \gamma}{\gamma -1}} W^{\frac{1-\alpha \gamma}{\gamma-1}} \cdot z, \qquad \qquad \Phi_1 = \left[ \frac{(1-\alpha)^{\alpha \gamma}}{(1-\alpha)\gamma \alpha^{\alpha \gamma}}\right]^{\frac{1}{\gamma -1}} \\
-%    \label{eq:k}
-%    & k(z) = \Phi_2 R^{\frac{1+\gamma(\alpha -1)}{\gamma -1}} W^{\frac{\gamma(1-\alpha)}{\gamma-1}} \cdot z, \qquad \Phi_2 = \frac{\alpha}{1-\alpha}\Phi_1
-%\end{align}
-%Substitute the optimal solutions (\ref{eq:n}) and (\ref{eq:k}) back to the definition of profits functions (\ref{eq:pi1z}) and (\ref{eq:pi0z}), we have
-%\begin{align*}
-%    & \pi_0(z) = (1-p\xi)\left(\Omega - \frac{1}{1-\alpha}\Phi_1 \right) \kappa z, \qquad \Omega = \left(\frac{\alpha}{1-\alpha}\right)^{\alpha \gamma} \Phi_1^{\gamma} \text{ and } \kappa = W^{\frac{\gamma(1-\alpha)}{\gamma-1}} R^{\frac{\alpha\gamma}{\gamma-1}} \\
-%    & \pi_1(z) = \left(\Omega - \frac{1}{1-\alpha}\Phi_1 \right) \kappa z - R k_E
-%\end{align*}
-%where it is clear that both functions are increasing and linear in $z$ and (\ref{eq:lemma1ap}) is true.
-%\end{proof}
-%
-%\noindent PROOF OF COROLLARY \ref{lemma:frictionpi_appen}:
-%\begin{corollary}
-%\label{lemma:frictionpi_appen}
-%Suppose the product market frictions are specified as $\max\left\{ 0, 1 - z^{\phi_1} \right\}$ with $1 - \gamma + \phi_1 > 0$, then $\pi_0(z)$ and $\pi_1(z)$ are both increasing and concave with respect to $z$.
-In addition, the slope of $\pi_1(z)$ is steeper than that of $\pi_0(z)$:
-%\begin{equation*}
-%    \frac{\partial \pi_0 (z)}{\partial z} = (1 - p\xi)\frac{\partial \pi_1 (z)}{\partial z}, \qquad \forall z \in Z
-%\end{equation*}
-%\end{corollary}
-%\begin{proof}
-%The proof is straightforward given Lemma \ref{lemma:nofrictionpi_appen}. Substituting in the tax function, $\pi_0(z)$ and $\pi_1(z)$ now becomes
-%\begin{align*}
-%    & \pi_0(z) = (1-p\xi)\left(\Omega - \frac{1}{1-\alpha}\Phi_1 \right) \kappa z^{\frac{1-\gamma+\phi_1}{1-\gamma}} \\
-%    & \pi_1(z) = \left(\Omega - \frac{1}{1-\alpha}\Phi_1 \right) \kappa z^{\frac{1-\gamma+\phi_1}{1-\gamma}} - R k_E
-%\end{align*}
-%where $\Omega, \Phi_1$ and $\kappa$ are defined as in Lemma \ref{lemma:nofrictionpi_appen}.
-%
-%Assumption $1-\gamma+\phi_1 > 0$ guarantees the monotonicity of the profits functions. Concavity is easily verified by taking second order derivatives.
-%\end{proof}
-%
-%\noindent PROOF OF PROPOSITION \ref{prop:threshold_appen}:
-%\begin{proposition}
-%\label{prop:threshold_appen}
-%There exists a unique threshold $\hat{z}$ such that all household members with $z \leq \hat{z}$ choose to be workers and those with $z \geq \hat{z}$ become entrepreneurs.
-Further, $\hat{z}$ is the solution of $W = \pi(\hat{z})$
-%\end{proposition}
-%\begin{proof}
-%Since the overall profit function $\pi(z)$ is the upper envelope of $\pi_0(z)$ and $\pi_1(z)$, from Lemma \ref{lemma:nofrictionpi_appen} and \ref{lemma:frictionpi_appen} we know $\pi(z)$ is monotonic increasing.
-It is easy to verify that $\pi(0)=0$.
-Therefore, as long as $0<W<\pi(\overline{z})$, we can find a unique $\hat{z}$ such that $\pi(\hat{z})=W$, where uniqueness follows from monotonicity.
-The condition $0<W<\pi(\overline{z})$ is guaranteed in the general equilibrium version of our model by Inada condition on the production function.
-%\end{proof}
-%
-%\noindent PROOF OF PROPOSITION \ref{prop:friction_appen}:
-%\begin{proposition}
-%\label{prop:friction_appen}
-%Given $k_E, W, \tau_z$ and $R$, there exist unique thresholds $\tilde{z}_n$ and $\tilde{z}_f$ such that:
-%\begin{enumerate}[(i)]
-%    \item
-%    In the economy with no product market frictions, entrepreneurs with $z \leq \tilde{z}_n$ produce using dirty technology while those with $z > \tilde{z}_n$ produce using clean technology.
-%    \item
-%    In the economy with product market frictions, entrepreneurs with $z \leq \tilde{z}_f$ produce using dirty technology while those with $z > \tilde{z}_f$ produce using clean technology.
-%    \item
-%    $\tilde{z}_n < \tilde{z}_f$, that is, product market frictions impede the technology upgrade.
-%\end{enumerate}
-%\end{proposition}
-%\begin{proof}
-%Uniqueness follows from
-%\begin{equation*}
-%    \frac{\partial \pi_0 (z)}{\partial z} = (1 - p\xi)\frac{\partial \pi_1 (z)}{\partial z}, \qquad \forall z \in Z
-%\end{equation*}
-%and monotonicity under both the case with and without frictions.
-%
-%We can solve for analytical expression for $z_n$:
-%\begin{equation}
-%    z_n = \frac{R k_E}{p \xi \left[ \Omega \kappa^{\gamma} - \frac{1}{1-\alpha} \kappa \right]}
-%\label{eq:zn}
-%\end{equation}
-%where $z_n$ is simply the ``distance'' ($R k_E$) over ``speed'' ($p \phi \left[ \Omega \kappa^{\gamma} - \frac{1}{1-\alpha} \kappa \right]$).
-The ``distance'' in both cases are the same, so eventually whether $z_f$ lies left or right to $z_n$ depends on the ``speed'' of convergence.
-%
-%Using expressions of the profits functions with frictions, we can show that
-%\begin{equation}
-%\label{eq:zf}
-%    z_n = \frac{R k_E}{p \xi \left[ \Omega - \frac{1}{1-\alpha} \right] \kappa} < \left(\frac{R k_E}{p \xi \left[ \Omega - \frac{1}{1-\alpha} \right]\kappa}\right)^{\frac{1-\gamma}{1-\gamma+\phi_1}} = z_f^*
-%\end{equation}
-%which proves the proposition.
-%
-%One caveat is that the second inequality holds only if the number in the parentheses is greater than 1.
-We verify this in our quantitative analysis but restrain ourselves from discussing extreme cases where the condition is not hold.
-%\end{proof}
-%\end{appendices}
-%
-%\newpage
-\bibliography{D:/Dissertation/Literature/Dissertation1}
-%\bibliography{./Dissertation1}
 \bibliographystyle{aea}
-\bibliographystyle{apacite}
-%\bibliographystyle{apalike}
-%
-%\newpage
-%\begin{appendices}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%% Adjust the Layout of the Appendix %%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\setcounter{equation}{0}
-%\setcounter{lemma}{0}
-%\setcounter{proposition}{0}
-%\setcounter{table}{0}
-%\setcounter{page}{1}
-%\renewcommand{\thesection}{\textnormal{\Alph{section}}}
-%\renewcommand{\thesubsubsection}{\textnormal{\thesubsection\arabic{subsubsection}}}
-%\titleformat*{\subsubsection}{\it \center}
-%\renewcommand{\theequation}{\thesubsection\arabic{equation}}
-%\renewcommand{\thetable}{\thesubsection\arabic{table}}
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%% Beginning of the Appendix %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{center}
-%\textsc{Online Appendix: Not for Publication}
-%\end{center}
-%[TO BE COMPLETED.]
-%
-%The section is a backup of the contents to be contained in Online Appendix only and will be removed from the paper upon the completion of the first draft.
-%
-%\subsection{Detailed Descriptions of Data Sources}
-%
-%The source of data that we draw upon in Sections \rom{1}.B and \rom{1}.C of the main text is the \textit{National General Survey of Pollution Sources} (henceforth, NGSPS).
-Since to the best of our knowledge, the data were not used before in economic studies, we provide a detailed description of the dataset in this section.
-The content in this section is combined from:
-%\begin{itemize}
-%    \item
-%    \textit{Census Program of the National General Survey of Pollution Sources} {\begin{CJK}{GBK}{kai}(第一次全国污染源普查方案)\end{CJK}};
-%    \item
-%    \textit{Regulation on National General Survey of Pollution Sources [Decree of the State Council of the People's Republic of China (No.508)]} {\begin{CJK}{GBK}{kai}(全国污染源普查条例[中华人民共和国国务院令第508号])\end{CJK}}.\footnote{An official English translation is provided at the end of the current document.}
-%    \item
-%    \textit{Technical Specifications Requirements of the First National General Survey of Pollution Sources} {\begin{CJK}{GBK}{kai}(第一次全国污染源普查技术规定)\end{CJK}}.
-%\end{itemize}
-%
-%\subsubsection{General Introduction}
-%
-%The purpose of the NGSPS is to understand the number of pollution sources and their distribution in different industries and regions; to understand the generation, discharge and treatment of major pollutants; to establish records for key pollution sources; to build a pollution source information database and an environmental statistics platform; and to provide basis for formulating policies and plans for economic and social development and environmental protection.
-%
-%The term ``pollution source'' here refers to premises, facilities and equipment which discharge pollutants to environment in the process of production, living or other activities or have adverse impact on environment, as well as other sources that result in pollution.
-%
-%The NGSPS surveys all entities and self-employed households which have pollution sources within the borders of the People's Republic of China.
-The scope of the survey includes industrial pollution sources, agricultural pollution sources, domestic pollution sources, facilities for centralized treatment of pollution, and other facilities generating or discharging pollutants.
-In this paper, we focus on the industrial sources.
-The industrial sources include all production entities that belong to any of the 39 manufacturing industries according to the \textit{Industrial Classification for National Economic Activities} (GB/T4547-2002).
-A complete list of the industries is provided in Table .
-%
-%\textit{Key Sources.---}The observations in the industrial sources are divided into two groups, \textit{key sources} and \textit{regular sources}.
-Key firms are required to file questionnaires that are more detailed than those filed by the regular firms.
-A firm is categorized as a key source, if one of the following condition is satisfied:
-%\begin{enumerate}
-%    \item
-%    All production entities that discharge pollutants that contain heavy metal, hazardous waste, and radioactive substance.
-%    \item
-%    All production entities that belong to the 11 heavily polluting industries, which include: Paper and Paper Products; Food Processing; Raw Chemical Materials and Chemical Products; Textile; Ferrous Metal Smelting and Rolling Processing; Food Manufacturing; Production and Supply of Electric and Heating Power; Manufacturing of Leather, Fur, and Feather; Processing of Petroleum, Coking, and Nuclear Fuel; Manufacturing of Non-metallic Mineral Goods; Ferrous Metal Smelting and Rolling Processing.
-%    \item
-%    Firms with more than CNY 5 million in revenue that belong to the 16 key industries, which include: Beverage Manufacturing; Medicine Manufacturing; Chemical Fibers Manufacturing; Transportation Equipment Manufacturing; Coal Mining and Washing; Non-ferrous Metal Mining; Processing of Timber, and Manufacture of Wood, Bamboo, Rattan, Palm and Straw Products; Petroleum and Natural Gas Exploitation; General Purpose Machinery Manufacturing; Ferrous Metal Mining; Non-metal Mining; Apparel, Footwear and Caps Manufacturing; Water Production and Supply; Metal Products Manufacturing; Special Purpose Machinery Manufacturing; Communication Equipment, Computers and Other Electronic Equipment.
-%\end{enumerate}
-%A firm is categorized as a regular firm, if none of the above conditions holds.
-%
-%\textit{Variables.---}The industrial sources contain information of the following variables:
-%\begin{enumerate}
-%    \item
-%    Firm's basic registration information, geographic latitude and longitude, receiving water of firm's discharged wastewater, etc;
-%    \item
-%    The consumption of raw and intermediate inputs, including: water consumption, energy consumption (coal, petroleum, gas, electricity, etc), sulfur content of fuel, the consumption of hazardous intermediate input, etc.
-%    \item
-%    The quantity of each of the products produced by the firm.
-%    \item
-%    The type, size and number of the pollutants treatment equipment that the firms own.
-%    \item
-%    The generation, control, discharge and comprehensive utilization of various kinds of pollutants, and the operation of various kinds of pollution prevention and control facilities.
-%    \item
-%    The monitoring of pollutants emission, including: the date and frequency of the monitoring; the type, quantity, and concentration of the pollutant.
-%\end{enumerate}
-%
-%\textit{Pollutants Included.---}The pollutants included for the industrial sources are those that have general implications on pollution control. In particular, they are
-%\begin{enumerate}
-%    \item
-%    Wastewater: Chemical Oxygen Demand (COD), Ammonian, Petrochemicals, Volatile Phenols, Mercury, Cadmium, Plumbum, Arsenium, Hexavalent Chromium, Cyanidium.
-For Paper and Paper Product, Food Processing, Food Manufacturing and Beverage Manufacturing Industries, Five-days Biochemical Oxygen Demand ($\text{BOD}_5$) is added.
-For Urban Sewage Treatment Plants, Total Phosphorus, Total Nitrogen, and $\text{BOD}_5$ are added.
-%    \item
-%    Exhaust: Soot, Industrial Dust, Sulfur Dioxide.
-For Electrolytic Aluminium, Cement, Ceramic, Frosted Glass industries, Fluoride.
-For Vehicle Exhaust Census, Carbon Monoxide and Hydrocarbon are added.
-%    \item
-%    Industrial Solid Waste: Hazardous Waste (according to the \textit{National Catalogue of Hazardous Wastes}), Smelting Waste, Fly Ash, Slag, Coal Refuse, Gangue, Radioactive Slag.
-%    \item
-%    Plaster discharged by Desulfurization Facilities, Sludge generated by waste water treatment facilities, and remaining from burning hazardous waste.
-%    \item
-%    Radioactive pollution sources from utilization of Concomitant Radioactive Mineral and from Civil Nuclear Power Generation.
-%\end{enumerate}
-%
-%\subsubsection{Methods of Measurement}
-%
-%There are three methods that the data of pollutants discharge are collected, which in the priority of adoption when data from multiple sources are available, are \textit{Monitoring, Method of Emission Coefficient}, and \textit{Material Balance Method}.
-In this section, we go over these three methods and the principles that the three methods are used in practice.
-%
-%\textit{Monitoring.---}Monitored data are collected by measuring the actual quantity and pollutants concentration of wastewater and exhaust to infer the annual quantity of generation and discharge of certain types of pollutants.
-In addition, there are three sources that monitored data are obtained, which in the priority of adoption when data from multiple sources are available are: \textit{NGSPS monitoring, historical monitoring}, and \textit{online monitoring}.
-The NGSPS monitoring data are measured by the field staff of the survey in the survey year.
-The historical monitoring data are those measured and recorded in past three years, with the latest data having the highest priority.\footnote{There are in addition four different sources of historical data, in the order of adoption when more than one source are available, these four sources are: the historical data monitored by the local environmental authorities, the data monitored upon the completion of a newly constructed project, the data monitored by a third-party agency, and those that are self-reported by the firms.} The online monitoring data are those that are automatically uploaded by computerized and Internet-connected pollutants treatment equipment.
-Before historical and online monitoring data are accepted, the field staff of the survey examine to ensure that the production and pollutants treatment technology have not undergone substantial changes.
-%
-%A pollution source is subject to reporting monitored data, if any of the following four criteria is satisfied:
-%\begin{enumerate}
-%    \item
-%    National Monitored Key Pollution Sources {\begin{CJK}{GBK}{kai}(国控重点污染源)\end{CJK}}: all firms listed in the \textit{List of National Intensively Monitored Firms} {\begin{CJK}{GBK}{kai}(国家重点监控企业名单,环办函[2007]93号)\end{CJK}}.
-%    \item
-%    Facilities for Centralized Treatment of Pollution.
-%    \item
-%    Provincial Monitored Key Pollution Sources {\begin{CJK}{GBK}{kai}(省控重点污染源)\end{CJK}} that in sum account for 65\% of total provincial emission as is recorded in the \textit{2005 Environmental Statistic Yearbook}.
-That is for each of the major pollutants, starting from the most polluting firm and adding up the quantity of emission, all firms until the summation reaches the 65\% of the total provincial emission are recorded.
-The union of the list of firms for all major pollutants are thus the firms that belong to this category.
-%    \item
-%    Newly established projects since 2005 whose pollutants discharge is more than the least polluting firms in the Provincial Monitored Key Pollution Sources.
-%\end{enumerate}
-%These firms are later referred to as the \textit{monitored firms} in this document.
-%
-%Starting from 2007Q1, for all National Monitored Key Pollution Sources, Centralized Treatment Facilities, and Provincial Monitored Key Pollution Sources, waste water sources have to be monitored at least once per quarter, and exhaust sources have to be monitored at least once per six months.
-%
-%The actual monitoring practice is subject to the following guidelines:
-%\begin{enumerate}
-%    \item
-%    The monitoring of Mercury, Cadmium, Hexavalent Chromium, Plumbum, and Arsenium must be conducted at the discharge outlets of the individual factory workshops, with each outlets monitored separately.
-%    \item
-%    Other water-based pollutants are monitored at the outlets of the factory.
-%    \item
-%    The flow rates of wastewater and exhaust are monitored at the same time with the monitoring of pollutant discharge.
-%    \item
-%    The monitoring of pollution sources are conducted at the representative polluting time periods.
-%    \item
-%    All monitoring technical standards of wastewater pollutants follow \textit{Technical Specifications Requirements for the Monitoring of Surface Water and Wastewater} {\begin{CJK}{GBK}{kai}(地表水和污水监测技术规范, HJ/T91-2002)\end{CJK}} and \textit{Technical Specifications Requirements for the Monitoring of Wastewater Pollutants Emission} {\begin{CJK}{GBK}{kai}(水污染物排放总量监测技术规范, HJ/T92-2002)\end{CJK}}.
-%    \item
-%    For unstable wastewater sources, the samples are collected using \textit{Water Ratio Automatic Sampler}.
-%    \item
-%    All monitoring technical standards of exhaust pollutants follow \textit{The Determination of Particulates and Sampling Methods of Gaseous Pollutants from Exhaust Gas of Stationary Sources} {\begin{CJK}{GBK}{kai}(固定污染源排气中颗粒物测定和气态污染物采样方法, GB/T16157-1996)\end{CJK}}.
-%\end{enumerate}
-%
-%\textit{Method of Emission Coefficient.---}The generation and discharge of pollutants are calculated according to the \textit{Handbook of Emission Coefficient}, edited by the \textit{Chinese Academy of Sciences}.
-The benchmark coefficients are estimated based on firm's production technology, production scale, etc.
-The actual coefficients used are modified from the benchmark coefficients according to firm's use of intermediate inputs, managerial practice, and pollution treatment equipment installed.
-The actual pollutants generation and discharge are then calculated according to the actual production scale of the firm in year 2007.
-%
-%\textit{Material Balance Method.---}The Material Balance Method is an application of conservation of mass to the analysis of physical systems.
-By accounting for material entering and leaving a system, mass flows can be identified which might have been unknown, or difficult to measure without this technique.
-The exact conservation law used in the analysis of the system depends on the context of the problem, but all revolve around mass conservation, i.e.
-that matter cannot disappear or be created spontaneously.
-When applied, a firm's usage of intermediate inputs, energy consumption, water consumption, and production technology are considered simultaneously, in order that the calculated pollutants generation and discharge can realistically reflect the actual production and emission of the firm in reality.
-%
-%\textit{Principles of Data Source Selection.---}The adoption of the methods of measurement follow the following guidelines:
-%\begin{enumerate}
-%    \item
-%    The data of the Key Pollution Sources are obtained mainly through monitoring and the method of emission coefficient, while the material balance method is only used when the other two methods are not feasible.
-More specifically, the data of all firms that are identified as the monitored firms are obtained by monitoring.
-The data of other firms in the key sources are obtained by the method of emission coefficient.
-%    \item
-%    The data of the Regular Pollution Sources are obtained mainly through the method of emission coefficient, while the material balance method is only used when the method of emission coefficient is not feasible.
-%    \item
-%    Before accepted, the monitored data are compared with those calculated from the method of emission coefficient.
-If the discrepancy is less than 20\% of the monitored value, the monitored value is used.
-If the discrepancy is larger than 20\%, the production technology and operating status of the firm is examined.
-If the operating status is in compliance with that specified in the technical regulations of the monitoring practice (for example, the firm has to reach at least 75\% of its production capacity when the emission is monitored), the monitored data are accepted.
-Otherwise, the emission is calculated using the method of emission coefficient.
-%\end{enumerate}
-%
-%\subsubsection{Comparisons of Statistical Features}
-%
-%In this section, we present detailed evidence to show that the samples covered in the CNEC and those in the NGSPS are broadly comparable.
-%
-%\subsection{Modeling Strategies}
-%\label{sec:model_appen}
-%In the paper, we model the costs of adopting abatement technology as a fixed costs $k_E$, regardless of the production scale of firms.
-The readers may concern that this could be a mis-specification.
-Two alternatives arise naturally: fixed costs plus operating costs and scale-related fixed costs.
-In this section, we show that each alternative contradicts some of the empirical evidence we document from the data.
-%
-%\textit{Operating Costs.}---We start with the case of operating costs.
-Trimming the top 1\% observations for outliers, the distribution of the ratio of operating costs over total value of production is shown in Table \ref{tab:oprcost_appen}.
-%\begin{table}[h]
-%    \footnotesize
-%    \centering
-%    \begin{threeparttable}
-%    \caption{Operating Costs as a Fraction of Output}
-%    \begin{tabular}{cccccc}
-%    \hline \hline
-%    Minimum & 25\%      & 50\%      & 75\%      & Maximum   & Mean \\
-%    \midrule
-%    0       & 0.0013    & 0.0049    & 0.0143    & 0.2084    & 0.0150 \\
-%    \bottomrule
-%    \end{tabular}
-%    \label{tab:oprcost_appen}
-%    \end{threeparttable}
-%\end{table}
-%On average, operating costs of abatement equipment takes about 1.5\% of a firm's annual value of production.
-In addition, the median of the ratio is less than 0.5\%, suggesting that operating costs are negligible for more than 50\% of the firms.
-For conciseness consideration, we choose to omit them from the model.
-%
-%\textit{Fixed Costs Proportional to Production Level.}---We do observe in the data that firms with larger production scale tend to make larger investment in abatement equipments.
-For instance, the correlation between the log value of production and abatement equipment investment is equal to 0.64.
-However, the relationship significantly weakens if we remove the percentage interpretation implied by taking logarithmic.
-In fact, if we calculate the ratio of abatement equipment investment over total production of firms below certain quantiles, the ratio decreases gradually as we include more large firms into the calculation.
-Table \ref{tab:key_appen} reports the ratio of \textit{aggregate} treatment equipments installation costs as a fraction of \textit{aggregate} value of output when firms with size below certain quantiles are included.
-%\begin{table}[h]
-%    \footnotesize
-%    \centering
-%    \begin{threeparttable}
-%    \caption{Installation Costs as a Fraction of Output}
-%    \begin{tabular}{cccccc}
-%    \hline \hline
-%    25\%      & 40\%      & 60\%      & 80\%      & 95\% \\
-%    \midrule
-%    0.6195    & 0.2475    & 0.1151    & 0.0668    & 0.0433 \\
-%    \bottomrule
-%    \end{tabular}
-%    \label{tab:key_appen}
-%    \end{threeparttable}
-%\end{table}
-%Recall that we have documented that the unit-cost per processing capacity is also decreasing with the equipment capacity, together these facts suggest the existence of returns to scale of treatment equipments.
-%
-%\textit{Relative Prices of Physical versus Biological Equipment.}---We assume in the main text that only the installation of biological equipments requires a fixed costs.
-In this paragraph, we provide evidence in support of this choice.
-The distributions of prices for physical and biological equipments in absolute term (CNY 10,000 in year 2007) are listed in Table \ref{tab:fixcosts_appen}.
-%\begin{table}[t]
-%    \footnotesize
-%    \centering
-%    \begin{threeparttable}
-%    \caption{Relative Prices of Treatment Equipments}
-%    \begin{tabular}{lcccccc}
-%    \hline \hline
-%    Technologies    & Minimum & 25\%      & 50\%      & 75\%      & Maximum   & Mean \\
-%    \midrule
-%    Physical        & 0.002   & 2.000     & 6.000     & 25.000    & 800.000   & 36.140 \\
-%    Biological      & 0.04    & 30.00     & 85.00     & 260.00    & 4000.00   & 249.90 \\
-%    \bottomrule
-%    \end{tabular}
-%    \label{tab:fixcosts_appen}
-%    \end{threeparttable}
-%\end{table}
-%As is shown in Table \ref{tab:fixcosts_appen}, the costs of biological equipments is 7 to 15 times of those of the physical equipments.
-We further calculate the ratio of \textit{aggregate} treatment equipments installation costs as a fraction of \textit{aggregate} value of output for different technologies.
-We find that the ratio is 3.07\% for physical technology and 12.83\% for biological technology.
-In addition, the total investment of physical equipment over biological equipment is 0.087, meaning that the installation costs of physical equipments when aggregated across the economy are only 9\% of those of the biological equipments.
-%
-%These evidence suggest that comparing to biological equipment, the costs of installing physical treatment equipments are nearly negligible.
-Therefore in our later calculation we assume that only the adoption of biological equipment is costly.
-%
-%In summary, the evidence suggests that firms' investment in abatement equipment is increasing with production scale but to a much lesser extent in absolute term.
-Again for simplicity and without loss of generality, we choose the fixed costs modeling strategy.
-%
-%\subsection{Intensity-Size Correlation}
-%
-%\subsection{Size-Distribution}
-%
-%\subsection{Accounting Exercise}
-%
-%\subsection{Calibration}
-%
-%\subsection{The Partial Equilibrium Model}
-%\label{sec:partial_appen}
-%
-%\end{appendices}
+\bibliography{./Dissertation1}
 

### 2019-09-19 Documentation/Replication_Instruction.tex
ready for submission

@@
 \fancyhead[LE,RO]{\thepage}
-%\fancyhead[CE]{\textit{JI QI, XIN TANG AND XICAN XI}}
-%\fancyhead[CO]{\textit{THE SIZE DISTRIBUTION OF FIRMS AND INDUSTRIAL POLLUTION}}
+\fancyhead[CE]{\textit{AMERICAN ECONOMIC JOURNAL: MACROECONOMICS}}
+\fancyhead[CO]{\textit{QI ET AL.: FIRM SIZE DISTRIBUTION AND POLLUTION REPLICATION}}
 \cfoot{}
@@
 
-\title{\vspace{-1cm}\Large{\textsf{The Size Distribution of Firms and Industrial Water Pollution: A Quantitative Analysis of China} \\ \textsf{Replication Instruction}}}
+\title{\vspace{-1cm}\Large{\textsf{The Size Distribution of Firms and Industrial Water Pollution: A Quantitative Analysis of China} \\ \textsf{Replication Instructions}}}
 \author{

### 2019-09-20 Documentation/Replication_Instruction.tex
daily sync

@@
 There is no particular scientific reason that we use one statistical software (\textsc{Stata}) for data cleaning and the other (\code{R}) for empirical analysis.\footnote{Due to limited backward compatibility of \textsc{Stata} and that the \code{foreign} package of \code{R} supports only \code{.dta} files saved by \textsc{Stata} up to Version 12, to run the code without any modification, the reader would need \textsc{Stata} 12.
-Readers with more recent version of the \textsc{Stata} would need to either modify in the \code{.do} file everywhere \code{.dta} files are read and written, or use alternative \code{R} package (for instance \code{readstata13}) to convert the data in \bcode{cpsc\_convert.R} and \bcode{cec\_convert.R}.
+Readers with more recent version of \textsc{Stata} would need to either modify in the \code{.do} file everywhere \code{.dta} files are read and written, or use alternative \code{R} package (for instance \code{readstata13}) to convert the data in \bcode{cpsc\_convert.R} and \bcode{cec\_convert.R}.
 Compatibility of our code is not tested under such environments.
-However, none of our results should be affected though.} We do this simply because it is easier to handle Chinese characters with \textsc{Stata} while \code{R} switches back and forth between different datasets swiftly.
-Veterans of \textsc{Stata} (or \code{R}) should be able to replicate all the empirical results with just one software using our source code as reference with ease.
-In addition, which in fact should go without saying, for readers without a licence to MATALB, GNU Octave could be used instead.
+However, none of our results should be affected though.} Veterans of \textsc{Stata} or \code{R} should be able to replicate all the empirical results with just one software using our source code as reference with ease.
+In addition, it should go without saying that for readers without a licence to MATALB, GNU Octave could be used instead.
 
@@
 
-    Individual researchers not affiliated with the MEE and institutions under its direct supervision needs to submit the application through the official portal for Information Access (\begin{CJK}{GBK}{kai} 政府信息公开\end{CJK}) by the MEE at the following url: \url{http://www.mee.gov.cn/weihu/201706/t20170625_416641.shtml}.
+    Individual researchers not affiliated with the MEE and institutions under its direct supervision need to submit the application through the official portal for requesting Information Access (\begin{CJK}{GBK}{kai} 政府信息公开\end{CJK}) by the MEE at the following url: \url{http://www.mee.gov.cn/weihu/201706/t20170625_416641.shtml}.
 The url is retrieved on September 15th, 2019 and may vary in the future.
@@
     For an official introduction to the NGSPS and declassified information at the aggregated level, interested readers could refer to the book \textit{Data Collection of the National General Survey of Pollution Sources} (\begin{CJK}{GBK}{kai}《污染源普查数据集》, 中国环境科学出版社, 2011\end{CJK}), which is publicly available.
+We provide a summary in English in Online Appendix A of our paper.
     \item
@@
 However, to facilitate replication by the readers who have access to the datasets, we post the log files when running the analysis on our computer.
+More details on the log files are provided at the end of this note.
 
@@
 As typographical convention, we use \bcode{blue computer modern typewriter} to indicate \bcode{folders} and \bcode{files}.
-The current folder is referred to as \bcode{./}.
+The parent folder is referred to as \bcode{./}.
 \begin{itemize}
@@
         \item
-        \bcode{./cpsc\_convert.R}: converts the NGSPS to binary format of \code{R}.
+        \bcode{./cpsc\_convert.R}: converts the NGSPS to the binary format of \code{R}.
         \item
-        \bcode{./cec\_convert.R}: converts the CNEC to binary format of \code{R}.
+        \bcode{./cec\_convert.R}: converts the CNEC to the binary format of \code{R}.
         \item
@@
         \item
-        \bcode{./plot\_figures.m}: plots Figures 4 and 5 in the main text.
+        \bcode{./plot\_figures.m}: plots Figures 5 and 6 in the main text.
         \item
@@
 The NGSPS comes by 5 \textsc{Stata} \code{.dta} files.
-\bcode{keynum.dta} contains information of the key sources, while \bcode{reg1.dta} to \bcode{reg4.dta} host information of the regular sources.
+\bcode{keynum.dta} contains the information of the key sources, while \bcode{reg1.dta} to \bcode{reg4.dta} host the information of the regular sources.
 There are 4 files for the regular sources because of the technical limitation back when we initially applied for the data.
@@
 Our copy of the CNEC has two \textsc{Stata} \code{.dta} files.
-\bcode{cec2004\_large\_full.dta} holds those samples that overlap with the commonly used 2004 Annual Surveys of Industrial Firms, while \bcode{cec2004\_small.dta} contains small firms not surveyed in the annual ASIF.
+\bcode{cec2004\_large\_full.dta} holds those samples that overlap with the commonly used 2004 Annual Surveys of Industrial Firms (ASIF), while \bcode{cec2004\_small.dta} contains small firms not surveyed in the annual ASIF.
 Again, they should be placed under \bcode{./Empirical/Data/}.
 The file \bcode{cec\_clean.do} labels all the variables.
-Upon completion, the original un-labeled files will be replaced by files of the same name.
+Upon completion, the original un-labeled files will be replaced by files with the same name.
 
-With these two steps completed, the reader needs to convert the data from \textsc{Stata} \code{.dta} to the internal binary \code{R} format \code{.RData}.
-File \bcode{cpsc\_convert.R} converts \bcode{keynum.dta} to \bcode{KEYFIRM\_R.RData}, \bcode{regall.dta} to \bcode{REGFIRM\_R.RData} and \bcode{allfirms.dta} to \bcode{ALLFIRM\_R.RData}.
+With these two steps completed, the reader needs to convert the data from \textsc{Stata} \code{.dta} format to the internal binary \code{R} format \code{.RData}.
+The file \bcode{cpsc\_convert.R} converts \bcode{keynum.dta} to \bcode{KEYFIRM\_R.RData}, \bcode{regall.dta} to \bcode{REGFIRM\_R.RData} and \bcode{allfirms.dta} to \bcode{ALLFIRM\_R.RData}.
 Similarly, \bcode{cec\_convert.R} converts \\ \bcode{cec2004\_small.dta} to \bcode{DSMALL\_R.RData}, \bcode{cec2004\_large\_full.dta} to \bcode{DLARGE\_R.RData}.
@@
 
-In what follows, we will only be using the files converted by \code{R}.
+In what follows, we will only use the files converted by \code{R}.
 A list of the essential files is provided below.
@@
     \item
-    \bcode{DLARGE\_R.RData (DL)}: A subset of \code{CA} which overlaps with the 2004 Annual Surveys of Industrial Firm.
+    \bcode{DLARGE\_R.RData (DL)}: A subset of \code{CA} which overlaps with the 2004 ASIF.
     \item
@@
 The code is written such that each section is self-contained, so the readers do not have to run from the very beginning if she/he only wants to replicate a certain result.\footnote{That said, the readers should always check to ensure that all the functional packages of \code{R} are loaded.} Table \ref{tab:navi_main} summarizes the correspondence between the results in the paper (tables, figures, regression results, in-text numbers, etc.) and the section of code files that computes them, as well as data dependency.
-To further assist the readers to visually navigate through the code, important sections are always indicated by a 76-character line of \code{=}.
+To further assist the readers to visually navigate through the code, important code snippets are always indicated by a 76-character line of \code{=}.
 This is the longest line in all the source code, and should be those most visually noticeable amongst all.
@@
     \item
-    Table 1 is produced by the first part of \bcode{Descriptive.R}. All the numbers are printed to the terminal. Row 1 comes first, with Rows 2 and 3 follow.
+    Table 1 is produced by the first part of \bcode{Descriptive.R}. All the numbers are printed to the terminal. Row 1 comes first, with Rows 2 and 3 follow in order.
     \item
@@
 Columns 3 and 4 are calculated by normalizing the physical equipment level to 100.
-Regression results are then printed to the terminal.
-First is the unnumbered regression, with those of Regressions (2) and (3) follow in order.
+Regression results are then printed to the terminal: first the unnumbered regression, with those of Regressions (2) and (3) follow in order.
     \item
@@
     \item
-    The in-text number of the accounting exercise can be calculated from the results following executing \bcode{Accounting.R}.
-The 33\% reduction in the last paragraph of Section \rom{1}.C part \textit{An Accounting Exercise} can then be calculated as the weighted average of the variable \bcode{ppar} with Row 1 of Table 1 as the weight.
+    The in-text number of the accounting exercise can be calculated from the results when executing \bcode{Accounting.R}.
+The 33\% reduction in the last paragraph of Section \rom{1}.C part \textit{An Accounting Exercise} can then be calculated as the weighted average of the variable \bcode{ppar} with Row 1 of Table 1 being the weight.
 Notice that the variable \bcode{ppar} is exactly Row 3 of Table F.1.
@@
 There are four cases to be computed: the benchmark case, the no distortion case, the regulation case and the flat tax case.
-The reader need to manually set the parameters in \bcode{twosectors.m} for each cases, namely the distortions \code{tauzd, tauzc}, the regulation intensity \code{xi} and the file name at the very end.
-The code is set to compute and save the benchmark results initially.
+The reader needs to manually set the parameters in \bcode{twosectors.m} for each cases, namely for the distortions \code{tauzd, tauzc}, the regulation intensity \code{xi} and the file name at the very end.
+The code is tuned to compute and save the benchmark results initially.
 The code contains all the relevant statements.
-The readers only need to comment and un-comment the relevant sections, which should be very easy to locate by searching for the variable name.
+Hence the reader only needs to comment and un-comment the relevant sections, which should be very easy to locate by searching the variable name.
     \begin{enumerate}
@@
 Some information would be printed to the terminal.
-Please refer to the log file \bcode{twosectors\_log.pdf} for details.
+Please refer to the log file \bcode{quantitative\_main\_log.pdf} for details.
 The results are saved in \\ \bcode{./Quantitative/Results/benchmark\_new.mat}.
@@
         \item
-        Set \code{tauzd} and \code{tauzc} to the benchmark level, change \code{xi} to 0.355, and the export destination to \bcode{./Results/regulation\_new.mat}.
+        Set \code{tauzd} and \code{tauzc} back to the benchmark level, change \code{xi} to 0.355, and the export destination to \bcode{./Results/regulation\_new.mat}.
 The results will be saved in this file after execution.
@@
         \item
-        Set \code{tauzd} and \code{tauzc} to the flat tax level, reverse \code{xi} back to 0.23, and the export destination to \bcode{./Results/flattax\_new.mat}.
+        Set \code{tauzd} and \code{tauzc} to the flat tax level, reverse \code{xi} back to 0.23, and set the export destination to \bcode{./Results/flattax\_new.mat}.
 The results will be saved in this file after execution.
@@
 By changing the input files at the beginning of \bcode{compute\_tables.m} (in particular the 4 \code{.mat} just computed), \bcode{compute\_tables.m} prints the raw data of the corresponding entries in the same structure as the tables in the paper.
-Table 5 can be directly taken from the output \code{Table 5} of executing \bcode{compute\_tables.m} with the input being the corresponding cases.
+Table 5 can be directly taken from the output \code{Table 5} after executing \bcode{compute\_tables.m} with the input being the corresponding cases.
 Entries in Table 4 can be calculated from the \code{Table 4} of the benchmark case and Cases (i) and (ii), while that of Table 6 can be calculated from \code{Table 4} of the benchmark case and Case (i').
-The calculations of the relative changes are not automated, and the readers do have to do the calculations manually as we did.
+The calculations of the relative changes are not automated, and the reader does have to do the calculations manually as we did.
 We apologize for the inconvenience.
-The in-text decomposition of the total reduction to the contribution of size distribution and technology adoption can be performed using \bcode{misc.m}.
-The readers need to change the second input file to either \bcode{notax\_new.mat} or \bcode{regulation\_new.mat}, depending on the cases to compute.
+
+    The in-text decomposition of total reduction to the contribution of size distribution and technology adoption can be performed using \bcode{misc.m}.
+The reader needs to change the second input file to either \bcode{notax\_new.mat} or \bcode{regulation\_new.mat}, depending on the case to compute.
 The role of technology adoption is printed to the terminal, with the residual being that from the size distribution.
     \item
-    Several calibration targets are computed from the data as well. This last bulletin explains where they are computed.
+    Several calibration targets are computed from the data as well. This last bulletin point explains where they are computed.
     \begin{itemize}
@@
     \ \ \ Figure D.1                & \bcode{Empirical\_Appendix.R}   & \code{CA}                & Section 4  \\
-    \ \ \ Figure D.2                & \bcode{misc.m}       \\
+    \ \ \ Figure D.2                & \bcode{misc.m}                  & \code{*.mat} \\
     \textbf{Appendix D.2} \\
@@
 The code then repeats the exercise for the manufacturing sector as a whole.
-Results to the un-numbered regressions on Pages 7, 9 and 10 (the last one) are then printed to the terminal, with Figure C.2 exported to \bcode{./Empirical/Results/FigureC2.pdf}.
+Results of the un-numbered regressions on Pages 9 and 10 (the last one) are then printed to the terminal, with Figure C.2 exported to \bcode{./Empirical/Results/FigureC2.pdf}.
 
@@
 This requires the results from the benchmark case \bcode{./Quantitative/Results/benchmark\_new.mat}.
-The file hosts this figure would be \\ \bcode{./Quantitative/Results/FigureD2.eps}.
+The file that hosts this figure would be \\ \bcode{./Quantitative/Results/FigureD2.eps}.
     \item
@@
 Specifically, the 4 panels of Figures D.3 are first plotted and saved as \bcode{./Empirical/Results/FigureD3\_TopLeft.pdf}, \bcode{FigureD3\_TopRight.pdf}, \bcode{FigureD3\_BotLeft.pdf} and \bcode{FigureD3\_BotRight.pdf}.
-A series of results are then printed to the terminal: first are the in-text numbers of the mean of the ratio of adoption cost to output for firms with output in each quintile (22\%, 11\%, 6.7\%, 5.0\% and 2.7\%), second the coefficients of the un-numbered regression, with the results to Table D.3 come at last.
+A series of results are then printed to the terminal: first are the in-text numbers of the mean of the ratio of adoption cost to output for firms with output in each quintile (22\%, 11\%, 6.7\%, 5.0\% and 2.7\%), second the coefficients of the un-numbered regression, with the results of Table D.3 come at last.
     \item
@@
     \item
-    Finally, to reproduce Table J.1, one essentially follows the same logic as in the main text: namely execute \bcode{twosectors\_ces.m} many times with different parameter values, print the raw numbers for the corresponding variables and then manually compute the percentage changes in Table J.1.
+    Finally, to reproduce Table J.1, one essentially follows the same logic as in the main text: namely execute \bcode{twosectors\_ces.m} many times with different parameter values, print the raw numbers for the corresponding table entries and then manually compute the percentage changes in Table J.1.
 There are two cases in general, where CES $=$ 1.5 and CES $=$ 3.0.
@@
 They are conveniently grouped together in the code, under the snippet \bcode{\% CES = 1.5} and  \bcode{\% CES = 3.0}.
-The readers would also need to modify \code{tauzd} and \code{tauzc} for different scenarios.
-As before, all the statements have been coded; and the readers only need to comment and un-comment the relevant snippets of the code.
+The reader would also need to modify \code{tauzd} and \code{tauzc} for different scenarios.
+As before, all the statements have been coded; and the reader only needs to comment and un-comment the relevant snippets of the code.
 Likewise, the instruction to save the results at the end of the file also needs to be changed.
-One complication is that the readers need to set the initial guess for the market clearing prices.
+One complication is that the reader needs to set the initial guess for the market clearing prices.
 For each case, the initial guesses are conveniently stored in the code snippets at the beginning of Section \code{Solve the equilibrium wage}.
-The program is reasonable robust to different initial guesses.
-However, if the readers do not use the exact initial guess as we do, there may be very minor numerical difference for some of the variables.
+The program is reasonably robust to different initial guesses.
+However, if the readers do not use the exact initial guess we use, there may be very minor numerical difference for some of the variables.
 Similarly, if the reader uses other versions of MATLAB (we use 2016a) or Octave, such numerical errors would probably show up as well.
@@
         By default, \bcode{twosectors\_ces.m} is tuned to produce the benchmark results with CES $=$ 1.5.
-Executing the file would print some information to the terminal, again please refer to the log file \bcode{twosectors\_ces\_log.pdf} for detail.
+Executing the file would print some information to the terminal, again please refer to the log file \bcode{quantitative\_ces\_log.pdf} for detail.
 The equilibrium results are then saved under \\ \bcode{./Quantitative/Results/benchmark\_ces.mat}.
@@
         \item
-        Set both \code{tauzd} to zero and leave \code{tauzc} untouched, change the initial guesses and the export destination.
+        Set \code{tauzd} to zero and leave \code{tauzc} untouched, change the initial guesses and the export destination.
 The results for eliminating only the distortions in the polluting sector would be saved under \bcode{./Quantitative/Results/nodirty\_ces.mat}.
-This is case (ii) in Appendix J.
+This is Case (ii) in Appendix J.
         \item
@@
 The results for the no distortion case would be saved under \\ \bcode{./Quantitative/Results/notax\_ces.mat}.
-This case is labeled as case (i) in Appendix J.
+This case is labeled as Case (i) in Appendix J.
     \end{enumerate}
@@
     \item
-    Repeat Steps 9 and 10 with the parameters set to CES $=$ 3.0 then produces the lower panel of Table J.1, which finally completes the replication of all the results in our paper.
+    Repeating Steps 9 and 10 with the parameters set to CES $=$ 3.0 then produces the lower panel of Table J.1, which finally completes the replication of all the results in our paper.
 \end{enumerate}
@@
 The correspondence between the log files and the source code is as follows.
-The original log files are with the same name but postfix \code{.log}.
+The original log files are saved in text files of \code{.log} extension with the same names.
 For instance, executing the source code \bcode{cpsc\_raw.do} will generate a text log file \bcode{cpsc\_raw.log}, which we converted to \bcode{cpsc\_raw\_log.pdf} manually.

### 2019-09-23 Documentation/DataAppendix_AEJ_Final.tex
appendix proofread

@@
 
-For an official introduction to the NGSPS and declassified information at the aggregated level, interested readers could refer to the book \textit{Data Collection of the National General Survey of Pollution Sources} (\begin{CJK}{GBK}{kai}《污染源普查数据集》, 中国环境科学出版社, 2011\end{CJK}), which is publicly available.
+For an official introduction to the NGSPS and declassified information at the aggregate level, interested readers could refer to the book \textit{Data Collection of the National General Survey of Pollution Sources} (\begin{CJK}{GBK}{kai}《污染源普查数据集》, 中国环境科学出版社, 2011\end{CJK}), which is publicly available.
 
@@
 The NGSPS was a joint effort of multiple national ministries in China.
-The survey was organized directly by the State Council with data collection and quality control done by specially trained field staffs.
+The survey was organized directly by the State Council with data collection and quality control done by specially trained field staff.
 According to the Regulation on National General Survey of Pollution Sources [Decree of the State Council of the People's Republic of China (No.
 508)], faking data would lead to financial penalties or even lawsuits.
-The purpose of the NGSPS is to understand the number of pollution sources and their distribution in different industries and regions; to understand the generation, discharge and treatment of major pollutants; to establish records for key pollution sources; to build a pollution source information database and an environmental statistics platform; and to provide basis for formulating policies and plans for economic and social development and environmental protection.
+The purpose of the NGSPS is to understand the total number of pollution sources and their distribution in different industries and regions; to understand the generation, discharge and treatment of major pollutants; to establish records for key pollution sources; to build a pollution source information database and an environmental statistics platform; and to provide basis for formulating policies and plans for economic and social development and environmental protection.
 The term ``pollution source'' here refers to premises, facilities and equipment which discharge pollutants to environment in the process of production, living or other activities or have adverse impact on environment, as well as other sources that result in pollution.
 
-The survey covers all of the pollution units from agricultural, industrial, domestic sources, and facilities for the centralized treatment of pollution within the borders of the People's Republic of China.
+The survey covers all of the pollution units from agricultural, industrial, domestic sources, and facilities for centralized treatment of pollution within the borders of the People's Republic of China.
 In this study, we focus on the {industrial pollution sources}, which consist of businesses from 39 manufacturing industries according to the \textit{Industrial Classification for National Economic Activities} (GB/T4547-2002).
@@
 
-\textit{Key and Regular Sources.---}The firms in the industrial sources are divided into two groups, \textit{key sources} and \textit{regular sources}.
+\textit{Key and Regular Sources.---}Firms in the industrial sources are divided into two groups: \textit{key sources} and \textit{regular sources}.
 A key source firm is required to file questionnaires that are more detailed than those filed by the regular source firms.
-A firm is categorized as a key source, if one of the following condition is satisfied:
+A firm is categorized as a key source, if one of the following conditions is satisfied:
 \begin{enumerate}
@@
     \item
-    Firms with more than CNY 5 million in revenue that belong to the 16 key industries, which include: Beverage Manufacturing; Medicine Manufacturing; Chemical Fibers Manufacturing; Transportation Equipment Manufacturing; Coal Mining and Washing; Non-ferrous Metal Mining; Processing of Timber, and Manufacture of Wood, Bamboo, Rattan, Palm and Straw Products; Petroleum and Natural Gas Exploitation; General Purpose Machinery Manufacturing; Ferrous Metal Mining; Non-metal Mining; Apparel, Footwear and Caps Manufacturing; Water Production and Supply; Metal Products Manufacturing; Special Purpose Machinery Manufacturing; Communication Equipment, Computers and Other Electronic Equipment.
+    Firms with revenue of more than CNY 5 million in the 16 key industries, which include: Beverage Manufacturing; Medicine Manufacturing; Chemical Fibers Manufacturing; Transportation Equipment Manufacturing; Coal Mining and Washing; Non-ferrous Metal Mining; Processing of Timber, and Manufacture of Wood, Bamboo, Rattan, Palm and Straw Products; Petroleum and Natural Gas Exploitation; General Purpose Machinery Manufacturing; Ferrous Metal Mining; Non-metal Mining; Apparel, Footwear and Caps Manufacturing; Water Production and Supply; Metal Products Manufacturing; Special Purpose Machinery Manufacturing; Communication Equipment, Computers and Other Electronic Equipment.
 \end{enumerate}
@@
     \item
-    Firm's basic registration information, geographic latitude and longitude, the receiving water body of firm's discharged wastewater, etc.
-    \item
-    The consumption of raw and intermediate inputs, including: water consumption, energy consumption (coal, petroleum, gas, electricity, etc.), the sulfur content of fuel, the consumption of hazardous intermediate input, etc.
+    Firm's basic registration information, geographic latitude and longitude, the receiving water body wastewater discharged by the firm, etc.
+    \item
+    The consumption of raw and intermediate inputs, including: water, energy (coal, petroleum, gas, electricity, etc.), the sulfur content of fuel, hazardous intermediate input, etc.
     \item
@@
 
-\textit{Pollutants.---}The pollutants included for the industrial sources are those that have general implications on pollution control. In particular, these pollutants are as follows.
+\textit{Pollutants.---}The pollutants included for the industrial sources are those that have general implications on pollution control. These pollutants are as follows.
 \begin{enumerate}
@@
 
-There are three different methods to measure the level of pollutant emissions, which are \textit{Monitoring Method, Method of Emission Coefficient}, and \textit{Material Balance Method}.
+Three different methods are used to measure the level of pollutant emissions: \textit{Monitoring Method, Method of Emission Coefficient}, and \textit{Material Balance Method}.
 In this section, we describe these three methods and explain which method is used to determine the level of pollutant emissions in practice.
@@
 
-\textit{Monitoring Method.---}In this method, the actual quantity and concentration of pollutants are measured, which are used to infer the annual quantity of the generation and discharge of different pollutants.
-In practice, there are three sources from which the monitored data are obtained, ranked by the priority of adoption when data from multiple sources are available: \textit{NGSPS monitoring, historical monitoring}, and \textit{online monitoring}.
+\textit{Monitoring Method.---}With this method, the actual quantity and concentration of pollutants are measured, which are used to infer the annual quantity of the generation and discharge of different pollutants.
+In practice, there are three sources from which the monitored data are obtained.
+Ranked by the priority of adoption when data from multiple sources are available, they are \textit{NGSPS monitoring, historical monitoring}, and \textit{online monitoring}.
 The NGSPS monitoring data are collected by the field staff in the survey year (2007).
-The historical monitoring data are measured and recorded in the past three years, with the latest data having the highest priority.\footnote{There are four different sources of historical data, ranked again by the priority of adoption when data from multiple sources are available: the historical data monitored by the local environmental authorities, the data monitored upon the completion of a newly constructed project, the data monitored by a third-party agency, and those self-reported by the firms.} The online monitoring data are those automatically uploaded by computerized and Internet-connected pollutants treatment equipment.
+The historical monitoring data are measured and recorded in the past three years, with the latest data having the highest priority.\footnote{There are four different sources of historical data.
+Again, ranked by the priority of adoption when data from multiple sources are available, they are the historical data monitored by the local environmental authorities, the data monitored upon the completion of a newly constructed project, the data monitored by a third-party agency, and those self-reported by the firms.} The online monitoring data are those automatically uploaded by computerized and Internet-connected pollutants treatment equipment.
 Before the historical and online monitoring data are adopted, the field staff of the survey would ensure that the production condition and pollutant treatment technology have not undergone substantial changes.
@@
 
-A pollution source needs to report monitored data, if any of the following four criteria is met:
+A pollution source is required to report monitored data, if any of the following four criteria is met:
 \begin{enumerate}
     \item
-    Nationally Monitored Key Pollution Sources {\begin{CJK}{GBK}{kai}(国控重点污染源)\end{CJK}}: all firms listed in the \textit{List of National Intensively Monitored Firms} {\begin{CJK}{GBK}{kai}(国家重点监控企业名单,环办函[2007]93号)\end{CJK}}.
+    Nationally Monitored Key Pollution Sources {\begin{CJK}{GBK}{kai}(国控重点污染源)\end{CJK}}: all firms in the \textit{List of Nationally Monitored Key Pollution Sources} {\begin{CJK}{GBK}{kai}(国家重点监控企业名单,环办函[2007]93号)\end{CJK}}.
     \item
@@
     \item
-    Provincially Monitored Key Pollution Sources {\begin{CJK}{GBK}{kai}(省控重点污染源)\end{CJK}} that in sum account for 65\% of total provincial emission as is recorded in the \textit{2005 Environmental Statistic Yearbook}.
-That is for each of the major pollutants, starting from the most polluting firm and adding up the quantity of emission, all firms until the summation reaches the 65\% of the total provincial emission are recorded.
-The collection of the list of firms for all major pollutants provides the firms in this category.
-    \item
-    Newly established projects since 2005 whose pollutants discharge is higher than the least polluting firms in the Provincial Monitored Key Pollution Sources.
+    Provincially Monitored Key Pollution Sources {\begin{CJK}{GBK}{kai}(省控重点污染源)\end{CJK}} that in sum account for 65\% of total provincial emission as recorded in the \textit{2005 Environmental Statistic Yearbook}.
+That is for each of the major pollutants, starting from the most polluting firm and adding up the quantity of emission, all the firms until the summation reaches the 65\% of the total provincial emission recorded.
+The collection of the firms for all major pollutants makes the list.
+    \item
+    Newly established projects since 2005 whose pollutants discharge is higher than the least polluting firms in the Provincially Monitored Key Pollution Sources.
 \end{enumerate}
@@
 
-Starting from 2007Q1, for all Nationally Monitored Key Pollution Sources, Centralized Treatment Facilities, and Provincially Monitored Key Pollution Sources, waste water sources have to be monitored at least once per quarter, and exhaust sources have to be monitored at least once per six months.
+Starting from 2007Q1, for all Nationally Monitored Key Pollution Sources, Centralized Treatment Facilities and Provincially Monitored Key Pollution Sources, waste water sources have to be monitored at least once per quarter, and exhaust sources have to be monitored at least once per six months.
 
@@
     \item
-    The monitoring of Mercury, Cadmium, Hexavalent Chromium, Plumbum, and Arsenium must be conducted at the discharging outlets of individual factory workshops, with each outlets monitored separately.
+    The monitoring of Mercury, Cadmium, Hexavalent Chromium, Plumbum, and Arsenium must be conducted at the discharging outlets of individual factory workshops, separately for each outlets.
     \item
@@
     \item
-    The flow rates of wastewater and exhaust are monitored at the same time with the monitoring of pollutants discharges.
-    \item
-    The monitoring of pollution sources are conducted at the representative production and polluting time periods.
-    \item
-    All monitoring technical standards of wastewater pollutants follow \textit{The Technical Specifications Requirements for the Monitoring of Surface Water and Wastewater} {\begin{CJK}{GBK}{kai}(地表水和污水监测技术规范, HJ/T91-2002)\end{CJK}} and \textit{The Technical Specifications Requirements for the Monitoring of Wastewater Pollutants Emission} {\begin{CJK}{GBK}{kai}(水污染物排放总量监测技术规范, HJ/T92-2002)\end{CJK}}.
+    The flow rates of wastewater and exhaust are monitored at the same time with the that of pollutants discharges.
+    \item
+    The monitoring of pollution sources are conducted at representative production and polluting time periods.
+    \item
+    All monitoring technical standards of wastewater pollutants follow \textit{The Technical Specifications for the Monitoring of Surface Water and Wastewater} {\begin{CJK}{GBK}{kai}(地表水和污水监测技术规范, HJ/T91-2002)\end{CJK}} and \textit{The Technical Specifications for the Monitoring of Wastewater Pollutants Emission} {\begin{CJK}{GBK}{kai}(水污染物排放总量监测技术规范, HJ/T92-2002)\end{CJK}}.
     \item
@@
 
-\textit{Method of Emission Coefficient.---}In this method, the generation and discharge of pollutants are calculated according to the \textit{Handbook of Emission Coefficient}, edited by the \textit{Chinese Academy of Sciences}.
+\textit{Method of Emission Coefficient.---}With this method, the generation and discharge of pollutants are calculated according to the \textit{Handbook of Emission Coefficient} edited by the \textit{Chinese Academy of Sciences}.
 The benchmark coefficients are estimated based on firm's production technology, production scale, etc.
@@
 
-\textit{Material Balance Method.---}In this method, the quantities of the materials entering and leaving a system are measured, and therefore the material flows which might have been unknown or difficult to measure without this method are identified.
-The exact rule of conservation used in the analysis of the system depends on the specific context, but all rules revolve around mass conservation, i.e., that matter cannot disappear or be created spontaneously.
-In parctice, a firm's usage of intermediate inputs, energy consumption, water consumption, and production technology are used simultaneously, in order that the calculated pollutants generation and discharge can realistically reflect the actual production and emission of the firm in reality.
-%\textit{Material Balance Method.---}The Material Balance Method is an application of conservation of mass to the analysis of physical systems.
-By accounting for material entering and leaving a system, mass flows can be identified which might have been unknown, or difficult to measure without this technique.
-The exact conservation law used in the analysis of the system depends on the context of the problem, but all revolve around mass conservation, i.e.
-that matter cannot disappear or be created spontaneously.
-When applied, a firm's usage of intermediate inputs, energy consumption, water consumption, and production technology are considered simultaneously, in order that the calculated pollutants generation and discharge can realistically reflect the actual production and emission of the firm in reality.
+\textit{Material Balance Method.---}With this method, the quantities of the materials entering and leaving a system are measured.
+Therefore the material flows which might have been unknown or difficult to measure without this method are indirectly measured.
+The exact rule of conservation used in analyzing the system depends on specific context, but all rules revolve around mass conservation.
+In practice, a firm's usage of intermediate inputs, energy, water as well as production technology are considered simultaneously, in order that the calculated pollutants generation and discharge can realistically reflect the actual production and emission of the firm in reality.
 
@@
     The data of the Key Pollution Sources are obtained mainly through monitoring and the method of emission coefficient, while the material balance method is only used when the other two methods are not feasible.
-More specifically, the data of all firms that are identified as the monitored firms are obtained by monitoring.
+%More specifically, the data of all firms that are identified as the monitored firms are obtained by monitoring.
 The data of other firms in the key sources are obtained by the method of emission coefficient.
     \item
-    The data of the Regular Pollution Sources are obtained mainly through the method of emission coefficient, while the material balance method is used only when the method of emission coefficient is not feasible.
-    \item
-    Before being accepted, the monitored data are compared with those calculated from the method of emission coefficient.
+    The data of the Regular Pollution Sources are obtained mainly by the method of emission coefficient, while the material balance method is used only when the method of emission coefficient is not feasible.
+    \item
+    Before accepted, the monitored data are compared with those calculated from the method of emission coefficient.
 If the discrepancy is less than 20\% of the monitored value, the monitored value is used.
 If the discrepancy is larger than 20\%, the production technology and operating status of the firm are examined.
-If the operating status is in compliance with that specified in the technical regulations of the monitoring practice (for example, the firm has to reach at least 75\% of its production capacity when the emission is monitored), the monitored data are accepted.
+If the operating status is in compliance with that specified in the technical regulations of the monitoring practice (for example, the firm has to reach at least 75\% of its production capacity when the emission is monitored), the monitored data are used.
 Otherwise, the emissions are calculated using the method of emission coefficient.
@@
 %\section{Firm Size Distribution in NGSPS and CNEC}
-This section compares the firm size distributions for different samples of firms in China.
+This section compares the firm size distributions from the different samples.
 In Figure \ref{fig:distcomp}, we present the kernel densities of firm size estimated using different samples in NGSPS and CNEC.
@@
 \end{figure}
-On the upper panels, we plot the firm size distributions for the samples that consist of the key source firms (the left panel) and all firms (the right panel) in the NGSPS, respectively.
-On the lower panels, we plot the firm size distributions for the \textit{Annual Surveys of Industrial Firms (ASIF)} sample (the left panel), which consists of all state-owned firms and private firms with sales above CNY 5 million, and the sample of all firms (the right panel) in the CNEC.
+In the upper panels, we plot the firm size distributions of the key sources (the left panel) and all firms (the right panel) in the NGSPS respectively.
+In the lower panels, we plot those of the \textit{Annual Surveys of Industrial Firms (ASIF)} sample (the left panel), which consists of all state-owned firms and private firms with sales above CNY 5 million, and of all firms (the right panel) in the CNEC.
 There are two findings that we would like to emphasize:
@@
     \item
-    Although the key source firms are on average larger than the firms in the full sample, they include both small and large firms, and the empirical density of the log output of the key source firms resembles a bell shape.
-This suggests that the key source firms are reflecting the characteristics of the firms over the entire range of firm size.
-As a result, no systematic bias will be introduced when we use the key source firms to empirically analyze the relationship between pollution intensity/treatment technology adoption and firm size in Section \rom{1}.B.
+    Although the key source firms are indeed a bit larger on average, they include both small and large firms; and the empirical density of the log output of the key source firms resembles a bell shape.
+This suggests that the key source firms are reflecting the characteristics of the firms over the entire range of the firm size distribution.
+As a result, the systematic bias introduced when using the key source firms to empirically analyze the intensity/size relationship in Section \rom{1}.B would be limited.
     %The key firms in NGSPS cover broadly firms of all sizes.
@@
     There are marked differences in the firm size distributions between the ASIF sample and CNEC full sample, with the ASIF sample missing most of the small firms.
-As a result, while the ASIF data are widely used in the studies of Chinese economy, we use the CNEC full sample in our paper, because both the small and large firms play a critical role in our empirical and quantitative analysis.
+As a result, while the ASIF data are widely used in studies of Chinese economy, we use the CNEC full sample in our paper, because both the small and large firms play a critical role in our empirical and quantitative analysis.
    % The densities estimated from the CNEC full sample and the Annual Surveys of Industrial Production subsample show marked difference, with the Annual Survey samples missing all the small firms, of which a lot are covered by the NGSPS key firms.
@@
 
-In sum, the two take away points from the four panels in Figure \ref{fig:distcomp} are that the key firms in NGSPS are representative of both large and small firms, and that we have to use the CNEC full sample in companion with the NSGPS for our purpose.
+In sum, the two take away points from the four panels in Figure \ref{fig:distcomp} are that the key firms in NGSPS are representative of both large and small firms; and that it is more appropriate to use the CNEC full sample in companion with the NSGPS for our purpose.
 
@@
 In this section, we present additional results on the statistical relationship between firm size and pollution intensity.
-In Section C.1, we show the scatter-plots and regression results for individual polluting industries and and for the whole manufacturing sector as well.
-In addition, we show that the negative relationship between firm size and pollution intensity holds conditional on whether the firms are using physical, chemical or biological technologies.
-We also show that our results in Section \rom{1}.B remain robust if we cluster the standard errors by provinces.
-In Section C.2, we explain our estimates on coefficients of the dummy variables, and compare our findings with those from the existing literature.
+In Section C.1, we show the scatter-plots and regression results for individual polluting industry and for the whole manufacturing sector as well.
+In addition, we show that the negative relationship between firm size and pollution intensity continues to hold after conditioning on whether firms are using physical, chemical or biological technologies.
+We also show that our results in Section \rom{1}.B remain robust if we cluster the standard errors by province.
+In Section C.2, we provide a brief overview on our estimates on coefficients of the dummy variables, and compare our findings with those from the existing literature.
 
@@
 \end{equation*}
-where $\vec{X_p}$ is the provincial dummy, and $\vec{X_o}$ is the ownership dummy.
-The estimation results are summarized in Table \ref{tab:olsresults}, with the corresponding scatterplots plotted in Figure \ref{fig:codscatters}.
+where $\vec{X_p}$ are the provincial dummies and $\vec{X_o}$ are the ownership dummies.
+The estimation results are summarized in Table \ref{tab:olsresults}, with the corresponding scatterplots presented in Figure \ref{fig:codscatters}.
 We also include the scatterplot with the top five industries pooled together in Figure \ref{fig:codscatters} for completeness.
@@
 \end{equation*}
-which implies a negative correlation between firm size and pollution intensity.
-However, as we mentioned in Section \rom{1}.A of the main text, because industrial water pollutants are typically concentrated in a handful of industries, when we apply the above analysis to the whole manufacturing sector, we lose about two thirds of the manufacturing firms, as firms in many industries did not report positive COD emissions.
-Figure \ref{fig:codscatter} visualizes the above regression by plotting residuals after controlling for all the covariates.
+implying again a negative correlation between firm size and pollution intensity.
+However, as we mentioned in Section \rom{1}.A of the main text, because industrial water pollutants are typically concentrated in a handful of industries, when we apply the above analysis to the whole manufacturing sector, we lose about two thirds of the observations, because firms in many industries did not report positive COD emissions.
+Figure \ref{fig:codscatter} visualizes the above regression by plotting the residuals after controlling for all the covariates.
 Likewise, if we apply the linear regression of technology adoption in Section \rom{1}.B of the main text to the whole manufacturing sector, we get the following results:
@@
 
-For the size-intensity relationship conditional on treatment equipment, in Section \rom{1}.B of the main text, we group physical and chemical equipments together with an extra dummy variable for chemical equipment.
+For the size-intensity relationship by treatment equipment, in Section \rom{1}.B of the main text, we group physical and chemical equipments together with an extra dummy variable for chemical equipment.
 Here, we show that the relationship holds as well when we estimate the relation for each type of equipment separately:
@@
 The pollution intensity also exhibits rich provincial level variations.
-We take the regression results on the paper industry for example.
+We take the regression results on the paper industry for illustration purpose.
 Using Beijing as the benchmark, of all the remaining 29 provinces and municipalities, only the coefficient of Shanghai is negative and statistically insignificant.
-For the remainders, all estimates are positive and highly significant.\footnote{One province, Hebei is significant at 10\% level.
-Four others are significant at 1\% level while all others are significant at 0.1\% level.
-We notice here that Hebei, a province that is commonly considered as heavily affected by industrial pollution, is in fact an outlier, since the paper manufacturing is not its pillar industry.} The five most polluting provinces are Ningxia, Inner Mongolia, Gansu, Shaanxi and Xinjiang, for which the rankings of their provincial GDP in 2007 are respectively 29, 16, 27, 19 and 25 out of 31 provincial administrative regions (not including Hong Kong and Macau).
+For the remainder provinces, all estimates are positive and highly significant.\footnote{One province, Hebei is significant at 10\% level.
+We notice here that Hebei, a province that is commonly considered as heavily affected by industrial pollution, is in fact an outlier, since the paper manufacturing is not its pillar industry.} The five most polluting provinces are Ningxia, Inner Mongolia, Gansu, Shaanxi and Xinjiang, for which the respective provincial GDP ranking in 2007 are 29, 16, 27, 19 and 25 out of 31 provincial administrative regions (not including Hong Kong and Macau).
 Geographically, these are also inland provinces.
-In fact, despite that the majority of the paper manufacturers are located in Zhejiang and Guangdong (ranked 1st and 4th by GDP), the pollution level is lower comparing to those inland less developed regions.
+In fact, despite that the majority of the paper manufacturers are located in Zhejiang and Guangdong (ranked 1st and 4th by GDP), their pollution levels are lower comparing to those inland less developed regions.
 These patterns are highly robust across various specifications of our regressions.
@@
 First, Beijing and Shanghai, arguably the political and economic center of China, exert pollution control standard far more stringent than the rest provinces.
-Second, inland and less developed provinces in general have worse control over and are more prone to the industrial pollution problem.
-These two patterns are broadly consistent with the environmental Kuznetz curve and the results from previous literature.
+Second, inland and less developed provinces in general have worse control over and hence are more prone to industrial pollution problem.
+These two patterns are broadly consistent with the environmental Kuznetz curve and results from previous literature.
 However, unlike \citet{Jiangetal:2014}, ownership rights do not seem to have significant effects.
@@
 In Section \ref{sec:appen_techspec}, we justify our choice of modeling the adoption of advanced treatment technology as fixed costs.
-We also describe additional distributional features of the treatment technology, including the {processing efficiency, designed processing capacity}, and {installation costs}, using the Paper and Paper Product industry as an example.
+We also describe additional technical features of the treatment technology, including the {processing efficiency, designed processing capacity}, and {installation costs}, using the Paper and Paper Product industry as an example.
 Section \ref{sec:china_regulation} contains a brief summary of the environmental regulations in China.
@@
 
-Recent studies of the Chinese economy have described large distortions at both the sector and the firm levels, which negatively affect aggregate productivity and output considerably.\footnote{See \citet{HsiehKlenow:2009}, \citet{Songetal:2011}, \citet{Brandtetal:2013}, and \citet{TombeZhu:2015}, among others.} Following the seminal approach developed by \citet{HsiehKlenow:2009,HsiehKlenow:2014}, we model and estimate firm-level distortions by using variations in the average products of capital and labor across firms.\footnote{Though average factor product dispersion could arise due to dynamic capital adjustment [\citet{Askeretal:2014}], for the case of China, \citet{DavidVenkateswaran:2017} show that dynamic adjustment costs only accounts for about 10\% of the variation in average factor product in the data.
+Recent studies of the Chinese economy have found large distortions at both the sector and the firm level, which negatively affect aggregate productivity and output considerably.\footnote{See \citet{HsiehKlenow:2009}, \citet{Songetal:2011}, \citet{Brandtetal:2013}, and \citet{TombeZhu:2015}, among others.} Following the seminal approach developed by \citet{HsiehKlenow:2009,HsiehKlenow:2014}, we model and estimate firm-level distortions by using variations in the average products of capital and labor across firms.\footnote{Though average factor product dispersion could arise due to dynamic capital adjustment [\citet{Askeretal:2014}], for the case of China, \citet{DavidVenkateswaran:2017} show that dynamic adjustment costs only accounts for about 10\% of the variation in average factor product in the data.
 Naturally, we also cannot separate out variations in average factor product caused by firm-specific characteristics, for instance firm-specific markup or capital share.
@@
 Similarly, we can show that $\partial y/\partial k = (1-\alpha) \gamma (y/l)$.}
-More specifically, if we let $\tau_{z_i}, \tau_{k_i}$, and $\tau_{l_i}$ be the wedges that firm $i$ faces in the product, capital, and labor markets, respectively, the profit maximization problem of firm $i$ is:
+More specifically, if we let $\tau_{z_i}, \tau_{k_i}$, and $\tau_{l_i}$ be the wedges that firm $i$ faces in the product, capital and labor markets respectively, the profit maximization problem of firm $i$ is:
 \begin{equation*}
@@
 \end{equation*}
-By using the first-order conditions, the firm level average product of capital $\phi_{k_i}$, labor $\phi_{l_i}$, and the capital/labor ratio $\kappa_i$ can be expressed as
+By using the first-order conditions, the firm-level average product of capital $\phi_{k_i}$, labor $\phi_{l_i}$ and the capital/labor ratio $\kappa_i$ can be expressed as
 \begin{align}
@@
 \end{align}
-The above equations show that in the absence of any distortions ($\tau_{z_i} = \tau_{k_i} = \tau_{l_i} = $ 0), $\phi_{k_i}, \phi_{l_i}$, and $\kappa_i$ should be equalized across firms.
+The above equations show that in the absence of any distortions ($\tau_{z_i} = \tau_{k_i} = \tau_{l_i} = $ 0), $\phi_{k_i}, \phi_{l_i}$ and $\kappa_i$ should all be equalized across firms.
 Equations (\ref{eq:phik}) and (\ref{eq:phil}) state that firms that face higher distortions in the capital (labor) and/or product markets demonstrate a higher average product of capital (labor).
-In addition, according to Equation (\ref{eq:kappa}), the capital/labor ratio increases with the {relative} size of labor to the capital market wedge.
-By using firm-level data on total production value, the book value of capital stock, and labor compensation from the CNEC, we calculate $z_i, \phi_{k_i}, \phi_{l_i}$, and $\kappa_i$ for each firm in our sample.
+In addition, according to Equation (\ref{eq:kappa}), the capital/labor ratio increases with the {relative} size of labor to capital market wedge.
+By using firm-level data on total production value, the book value of capital stock and labor compensation from the CNEC, we calculate $z_i, \phi_{k_i}, \phi_{l_i}$, and $\kappa_i$ for each firm in our sample.
 Here we set $\gamma = $ 0.93, which is the calibrated value of returns to scale in the main text.
-Figure \ref{fig:phiklkappa} shows on log scales the scatterplots of $\phi_{k_i}, \phi_{l_i}$, and $\kappa_i$ against firm-level productivity $z_i$ for the Paper and Paper Products industry.
-We plot the Paper industry for demonstration purpose, qualitatively the results for all five polluting industries as well as all manufacturing industries combined are the same.
-\begin{figure}[t]
+Figure \ref{fig:phiklkappa} shows on log scale the scatterplots of $\phi_{k_i}, \phi_{l_i}$ and $\kappa_i$ against firm-level productivity $z_i$ for the Paper and Paper Products industry.
+We plot the Paper industry for demonstration purpose, qualitatively the results for all five polluting industries as well as all manufacturing industries combined are very similar.
+\begin{figure}[htbp]
     \begin{center}
@@
     \caption{Average Factor Products and Capital-Labor Ratio across Firm TFP Levels}
-    \floatfoot{Source: CNEC. All panels are plot in log scale. Lines are least square fit. Data of the Paper and Paper Product Industry are plotted.}
+    \floatfoot{Source: CNEC. All panels are plotted in log scale. Lines are least square fit. Data of the Paper and Paper Product Industry are plotted.}
     \label{fig:phiklkappa}
@@
 By using data from the World Bank's Enterprise Surveys, \citet{BentoRestuccia:2016} find that the elasticities range from 0.22 to 0.74, averaging 0.52.}
-This could be because more productive firms are subject to higher factor or product market distortions or both.
+This could be because that more productive firms are subject to higher factor or product market distortions or both.
 %Statistically, if we regress the average factor products to $\log z$, then for the five polluting industries, we get
@@
 
-As a result, following \citet{HsiehKlenow:2014} and \citet{BentoRestuccia:2016}, we model these distortions as implicit progressive output taxes, and the tax rate function takes the form used in the main text:%\footnote{This tax function has a long history in macro-public finance literature, which dates back to at least \citet{Benabou:2002}.
+As a result, following \citet{HsiehKlenow:2014} and \citet{BentoRestuccia:2016}, we model these distortions as implicit progressive output taxes; and the tax function takes the form used in the main text:%\footnote{This tax function has a long history in macro-public finance literature, which dates back to at least \citet{Benabou:2002}.
 We thank a referee for pointing this out.
@@
 \end{equation}
-where the parameter $\phi_0$ determines the mean level of the taxes, and the parameter $\phi_1$ determines the progressiveness of the taxes.
-When $\phi_1<0$, the tax rates are increasing in firm TFP $z$, and the progressiveness of the taxes is decreasing in the value of $\phi_1$.\footnote{Notice that since $\phi_1 < $0, decreasing $\phi_1$ increases its absolute value.} %\footnote{There is one difference between Equation (\ref{eq:tax}) and the tax function used by \citet{AdamopoulosRestuccia:2014}.
+where $\phi_0$ determines the mean level of the taxes, and $\phi_1$ determines the progressivity of the taxes.
+When $\phi_1<0$, the tax rates are increasing in firm TFP $z$, and the progressivity of the tax is decreasing in $\phi_1$.\footnote{Notice that since $\phi_1 < $0, decreasing $\phi_1$ increases its absolute value.} %\footnote{There is one difference between Equation (\ref{eq:tax}) and the tax function used by \citet{AdamopoulosRestuccia:2014}.
 To model the progressiveness, in their specification, the authors use an exponential function as opposed to the power function here.
@@
 Examples include size-dependent taxes and subsidies that favor small firms, imperfect tax enforcement that induces tax evasion among small firms, financial constraints and contractual frictions that impede the growth of productive firms [\citet{CooleyQuadrini:2001}, \citet{ClementiHopenhayn:2006} and \citet{Akcigitetal:2018}], and local protectionism and internal trade barriers that disproportionately affect large productive firms [\citet{Eberhardtetal:2016} and \citet{TombeZhu:2015}].
-While it is of great policy interest to study specific policies and institutions underlying $\tau_z$, we leave this important task to future work.\footnote{\citet{AdamopoulosRestuccia:2014} and \citet{AGpaper} are two recent examples where observable policy distortions are investigated.
-\citet{AdamopoulosRestuccia:2014} study the observable farm-level price distortions while our own work \citet{AGpaper} focuses on distortions created by migration and land distribution policies in China.}
+While it is of great policy interest to study specific policies and institutional features underlying $\tau_z$, we leave this important task to future work.\footnote{\citet{AdamopoulosRestuccia:2014} and \citet{AGpaper} are two recent examples where observable policy distortions are investigated.
+\citet{AdamopoulosRestuccia:2014} study the observable farm-level price distortions while our own work \citet{AGpaper} focuses on distortions created by migration and land policies in China.}
 
@@
 In the main text, we model the cost of adopting the clean technology as a fixed cost $k_E$ independent of the production scale of firms.
-In this subsection, we provide additional empirical evidence in support of this assumption using the firm-level data from the NGSPS.
+In this subsection, we provide empirical evidence in support of this assumption using the firm-level data from the NGSPS.
 
@@
 The linear probability model in the main text shows the first.
-Here we calculate the correlation between the log value of production and treatment equipment investment as well.
+Here we calculate the correlation between the log value of production and treatment equipment investment.
 Not surprisingly, we find that it is positive (0.64) as well.
@@
 \begin{equation*}
-    \log \left(\frac{\text{Investment}_i}{\text{Output}_i} \right) = \underset{(0.11)}{-0.73} - \underset{(0.004)}{0.40} \times \log (\text{Output}_i) + \vec{X} \gvec{\upgamma} + \varepsilon_i,
-\end{equation*}
-which shows a negative correlation as well. Together, the evidence supports our choice of modeling the adoption cost of clean technology as a fixed cost.
+    \log \left(\frac{\text{Investment}_i}{\text{Output}_i} \right) = \underset{(0.11)}{-0.73} - \underset{(0.004)}{0.40} \times \log (\text{Output}_i) + \vec{X} \gvec{\upgamma} + \varepsilon_i.
+\end{equation*}
+Together, the evidence supports our choice of modeling the adoption cost of clean technology as a fixed cost.
 
@@
 \end{table}
-As is shown in the table, the prices of biological equipments are 7 to 15 times of those of physical equipments.
+As is shown in the table, the prices of biological equipments are 9 to 15 times of those of physical equipments.
 In addition, the total installation costs of physical equipment for the top-5 polluting industries over those of biological equipment is only 0.087.
@@
 We proxy the {processing efficiency} using one minus the ratio of {emitted COD} to {generated COD}.
-The {designed processing capacity} (in tons) and {actual installation costs} are recorded directly by the data.
-We then calculate the {unit capacity costs} by dividing the installation costs by the processing capacity.
-We use the unit capacity costs as an indicator of returns to scale of clean treatment equipment.
-In Figure \ref{fig:techdiff}, in clockwise order we plot the density functions of processing capacity, installation costs, total value of industrial output and unit capacity cost by technology types.
+The {designed processing capacity} (in tons) and {actual installation costs} are recorded directly in the data.
+We then calculate the {unit capacity costs} by dividing the installation costs with the processing capacity.
+We use the unit capacity costs as an indicator of the returns to scale of clean treatment equipment.
+In Figure \ref{fig:techdiff}, in clockwise order we plot the density functions of processing capacity, installation costs, total value of industrial output and unit capacity cost by technology type.
 For all panels, log-scale is used in the horizontal axes.
-\begin{figure}[t]
+\begin{figure}[htbp]
     \begin{center}
@@
 Broadly speaking, biological technologies have the {best} processing efficiency, the {largest} processing capacity, the {highest} installation costs but the {lowest} unit capacity cost.
-More specifically, the mean and median processing efficiency of biological technology are 17 and 10 percentage points higher than the physical technology.
+More specifically, the mean and median processing efficiency of biological technology are 17 and 10 percentage points higher those of physical technology.
 %The density functions of processing capacity, installation costs and production scale for physical, chemical and biological equipments order from left to right while those of the unit capacity costs order from right to left.
@@
 
-Environmental regulations in China are specified in \textit{The Environmental Protection Law of the People's Republic of China (EPL)}.
+Environmental regulations in China are specified in \textit{The Environmental Protection Law of the People's Republic of China (EPL, {\begin{CJK}{GBK}{kai}中华人民共和国环境保护法\end{CJK}})}.
 The EPL was launched on trial basis in 1979 and was officially enacted by the National People's Congress in 1989.
 It was later amended in 1993 and 2003.
-The Ministry of Environmental Protection (MEP, previously the State Environmental Protection Administration) is in charge of the monitoring and administration of China's environmental issues.
-Two major policy instruments that the MEP uses are a pollution levy system and command-and-control instruments.
+The Ministry of Ecology and Environment (MEE, previously the State Environmental Protection Administration and the Ministry of Environmental Protection) is in charge of the monitoring and administration of China's environmental issues.
+Two major policy instruments that the MEE uses are a pollution levy system and command-and-control instruments.
 
@@
 
-In practice, the MEP oversees the enforcement of the EPL and the implementation of environmental policies.
+In practice, the MEE oversees the enforcement of the EPL and the implementation of environmental policies.
 Local Environmental Protection Bureaus (EPBs) are the main authorities that do the field work.
@@
 The EPBs send field staff to verify the credibility of firms' reports.
-The inspections include consistence between emissions, output, material usage, and across historical data.
+The inspections include consistence between emissions, output, material usage and across historical data.
 Field inspectors also conduct random on-site inspections of the emissions by firms without prior warning.
@@
 Serious violation sometimes also leads administrative detention and criminal charges similar to the case of fraudulent report of emissions.
-Because the pollution levy system is widely acknowledged for being ineffective in providing firms with incentives to control pollution [\citet{Dasguptaetal:2001}, \citet{WangWheeler:2005} and \citet{Lin:2013}], command-and-control instruments are usually used as a deterrence for potential violation by polluting firms.
+Because the pollution levy system is widely acknowledged for being ineffective in providing firms with incentives to control pollution [\citet{Dasguptaetal:2001}, \citet{WangWheeler:2005} and \citet{Lin:2013}], command-and-control instruments are usually used as deterrence for potential violation by polluting firms.
 The command-and-control instruments prove to be effective in many government-led campaigns against pollution.
@@
 We use the 2004 CNEC and 2004 Statistics of U.S.
-Businesses (SUSB) data to construct the firm size distributions in China and in the U.S., respectively.
-The SUSB organizes data around the so-called {enterprise} size groups instead of firm size groups.
+Businesses (SUSB) data to construct the firm size distributions in China and in the U.S.
+respectively.
+The SUSB organizes data by {enterprise} size groups instead of firm size groups.
 According to the definition in SUSB, a large enterprise could consist of firms that belong to different industries.
@@
 We then assign groups of firms to different size bins according to their average size.
-Such imputation introduces approximation errors.
+Such imputation introduces approximation errors naturally.
 %, but it is less likely for enterprises with less than 100 employees to have multiple firms.
-To further reduce the approximation noise, we group the size bins into four main groups: 1--19, 20--99, 100--399 and 400+.
+To reduce the approximation noise, we group the size bins into four main groups: 1--19, 20--99, 100--399 and 400+.
 The firm size distributions for each of the top polluting industries and all industries pooled together are shown in Figure \ref{fig:es}.
@@
 Unfortunately, the NGSPS only reports total output value and total amount of pollution at the firm level.
-Therefore, we need to construct pollution intensity over the number of employees.
+Therefore, we need to impute pollution intensity over the number of employees.
 To do this, we use the CNEC to estimate a relationship between employment and output.
@@
 employment bin.
-Notice that in this case we have a direct functional form for employment and intensity).
+Notice that in this case we have a direct functional form for the relationship between employment and intensity.
     \item
@@
 Further, there are situations when there are gaps not covered by adjacent output bins and situations when these output bins overlap with each other.
-Under these conditions, some information will be lost while others are used for multiple times.
-Nevertheless, the results are robust across different estimation strategies.
-In the Section \rom{1}.C of the main text, we use the results from the parametric method.
+Under these conditions, some information will be lost with other being used for multiple times.
+Nevertheless, the results are reasonably robust across different estimation strategies.
+In the Section \rom{1}.C of the main text, we use the results of the parametric method.
 
@@
 We also include additional analytical results in this section.
-Specifically, in Section \ref{sec:appen_proof_tech}, Lemma \ref{lemma:nofrictionpi_appen} and Corollary \ref{lemma:frictionpi_appen} highlight the key trade-off that firms face in deciding which type of treatment technology to install, when firms are and are not subject to correlated distortions respectively.
+Specifically, in Section \ref{sec:appen_proof_tech}, Lemma \ref{lemma:nofrictionpi_appen} and Corollary \ref{lemma:frictionpi_appen} highlight the key trade-off that firms face in deciding which type of treatment technology to install, depending on whether they are subject to correlated distortions or not.
 Lemma \ref{prop:threshold_appen} shows the standard results of the \citet{Lucas:1978b} model where household members choose their occupations according to their comparative advantage.
 In Section \ref{sec:appen_proof_pollution}, in a simple one-sector model with a fixed number of firms and \emph{exogenous} firm-level pollution intensity, we present the conditions under which removing the progressiveness of the distortions would reduce average pollution intensity.
-In Section \ref{sec:appen_proof_melitz}, we show the qualitative equivalence between the effects of distortions on aggregate output and pollution in the \citet{Lucas:1978b} model with those in the closed-economy version of the \citet{Melitz:2003} model.
+In Section \ref{sec:appen_proof_melitz}, we show the qualitative equivalence between the effects of distortions on aggregate output and pollution in the \citet{Lucas:1978b} model with those in a closed-economy version of the \citet{Melitz:2003} model.
 Many researchers working with heterogeneous firms models are more familiar with the \citet{Melitz:2003} setup as opposed to the \citet{Lucas:1978b} setting, especially in the trade and environment community.
@@
 
-In this section, we prove Proposition 1 of the main text. To simplify notation, we set $\phi_0 =$ 1 in this section.
-
-\noindent PROOF OF LEMMA \ref{lemma:nofrictionpi_appen}:
+In this section, we prove Proposition 1 of the main text. To simplify notation, we set $\phi_0 =$ 1 in this section. We begin with a couple of lemmas.
+
 \begin{lemma}
@@
 \end{align}
-Dividing (\ref{eq:fock}) with (\ref{eq:focn}) yields constant capital to labor ratio $h$
+Dividing (\ref{eq:fock}) by (\ref{eq:focn}) yields constant capital to labor ratio $h$
 \begin{equation*}
@@
 
-\noindent PROOF OF COROLLARY \ref{lemma:frictionpi_appen}:
 \begin{corollary}
@@
 
-\noindent PROOF OF LEMMA \ref{prop:threshold_appen}:
 \begin{lemma}
@@
 One caveat is that the second inequality holds only if the number in the parentheses is greater than 1.
-We verify this in our quantitative analysis but restrain ourselves from discussing extreme cases where the condition is not hold.
+We verify this in our quantitative analysis but restrain ourselves from discussing extreme cases where the condition does not hold.
 \end{proof}
@@
 A measure one of the members are managers, while a measure $N$ are workers.
-The occupation of household members are fixed once born.
+The occupations of household members are fixed once born.
 Each manager is endowed with $z$ units of managerial talent, which is drawn from a log-normal distribution $G(z)$ with logarithmic mean and standard deviation $(\mu, \sigma)$.
-Workers supply one unit of labor inelastically in exchange for wage income, and managers run a neoclassical firms and earn profits.
+Workers supply one unit of labor inelastically in exchange for wage income; and managers run a neoclassical firms and earn profits.
 In the simplified economy, labor is the only production factor.
@@
 \end{equation*}
-where $-1<\psi_1<1$ captures the negative correlation between output level and emission intensity as documented in Section \rom{1}.B of the main text.
+where $-1<\psi_1<0$ captures the negative correlation between output level and emission intensity as documented in Section \rom{1}.B of the main text.
 
@@
 
-\noindent PROOF OF PROPOSITION 2:
 \begin{proposition}
@@
 \end{equation*}
-is a constant independent of $\phi_1$. Notice that inside the bracket in Equation (\ref{eq:agge_phi1}) is a parabola opening to the bottom. Importantly, the axis of the parabola is
+is a constant independent of $\phi_1$. Notice that inside the bracket in Equation (\ref{eq:agge_phi1}) is a parabola opening to the bottom. Importantly, the symmetry axis of the parabola is
 \begin{equation}
@@
 
-\noindent PROOF OF COROLLARY \ref{prop:intensity_distortion_appen}:
 \begin{corollary}
@@
 When $\psi_1 < (1-2\gamma)/\gamma$, its opening is to the top, and hence the intensity is always increasing in distortions $\phi_1$.
-On the other hand, when $\psi_1 \geq (1-2\gamma)/\gamma$, the parabola is opening to the bottom with the axis being
+On the other hand, when $\psi_1 \geq (1-2\gamma)/\gamma$, the parabola is opening to the bottom with the symmetry axis being
 \begin{equation}
@@
 \end{equation}
-which gives us items (ii) and (iii) of Corollary \ref{prop:intensity_distortion_appen} immediately. Straight forward comparison of Equations (\ref{eq:phi1hat}) and (\ref{eq:phi1bar}) yield item (iv).
+which gives us items (ii) and (iii) of Corollary \ref{prop:intensity_distortion_appen} immediately. Straight forward comparison of Equations (\ref{eq:phi1hat}) and (\ref{eq:phi1bar}) yields item (iv).
 \end{proof}
@@
 \end{equation*}
-instead of as that in Equation (\ref{eq:ez_simple}), then Equations (\ref{eq:agge_phi1}) and (\ref{eq:aggi_phi1}) become
+instead of that in Equation (\ref{eq:ez_simple}), then Equations (\ref{eq:agge_phi1}) and (\ref{eq:aggi_phi1}) are simplified to
 \begin{equation*}
@@
 
-The two equations imply that first, the average pollution intensity is always increasing in distortions; and second, aggregate pollution is increasing in distortions, as long as the elasticity of distortions to productivity $|\phi_1|$ is larger than that of pollution $|\psi_1|$.
+The two equations show that first, the average pollution intensity is always increasing in distortions; and second, aggregate pollution is increasing in distortions, as long as the elasticity of distortions to productivity $|\phi_1|$ is larger than that of pollution $|\psi_1|$.
 Intuitively, this simply says that when output is more responsive to firm size, it dominates the effect of firm-level pollution intensity.
@@
 First, in the equilibrium, there needs to be a non-degenerated distribution of firms with different levels of productivity.
-Second, the model should feature resource allocation along the extensive margin and intensive margin, where we refer to the selection of firms into production as the extensive margin, and the distribution of factors among active firms as the intensive margin.
-Mathematically, what we really need is decreasing returns to scale in profits which prevents the most productive firm from taking over all the resources in the economy and profits be a function in productivity which creates selection.
+Second, the model should feature resource allocation along both the extensive and intensive margin, where we refer to the selection of firms into production as the extensive margin, and the distribution of factors among active firms as the intensive margin.
+Mathematically, what we really need are decreasing returns to scale in profits which prevents the most productive firm from taking over all the resources in the economy and profits be a function in productivity which creates selection.
 The curvature could come from decreasing returns to scale in production as in \citet{Lucas:1978b}, or from the demand and market structure as in \citet{Melitz:2003}.
-We need curvature from one source or the other, but \textit{not} necessarily from both.\footnote{In fact, \citet{Hopenhayn:1992} has directly assumed that the profit function is increasing in productivity [Assumption A.2.(b)] without specifying the underlying mechanism, and \citet{Bartelsmanetal:2013} have assumed diminishing returns in production and utility coexist (page 319).} To ease the exposition, we first show the equivalence using only the backbone elements with no distortions or emissions.
+We need curvature from one source or the other, but \textit{not} necessarily from both.\footnote{In fact, \citet{Hopenhayn:1992} had directly assumed that the profit function is increasing in productivity [Assumption A.2.(b)] without specifying the underlying mechanism, and \citet{Bartelsmanetal:2013} had assumed diminishing returns in production and utility coexist (page 319).} To ease the exposition, we first show the equivalence using only the backbone elements with no distortions or emissions.
 We then show that a similar version of Proposition \ref{prop:pollution_distortion_appen} holds under the monopolistic competition structure as well.
@@
 \begin{equation*}
-    \pi(z) = \left[\left(\frac{\gamma}{W}\right)^{\frac{\gamma}{1-\gamma}} - W\left(\frac{\gamma}{W} \right)^{\frac{1}{1-\gamma}} \right]z,
-\end{equation*}
-and Equation (\ref{eq:melitz_selection}) stays the same, it can be seen that the two models are equivalent, with the elasticity of substitution $\rho$ in the monopolistic setting plays the same role as the span-of-control parameter $\gamma$.
+    \pi(z) = \left[\left(\frac{\gamma}{W}\right)^{\frac{\gamma}{1-\gamma}} - W\left(\frac{\gamma}{W} \right)^{\frac{1}{1-\gamma}} \right]z.
+\end{equation*}
+With Equation (\ref{eq:melitz_selection}) being the same, it can be seen immediately that the two models are equivalent, with the elasticity of substitution $\rho$ in the monopolistic setting plays the same role as the span-of-control parameter $\gamma$.
 In fact, in the \citet{Lucas:1978b} model, one can think of firms as earning rents over the managerial talent $z$.
@@
 \end{equation*}
-which is decreasing in the progressiveness of distortions $-\phi_1$.
+which is decreasing in the progressivity of distortions $-\phi_1$.
 The impact of distortions on aggregate output in this case is equivalent to that in the Lucas span-of-control case of Section \ref{sec:appen_proof_pollution} [Equation (\ref{eq:aggy_simple})].%, as long as we create a one-to-one mapping between the elasticity of substitution among varieties $\rho$ in \citet{Melitz:2003} and the span-of-control parameter $\gamma$ in \citet{Lucas:1978b}.
@@
 However, as can be seen from Figure \ref{fig:phiklkappa},  there are also substantial variations in average products across firms with the same TFP level.\footnote{We thank a referee for pointing this out.} In the language of \citet{RestucciaRogerson:2008}, these variations suggest the existence of \emph{uncorrelated} distortions, which are uncorrelated with firm TFP.
-In this section, we use the same model in Section \ref{sec:appen_proof_pollution}, except that the firm-level distortions are uncorrelated with firms' productivity $z$, to study the impact of uncorrelated distortions on aggregate output and pollution.
+In this section, we use the same model in Section \ref{sec:appen_proof_pollution}, except that the firm-level distortions are now uncorrelated with firms' productivity $z$, to study the impact of uncorrelated distortions on aggregate output and pollution.
 We find that unlike the case of correlated distortions, uncorrelated distortions lower both aggregate output and aggregate pollution.
@@
 
-In this section, we explain in greater details the differences between our paper and the literature on how international trade affects the environment through the reallocation across heterogeneous firms.
+In this section, we explain in greater detail the differences between our paper and the literature on how international trade affects the environment through the reallocation across heterogeneous firms.
 Specifically, our paper differs from this literature in following ways.
@@
 
-\textit{Technology Adoption.---}A unique feature of our data is that we observe both the emissions and treatment technologies at the firm level.
+\textit{Technology Adoption.---}A unique feature of our data is that we observe both the emissions and treatment technologies at the firm-level.
 Using the data on treatment technologies, we provide an explanation for the negative correlation between firm size and pollution intensity.
@@
 This differentiates our paper from empirical work such as \citet{Andersen:2016} and \citet{Holladay:2016}.
-Specifically, \citet{Andersen:2016} studies the effects of credit constraints on pollution using regional data, which provides only indirect evidence on the firm behavior.
-While \citet{Holladay:2016} shows that on average exporters tend to be cleaner, but does not provide an explanation for this fact.
+Specifically, \citet{Andersen:2016} studies the effects of credit constraints on pollution using regional data, which provides only indirect evidence on firm's behavior; while \citet{Holladay:2016} shows that on average exporters tend to be cleaner, the paper does not provide an explanation for this fact.
 %It also differentiates our work from \citet{ShapiroWalker:2015}, where environmental regulation works as a residual (and hence can include a wide range of factors) to match the model with the data.
@@
 \textit{Implications for Environmental Regulations.---}The implication of our model for environmental regulations distinguishes us from studies that emphasize the role of trade costs, most of which build their models on the \citet{Melitz:2003} model.
-A major difference between the distortions in our model and the trade costs in an open-economy Melitz model is that exporting is an endogenous choice of firms which brings extra revenues.\footnote{In Section \ref{sec:appen_proof_melitz}, we establish the qualitative equivalence between the effects of distortions on aggregate output and pollution in \citet{Lucas:1978b}, and those in the \emph{closed-economy} version of \citet{Melitz:2003}.}A productive firm can choose not to pay the trade costs if it decides to stay domestic, while the distortions in our model are imperative and are purely deadweight losses.
+A major difference between the distortions in our model and the trade costs in an open-economy Melitz model is that exporting is an endogenous choice of firms which brings extra revenues.\footnote{In Section \ref{sec:appen_proof_melitz}, we establish the qualitative equivalence between the effects of distortions on aggregate output and pollution in \citet{Lucas:1978b}, and those in a \emph{closed-economy} version of \citet{Melitz:2003}.}A productive firm can choose not to pay the trade costs if it decides to stay domestic, while the distortions in our model are imperative and are purely deadweight losses.
 In addition, they interact with environmental regulations in different ways.
 In our model, environmental regulations would worsen resource allocation along the intensive margin, but this is not necessarily the case with trade costs, because the productive exporting firms can use foreign markets as a cushion to buffer the burdens from environmental regulations after paying the trade costs.
-We believe that such differences are policy-relevant, because in many cases environmental authorities have to make policy decisions in the presence of distortions.
+We believe that such differences are policy-relevant, because in many cases environmental authorities have to make policy decisions with the presence of distortions.
 
@@
 Admittedly an extreme assumption, it is not critical to our quantitative results in the main text, because the counterfactual experiments there cause little reallocation across sectors.
-However, if we want to evaluate the effects of removing distortions from one sector only, this assumption is problematic because it would imply a reallocation across sectors that is too large.
+However, if we want to evaluate the effects of removing distortions from one sector only, this assumption is problematic because it would imply a reallocation across sectors that is unrealistically large.
 To address this issue, we build a two-sector model in which the final goods are produced by a representative producer, who combines the intermediate goods from the polluting and non-polluting sectors using a constant elasticity of substitution (CES) production function.
@@
 Table \ref{tab:aggregates_appen} presents the results.
-In the upper panels, we report the results for $\rho =$ 1.5 and in the lower panels $\rho =$ 3.
+In the upper panel, we report the results for $\rho =$ 1.5 and in the lower panel $\rho =$ 3.
 For experiment (i), it is reassuring to see that for both levels of elasticity of substitution, the results are quantitatively similar to the perfect substitutes case in the main text.
@@
 
-For Experiment (ii), we start with the case $\rho =$ 1.5.
+For Experiment (ii), we start with the case of $\rho =$ 1.5.
 Following the elimination of $\tau_z$ in the polluting sector, there again are a large increase in output and a large decrease in average pollution in the polluting sector.
@@
 
-When $\rho =$ 3,  the cross-sector reallocation of factors would be much larger given a higher elasticity of substitution.
-The physical output of the polluting sector increases by 60\% instead of 35\% in this case, and while physical output of the non-polluting sector decreases by 11\% instead of 2\%.
+When $\rho =$ 3, the cross-sector reallocation of factors is much larger given a higher elasticity of substitution.
+The physical output of the polluting sector increases by 60\% instead of 35\% in this case, while physical output of the non-polluting sector decreases by 11\% instead of 2\%.
 As a result, although the average pollution intensity decreases by 44\%, the aggregate pollution in this case decreases by only 10\% as opposed to 20\% when $\rho =$ 1.5.
@@
 However, as we mentioned above,  $\rho =$ 3 is likely to be upper bound of the range for empirically plausible elasticity of substitution in our model, given that we divide the whole economy into two broad sectors.
-Hence, our results suggest that even if we remove the distortions from the polluting sector only, the technique effect would still dominate within the empirically plausible range of $\rho$.%the effects on aggregate pollution are smaller when the elasticity of substitution $\rho$ is larger, but the technique effect would still dominate within the empirically plausible range of $\rho$.
+Hence, our results suggest that even if we remove the distortions from the polluting sector only, the technique effect would still dominate within empirically plausible range of $\rho$.%the effects on aggregate pollution are smaller when the elasticity of substitution $\rho$ is larger, but the technique effect would still dominate within the empirically plausible range of $\rho$.
 

### 2019-09-23 Documentation/Pollution_Final_AEJ_Template_Ver2.tex
printing

--- 2019-09-19 Documentation/Pollution_Final_AEJ_Template.tex
@@
 \author{Ji Qi, Xin Tang, and Xican Xi\thanks{%
-Qi: Chinese Academy for Environmental Planning, Room 709-B BeiKeChuangYe Tower, No.10 Dayangfang, Beiyuan Road, Beijing, China, 100012 (e-mail: qiji@caep.org.cn); Tang: Wuhan University and International Monetary Fund, 700 19th St NW, Washington D.C., United States, 20431 (e-mail:zjutangxin@gmail.com); Xi: School of Economics, Fudan University, 600 Guoquan Road, Shanghai, China, 200433 (e-mail:xicanxi@fudan.edu.cn).
-We are grateful for the comments from Alexis Anagnostoupolos, Marina Azzimonti, Juan Carlos Conesa, Berthold Herrendorf, Nicolai Kuminoff, Pietro Peretto, Edward Prescott, Diego Restuccia, Todd Schoellman, Kerry Smith, Daniel Yi Xu, Gustavo Ventura, the editor and three anonymous referees.
-We also benefited from the comments received at Arizona State University, the Chinese Academy of Environmental Planning, Duke University, the IMF, U.S International Trade Commission, Peking University, Shanghai University of Finance and Economics, Singapore Management University, Stony Brook University, Washington State University, Wuhan University, and Zhejiang University.
+Qi: Chinese Academy for Environmental Planning, Room 709-B BeiKeChuangYe Tower, No.10 Dayangfang, Beiyuan Road, Beijing, China, 100012 (e-mail: qiji@caep.org.cn); Tang: Wuhan University and the International Monetary Fund, 700 19th St NW, Washington D.C., United States, 20431 (e-mail:zjutangxin@gmail.com); Xi: China Center for Economic Studies, School of Economics, Fudan University, 600 Guoquan Road, Shanghai, China, 200433, and  Shanghai Institute of International Finance and Economics (e-mail:xicanxi@fudan.edu.cn).
+We are grateful for the comments from Alexis Anagnostoupolos, Marina Azzimonti, Juan Carlos Conesa, Berthold Herrendorf, Nicolai Kuminoff, Pietro Peretto, Edward C.
+Prescott, Diego Restuccia, Todd Schoellman, V.
+Kerry Smith, Daniel Yi Xu, Gustavo Ventura, the editor and three anonymous referees.
+We also benefited from the comments received at Arizona State University, the Chinese Academy for Environmental Planning, Duke University, the International Monetary Fund, the U.S.
+International Trade Commission, Peking University, Shanghai University of Finance and Economics, Singapore Management University, Stony Brook University, Washington State University, Wuhan University, and Zhejiang University.
 We sincerely thank the China Ministry of Ecology and Environment for granting us access to the National General Survey of Pollution Sources data.
@@
 Quantitatively, eliminating these correlated distortions would increase output by 30\% and decrease pollution by 20\%.
-Meanwhile, environmental regulations have sizable impact on pollution but only limited effect on output.
+Meanwhile, environmental regulations have sizable impact on pollution but limited effects on aggregate output.
 \end{abstract}
@@
 
-Severe pollution has accompanied China's remarkable economic growth in the past few decades, causing environmental degradation, public health damage, and millions of premature deaths.\footnote{\citet{WorldBank_Cost_2007} estimates that the cost of air and water pollution in China is about 6\% of GDP.
-The health cost of pollution is estimated to be 4\% of GDP, the majority of which is associated with premature deaths caused by pollution.
-See \citet{Vennemoetal:2009} and \citet{ZhengKahn:2013} for review of empirical studies on environmental pollution in China.} Understanding the driving forces behind this severe pollution is crucial for designing and evaluating anti-pollution policies.
+Severe pollution has accompanied China's remarkable economic growth in the past few decades, causing environmental degradation, public health damage, and millions of premature deaths.\footnote{\citet{WorldBank_Cost_2007} estimates that the total costs of air and water pollution in China are about 6\% of China's GDP.
+The health costs of pollution are estimated to be 4\% of GDP in China, the majority of which are associated with premature deaths caused by pollution.
+See \citet{Vennemoetal:2009} and \citet{ZhengKahn:2013} for reviews of empirical studies on pollution in China.} Understanding the driving forces behind this severe pollution is crucial for designing and evaluating anti-pollution policies.
 An outstanding question is whether the severe pollution is an inevitable consequence of rapid economic growth, or largely exacerbated by policy distortions and/or market inefficiencies.
@@
 In this paper, we argue that misallocation across firms amplifies industrial water pollution by distorting the firm size distribution in China.
-Using nationally representative data on firm production, pollution emissions and pollution treatment technologies, we document two facts on firm size and pollution intensity (pollutants per output) in China.\footnote{We use the \textit{National General Survey of Pollution Sources} (NGSPS) and \textit{National Economic Census} (CNEC) in China.
-Section I provides more details.} First, large firms have lower pollution intensity than small firms, with an elasticity of $-$0.37 between firm size and pollution intensity for the top five polluting industries in China.\footnote{The industries are ranked by their emissions of \textit{Chemical Oxygen Demand} (COD).
+Using nationally representative data on firm production, pollution emissions and pollution treatment technologies, we document two facts on firm size and pollution intensity (pollutants per output) in China.
+%\footnote{We use the \textit{National General Survey of Pollution Sources} (NGSPS) and \textit{National Economic Census} (CNEC) in China.
+Section I provides more details.}
+First, large firms have lower pollution intensity than small firms, with an elasticity of $-$0.37 between firm size and pollution intensity for the top five polluting industries in China.
+%\footnote{The industries are ranked by their emissions of \textit{Chemical Oxygen Demand} (COD).
 The five industries are (with two-digit GB/T4547-2002 code in parentheses): Paper and Paper Products (C22), Processing of Food from Agricultural Products (C13), Textiles (C17), Raw Chemical Materials and Chemical Products (C26), and Beverages (C15).}  Furthermore, we find that this is not only due to fewer pollutants per output are generated by large firms during production, but also that large firms are also more likely to use advanced end-of-pipe treatment technologies that require sizable fixed installation costs.
+Not only do large firms generate  fewer pollutants per output during production, but they are also more likely to use advanced end-of-pipe treatment technologies that require large installation costs.
 Second, large firms account for a smaller proportion of the total employment in China than in the United States.
@@
 As in \citet{CopelandTaylor:1994}, pollution emissions are a by-product of production for firms in the polluting sector.
-Following Fact 1 above, we assume that generated emissions per output during production is decreasing in firm output.\footnote{While our data reveal that large firms generate fewer pollutants per output, we do not know precisely the reasons behind that.
+Following Fact 1 above, we assume that generated emissions per output during production is decreasing in firm output.
+%\footnote{While our data reveal that large firms generate fewer pollutants per output, we do not know precisely the reasons behind that.
 Without further data, we model the emissions generated during production in a reduced-form way, which is then calibrated to the data.
-Section I.B discusses this point in more details.} Third, firms have the option to adopt an advanced end-of-pipe treatment technology, which we refer to as \textit{clean} technology later, after paying a fixed adoption cost.
+Section I.B discusses this point in more details.}
+Third, firms have the option to adopt an advanced end-of-pipe treatment technology, which we refer to as clean technology later, after paying a fixed adoption cost.
 Firms in the polluting sector are subject to environmental regulations such that firms that do not use the clean technology face a penalty that takes away a fraction of their profits.
@@
 We map the polluting sector to the top five polluting industries mentioned above, which account for 80\% of the total emissions in the data, and map the non-polluting sector to the rest of the manufacturing sector.
-We then use the calibrated model to evaluate the effects of two policies: removing correlated distortions from both sectors and strengthening environmental regulations.\footnote{Here we follow the so-called \textit{indirect} approach in the study of misallocation [\citet{RestucciaRogerson:2013}] by quantifying the overall effects of a variety of policies and institutions that relocate production factors from high to low TFP firms.
+We then use the calibrated model to evaluate the effects of two policies: removing correlated distortions from both sectors and strengthening environmental regulations.%\footnote{Here we follow the so-called \textit{indirect} approach in the study of misallocation [\citet{RestucciaRogerson:2013}] by quantifying the overall effects of a variety of policies and institutions that relocate production factors from high to low TFP firms.
 Several examples of such policies include size-dependent taxes and subsidies, selective enforcement of regulations, financial constraints, poor enforcement of contracts, and internal trade costs, among others.
@@
 About half of the technique effect comes from the reallocation of factors across firms, while the rest is from a 27 percentage points increase in the adoption rate of clean technology.
-To isolate the importance of the \textit{progressivity} of distortions, we solve a version of the model in which the progressive taxes are replaced with flat taxes while holding the total tax revenue constant.
-Our results show that while the progressivity of distortions does not imply large output losses (7\%), it plays a central role in amplifying aggregate pollution (30\%).
+To isolate the importance of the progressivity of distortions, we solve a version of the model in which the progressive taxes are replaced with flat taxes while holding the total tax revenue constant.
+Our results show that while the progressivity of distortions does not imply large output losses, it plays a central role in amplifying aggregate pollution: replacing the progressive taxes with flat taxes would cause a 7\% increase in aggregate output, and a 30\% decrease in aggregate pollution.
 
@@
 We find that the policy reduces aggregate pollution by 14\%, but has very limited effect on aggregate output in the long run.
-Comparing this with the first experiment, we find that tightening environmental regulations {improves} the resource allocation on the \textit{extensive} margin of resource allocation by driving small unproductive firms out of the economy.
-However, the allocation {worsens} on the \textit{intensive} margin in the sense that among the remaining active firms, the production of medium-sized firms expands more at the expense of that of large firms.
+Comparing this with the first experiment, we find that tightening environmental regulations improves the resource allocation on the extensive margin of resource allocation by driving small unproductive firms out of the economy.
+However, the allocation {worsens} on the intensive margin in the sense that among the remaining active firms, the production of medium-sized firms expands more at the expense of that of large firms.
 In contrast, the removal of correlated distortions improves the allocation on both margins.
@@
 
-\textit{NGSPS.}---The NGSPS was a joint effort of multiple national ministries in China.\footnote{A more detailed description of the dataset can be found in Online Appendix A.} It covers all of the pollution units from the agricultural, industrial, and domestic sources, as well as facilities for the centralized treatment of pollution.
+\textit{NGSPS.}---The NGSPS was a joint effort of multiple national ministries in China. %\footnote{A more detailed description of the dataset can be found in Online Appendix A.}
+It covers all of the pollution units from the agricultural, industrial, and domestic sources, as well as facilities for the centralized treatment of pollution.
 In this study, we focus on the {industrial pollution sources}, which consist of businesses generating pollutants from the 39 manufacturing industries.
@@
 Our results will be contaminated only if under-reporting by large firms is more severe than that by small firms, which is less likely in most polluting industries since larger firms are usually inspected more carefully.
-For instance, many large firms in these industries are identified as \textit{Key Pollution Sources}, and therefore are inspected and monitored by the government routinely and carefully, making it harder for them to fake data during this one-time survey.} While we are not aware of other economic studies that use NGSPS, a number of studies in environmental sciences have used this dataset.\footnote{See \citet{Niuetal:2016} and \citet{Qietal:2017} and the references therein for recent examples.}
+For instance, many large firms in these industries are identified as \textit{key sources}, and therefore are inspected and monitored by the government routinely and carefully, making it harder for them to fake data during this one-time survey.} While we are not aware of other economic studies that use NGSPS, a number of studies in environmental sciences have used this dataset.
+See, for example, \citet{Niuetal:2016}, \citet{Qietal:2017} and the references therein.
+A more detailed description of the dataset can be found in Online Appendix A.
+%\footnote{See \citet{Niuetal:2016} and \citet{Qietal:2017} and the references therein for recent examples.}
 
@@
 We would like to stress that many firms do not report emissions of specific pollutants such as cyanidium or chromium simply because they do not use related materials in production.
-It is \textit{not} because of under-reporting or other issues related to data quality.
+It is not because of under-reporting or other issues related to data quality.
 In fact, since these pollutants are more hazardous than others, firms that discharge these pollutants are usually monitored more closely.} Moreover, COD emissions are typically highly correlated with the emissions of other pollutants when both are positive.\footnote{In the Paper and Paper Products industry, for example, the correlation between the emissions of COD and $\text{NH}_4^+$ is $\text{corr}(\text{COD},\text{NH}_4^+) = \text{0.82}$ and that between COD and BOD is $\text{corr}(\text{COD},\text{BOD}) = \text{0.94}$.}
@@
 Within narrowly defined manufacturing industries, the NGSPS divides firms into two large groups---\textit{key sources} and \textit{regular sources}.
-Firms identified as ``key sources'' are deemed as more polluting, and therefore are inspected and monitored by the government more carefully.\footnote{See Online Appendix A.1 for more information on the definition of key sources.} During this census, the field staff also collected extra information on these firms, and the data from these firms were inspected with greater care.
-Importantly, the key sources include both small and large firms, and the empirical densities of the log output of the key sources resemble the bell shape of those of all firms.\footnote{Please see Figure B.1 in Online Appendix B.} As a result, when empirically analyzing the relationship of firm size with pollution intensity and treatment technology adoption, we focus on the key sources, which account for more than 90\% of total COD emissions and 80\% of total output from the top five polluting industries (Table \ref{tab:top5summary}).
+Firms identified as key sources are deemed as more polluting, and therefore are inspected and monitored by the government more carefully.
+%\footnote{See Online Appendix A.1 for more information on the key sources.}
+During this census, the field staff also collected extra information on these firms, and the data from these firms were inspected with greater care.
+Importantly, the key sources include both small and large firms, and the empirical densities of the log output of the key sources resemble the bell shape of those of all firms.\footnote{Please see Online Appendix A.1 for the formal definition of the key sources, and Figure B.1 in Online Appendix B for  the empirical densities of the log output of the key sources.} As a result, when empirically analyzing the relationship of firm size with pollution intensity and treatment technology adoption, we focus on the key sources, which account for more than 90\% of total COD emissions and 80\% of total output from the top five polluting industries (Table \ref{tab:top5summary}).
 The variables we use are the firm's output, the amount of major pollutants generated and emitted, installation costs of pollutant treatment technologies, industry (up to four-digit GB/T4574-2002), ownership classification, and province.
@@
 We use observations that belong to the manufacturing sector.
-The variables we use are the firm's output, labor compensation, book value of capital stock, number of employees, industry (up to four-digit GB/T4574-2002), ownership classification, and province.\footnote{A widely used firm-level dataset in China is the Annual Surveys of Industrial Firm (ASIF).
+The variables we use are the firm's output, labor compensation, book value of capital stock, number of employees, industry (up to four-digit GB/T4574-2002), ownership classification, and province.\footnote{A widely used firm-level dataset in China is the Annual Surveys of Industrial Firms (ASIF).
 We use CNEC instead of ASIF because that ASIF does not have information on non-state firms with sales below 5 million CNY, which are crucial for our analysis.
@@
 
-\textit{Firm Size and Pollution Intensity.---}To examine the statistical relationship between pollution intensity and firm size for the polluting sectors in China, we run the following regression using data on firms identified as ``key sources'' in the top five polluting industries:
+\textit{Firm Size and Pollution Intensity.---}To examine the statistical relationship between pollution intensity and firm size for the polluting sectors in China, we run the following regression using data on firms identified as key sources in the top five polluting industries:
 \begin{equation}
@@
 That is, other things equal, a 1\% increase in firm output is associated with a 0.37\% decrease in pollution intensity.
-Figure \ref{fig:codscatter} visualizes this negative relationship, where the residuals from regressing intensity and output on the dummies are plotted to remove the influences of other covariates.\footnote{Recall that here by the \textit{Regression Anatomy Formula}, the slope of the least square fit in Figure \ref{fig:codscatter} is precisely one minus the coefficient on $\log(\text{Output})$ in Equation (\ref{eq:poolols}).} The estimation has an $R^2$ of 0.41, suggesting that nearly half of the variations in COD emissions can be explained by the variations in firm output and in the three sets of dummies.\footnote{We also tried other econometric specifications, and found similar negative correlations between pollution intensity and firm size.
+Figure \ref{fig:codscatter} visualizes this negative relationship, where the residuals from regressing intensity and output on the dummies are plotted to remove the influences of other covariates.
+%\footnote{Recall that here by the \textit{Regression Anatomy Formula}, the slope of the least square fit in Figure \ref{fig:codscatter} is precisely one minus the coefficient on $\log(\text{Output})$ in Equation (\ref{eq:poolols}).}
+The estimation has an $R^2$ of 0.41, suggesting that nearly half of the variations in COD emissions can be explained by the variations in firm output and in the three sets of dummies.\footnote{We also tried other econometric specifications, and found similar negative correlations between pollution intensity and firm size.
 For instance, we estimated versions of Equation (\ref{eq:poolols}) for each industry and with robust standard errors clustered in provinces.
-Please see Online Appendix C for more information.} We would also like to point out that the coefficient of the dummy on whether a firm is state-owned or not, is statistically \textit{insignificant}.
+Please see Online Appendix C for more information.} We would also like to point out that the coefficient of the dummy on whether a firm is state-owned or not, is statistically insignificant.
 As a result, we do not distinguish between whether a firm is state-owned or not in our later analysis.
@@
 
-To illustrate the difference in technology adoption by firms of different sizes, we use the Paper and Paper Products industry as an example.\footnote{We focus on one industry because of the potential heterogeneity in production processes across industries.} Table \ref{tab:techeffi} shows the mean abatement efficiency, median installation costs, and median output of firms that adopt these technologies, where the {abatement efficiency} is defined as one minus the ratio of {emitted COD} to {generated COD}.\footnote{Online Appendix D.2 provides more details.}
+To illustrate the difference in technology adoption by firms of different sizes, we use the Paper and Paper Products industry as an example.
+By focusing on one specific industry, we abstract from the potential heterogeneity in production processes across industries.
+%\footnote{We focus on one industry because of the potential heterogeneity in production processes across industries.}
+Table \ref{tab:techeffi} shows the mean abatement efficiency, median installation costs, and median output of firms that adopt these technologies, where the {abatement efficiency} is defined as one minus the ratio of {emitted COD} to {generated COD}.
+%\footnote{Online Appendix D.2 provides more details.}
 \begin{table}[t]
@@
 Running regression (\ref{eq:poolols}) separately for firms using physical and chemical equipments yield similarly significantly negative correlations between COD per output and firm size for each technology.
-Online Appendix C.3 reports the results in details.}
-
-Such within group negative correlations could be because that larger firms use \textit{cleaner} or \textit{fewer} inputs to produce the same amount of output.
-For one example, the paper pulp industry uses two different types of inputs: bagasse and wood.
-While bagasse, which generates 140--180 kg COD per ton, is mostly used by firms with an annual production of less than 100 kilotons, wood, which generates 30--55 kg COD per ton, is mostly used by firms with an annual production of more than 100 kilotons.\footnote{See the \textit{Handbook of Emission Coefficients} published by the \textit{Chinese Academy of Sciences}.} As another example, \citet{Bloometal:2010} find that better managed firms use less energy to produce the same amount of output in the U.K.
+Online Appendix C.3 reports the results in detail.}
+
+Such within group negative correlations could be because that larger firms use cleaner or fewer inputs to produce the same amount of output.
+For one example, the paper pulp industry uses two different types of inputs: the bagasse and the wood.
+According to the \textit{Handbook of Emission Coefficients} by the Chinese Academy of Sciences, the bagasse, which is mostly used by firms with an annual production of less than 100 kilotons, generates 140--180 kg of COD per ton of output, and the wood, which is mostly used by firms with an annual production of more than 100 kilotons, generates 30--55 kg of COD per ton of output.
+%\footnote{See the \textit{Handbook of Emission Coefficients} published by the \textit{Chinese Academy of Sciences}.}
+As another example, \citet{Bloometal:2010} find that better managed firms use less energy to produce the same amount of output in the U.K.
 Unfortunately, we cannot test these hypotheses directly using our data.
@@
 For the top five polluting industries in China, we fix the total output and  the estimated firm size--pollution intensity relationship, and replace the firm size distributions with those in the U.S.
-Then we compute the resulting average pollution intensity for these polluting industries pooled together.\footnote{Online Appendix F provides more details.} This simple exercise is complicated by the fact that the NGSPS reports firm-level output instead of number of employees.
+Then we compute the resulting average pollution intensity for these polluting industries pooled together.
+%\footnote{Online Appendix F provides more details.}
+ This simple exercise is complicated by the fact that the NGSPS reports firm-level output instead of number of employees.
 Therefore, we construct an employment--output relationship from a linear regression using the CNEC data.\footnote{There are different methods to construct the employment--output relationship using the CNEC data, and all of them provide similar results.
@@
 \citet{HsiehKlenow:2009} establish that these two frameworks are isomorphic for the effects of misallocation on aggregate output when the number of firms is fixed.
-In Appendix G.3, we show the qualitative equivalence between the two family of models.} The model features heterogeneity in firm productivities in both sectors, heterogeneity in pollution intensity and endogenous choice of pollution treatment technologies in the polluting sector.
+In Appendix G.3, we show the qualitative equivalence between the two families of models.} The model features heterogeneity in firm productivities in both sectors, heterogeneity in pollution intensity and endogenous choice of pollution treatment technologies in the polluting sector.
 Motivated by the data, firms in both sectors are subject to correlated distortions [\citet{RestucciaRogerson:2008}] in the form of progressive output taxes.
-Throughout, we refer to the sectors as polluting and non-polluting, and technologies as dirty and clean.
+%Throughout, we refer to the sectors as polluting and non-polluting, and technologies as dirty and clean.
 In the context of our model, the polluting sector is mapped to the top five polluting industries and the non-polluting sector to the rest of the manufacturing sector, while clean and dirty technologies are interpreted as biological and other (physical plus chemical) equipments as specified in Section I.B.
@@
 
-A fraction $\mu$ of the members are endowed with managerial talent that can be used in the polluting sector, drawn from a distribution with cumulative distribution function (CDF) $G^{d}(z)$.
-Meanwhile, a fraction $1-\mu$ of the members are endowed with managerial talent for the non-polluting sector with CDF $G^{c}(z)$.
+A fraction $\mu$ of the members are endowed with managerial talent that can be used in the polluting sector, drawn from a distribution with cumulative distribution function (CDF) $G^{d}(z)$, where the superscript $d$ refers to the polluting sector.
+Meanwhile, a fraction $1-\mu$ of the members are endowed with managerial talent for the non-polluting sector with CDF $G^{c}(z)$, where the superscript $c$ refers to the non-polluting sector.
 The support for both distributions are $Z \triangleq [0,\overline{z}]$.
@@
 \end{equation*}
-where $0<\gamma<1$ is the \emph{span-of-control} parameter, which governs the returns to scale at the firm level.
+where $0<\gamma<1$ is the span-of-control parameter, which governs the returns to scale at the firm level.
 Due to diminishing returns to scale at the firm level, a non-degenerate distribution of firm size can be supported, and firms earn positive profits as the payment to managerial talent $z$.
@@
 In the polluting sector, pollutants $e$ are generated as a by-product of production.
-Total emissions $e = \mathcal{E}(i,y)$ depend on the amount of output $y$, and the pollution treatment technology firms use, with $i = 1$ refers to the {clean} technology and $i = 0$ the dirty technology.
+Total emissions $e = \mathcal{E}(j,y)$ depend on the amount of output $y$, and the pollution treatment technology firms use, with $j = 1$ refers to the clean technology and $j = 0$ the dirty technology.
 Based on the empirical findings from Section I, we assume that
@@
 \label{eq:intensity_size}
-    \log\left(\frac{e}{y}\right) = \psi_0^i + \psi_1^i \log y, \quad i = 0,1,
+    \log\left(\frac{e}{y}\right) = \psi_0^{(j)}+ \psi_1^{(j)} \log y, \quad j = 0,1,
 \end{equation}
-where $\psi_1^i<0$. This formulation indicates that larger firms emit fewer pollutants per unit of output, which is consistent with our empirical findings in Section I.B.
+where $\psi_1^{(j)}<0$. This formulation indicates that larger firms emit fewer pollutants per unit of output, which is consistent with our empirical findings in Section I.B.
 
@@
 \end{equation*}
-where the superscript $c$ stands for ``clean.''
+where the superscript $c$ refers to the non-polluting sector.
 
@@
 \end{equation*}
-where the superscript $d$ stands for ``dirty,'' and the subscript denotes the treatment technologies.
+where the superscript $d$ refers to the polluting sector, and the subscripts denotes the treatment technologies.
 Firms using the clean technology are not subject to environmental penalties, hence the profit $\pi_1^d(z)$ is:
@@
 In addition, when $1-\gamma+\phi_1 > 0$, which is satisfied given our calibrated values for $\gamma$ and $\phi_1$, $\pi_i^d(z)$ and $l^d(z)$ are both increasing $z$.
-Then there exists a threshold $\tilde{z}_d$ such that only firms with TFP higher than $\tilde{z}_d$ would choose clean technology.\footnote{Please see Lemma 2 in Online Appendix G.1 for details.} There also exist two thresholds $\hat{z}_i, i=c,d,$ such that in sector $i$, only members with $z > \hat{z}_i$ choose to be managers.
+Then, as we show in Lemma 2 of Online Appendix G.1, there exists a threshold $\tilde{z}_d$ such that only firms with TFP higher than $\tilde{z}_d$ would choose clean technology.
+%\footnote{Please see Lemma 2 in Online Appendix G.1 for details.}
+There also exist two thresholds $\hat{z}_i, i=c,d,$ such that in sector $i$, only members with $z > \hat{z}_i$ choose to be managers.
 
@@
 First, we show that correlated distortions have a negative impact on firms' incentives to adopt the clean technology.
-Second, using a simplified one-sector model with a fixed number of firms and \emph{exogenous} firm-level pollution intensity, we characterize the conditions under which correlated distortions lead to higher aggregate pollution.
-The core trade-off here is between the scale and technique effects, because the correlated distortions generally cause a decrease in average pollution intensity but an increase in aggregate output.\footnote{All the proofs and additional analytical results can be found in Appendices G.1 and G.2.}
+Second, using a simplified one-sector model with a fixed number of firms and exogenous firm-level pollution intensity, we characterize the conditions under which correlated distortions lead to higher aggregate pollution.
+The core trade-off here is between the scale and technique effects, because the correlated distortions generally cause a decrease in average pollution intensity but an increase in aggregate output.
+All the proofs and related analytical results can be found in Appendices G.1 and G.2.
+%\footnote{All the proofs and additional analytical results can be found in Appendices G.1 and G.2.}
 
@@
 As a result, while firms with TFP in the range $[\tilde{z}_n, \tilde{z}_f]$ would choose the clean technology when they are not subject to distortions and choose the dirty technology when they are.\footnote{Of course, when the correlated distortions apply to all firms in the economy, they would affect the equilibrium wage $W$ and hence $\tilde{z}_f$ in equilibrium.
-We find later in our quantitative exercises that $\tilde{z}_f > \tilde{z}_n$ even with general equilibrium effects considered.}
-
-\textit{Aggregate Pollution.---}To derive a closed-form expression for the relationship between correlated distortions and aggregate pollution, we build a simplified one-sector model that abstracts from the endogenous occupation choice and treatment technology choice.\footnote{Please see Online Appendix G.2 for a detailed description of the simplified model and additional analytical results.} This complements our analysis in Proposition \ref{prop:friction}, which focuses on how distortions affect firms' decision in that the general equilibrium effects are captured.
+We find later in our quantitative analysis that $\tilde{z}_f > \tilde{z}_n$ even when general equilibrium effects are considered.}
+
+\textit{Aggregate Pollution.---}To derive a closed-form expression for the relationship between correlated distortions and aggregate pollution, we build a simplified one-sector model that abstracts from the endogenous occupation choice and treatment technology choice.
+%\footnote{Please see Online Appendix G.2 for a detailed description of the simplified model and additional analytical results.}
+This complements our analysis in Proposition \ref{prop:friction}, which focuses on how distortions affect firms' decision in that the general equilibrium effects are captured.
 Proposition \ref{prop:agge} summarizes our main findings.
@@
 
-Proposition \ref{prop:agge} says that the relationship between $E$ and the progressivity of the distortions $|\phi_1|$ is inverted-U shaped with the turning point $|\hat{\phi}_1|$ increasing in the elasticity of emission intensity to output $|\psi_1|$.\footnote{Here because $\phi_1$ and $\psi_1$ are both negative, the progressivity and elasticity are stronger when $|\phi_1|$ and $|\psi_1|$ are larger, meaning that the raw values $\phi_1$ and $\psi_1$ are smaller.} Because correlated distortions generally decreases the total output while increasing the average pollution intensity, the intuition behind Proposition \ref{prop:agge} is a race between the scale and technique effects.
+Proposition \ref{prop:agge} says that the relationship between $E$ and the progressivity of the distortions $|\phi_1|$ is inverted-U shaped with the turning point $|\hat{\phi}_1|$ increasing in the elasticity of emission intensity to output $|\psi_1|$.\footnote{Since $\phi_1$ and $\psi_1$ are both negative, the progressivity and elasticity are stronger when $|\phi_1|$ and $|\psi_1|$ are larger, meaning that the raw values $\phi_1$ and $\psi_1$ are smaller.} Because correlated distortions generally decreases the total output while increasing the average pollution intensity, the intuition behind Proposition \ref{prop:agge} is a race between the scale and technique effects.
 In particular, the scale effect is larger when the progressivity of the distortions is stronger (a smaller negative $\phi_1$), while the technique effect is larger when the elasticity of emission intensity to output is larger (a smaller negative $\psi_1<0$).
@@
 \begin{equation*}
-    e = \mathcal{E}(i,y) = \mathrm{e}^{\psi_0^{(i)}} y^{1+\psi_1^{(i)}}, i=0,1,
-\end{equation*}
-where $\{\psi_0^{(i)}, \psi_1^{(i)}\}$ are based on the reduced-form estimates from Equations (\ref{eq:poolols_biological}) and (\ref{eq:poolols_others}).
+    e = \mathcal{E}(j,y) = \mathrm{e}^{\psi_0^{(j)}} y^{1+\psi_1^{(j)}}, j=0,1,
+\end{equation*}
+where $\{\psi_0^{(j)}, \psi_1^{(j)}\}$ are based on the reduced-form estimates from Equations (\ref{eq:poolols_biological}) and (\ref{eq:poolols_others}).
 
@@
 In the context of our model, these estimates suggest that, on average, for two firms with the same level of output but different treatment technologies, the firm using the clean technology emits 40\% to 60\% less pollutants than the one with the dirty technology.
-We set $\mu =$ 0.20, which is the share of manufacturing firms accounted for by the five polluting industries in the CNEC data.\footnote{The share of manufacturing output accounted for by these five industries is 18\%, which is very close as well.}
+We set $\mu =$ 0.20, which is the share of manufacturing firms accounted for by the five polluting industries in the CNEC data.
+The share of manufacturing output accounted for by these five industries is also quite close, which is 18\%.%\footnote{The share of manufacturing output accounted for by these five industries is 18\%, which is very close as well.}
 
@@
 We set $\xi$ and $k_E$ such that the model reflects the average cost to install clean technology in the data.
-For the five polluting industries, we find in the NGSPS that 57\% of the firms use biological technology, and the average adoption cost of biological equipments is approximately 2.5\% of the average firm output \textit{for these firms}.
+For the five polluting industries, we find in the NGSPS that 57\% of the firms use biological technology, and the average adoption cost of biological equipments is approximately 2.5\% of the average firm output for these firms.
 These two targets help us pin down the values of $\xi$ and $k_E$.
@@
 We conduct two sets of counterfactual experiments.
-In Experiment (i), we follow the \emph{indirect} approach in the misallocation literature and remove correlated distortions from both sectors by changing $\tau_z$ to $0$.\footnote{In Online Appendix I, we build and calibrate a similar model in which the final consumption is a CES aggregation of the products from two sectors, and use the model to evaluate the impact of removing the correlated distortions from \emph{the polluting sector only}.
+In Experiment (i), we follow the \emph{indirect} approach in the misallocation literature and remove correlated distortions from both sectors by changing $\tau_z$ to $0$.\footnote{In Online Appendix I, we build and calibrate a similar model in which the final consumption is a CES aggregation of the products from two sectors, and use the model to evaluate the impact of removing the correlated distortions from the polluting sector only.
 The main difference between this experiment and Experiment (i) in the main text is that this one induces large reallocation of factors from the non-polluting to the polluting sector.
@@
 Since both sectors share the same distributions of firm-level productivity and distortions, removing correlated distortions induces little reallocation across sectors (composition effect).
-Therefore, the technique effect from eliminating correlated distortions dominates the scale and composition effects, and aggregate pollution drops by 23\%.\footnote{The decrease in aggregate pollution is consistent with the prediction from Proposition \ref{prop:agge}, given the calibrated values for $\phi_1$, $\gamma$ and the estimated relationship between pollution intensity and firm size.}
+Therefore, the technique effect from eliminating correlated distortions dominates the scale and composition effects, and aggregate pollution drops by 23\%.
+The decrease in aggregate pollution is consistent with Proposition \ref{prop:agge}, given the calibrated values for $(\phi_1, \gamma)$, and the estimated relationship between pollution intensity and firm size.
+%\footnote{The decrease in aggregate pollution is consistent with the prediction from Proposition \ref{prop:agge}, given the calibrated values for $\phi_1$, $\gamma$ and the estimated relationship between pollution intensity and firm size.}
 
@@
 
-In Experiment (i), by setting $\tau_z = 0$, we change both the progressivity and and the average level of firm-level distortions.
+In Experiment (i), by setting $\tau_z = 0$, we change both the progressivity and and the average level of distortions.
 To isolate the importance of the progressivity of $\tau_z$, we solve a version of the model where the progressive taxes are replaced with uniform taxes by setting $\phi_1 =$ 0, and change $\phi_0$ to keep the total implicit tax revenue constant.\footnote{This strategy has a long tradition in the public finance and development economics literature.
@@
 
-In sum, our findings imply that it is the progressivity of distortions, rather than the average level of firm-level distortions, that plays a dominate role in amplifying aggregate pollution and pollution intensity.
+In sum, our findings imply that it is the progressivity of firm-level distortions, rather than the average level of distortions, that plays a dominate role in amplifying aggregate pollution and pollution intensity.
 
@@
 This paper proposes a novel explanation for the industrial water pollution problem in China.
-In our theory, large productive firms are more likely to use clean technology and have lower pollution intensity, largely due to the fixed adoption cost of clean technology and imperfect environmental regulations.
+In our theory, large productive firms are more likely to use the clean technology and have lower pollution intensity, largely due to the fixed adoption cost of clean technology and imperfect environmental regulations.
 Distortions that increase with firm TFP reallocate production factors away from large productive firms, therefore reduce aggregate output while increasing aggregate pollution intensity.

### 2019-09-23 Documentation/Response_to_AEJ_Editor.tex
final submission

\documentclass[twoside,12pt,leqno]{article}
%\documentclass[twoside,12pt,leqno]{report}

\usepackage{amsmath,amssymb,amsfonts,amsthm,mathrsfs,multirow,upgreek}
\usepackage[capposition=bottom]{floatrow} % For Figure Notes
\usepackage{graphicx,pstricks,epstopdf}
\usepackage{url}      % This package helps to typeset urls

%\usepackage{apacite}
%\usepackage{natbib}   % This is a great aid with bibliographies
%\setcitestyle{authoryear,round,semicolon,aysep={},yysep={,},notesep={:}}

\usepackage[title]{appendix}
\renewcommand{\appendixname}{Appendix}

\usepackage[authoryear,comma]{natbib}
\renewcommand{\bibfont}{\small}
\setlength{\bibsep}{0em}

%\usepackage[sc,tiny,center]{titlesec}
\usepackage{titlesec}
\titleformat*{\section}{\sc \center}
\titleformat*{\subsection}{\it \center}
\renewcommand\thesection{\textnormal{{\Roman{section}}}}
\renewcommand{\refname}{Reference}
\usepackage[font={sc,small}]{caption}

\usepackage[%dvipdfmx,%
            bookmarks=true,%
            pdfstartview=FitH,%
            breaklinks=true,%
            colorlinks=true,%
            %allcolors=black,%
            citecolor=blue,
            linkcolor=red,
            pagebackref=true]{hyperref}

\renewcommand{\rmdefault}{ptm}
%\usepackage[lite]{mtpro2}
% use Palatinho-Roman as default font family
%\renewcommand{\rmdefault}{ppl}
\usepackage[scaled=0.88]{helvet}
\makeatletter   % Roman Numbers
\newcommand*{\rom}[1]{\expandafter\@slowromancap\romannumeral #1@}
\makeatother

\newcommand{\E}{\mathbb{E}}
\newcommand{\e}{\mathrm{e}}
\DeclareMathOperator*{\argmax}{argmax}
\renewcommand{\vec}[1]{\ensuremath{\mathbf{#1}}}
\newcommand{\gvec}[1]{{\boldsymbol{#1}}}

\usepackage[hmargin={1.2in,1.2in},vmargin={1.5in,1.5in}]{geometry}
\usepackage{threeparttable,booktabs,multirow} % This allows notes in tables

\usepackage{graphicx}
\usepackage{enumerate}
\usepackage{CJK}
\usepackage[title]{appendix}
\renewcommand{\appendixname}{Appendix}
\newtheorem{result}{Result}
\setlength{\unitlength}{1mm}

\topmargin -1cm        % read Lamport p.163
\oddsidemargin -0.04cm   % read Lamport p.163
\evensidemargin -0.04cm  % same as oddsidemargin but for left-hand pages
\textwidth 16.59cm
\textheight 21.94cm
\renewcommand\baselinestretch{1.15}
\parskip 0.25em
\parindent 1em
\linespread{1}

% Set header and footer
%\usepackage{fancyhdr}
%\pagestyle{fancy}
%\fancyhead{}
%\fancyhead[LE,RO]{\thepage}
%\cfoot{}
%\renewcommand{\headrulewidth}{0pt}

%\pdfoptionpdfminorversion 6

\begin{document}

\title{\large{THE LETTER TO THE EDITOR}}
\date{}
\maketitle

\vspace{-1.75cm}

\begin{flushleft}
Dear Dr. Moll,
\end{flushleft}

This letter summarizes our responses to the comments that we received from you and the referees after our resubmission to the \textit{American Economic Journal: Macroeconomics}. We truly appreciate it that you have conditionally accepted our paper. Overall, it has been a wonderful experience working with the \textit{AEJ: Macro}. It was very enjoyable revising our paper following the guidance we received from you and the referees.

We have taken the expositional comments from both referees. We have also followed your advice on leaving the CES case in Appendix J. Our responses in detail are as follows.

\begin{flushleft}
\textbf{Response to Referee 1's Comments:}
\end{flushleft}

\begin{enumerate}
    \item
    We thank Referee 1 for mentioning the paper by \citet{Heetal:2019} to us. It is clear that the paper used a different dataset, which has a panel structure. However, since the authors did not provide enough details on the original source of the environmental dataset they used---possibly due to the lack of an official English translation for the name of the dataset---we had a really hard time identifying the exact dataset. Our educated guess is that they were using the firm-level data from \textit{Annual Statistic Report on Environment in China} (in Chinese \begin{CJK}{GBK}{kai}中国环境统计年报\end{CJK}), but we cannot be 100\% sure.

    We talked with our colleagues who have direct access to the above dataset, and learned that there are at least two important differences between that dataset and the one we used. First, the firm-level emission data in the Annual Statistic Report were mostly self-reported by the firms, while the emission data in our dataset were collected by well-trained field staff who could also borrow manpower from local government agencies. As a result, the data quality of the Annual Statistic Report is likely to be lower. \citet{Heetal:2019} seemed to be concerned with the quality of their dataset as well, for which they wrote in their paper that ``Unlike the ASIF, however, we are less confident about the quality of ESR data.'' Second, while the treatment equipment data in our dataset plays a key role in our analysis, the Annual Statistic Report does not provide any information on the treatment equipment used by firms.

    \item
    We have taken Referee 1's advice, removed some footnotes and put some into the main text. We have also removed italics from more than a dozen of words.

    Specifically, the following footnotes from our previous draft are removed: 2, 3, 4, 7, 19, 23, 28, and 41. The following footnotes are integrated into the main text: 10, 12, 22, 25, 36, 39, 44, and 49. We have also merged Footnotes 16 and 17. As a result, the total number of footnotes has been reduced from 52 to 35.

    \item
    In our accounting exercise in Section I.C., we do take the U.S. as a benchmark, since we have data on the U.S. firm size distribution. In our quantitative analysis, however, we are not able to do that, simply because we do not have access to the U.S. firm-level data. Instead, we remove all the correlated distortions from our benchmark model. We did include some discussion on the economic interpretation of the measured wedges that we call distortions in Part \textit{Correlated Distortions} of Section II.A, with Appendix D.1 providing further details. We choose to call these measured wedges as distortions because we prefer to stay close to the literature. In that section, we have cited two survey articles by \citet{RestucciaRogerson:2013, RestucciaRogerson:2017} that elaborate this interpretation issue that the referee concerns. That said, we believe that it is of interest to carry out an additional exercise where the U.S. is the benchmark, if the U.S. firm-level data are available, and we leave this interesting exercise to future work.
\end{enumerate}

\begin{flushleft}
\textbf{Response to Referee 3's Comments:}
\end{flushleft}

\begin{enumerate}[1.]
    \item
    \textit{Introduction}
    \begin{enumerate}[(1)]
        \item
        The sentence has been changed to the following: ``Not only do large firms generate fewer pollutants per output during production, but they are also more likely to use advanced end-of-pipe treatment technologies that require large installation costs.'' Please see the middle of the first paragraph on Page 2 of our new draft.
        \item
        The sentence has been changed as follows: ``Our results show that while the progressiveness of distortions does not imply large output losses, it plays a central role in amplifying aggregate pollution: replacing the progressive taxes with flat taxes would cause a 7\% increase in aggregate output, and a 30\% decrease in aggregate pollution.'' Please see the end of the last paragraph on Page 3 of our new draft.
        \item
        We have removed some footnotes and integrated some into the main text. Specifically, the following footnotes from our previous draft are removed: 2, 3, 4, 7, 19, 23, 28, and 41. The following footnotes are integrated into the main text: 10, 12, 22, 25, 36, 39, 44, and 49. We have also merged Footnotes 16 and 17. As a result, the total number of footnotes has been reduced from 52 to 35.
    \end{enumerate}

    \item
    \textit{Model}
    \begin{enumerate}[(1)]
        \item
        We have explained what the superscripts $c$ and $d$ refer to when they first appear in the model section; please see the beginning of the second paragraph of part \textit{Household} in Section II.A (page 13) of our new draft. Specifically, the superscript $c$ refers to the non-polluting sector, and $d$ refers to the polluting sector.
        \item
        In our initial submission, our model had one sector and two types of treatment technologies, so we used the index $i=0,1$ to denote the type of treatment technology ($i=1$ for clean technology). In our version, there were two sectors in the model, so we used $i=0,1$ to denote the treatment technologies and $i=c,d$ to denote the sectors. It seems that the use of $i$ in both places has caused some confusion, hence we use the index $j=0,1$ in our new draft. We apologize for the confusion. The $j$ superscript is needed though, as there are a few technology-specific variables that we refer to.
    \end{enumerate}

    \item
    \textit{Quantitative Exercises}

    We sincerely appreciate it that Referee 3 finds the results in Appendix J interesting. Indeed, this exercise is inspired by the referee's comments. We considered this suggestion very carefully; however, we decided to leave these results in Appendix J as they are for the following reasons. First, the firm-level data suggest that there are severe correlated distortions in both the polluting and non-polluting sectors. Therefore, we think it is more natural to consider removing distortions from both sectors. Second, when we remove the correlated distortions from the polluting sector only, the results depend critically on the elasticity of substitution between the two sectors $\rho$. Unfortunately, we have not been able to come up with a good estimate of $\rho$ yet. On the other hand, if we remove distortions from both sectors, the value of $\rho$ has very limited impact on the results.
\end{enumerate}

\bibliographystyle{aea}
\bibliography{./Dissertation1}

\end{document}

### 2019-09-23 Documentation/Response_to_Ref1.tex
final submission

--- 2019-09-23 Documentation/Response_to_AEJ_Editor.tex
@@
 
-\usepackage{amsmath,amssymb,amsfonts,amsthm,mathrsfs,multirow,upgreek}
+\usepackage{amsmath,amssymb,amsfonts,amsthm,mathrsfs,multirow}
 \usepackage[capposition=bottom]{floatrow} % For Figure Notes
@@
 \renewcommand{\vec}[1]{\ensuremath{\mathbf{#1}}}
-\newcommand{\gvec}[1]{{\boldsymbol{#1}}}
 
@@
 \usepackage{CJK}
+
 \usepackage[title]{appendix}
@@
 
-\title{\large{THE LETTER TO THE EDITOR}}
+\title{\large{RESPONSES TO REFEREE 1'S COMMENTS}}
 \date{}
@@
 \begin{flushleft}
-Dear Dr. Moll,
+To Referee \#1,
 \end{flushleft}
 
-This letter summarizes our responses to the comments that we received from you and the referees after our resubmission to the \textit{American Economic Journal: Macroeconomics}.
-We truly appreciate it that you have conditionally accepted our paper.
-Overall, it has been a wonderful experience working with the \textit{AEJ: Macro}.
-It was very enjoyable revising our paper following the guidance we received from you and the referees.
-
-We have taken the expositional comments from both referees. We have also followed your advice on leaving the CES case in Appendix J. Our responses in detail are as follows.
-
-\begin{flushleft}
-\textbf{Response to Referee 1's Comments:}
-\end{flushleft}
+This letter summarizes our response to Referee 1’s report, which begins with ``The paper says no existing economic research...'' We thank Referee 1 again for the comments we received.
+Below, we respond to Referee 1's comments point by point.
 
@@
 
-\begin{flushleft}
-\textbf{Response to Referee 3's Comments:}
-\end{flushleft}
-
-\begin{enumerate}[1.]
-    \item
-    \textit{Introduction}
-    \begin{enumerate}[(1)]
-        \item
-        The sentence has been changed to the following: ``Not only do large firms generate fewer pollutants per output during production, but they are also more likely to use advanced end-of-pipe treatment technologies that require large installation costs.'' Please see the middle of the first paragraph on Page 2 of our new draft.
-        \item
-        The sentence has been changed as follows: ``Our results show that while the progressiveness of distortions does not imply large output losses, it plays a central role in amplifying aggregate pollution: replacing the progressive taxes with flat taxes would cause a 7\% increase in aggregate output, and a 30\% decrease in aggregate pollution.'' Please see the end of the last paragraph on Page 3 of our new draft.
-        \item
-        We have removed some footnotes and integrated some into the main text.
-Specifically, the following footnotes from our previous draft are removed: 2, 3, 4, 7, 19, 23, 28, and 41.
-The following footnotes are integrated into the main text: 10, 12, 22, 25, 36, 39, 44, and 49.
-We have also merged Footnotes 16 and 17.
-As a result, the total number of footnotes has been reduced from 52 to 35.
-    \end{enumerate}
-
-    \item
-    \textit{Model}
-    \begin{enumerate}[(1)]
-        \item
-        We have explained what the superscripts $c$ and $d$ refer to when they first appear in the model section; please see the beginning of the second paragraph of part \textit{Household} in Section II.A (page 13) of our new draft.
-Specifically, the superscript $c$ refers to the non-polluting sector, and $d$ refers to the polluting sector.
-        \item
-        In our initial submission, our model had one sector and two types of treatment technologies, so we used the index $i=0,1$ to denote the type of treatment technology ($i=1$ for clean technology).
-In our version, there were two sectors in the model, so we used $i=0,1$ to denote the treatment technologies and $i=c,d$ to denote the sectors.
-It seems that the use of $i$ in both places has caused some confusion, hence we use the index $j=0,1$ in our new draft.
-We apologize for the confusion.
-The $j$ superscript is needed though, as there are a few technology-specific variables that we refer to.
-    \end{enumerate}
-
-    \item
-    \textit{Quantitative Exercises}
-
-    We sincerely appreciate it that Referee 3 finds the results in Appendix J interesting.
-Indeed, this exercise is inspired by the referee's comments.
-We considered this suggestion very carefully; however, we decided to leave these results in Appendix J as they are for the following reasons.
-First, the firm-level data suggest that there are severe correlated distortions in both the polluting and non-polluting sectors.
-Therefore, we think it is more natural to consider removing distortions from both sectors.
-Second, when we remove the correlated distortions from the polluting sector only, the results depend critically on the elasticity of substitution between the two sectors $\rho$.
-Unfortunately, we have not been able to come up with a good estimate of $\rho$ yet.
-On the other hand, if we remove distortions from both sectors, the value of $\rho$ has very limited impact on the results.
-\end{enumerate}
-
 \bibliographystyle{aea}

### 2019-09-23 Documentation/Response_to_Ref3.tex
final submission

--- 2019-09-23 Documentation/Response_to_AEJ_Editor.tex
@@
 
-\title{\large{THE LETTER TO THE EDITOR}}
+\title{\large{RESPONSES TO REFEREE 3'S COMMENTS}}
 \date{}
@@
 \begin{flushleft}
-Dear Dr. Moll,
+To Referee \#3,
 \end{flushleft}
 
-This letter summarizes our responses to the comments that we received from you and the referees after our resubmission to the \textit{American Economic Journal: Macroeconomics}.
-We truly appreciate it that you have conditionally accepted our paper.
-Overall, it has been a wonderful experience working with the \textit{AEJ: Macro}.
-It was very enjoyable revising our paper following the guidance we received from you and the referees.
-
-We have taken the expositional comments from both referees. We have also followed your advice on leaving the CES case in Appendix J. Our responses in detail are as follows.
-
-\begin{flushleft}
-\textbf{Response to Referee 1's Comments:}
-\end{flushleft}
-
-\begin{enumerate}
-    \item
-    We thank Referee 1 for mentioning the paper by \citet{Heetal:2019} to us.
-It is clear that the paper used a different dataset, which has a panel structure.
-However, since the authors did not provide enough details on the original source of the environmental dataset they used---possibly due to the lack of an official English translation for the name of the dataset---we had a really hard time identifying the exact dataset.
-Our educated guess is that they were using the firm-level data from \textit{Annual Statistic Report on Environment in China} (in Chinese \begin{CJK}{GBK}{kai}中国环境统计年报\end{CJK}), but we cannot be 100\% sure.
-
-    We talked with our colleagues who have direct access to the above dataset, and learned that there are at least two important differences between that dataset and the one we used.
-First, the firm-level emission data in the Annual Statistic Report were mostly self-reported by the firms, while the emission data in our dataset were collected by well-trained field staff who could also borrow manpower from local government agencies.
-As a result, the data quality of the Annual Statistic Report is likely to be lower.
-\citet{Heetal:2019} seemed to be concerned with the quality of their dataset as well, for which they wrote in their paper that ``Unlike the ASIF, however, we are less confident about the quality of ESR data.'' Second, while the treatment equipment data in our dataset plays a key role in our analysis, the Annual Statistic Report does not provide any information on the treatment equipment used by firms.
-
-    \item
-    We have taken Referee 1's advice, removed some footnotes and put some into the main text. We have also removed italics from more than a dozen of words.
-
-    Specifically, the following footnotes from our previous draft are removed: 2, 3, 4, 7, 19, 23, 28, and 41.
-The following footnotes are integrated into the main text: 10, 12, 22, 25, 36, 39, 44, and 49.
-We have also merged Footnotes 16 and 17.
-As a result, the total number of footnotes has been reduced from 52 to 35.
-
-    \item
-    In our accounting exercise in Section I.C., we do take the U.S.
-as a benchmark, since we have data on the U.S.
-firm size distribution.
-In our quantitative analysis, however, we are not able to do that, simply because we do not have access to the U.S.
-firm-level data.
-Instead, we remove all the correlated distortions from our benchmark model.
-We did include some discussion on the economic interpretation of the measured wedges that we call distortions in Part \textit{Correlated Distortions} of Section II.A, with Appendix D.1 providing further details.
-We choose to call these measured wedges as distortions because we prefer to stay close to the literature.
-In that section, we have cited two survey articles by \citet{RestucciaRogerson:2013, RestucciaRogerson:2017} that elaborate this interpretation issue that the referee concerns.
-That said, we believe that it is of interest to carry out an additional exercise where the U.S.
-is the benchmark, if the U.S.
-firm-level data are available, and we leave this interesting exercise to future work.
-\end{enumerate}
-
-\begin{flushleft}
-\textbf{Response to Referee 3's Comments:}
-\end{flushleft}
+This letter summarizes our response to Referee 3¡¯s report, which begins with ``The revised version of the paper is improved...'' We thank Referee 3 sincerely again for the constructive comments.
+Below, we respond to Referee 3's comments point by point.
 
@@
 
-\bibliographystyle{aea}
-\bibliography{./Dissertation1}
-
 \end{document}

### 2019-09-23 Documentation/Pollution_Final_AEJ_Template_Ver2.tex
final submission

@@
 % Uncomment the next line to use the natbib package with bibtex
-\usepackage{natbib}
+%\usepackage{natbib}
 
@@
 
-\newcommand{\E}{\mathbb{E}}
-\newcommand{\e}{\mathrm{e}}
-\DeclareMathOperator*{\argmax}{argmax}
-\DeclareMathOperator*{\argmin}{argmin}
-\DeclareMathOperator*{\plim}{plim}
 \renewcommand{\vec}[1]{\ensuremath{\mathbf{#1}}}
@@
 \author{Ji Qi, Xin Tang, and Xican Xi\thanks{%
-Qi: Chinese Academy for Environmental Planning, Room 709-B BeiKeChuangYe Tower, No.10 Dayangfang, Beiyuan Road, Beijing, China, 100012 (e-mail: qiji@caep.org.cn); Tang: Wuhan University and the International Monetary Fund, 700 19th St NW, Washington D.C., United States, 20431 (e-mail:zjutangxin@gmail.com); Xi: China Center for Economic Studies, School of Economics, Fudan University, 600 Guoquan Road, Shanghai, China, 200433, and  Shanghai Institute of International Finance and Economics (e-mail:xicanxi@fudan.edu.cn).
-We are grateful for the comments from Alexis Anagnostoupolos, Marina Azzimonti, Juan Carlos Conesa, Berthold Herrendorf, Nicolai Kuminoff, Pietro Peretto, Edward C.
-Prescott, Diego Restuccia, Todd Schoellman, V.
-Kerry Smith, Daniel Yi Xu, Gustavo Ventura, the editor and three anonymous referees.
-We also benefited from the comments received at Arizona State University, the Chinese Academy for Environmental Planning, Duke University, the International Monetary Fund, the U.S.
-International Trade Commission, Peking University, Shanghai University of Finance and Economics, Singapore Management University, Stony Brook University, Washington State University, Wuhan University, and Zhejiang University.
-We sincerely thank the China Ministry of Ecology and Environment for granting us access to the National General Survey of Pollution Sources data.
-This paper has been screened to ensure that no confidential data are revealed.}}
+Qi: Chinese Academy for Environmental Planning, Room 709-B BeiKeChuangYe Tower, No.10 Dayangfang, Beiyuan Road, Beijing, China, 100012 (qiji@caep.org.cn); Tang: Center for Economic Development and Research, Economics and Management School, Wuhan University, and International Monetary Fund, 700 19th St NW, Washington D.C., United States, 20431 (zjutangxin@gmail.com); Xi: China Center for Economic Studies, School of Economics, Fudan University, and Shanghai Institute of International Finance and Economics, 600 Guoquan Road, Shanghai, China, 200433 (xicanxi@fudan.edu.cn).
+We are grateful for the comments from Alexis Anagnostoupolos, Marina Azzimonti, Dong Cao, Juan Carlos Conesa, Berthold Herrendorf, Nicolai Kuminoff, Pietro Peretto, Edward Prescott, Diego Restuccia, Todd Schoellman, V.
+Kerry Smith, Gustavo Ventura, Jinnan Wang, Daniel Yi Xu, Fang Yu, the editor and three anonymous referees.
+We also benefited from the comments received from seminars at many institutions.
+We thank the Ministry of Ecology and Environment for granting us access to the National General Survey of Pollution Sources data.
+This paper has been screened to ensure that no confidential data are revealed.
+The results and conclusions in this paper are those of the authors, and do not necessarily reflect the views of the MEE or IMF, its Executive Board, or IMF management.
+For financial support, Qi acknowledges the National Key R\&D Program of China (2016YFC0207604); and Tang thanks the Key Grant of Ministry of Education of China (16JJD790045).}}
 \date{\today}
@@
 
-Severe pollution has accompanied China's remarkable economic growth in the past few decades, causing environmental degradation, public health damage, and millions of premature deaths.\footnote{\citet{WorldBank_Cost_2007} estimates that the total costs of air and water pollution in China are about 6\% of China's GDP.
+Severe pollution has accompanied China's remarkable economic growth in the past few decades, causing environmental degradation, public health damage and millions of premature deaths.\footnote{\citet{WorldBank_Cost_2007} estimates that the total costs of air and water pollution in China are about 6\% of China's GDP.
 The health costs of pollution are estimated to be 4\% of GDP in China, the majority of which are associated with premature deaths caused by pollution.
 See \citet{Vennemoetal:2009} and \citet{ZhengKahn:2013} for reviews of empirical studies on pollution in China.} Understanding the driving forces behind this severe pollution is crucial for designing and evaluating anti-pollution policies.
-An outstanding question is whether the severe pollution is an inevitable consequence of rapid economic growth, or largely exacerbated by policy distortions and/or market inefficiencies.
+An outstanding question is whether the severe pollution is an inevitable consequence of rapid economic growth, or is it largely exacerbated by policy distortions and/or market inefficiencies.
 
@@
 Using nationally representative data on firm production, pollution emissions and pollution treatment technologies, we document two facts on firm size and pollution intensity (pollutants per output) in China.
-%\footnote{We use the \textit{National General Survey of Pollution Sources} (NGSPS) and \textit{National Economic Census} (CNEC) in China.
-Section I provides more details.}
-First, large firms have lower pollution intensity than small firms, with an elasticity of $-$0.37 between firm size and pollution intensity for the top five polluting industries in China.
-%\footnote{The industries are ranked by their emissions of \textit{Chemical Oxygen Demand} (COD).
-The five industries are (with two-digit GB/T4547-2002 code in parentheses): Paper and Paper Products (C22), Processing of Food from Agricultural Products (C13), Textiles (C17), Raw Chemical Materials and Chemical Products (C26), and Beverages (C15).}  Furthermore, we find that this is not only due to fewer pollutants per output are generated by large firms during production, but also that large firms are also more likely to use advanced end-of-pipe treatment technologies that require sizable fixed installation costs.
+First, large firms have lower pollution intensity than small firms, with an elasticity of $-$0.37 between firm size and pollution intensity for the top five polluting industries (by chemical oxygen demand emissions) in China.
 Not only do large firms generate  fewer pollutants per output during production, but they are also more likely to use advanced end-of-pipe treatment technologies that require large installation costs.
@@
 Following Fact 1 above, we assume that generated emissions per output during production is decreasing in firm output.
-%\footnote{While our data reveal that large firms generate fewer pollutants per output, we do not know precisely the reasons behind that.
-Without further data, we model the emissions generated during production in a reduced-form way, which is then calibrated to the data.
-Section I.B discusses this point in more details.}
 Third, firms have the option to adopt an advanced end-of-pipe treatment technology, which we refer to as clean technology later, after paying a fixed adoption cost.
-Firms in the polluting sector are subject to environmental regulations such that firms that do not use the clean technology face a penalty that takes away a fraction of their profits.
+Firms in the polluting sector are subject to environmental regulations such that firms that do not use clean technology face a penalty that takes away a fraction of their profits.
 As a result, our model predicts that only firms above a certain size threshold would choose the clean technology, which is qualitatively consistent with the fact that large firms are more likely to use clean technology.
@@
 Both correlated and size-dependent distortions lead to a reallocation of resources from high TFP to low TFP firms, and they are essentially equivalent when distortions do not lead to rank reversal defined as more productive firms being smaller [\citet{Hopenhayn:2014}].} We find in our data that firms with higher TFP exhibit substantially higher average products of capital and labor in both the polluting and non-polluting sectors, indicating that more productive firms do face higher distortions [\citet{HsiehKlenow:2009, HsiehKlenow:2014}].
-As emphasized by previous studies, such as \citet{RestucciaRogerson:2008} and \citet{HsiehKlenow:2014}, correlated distortions lower both mean firm size and aggregate output, since they limit the operations of productive firms and allow too many unproductive firms to survive and expand.
+As emphasized by previous studies, such as \citet{RestucciaRogerson:2008} and \citet{HsiehKlenow:2014}, correlated distortions lower both mean firm size and aggregate output, since they limit the operation of productive firms and allow too many unproductive firms to survive and expand.
 A new insight from our model is that correlated distortions also increase aggregate pollution intensity for two reasons.
-First, they lower the profits of productive firms which reduces their incentives to adopt the clean technology.
+First, they lower the profits of productive firms which reduce their incentives to adopt the clean technology.
 Therefore fewer firms adopt clean technology in the equilibrium with correlated distortions.
@@
 Conventionally, environmental economics decomposes changes in aggregate pollution into three effects: scale (change in aggregate output), composition (reallocation across sectors), and technique (change in sectoral pollution intensity) effects.\footnote{See for example, \citet{GrossmanKrueger:1993}, \citet{CopelandTaylor:2004} and \citet{Levinson:2009} among others.} Our model allows us to assess structurally how distortions affect aggregate pollution through the three channels.
-Moreover, our model and data allow us to further decompose the technique effect into within sector reallocation across firms and the change in the adoption of clean technology.
-
-To discipline our quantitative analysis, we calibrate our model to match the observed pollution intensity, the adoption of clean technology, the correlation between distortions and firm TFP, and the firm size distribution in the Chinese data.
+Moreover, our model and data allow us to further decompose the technique effect into within sector reallocation across firms and the change caused by the adoption of clean technology.
+
+To discipline our quantitative analysis, we calibrate our model to match the observed pollution intensity, the adoption of clean technology, the correlation between distortions and firm TFP and the firm size distribution in the Chinese data.
 We map the polluting sector to the top five polluting industries mentioned above, which account for 80\% of the total emissions in the data, and map the non-polluting sector to the rest of the manufacturing sector.
-We then use the calibrated model to evaluate the effects of two policies: removing correlated distortions from both sectors and strengthening environmental regulations.%\footnote{Here we follow the so-called \textit{indirect} approach in the study of misallocation [\citet{RestucciaRogerson:2013}] by quantifying the overall effects of a variety of policies and institutions that relocate production factors from high to low TFP firms.
-Several examples of such policies include size-dependent taxes and subsidies, selective enforcement of regulations, financial constraints, poor enforcement of contracts, and internal trade costs, among others.
-This approach has been widely used in the misallocation literature, for instance, by \citet{HsiehKlenow:2009, HsiehKlenow:2014}, \citet{Bartelsmanetal:2013}, \citet{AdamopoulosRestuccia:2014}, and \citet{BentoRestuccia:2016}, among others.}
+We then use the calibrated model to evaluate the effects of two policies: removing correlated distortions from both sectors and strengthening environmental regulations.
 
@@
 About half of the technique effect comes from the reallocation of factors across firms, while the rest is from a 27 percentage points increase in the adoption rate of clean technology.
-To isolate the importance of the progressivity of distortions, we solve a version of the model in which the progressive taxes are replaced with flat taxes while holding the total tax revenue constant.
-Our results show that while the progressivity of distortions does not imply large output losses, it plays a central role in amplifying aggregate pollution: replacing the progressive taxes with flat taxes would cause a 7\% increase in aggregate output, and a 30\% decrease in aggregate pollution.
+To isolate the importance of the progressiveness of distortions, we solve a version of the model in which the progressive taxes are replaced with flat taxes while holding the total tax revenue constant.
+Our results show that while the progressiveness of distortions does not imply large output losses, it plays a central role in amplifying aggregate pollution: replacing the progressive taxes with flat taxes would cause a 7\% increase in aggregate output, and a 30\% decrease in aggregate pollution.
 
@@
 Another line of research focuses on how international trade affects the environment through resource reallocation across heterogeneous firms.
-\citet{Cherniwchanetal:2017} provide a comprehensive survey of recent contributions.\footnote{Notable examples include \citet{Martin:2013}, \citet{Cherniwchan:2017}, \citet{BarrowsOllivier:2016}, \citet{Forslidetal:2015}, and \citet{ShapiroWalker:2015}.
+\citet{Cherniwchanetal:2017} provide a comprehensive survey of recent contributions.\footnote{Notable examples include \citet{Martin:2013}, \citet{Cherniwchan:2017}, \citet{BarrowsOllivier:2016}, \citet{Forslidetal:2015} and \citet{ShapiroWalker:2015}.
 A more detailed comparison between our paper and this line of research can be found in Online Appendix H.} Our paper differs from this literature in two aspects.
@@
 In this section, we describe our empirical findings on the firm-level pollution intensity and the firm size distribution in China.
-We start by introducing the data sources we use, and then document the key facts on pollution intensity, pollution treatment technologies and employment shares across firms of different sizes.
+We start by introducing the data sources we use, and then document key facts on pollution intensity, pollution treatment technologies and employment shares across firms of different sizes.
 In the end, using a simple accounting exercise, we show that firm size distribution plays a quantitatively important role in aggregate pollution intensity.
@@
 
-This study draws upon three major data sources: the 2007 National General Survey of Pollution Sources (NGSPS) in China, the 2004 China National Economic Census (CNEC), and the Statistics of U.S.
+This study draws upon three major data sources: the 2007 National General Survey of Pollution Sources (NGSPS) of China, the 2004 China National Economic Census (CNEC), and the Statistics of U.S.
 Businesses (SUSB).
 
-\textit{NGSPS.}---The NGSPS was a joint effort of multiple national ministries in China. %\footnote{A more detailed description of the dataset can be found in Online Appendix A.}
-It covers all of the pollution units from the agricultural, industrial, and domestic sources, as well as facilities for the centralized treatment of pollution.
+\textit{NGSPS.}---The NGSPS was a joint effort of multiple national ministries in China.
+It covers all of the pollution units from the agricultural, industrial, and domestic sources, as well as facilities for centralized treatment of pollution.
 In this study, we focus on the {industrial pollution sources}, which consist of businesses generating pollutants from the 39 manufacturing industries.
-The survey is organized directly by the State Council with data collection and quality control done by specially trained field staffs.
+The survey is organized directly by the State Council with data collection and quality control done by specially trained field staff.
 According to the \textit{Regulation on the National General Survey of Pollution Sources [Decree of the State Council of the People's Republic of China (No.
 508)]}, faking data would lead to financial penalties or even lawsuits.
-Therefore, the dataset is administrative in nature and is subject to less concerns of systematic under-reporting.\footnote{In fact, uniform under-reporting of emissions by small and large firms will not change the basic conclusions of this paper.
+Therefore, the dataset is administrative in its nature and is subject to less concerns of systematic under-reporting.\footnote{In fact, uniform under-reporting of emissions by small and large firms will not change the basic conclusions of this paper.
 Our results will be contaminated only if under-reporting by large firms is more severe than that by small firms, which is less likely in most polluting industries since larger firms are usually inspected more carefully.
@@
 A more detailed description of the dataset can be found in Online Appendix A.
-%\footnote{See \citet{Niuetal:2016} and \citet{Qietal:2017} and the references therein for recent examples.}
-
-The NGSPS collects information on the emissions of multiple air, water, and solid waste pollutants.
-In this paper, we focus on water pollution mainly because the data are more accurately measured than air pollution.\footnote{After our interview with the field staff, we learned that the differences in data quality was mainly caused by the differences in the sampling environment.
+
+The NGSPS collects information on the emissions of multiple air, water and solid waste pollutants.
+In this paper, we focus on water pollution mainly because the data are more accurately measured than air pollution.\footnote{After our interview with the field staff, we learned that the difference in data quality was mainly caused by the difference in sampling environment.
 For water pollution, firms rarely discharge wastewater directly.
-Instead, the wastewater is first stored in a sedimentation tank to settle heavier solids to the bottom and let lighter materials to float.
-This process creates a quiescent environment for sampling.
+Instead, the wastewater is first stored in a sedimentation tank to settle heavier solids to the bottom and let lighter materials float.
+This process creates a stable environment for sampling.
 For air pollutants, the sampling tube has to be placed in the chimneys, where the environment is much more volatile.
@@
 It is not because of under-reporting or other issues related to data quality.
-In fact, since these pollutants are more hazardous than others, firms that discharge these pollutants are usually monitored more closely.} Moreover, COD emissions are typically highly correlated with the emissions of other pollutants when both are positive.\footnote{In the Paper and Paper Products industry, for example, the correlation between the emissions of COD and $\text{NH}_4^+$ is $\text{corr}(\text{COD},\text{NH}_4^+) = \text{0.82}$ and that between COD and BOD is $\text{corr}(\text{COD},\text{BOD}) = \text{0.94}$.}
+In fact, since these pollutants are more hazardous than others, firms that discharge these pollutants are usually monitored more closely.} Moreover, COD emissions are typically highly correlated with the emissions of other pollutants when both are positive.\footnote{In the Paper and Paper Products industry, for example, the correlation between the emissions of COD and $\text{NH}_4^+$ is 0.82 and that between COD and BOD is 0.94.}
 
 The data reveal that industrial water pollutants are typically concentrated in a handful of industries, including COD.
-In our empirical analysis, we focus on the top five polluting industries in terms of COD emissions, which account for nearly 80\% of all COD emissions from industrial sources.
+In our empirical analysis, we focus on the top five polluting industries by COD emissions, which account for nearly 80\% of all COD emissions from industrial sources.
 Within narrowly defined manufacturing industries, the NGSPS divides firms into two large groups---\textit{key sources} and \textit{regular sources}.
 Firms identified as key sources are deemed as more polluting, and therefore are inspected and monitored by the government more carefully.
-%\footnote{See Online Appendix A.1 for more information on the key sources.}
 During this census, the field staff also collected extra information on these firms, and the data from these firms were inspected with greater care.
 Importantly, the key sources include both small and large firms, and the empirical densities of the log output of the key sources resemble the bell shape of those of all firms.\footnote{Please see Online Appendix A.1 for the formal definition of the key sources, and Figure B.1 in Online Appendix B for  the empirical densities of the log output of the key sources.} As a result, when empirically analyzing the relationship of firm size with pollution intensity and treatment technology adoption, we focus on the key sources, which account for more than 90\% of total COD emissions and 80\% of total output from the top five polluting industries (Table \ref{tab:top5summary}).
-The variables we use are the firm's output, the amount of major pollutants generated and emitted, installation costs of pollutant treatment technologies, industry (up to four-digit GB/T4574-2002), ownership classification, and province.
+The variables we use are firm's output, the amount of major pollutants generated and emitted, installation costs of pollutant treatment technologies, industry (up to four-digit GB/T4574-2002), ownership classification, and province.
 
@@
     \hline \hline
-                                       & Paper & Food Processing& Textiles  & Chemical Materials & Beverages  \\
+                                       & Paper & Food & Textiles  & Chemicals & Beverages  \\
     \hline
@@
 We use observations that belong to the manufacturing sector.
-The variables we use are the firm's output, labor compensation, book value of capital stock, number of employees, industry (up to four-digit GB/T4574-2002), ownership classification, and province.\footnote{A widely used firm-level dataset in China is the Annual Surveys of Industrial Firms (ASIF).
+The variables we use are firm's output, labor compensation, book value of capital stock, number of employees, industry (up to four-digit GB/T4574-2002), ownership classification, and province.\footnote{A widely used firm-level dataset in China is the Annual Surveys of Industrial Firms (ASIF).
 We use CNEC instead of ASIF because that ASIF does not have information on non-state firms with sales below 5 million CNY, which are crucial for our analysis.
@@
 \end{equation}
-where $\vec{X} = \{\vec{X_s}, \vec{X_p}, \vec{X_o}\}$ refers to the dummy variables for two-digit industry, province, and ownership respectively.
-The estimates are all statistically significant at the 0.1\% level, with the standard errors reported in the parentheses below the estimates.
+where $\vec{X} = \{\vec{X_s}, \vec{X_p}, \vec{X_o}\}$ refers to the dummy variables for two-digit industry, province and ownership respectively.
+The estimates are all statistically significant at 0.1\% level, with standard errors reported in the parentheses below the estimates.
 
@@
 Figure \ref{fig:codscatter} visualizes this negative relationship, where the residuals from regressing intensity and output on the dummies are plotted to remove the influences of other covariates.
-%\footnote{Recall that here by the \textit{Regression Anatomy Formula}, the slope of the least square fit in Figure \ref{fig:codscatter} is precisely one minus the coefficient on $\log(\text{Output})$ in Equation (\ref{eq:poolols}).}
 The estimation has an $R^2$ of 0.41, suggesting that nearly half of the variations in COD emissions can be explained by the variations in firm output and in the three sets of dummies.\footnote{We also tried other econometric specifications, and found similar negative correlations between pollution intensity and firm size.
-For instance, we estimated versions of Equation (\ref{eq:poolols}) for each industry and with robust standard errors clustered in provinces.
+For instance, we estimated versions of Equation (\ref{eq:poolols}) for each industry and with robust standard errors clustered by provinces.
 Please see Online Appendix C for more information.} We would also like to point out that the coefficient of the dummy on whether a firm is state-owned or not, is statistically insignificant.
@@
 The NGSPS groups wastewater treatment technologies into five categories: physical, chemical, physio-chemical, biological, and {combined} technologies.
-In the subsequent analysis, we drop {physio-chemical} technologies because fewer than 0.5\% of the firms adopt this type of technologies.
-In addition, because {combined} technologies look very similar to biological technologies for all the technical aspects we are interested in, we group them with {biological} technologies.\footnote{Examples of the technologies attributed to these three base categories include filtering, centrifuging, precipitation, and separation (physical); oxidation reduction and neutralization (chemical); and aerobic biological treatment and activated sludge processes (biological).
+In the subsequent analysis, we drop {physio-chemical} technology because fewer than 0.5\% of the firms adopt this type of technology.
+In addition, because {combined} technology looks very similar to biological technology for all the technical aspects we are interested in, we group them with {biological} technology.\footnote{Examples of the technologies attributed to these three base categories include filtering, centrifuging, precipitation, and separation (physical); oxidation reduction and neutralization (chemical); and aerobic biological treatment and activated sludge processes (biological).
 Broadly speaking, physical technology corresponds to the \textit{Preliminary} and \textit{Primary} treatment in the U.S., while chemical and biological technologies correspond to the \textit{Secondary} and \textit{Tertiary} treatment.} In sum, we are left with three broad categories of technologies.
@@
 By focusing on one specific industry, we abstract from the potential heterogeneity in production processes across industries.
-%\footnote{We focus on one industry because of the potential heterogeneity in production processes across industries.}
 Table \ref{tab:techeffi} shows the mean abatement efficiency, median installation costs, and median output of firms that adopt these technologies, where the {abatement efficiency} is defined as one minus the ratio of {emitted COD} to {generated COD}.
-%\footnote{Online Appendix D.2 provides more details.}
 \begin{table}[t]
@@
 \end{table}
-We find that for each 100 tons of COD generated, firms with biological technologies on average emit 19.1 tons of COD, compared to 36.6 tons for firms with physical technologies.
-Meanwhile, the median installation costs of biological technologies are 8 times higher than those of physical technologies.
-In addition, the median output of the firms using biological technologies are 4 times higher than those of firms with physical technologies.
-These point to increasing returns to scale in the adoption of cleaner technologies.
+We find that for each 100 tons of COD generated, firms with biological technology on average emit 19.1 tons of COD, compared to 36.6 tons for firms with physical technology.
+Meanwhile, the median installation costs of biological technology are 8 times higher than those of physical technology.
+In addition, the median output of the firms using biological technology are 4 times higher than those of firms with physical technology.
+These evidence points to increasing returns to scale in the adoption of cleaner technologies.
 As a result, small firms lack the profit margins needed to take advantage of these increasing returns to scale, while large firms are more likely to adopt cleaner technologies.
@@
 \end{equation*}
-where $y_i$ is a dummy variable which equals to 1 when a firm uses biological technologies.
-The estimates show that doubling a firm's output leads to a 5 percentage points increase in the adoption rate of biological technologies.
+where $y_i$ is a dummy variable which equals to 1 when a firm uses biological technology.
+The estimates show that doubling a firm's output leads to a 5 percentage points increase in the adoption rate of biological technology.
 This confirms our previous finding with the paper industry that larger firms are more likely to use cleaner technologies.
 
-\textit{Emissions Generated During Production.---}Another reason behind the negative correlation between pollution intensity and firm size is that large firms also generate less COD per output during the production stage.
-In particular, if we divide our sample into two groups according to whether a firm is using biological technologies or not and repeat regression (\ref{eq:poolols}) again, we find significantly negative correlations between COD per output and firm size within each group:
+\textit{Emissions Generated during Production.---}Another reason behind the negative correlation between pollution intensity and firm size is that large firms also generate less COD per output during the production stage.
+In particular, if we divide our sample into two groups according to whether a firm is using biological technology or not and repeat regression (\ref{eq:poolols}) again, we find significantly negative correlations between COD per output and firm size within each group:
 \begin{align}
@@
 Such within group negative correlations could be because that larger firms use cleaner or fewer inputs to produce the same amount of output.
-For one example, the paper pulp industry uses two different types of inputs: the bagasse and the wood.
-According to the \textit{Handbook of Emission Coefficients} by the Chinese Academy of Sciences, the bagasse, which is mostly used by firms with an annual production of less than 100 kilotons, generates 140--180 kg of COD per ton of output, and the wood, which is mostly used by firms with an annual production of more than 100 kilotons, generates 30--55 kg of COD per ton of output.
-%\footnote{See the \textit{Handbook of Emission Coefficients} published by the \textit{Chinese Academy of Sciences}.}
+For one example, the paper pulp industry uses two different types of inputs: bagasse and wood.
+According to the \textit{Handbook of Emission Coefficients} by the Chinese Academy of Sciences, bagasse, which is mostly used by firms with an annual production of less than 100 kilotons, generates 140--180 kg of COD per ton of output, while wood, which is mostly used by firms with an annual production of more than 100 kilotons, generates 30--55 kg of COD per ton of output.
 As another example, \citet{Bloometal:2010} find that better managed firms use less energy to produce the same amount of output in the U.K.
@@
 The negative correlation between pollution intensity and firm size suggests that firm size distribution plays a potentially important role in aggregate pollution intensity.
-To illustrate the point, we document facts on the firm size distribution in China and in the U.S., and compute the change in the aggregate pollution intensity if the firm size distribution for the top five polluting industries in China were replaced with that in the U.S.
+To illustrate this point, we document facts on the firm size distributions in China and in the U.S., and compute the change in the aggregate pollution intensity if the firm size distribution for the top five polluting industries in China were replaced with that in the U.S.
 We choose the U.S.
-as the benchmark because it is a relatively less distorted economy, and China and the U.S.
+as the benchmark because it is a relatively less distorted economy; and China and the U.S.
 are both large economies with a complete set of industries so that we can find comparable industries in both economies.\footnote{It is a commonly used strategy in the macro-development literature to take the U.S.
 economy as an undistorted benchmark.
-See \citet{Guneretal:2008}, \citet{HsiehKlenow:2009, HsiehKlenow:2014}, \citet{Bartelsmanetal:2013}, and \citet{AdamopoulosRestuccia:2014}, among others.}
+See \citet{Guneretal:2008}, \citet{HsiehKlenow:2009, HsiehKlenow:2014}, \citet{Bartelsmanetal:2013} and \citet{AdamopoulosRestuccia:2014}, among others.}
 
@@
 We use the \textit{International Standard Industrial Classification of All Economic Activities, Revision 3.1} (ISIC Rev.
-3.1) published by the United Nations to bridge the different industrial classification systems adopted by China (GB/T4574-2002) and the United States (NAICS 2002).
+3.1) published by the United Nations to bridge the different industrial classification systems adopted by China (GB/T4574-2002) and the U.S.
+(NAICS 2002).
 Specifically, we use the crosswalks of GB/2002 at the four-digit level and those of NAICS/2002 at the six-digit level to the ISIC Rev.
@@
 The left panel of Figure \ref{fig:es} depicts the firm size distribution for the top five polluting industries pooled together.
-We find that approximately 70\% of employment in the United States is accounted for by firms with 400+ employees, while in China the number is only 20\%.\footnote{In Online Appendix E, we compare the firm size distributions between China and the U.S.
+We find that approximately 70\% of employment in the U.S.
+is accounted for by firms with 400+ employees, while in China the number is only 20\%.\footnote{In Online Appendix E, we compare the firm size distributions between China and the U.S.
 for each individual polluting industry.
 We find that while there is substantial heterogeneity across individual industries, large firms in China account for a much smaller employment shares than those in the U.S.
-for each industry.}
+for all five industries.}
 Compared with the U.S., a much larger share of production is carried out by small and medium-sized firms in China.
@@
 Then we compute the resulting average pollution intensity for these polluting industries pooled together.
-%\footnote{Online Appendix F provides more details.}
 This simple exercise is complicated by the fact that the NGSPS reports firm-level output instead of number of employees.
-Therefore, we construct an employment--output relationship from a linear regression using the CNEC data.\footnote{There are different methods to construct the employment--output relationship using the CNEC data, and all of them provide similar results.
+Therefore, we construct an employment--output relationship from a linear regression using the CNEC data.\footnote{There are different methods to construct the employment--output relationship using the CNEC data, but all of them provide similar results.
 See Online Appendix F for details.}
@@
 are mainly caused by distortions or by some other factors.
-Second, the accounting exercise captures the technique channel only, while distortions may operate through the scale and composition effects as well.
+Second, the accounting exercise captures the technique effect only, while distortions may operate through the scale and composition effects as well.
 Third, the relationship between firm size and emissions intensity is taken as exogenous in the accounting exercise.
-However, distortions to firm size may also influence firm's incentive to adopt different treatment technologies, which endogenizes the firm size-intensity relationship.
-
-To address these issues, we build a two-sector (polluting and non-polluting) model of heterogeneous firms based on the classic \citet{Lucas:1978b} span-of-control model.\footnote{A widely used alternative  in the misallocation literature is the closed-economy version of \citet{Melitz:2003}.
+However, distortions to firm size may also influence firm's incentive to adopt different treatment technologies, which endogenizes the firm size--intensity relationship.
+
+To address these issues, we build a two-sector (polluting and non-polluting) model of heterogeneous firms based on the classic \citet{Lucas:1978b} span-of-control model.\footnote{A widely used alternative  in the misallocation literature is the closed-economy version of the \citet{Melitz:2003} model.
 \citet{HsiehKlenow:2009} establish that these two frameworks are isomorphic for the effects of misallocation on aggregate output when the number of firms is fixed.
-In Appendix G.3, we show the qualitative equivalence between the two families of models.} The model features heterogeneity in firm productivities in both sectors, heterogeneity in pollution intensity and endogenous choice of pollution treatment technologies in the polluting sector.
+In Appendix G.3, we show the qualitative equivalence between the two families of models as well.} The model features heterogeneity in firm productivity in both sectors, heterogeneity in pollution intensity and an endogenous choice of pollution treatment technologies in the polluting sector.
 Motivated by the data, firms in both sectors are subject to correlated distortions [\citet{RestucciaRogerson:2008}] in the form of progressive output taxes.
@@
 
-We assume that the products of the two sectors in the model economy are perfect substitutes to each other.\footnote{In Online Appendix J, we consider the case in which the final good is a CES aggregation of the goods produced in two sectors, and conduct counterfactual experiments under different values of the elasticity of substitution in the CES function.
+We assume that the products of the two sectors in the model economy are perfect substitutes to each other.\footnote{In Online Appendix J, we consider the case in which the final good is a CES aggregation of the goods produced in the two sectors, and conduct counterfactual experiments under different values of the elasticity of substitution in the CES function.
 For the counterfactual experiments we discuss in the main text, the quantitative results in the CES cases are similar to those in the perfect substitute case, largely because the experiments induce very limited reallocation between sectors.} The polluting sector generates emissions as a by-product of production as in \citet{CopelandTaylor:1994}, while the non-polluting sector does not.
-The top five polluting industries (hence the polluting sector) account for nearly 80\% of total industrial COD emissions and 20\% of total industrial output, with the rest accounted for by the non-polluting sector.
+The top five polluting industries (henceforth the polluting sector) account for nearly 80\% of total industrial COD emissions and 20\% of total industrial output, with the rest accounted for by the non-polluting sector.
 Firms in both sectors behave competitively.
@@
 A fraction $\mu$ of the members are endowed with managerial talent that can be used in the polluting sector, drawn from a distribution with cumulative distribution function (CDF) $G^{d}(z)$, where the superscript $d$ refers to the polluting sector.
-Meanwhile, a fraction $1-\mu$ of the members are endowed with managerial talent for the non-polluting sector with CDF $G^{c}(z)$, where the superscript $c$ refers to the non-polluting sector.
+Meanwhile, a fraction $1-\mu$ of the members are endowed with managerial talent for the non-polluting sector with CDF $G^{c}(z)$, with the superscript $c$ referring to the non-polluting sector.
 The support for both distributions are $Z \triangleq [0,\overline{z}]$.
@@
 The goods produced in the non-polluting sector are taken as the numeraire.
-With perfect substitution between goods, the price of the goods produced in the polluting sector is also 1.
+With perfect substitution between goods, the price of the polluting sector product is also 1.
 $R$ and $W$ are the capital rental price and wage rate, respectively.
@@
 \label{eq:intensity_size}
-    \log\left(\frac{e}{y}\right) = \psi_0^{(j)}+ \psi_1^{(j)} \log y, \quad j = 0,1,
+    \log\left(\frac{e}{y}\right) = \psi_0^{j}+ \psi_1^{j} \log y, \quad j = 0,1,
 \end{equation}
-where $\psi_1^{(j)}<0$. This formulation indicates that larger firms emit fewer pollutants per unit of output, which is consistent with our empirical findings in Section I.B.
+where $\psi_1^{j}<0$. This formulation indicates that larger firms emit fewer pollutants per unit of output, which is consistent with our empirical findings in Section I.B.
 
@@
 We assume that the environmental authority punishes firms for using the dirty technology.
-Similar in spirit to \citet{ShapiroWalker:2015}, we model the environmental regulations in a parsimonious way as a penalty which equals to a proportion $\xi$ of the firm's profits.
+Similar in spirit to \citet{ShapiroWalker:2015}, we model environmental regulations in a parsimonious way as a penalty which equals to a proportion $\xi$ of the firm's profits.
 The penalty is later redistributed to the household as lump-sum transfers.\footnote{In practice, China employs both economic incentives and command-and-control instruments in its current industrial pollution management and control system.
@@
 See Trevor Nace, ``China shuts down tens of thousands of factories in widespread pollution crackdown,'' Forbes, October 24th 2017, for an anecdotal example.
-We present a short summary of China's current environmental regulations based on \citet{Lin:2013} in Online Appendix D.3.} Therefore, the central trade-off in a firm's technology choice is weighing the adoption cost $R k_E$ against the profit losses from the environmental penalties.
-To the extent that firms' profits increase with firm size, we implicitly capture the size-dependency of the environmental regulations, in the sense that larger firms are usually monitored and inspected more closely.
+We present a short summary of China's current environmental regulations based on \citet{Lin:2013} in Online Appendix D.3.} Therefore, the central trade-off in a firm's technology choice is weighing the adoption cost $R k_E$ against the profit losses from environmental penalties.
+To the extent that firm's profits increase with firm size, we implicitly capture the size-dependency of environmental regulations, in the sense that larger firms are usually monitored and inspected more closely.
 A key prediction from these assumptions is that, only firms above a certain size threshold would choose the clean technology, which is qualitatively consistent with our empirical findings on technology adoption in Section I.B.\footnote{In Online Appendix D.2, we provide further evidence that the ratio of a firm's expenditures on treatment technology to firm output decreases with firm size, which supports the fixed cost assumption.}
@@
 In Online Appendix D.1, we discuss distortions that take more general forms, and present empirical evidence in support of this specific form.
-See Figure D.2 in Online Appendix D for an illustration of this tax function.}
+Figure D.2 in Online Appendix D provides an illustration of this tax function.}
 
@@
 We take these values from our calibration in Section III, which implies that $\alpha = \text{0.54}$ and $\gamma = \text{0.93}$.
-The positive relationship between firm TFP and average product of factors, however, hold for a wide range of values for $\alpha$ and $\gamma$, in addition to the values used here.
+The positive relationship between firm TFP and average product of factors, however, holds for a wide range of values for $\alpha$ and $\gamma$, in addition to the values used here.
 Moreover, similar patterns are also observed in other countries.
@@
 
-The firm-level distortions $\tau_z$ are meant to capture a variety of policies and institutions that reallocate production factors from large productive to small unproductive firms, following the \emph{indirect} approach in the misallocation literature [\citet{RestucciaRogerson:2013}].
-These policies and institutions include size-dependent taxes and subsidies that favor small firms, imperfect tax enforcement that induces tax evasion among small firms, financial constraints and contractual frictions that impede the growth of productive firms [\citet{CooleyQuadrini:2001}, \citet{ClementiHopenhayn:2006} and \citet{Akcigitetal:2018}], and local protectionism and internal trade barriers that disproportionately affect large productive firms [\citet{Eberhardtetal:2016} and \citet{TombeZhu:2015}].
+The firm-level distortions $\tau_z$ are meant to capture a variety of policies and institutions that reallocate production factors from large productive to small unproductive firms, following the \emph{indirect} approach in the misallocation literature [\citet{RestucciaRogerson:2013,RestucciaRogerson:2017}].
+These policies and institutions include size-dependent taxes and subsidies that favor small firms, imperfect tax enforcement that induces tax evasion among small firms, financial constraints and contractual frictions that impede the growth of productive firms [\citet{CooleyQuadrini:2001}, \citet{ClementiHopenhayn:2006} and \citet{Akcigitetal:2018}] and local protectionism and internal trade barriers that disproportionately affect large productive firms [\citet{Eberhardtetal:2016} and \citet{TombeZhu:2015}].
 While it is of great policy interest to study specific policies and institutions underlying $\tau_z$, we leave this important task to future work.
@@
 Firms in the polluting sector choose first the optimal treatment technology and then the optimal production plan.
-The profit function $\pi^d(z)$ is the envelope of the profits when using the dirty technology $\pi_0^d(z)$ and clean technology, $\pi_1^d(z)$:
+The profit function $\pi^d(z)$ is the envelope of the profits when using the dirty technology $\pi_0^d(z)$ and clean technology $\pi_1^d(z)$:
 \begin{equation*}
     \pi^d(z) = \max \left\{ \pi_0^d(z), \pi_1^d(z) \right\},
-%\label{eq:piz}
-\end{equation*}
-where the superscript $d$ refers to the polluting sector, and the subscripts denotes the treatment technologies.
+\end{equation*}
+where the superscript $d$ refers to the polluting sector, and the subscripts denote the treatment technologies.
 Firms using the clean technology are not subject to environmental penalties, hence the profit $\pi_1^d(z)$ is:
@@
     \pi_1^d(z) = \max_{k,l} \left\{ (1-\tau_z) z^{1-\gamma} (k^{\alpha} l^{1-\alpha})^{\gamma} - Wl - R (k+k_E) \right\}.
-%\label{eq:pi1z}
-\end{equation*}
-However, when a firm chooses the dirty technology, it will be punished by the environmental authority, and lose a fraction $\xi$ of its gross profit. Its net profit $\pi_0^d(z)$ is thus:
+\end{equation*}
+However, when a firm chooses the dirty technology, it will be punished by the environmental authority, and loses a fraction $\xi$ of its gross profit. The net profit $\pi_0^d(z)$ is thus:
 \begin{equation*}
@@
         \left[ (1-\tau_z) z^{1-\gamma} (k^{\alpha} l^{1-\alpha})^{\gamma} - Wl - Rk \right] \right\}.
-%\label{eq:pi0z}
 \end{equation*}
@@
 \end{equation*}
-In addition, when $1-\gamma+\phi_1 > 0$, which is satisfied given our calibrated values for $\gamma$ and $\phi_1$, $\pi_i^d(z)$ and $l^d(z)$ are both increasing $z$.
-Then, as we show in Lemma 2 of Online Appendix G.1, there exists a threshold $\tilde{z}_d$ such that only firms with TFP higher than $\tilde{z}_d$ would choose clean technology.
-%\footnote{Please see Lemma 2 in Online Appendix G.1 for details.}
+When $1-\gamma+\phi_1 > 0$, which is satisfied given our calibrated values for $\gamma$ and $\phi_1$, $\pi_i^d(z)$ and $l^d(z)$ are both increasing $z$.
+Then, as we show in Lemma 2 of Online Appendix G.1, there exists a threshold $\tilde{z}_d$ (hence $\tilde{l}^d$) such that only firms with TFP higher than $\tilde{z}_d$ would choose clean technology.
 There also exist two thresholds $\hat{z}_i, i=c,d,$ such that in sector $i$, only members with $z > \hat{z}_i$ choose to be managers.
@@
 \end{align}
-where $K_t$ is aggregate capital, $\delta$ is the depreciation rate, and $I_t$ is household income, which we specify in detail shortly.\footnote{Here we do not explicitly model the household's preference over water quality.
+where $K_t$ is aggregate capital, $\delta$ is depreciation rate and $I_t$ is household income, which we specify in detail shortly.\footnote{Here we do not explicitly model the household's preference over water quality.
 Adding water quality to the household's utility function will not change the firm's choices in a competitive equilibrium, as no individual household member has any control over the aggregate environmental quality.
@@
 \end{align*}
-where the transfer $T$ is given by
+where the transfers $T$ are given by
 \begin{equation*}
@@
 \label{def:ge}
-A stationary equilibrium of the model consists of prices $\{W, R \}$, allocations $\{C, K, Y \}$, firms' policy functions $\{k^j(z),l^j(z),y^j(z),\pi^j(z)\}, j = c,d$, thresholds for household's occupational choices $\{\hat{z}_c, \hat{z}_d\}$ and polluting firms' technology adoption $\tilde{z}_d$, as well as aggregate pollution $E$, such that:
+cA stationary equilibrium of the model consists of prices $\{W, R \}$, allocations $\{C, K, Y \}$, firms' policy functions $\{k^j(z),l^j(z),y^j(z),\pi^j(z)\}, j = c,d$, thresholds for household's occupational choices $\{\hat{z}_c, \hat{z}_d\}$ and polluting firms' technology adoption $\tilde{z}_d$, as well as aggregate pollution $E$, such that:
 \begin{enumerate}[(i)]
@@
 Second, using a simplified one-sector model with a fixed number of firms and exogenous firm-level pollution intensity, we characterize the conditions under which correlated distortions lead to higher aggregate pollution.
-The core trade-off here is between the scale and technique effects, because the correlated distortions generally cause a decrease in average pollution intensity but an increase in aggregate output.
+The core trade-off here is between the scale and technique effects, because removing the correlated distortions generally brings a decrease in average pollution intensity but an increase in aggregate output.
 All the proofs and related analytical results can be found in Appendices G.1 and G.2.
-%\footnote{All the proofs and additional analytical results can be found in Appendices G.1 and G.2.}
 
@@
 Since $\phi_1 < 0$, the slope of the profit functions are flatter, and the threshold where firms switch technologies is higher when they face distortions.
-As a result, while firms with TFP in the range $[\tilde{z}_n, \tilde{z}_f]$ would choose the clean technology when they are not subject to distortions and choose the dirty technology when they are.\footnote{Of course, when the correlated distortions apply to all firms in the economy, they would affect the equilibrium wage $W$ and hence $\tilde{z}_f$ in equilibrium.
+As a result, while firms with TFP in the range $[\tilde{z}_n, \tilde{z}_f]$ would choose the clean technology when they are not subject to distortions, they will choose the dirty technology instead when distortions exist.\footnote{Of course, when the correlated distortions apply to all firms in the economy, they would affect the equilibrium wage $W$ and hence $\tilde{z}_f$ in equilibrium.
 We find later in our quantitative analysis that $\tilde{z}_f > \tilde{z}_n$ even when general equilibrium effects are considered.}
 
-\textit{Aggregate Pollution.---}To derive a closed-form expression for the relationship between correlated distortions and aggregate pollution, we build a simplified one-sector model that abstracts from the endogenous occupation choice and treatment technology choice.
-%\footnote{Please see Online Appendix G.2 for a detailed description of the simplified model and additional analytical results.}
+\textit{Aggregate Pollution.---}To derive a closed-form expression for the relationship between correlated distortions and aggregate pollution, we build a simplified one-sector model that abstracts from endogenous occupation choice and treatment technology choice.
 This complements our analysis in Proposition \ref{prop:friction}, which focuses on how distortions affect firms' decision in that the general equilibrium effects are captured.
@@
 \end{equation*}
-such that $E$ is increasing in $\phi_1$ when $\phi_1 < \hat{\phi}_1$, and decreasing when $\phi_1 \geq \hat{\phi}_1$.
+such that $E$ is increasing in $\phi_1$ when $\phi_1 < \hat{\phi}_1$ and decreasing when $\phi_1 \geq \hat{\phi}_1$.
 \end{proposition}
@@
 \begin{equation*}
-    e = \mathcal{E}(j,y) = \mathrm{e}^{\psi_0^{(j)}} y^{1+\psi_1^{(j)}}, j=0,1,
-\end{equation*}
-where $\{\psi_0^{(j)}, \psi_1^{(j)}\}$ are based on the reduced-form estimates from Equations (\ref{eq:poolols_biological}) and (\ref{eq:poolols_others}).
+    e = \mathcal{E}(j,y) = \mathrm{e}^{\psi_0^{j}} y^{1+\psi_1^{j}}, j=0,1,
+\end{equation*}
+where $\{\psi_0^{j}, \psi_1^{j}\}$ are based on the reduced-form estimates from Equations (\ref{eq:poolols_biological}) and (\ref{eq:poolols_others}).
 
@@
 To calibrate $G(\cdot)$, we cannot use Equation (\ref{eq:zandl}) and the firm-level data to back out the distribution semi-parametrically.
-The reason is that the endogenous occupation choice in our model makes the distribution of firm TFP in equilibrium also endogenous, making the semi-parametric way of calibration untractable in practice.
+The reason is that the endogenous occupation choice in our model makes the distribution of firm TFP in equilibrium also endogenous, causing the semi-parametric way of calibration untractable in practice.
 This is unlike other studies that assume a fixed distribution of firm TFP in equilibrium, for instance \citet{BentoRestuccia:2016}.
 To keep the calibration process tractable, motivated by Equation (\ref{eq:zandl}), we assume that the distribution of the ``after-tax'' TFP $z' = (1-\tau_z)z^{1-\gamma}$ takes the following form: the majority on the bottom side characterized by a truncated log-normal distribution with log mean $\mu$ and standard deviation $\sigma$, and a top value $z'_{max}$ with a total mass $g_{max}$ representing the large firms.
-This mass of top managers allows our model to match the observed concentration of employment among large firms, which have lower emission intensities than other firms.\footnote{This strategy is popular among macroeconomic studies on distributions with fat tails.
+This mass of top managers allows our model to match the observed concentration of employment among large firms, which have lower emission intensities than other firms.\footnote{This strategy is popular among macroeconomic studies featuring distributions with fat tails.
 See for example, \citet{Castanedaetal:2003} and \citet{Guneretal:2008}.} We then choose the values of $(\mu, \sigma, z'_{max}, g_{max})$ together with $\gamma$ and $\phi_1$ to match the observed firm size distribution and Equation (\ref{eq:avgl}).
@@
 
-In total, we need to choose values for 17 parameters: the discount factor $\beta$, depreciation rate $\delta$, production technology parameters $\{\alpha, \gamma \}$, the relative size of the polluting sector $\mu$, treatment technology parameters $\{\psi_0^{(0)}, \psi_1^{(0)}, \psi_0^{(1)}, \psi_1^{(1)}, k_E, \xi \}$, correlated distortions $\{ \phi_0, \phi_1 \}$, and distributional parameters $\{\mu_z, \sigma_z, z'_{max}, g_{max}\}$.
+In total, we need to determine values for 17 parameters: discount factor $\beta$, depreciation rate $\delta$, production technology parameters $\{\alpha, \gamma \}$, the relative size of the polluting sector $\mu$, treatment technology parameters $\{\psi_0^{0}, \psi_1^{0}, \psi_0^{1}, \psi_1^{1}, k_E, \xi \}$, correlated distortions $\{ \phi_0, \phi_1 \}$, and distributional parameters $\{\mu_z, \sigma_z, z'_{max}, g_{max}\}$.
 
@@
 We set the depreciation rate $\delta$ to 10\% [\citet{Songetal:2011}].
-\\ $\{\psi_0^{(0)}, \psi_1^{(0)}, \psi_0^{(1)}, \psi_1^{(1)} \}$ are taken from the reduced-form estimates from regressions (\ref{eq:poolols_biological}) and (\ref{eq:poolols_others}) in Section I.B, giving us $\psi_0^{(0)} = -$3.41, $\psi_1^{(0)} = -$0.36, $\psi_0^{(1)} = -$4.37, and  $\psi_1^{(1)} = -$0.33.
+$\{\psi_0^{0}, \psi_1^{0}, \psi_0^{1}, \psi_1^{1} \}$ are taken from the reduced-form estimates from regressions (\ref{eq:poolols_biological}) and (\ref{eq:poolols_others}) in Section I.B, giving us $\psi_0^{0} = -$3.41, $\psi_1^{0} = -$0.36, $\psi_0^{1} = -$4.37, and  $\psi_1^{1} = -$0.33.
 In the context of our model, these estimates suggest that, on average, for two firms with the same level of output but different treatment technologies, the firm using the clean technology emits 40\% to 60\% less pollutants than the one with the dirty technology.
 We set $\mu =$ 0.20, which is the share of manufacturing firms accounted for by the five polluting industries in the CNEC data.
-The share of manufacturing output accounted for by these five industries is also quite close, which is 18\%.%\footnote{The share of manufacturing output accounted for by these five industries is 18\%, which is very close as well.}
+The share of manufacturing output accounted for by these five industries is also quite close, which is 18\%.
 
@@
 Still, some parameters can be calibrated more or less independently from others, which substantially improves the tractability of the calibration process.
-In particular, we choose $\beta$ and $\alpha$ to match the capital to output ratio of 1.65, and capital share of 0.5 in China respectively [\citet{Baietal:2006}].
+In particular, we choose $\beta$ and $\alpha$ to match the capital to output ratio of 1.65 and capital share of 0.5 in China respectively [\citet{Baietal:2006}].
 We set $\xi$ and $k_E$ such that the model reflects the average cost to install clean technology in the data.
@@
 Reassuringly, a change in $\phi_0$ causes a uniform change in firm-level distortions, and therefore has very limited impact on firm size distribution and aggregate pollution intensity.
-As a result, a different calibration target for $\phi_0$ will not affect the main insight of our paper.} Table \ref{tab:calibration} lists the model parameters, their targets, and the calibrated values.
+As a result, a different calibration target for $\phi_0$ will not affect the main insight of our paper.} Table \ref{tab:calibration} lists the model parameters, their targets and the calibrated values.
 
@@
     \hline
-    Treatment     & $\psi_0^{(0)}$    & $-$3.4144     & Estimates from Regression (\ref{eq:poolols_biological})     \\
-                  & $\psi_1^{(0)}$    & $-$0.3636     &                                                             \\
-                  & $\psi_0^{(1)}$    & $-$4.3748     & Estimates from Regression (\ref{eq:poolols_others})         \\
-                  & $\psi_1^{(1)}$    & $-$0.3288     &                                                             \\
+    Treatment     & $\psi_0^{0}$      & $-$3.4144     & Estimates from Regression (\ref{eq:poolols_biological})     \\
+                  & $\psi_1^{0}$      & $-$0.3636     &                                                             \\
+                  & $\psi_0^{1}$      & $-$4.3748     & Estimates from Regression (\ref{eq:poolols_others})         \\
+                  & $\psi_1^{1}$      & $-$0.3288     &                                                             \\
                   & $k_E$             & 4.6000        & Clean Firms: Fixed Cost/Output Ratio (2.5\%)                \\
@@
 \begin{tablenotes}
-     \textsuperscript{$\dagger$}The parameters are jointly calibrated.
+     \textsuperscript{$\dagger$}These parameters are jointly calibrated.
 \end{tablenotes}
@@
 For example, \citet{OlleyPakes:1996} estimate the value to be between 0.8 and 0.9 for the U.S.
-telecommunications equipment industry, while the estimates from \citet{Bailyetal:1992} point towards close to constant returns to scale for many manufacturing industries in the U.S..
+telecommunications equipment industry, while the estimates from \citet{Bailyetal:1992} point towards close to constant returns to scale for many manufacturing industries in the U.S.
 See also the discussions in \citet{AtkesonKehoe:2005}.} A relatively high value of $\gamma$ is needed to match the employment share of large firms (in particular those with 400+ employees) given the existence of correlated distortions, because we need high returns to scale so that the right amount of resources will be concentrated among firms with high TFP.
-However, if $\gamma$ is too large, the high demand for factors from the large firms would push up the factor prices, and therefore drive many small firms with low TFP out of the market through endogenous occupation choices.
+However, if $\gamma$ is too large, the high demand for labor from the large firms would push up the wage, and therefore drive many small firms with low TFP out of the market through endogenous occupation choice.
 This would jeopardize our model's fit of the fraction of small firms to the data.
@@
 We conduct two sets of counterfactual experiments.
-In Experiment (i), we follow the \emph{indirect} approach in the misallocation literature and remove correlated distortions from both sectors by changing $\tau_z$ to $0$.\footnote{In Online Appendix I, we build and calibrate a similar model in which the final consumption is a CES aggregation of the products from two sectors, and use the model to evaluate the impact of removing the correlated distortions from the polluting sector only.
+In Experiment (i), we follow the \emph{indirect} approach in the misallocation literature and remove correlated distortions from both sectors by changing $\tau_z$ to $0$.\footnote{For the CES case in Online Appendix I, we use the model to evaluate the impact of removing the correlated distortions from the polluting sector only.
 The main difference between this experiment and Experiment (i) in the main text is that this one induces large reallocation of factors from the non-polluting to the polluting sector.
@@
 } This is meant to capture the overall effects of a variety of policies and institutions that reallocate resources from high to low TFP firms.
-To isolate the importance of the {progressivity} of distortions, later we replace the progressive taxes with flat taxes by setting $\phi_1=0$, and change $\phi_0$ to keep the total implicit tax revenue constant.
+To isolate the importance of the {progressiveness} of distortions, later we replace the progressive taxes with flat taxes by setting $\phi_1 = $ 0, and change $\phi_0$ to keep the total implicit tax revenue constant.
 In Experiment (ii), we tighten the environmental regulations by increasing $\xi$ to the extent that the fraction of firms using the clean technology is the same as in Experiment (i).
@@
 The decrease in aggregate pollution is consistent with Proposition \ref{prop:agge}, given the calibrated values for $(\phi_1, \gamma)$, and the estimated relationship between pollution intensity and firm size.
-%\footnote{The decrease in aggregate pollution is consistent with the prediction from Proposition \ref{prop:agge}, given the calibrated values for $\phi_1$, $\gamma$ and the estimated relationship between pollution intensity and firm size.}
 
@@
 \caption{Resource Allocation on the Intensive Margin}
-\begin{tabular}{lccccc}%{p{65pt} >{\centering\arraybackslash}p{45pt} >{\centering\arraybackslash}p{45pt} >{\centering\arraybackslash}p{45pt} >{\centering\arraybackslash}p{45pt} >{\centering\arraybackslash}p{45pt}}
+\begin{tabular}{lccccc}
     \hline \hline
@@
 
-Removing correlated distortions causes large reallocation of production factors across firms, and leads to improved allocation along both the extensive and intensive margins.
-The \textit{extensive} margin is defined as the selection of firms into production, and the \textit{intensive} margin as the production distribution among the active firms.
+Removing correlated distortions causes large reallocation of production factors across firms and leads to substantial changes in the firm size distribution.
+Resource allocation along both the extensive and intensive margins are improved.
+The {extensive} margin is defined as the selection of firms into production, and the {intensive} margin as the production distribution among the active firms.
 Specifically, since the distortions $\tau_z$ are higher for high TFP firms in the benchmark economy, a large share of the production factors would flow to these firms after the removal of distortions (intensive margin).
-The increased labor demand from these firms would drive up the equilibrium wage by 60\%, which would in turn drive many unproductive firms out of the market through the endogenous occupation choices (extensive margin).
-Due to the changes along the extensive margin, the total number of firms is cut by more than half, and the mean firm size more than doubles.
+The increased labor demand from these firms pulls up the equilibrium wage by 60\%, which in turn drives many unproductive firms out of the market through the endogenous occupation choice (extensive margin).
+Due to the changes along the extensive margin, the total number of firms is cut by more than 50\%, and the mean firm size more than doubles.
 Along the intensive margin, as we see from Table \ref{tab:talentdist}, surviving firms with TFP in the top two quintiles expand at the expense of those with lower TFP.
-The two panels on the left of Figure \ref{fig:compare_size} show the changes in firm size distributions following the removal of the correlated distortions.
+The two panels on the left of Figure \ref{fig:compare_size} show the changes in firm size distributions following the removal of correlated distortions.
 
@@
 
-The large increase in aggregate output is caused by both an improved allocation of production factors across firms, and a large increase in capital accumulation by about 60\% due to decreased average tax rate from 13\% to 0\%.
+The large increase in aggregate output is caused by both an improved allocation of production factors across firms, and a large increase in capital accumulation of about 60\% due to decrease in average tax rate from 13\% to 0\%.
 The increase in capital accumulation plays a much larger role than improved allocation of factors in the increase in aggregate output.
-Our quantitative exercises in Section IV.B below illustrate this point further.
+Our quantitative exercise in Section IV.B below illustrates this point further.
 The large decline in average pollution intensity is also caused by two factors: the improved allocation of production factors, and increased adoption of the clean technology.
@@
 This reallocation lowers the average pollution intensity.
-Meanwhile, as we discuss in Section III.D, correlated distortions lower the elasticity of firm profits to firm TFP $z$, and therefore reduce their incentives to adopt the clean technology.
+Meanwhile, as we discuss in Section III.D, correlated distortions lower the elasticity of firm profits to firm TFP $z$, and therefore dampen their incentives to adopt the clean technology.
 Removing correlated distortions would do exactly the opposite and encourage the adoption of clean technology.
 
-To evaluate the relative contributions of the improved allocation of factors and improved adoption of clean technologies, we consider a hypothetical economy that is identical to our benchmark economy, except that the clean technology shows no improvement in abatement efficiency over the dirty technology, that is, $\psi_0^{(1)} = \psi_0^{(0)}$ and $\psi_1^{(1)} = \psi_1^{(0)}$.
+To evaluate the relative contributions of the improved allocation of factors and improved adoption of clean technologies, we consider a hypothetical economy that is identical to our benchmark economy, except that the clean technology shows no improvement in abatement efficiency over the dirty technology, that is, $\psi_0^{1} = \psi_0^{0}$ and $\psi_1^{1} = \psi_1^{0}$.
 First, we remove correlated distortions from this hypothetical economy, which reveals the importance of the improved allocation of factors.
 We then re-introduce the differences between clean and dirty technologies to the hypothetical economy, so that the resulting equilibrium is exactly the same as that in Experiment (i).
-This further reveals the importance of the improved adoption of clean technologies.
-We find that the improved adoption of clean technologies account for 48\% of the decrease in average intensity.
+The latter calculation reveals the importance of the improved adoption of clean technologies.
+We find that the improved adoption of clean technology accounts for 48\% of the decrease in average intensity.
 
 Finally, the polluting and non-polluting sectors respond in similar ways to the removal of correlated distortions, and little reallocation is induced across sectors.
-Recall that the distributions of managerial talent and distortions are the same across these two sectors, and the only material difference between these two sectors is the presence of the fixed adoption cost of clean technology $k_E$ and environmental regulations.
+Recall that the distributions of managerial talent and distortions are the same across these two sectors, and the only material difference between these two sectors is the presence of the fixed adoption cost of clean technology $k_E$ and environmental regulations in the polluting sector.
 Since the calibrated value of $k_E$ is not too large, the differences in the reaction of these two sectors to the removal of distortions are rather limited.
 
-One notable difference is that the mean firm size is somewhat larger in the polluting sector, because the environmental regulations work as an additional selection mechanism.
+One notable difference is that the mean firm size is somewhat larger in the polluting sector, because environmental regulations work as an additional selection mechanism.
 The interaction between the correlated distortions and environmental regulations leads to further efficiency losses in the polluting sector, because average firm size and hence the effective distortions increase.
@@
 
-\textit{Tightening Environmental Regulations.}---In Experiment (ii), we increase environmental penalties $\xi$ to the extent that the fraction of firms using the clean technology increases to the same 56\% as in Experiment (i).
+\textit{Tightening Environmental Regulations.}---In Experiment (ii), we increase environmental penalties $\xi$ to the extent that the fraction of firms using the clean technology increases to the same 85\% as in Experiment (i).
 The results are shown in Column (ii) of Table \ref{tab:aggregates}.
@@
 The increase in $\xi$ affects the resource allocation in the polluting sector along both the extensive and intensive margins.
-The most notable changes come along the extensive margin.
+Most notable changes come along the extensive margin.
 In our model as well as in the data, it is the small unproductive firms that choose the dirty technology.
 Therefore, an increase in environmental penalties would mostly fall on small unproductive firms and lower their profits.
-This would drive a substantial fraction of small firms out of the market through the endogenous occupation choices, and lead to a sizable increase in average firm size.
+This would drive a substantial fraction of small firms out of the market through the endogenous occupation choice, and lead to a sizable increase in average firm size.
 Meanwhile, labor supply increases as the managers of these exiting firms now choose to be workers, which suppresses the equilibrium wage.
@@
 
-While small firms account for a large fraction of firms, they account for only a small fraction of production factors, which implies that the total amount of factors affected by the extensive changes is small.
+While small firms account for a large fraction of firms, they account for only a small fraction of production factors, which implies that the total amount of factors affected by the extensive margin is small.
 In addition, the polluting sector only account for 20\% of production factors in the benchmark economy.
@@
 In addition, our calibrated value of the adoption cost of clean technology $k_E$ is not too large.
-Therefore, the impact on surviving firms in the polluting sector is also limited, which can be seen in Table \ref{tab:talentdist}.
+Therefore, the impact on surviving firms in the polluting sector is also limited, which can be seen from Table \ref{tab:talentdist}.
 Despite this, the allocation of factors along the intensive margin worsens, in the sense that the share of factors used by the most productive group decreases, because more distorted productive firms benefit less from the wage decline.
@@
 We repeat the same decomposition exercise as we did in Experiment (i), and find that 94\% and 96\% of the reductions in aggregate pollution and average intensity, respectively, stem from the increased adoption of the clean technology.
-Since the output of the polluting sector only decreases only slightly in this experiment, the decreases in aggregate pollution and intensity are quantitatively similar at around 14\%.
+Since the output of the polluting sector decreases only slightly in this experiment, the decreases in aggregate pollution and intensity are quantitatively similar at around 14\%.
 
@@
 
-\textit{Comparing the Two Experiments.}---Both of the above experiments cause the reallocation of factors across firms, but in different ways.
+\textit{Comparing the Two Experiments.}---Both experiments cause the reallocation of factors across firms, but in different ways.
 Removing the correlated distortions from both sectors improve resource allocation along both the extensive and intensive margins, which push the economy closer to the production possibility frontiers.
@@
 See for example, \citet{Ventura:1999}, \citet{ConesaKrueger:2006}, \citet{Bhattacharyaetal:2013} and \citet{BentoRestuccia:2016}, among others.} Not surprisingly, the implied uniform tax rate $\tau_z =$ 18\% is higher than the average tax rate of 13\% under the progressive tax system.
-Column (i') in Table \ref{tab:uniform} summarizes the results of this experiment and compares them to those from Experiment (i).
+Column (i') in Table \ref{tab:uniform} summarizes the results from this experiment and compares them to those from Experiment (i).
 A comparison of Column Benchmark and Column (i') reveals the effects of a change in progressivity of $\tau_z$, while a comparison of Column (i') and (i) highlights the effects of a uniform change in tax rates across firms.
@@
 
-As we can see from Table \ref{tab:uniform}, removing the progressivity of $\tau_z$ increases aggregate output, capital, consumption and output per worker.
+As we can see from Table \ref{tab:uniform}, removing the progressiveness of $\tau_z$ increases aggregate output, capital, consumption and output per worker.
 However, the 6\% to 11\% increases here are rather moderate compared to the 20\% to 60\% increases when all the distortions are eliminated.
@@
 
-However, removing the progressivity of $\tau_z$ causes a large change in firm size distribution, and therefore large declines in aggregate pollution and pollution intensity.
+However, removing the progressiveness of $\tau_z$ causes a large change in firm size distribution, and therefore large declines in aggregate pollution and pollution intensity.
 In fact, the resulting number of firms and mean firm size are the same between Experiment (i) and (i'), since the only difference between them is a uniform increase in tax rates across firms.
-The average pollution intensity decreases by 35\% when the progressivity of $\tau_z$ is removed, compared to a 42\% decline when all the correlated distortions are eliminated.
+The average pollution intensity decreases by 35\% when the progressiveness of $\tau_z$ is removed, compared to a 42\% decline when all the correlated distortions are eliminated.
 Again, the decline in average pollution intensity is caused by both an improved resource allocation and improved adoption of the clean technology among firms.
-However, the second channel is not as strong as in Experiment (i) (16 versus 28 percentage points), since the increase in the slope of the firm's profit functions is not as large as in Experiment (i).
+However, the second channel is not as strong as in Experiment (i) (16 versus 28 percentage points), since the increases in firm's profit are not as large as in Experiment (i).
 Moreover, since the output of the polluting sector only increases by 8\% in this experiment compared to 30\% in Experiment (i), the 30\% decline in aggregate pollution here is larger than the 23\% in Experiment (i).
 
-In sum, our findings imply that it is the progressivity of firm-level distortions, rather than the average level of distortions, that plays a dominate role in amplifying aggregate pollution and pollution intensity.
+In sum, our findings imply that it is the progressiveness of firm-level distortions, rather than the average level of distortions, that plays a dominate role in amplifying aggregate pollution and pollution intensity.
 
@@
 Distortions that increase with firm TFP reallocate production factors away from large productive firms, therefore reduce aggregate output while increasing aggregate pollution intensity.
-We support our theory by firm-level data on production, emissions, and pollution treatment technologies from China.
+We support our theory by firm-level data on production, emissions and pollution treatment technologies from China.
 Quantitatively, we find that distortions correlated with firm TFP reduce aggregate output by about 30\% and increase aggregate pollution by about 20\%.
@@
 Our findings also challenge a popular view that economic growth necessarily comes at the cost of more pollution in developing countries.
-They suggest that a growth path with both higher output and lower pollution is attainable, if policy and institutional distortions can be removed in a cost effective way.
-
-The analytical framework in this paper can be extended to other pollutants, sectors, and countries.
-For other pollutants, China also has a severe air pollution problem, and casual observations reveal that small and medium-sized firms in high-polluting industries such as steel contribute disproportionately to air pollution in China.
-For other sectors, \citet{AGpaper} find that misallocation caused by migration and land policies is an important cause of agricultural pollution in China.
+They suggest that a growth path with both higher output and lower pollution is attainable, if policy and institutional distortions can be removed in a cost-effective way.
+
+The analytical framework in this paper can be extended to other pollutants, sectors and countries.
+For other pollutants, China also has a severe air pollution problem, and casual observations reveal that small and medium-sized firms in high-polluting industries such as steel contribute disproportionately to air pollution in China as well.
+For other sectors, \citet{AGpaper} find that misallocation caused by migration and land policies is an important driver of agricultural pollution in China.
 For other countries, \citet{HsiehKlenow:2014} and \citet{BentoRestuccia:2016} find evidence of distortions that are highly correlated with firm TFP in a number of developing countries, while \citet{Dasguptaetal:1998} find that small firms have higher air pollution intensity in Brazil and Mexico.

### 2019-09-23 Documentation/Response_to_AEJ_Editor.tex
final submission

@@
 It is clear that the paper used a different dataset, which has a panel structure.
-However, since the authors did not provide enough details on the original source of the environmental dataset they used---possibly due to the lack of an official English translation for the name of the dataset---we had a really hard time identifying the exact dataset.
+However, we were not able to trace the exact source of the dataset based on the information in the paper.
+The dataset does not seem to have an official English translation for its name.
+Hence we had a hard time trying to pin down the source by its name.
 Our educated guess is that they were using the firm-level data from \textit{Annual Statistic Report on Environment in China} (in Chinese \begin{CJK}{GBK}{kai}中国环境统计年报\end{CJK}), but we cannot be 100\% sure.

### 2019-09-23 Documentation/Response_to_AEJ_Editor.tex
final submission

@@
 Hence we had a hard time trying to pin down the source by its name.
-Our educated guess is that they were using the firm-level data from \textit{Annual Statistic Report on Environment in China} (in Chinese \begin{CJK}{GBK}{kai}中国环境统计年报\end{CJK}), but we cannot be 100\% sure.
+Our educated guess is that they were using the firm-level data from the \textit{Annual Statistic Report on Environment in China} (in Chinese \begin{CJK}{GBK}{kai}中国环境统计年报\end{CJK}), but we cannot be 100\% sure.
 
@@
 Indeed, this exercise is inspired by the referee's comments.
-We considered this suggestion very carefully; however, we decided to leave these results in Appendix J as they are for the following reasons.
+We considered this suggestion very carefully; however, we decided to leave these results in Appendix J as they are now for the following reasons.
 First, the firm-level data suggest that there are severe correlated distortions in both the polluting and non-polluting sectors.
-Therefore, we think it is more natural to consider removing distortions from both sectors.
+Therefore, we think that it is more natural to consider removing distortions from both sectors.
 Second, when we remove the correlated distortions from the polluting sector only, the results depend critically on the elasticity of substitution between the two sectors $\rho$.

### 2019-09-23 Documentation/Replication_Instruction.tex
final submission

@@
   \and
-  \normalsize{{Xin Tang}}\footnote{Corresponding Author: zjutangxin@gmail.com} \\
+  \normalsize{{Xin Tang}}\footnote{Please send all correspondence to: zjutangxin@gmail.com} \\
   \normalsize{{Wuhan University}} \\
@@
 The code then repeats the exercise for the manufacturing sector as a whole.
-Results of the un-numbered regressions on Pages 9 and 10 (the last one) are then printed to the terminal, with Figure C.2 exported to \bcode{./Empirical/Results/FigureC2.pdf}.
+Results of the un-numbered regressions on Pages 7, 9 and 10 (the last one) are then printed to the terminal, with Figure C.2 exported to \bcode{./Empirical/Results/FigureC2.pdf}.
 

### 2019-09-23 Empirical/Empirical_Appendix.R

@@ -346,7 +346,7 @@ sel <- which(POLLUTEALL$product > 0 & POLLUTEALL$product < qup
              & POLLUTEALL$product > qdown)
 POLLUTEALL <- POLLUTEALL[sel]
 
-# ================== Regression (!#) Page 9 Upper ==========================
+# ================== Regression (!#) Page 7 ================================
 CODR <- POLLUTEALL[cod_e > 0]
 lm_all <- lm(log(cod_e)~log(product)+industry_a+province+type_a,
              data=CODR)
@@ -369,7 +369,7 @@ codr_residual <- lm(res_intensity ~ res_product, data = CODR)
 abline(codr_residual,col="red",lwd=4)
 dev.off()
 
-# ================== Regression (!#) Page 9 Lower ==========================
+# ================== Regression (!#) Page 9 ================================
 CODR$clean <- 0
 sel <- which(CODR$dm1_code_a == 4 | CODR$dm1_code_a == 5)
 CODR$clean[sel] <- 1

### 2019-09-24 Quantitative/misc.m
bug fix

@@ -40,12 +40,11 @@ disp('The Role of Technology')
 disp(1-(1-prodredi)/(1-totredi))
 
 % Plot the tax function
-clear all;
+clear ;
 load('./Results/benchmark_new.mat');
 figure(1)
-plot(log(zgrid(indzhatc:end)),tauzc(indzhatc:end),...
-    'LineWidth',2);
+plot(log(zgrid(indzhatc:end)),tauzc(indzhatc:end),'LineWidth',2);
 title('The Generic Tax Function');
-xlabel('Log Productivity')
-ylim([0.04 0.28])
+xlabel('Log Productivity');
+ylim([0.04 0.28]);
 saveas(gcf,'./Results/FigureD2.eps','epsc');

### 2019-09-24 Quantitative/tax_figure.m

@@ -1,0 +1,9 @@
+clear all;
+load('testplot.mat');
+figure(1)
+plot(log(zgrid(indzhatc:end)),tauzc(indzhatc:end),...
+    'LineWidth',2);
+title('The Generic Tax Function');
+xlabel('Log Productivity');
+ylim([0.04 0.28]);
+saveas(gcf,'./Results/FigureD2.eps','epsc');

### 2019-09-27 Documentation/IMF_RES_Fall_2019.tex
slides

\documentclass[10pt]{beamer}
\usepackage{amsmath,upgreek}
%\usepackage{amsthm}
\usepackage{booktabs,threeparttable}
%\usepackage[capposition=top]{floatrow} % For Figure Notes
\usepackage{mathpazo}
\usepackage{hyperref}
\usepackage{multimedia}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{pause}

%\renewcommand{\rmdefault}{ppl}
\usepackage[scaled=0.88]{helvet}
\makeatletter   % Roman Numbers
\newcommand*{\rom}[1]{\expandafter\@slowromancap\romannumeral #1@}
\makeatother
%\setcounter{MaxMatrixCols}{10}
%TCIDATA{OutputFilter=LATEX.DLL}
%TCIDATA{Version=5.50.0.2890}
%TCIDATA{<META NAME="SaveForMode" CONTENT="1">}
%TCIDATA{BibliographyScheme=Manual}
%TCIDATA{Created=Sunday, May 18, 2008 16:47:28}
%TCIDATA{LastRevised=Tuesday, November 18, 2008 20:57:42}
%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
%TCIDATA{<META NAME="DocumentShell" CONTENT="Other Documents\SW\Slides - Beamer">}
%TCIDATA{CSTFile=beamer.cst}

\newcommand{\E}{\mathbb{E}}
\newcommand{\e}{\mathrm{e}}
\newcommand{\I}{\mathbb{I}}
\DeclareMathOperator*{\argmax}{argmax}
\DeclareMathOperator*{\plim}{plim}
\renewcommand{\vec}[1]{\ensuremath{\mathbf{#1}}}
\newcommand{\gvec}[1]{{\boldsymbol{#1}}}
\renewcommand{\qedsymbol}{$\blacksquare$}
\newenvironment{stepenumerate}{\begin{enumerate}[<+->]}{\end{enumerate}}
\newenvironment{stepitemize}{\begin{itemize}[<+->]}{\end{itemize} }
\newenvironment{stepenumeratewithalert}{\begin{enumerate}[<+-| alert@+>]}{\end{enumerate}}
\newenvironment{stepitemizewithalert}{\begin{itemize}[<+-| alert@+>]}{\end{itemize} }
\newtheorem{proposition}{Proposition}[section]
\newcommand{\bcode}[1]{\texttt{{\color{blue}{#1}}}}
\newcommand{\rcode}[1]{\texttt{{\color{red}{#1}}}}
\newcommand{\rtext}[1]{{\color{red}{#1}}}
\newcommand{\btext}[1]{{\color{blue}{#1}}}
\newcommand{\code}{\texttt}
\definecolor{purpledef}{RGB}{51,51,178}

\setbeamertemplate{caption}[numbered]
%\usefonttheme{serif}
%\usetheme{Madrid}
%\usetheme{Warsaw}
%\usetheme{JuanLesPins}
%\usetheme{Berlin}
%\usetheme{Boadilla}
%\usetheme{default}

\makeatletter
\setbeamertemplate{footline}
{
  \leavevmode%
  \hbox{%
  \begin{beamercolorbox}[wd=.333333\paperwidth,ht=2.25ex,dp=1ex,center]{author in head/foot}%
    \usebeamerfont{author in head/foot}\insertshortauthor
  \end{beamercolorbox}%
  \begin{beamercolorbox}[wd=.333333\paperwidth,ht=2.25ex,dp=1ex,center]{title in head/foot}%
    \usebeamerfont{title in head/foot}\insertshorttitle
  \end{beamercolorbox}%
  \begin{beamercolorbox}[wd=.333333\paperwidth,ht=2.25ex,dp=1ex,right]{date in head/foot}%
    \usebeamerfont{date in head/foot}\insertshortdate{}\hspace*{2em}
    \insertframenumber{} / \inserttotalframenumber\hspace*{2ex}
  \end{beamercolorbox}}%
  \vskip0pt%
}
\makeatother

\title[Firm Size and Industrial Pollution]{\large The Size Distribution of Firms and Industrial Water Pollution \\ A Quantitative Analysis of China}
\author[Qi, Tang and Xi]{{Ji Qi} \inst{\star} \and {Xin Tang} \inst{\dagger} \and {Xican Xi} \inst{\ddagger}}
\institute[MEP \& IMF \& FDU]{
    \inst{\star} {Chinese Academy for Environmental Planning} \and
    \inst{\dagger} {International Monetary Fund} \and
    \inst{\ddagger} {Fudan University}}
\date[IMF (RES) Fall 2019]{\footnotesize{\today} \\ \scriptsize{The views expressed here are those of the authors and do not necessarily reflect the views of the CAEP and the IMF.}}

\begin{document}

\frame{\titlepage}

\section{Introduction}

\begin{frame}
\frametitle{Motivation}
\begin{itemize}
\itemsep=0.15in
    \item
    Rapid economic growth in China is paired with severe environmental consequences.
    \begin{itemize}
        \item
        Is pollution an inevitable consequence of growth or exacerbated by policy distortions and/or market inefficiencies?
    \end{itemize}
    \item
    We argue that misallocation across firms reduces output and amplifies industrial pollution by distorting the firm size distribution.
    \item
    \textit{\color{blue}Policy Implications}:
    \begin{itemize}
        \item
        Reducing the distortions firms face increases output while reducing pollution.
        \item
        Environmental regulations could amplify existing market distortions.
    \end{itemize}
    \item
    We believe that the findings of our paper could be generalized to
    \begin{itemize}
        \item air and solid waste pollution;
        \item the agricultural sector;
        \item other developing countries.
    \end{itemize}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Intuition}
\begin{itemize}
\itemsep=0.15in
    \item
    \textit{\color{blue}Hypothesis}: Distortions $\rightarrow$ Size Distribution $\rightarrow$ Industrial Pollution.
    \begin{itemize}
    \itemsep=0.10in
        \item
        Larger firms have lower pollution intensity because they use cleaner production and treatment technologies.
        \item
        Distortions limit the expansion of productive firms in China.
        \item
        Compared to an economy with fewer distortions (e.g., the U.S.), less productive firms with higher pollution intensity are active.
        \item
        As a result, aggregate output is lower, but industrial pollution is higher.
    \end{itemize}
    \item
    Technique effect dominates scale effect.
    \item
    \textit{\color{blue}Significance}: Growth and environmental protection are not necessarily a trade-off.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Overview of Results}
\begin{itemize}
\itemsep=0.15in
    \item
    Empirical Evidence:
    \begin{itemize}
        \item
        Large firms have lower pollution intensity.
        \item
        Correlated distortions limit the expansion of large firms.
    \end{itemize}
    \item
    Model:
    \begin{itemize}
        \item
        Two sectors (polluting and non-polluting);
        \item
        Firms heterogeneous in productivity, pollution intensity and correlated distortions;
        \item
        Endogenous treatment technology choice with imperfect regulations.
    \end{itemize}
    \item
    Qualitative Results:
    \begin{itemize}
        \item
        Correlated distortions discourage technology adoption.
        \item
        When would technique effect dominates scale effect.
    \end{itemize}
    \item
    Quantitative Exercises:
        \begin{itemize}
        \item
        Removing distortions: $Y \uparrow $ 30\%, $E \downarrow $ 20\%.
        \item
        Strengthening regulations: $Y = $, $E \downarrow $ 15\%.
        \end{itemize}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Related Literature}
\begin{itemize}
\itemsep=0.15in
    \item
    Misallocation:
    \begin{itemize}
        \item
        Restuccia and Rogerson (2008), Guner et al. (2008), Hsieh and Klenow (2009).
        \item
        We consider both the output and pollution.
    \end{itemize}
    \item
    Economic Growth and Environment:
    \begin{itemize}
        \item
        Grossman and Krueger (1993, 1995), Copeland and Taylor (2004), Levinson (2009).
        \item
        Cherniwchan et al. (2017), Shapiro and Walker (2018).
        \item
        We focus on a theoretical interpretation behind the scale and technique effects.
    \end{itemize}
    \item
    Technology Adoption in Developing Countries:
    \begin{itemize}
        \item
        Parente and Prescott (1994, 1999), Bustos (2011), Acemoglu et al. (2012).
        \item
        We study the role of size and misallocation.
    \end{itemize}
    \item
    {\color{black}Industrial Pollution in China}£º
    \begin{itemize}
        \item
        Jiang et al. (2014), Kahn et al. (2015), Cai et al. (2016), Jia (2017).
        \item
        We emphasize the role of distortions and size distribution.
    \end{itemize}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Outline}
\begin{itemize}
\itemsep=0.15in
    \item
    Empirical Evidence:
    \begin{itemize}
        \item Data
        \item Fact: Pollution Intensity
        \item Fact: Employment Distribution
    \end{itemize}
    \item
    The Model:
    \begin{itemize}
        \item Measuring Distortions
        \item Analytical Properties
    \end{itemize}
    \item
    Quantitative Results:
    \begin{itemize}
        \item Removing Distortions
        \item Tightening Regulations
    \end{itemize}
\end{itemize}
\end{frame}

\section{Empirical Evidence}

\begin{frame}
\begin{center}
\LARGE{1. Empirical Evidence}
\end{center}
\end{frame}

\subsection{Data Sources}

\begin{frame}
\frametitle{Data}
\framesubtitle{Data Sources}
\begin{itemize}
\itemsep=0.15in
    \item
    National General Survey of Pollution Sources (2007)
    \begin{itemize}
    \item
    Firm sales, emission, and treatment equipment.
    \end{itemize}
    \item
    China National Economic Census (2004)
    \begin{itemize}
    \item
    Firm sales, employment, labor compensation, and capital stock.
    \end{itemize}
    \item
    Statistics of U.S. Business (2004)
    \begin{itemize}
    \item
    Firm size distribution in the U.S.
    \end{itemize}
\end{itemize}
\end{frame}

\begin{frame}[label=datasource]
\frametitle{Data}
\framesubtitle{Measurement}
\begin{itemize}
\itemsep=0.15in
    \item
    We use Chemical Oxygen Demand (COD) as the main measure.
    \begin{itemize}
    \itemsep=0.10in
    \item More than 70\% of firms in our sample have positive COD emissions.
    \item COD emission is highly correlated with those of other pollutants.
    \item In the Paper industry, $\text{corr}(\text{NH}_4^+,\text{COD}) = 0.82$, and $\text{corr}(\text{BOD},\text{COD}) = 0.94$.
    \end{itemize}
    \item
    We focus on the 5 most polluting industries.
    \begin{itemize}
    \item They account for 77\% of total COD emission in China.
    \end{itemize}
    \item
    We focus on the key sources.
    \begin{itemize}
        \item For the polluting industries, they account for 90\% of the emissions, and 80\% of the production.
    \end{itemize}
\end{itemize}
\hyperlink{coddef}{\beamergotobutton{COD Definition}}
\hyperlink{pollutants}{\beamergotobutton{Pollutants}}
\end{frame}

\begin{frame}[label=codquartile]
\frametitle{Firm Size and Pollution Intensity}
\framesubtitle{Scatter Plots}
\begin{itemize}
\itemsep=0.15in
    \item
    Emission intensity = emission/sales.
\end{itemize}
\begin{figure}[htb]
\begin{center}
    \includegraphics[width=0.45\textwidth]{./Figures/paper_ez.pdf}
    \includegraphics[width=0.45\textwidth]{./Figures/pooled_intensity_size.pdf}
\end{center}
\end{figure}
\hyperlink{codscatter}{\beamergotobutton{Scatter by Industries}}
\end{frame}

\begin{frame}[label=codreg]
\frametitle{Firm Size and Pollution Intensity}
\framesubtitle{Regression Results}
\begin{itemize}
\itemsep=0.15in
    \item
    Regression Specification:
    \begin{align*}
        \log (\text{COD}_i) = &\underset{(0.17)}{-3.75} + \underset{(0.01)}{0.63} \times \log (\text{Output}_i) + \mathbf{X}_i\gvec{\upgamma} + \varepsilon_i, \\
        & N = 29,019, R^2 = 0.41.
    \end{align*}
    \item
    $\mathbf{X}_i$ controls for sectors, provinces, and ownership rights.
    \begin{itemize}
        \item Pollution intensity does \rtext{not} vary systematically with \btext{ownership rights}.
    \end{itemize}
    \item
    As sales rise by 1\%, emission intensity drops by $(1-0.63) = 0.37\%$.
\end{itemize}
\end{frame}

\begin{frame}[label=treatment1]
\frametitle{Treatment Technologies and Firm Size}
\begin{itemize}
\itemsep=0.15in
    \item
    For the Paper industry:
    \begin{itemize}
    \item
    Treatment efficiency ($1 - \text{COD Emitted}/\text{COD Generated}$):
    \end{itemize}
\end{itemize}

\begin{table}[t]
    \small
    \centering
    \begin{threeparttable}
    \begin{tabular}{p{80pt}p{75pt}p{50pt}p{50pt}}
        \hline \hline
        Technology          & Physical          & Chemical      & Biological \\
        \midrule
        Adoption Rate       & 26\%              & 34\%          & 39\%    \\
        Mean Efficiency     & 63\%              & 75\%          & 81\%    \\
        \midrule
        Median Costs        & 100 (Normalized)  & 308           & 923     \\
        Median Sales        & 100 (Normalized)  & 219           & 500     \\
        \bottomrule
    \end{tabular}
    \end{threeparttable}
\end{table}

\begin{itemize}
    \item
    A linear probability model of biological equipment adoption on log-output:
    \begin{equation*}
        y_i = \underset{(0.04)}{0.23} + \underset{(0.001)}{0.05} \times \log (\text{Output}_i) + \mathbf{X}_i\gvec{\upgamma} + \epsilon_i.
    \end{equation*}
\end{itemize}
\hyperlink{treatment2}{\beamergotobutton{Examples}}
\hyperlink{treattech2}{\beamergotobutton{Additional Tech Specs}}
\end{frame}

\begin{frame}[label=producttech]
%\small
\frametitle{Production Technologies and Firm Size}
\framesubtitle{Regression Results}
\begin{itemize}
\itemsep=0.15in
    \item
    Large firms also {\color{black}generate} less pollution conditional on treatment technology.
    \item
    Regression Specifications:
    \begin{align*}
        \text{Physical:}   \quad \log (\text{COD}_i) &= \underset{(0.40)}{-3.50} + \underset{(0.01)}{0.58} \times \log (\text{Sales}_i) + \mathbf{X}_i\gvec{\upgamma} + \epsilon_i, \\
        \text{Chemical:}   \quad \log (\text{COD}_i) &= \underset{(0.49)}{-4.59} + \underset{(0.01)}{0.77} \times \log (\text{Sales}_i) + \mathbf{X}_i\gvec{\upgamma} + \epsilon_i, \\
        \text{Biological:} \quad \log (\text{COD}_i) &= \underset{(0.20)}{-4.37} + \underset{(0.01)}{0.67} \times \log (\text{Sales}_i) + \mathbf{X}_i\gvec{\upgamma} + \epsilon_i.
    \end{align*}
\end{itemize}
%\hyperlink{treattech}{\beamergotobutton{Treatment Technology Choice}}
\end{frame}

\begin{frame}[label=producttech2]
\frametitle{Production Technologies and Firm Size}
\framesubtitle{Possible Interpretations}
\begin{itemize}
\itemsep=0.15in
    \item
    An example from the \textit{Handbook of Emission Coefficients} by the \textit{Chinese Academy of Sciences}:
    \begin{itemize}
    \item Two technologies in paper pulp manufacturing use different inputs: {\color{black}bagasse} and {\color{black}wood}.
    \item {\color{black}Bagasse} is used mostly by firms with annual production of {\color{red}less} than 100 k-tons with COD generation of 140--180 kg per ton.
    \item {\color{black}Wood} is used mostly by firms with annual production {\color{red}more} than 100 k-tons with COD generation of 30--55 kg per ton.
    \end{itemize}
    \item
    It could also be that more productive firms simply use less input (Bloom et al. 2010).
    \item
    We capture such decrease in intensity in a reduced-form way.
\end{itemize}
\end{frame}

\begin{frame}[label=esdistall]
\frametitle{Firm Size Distributions}
\begin{figure}[htb]
\begin{center}
    \includegraphics[width=0.45\textwidth]{./Figures/poolES_R_1.pdf}
    \includegraphics[width=0.45\textwidth]{./Figures/allES_R_1.pdf}
\end{center}
\end{figure}
\hyperlink{esdist}{\beamergotobutton{By Industry}}
\end{frame}

\begin{frame}[label=accounting]
\frametitle{Accounting Exercise}
\begin{itemize}
\itemsep=0.15in
    \item
    {\color{blue}Question:} How will the {\color{black}average pollution intensity} change if the {\color{black}size distribution} is mechanically changed to that in the U.S.?
    \begin{itemize}
    \itemsep=0.10in
        \item
        Production level is fixed.
        \item
        The relation between pollution intensity and firm size in China is used.
        \item
        It captures the \textit{Technique} effect while holding the \textit{Scale} effect constant.
    \end{itemize}
    \item
    {\color{blue}Answer:} Average pollution intensity would drop by 33\%.
\end{itemize}
\hyperlink{accountingrbst}{\beamergotobutton{Robustness}}
\end{frame}

\section{The Model}

\begin{frame}
\begin{center}
\LARGE{2. The Model}
\end{center}
\end{frame}

%\begin{frame}
%\frametitle{Why Are We \textit{Not} Done Yet?}
%The accounting exercise has several limitations:
%\begin{itemize}
%    \item
%    Aggregate output is fixed.
%    \item
%    Firm size distribution is mechanically changed to that in the U.S.
%    \item
%    The firm size and emission intensity relationship is taken as invariant.
%\end{itemize}
%\end{frame}

\begin{frame}
%\frametitle{We Need a Model}
\frametitle{Why Are We \textit{Not} Done Yet?}
\begin{itemize}
\itemsep=0.15in
    \item
    The accounting exercise has several limitations:
    \begin{itemize}
    \itemsep=0.10in
        \item
        Only the polluting sector is considered.
        \item
        Aggregate output is fixed.
        \item
        Firm size distribution is mechanically changed to that in the U.S.
        \item
        The firm size and pollution intensity relationship is taken as invariant.
    \end{itemize}
    %\pause
    \item
    To better evaluate the environmental consequences of distortions to firm size, we need a model:
    \begin{itemize}
    \itemsep=0.10in
        \item
        features two sectors;
        \item
        where distortions affect both aggregate output and pollution;
        \item
        which reveals why firm size is distorted and how it will be changed;
        \item
        and which features treatment technology choice.
    \end{itemize}
\end{itemize}
\end{frame}

\subsection{Setup}
\begin{frame}
\frametitle{Overview of the Model}
\begin{itemize}
\itemsep=0.15in
    \item
    A two-sector model with perfect substitution between products.
    \item
    Each sector features a Lucas (1978) span-of-control model.
    \item
    Firms differ in productivity and pollution intensity.
    \item
    Firms can use treatment equipment to reduce emissions.
    \begin{itemize}
    \item The cost of treatment equipment is independent of firm size.
    \item There are penalties for not using clean technology.
    \end{itemize}
    \item
    Correlated distortions that increase with firm size (Restuccia and Rogerson, 2008).
    \begin{itemize}
    \item Domestic local protectionism, size-dependent tax treatments, etc.
    \end{itemize}
    \item
    {\color{black}Steady state} analysis.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Household}
\begin{itemize}
\itemsep=0.15in
    \item
    A representative household with a continuum of members:
    \begin{equation*}
        \sum_{t=0}^{\infty} \beta^t U(C_t).
    \end{equation*}
    \item
    Each member is endowed with $z$ units of \btext{sector-specific} managerial talent.
    \begin{itemize}
        \item The CDFs are $G^c(z)$ and $G^d(z)$ with a common support $Z \triangleq [0,\overline{z}]$;
        \item $z$ is fixed once drawn.
        \item A fraction $\mu$ of members possess talent in the \btext{polluting} sector.
    \end{itemize}
    \item
    Members can only become entrepreneurs in their designated sector, but are free to enter both sectors as worker.
    \item
    The household owns all firms and capital in the economy.
\end{itemize}
\end{frame}

\begin{frame}[label=firmset]
\frametitle{Firms}
\framesubtitle{Non-polluting Sector}
\begin{itemize}
\itemsep=0.15in
    \item
    The production function is the same in both sectors:
    \begin{equation*}
        y = F(z,k,l) = z^{1-\gamma}(k^{\alpha}l^{1-\alpha})^{\gamma},
    \end{equation*}
    where $0<\gamma<1$ is the span-of-control parameter.
    \item
    Firms in the non-polluting sector do not discharge pollutants and are not subject to environmental regulations.
\end{itemize}
\end{frame}

\begin{frame}[label=treattech]
\frametitle{Firms}
\framesubtitle{Polluting Sector: Clean Technology and Regulations}
\begin{itemize}
\itemsep=0.15in
    \item
    Treatment Technologies:
    \begin{itemize}
    \itemsep=0.10in
        \item
        Emissions $e$ are by-product of production:
        \begin{equation*}
            \log \left(\frac{e}{y}\right) = \psi_0^j + \psi_1^j \log y, \quad j = 0,1,
        \end{equation*}
        where $j=1$ indicates clean technology and $\psi_1^j < 0$.
        \item
        Clean technology requires fixed installation costs $k_E$.
    \end{itemize}
    %\pause
    \item
    Regulations:
    \begin{itemize}
    \itemsep=0.10in
        \item
        If a firm using dirty technology is inspected, a fraction $\xi$ of its total profits $\pi(z)$ is confiscated.
    \end{itemize}
        %\pause
    \begin{itemize}
        \item Confiscated profits are rebated back to household as {\color{black}lump-sum} transfers.
    \end{itemize}
\end{itemize}
%\hyperlink{producttech}{\beamergotobutton{Evidence on $\psi_1^{i}$}}
\end{frame}

\begin{frame}[label=firmset]
\frametitle{Which Distortion Matters?}
\framesubtitle{Identification Assumption}
\begin{itemize}
\itemsep=0.15in
    \item
    We use the variations in average factor products to measure these wedges (Hsieh and Klenow, 2009).
    \item
    Let {\color{blue}$\tau_{z_i}, \tau_{k_i}$} and {\color{blue}$\tau_{l_i}$} be the wedges firm $i$ faces on the product, capital and labor market, the problem of firm $i$ is
    \begin{equation*}
      \pi_i = \max_{k_i,l_i} \left\{ (1-\tau_{z_i}) z_i^{1-\gamma} (k_i^{\alpha} l_i^{1-\alpha})^{\gamma} - (1+\tau_{k_i})Rk_i - (1+\tau_{l_i})W l_i \right\}.
    \end{equation*}
    \item
    Assuming $\tau_{l_i} = 0$:
    \begin{align*}
        \frac{y_i}{l_i} &= \frac{W}{(1-\alpha) \gamma (1-\tau_{z_i})} \varpropto \frac{1}{1-\tau_{z_i}}, \\
        \frac{k_i}{l_i} &= \frac{\alpha}{1-\alpha} \cdot \frac{W}{(1+\tau_{k_i})R} \varpropto \frac{1}{1+\tau_{k_i}}.
    \end{align*}
\end{itemize}
\end{frame}

\begin{frame}[label=arp]
\frametitle{Which Distortion Matters?}
\framesubtitle{Data}
\begin{itemize}
    \item
    Using the China National Economic Census, we find:
    \makebox[\linewidth]{
    \includegraphics[width=0.33\paperwidth,height=0.4\paperheight]{D:/PaperDrafts/Pollution/R_Implementation/arpl_1.pdf}
    \includegraphics[width=0.33\paperwidth,height=0.4\paperheight]{D:/PaperDrafts/Pollution/R_Implementation/klratio_1.pdf}}
    \item
    The firm's problem becomes:
    \begin{equation*}
      \pi_i = \max_{k_i,l_i} \left\{ (1-\tau_{z_i}) z_i^{1-\gamma} (k_i^{\alpha} l_i^{1-\alpha})^{\gamma} - Rk_i - W l_i \right\}.
    \end{equation*}
    \item
    Tax revenues from $\tau_z$ is rebated to household as lump-sum transfers.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Correlated Distortions}
\framesubtitle{Polluting and Non-polluting Sectors}
\begin{figure}[htb]
\begin{center}
    \includegraphics[width=0.40\textwidth]{./Figures/apf_pol_weight.pdf}
    \includegraphics[width=0.40\textwidth]{./Figures/apf_npol_weight.pdf}
\end{center}
\end{figure}
\begin{itemize}
    \item
    Assume the correlated distortions are the same in both sectors:
    \begin{equation*}
        \tau_z = \max \left\{0,1-\phi_0 z^{\phi_1} \right\},
    \end{equation*}
    where $\tau_z$ is progressive when $\phi_1 < 0$.
\end{itemize}
\end{frame}

\begin{frame}[label=gedef]
\frametitle{Stationary Equilibrium}
\begin{itemize}
\itemsep=0.15in
    \item
    In the equilibrium, there are three thresholds:
    \begin{itemize}
        \itemsep=0.10in
        \item individuals choose to be manager iff $z > z_c (z_d)$ in each sector,
        \item firms in the polluting sector install clean technology iff $z > z_E$.
    \end{itemize}
    \item
    In the equilibrium,
    \begin{itemize}
        \itemsep=0.10in
        \item Household and firms optimize.
        \item Labor, capital and product markets clear.
        \item Aggregate emission:
        \begin{equation*}
            E = \mu\left[ \underbrace{\int_{z_d}^{{z}_E} e_0(y_z) dG(z)}_{\text{Dirty}} + \underbrace{\int_{{z}_E}^{\overline{z}} e_1(y_z) dG(z)}_{\text{Clean}} \right].
        \end{equation*}
    \end{itemize}
\end{itemize}
\hyperlink{firm_opt1}{\beamergotobutton{Optimization}}
\end{frame}

\begin{frame}[label=prop1]
\frametitle{Correlated Distortions and Technology Adoption}
\begin{figure}[htb]
\begin{center}
    \includegraphics[width=0.60\textwidth]{./Figures/prod_tax_effect.pdf}
\end{center}
\end{figure}
\hyperlink{firm_opt2}{\beamergotobutton{Algebra}}
\end{frame}

\begin{frame}
\frametitle{Correlated Distortions and Aggregate Pollution}
\begin{itemize}
\itemsep=0.15in
    \item
    Consider a simplified one-sector model with no occupational and technology adoption choice.
    \item
    There exists a threshold
    \begin{equation*}
        \hat{\phi}_1 = \frac{\psi_1 (1-\gamma)}{1-\gamma(1+\psi_1)},
    \end{equation*}
    such that $E$ is decreasing in $|\phi_1|$ when $|\phi_1| < |\hat{\phi}_1|$.
    \item
    \btext{Intuition:}
    \begin{itemize}
        \item Technique effect dominates when the progressivity of the distortions is low.
        \item $|\hat{\phi}_1|$ is increasing in $|\psi_1|$.
    \end{itemize}
\end{itemize}
\end{frame}

\section{Quantitative Analysis}

\begin{frame}
\begin{center}
\LARGE{3. Quantitative Analysis}
\end{center}
\end{frame}

\begin{frame}
\frametitle{Calibration}
\framesubtitle{Calibration Strategy}
\begin{itemize}
\itemsep=0.15in
    \item
    \textit{\color{blue}Our Objective}: how firm size distribution affects aggregate pollution.
    \item
    Crucial to match the Chinese economy on:
    \begin{itemize}
        \item
        firm size distribution;
        \item
        relative distortions faced by large versus small firms;
        \item
        pollution intensity of differently sized firms.
    \end{itemize}
    \item
    $\tau_z$ and $G(z)$ jointly determine the firm size distribution.
    \item
    \textit{\color{blue}Identification}: Let $\theta_l = y/l$, then
    \begin{align*}
        \left(\frac{z_i}{z_j} \right)^{\phi_1} &= \frac{\theta_{l,j}}{\theta_{l,i}}, \\
        l^{1-\gamma} &= \Phi(1-\tau_z)z^{1-\gamma}.
    \end{align*}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Calibration}
\framesubtitle{Parameterizations: Exogenously Calibrated}
\begin{table}[t]
\footnotesize
\centering
\begin{threeparttable}
\begin{tabular}{p{55pt}p{30pt}p{45pt}p{130pt}}
    \hline \hline
    Parameter   &                   & Value         & Target                                   \\
    \midrule
    Production  & $\delta$          & 0.1000        & Depreciation Rate                         \\
                & $\alpha$          & 0.5376        & Capital Share 0.5                         \\
                & $\mu$             & 0.20          & Fraction of firms in the polluting sector \\
    \midrule
    Treatment   & $\psi_0^{0}$      & $-$3.4144     & Physical Intensity-output Elasticity      \\
                & $\psi_1^{0}$      & $-$0.3636     & \\
                & $\psi_0^{1}$      & $-$4.3748     & Biological Intensity-output Elasticity    \\
                & $\psi_1^{1}$      & $-$0.3288     & \\
    \bottomrule
\end{tabular}
\end{threeparttable}
\end{table}
\end{frame}

\begin{frame}
\frametitle{Calibration}
\framesubtitle{Parameterizations: Endogenously Calibrated}
\begin{table}[t]
\footnotesize
\centering
\begin{threeparttable}
\begin{tabular}{p{55pt}p{30pt}p{45pt}p{135pt}}
    \hline \hline
    Parameter       &                   & Value         & Target                                   \\
    \midrule
    Treatment       & $k_E$             & 4.60          & Clean Firms: Fixed Cost/Output Ratio 2.5\%        \\
                    & $\xi$             & 0.23          & Clean Technology Adoption Rate 57\%            \\
    \midrule
    Preference      & $\beta$           & 0.8750        & Capital-output Ratio 1.65                 \\
    \midrule
    Distortions     & $\phi_0$          & 1.15          & Average Value Added Tax 13\%                   \\
                    & $\phi_1$          & $-$0.03       & $\theta_l$--$z$ Elasticity           \\
    \midrule
    Production      & $\gamma$          & 0.9300        & Size Distributions        \\
    \midrule
    Productivity    & $\mu$             & $-$2.4567     & Size Distributions        \\
                    & $\sigma$          & 4.0020        & \\
                    & $z'_{max}$        & 24855         & \\
                    & $g_{max}$         & 0.00048       & \\
    \bottomrule
\end{tabular}
\end{threeparttable}
\end{table}
\end{frame}

\begin{frame}[label=fitness]
\frametitle{Model Fit}
\begin{itemize}
    \item Size and Employment Distributions:
\end{itemize}
\begin{figure}[htb]
\begin{center}
    \includegraphics[width=0.45\textwidth]{./Figures/benchfit_fs.eps}
    \includegraphics[width=0.45\textwidth]{./Figures/benchfit_es.eps}
\end{center}
\end{figure}
\end{frame}

\begin{frame}
\frametitle{Two Experiments}
\framesubtitle{Results}
\begin{itemize}
    \item
    Two Exercises:
    \begin{enumerate}[(i)]
        \item Removing all distortions.
        \item Increase regulation $\xi$ such that the fraction of firms using clean technology is the same 85\% as in (i).
    \end{enumerate}
    \item
    None of the exercises has large compositional effect, hence we focus on the polluting sector.
\end{itemize}
\begin{table}[t]
\footnotesize
\centering
\begin{threeparttable}
\begin{tabular}{p{85pt}p{45pt}p{45pt}p{35pt}}
    \hline \hline
    Statistic                       & Benchmark            & (i)                  & (ii)   \\
    \midrule
    Aggregate Output                & 100.0                & 131.2                & 99.0   \\
    Capital                         & 100.0                & 163.1                & 99.0   \\
    \midrule
    Number of Firms                 & 100.0                & 44.1                 & 89.9   \\
    Mean Size                       & 60                   & 139                  & 66     \\
    \midrule
    Aggregate Pollution             & 100.0                & 76.7                 & 85.8   \\
    Average Intensity               & 100.0                & 58.5                 & 86.7   \\
    Clean Share                     & 57.8                 & 85.6                 & 85.1   \\
    \bottomrule
\end{tabular}
\end{threeparttable}
\end{table}
\end{frame}

\begin{frame}
\frametitle{Mechanism}
\framesubtitle{No Distortions}
\begin{figure}[htb]
\begin{center}
  \includegraphics[width=0.45\textwidth]{./Figures/bench_notax_fs.eps}
  \includegraphics[width=0.45\textwidth]{./Figures/bench_notax_es.eps}
\end{center}
\end{figure}
\end{frame}

\begin{frame}
\frametitle{Mechanism}
\framesubtitle{Stronger Regulations}
\begin{figure}[htb]
\begin{center}
  \includegraphics[width=0.45\textwidth]{./Figures/bench_reg_fs.eps}
  \includegraphics[width=0.45\textwidth]{./Figures/bench_reg_es.eps}
\end{center}
\end{figure}
\end{frame}

\begin{frame}[label=geresults]
%\small
\frametitle{Mechanism}
\framesubtitle{Misallocation}
\begin{itemize}
\itemsep=0.15in
    \item
    {\color{black}Extensive} and {{\color{black}Intensive}} Margin:
    \begin{itemize}
    \item {\color{black}Extensive margin}: selection of more productive firms.
    \item {\color{black}Intensive margin}: production distribution among active firms.
    \end{itemize}
    \begin{table}[t]
    \footnotesize
    \centering
    \begin{threeparttable}
    \begin{tabular}{p{45pt}p{25pt}p{25pt}p{25pt}p{25pt}p{25pt}}
        \hline \hline
        Economy     & $\text{QU}_1$ & $\text{QU}_2$ & $\text{QU}_3$ & $\text{QU}_4$ & $\text{QU}_5$ \\
        \midrule
        Benchmark   & 2.79          & 4.26          & 7.45          & 16.81         & 68.70 \\
        Case (i)    & 1.53          & 2.89          & 6.46          & 18.25         & 70.87 \\
        Case (ii)   & 3.02          & 4.63          & 8.01          & 17.79         & 66.55 \\
        \bottomrule
    \end{tabular}
    \end{threeparttable}
    \end{table}
    \item
    Regulations {\color{red}worsen} resource allocation on the intensive margin by amplifying the effects of distortions.
    \item
    Core mechanics:
    \begin{itemize}
        \item
        General equilibrium feedback through wages.
        \item
        The interaction between selection and correlated distortions.
    \end{itemize}
\end{itemize}
\hyperlink{peresults}{\beamergotobutton{Monopolistic Competition}}
\end{frame}

\begin{frame}[label=sizedepen]
\frametitle{Mechanism}
\framesubtitle{The Progressiveness in Distortions}
\begin{itemize}
    \item Experiment (i') imposes a uniform distortion to all the firms that collects the same amount of tax revenue.
\end{itemize}
\begin{table}[t]
\footnotesize
\centering
\begin{threeparttable}
\begin{tabular}{p{85pt}p{45pt}p{45pt}p{25pt}}
    \hline \hline
    Statistic                & Benchmark            & (i')            & (i)   \\
    \midrule
    Aggregate Output         & 100.0                & 108.2           & 131.2  \\
    Capital                  & 100.0                & 110.9           & 163.1  \\
    \midrule
    Number of Firms          & 100.0                & 44.1            & 44.1   \\
    Mean Size                & 60                   & 139             & 139    \\
    \midrule
    Aggregate Pollution      & 100.0                & 70.0            & 76.7   \\
    Average Intensity        & 100.0                & 64.8            & 58.5   \\
    Clean Share              & 57.4                 & 73.3            & 85.6   \\
    \bottomrule
\end{tabular}
\end{threeparttable}
\end{table}
\begin{itemize}
    \item
    The progressiveness of the distortions is particularly damaging to the environment.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Compositional Effect}
\framesubtitle{Setting}
\begin{itemize}
    \item
    Consider when the products from the two sectors have a constant elasticity of substitution $\rho$:
    \begin{equation*}
        Y = \left[\varphi(Y_d)^{\frac{\rho-1}{\rho}} + (1-\varphi)(Y_c)^{\frac{\rho-1}{\rho}} \right]^{\frac{\rho}{\rho-1}}.
    \end{equation*}
    \item
    The price of the final good $Y$ is normalized to one:
    \begin{equation*}
        \left[ \varphi^{\rho} p_d^{1-\rho} + (1-\varphi)^{\rho} p_c^{1-\rho} \right]^{\frac{1}{\rho-1}} = 1.
    \end{equation*}
    \item
    Two Exercises:
    \begin{enumerate}[(i)]
        \item Removing all distortions.
        \item Removing only the distortions in the polluting sector.
    \end{enumerate}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Compositional Effect}
\framesubtitle{Results}
\begin{table}[t]
\footnotesize
\centering
\begin{threeparttable}
\begin{tabular}{lccccccc}
    \hline \hline
                         & \multicolumn{3}{c}{Polluting}    & & \multicolumn{3}{c}{Non-polluting} \\
    \cmidrule{2-4} \cmidrule{6-8}
    Statistics           & Benchmark & (i)      & (ii)      & & Benchmark     & (i)    & (ii) \\
    \midrule
    Physical Output      & 100.00    & 129.64   & 134.63    & & 100.00        & 129.90 &  98.03 \\
    Price                & 100.00    & 99.97    & 85.00     & & 100.00        & 100.00 & 102.34 \\
    Revenue              & 100.00    & 129.60   & 114.42    & & 100.00        & 129.90 & 100.32 \\
    \midrule
    \# of Firms          & 100.00    & 42.63    & 46.44     & & 100.00        & 41.88  &  95.38 \\
    Mean Size            & 64.31     & 152.21   & 176.17    & & 51.16         & 123.50 &  49.38 \\
    \midrule
    Pollution            & 100       & 74.69    & 80.05     \\
    Intensity            & 100       & 57.81    & 59.47     \\
    Clean Share          & 56.18     & 83.80    & 73.10     \\
    \bottomrule
\end{tabular}
\end{threeparttable}
\end{table}
\end{frame}

\section{Conclusion}
\begin{frame}
\frametitle{Conclusions}
\begin{itemize}
\itemsep=0.15in
    \item
    This paper proposes a new explanation for the industrial pollution problem in China:
    \begin{itemize}
        \item
        a negative relationship between firm size and the pollution intensity;
        \item
        expansion of productive firms is limited by distortions.
    \end{itemize}
    \item
    We build a model consistent with the empirical regularities.
    \item
    Quantitative results show that distortions reduce output by 30\% and increase pollution by 20\%.
    \item
    Regulations improves resource allocation on the extensive margin, but worsens the intensive margin by amplifying distortions.
\end{itemize}
\end{frame}

%\begin{frame}
%\frametitle{Future Research}
%\begin{itemize}
%\itemsep=0.15in
%    \item
%    Agricultural Sector:
%    \begin{itemize}
%        \item
%        Our PNAS paper: Land and migration policies on fertilizer intensity.
%        \item
%        What drives the difference in cropping practice of small versus large farmers?
%        \item
%        What are the structural transformation implications of land consolidation (Hornbeck, 2012, 2014; Bustos et al., 2016; Henderson et al. 2018)?
%    \end{itemize}
%    \item
%    Spatial Distribution of Pollution:
%    \begin{itemize}
%        \item
%        Different forces of economic agglomeration (Combes et al., 2012; Gaubert, 2018).
%        \item
%        Preliminary analysis of the data shows that economic-advanced regions have lower pollution intensity.
%        \item
%        What are the environmental consequences of regional development policies (Kline and Moretti, 2014)?
%    \end{itemize}
%    \item
%    Trade and Structural Change:
%    \begin{itemize}
%        \item
%        The theory of mass consumption (Matsuyama, 2002; Faber and Fally, 2017).
%        \item
%        Economic Density (Holmes, 2011; Lagakos, 2016).
%    \end{itemize}
%\end{itemize}
%\end{frame}

\begin{frame}
\begin{center}
\LARGE{Thank You!}
\end{center}
\end{frame}

\section{Appendix}

\begin{frame}
\begin{center}
\LARGE{Appendix}
\end{center}
\end{frame}

\begin{frame}[label=coddef]
\small
\frametitle{Chemical Oxygen Demand Definition}
\begin{itemize}
\itemsep=0.15in
    \item
    In environmental chemistry, the chemical oxygen demand (COD) test is commonly used to {\color{black}indirectly measure the amount of organic compounds in water}. Most applications of COD determine the amount of organic pollutants found in surface water (e.g. lakes and rivers) or waste water, making COD a useful measure of water quality. It is expressed in milligrams per liter (mg/L) also referred to as ppm (parts per million), which indicates the mass of oxygen consumed per liter of solution.
    \item
    COD is an indirect measure that indicates the presence of contaminants that will eventually cause oxygen loss.
\end{itemize}
\hyperlink{datasource}{\beamergotobutton{Data Source}}
\end{frame}

\begin{frame}[label=pollutants]
\frametitle{Major Pollutant Discharge}
\begin{table}[t]
\footnotesize
\centering
\begin{threeparttable}
\begin{tabular}{lcccccccccc}
    \hline \hline
        & Waste & COD  & Petro & $\text{NH}_4^+$ & BOD  & CN   & $\text{Cr}^{6+}$ & Phenol & As   & Cr   \\
    \midrule
    Key & 76.2  & 73.2 & 31.4  & 25.2            & 17.5 & 4.90 & 4.86             & 2.42   & 2.27 & 2.01 \\
    Reg & 35.2  & 28.3 & 7.91  & 6.49            & 2.56 & 0.13 & N/A              & 0.04   & 0.07 & N/A  \\
    \bottomrule
\end{tabular}
\begin{tablenotes}
     \footnotesize{\item[$\dagger$]
     Data Source: National General Survey of Pollution Sources. \\
     Acronyms: \\
     {\color{purpledef}Waste}: Wastewater; {\color{purpledef}COD}: Chemical Oxygen Demand; {\color{purpledef}Petro}: Petrochemicals; {\color{purpledef}$\text{NH}_4^+$}: Ammonian \\
     {\color{purpledef}BOD}: Biochemical Oxygen Demand; {\color{purpledef}CN}: Cyanidium; {\color{purpledef}$\text{Cr}^{6+}$}: Hexavalent Chromium \\
     {\color{purpledef}Phenol}: Volatile Phenols; {\color{purpledef}As}: Arsenium; {\color{purpledef}Cr}: Chromium.}
\end{tablenotes}
\label{tab:nfirmPollutant}
\end{threeparttable}
\end{table}
\hyperlink{datasource}{\beamergotobutton{Data Sources}}
\end{frame}

\begin{frame}[label=codscatter]
\frametitle{Firm Size and Pollution Intensity}
\makebox[\linewidth]{%
  \includegraphics[width=0.3\textwidth]{./Figures/paper_ez.pdf}%
  \includegraphics[width=0.3\textwidth]{./Figures/agri_ez.pdf}
  \includegraphics[width=0.3\textwidth]{./Figures/text_ez.pdf}}
\\
\makebox[\linewidth]{%
  \includegraphics[width=0.3\textwidth]{./Figures/chem_ez.pdf}
  \includegraphics[width=0.3\textwidth]{./Figures/bever_ez.pdf}
  \includegraphics[width=0.3\textwidth]{./Figures/pooled_intensity_size.pdf}}
\end{frame}

\begin{frame}[label=treatment2]
\small
\frametitle{Treatment Technologies}
\framesubtitle{Efficiency of Technologies}
\begin{itemize}
\itemsep=0.15in
    \item
    Examples of the treatment technologies:
    \begin{itemize}
    \item {\color{black}Physical}: Filtering, Centrifuging, Precipitation Separation, etc.
    \item {\color{black}Chemical}: Oxidation-reduction, neutralization, etc.
    \item {\color{black}Biological}: Aerobic Biological Treatment, Activated Sludge Process, etc.
    \end{itemize}
    \item
    In the U.S. wastewater treatment system,
    \begin{itemize}
        \item
        Physical technology: preliminary and primary treatments.
        \item
        Chemical and biological technologies: secondary and tertiary treatments.
    \end{itemize}
\end{itemize}
\hyperlink{treatment1}{\beamergotobutton{Treatment Technology}}
\end{frame}

\begin{frame}[label=treattech2]
\small
\frametitle{Treatment Technologies}
\framesubtitle{Costs, Capacity and Production Scale}
\makebox[\linewidth]{
    \includegraphics[width=0.33\textwidth]{./Figures/abate_cap.pdf}
    \includegraphics[width=0.33\textwidth]{./Figures/abate_inv.pdf}}
\\
\makebox[\linewidth]{
    \includegraphics[width=0.33\textwidth]{./Figures/abate_unit.pdf}
    \includegraphics[width=0.33\textwidth]{./Figures/abate_prod.pdf}}
\hyperlink{treatment1}{\beamergotobutton{Treatment Technology}}
\end{frame}

\begin{frame}[label=esdist]
\frametitle{Firm Size Distribution}
\framesubtitle{By Industry}
\makebox[\linewidth]{%
  \includegraphics[width=0.3\paperwidth,height=0.35\paperheight]{D:/PaperDrafts/Pollution/R_Implementation/paperES_R.pdf}%
  \includegraphics[width=0.3\paperwidth,height=0.35\paperheight]{D:/PaperDrafts/Pollution/R_Implementation/agriES_R.pdf}
  \includegraphics[width=0.3\paperwidth,height=0.35\paperheight]{D:/PaperDrafts/Pollution/R_Implementation/textileES_R.pdf}}
\\
\makebox[\linewidth]{%
  \includegraphics[width=0.3\paperwidth,height=0.35\paperheight]{D:/PaperDrafts/Pollution/R_Implementation/chemmatES_R.pdf}
  \includegraphics[width=0.3\paperwidth,height=0.35\paperheight]{D:/PaperDrafts/Pollution/R_Implementation/beverES_R.pdf}
  \includegraphics[width=0.3\paperwidth,height=0.35\paperheight]{D:/PaperDrafts/Pollution/R_Implementation/poolES_R.pdf}}
\hyperlink{esdistall}{\beamergotobutton{Polluting and All Manufacturing}}
\end{frame}

\begin{frame}[label=accountingrbst]
\small
\frametitle{Robustness of the Accounting Exercise}
\begin{itemize}
    \item
    We need to estimate the employment--production relationship of Chinese firms because
    \begin{itemize}
    \item the U.S data contain only information on number of employees;
    \item the pollution census has information on production, but {\color{black}not} on number of employees.
    \end{itemize}
    \item
    China National Economic Census data are used.
    \item
    Results:
    \begin{table}[t]
    \footnotesize
    \centering
    \begin{threeparttable}
    %\caption{Size Distribution on Pollution}
    \begin{tabular}{lccccccc}
        \hline \hline
        Method             & Paper  & Agri   & Tex    & Chem    & Bever        & Pooled & Reduc  \\
        \midrule
        Non-parametric      & 39.8\% & 60.7\% & 81.6\% & 102.5\% & 103.7\%      & 63.5\% & 28.2\% \\
        Piecewise-linear    & 34.8\% & 69.4\% & 93.5\% & 180.1\% & N/A          & 75.4\% & 19.0\% \\
        Parametric          & 43.5\% & 61.1\% & 97.5\% & 101.2\% & 89.0\%       & 67.0\% & 25.5\% \\
        \bottomrule
    \end{tabular}
    \end{threeparttable}
    \end{table}
\end{itemize}
\hyperlink{accounting}{\beamergotobutton{Accounting Exercise}}
\end{frame}

\begin{frame}[label=firm_opt1]
\frametitle{Firm's Optimization}
\framesubtitle{Setting}
\begin{itemize}
    \item
    Non-polluting sector:
    \begin{equation*}
        \pi^c(z) = \max_{k,l}\left\{(1-\tau_z)z^{1-\gamma}(k^{\alpha}l^{1-\alpha})^{\gamma} - Wl - Rk \right\}.
    \end{equation*}
    \item
    Polluting sector:
    \begin{itemize}
        \item
        Technology Adoption:
        \begin{equation*}
            \pi^d(z) = \max_{i \in \{0,1\}} \left\{ \pi^d_0(z), \pi^d_1(z) \right\}.
        \end{equation*}
        \item
        Profits when using dirty technology
        \begin{equation*}
            \pi^d_0(z) = \max_{k,l} \left\{ (1-\xi )\left[ \left( 1-\tau_z \right) z^{1-\gamma} (k^{\alpha} l^{1-\alpha})^{\gamma} - Wl - Rk \right] \right\}.
        \end{equation*}
        \item
        Profits when using clean technology
        \begin{equation*}
            \pi^d_1(z) = \max_{k,l} \left\{\left( 1-\tau_z \right) z^{1-\gamma} (k^{\alpha} l^{1-\alpha})^{\gamma} - Wl - R(k+k_E) \right\}.
        \end{equation*}
    \end{itemize}
\end{itemize}
\hyperlink{gedef}{\beamergotobutton{Equilibrium}}
\end{frame}

\begin{frame}[label=firm_opt2]
\frametitle{Firm's Optimization}
\framesubtitle{Technology Adoption Decision}
\begin{itemize}
\itemsep=0.15in
    \item
    Difference in potential profits using different technologies:
    \begin{equation*}
        \pi_1^d(z) - \pi_0^d(z) = \frac{\xi (1-\gamma)}{(1-\alpha)\gamma} W l^d(z) - Rk_E.
    \end{equation*}
    \item
    There exists a threshold $z^E$ where firms switch technology.
    \begin{itemize}
    \itemsep=0.10in
        \item
        $z_E$ increases with $\xi$ and decreases with $k_E$.
        \item
        $z_E$ increases with $\tau_z$.
    \end{itemize}
\end{itemize}
\hyperlink{prop1}{\beamergotobutton{Graphical}}
\end{frame}

\begin{frame}[label=fitness1]
\frametitle{Model Fit Benchmark Full Groups}
\makebox[\linewidth]{
    \includegraphics[width=0.45\paperwidth,height=0.45\paperheight]{D:/PaperDrafts/Pollution/PrelimResults/sizedist_china_full.eps}
    \includegraphics[width=0.45\paperwidth,height=0.45\paperheight]{D:/PaperDrafts/Pollution/PrelimResults/eshare_china_full.eps}}
\hyperlink{fitness}{\beamergotobutton{Model Fit}}
\end{frame}

\begin{frame}[label=peresults]
\frametitle{Monopolistic Competition}
\framesubtitle{Setting}
\begin{itemize}
\itemsep=0.15in
    \item
    The crucial elements of our analysis:
    \begin{itemize}
        \item a non-degenerate distribution of firms;
        \item profits be a function of productivity.
    \end{itemize}
    \item
    Melitz (2003) setting:
    \begin{itemize}
        \item
        CES preference:
        \begin{equation*}
            U = \left[\int_{\omega \in \Omega} q(\omega)^{\frac{\rho-1}{\rho}} d\omega \right]^{\frac{\rho}{\rho-1}}.
        \end{equation*}
        \item
        Linear production function:
        \begin{equation*}
            y = F(z,l) = zl.
        \end{equation*}
        \item
        Monopolistic competition:
        \begin{equation*}
            \max_{p(z), q(z)} \left\{p(z)q(z) - Wl \right\}.
        \end{equation*}
    \end{itemize}
\end{itemize}
\hyperlink{geresults}{\beamergotobutton{Perfect Substitutes}}
\end{frame}

\begin{frame}
\frametitle{Monopolistic Competition}
\framesubtitle{Equivalence between Lucas (1978) and Melitz (2003)}
\begin{itemize}
\itemsep=0.15in
    \item
    The equivalence between {\color{purpledef}Lucas (1978)} and \rtext{Melitz (2003)}:
    \begin{itemize}
        \item Intensive margin
        \begin{equation*}
            {\color{purpledef}l(z) = \left(\frac{\gamma}{W} \right)^{\frac{1}{1-\gamma}}z}, \qquad \rtext{l(z) = Q \left(\frac{W\rho}{\rho-1} \right)^{-\rho} z^{\rho-1}}.
        \end{equation*}
        \item Intensive margin
        \begin{equation*}
            {\color{purpledef}\pi(z) = \left[\left(\frac{\gamma}{W}\right)^{\frac{\gamma}{1-\gamma}} - W\left(\frac{\gamma}{W}\right)^{\frac{1}{1-\gamma}} \right]z}
        \end{equation*}
        \begin{equation*}
            \rtext{\pi(z) = \frac{Q}{\rho} \left(\frac{\rho-1}{\rho} \right)^{\rho-1}z^{\rho-1}}.
        \end{equation*}
    \end{itemize}
    \item
    The equivalence of diminishing returns to scale and to utility.
\end{itemize}
\hyperlink{geresults}{\beamergotobutton{Perfect Substitutes}}
\end{frame}

\end{document}

### 2019-09-27 Quantitative/misc.m

@@ -40,7 +40,7 @@ disp('The Role of Technology')
 disp(1-(1-prodredi)/(1-totredi))
 
 % Plot the tax function
-clear ;
+clear all ;
 load('./Results/benchmark_new.mat');
 figure(1)
 plot(log(zgrid(indzhatc:end)),tauzc(indzhatc:end),'LineWidth',2);

### 2019-10-07 Documentation/IMF_RES_Fall_2019.tex
slides updated

@@
     \inst{\ddagger} {Fudan University}}
-\date[IMF (RES) Fall 2019]{\footnotesize{\today} \\ \scriptsize{The views expressed here are those of the authors and do not necessarily reflect the views of the CAEP and the IMF.}}
+\date[IMF (RES) Fall 2019]{\footnotesize{\today} \\ \scriptsize{The views expressed here are those of the authors and do not necessarily reflect the views of the CAEP or the IMF.}}
 
@@
     \item
-    We argue that misallocation across firms reduces output and amplifies industrial pollution by distorting the firm size distribution.
+    We argue that misallocation across firms reduces output and amplifies industrial pollution by distorting firm size distribution.
     \item
@@
         \item
-        Reducing the distortions firms face increases output while reducing pollution.
+        Reducing the distortions firms face increases output while decrease pollution.
         \item
@@
         \item
-        Compared to an economy with fewer distortions (e.g., the U.S.), less productive firms with higher pollution intensity are active.
+        Compared to an economy with fewer distortions (e.g., the U.S.), less productive but more polluting firms survive.
         \item
@@
         \item
-        We emphasize the role of distortions and size distribution.
+        We emphasize the role of economic factors.
     \end{itemize}
@@
         \item Removing Distortions
-        \item Tightening Regulations
+        \item Strengthening Regulations
     \end{itemize}
@@
     \item
-    Firm sales, emission, and treatment equipment.
+    Firm output, emission and treatment equipment.
     \end{itemize}
@@
     \item
-    Firm sales, employment, labor compensation, and capital stock.
+    Firm output, employment labor compensation, and capital stock.
     \end{itemize}
@@
     \itemsep=0.10in
-    \item More than 70\% of firms in our sample have positive COD emissions.
+    \item More than 70\% firms in our sample have positive COD emission.
     \item COD emission is highly correlated with those of other pollutants.
@@
     \begin{itemize}
-        \item For the polluting industries, they account for 90\% of the emissions, and 80\% of the production.
+        \item For the polluting industries, they account for 90\% of the emission and 80\% of the production.
     \end{itemize}
@@
     \item
-    $\mathbf{X}_i$ controls for sectors, provinces, and ownership rights.
+    $\mathbf{X}_i$ controls for sectors, provinces and ownership rights.
     \begin{itemize}
@@
     \item
-    As sales rise by 1\%, emission intensity drops by $(1-0.63) = 0.37\%$.
+    As output rises by 1\%, emission intensity drops by $(1-0.63) = 0.37\%$.
 \end{itemize}
@@
     \item
+    Treatment efficiency: $1 - \text{COD Emitted}/\text{COD Generated}$.
+    \begin{itemize}
+    \item
     For the Paper industry:
-    \begin{itemize}
-    \item
-    Treatment efficiency ($1 - \text{COD Emitted}/\text{COD Generated}$):
     \end{itemize}
@@
     \begin{align*}
-        \text{Physical:}   \quad \log (\text{COD}_i) &= \underset{(0.40)}{-3.50} + \underset{(0.01)}{0.58} \times \log (\text{Sales}_i) + \mathbf{X}_i\gvec{\upgamma} + \epsilon_i, \\
-        \text{Chemical:}   \quad \log (\text{COD}_i) &= \underset{(0.49)}{-4.59} + \underset{(0.01)}{0.77} \times \log (\text{Sales}_i) + \mathbf{X}_i\gvec{\upgamma} + \epsilon_i, \\
-        \text{Biological:} \quad \log (\text{COD}_i) &= \underset{(0.20)}{-4.37} + \underset{(0.01)}{0.67} \times \log (\text{Sales}_i) + \mathbf{X}_i\gvec{\upgamma} + \epsilon_i.
+        \text{Physical:}   \quad \log (\text{COD}_i) &= \underset{(0.40)}{-3.50} + \underset{(0.01)}{0.58} \times \log (\text{Output}_i) + \mathbf{X}_i\gvec{\upgamma} + \epsilon_i, \\
+        \text{Chemical:}   \quad \log (\text{COD}_i) &= \underset{(0.49)}{-4.59} + \underset{(0.01)}{0.77} \times \log (\text{Output}_i) + \mathbf{X}_i\gvec{\upgamma} + \epsilon_i, \\
+        \text{Biological:} \quad \log (\text{COD}_i) &= \underset{(0.20)}{-4.37} + \underset{(0.01)}{0.67} \times \log (\text{Output}_i) + \mathbf{X}_i\gvec{\upgamma} + \epsilon_i.
     \end{align*}
@@
     \item
-    {\color{blue}Question:} How will the {\color{black}average pollution intensity} change if the {\color{black}size distribution} is mechanically changed to that in the U.S.?
+    {\color{blue}Question:} How will {\color{black}average pollution intensity} change if the {\color{black}size distribution} is mechanically changed to that in the U.S.?
     \begin{itemize}
@@
         \item
-        It captures the \textit{Technique} effect while holding the \textit{Scale} effect constant.
+        It captures the \textit{Technique Effect} while holding the \textit{Scale Effect} constant.
     \end{itemize}
@@
     \item
-    Each sector features a Lucas (1978) span-of-control model.
+    Each sector features a Lucas (1978) span-of-control economy.
     \item
@@
     \item
-    Correlated distortions that increase with firm size (Restuccia and Rogerson, 2008).
+    Correlated distortions that increase with firm's productivity (Restuccia and Rogerson, 2008).
     \begin{itemize}
@@
         \item The CDFs are $G^c(z)$ and $G^d(z)$ with a common support $Z \triangleq [0,\overline{z}]$;
-        \item $z$ is fixed once drawn.
+        \item $z$ is fixed once drawn;
         \item A fraction $\mu$ of members possess talent in the \btext{polluting} sector.
@@
     \item
+    Let {\color{blue}$\tau_{z_i}, \tau_{k_i}$} and {\color{blue}$\tau_{l_i}$} be the wedges firm $i$ faces on the product, capital and labor market, the problem of firm $i$ is
+    \begin{equation*}
+      \pi_i = \max_{k_i,l_i} \left\{ (1-\tau_{z_i}) z_i^{1-\gamma} (k_i^{\alpha} l_i^{1-\alpha})^{\gamma} - (1+\tau_{k_i})Rk_i - (1+\tau_{l_i})W l_i \right\}.
+    \end{equation*}
+    \item
     We use the variations in average factor products to measure these wedges (Hsieh and Klenow, 2009).    
-    \item
-    Let {\color{blue}$\tau_{z_i}, \tau_{k_i}$} and {\color{blue}$\tau_{l_i}$} be the wedges firm $i$ faces on the product, capital and labor market, the problem of firm $i$ is
-    \begin{equation*}
-      \pi_i = \max_{k_i,l_i} \left\{ (1-\tau_{z_i}) z_i^{1-\gamma} (k_i^{\alpha} l_i^{1-\alpha})^{\gamma} - (1+\tau_{k_i})Rk_i - (1+\tau_{l_i})W l_i \right\}.
-    \end{equation*}
     \item
@@
         \item
-        $z_E$ increases with $\xi$ and decreases with $k_E$.
+        $z_E$ decreases with $\xi$ and increases with $k_E$.
         \item

### 2019-11-15 Documentation/Pollution_Final_AEJ_Template_Ver2.tex
final submission

@@
     Consumption          & 100.00    & 123.63   & 100.02    & & 100.00        & 123.63 & 100.02 \\
-    Wage                 & 100.00    & 160.00   & 99.96     & & 100.00        & 160.00 &  99.96 \\
+    Wage                 & 100.00    & 160.00   & 99.95     & & 100.00        & 160.00 &  99.95 \\
     Output per Worker    & 100.00    & 128.25   & 100.15    & & 100.00        & 128.60 &  99.95 \\
@@
     \hline
-    \# of Firms          & 100.00    & 44.07    & 89.86     & & 100.00        & 41.56  & 100.00 \\
+    \# of Firms          & 100.00    & 44.07    & 89.85     & & 100.00        & 41.56  & 100.00 \\
     Mean Size            & 59.98     & 139.19   & 65.98     & & 52.18         & 126.53 &  52.35 \\
@@
     \hline
-    Pollution            & 100       & 76.67    & 85.82     \\
-    Intensity            & 100       & 58.46    & 86.73    \\
+    Pollution            & 100       & 76.67    & 85.83    \\
+    Intensity            & 100       & 58.45    & 86.70    \\
     Clean Share          & 57.77     & 85.61    & 85.10     \\
@@
     \multicolumn{3}{l}{\textbf{Non-polluting Sector:}} \\
-    \ \ \ Benchmark   & 2.42          & 3.78          & 6.65          & 15.39         & 71.75          \\
+    \ \ \ Benchmark   & 2.43          & 3.78          & 6.65          & 15.39         & 71.75          \\
     \ \ \ Case (i)    & 1.30          & 2.49          & 5.68          & 16.97         & 73.57          \\
-    \ \ \ Case (ii)   & 2.42          & 3.78          & 6.65          & 15.39         & 71.75          \\
+    \ \ \ Case (ii)   & 2.43          & 3.78          & 6.65          & 15.39         & 71.75          \\
     \hline
@@
     Consumption          & 100.00    & 106.57   & 123.63    & & 100.00        & 106.57 & 123.63 \\
-    Wage                 & 100.00    & 108.76   & 160.00    & & 100.00        & 108.76 & 160.00 \\
+    Wage                 & 100.00    & 108.77   & 160.00    & & 100.00        & 108.77 & 160.00 \\
     Output per Worker    & 100.00    & 105.74   & 128.25    & & 100.00        & 106.03 & 128.60 \\
     \hline
-    \# of Firms          & 100.00    & 44.07    &44.07      & & 100.00        & 41.56  & 41.56 \\
+    \# of Firms          & 100.00    & 44.07    & 44.07     & & 100.00        & 41.56  & 41.56 \\
     Mean Size            & 59.98     & 139.19   & 139.19    & & 52.18         & 126.53 & 126.53 \\
@@
     Pollution            & 100       & 70.04    & 76.67     \\
-    Intensity            & 100       & 64.78    & 58.46     \\
-    Clean Share          & 57.77     & 73.33    & 85.61     \\
+    Intensity            & 100       & 64.77    & 58.45     \\
+    Clean Share          & 57.77     & 73.34    & 85.61     \\
     \hline

### 2019-11-15 Documentation/Replication_Instruction.tex
slides
final submission

@@
 Section \rom{3} shows how the results in the appendices can be replicated.
+The data and code can be downloaded from the AEA Data and Code Repository (OPENICPSR-112005).
 
@@
 MATLAB is used to compute all the quantitative results.
-There is no particular scientific reason that we use one statistical software (\textsc{Stata}) for data cleaning and the other (\code{R}) for empirical analysis.\footnote{Due to limited backward compatibility of \textsc{Stata} and that the \code{foreign} package of \code{R} supports only \code{.dta} files saved by \textsc{Stata} up to Version 12, to run the code without any modification, the reader would need \textsc{Stata} 12.
-Readers with more recent version of \textsc{Stata} would need to either modify in the \code{.do} file everywhere \code{.dta} files are read and written, or use alternative \code{R} package (for instance \code{readstata13}) to convert the data in \bcode{cpsc\_convert.R} and \bcode{cec\_convert.R}.
-Compatibility of our code is not tested under such environments.
-However, none of our results should be affected though.} Veterans of \textsc{Stata} or \code{R} should be able to replicate all the empirical results with just one software using our source code as reference with ease.
+There is no particular scientific reason that we use one statistical software (\textsc{Stata}) for data cleaning and the other (\code{R}) for empirical analysis.
+Veterans of \textsc{Stata} or \code{R} should be able to replicate all the empirical results with just one software using our source code as reference with ease.
 In addition, it should go without saying that for readers without a licence to MATALB, GNU Octave could be used instead.
+
+The specific versions we use are: \textsc{Stata} 12, \texttt{R} 3.5.3 (code name \textit{Great Truth}) and MATLAB R2016a.
+The readers may need to do some very minor syntax change if using other versions.
+None of our results should be affected though.
+We did test our code in other versions of the softwares to the best as we could.
+Below are two examples:
+\begin{itemize}
+    \item
+    Due to limited backward compatibility of \textsc{Stata} and that the \code{foreign} package of \code{R} supports only \code{.dta} files saved by \textsc{Stata} up to Version 12, readers with more recent version of \textsc{Stata} would need to either modify in the \code{.do} file everywhere \code{.dta} files are read and written, or use alternative \code{R} package (for instance \code{readstata13}) to convert the data in \bcode{cpsc\_convert.R} and \bcode{cec\_convert.R}.
+    \item
+    The syntax for several routines was slightly changed in MATLAB R2014b. If vintage versions are used, the reader would get a complaint saying (here from R2014a)
+\begin{verbatim}    
+Error using optimoptions (line 105)
+'OptimalityTolerance' is not an option for FSOLVE.
+A list of options can be found on the FSOLVE documentation page.
+\end{verbatim}
+    The code would run through by simply fixing the syntax to R2014a version; namely, the keywords to two optimization option need to be changed to \code{TolFun} and \code{MaxIter}.
+The code will run through seamlessly.
+\end{itemize}
 
@@
 Our copy was obtained from Fudan University.
+\\ \rtext{MORE INFORMATION IS NEEDED HERE!!!!!!!!}
     \item
@@
         \item
-        \bcode{./compute\_tables.m}: computes the raw data used to calculate Tables 4, 5 and 6 in the main text.
+        \bcode{./generate\_tables\_main.m}: prints Tables 4, 5 and 6 in the main text.
         \item
@@
         \item
-        \bcode{./compute\_tables\_ces.m}: computes the raw data used to calculate Tables J.1 in Appendix J.
+        \bcode{./generate\_tables\_appendix.m}: prints Table J.1 in Appendix J.
         \item
@@
 The file \bcode{cpsc\_convert.R} converts \bcode{keynum.dta} to \bcode{KEYFIRM\_R.RData}, \bcode{regall.dta} to \bcode{REGFIRM\_R.RData} and \bcode{allfirms.dta} to \bcode{ALLFIRM\_R.RData}.
-Similarly, \bcode{cec\_convert.R} converts \\ \bcode{cec2004\_small.dta} to \bcode{DSMALL\_R.RData}, \bcode{cec2004\_large\_full.dta} to \bcode{DLARGE\_R.RData}.
-It then extracts only the variables used in the paper and combines the two \code{.RData} files to one file \bcode{CNEC\_avgp.RData}.
+Similarly, \bcode{cec\_convert.R} converts \bcode{cec2004\_small.dta} to \bcode{DSMALL\_R.RData}, \bcode{cec2004\_large\_full.dta} to \bcode{DLARGE\_R.RData}.
+It then extracts only the variables used in the paper and combines the two \code{.RData} files to one file \\ \bcode{CNEC\_avgp.RData}.
 All the files are saved under \bcode{./Empirical/Data/} as before.
@@
 \end{itemize}
+Because we cannot post the NGSPS and CNEC publicly, the readers will not be able to run some of the files.
+Tables \ref{tab:navi_main} and \ref{tab:navi_appendix} list respectively which part of each file depends on which datasets and generates which results; the datasets are referenced using the above two-letter acronyms.
 
@@
 Because according to Row 1 of Table 1, the five industries combined contribute to 77\% of total COD emission, assuming that industries emitting the other 23\% COD remain intact, the 25\% reduction in average intensity is simply calculated as $1 - (67\% \times 77\% + 100\% \times 23\%) \triangleq 25\%$.
+The calculation of the two numbers are automated in the code.
     \item
@@
     \item
-    Tables 4, 5 and 6 are calculated using the output of \bcode{compute\_tables.m}.
+    Similarly, file \bcode{generate\_tables\_main.m} reads the four \code{.mat} files and prints Tables 4, 5 and 6 to MATLAB terminal.
+    %Tables 4, 5 and 6 are calculated using the output of \bcode{compute\_tables.m}.
 Notice that Tables 4 and 6 are presented in relative changes and share a similar structure.
@@
 
-    The in-text decomposition of total reduction to the contribution of size distribution and technology adoption can be performed using \bcode{misc.m}.
-The reader needs to change the second input file to either \bcode{notax\_new.mat} or \bcode{regulation\_new.mat}, depending on the case to compute.
+    The in-text decomposition of total reduction to the contribution of size distribution and technology adoption can be performed using \bcode{misc.m}.\footnote{The code snippet \textit{must be} executed by using the MATLAB shortcut of 'Select $\rightarrow$ F9'.
+Executing \bcode{misc.m} by using the \textit{Run} command in MATLAB toolstrip would yield an error when calling the function \code{plot}.
+This is confirmed to be a known issue by staff from MathWorks.
+The supporting team claims that the issue has been fixed in MATLAB R2019b.
+We were not able to test the code under the environment.} The reader needs to change the second input file to either \bcode{notax\_new.mat} or \bcode{regulation\_new.mat}, depending on the case to compute.
 The role of technology adoption is printed to the terminal, with the residual being that from the size distribution.
@@
     \item
-    With all the \code{*.mat} files computed, as before, \bcode{compute\_tables\_ces.m} computes the raw data used in calculating entries in Table J.1.
-The results printed to the terminal can then be used to compute the percentage changes between equilibria in Table J.1.
-In particular, with the three cases at hand, the upper panel of Table J.1 can be reproduced.
+    Repeat Step 9 with the parameters set to CES $=$ 3.0 will generate three corresponding \code{.mat} files:
+    \begin{itemize}
         \item
-    Repeating Steps 9 and 10 with the parameters set to CES $=$ 3.0 then produces the lower panel of Table J.1, which finally completes the replication of all the results in our paper.
+        \bcode{./Quantitative/Results/benchmark\_ces3.mat}
+        \item
+        \bcode{./Quantitative/Results/nodirty\_ces3.mat}
+        \item
+        \bcode{./Quantitative/Results/notax\_ces3.mat}
+    \end{itemize}
+    \item
+    With all the \code{*.mat} files computed, as before, \bcode{generate\_tables\_appendix} prints Table J.1 to MATLAB terminal. This completes the replication of our paper.
 \end{enumerate}
@@
 The correspondence between the log files and the source code is as follows.
+Once again, to \textit{exactly} replicate what is in these files, the reader needs to use the exact same version of the softwares as we do.
 The original log files are saved in text files of \code{.log} extension with the same names.

### 2019-11-15 Empirical/Accounting.R

@@ -646,3 +646,13 @@ ppar <- c(ppar_paper,ppar_agri,ppar_text,ppar_chem,ppar_bever)
 pmed
 preg
 ppar
+
+# wgt is the first row of Table 1, main text
+wgt = c(0.334,0.151,0.140,0.104,0.0427)
+# ======================= Intext Page 12 ===================================
+# Decrease in average pollution intensity, top-5 polluting
+reduction5 <- 1-sum(wgt*ppar)/sum(wgt)
+reduction5
+# Decrease in average pollution intensity, whole manufacturing
+reductionall <- 1-((1-reduction5)*sum(wgt)+(1-sum(wgt)))
+reductionall

### 2019-11-15 Quantitative/compute_tables.m

@@ -11,10 +11,6 @@
 % Author:
 %     - Xin Tang @ International Monetary Fund
 % 
-% File Dependence:
-%     - fcn.m: evaluates all the allocations at a given wage and returns 
-%       the excess demand in the labor market.
-%  
 % Record of Revisions:
 %         Date:                 Description of Changes
 %     ============        =================================

### 2019-11-15 Quantitative/generate_tables_appendix.m

@@ -1,0 +1,423 @@
+% -------------------------------------------------------------------------
+%                      Program Description
+% -------------------------------------------------------------------------
+%   
+% Purpose:
+%     - Generate Appendix Table J.1
+%     - Two Sectors Model with CES Aggregation
+%     - The Size Distribution of Firms and Industrial Water Pollution: A
+%       Quantitative Analysis of China.
+%  
+% Author:
+%     - Xin Tang @ International Monetary Fund
+%  
+% Record of Revisions:
+%         Date:                 Description of Changes
+%     ============        =================================
+%      11/15/2019                 Original Version
+% =========================================================================
+clc;
+clear all;
+
+% ========================= CES = 1.5 =====================================
+% ============= Compute the raw numbers for Benchmark =====================
+load('./Results/benchmark_ces.mat');
+% --------------- Panel A -------------------
+% Aggregate Output
+aggyd_bench = sum(yd(indzhatd:end).*zprob(indzhatd:end));
+aggyc_bench = sum(yc(indzhatc:end).*zprob(indzhatc:end));
+priced_bench = priced ;
+pricec_bench = pricec ;
+aggypd_bench = priced_bench*aggyd_bench;
+aggypc_bench = pricec_bench*aggyc_bench;
+aggyp_bench = aggypd_bench+aggypc_bench;
+aggy_bench = (varces*aggyd_bench^((sigmaces-1)/sigmaces)+...
+    (1-varces)*aggyc_bench^((sigmaces-1)/sigmaces))...
+    ^(sigmaces/(sigmaces-1));
+
+% --------------- Panel B -------------------
+totfirmd_bench = sum(zprob(indzhatd:end));
+totfirmc_bench = sum(zprob(indzhatc:end));
+totfirm_bench = mud*totfirmd_bench + (1-mud)*totfirmc_bench;
+% Mean Size
[…]

### 2019-11-15 Quantitative/generate_tables_main.m

@@ -1,0 +1,760 @@
+% -------------------------------------------------------------------------
+%                      Program Description
+% -------------------------------------------------------------------------
+%   
+% Purpose:
+%     - Generate Tables 4, 5 and 6
+%     - Two Sectors Model
+%     - The Size Distribution of Firms and Industrial Water Pollution: A
+%       Quantitative Analysis of China.
+%  
+% Author:
+%     - Xin Tang @ International Monetary Fund
+%  
+% Record of Revisions:
+%         Date:                 Description of Changes
+%     ============        =================================
+%      11/15/2019                 Original Version
+% =========================================================================
+clc;
+clear all;
+
+% ============= Compute the raw numbers for Benchmark =====================
+load('./Results/benchmark_new.mat');
+% =========================================================================
+%                               Table 4
+%                          Aggregate Impacts
+% =========================================================================
+% --------------- Panel A -------------------
+% Aggregate Output
+aggyd_bench = sum(yd(indzhatd:end).*zprob(indzhatd:end));
+aggyc_bench = sum(yc(indzhatc:end).*zprob(indzhatc:end));
+aggy_bench  = mud*aggyd_bench + (1-mud)*aggyc_bench;
+aggydshare_bench = mud*aggyd_bench/aggy_bench;
+aggycshare_bench = 1-aggydshare_bench;
+% Aggregate Capital
+aggkd_bench = sum(kdd(indzhatd:end).*zprob(indzhatd:end));
+aggkd_bench = aggkd_bench + ke*sum(zprob(indztilded:end));
+aggkc_bench = sum(kdc(indzhatc:end).*zprob(indzhatc:end));
+aggk_bench = mud*aggkd_bench + (1-mud)*aggkc_bench ;
+% Aggregate Consumption
[…]

### 2019-11-15 Quantitative/twosectors.m

@@ -136,6 +136,10 @@ wage = 1.5;
 [wss, fval] = fsolve(@fcn2,wage,...
     optimoptions('fsolve','Display','final-detailed',...
     'OptimalityTolerance',1.0e-8,'MaxIterations',4000));
+% For MATLAB R2014a
+% [wss, fval] = fsolve(@fcn2,wage,...
+%     optimoptions('fsolve','Display','final-detailed',...
+%     'TolFun',1.0e-8,'MaxIter',4000));
 
 % =========================================================================
 %             Compute Model Fit on Key Dimensions

### 2019-11-15 Documentation/Replication_Instruction.tex
final submission

@@
     \item
-    The syntax for several routines was slightly changed in MATLAB R2014b. If vintage versions are used, the reader would get a complaint saying (here from R2014a)
+    The syntax for several routines was slightly changed in MATLAB R2014b. If vintage versions are used, the reader would get a complaint saying (here from R2014a for instance)
 \begin{verbatim}    
@@
 \end{verbatim}
-    The code would run through by simply fixing the syntax to R2014a version; namely, the keywords to two optimization option need to be changed to \code{TolFun} and \code{MaxIter}.
-The code will run through seamlessly.
+    The code would run through by simply fixing the syntax to R2014a version; namely, the keywords to two optimization options need to be changed to \code{TolFun} and \code{MaxIter}.
+The code would then run through seamlessly.
 \end{itemize}

### 2019-11-20 Documentation/DataAppendix_AEJ_Final.tex
final submission

@@
 
-The most important data source that we draw upon in Section \rom{1}.B of the main text is the 2007 \textit{National General Survey of Pollution Sources} (henceforth NGSPS).
+The most important data source that we draw upon in Section \rom{1}.B of the main text is the 2007 \textit{National General Survey of Pollution Sources} (henceforth NGSPS) [\citet{NGSPS:2007}].
 In this section, we provide a detailed description of the dataset, which is based on the following documents:
@@
     \item
-    \textit{Census Program of the National General Survey of Pollution Sources} {\begin{CJK}{GBK}{kai}(第一次全国污染源普查方案)\end{CJK}};
-    \item
-    \textit{Regulation on National General Survey of Pollution Sources [Decree of the State Council of the People's Republic of China (No.508)]} {\begin{CJK}{GBK}{kai}(全国污染源普查条例[中华人民共和国国务院令第508号])\end{CJK}}.
-    \item
-    \textit{Technical Specifications Requirements of the First National General Survey of Pollution Sources} {\begin{CJK}{GBK}{kai}(第一次全国污染源普查技术规定)\end{CJK}}.
+    \textit{Census Program of the National General Survey of Pollution Sources} {\begin{CJK}{GBK}{kai}(第一次全国污染源普查方案)\end{CJK}}, issued by \citet{CensusProgram};
+    \item
+    \textit{The Regulations on National General Survey of Pollution Sources [Decree of the State Council of the People's Republic of China (No.508)]} {\begin{CJK}{GBK}{kai}(全国污染源普查条例[中华人民共和国国务院令第508号])\end{CJK}}, issued by \citet{Decree508};
+    \item
+    \textit{Technical Specifications Requirements of the First National General Survey of Pollution Sources} {\begin{CJK}{GBK}{kai}(第一次全国污染源普查技术规定)\end{CJK}}, issued by \citet{TechSpec}.
 \end{itemize}
 
-For an official introduction to the NGSPS and declassified information at the aggregate level, interested readers could refer to the book \textit{Data Collection of the National General Survey of Pollution Sources} (\begin{CJK}{GBK}{kai}《污染源普查数据集》, 中国环境科学出版社, 2011\end{CJK}), which is publicly available.
+For an official introduction to the NGSPS and declassified information at the aggregate level, interested readers could refer to the book \textit{Data Collection of the National General Survey of Pollution Sources} (\begin{CJK}{GBK}{kai}《污染源普查数据集》, 中国环境科学出版社, 2011\end{CJK}) prepared by \citet{DataCollect}, which is publicly available.
+Besides the NGSPS, we also use two other datasets in preparing this appendix: \textit{China National Economic Census} [\citet{CNEC:2004}] and \textit{Statistics of U.S.
+Businesses} [\citet{SUSB:2004}].
 
@@
 The survey was organized directly by the State Council with data collection and quality control done by specially trained field staff.
-According to the Regulation on National General Survey of Pollution Sources [Decree of the State Council of the People's Republic of China (No.
-508)], faking data would lead to financial penalties or even lawsuits.
+According to the \citet{Decree508}, faking data would lead to financial penalties or even lawsuits.
 The purpose of the NGSPS is to understand the total number of pollution sources and their distribution in different industries and regions; to understand the generation, discharge and treatment of major pollutants; to establish records for key pollution sources; to build a pollution source information database and an environmental statistics platform; and to provide basis for formulating policies and plans for economic and social development and environmental protection.
@@
 For all panels, log-scale is used in the horizontal axes.
-\begin{figure}[htbp]
+\begin{figure}[t]%[htbp]
     \begin{center}
@@
     \textbf{CES $=$ 1.5} \\
-    \ \ \ Physical Output      & 100.00    & 129.64   & 134.63    & & 100.00        & 129.90 &  98.03 \\
+    \ \ \ Physical Output      & 100.00    & 129.64   & 134.63    & & 100.00        & 129.94 &  98.03 \\
     \ \ \ Price                & 100.00    & 99.97    & 85.00     & & 100.00        & 100.00 & 102.34 \\
-    \ \ \ Revenue              & 100.00    & 129.60   & 114.42    & & 100.00        & 129.90 & 100.32 \\
+    \ \ \ Revenue              & 100.00    & 129.60   & 114.42    & & 100.00        & 129.94 & 100.32 \\
     \midrule
-    \ \ \ \# of Firms          & 100.00    & 42.63    & 46.44     & & 100.00        & 41.88  &  95.38 \\
+    \ \ \ \# of Firms          & 100.00    & 42.63    & 46.44     & & 100.00        & 41.87  &  95.38 \\
     \ \ \ Mean Size            & 64.31     & 152.21   & 176.17    & & 51.16         & 123.50 &  49.38 \\
     \midrule
-    \ \ \ Pollution            & 100       & 74.69    & 80.05     \\
-    \ \ \ Intensity            & 100       & 57.81    & 59.47     \\
+    \ \ \ Pollution            & 100       & 74.95    & 80.04     \\
+    \ \ \ Intensity            & 100       & 57.81    & 59.45     \\
     \ \ \ Clean Share          & 56.18     & 83.80    & 73.10     \\
@@
     \midrule
-    \ \ \ Pollution            & 100       & 74.69    & 89.61     \\
-    \ \ \ Intensity            & 100       & 57.53    & 55.81     \\
+    \ \ \ Pollution            & 100       & 74.69    & 89.60     \\
+    \ \ \ Intensity            & 100       & 57.53    & 55.82     \\
     \ \ \ Clean Share          & 56.48     & 84.04    & 74.37     \\

### 2019-11-20 Documentation/Pollution_Final_AEJ_Template_Ver2.tex
final submission

@@
 
-This study draws upon three major data sources: the 2007 National General Survey of Pollution Sources (NGSPS) of China, the 2004 China National Economic Census (CNEC), and the Statistics of U.S.
-Businesses (SUSB).
+This study draws upon three major data sources: the 2007 National General Survey of Pollution Sources (NGSPS) of China [\citet{NGSPS:2007}], the 2004 China's National Economic Census [CNEC, \citet{CNEC:2004}], and the Statistics of U.S.
+Businesses [\citet{SUSB:2004}].
 
@@
 The survey is organized directly by the State Council with data collection and quality control done by specially trained field staff.
-According to the \textit{Regulation on the National General Survey of Pollution Sources [Decree of the State Council of the People's Republic of China (No.
+%According to the \textit{Regulation on the National General Survey of Pollution Sources [Decree of the State Council of the People's Republic of China (No.
 508)]}, faking data would lead to financial penalties or even lawsuits.
+According to the \citet{Decree508}, faking data would lead to financial penalties or even lawsuits.
 Therefore, the dataset is administrative in its nature and is subject to less concerns of systematic under-reporting.\footnote{In fact, uniform under-reporting of emissions by small and large firms will not change the basic conclusions of this paper.

### 2019-11-20 Documentation/Replication_Instruction.tex
final submission

@@
             linkcolor=red,
+            urlcolor=black,
             pagebackref=true]{hyperref}
@@
 
-We use three datasets in our analysis: The National General Survey of Pollution Sources (NGSPS, \begin{CJK}{GBK}{kai}第一次全国污染源普查\end{CJK}), The National Economic Census (CNEC, \begin{CJK}{GBK}{kai}第一次全国经济普查\end{CJK}) and the Statistics of U.S.
+We use three datasets in our analysis: The 2007 National General Survey of Pollution Sources (NGSPS, \begin{CJK}{GBK}{kai}第一次全国污染源普查\end{CJK}), The 2004 National Economic Census (CNEC, \begin{CJK}{GBK}{kai}第一次全国经济普查\end{CJK}) and the 2004 Statistics of U.S.
 Businesses (SUSB).
@@
 The dataset is subject to regulation by \textit{The Law of the People's Republic of China on Guarding State Secrets} (\begin{CJK}{GBK}{kai}中华人民共和国保守国家秘密法\end{CJK}) because it contains sensitive information.
-Please refer to \textit{Regulation on Archiving the National General Survey of Pollution Sources Data} (\textit{State Environmental Protection Administration [2007] No.187}, {\begin{CJK}{GBK}{kai}污染源普查档案管理办法[环发[2007]187号]\end{CJK}}).
+Please refer to \textit{Regulation on Archiving the National General Survey of Pollution Sources Data} (\textit{State Environmental Protection Administration [2007] No.187}, {\begin{CJK}{GBK}{kai}污染源普查档案管理办法[环发[2007]187号]]\end{CJK}}).
 The data can only be accessed within the MEE as well as institutions under its direct supervision (\begin{CJK}{GBK}{kai}中华人民共和国生态环境部及其直属单位\end{CJK}).
@@
 
-    Individual researchers not affiliated with the MEE and institutions under its direct supervision need to submit the application through the official portal for requesting Information Access (\begin{CJK}{GBK}{kai} 政府信息公开\end{CJK}) by the MEE at the following url: \url{http://www.mee.gov.cn/weihu/201706/t20170625_416641.shtml}.
-The url is retrieved on September 15th, 2019 and may vary in the future.
+    Individual researchers not affiliated with the MEE and institutions under its direct supervision need to submit the application through the official portal for requesting Information Access (\begin{CJK}{GBK}{kai}政府信息公开\end{CJK}) by the MEE at the following url: \url{http://www.mee.gov.cn/weihu/201706/t20170625_416641.shtml}.
+The url was retrieved on November 15th, 2019 and may vary in the future.
 All applications are subject to official approval by the General Office of Ministry of Ecology and Environment (\begin{CJK}{GBK}{kai}中华人民共和国生态环境部办公厅\end{CJK}).
@@
 We provide a summary in English in Online Appendix A of our paper.
+For more information on the NGSPS, please visit the following websites: \url{http://env.people.com.cn/GB/8220/113963/index.html}, or \url{http://www.mee.gov.cn/home/ztbd/rdzl/wrypc/}.\footnote{The latter website was initially dedicated to the first NGSPS starting in 2007.
+Since the launch of the second NGSPS in 2017, the content of the website has been changed accordingly.
+However, the two surveys share similar structures.} The urls were retrieved on November 15th, 2019 and may vary in the future.
     \item
-    The CNEC is also a confidential dataset belonging to National Bureau of Statistics of China.
+    The CNEC was conducted by the National Bureau of Statistics (NBS) of China in 2004, and was designed to cover the entire population of Chinese firms in that year.
+The firm-level data from the CNEC are not available to the general public and therefore not uploaded as part of our data files.
+For data access, please contact the NBS of China at \url{wgsjsys@stats.gov.cn}.
+For more information on the CNEC, please visit the dedicated page maintained by NBS at the following url: \url{http://www.stats.gov.cn/ztjc/zdtjgz/zgjjpc}.
+The url was retrieved on November 15th, 2019 and may vary in the future.
+   % The CNEC is also a confidential dataset belonging to National Bureau of Statistics of China.
 Many universities and institutions have legal copy of the dataset though.
@@
     \item
-    The SUSB is publicly available from the Census Bureau's dedicated website.
-The url, retrieved on September 15th, 2019, and subject to possible change in the future, is \url{https://www.census.gov/programs-surveys/susb.html}.
+    The SUSB is publicly available from the U.S.
+Census Bureau's dedicated website.
+The url, retrieved on November 15th, 2019, and subject to possible change in the future, is \url{https://www.census.gov/programs-surveys/susb.html}.
 \end{itemize}
 
-In the replication files, we cannot provide micro-level data of the NGSPS and CNEC, due to non-disclosure agreements with the MEE and Fudan University.
-Therefore, we only post the source code that generates the results.
+We cannot provide confidential micro-level data of the NGSPS and CNEC as part of the replication files.
+Instead, we post the source code that generates the results.
 However, to facilitate replication by the readers who have access to the datasets, we post the log files when running the analysis on our computer.

### 2019-11-20 Documentation/Replication_Instruction.tex
final submission

@@
 The firm-level data from the CNEC are not available to the general public and therefore not uploaded as part of our data files.
-For data access, please contact the NBS of China at \url{wgsjsys@stats.gov.cn}.
+For data access, please contact the NBS of China at \code{wgsjsys@stats.gov.cn}.
 For more information on the CNEC, please visit the dedicated page maintained by NBS at the following url: \url{http://www.stats.gov.cn/ztjc/zdtjgz/zgjjpc}.
@@
 Because we cannot post the NGSPS and CNEC publicly, the readers will not be able to run some of the files.
-Tables \ref{tab:navi_main} and \ref{tab:navi_appendix} list respectively which part of each file depends on which datasets and generates which results; the datasets are referenced using the above two-letter acronyms.
+Tables \ref{tab:navi_main} and \ref{tab:navi_appendix} list respectively which part of each file depends on which datasets and generates which result; the datasets are referenced using the above two-letter acronyms.
 
@@
 
-    The in-text decomposition of total reduction to the contribution of size distribution and technology adoption can be performed using \bcode{misc.m}.\footnote{The code snippet \textit{must be} executed by using the MATLAB shortcut of 'Select $\rightarrow$ F9'.
+    The in-text decomposition of total reduction to the contribution of size distribution and technology adoption can be performed using \bcode{misc.m}.\footnote{The code snippet \textit{must be} executed by using the MATLAB shortcut of 'Select $\rightarrow$ F9' unless version 2019b is used.
 Executing \bcode{misc.m} by using the \textit{Run} command in MATLAB toolstrip would yield an error when calling the function \code{plot}.
-This is confirmed to be a known issue by staff from MathWorks.
-The supporting team claims that the issue has been fixed in MATLAB R2019b.
+This is confirmed to be an issue by staff from MathWorks.
+The supporting team informed us that the issue has been fixed in MATLAB R2019b.
 We were not able to test the code under the environment.} The reader needs to change the second input file to either \bcode{notax\_new.mat} or \bcode{regulation\_new.mat}, depending on the case to compute.

### 2020-01-21 Documentation/Replication_Instruction.tex
data_rev_v2

@@
 This note explains step-by-step how to replicate all the results in \textit{The Size Distribution of Firms and Industrial Water Pollution: A Quantitative Analysis of China}.
-We begin with some housekeeping stuff in Section \rom{1}.
+We begin with some housekeeping information in Section \rom{1}.
 Section \rom{2} explains in detail how to replicate all the results in the main text.
@@
 The readers will get a number of files for replicating the results.
-To ease digestion, we briefly introduce the structure of the folders and files.
+To facilitate digestion, we briefly introduce the structure of the folders and files.
 As typographical convention, we use \bcode{blue computer modern typewriter} to indicate \bcode{folders} and \bcode{files}.
@@
         \bcode{./Empirical\_Appendix.R} produces most empirical results in the appendices.
+        \item
+        \bcode{./Empirical\_Public\_Data.R} produces the empirical results reproducible using the published data (SUSB): the U.S. firm size distributions in Figures 2 and E.1 (blue bars).
         \item
@@
 
+\subsection{Reproducibility Using the Published Data}
+
 In what follows, we will only use the files converted by \code{R}.
@@
 Tables \ref{tab:navi_main} and \ref{tab:navi_appendix} list respectively which part of each file depends on which datasets and generates which result; the datasets are referenced using the above two-letter acronyms.
+With the published data, for the empirical part, the readers would be able to replicate the U.S.
+firm size distributions in Figure 2 and E.1 (the blue bars); program \bcode{Empirical\-Public\_Data.R} does the job.
+The program is constructed by taking the relevant code snippet from \bcode{Empirical\_AEJ.R} (Section 3) and \bcode{Empirical\_Appendix.R} (Section 5), as can be seen by direct comparison between the files.
+All the quantitative results can be replicated using the programs provided.
 

### 2020-01-21 Empirical/Empirical_Public_Data.R

@@ -1,0 +1,332 @@
+# --------------------------------------------------------------------------
+#                       Program Description
+# --------------------------------------------------------------------------
+#    
+# Purpose:
+#     - For replicating the U.S. firm size distributions in 
+#         Figures 2 and E.1.
+#     - These are the results reproducible with the published data.
+#     - Code snippet taken directly from Empirical_AEJ.R (Section 3) and
+#         Empirical_Appendix.R (Section 5).
+#     - The Size Distribution of Firms and Industrial Water Pollution: A
+#       Quantitative Analysis of China
+#     - Prepared for AEJ: Macro
+# 
+# Author:
+#     - Xin Tang @ International Monetary Fund
+# 
+# Record of Revisions:
+#          Date:                 Description of Changes
+#    ============        =================================
+#     01/13/2020                  Original Version
+# ==========================================================================
+# Clear memory
+rm(list = ls())
+
+# Load packages
+library(foreign)
+library(data.table)
+library(AER)
+library(scales)
+library(grid)
+
+# ==========================================================================
+#           U.S. Distribution in Figure 2 (blue bar)
+# ==========================================================================
+USall <- read.csv("./Data/susb04.csv",header = TRUE)  
+USall <- as.data.table(USall)
+USall <- USall[,list(NAICS, ENTRSIZE, FIRM, ESTB, 
+                     EMPL, NAICSDSCR, ENTRSIZEDSCR)]
+
+# ------------------------ Pooled Polluting ---------------------------
+sel <- which(USall$NAICS == 3221 | USall$NAICS == 311 
+             | USall$NAICS == 313 | USall$NAICS == 3251 
+             | USall$NAICS == 3252 | USall$NAICS == 3253 
+             | USall$NAICS == 3255 | USall$NAICS == 3256 
[…]
